### 2024-06-25 paper.tex
UQ repo

\documentclass[letterpaper,12pt]{article}
\usepackage{tabularx} % extra features for tabular environment
\usepackage{amsmath}  % improve math presentation
\usepackage{amsfonts}
\usepackage{verbatim}
\usepackage{graphicx} % takes care of graphic including machinery
\usepackage[margin=1in,letterpaper]{geometry} % decreases margins
\usepackage{cite} % takes care of citations
\usepackage[final]{hyperref} % adds hyper links inside the generated pdf file
\hypersetup{
	colorlinks=true,       % false: boxed links; true: colored links
	linkcolor=blue,        % color of internal links
	citecolor=blue,        % color of links to bibliography
	filecolor=magenta,     % color of file links
	urlcolor=blue         
}
\usepackage{blindtext}

\usepackage{units}
\usepackage{lineno}
%++++++++++++++++++++++++++++++++++++++++

\begin{document}
\linenumbers
\title{Uncertain Effects of DFT Functionals on Calculations of Organic semiconductor Charge Mobility}
\author{authors}
\date{\today}
\maketitle

\begin{abstract}
    We study the uncertainty effect from the DFT functional to the charge mobility calculations of organic semiconductors (OSC). 
    The ToF mobilities of the BCP and MADN devices are calculated from the first principle multiscale model. 
    BCP has a large energy disorder while MADN has a small energy disorder.
    Using a total of 10 different DFT functionals, we find that the electronic structure properties have similar distributions as indicated by Wasserstein distance, while the charge mobility of the could have a relatively large deviation.
    Further investigation reveals that ToF can be sensitive to the energy of a single node, leading to the ToF being sensitive to DFT functionals.
    And those nodes are effectively trap nodes.
    Further investigation reveals that the BHANDHLYP functional leads to a trap site, and the charge mobility is very sensitive to the trap sites' energy, so a small change in the site's energy results in a large deviation of ToF.

    We further investigate the uncertainty effect of electronic structure properties on the charge mobility 
    We find that the site energy has the most significant effect on the charge mobility and a confidence level of charge mobility is obtained encoding the maximum amount of uncertainty in electronic structure parameters. 
\end{abstract}

\section{Introduction}
Charge mobility is one of the main quantities of interest for OSC.

Since the charge transport in OSC involves electrons, quantum mechanics and Schr\"odinger equation are essential for the theoretical study of charge mobility.

Charge conductance is due to electron dynamics, so quantum mechanics and Schr\"odinger equation are essential for the theoretical study of charge mobility.

Due to the complexity of Schr\"odinger Equation, one alternative theory is the density functional theory (DFT). DFT has two challenges. Firstly, it is computationally impossible to perform electronic structure calculations for the whole OSC device. And secondly, the exchange-correlation potential in DFT has an unknown formula.

The first challenge is overcome by approximating the electron dynamics as transition processes between the localized states, with the transition rates calculated as the temperature-activated bi-molecule transition rates, known as the Marcus rate. 
The second challenge is addressed by utilizing DFT functionals to represent the exchange-correlation potential. 
Those functionals are benchmarked to achieve good consistency with many physical quantities, such as ionization potential, and density of states.

In the framework of this multiscale model, the accuracy of the DFT functionals determine the accuracy of the calculated mobility.

We can use the steady state mobility,

The influence of the different functionals on ToF calculation is missing. 
In this work, we want to study how the DFT functionals affect the electronic structures and ToF charge mobility.

The goal of this work is to investigate how the DFT functionals affect the electronic structures and ToF charge mobility.
We want to answer questions:

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\label{sec:result}

\subsection{Distribution Distance and ToF Differences}
A summary of the Time-of-Flight (ToF) and molecular energies using different functionals is provided in Table \ref{tab:para}, with the drift ToF detailed in Table \ref{tab:para2}. The tables indicate that while the energy standard deviations $\sigma(E)$ are similar across different functionals, the ToF values vary significantly, notably for functionals like BHANDHLYP, M06L, and BHLYP.

\begin{table}[h]
    \centering
    \begin{tabular}{c c c c c }
    \hline
        Functional & ScaleHFX & $\lambda_h$ [eV] & ToF [s] & $\sigma(E)$ \\ 
        \hline
        PBE0 & 0.25 & 0.388 & 1.23e-3 & 0.175 \\
        PBE & 0 & 0.303 & 1.04e-3 & 0.172 \\ 
        B3LYP & 0.20 & 0.375 & 4.28e-3 & 0.175 \\
        BHANDHLYP & 0.5 & 0.494 & \textbf{737.94} & 0.192 \\
        TPSS & 0 & 0.310 & 1.37e-2 & 0.168 \\
        BP86 & 0 & 0.304 & 7.46e-3 & 0.175 \\
        wB97X & 0.157 & 0.505 & 2.92e-2 & 0.191 \\
        wB97X-D3 & 0.195 & 0.496 & 4.89e-2 & 0.180 \\
        M06L & 0 & 0.312 & 3.19e-1 & 0.165 \\
        BHLYP & 0.5 & 0.493 & 2.47 & 0.192 \\
    \hline
    \end{tabular}
    \caption{Values of $\lambda_h$, ToF, stationary state velocity, and energy standard deviation of BCP molecules calculated from different functionals.}
    \label{tab:para}
\end{table}

\begin{table}[h]
    \centering
    \begin{tabular}{c c c}
    \hline
        Functional & ToF [s] & $\mu$ [m/s] \\ 
        \hline
        PBE0 & 2.39e-8 & 5.68e-5 \\
        PBE & 6.03e-9 & 2.25e-4 \\ 
        B3LYP & 1.67e-8 & 8.13e-5 \\
        BHANDHLYP & 3.36e-4 & 4.04e-9 \\
        TPSS & 1.23e-8 & 1.10e-4 \\
        BP86 & 3.77e-7 & 3.59e-6 \\
        wB97X & 1.68e-6 & 8.08e-7 \\
        wB97X-D3 & 6.92e-7 & 1.96e-6 \\
        M06L & 3.90e-3 & 3.47e-10 \\
    \hline
    \end{tabular}
    \caption{Mobility and ToF with drift electric field $6 \times 10^7$ V/m.}
    \label{tab:para2}
\end{table}

\textbf{Point 1:} To investigate the effect of different functionals $f^\text{DFT}$ on electronic structures, we compare the energies $E_i$ and couplings $J_{i,j}$ for all molecule indices $i,j$. Scatter plots in Figures \ref{fig:scatterE} and \ref{fig:scatterJ} illustrate these comparisons.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.95\textwidth]{figs/scatterE_all.pdf}
    \caption{Energy heat maps: $X$-axis shows energies of BCP molecules obtained using PBE0, while the $Y$-axis shows energies from a different functional $f'$.}
    \label{fig:scatterE}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.95\textwidth]{figs/scatterJ_all.pdf}
    \caption{Scatter heat maps of $\log_{10}(J^2)$: $X$-axis shows $\log_{10}(J^2)$ of BCP molecules obtained using PBE0, while the $Y$-axis shows $\log_{10}(J^2)$ from a different functional $f'$.}
    \label{fig:scatterJ}
\end{figure}

\textbf{Point 2:} Both $E_i$ and $J_{i,j}$ are distributions. To quantify the impact of these distributions on $\Delta$ToF, we plot the Wasserstein distance versus $\Delta$ToF. Figure \ref{fig:distance_ToF} shows that different functionals generate similar energy sets, but $\Delta$ToF is not correlated with energy distribution distance.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.9\textwidth]{figs/DeltaToF_W_KL_E.pdf}
    \caption{Left: scatter plot of $W_1(P_f,P_{f'})$ vs. $\Delta$ToF. Right: scatter plot of $KL(P_f(E),P_{f'}(E))$ vs. $\Delta$ToF.}
    \label{fig:distance_ToF}
\end{figure}

\textbf{Point 3:} We then examine other rate-related parameter distributions, calculating the Wasserstein distance and plotting against $\Delta$ToF. Figure \ref{fig:d_WD_tof} reveals that only the rate $P_f(\omega)$ has a large Wasserstein distance when varying $f^\text{DFT}$; other parameters show similar distributions.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{figs/DeltaToF_W_all.pdf}
    \caption{Scatter plots of (a): $W_1(P_f(\Delta E),P_{f'}(\Delta E))$, (b): $W_1(P_f(\exp(\Delta E)),P_{f'}(\exp(\Delta E)))$, (c): $W_1(P_f(\exp \frac{-(\Delta E - \lambda)^2}{4 k_B T \lambda}),P_{f'}(\exp \frac{-(\Delta E - \lambda)^2}{4 k_B T \lambda}))$, and (d): $W_1 (P_f(\omega), P_{f'}(\omega) )$ vs. $\Delta$ToF.}
    \label{fig:d_WD_tof}
\end{figure}

\textbf{Point4:} Although $f^\text{DFT}$ affects $P_f(\omega)$, but we further notice that $\Delta$ToF is not correlated to its Wasserstein distance. 
So we hypothesize that the connectivity of the graph changed due to different $f^\text{DFT}$. The connectivity of the graph is quantified by the second eigenvector of the graph Laplacian, so we make the figure to investigate the correlation between the $\Delta$ToF and the graph connectivity. 
Figure .\ref{fig:d_eig_tof} shows the ratio of $f^\text{DFT}$ and the second eigenvalue ratio between the graph Laplacian. These two quantities look correlated, and we calculate the Spearman rank coefficient, which is shown in Table.\ref{tab:spearman}.

\begin{table}[h]
    \centering
    \begin{tabular}{c c c}
    \hline
        Data Set & Spearman Rank Coefficient & $p$-value \\ 
        \hline
        $\frac{\lambda_{2,L_W}(f)}{\lambda_{2,L_W}(f')}$ vs $\frac{\text{ToF}(f)}{\text{ToF}(f')}$ & -0.57 & 4.6e-5 \\
        $\frac{\lambda_{2,L_\text{rw}}(f)}{\lambda_{2,L_\text{rw}}(f')}$ vs $\frac{\text{ToF}(f)}{\text{ToF}(f')}$ & -0.38 & 9.4e-3 \\ 
    \hline
    \end{tabular}
    \caption{Spearman rank coefficients for the relationship between $\frac{\lambda_2(f)}{\lambda_2(f')}$ and $\frac{\text{ToF}(f)}{\text{ToF}(f')}$}
    \label{tab:spearman}
\end{table}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\textwidth]{figs/ratio_tof_2ndEigval.pdf}
    \caption{Scatter plot of $\frac{\lambda_{2}(f)}{\lambda_{2}(f')}$ vs. $\frac{\text{ToF}(f)}{\text{ToF}(f')}$}
    \label{fig:d_eig_tof}
\end{figure}

\textbf{Point5:} The eigenvalue comes in pair with the eigenvector, so we further investigated the corresponding second eigenvector element distributions, as shown in Fig.\ref{fig:2ndVecLW}. 
To our surprise, node 66 has very different second eigenvector entries, so we performed K-means partitioning on those second eigenvector elements.

\textbf{Point6:} After partitioning, we notice that the partition cost function is correlated to $\Delta$ToF.
This correlation shows that the $\Delta$ToF correlated to the connectivity of the graph, althouth the electronic structures and rate-related parameters are similar.

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{figs/fig_2ndVecLw.png}
    \caption{Scatter plot of the eigen vector entries $\Vec{v}_i$ of $L_W$ for various $f$ indicated by the legend and point color. 
    The numbers are node index. The dash rectangular indicates the 3-means clusters that are detected as clusters by the Kmeans Lloyd's algorithm. }
    \label{fig:2ndVecLW}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{figs/fig_2ndVecRW.png}
    \caption{Scatter plot of the eigen vector entries $\Vec{v}_i$ of $L_{rw}$ for various $f$ indicated by the legend and point color. 
    The numbers are node index. The dash rectangular indicates the 3-means clusters that are detected as clusters by the Kmeans Lloyd's algorithm.  }
    \label{fig:2ndVecRW}
\end{figure}

Figure \ref{fig:fig_Z_ToF} shows scatter plots of K-means clustering partition cost $Z_{2c}, Z_{3c}$ versus ToF. For the normal Laplacian $L_w$, $Z_{2c}$ is not correlated with the ToF, but $Z_{3c}$ is. For the Random-walk Laplacian, both $Z_{2c}$ and $Z_{3c}$ show a strong correlation with ToF. Thus, the clustering cost function indicates the speed of charge dynamics as measured by ToF.

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{figs/fig_Z_ToF.pdf}
    \caption{Scatter plot of $Z$ vs $\text{ToF}$. (a): K-means partition of the second eigenvector of $L_W$ for $K=2$ and $K=3$ (b) K-means partition of the second eigenvector of $L_{RW}$ for $K=2$ and $K=3$}
    \label{fig:fig_Z_ToF}
\end{figure}

\textbf{Point7:} Now that the ToF has a large range, we want to know which ToF to trust.  And for application purposes, a very important message is to know what the range of ToF will give a 90\% confidence level.

Since we do not really know the exchange-correlation potential, we assume that for each molecule, the uncertainty in its energy $E_i$ is represented by a normal distribution $E_i \in N(\bar{E_i},\sigma(E_i))$. Normal distribution is used because the normal distribution encodes the maximum amount of uncertainty over the real numbers out of all possible probability distributions with the same variance. 
So the normal distribution inserts the least amount of prior knowledge into our model. 
So we experiment:

\textbf{Point8:} For each molecule energy $E_i$, we use maximum likelihood estimation to obtain the $N(\bar{E_i},\sigma(E_i))$. Then use sample a set of $E_i$ and calculate the ToF, with $\lambda,J_{i,j}$ fixed at the average values. 
Repeat the $E_i$ sampling and ToF calculation for 100000 times, and plot ToF distribution. This process is called the Monte Carlo sampling.

Similarly, for $\lambda,J_{i,j}$, we perform the Monte Carlo sampling as been done for $E_i$. The resulting ToF is shown in Fig.\ref{fig:ToFs}.

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{figs/fig_mle.png}
    \caption{(a)The ToF distribution for 100000 samples where each $E_i$ is drawn from $N(\bar{E}_i,\sigma(E_i))$. The red curve is fitted to a gamma distribution. (b)The ToF distribution for 100000 samples where each $\lambda$ is drawn from $N(\bar{\lambda},\sigma(\lambda))$.(c)The ToF distribution for 100000 samples when each $J_{i,j}$ is drawn from $N(\bar{J_{i,j}},\sigma(J_{i,j}))$.}
    \label{fig:ToFs}
\end{figure}

This figure shows that ToF is more sensitive to change in $E_i$ and least sensitive to $J_{i,j}$, even though from the scatter plots Fig.\ref{fig:scatterJ} the $J_{i,j}$ has a very large magnitude deviation.

The dataset of $\log_{10}(\text{ToF})$ can be well-fitted to a Gamma distribution. 
The statistical calculation has results:
\begin{itemize}
    \item When $E_i \in N(\bar{E_i},\sigma(E_i))$, the $\log_{10}(\text{ToF})$ has mean -1.73 and a standard deviation of 0.73.
    \item When $\lambda \in N(\bar{\lambda},\sigma(\lambda))$, the $\log_{10}(\text{ToF})$ has mean -1.91 and a standard deviation of 0.34.
    \item When $J_{i,j} \in N(\bar{J_{i,j}},\sigma(J_{i,j}))$, the $\log_{10}(\text{ToF})$ has mean -2.92 and a standard deviation of 0.08.
\end{itemize}

When we use $E_i \in N(\bar{E_i},\sigma(E_i))$, $\lambda \in N(\bar{\lambda},\sigma(\lambda))$, $J_{i,j} \in N(\bar{J_{i,j}},\sigma(J_{i,j}))$ at the same to perform the Monte Carlo sampling of ToF calculation, the ToF is shown in Fig.\ref{fig:ToFs2}. the $\log_{10}(\text{ToF})$ has mean -2.72 and a standard deviation of 0.80. To obtain a 90\% confidence level, then $-3.93 < \log_{10}(\text{ToF}) < -1.30$.
\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth]{figs/fig_mle2.png}
    \caption{The ToF distribution for 100000 samples where each $E_i$ is drawn from $N(\bar{E}_i,\sigma(E_i))$, $\lambda$ is drawn from $N(\bar{\lambda},\sigma(\lambda))$, and each $J_{i,j}$ is drawn from $N(\bar{J_{i,j}},\sigma(J_{i,j}))$. The red curve is fitted to a gamma distribution.}
    \label{fig:ToFs2}
\end{figure}

%\bibliographystyle{unsrt}
%\bibliography{references}

\end{document}

### 2024-06-25 pater_uncertain.tex
UQ repo

\documentclass[letterpaper,12pt]{article}
\usepackage{tabularx} % extra features for tabular environment
\usepackage{amsmath}  % improve math presentation
\usepackage{amsfonts}
\usepackage{verbatim}
\usepackage{graphicx} % takes care of graphic including machinery
\usepackage[margin=1in,letterpaper]{geometry} % decreases margins
\usepackage{cite} % takes care of citations
\usepackage[final]{hyperref} % adds hyper links inside the generated pdf file
\hypersetup{
	colorlinks=true,       % false: boxed links; true: colored links
	linkcolor=blue,        % color of internal links
	citecolor=blue,        % color of links to bibliography
	filecolor=magenta,     % color of file links
	urlcolor=blue         
}
\usepackage{blindtext}

\usepackage{units}
%++++++++++++++++++++++++++++++++++++++++

\begin{document}

\title{Uncertain Effects of DFT Functionals on Charge Mobility Calculations}
\author{authors}
\date{\today}
\maketitle

\begin{abstract}
    We study the uncertainty effect from the DFT functional to the charge mobility calculations of organic semiconductors (OSC). 
    The charge mobilities of the BCP and MADN devices are calculated from the first principle multiscale model. Using a total of 10 different DFT functionals, we find that the electronic structure properties have similar distributions as indicated by Wasserstein distance, while the charge mobility of the BHANDHLYP functional has a large deviation. 
    Further investigation reveals that the BHANDHLYP functional leads to a trap site, and the charge mobility is very sensitive to the trap sites' energy, so a small change in the site's energy results in a large deviation of ToF.

    We further investigate the uncertainty effect of electronic structure properties on the charge mobility 
    We find that the site energy has the most significant effect on the charge mobility and a confidence level of charge mobility is obtained encoding the maximum amount of uncertainty in electronic structure parameters. 
\end{abstract}

\section{Introduction}
Charge mobility is one of the key quantities of interest for OSC.

Charge conductance is due to electron dynamics, so quantum mechanics and Schr\"odinger equation are essential for the theoretical study of charge mobility.

Due to the complexity of Schr\"odinger Equation, one alternative theory is the density functional theory (DFT). DFT has two challenges. Firstly, it is computationally impossible to perform electronic structure calculations for the whole OSC device. And secondly, the exchange-correlation potential in DFT has an unknown formula.

The first challenge is overcome by approximating the electron dynamics as transition processes between the localized states, with the transition rates calculated as the temperature-activated bi-molecule transition rates, known as the Marcus rate. 
The second challenge is addressed by utilizing DFT functionals to represent the exchange-correlation potential. 
Those functionals are benchmarked to achieve good consistency with many physical quantities, such as ionization potential, and density of states.

The influence of the different functionals on ToF calculation is missing.

\section{Results}
\label{sec:result}
The list of figures:
\begin{itemize}
    \item Heat map of $E(f)$ versus $E(f=PBE0)$. This figure visually shows how energy are affected by different functionals and we can learn which sites have large different energies.
    \item Heat map of $J_{i,j}(f)$ versus $J_{i,j}(f=PBE0)$. This figure visually shows how $J_{i,j}$ are affected by different functionals and we can learn the pairs having very different $J_{i,j}$.
    \item Scatter plot of $\Delta \text{ToF}$ versus Wasserstein distance $W_1 (P_f(E),P_{f'}(E))$, and $\Delta \text{ToF}$ versus $\text{KL}(P_f(E),P_{f'}(E))$. This figure shows the change of $\text{ToF}$ as a result of different energy distributions measured by two commonly used metrics. We can learn that $\Delta \text{ToF}$ can be very large even though the two distributions are close.
    \item Scatter plot of standard graph Laplacian matrix 2nd eigenvalue ratio $\frac{\lambda_{2}}{\lambda'_{2}}$ versus ToF ratio $\frac{\text{ToF}_f}{\text{ToF}_{f'}}$. We can learn that $\frac{\lambda_{2}}{\lambda'_{2}}$ is correlated with the change of ToF, and $\lambda_{2}$ is a metric indicating the change of ToF due to the functionals. 
    \item Distribution (Scatter) of 2nd eigenvector entries for specific functionals. This plot tells how the entries are distributed in one-dimensional space, and if any clusters are formed.
    we can learn that in all functionals, some nodes (such as node66) have very different eigenvector entries than others, indicating that those nodes can be partitioned into clusters.
    \item Scatter plot of K-means clustering partition cost $Z_{2c},Z_{3c}$ versus ToF. This plot tells us that in the case of $Z_{3c}$, large ToF corresponds to small $Z_{3c}$, indicating the large ToF system can be partitioned into three clusters with a small cost. 
    \item Scatter plot show $Z_{2c}$ versus $E_{t}$, and $Z_{2c}$ versus ToF when varying the $E_{t}$ to introduce trap. We can learn that When $E_{t}$ is small, there is a log-linear relationship between $Z_{2c}$ and $E_{t}$, ToF. But when $E_{t}$ is large, both $Z_{2c}$ and ToF remain unchanged. This suggests that when $E_{t}$ is large, the node (node66) is not visited in the random walk and does not contribute to the ToF.
    \item Using symmetrized adjacency matrix $W := \frac{1}{2}(W+W^T)$, scatter plot showing $Z_{2c}$ versus $E_{66}$, and $Z_{2c}$ versus ToF is made. In $Z_{2c}$-$E_{66}$ plot we learn that both large and small $E_{66}$ give small $Z_{2c}$, meaning that this symmetrized graph is able to identify trap nodes and nodes that are rarely visited (anti-trap).
\end{itemize}

\subsection{Distribution Distance and  $\Delta$ToF}
\begin{table}[h]
    \centering
    \begin{tabular}{c c c c c }
    \hline
        functional & scaleHFX & $\lambda_h$ [eV]   & ToF [s]  & $\sigma(E)$ \\ 
        \hline
        PBE0 & 0.25 & 0.388 & 1.23e-3  & 0.175 \\
        PBE & 0 & 0.303  & 1.04e-3  & 0.172 \\ 
        B3LYP & 0.20 & 0.375  & 4.28e-3  & 0.175 \\
        BHANDHLYP & 0.5 & 0.494  &\textbf{737.94}  & 0.192 \\
        TPSS & 0 & 0.310  &1.37e-2 &  0.168 \\
        BP86 & 0 & 0.304  & 7.46e-3 & 0.175 \\
        wB97X & 0.157 & 0.505 & 2.92e-2  & 0.191 \\
        wB97X-D3 & 0.195 & 0.496 & 4.89e-2  & 0.180 \\
        M06L & 0 & 0.312 & 3.19e-1  & 0.165 \\
        BHLYP & 0.5 & 0.493 &  2.47 & 0.192 \\
    \hline
    \end{tabular}
    \caption{ The values of $\lambda_h$, ToF, Stationary state velocity and energy standard deviation of BCP molecules calculated from different functionals. }
    \label{tab:para}
\end{table}
\begin{table}[h]
    \centering
    \begin{tabular}{c c c  }
    \hline
        functional & ToF[s] & $\mu$ [m/s]   \\ 
        \hline
        PBE0 & 2.39e-8 & 5.68e-5 \\
        PBE & 6.03e-9 & 2.25e-4  \\ 
        B3LYP & 1.67e-8 & 8.13e-5 \\
        BHANDHLYP & 3.36e-4 & 4.04e-9   \\
        TPSS & 1.23e-8 & 1.10e-4   \\
        BP86 & 3.77e-7 & 3.59e-6   \\
        wB97X & 1.68e-6 & 8.08e-7  \\
        wB97X-D3 & 6.92e-7 & 1.96e-6  \\
        M06L & 3.90e-3 & 3.47e-10  \\
    \hline
    \end{tabular}
    \caption{ Mobility and ToF with drift electric field $6e7$ V/m. }
    \label{tab:para2}
\end{table}

\begin{figure}
    \centering
    \includegraphics[width=0.95\textwidth]{figs/scatterE_all.pdf}
    \caption{Energy heat maps. $X$-axis the is energy of BCP molecules obtained using $f$=PEB0, the $Y$-axis is the energy from a different functional $f'$ than PBE0.}
    \label{fig:scatterE}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.95\textwidth]{figs/scatterJ_all.pdf}
    \caption{$\log_{10}(J^2)$ scatter heat maps where $X$-axis the is $\log_{10}(J^2)$ of BCP molecules obtained using $f$=PEB0, the $Y$-axis is the $\log_{10}(J^2)$ from a different functional $f'$ than PBE0.}
    \label{fig:scatterJ}
\end{figure}

First-principle multiscale model for ToF study begins with a set of molecules (molecular structures) and DFT functionals, which characterize the ground state electronic structure of molecules, then a graph is defined, and finally, a ToF is calculated.

In this multiscale model, the molecular structure is kept fixed while different choices of DFT functionals are made. Using those functionals similar distributions of parameters $E_i,J_{ij}$ are obtained. 
Compared with those parameter distributions, the ToF shows a large difference, especially for $f^\text{BHANDHLYP}$ which gives ToF $\sim 700$ (the level of insulator).

Table \ref{tab:para} summarizes statistical properties: the name of exchange-correlation functionals for DFT calculation, the magnitude of the Hartree-Fock exchange energy (scaleHFX), reorganization energy ($\lambda_h$), time-of-flight (ToF), and energy disorder ($\sigma(E)$) for various functionals. Drift ToF and mobility at an electric field of $6 \times 10^7$ V/m are presented in Table \ref{tab:para2}.

As is shown in Table \ref{tab:para}, the energy disorders $\sigma_E$ are in a small range from 0.165 to 0.192 eV.

Scatter plots comparing the site energies ($E_i$) and coupling elements ($J_{i,j}$) of PBE0 functional ($f$=PBE0) with of other functionals ($f'$) are displayed in Figs.\ref{fig:scatterE} and \ref{fig:scatterJ}  respectively.
Figure \ref{fig:scatterE} shows almost all energies obtained from $f=\text{PBE0}$ are very close to energies from other functionals. 
Although a few points stay some distance away from the diagonal, the majority of the scatter points lie on the diagonal line indicating similarity between $E(f^\text{DET})$ for $f^\text{DET} \neq \text{PBE0}$ and $E(\text{PBE0})$.

To further confirm this observation and understand the effect of parameter difference such as energy $\{ E_i \}$ in ToF, the Wasserstein distance ($W_1$) and Kullback-Leibler divergence $KL(P_f(E),P_{f'}(E))$ between two any two energy distributions $w_1(P_f(E),P_{f'}(E))$ are calculated, and plotted against the different in ToF $\Delta $ToF. 
The results are shown in Fig. \ref{fig:distance_ToF}. 
Notably, $W_1(P_f(E),P_{f'}(E))$ and $KL(P_f(E),P_{f'}(E))$ exhibit small variations, contrasting with the large changes observed in $\Delta \text{ToF}$.

Specifically, those figure shows that $W_1(P_f(E),P_{f'}(E))$ and $KL(P_f(E),P_{f'}(E))$ are in a small range, but $\Delta \text{ToF}$ can change significantly. This means $P_f(E)$ does not change a lot with different functionals but the resulting $\Delta \text{ToF}$ change significantly.

Furthermore, the Wasserstein distances of other distributions (such as $P(\Delta E), P(e^{\Delta E})$ shown in Appendix Fig.\ref{fig:distance_ToF}) are not correlated to $\Delta$ToF.

In conclusion, the distribution distance between the parameters themselves can not explain the $\Delta \text{ToF}$.

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{figs/DeltaToF_W_KL_E.pdf}
    \caption{Left: scatter plot of $W_1(P_f,P_{f'})$ vs. $\Delta \text{ToF}$. 
    Right: scatter plot of  $KL(P_f(E),P_{f'}(E))$ vs. $\Delta \text{ToF}$. }
    \label{fig:distance_ToF}
\end{figure}

\subsection{Spectral Clustering}
The Wasserstein distance metric was found to be ineffective for measuring differences between graph properties. In spectral clustering theory, the second eigenvalue indicates a graph's ability to be partitioned into two clusters. Mapping the graph into a vector $\vec{x} \in \mathbb{R}^n$ with $||\vec{x}||_1=0$ allows partitioning such that nodes in different clusters are maximally separated. This second eigenvalue metric measures the minimum distance between the two most separated clusters, as shown in Equations \ref{eq:min2} and \ref{eq:min3}.

Figure \ref{fig:d_eig_tof} plots $\frac{\text{ToF}(f)}{\text{ToF}(f')}$ against $\frac{\lambda_2(f)}{\lambda_2(f')}$, showing a strong correlation as indicated by the Spearman rank coefficient.
\begin{table}[h]
    \centering
    \begin{tabular}{c c c  }
    \hline
        data set & Spearman rank coefficient & $p$-value   \\ 
        \hline
        $\frac{\lambda_{2,L_W}(f)}{\lambda_{2,L_W}(f')}$ vs $\frac{\text{ToF}(f)}{\text{ToF}(f')}$,  & -0.57 & 4.6e-5 \\
        $\frac{\lambda_{2,L_\text{rw}}(f)}{\lambda_{2,L_\text{rw}}(f')}$ vs $\frac{\text{ToF}(f)}{\text{ToF}(f')}$ & -0.38 & 9.4e-3  \\ 
    \hline
    \end{tabular}
    \caption{ Spearman rank coefficient of relationship between $\frac{\lambda_2(f)}{\lambda_2(f')}$ and  $\frac{\text{ToF}(f)}{\text{ToF}(f')}$}
    \label{tab:spearman}
\end{table}

\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth]{figs/ratio_tof_2ndEigval.pdf}
    \caption{Scatter plot of $\frac{\lambda_{2}(f)}{\lambda_{2}(f')}$ vs. $\frac{\text{ToF}(f)}{\text{ToF}(f')}$. The type of the Laplacian matrixes is indicated by the legend.}
    \label{fig:d_eig_tof}
\end{figure}

When the graph $G$ is mapped to the space of the second eigenvalue of $L_w$, $\vec{v}_2$,
The equality is obtained in Eqn.\ref{eq:min2}. So the entries of this vector can be used to partition the graph into clusters. The distribution of $\vec{v}_2$ entries are displayed in Fig.\ref{fig:2ndVecLW} and \ref{fig:2ndVecRW}.

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{figs/fig_2ndVecLw.png}
    \caption{Scatter plot of the eigen vector entries $\Vec{v}_i$ of $L_W$ for various $f$ indicated by the legend and point color. 
    The numbers are node index. The dash rectangular indicates the 3-means clusters that are detected as clusters by the Kmeans Lloyd's algorithm. }
    \label{fig:2ndVecLW}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{figs/fig_2ndVecRW.png}
    \caption{Scatter plot of the eigen vector entries $\Vec{v}_i$ of $L_{rw}$ for various $f$ indicated by the legend and point color. 
    The numbers are node index. The dash rectangular indicates the 3-means clusters that are detected as clusters by the Kmeans Lloyd's algorithm.  }
    \label{fig:2ndVecRW}
\end{figure}

From Figs. \ref{fig:2ndVecLW} and \ref{fig:2ndVecRW}, certain nodes, such as node 66, are isolated from most of the graph. The distributions of the second eigenvector entries reveal that a few points are separated from the rest. For example, both figures show that node 66 is often partitioned as a cluster where the CTMC spends significant time compared to other nodes. Since those distributions show similar structure, we need to have an indicator to find out which nodes slow the dynamics.

Recalling that the second eigenvalue is a metric derived from graph partitioning while the second eigenvector contains the entries, we further find that the cost function $Z$ from K-means clustering is correlated with the ToF. Scatter plots of $Z$ and ToF are shown in Fig. \ref{fig:fig_Z_ToF}. K-means clustering requires the number of clusters as input, determined using the kernel density estimation (KDE) method described in the Appendix.

Figure \ref{fig:fig_Z_ToF} shows scatter plots of K-means clustering partition cost $Z_{2c}, Z_{3c}$ versus ToF. For the normal Laplacian $L_w$, $Z_{2c}$ is not correlated with the ToF, but $Z_{3c}$ is. For the Random-walk Laplacian, both $Z_{2c}$ and $Z_{3c}$ show a strong correlation with ToF. Thus, the clustering cost function indicates the speed of charge dynamics as measured by ToF.

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{figs/fig_Z_ToF.pdf}
    \caption{Scatter plot of $Z$ vs $\text{ToF}$. (a): K-means partition of the second eigenvector of $L_W$ for $K=2$ and $K=3$ (b) K-means partition of the second eigenvector of $L_{RW}$ for $K=2$ and $K=3$}
    \label{fig:fig_Z_ToF}
\end{figure}

\subsection{Trap energy effect and cost function}
As shown in Figs. \ref{fig:2ndVecRW} and \ref{fig:fig_Z_ToF}, $Z$ can identify nodes/molecules (traps) that cause large ToF. However, we need to clarify how a single trap energy $E_t$ affects $Z$ before using $Z$ to identify traps. Specifically, we need to determine the sensitivity of $Z$ to the trap energy $E_t$ and ToF, and the functional form of $Z(E_t)$.

To investigate the effect of trap energy on $Z$, we vary $E_t$ in the PBE functional system over a range from small to large values: $[-2.0, -0.3]$. Node 66 is chosen as the trap. We then calculate the ToF and $Z$ from 2-means clustering with $L_{rw}$.

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{figs/fig_E_ToF_Z_nonsym.pdf}
    \caption{Scatter plot of $E_t$ vs $Z$, and ToF vs $Z$ for the BCP system with PBE functionals.}
    \label{fig:fig_E_ToF_Z2_Lrw}
\end{figure}

Figure \ref{fig:fig_E_ToF_Z2_Lrw} shows a linear relationship between $E_t$ and $\log_{10} Z$ when $E_t < -1.6$. As $E_t$ increases, node 66 is no longer identified as a cluster because it is rarely visited in the CTMC. When $E_t$ is very large, both the out-going and in-going rates are small, but the in-going rate is much smaller. The ToF vs. $\log_{10} Z$ plot shows that ToF remains unchanged as $E_t$ continues to increase.

Thus, spectral clustering using $\vec{v}_2$ of $L_{rw}$ can identify traps in the system but cannot detect nodes that are rarely visited (anti-traps).

To identify anti-trap nodes using spectral clustering, we symmetrize the adjacency matrix:
\begin{equation}
    W := \frac{1}{2}(W + W^T)
\end{equation}
and use the second eigenvector $\vec{v}_2$ of $L_\text{sym} = \text{diag}(W) - W$, where $\text{diag}(W)$ is the out-degree matrix of $W$. We then calculate the cost function $Z$.

The relationship between the cost function from $L_\text{sym}$ and $E_t$ is shown in Fig.\ref{fig:fig_E_ToF_Z2_1}.

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{figs/fig_E_ToF_Z_sym.pdf}
    \caption{Scatter plot of $E_{66}$ vs $Z$, and ToF vs $Z$ for the BCP system with PBE functionals. The cost function $Z$ is calculated from 2-means clustering on the $\vec{v}_2$ of $L_\text{sym}$.}
    \label{fig:fig_E_ToF_Z2_1}
\end{figure}

When $E_t$ is very small ($<-2$), node 66 is identified as a separate cluster, and $Z$ decreases as $E_t$ decreases, while ToF increases.

For $-0.5 > E_t > -2.0$, $Z$ remains relatively stable since other nodes can be identified as a second cluster. When $E_t > -0.4$, node 66 is again identified as a cluster, and $Z$ decreases as $E_t$ increases. However, ToF remains unchanged because a high $E_t$ results in the node being rarely visited.
Partitioning $\vec{v}_2$ of $L_\text{sym}$ when $E_t$ is not too low will not identify node 66 as a trap cluster, unlike $\vec{v}_2$ of $L_{rw}$ or $L_{W}$, as seen in the BHANDHLYP functional BCP system. This is because the in-going rate from neighbors to node 66 is not small compared to other rates, although the out-going rate is small. Using $L_\text{sym}$ averages the edge weights, making $W_{66,i}$ larger. Therefore, $\vec{v}_2$ of $L_\text{sym}$ will not identify node 66 as a separate cluster in the BHANDHLYP system.

In conclusion, $\vec{v}_2$ of $L_\text{sym}$ can identify both traps and anti-traps only when both in-going and out-going rates are small compared to all rates.

\section{Conclusion}
\label{sec:con}

In this study, we investigated the influence of various functionals on the electronic properties and time-of-flight in charge transport systems. Our multiscale model demonstrated that different exchange-correlation functionals can significantly impact ToF although the electronic parameters such as the reorganization energy, energy disorder, and mobility do not change significantly.
Through extensive analysis, including scatter plots and clustering, we identified that certain nodes exhibit distinct behaviors, forming clusters that correlate with ToF variations.

Key findings include the identification of a log-linear relationship between clustering partition cost and ToF under varying conditions, particularly highlighting role of the trap energy $E_t$ effect. 
Additionally, the use of the random walk Laplacian matrix and symmetrized Laplacian matrix allowed us to identify both trap and anti-trap nodes effectively depending on $E_t$ scale, correlating well with partition cost metrics.

In summary, this study provides a comprehensive analysis of how electronic properties influence charge transport, offering valuable insights for future research in optimizing functional selection for accurate ToF predictions in electronic systems.

\section{Appendix}
\label{sec:stat}
To investigate the distribution of parameters and quantity of interest, correlation functions and distribution distance need to be used.

\subsection{Correlation Coefficient}
The Spearman rank correlation coefficient, denoted as $\rho$, a statistical measure of the strength and direction of association between two ranked variables, is used to quantify the correlation between two sets of variables:
\begin{equation}
\rho = 1 - \frac{6 \sum d_i^2}{n(n^2 - 1)}    
\end{equation}
where $d_i$ is the difference between the ranks of corresponding pairs of observations, and
$n$ is the number of observations.

A value of 1 indicates a perfect positive monotonic relationship, where high ranks of one variable are consistently associated with high ranks of the other, and vice versa.
A value of -1 indicates a perfect negative monotonic relationship, where high ranks of one variable are associated with low ranks of the other, and vice versa.
A value of 0 suggests no monotonic relationship between the variables.

Spearman's $\rho$ is used because it makes fewer assumptions about the underlying distribution of the data compared to Pearson's correlation coefficient. It does not assume that there is a linear relationship between variables. 
It measures the strength of monotonic relationships between variables, meaning it captures whether variables tend to increase or decrease together, even if the relationship is not strictly linear. This makes it particularly useful when assessing associations in data where the relationship may be nonlinear or when the variables have a consistent direction of change but not necessarily a linear one.

\subsection{Distance between Two Distributions}
Let $P_1$,$P_2$ be two distributions with probability density $p_1,p_2$. 
There are many ways to define a distance between P and Q such as:
Total variation: $\frac{1}{2}\int |p_1 - p_2|$, $L_2$ distance $\int |p_1 - p_2|^2$, Hellinger: $\sqrt{\int (\sqrt{p_1}-\sqrt{p_2})^2}$, Kullback-Leibler Divergence\cite{csiszar_divergence_1975} and Wasserstein distance\cite{villani_optimal_2009}.

For a $S \in \mathcal{S}$, the vector $\Vec{E}_f$ can be seen as a collection of $N$ random variables, its empirical cumulative distribution function can be written as:
$P_f(E) = \frac{1}{N} \sum\limits_{i=1}^N U(E-E_i)$ where $U(x)$ is the unit-step function with $U(0) = 0.5$.

We choose to use Kullback-Leibler (KL) divergence and Wasserstein distance instead of Total variation, $L_2$ distance and Hellinger 
because these distances ignore the underlying geometry of the space, and they can not be used to compare $P_1$ and $P_2$ when one is discrete and the other is continuous.

The KL Divergence quantifies how difficult it is to discriminate between two populations with the best test\cite{csiszar_divergence_1975}, its estimator is given by\cite{noauthor_2008_2008}:
\begin{equation}
    \Hat{D}(P_f||P_{f'}) = \frac{1}{N} \sum\limits_{i=1}^N \log \frac{\delta P_f(E_i)}{\delta P_{f'}(E_i)}
\end{equation}
where $\delta P_f(E_i) = P_f(E_i) - P_f(E_i - \epsilon) $ for any $\epsilon < \min_i \{ E_i - E_{i-1} \}$.

The Wasserstein distance for two empirical distributions $P$ of dataset $X_1,\cdots,X_n$ and $Q$ of dataset $Y_1, Y_2,\cdots, Y_n$ can be computed using:
\begin{equation}
    W_p (P,Q) = (\sum_i || X_i - Y_i ||^p )^{\frac{1}{p}}
\end{equation}
If the dimension of the dataset $d>1$,  then
\begin{equation}
    W_p (P,Q) = \inf_{\pi} (\sum_i || X_i - Y_i ||^p )^{\frac{1}{p}}
\end{equation}
where the infimum is over all permutations $\pi$.

There are differences between Wasserstein distance and KL Divergence.
Wasserstein distance defines a metric on the space of probability distributions, meaning it satisfies properties like non-negativity, symmetry, and the triangle inequality. This makes it useful for clustering, classification, and optimization problems where a notion of distance or similarity between distributions is required. KL divergence, on the other hand, is not a metric as it lacks symmetry and the triangle inequality.
Wasserstein distance tends to be more stable under small perturbations in the distributions compared to KL divergence. This can be advantageous in situations where the data is noisy or uncertain. For completeness, we use both Wasserstein distance and KL divergence to measure the distribution distance.

\subsection{KDE Method of Finding Cluster Number}
For 1D clustering problem kernel density estimation (KDE) is often used to find the number of clusters that correspond to peaks of eigenvector elements. 
Let $(x_1, x_2, \cdots, x_n)$ be independent and identically distributed samples drawn from some univariate distribution with an unknown density $f$ at any given point $x$.
The kernel density estimator is:
\begin{equation}
    \hat{f}_h(x) = \frac{1}{nh} \sum\limits_{i=1}^n K(\frac{x-x_i}{h})
\end{equation}
Where $K(x) = \frac{1}{\sqrt{2\pi} } e^{-\frac{1}{2}x^2}$ is the kernal and here the standard normal density function is used, $h$ is a smoothing parameter which influences the smoothness and accuracy of the estimated density. An optimal choice\cite{silverman_density_1998} is $h=(\frac{4 \sigma^5}{3n})^{1/5}$ where $\sigma$ is the sample standard deviation and $n$ the sample size.

The kernel density estimator plot is shown in Fig.\ref{fig:kde}. This figure shows that, in the systems where two-cluster partitions have a large $Z$ cost function, it can be further subdivided into smaller clusters.

The peaks correspond to the scatter groups in Fig.\ref{fig:d_eig_tof3}.

\begin{figure}
    \centering
    \includegraphics[width=1.0\textwidth]{figs/kde.png}
    \caption{$\hat{f}_h(x)$ as a function of $x$ with $h=1e-5$. In each plot Y-axis represents $\hat{f}_h(x)$ and X-axis represents $x$. The legend indicates the functionals.}
    \label{fig:kde}
\end{figure}

\subsection{Other Parameter Difference and ToF Difference}
\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{figs/DeltaToF_W_all.pdf}
    \caption{Scatter plot of (a): $W_1(P_f(\Delta E),P_{f'}(\Delta E))$, (b): $W_1(P_f(\exp(\Delta E)),P_{f'}(\exp(\Delta E)))$, (c): $W_1(P_f(\exp \frac{-(\Delta E - \lambda)^2}{4 k_B T \lambda}),P_{f'}(\exp \frac{-(\Delta E - \lambda)^2}{4 k_B T \lambda}))$ and (d): $W_1 (P_f(\omega), P_{f'}(\omega) )$ vs. $\Delta \text{ToF}$.   }
    \label{fig:d_WD_tof}
\end{figure}
Fig. \ref{fig:d_WD_tof} explores $\Delta \text{ToF}$ relative to properties derived from the energy distribution ($\Delta E$) and related transformations, revealing that while the Wasserstein distance remains stable across different functionals, $\Delta \text{ToF}$ varies notably.

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{figs/cdf_w_log.pdf}
    \caption{Empirical distribution of Marcus rates in the seven systems whose function is indicated by the legend. Left: no log scale, right: with log scale}
    \label{fig:cdf_w}
\end{figure}
Fig. \ref{fig:cdf_w} depicts the empirical cumulative distribution function of Marcus rates calculated with different functionals, to find the correlation of $\omega$ with ToF, particularly noting the distinct behavior of the BP86 functional although its ToF is close to that of PBE0. 
So the correlation between $P_f(\omega)$ and ToF is not obvious, and it is delusive to tell how the ToF is correlated to the parameters $E,J_{i,j}$ and $\omega$.

In summary, these findings indicates the nuanced relationship between electronic properties ($E_i$, $J_{i,j}$, $\lambda_{i,j}$) and $\omega$, and eventually the ToF in  charge transport systems.

\bibliographystyle{unsrt}
\bibliography{references}

\end{document}

### 2024-06-25 figs/2CC-RW-TOF.py

@@ -1,0 +1,755 @@
+#!/usr/bin/env python
+# coding: utf-8
+
+#!/usr/bin/env python
+import numpy as np
+import argparse
+import glob, os
+import sqlite3
+import inspect
+
+import math
+
+import scipy as sp
+import matplotlib.pyplot as plt
+
+from scipy.sparse import lil_matrix
+from scipy.sparse.linalg import *
+
+import scipy.sparse
+import networkx as nx
+
+from functools import partial
+import itertools
+from itertools import repeat
+import  multiprocessing 
+
+from datetime import datetime
+
+import os.path
+
+ 
+ 
+
+k_B = 8.617333 * 10**(-5) # ev/K
+pi = math.pi
+hbar = 6.582119569 * 1e-16 # eV*s
+
+
+def report(xk):
+    frame = inspect.currentframe().f_back
+    if frame.f_locals['iter_']%100 == 0:
+        print("    ---INFO SOLVER, iteration:", frame.f_locals['iter_'], "residual:", frame.f_locals['resid'])
+
+#rate Matrix calculator
+def calculate_1c_ratematrix(J2, E1, lam, n_sites, seg1, seg2, drX, drY, drZ, efield):
+
+    W1 = np.zeros((int(n_sites),int(n_sites)))
+
+    fieldVector = [efield,0,0] # field in x direction
+            
+    for i in range(len(seg1)):
+        if seg1[i] < seg2[i]:
+            # marcus rate seg2[i] -> seg1[i]
+            dE_field = 1E-9*(fieldVector[0]*drX[i] + fieldVector[1]*drY[i] + fieldVector[2]*drZ[i])
+            dE = dE_field  +  (E1[seg2[i]]-E1[seg1[i]])
+            W1[seg2[i],seg1[i]] = Marcus(dE, J2[i], lam)
+            W1[seg1[i],seg2[i]] = Marcus(-dE, J2[i], lam)
+
+    return W1
+
+# marcus rate
+def Marcus(dE,Jsq,re):
+    temp = 2*pi/hbar * Jsq/math.sqrt(4*pi*(re*k_B*T))*math.exp(-(dE-re)**2/(4*re*k_B*T) )
+    return temp
+
+
+def parse_SQL(statefile):
+
+    con = sqlite3.connect(statefile)
+    c=con.cursor()
+    id = []
+    posX = []
+    posY = []
+    posZ = []
+    eCation = []
+    sql = "SELECT id, posX, posY, posZ, eCation FROM segments"
+
[…]

### 2024-06-25 figs/KDE.py

@@ -1,0 +1,48 @@
+from sklearn.cluster import KMeans
+from sklearn.neighbors import RadiusNeighborsClassifier
+import numpy as np
+import math
+import matplotlib.pyplot as plt
+
+N = 1000
+
+def kde(data):
+    h = 1e-5
+    input = np.arange(-2,2,0.002)
+    kde_result = []
+    for i in range(2000):
+        temp = 0
+        for j in range(data.shape[0]):
+            temp += 1/ (h * np.sqrt(2 * math.pi)) * np.exp(-(input[i] - data[j])**2/(2*h))
+        kde_result.append(temp/N)
+    return input, kde_result
+
+fig,ax = plt.subplots(2,3,figsize=(15,10))
+x,y = kde(np.loadtxt("PBE0/eigenvec1.txt"))
+ax[0][0].plot(x,y,label="PBE0",color="black",linewidth=3.0)
+ax[0][0].set_yscale("log")
+x,y = kde(np.loadtxt("PBE/eigenvec1.txt"))
+ax[0][1].plot(x,y,label="PBE",color="black",linewidth=3.0)
+ax[0][1].set_yscale("log")
+x,y = kde(np.loadtxt("B3LYP/eigenvec1.txt"))
+ax[0][2].plot(x,y,label="B3LYP",color="black",linewidth=3.0)
+ax[0][2].set_yscale("log")
+x,y = kde(np.loadtxt("BHANDHLYP/eigenvec1.txt"))
+ax[1][0].plot(x,y,label="BH",color="black",linewidth=3.0)
+ax[1][0].set_yscale("log")
+x,y = kde(np.loadtxt("TPSS/eigenvec1.txt"))
+ax[1][1].plot(x,y,label="TPSS",color="black",linewidth=3.0)
+ax[1][1].set_yscale("log")
+x,y = kde(np.loadtxt("BP86/eigenvec1.txt"))
+ax[1][2].plot(x,y,label="BP86",color="black",linewidth=3.0)
+ax[1][2].set_yscale("log")
+for i in range(2):
+    for j in range(3):
+        ax[i][j].set_yscale("log")
+        ax[i][j].legend(frameon=False,fontsize=14)
+        ax[i][j].set_xlabel(r"$x$",fontsize=16)
+        ax[i][j].set_ylabel(r"$\hat{f}(x)$",fontsize=16)
+        ax[i][j].tick_params(axis='both', which='major', labelsize=14)
+
+plt.tight_layout()
+plt.savefig("kde.png",dpi=300)

### 2024-06-25 figs/PBE/metric3.py

@@ -1,0 +1,255 @@
+import math
+k_B = 8.617333 * 10**(-5) # ev/K
+pi = math.pi
+hbar = 6.582119569 * 1e-16 # eV*s
+###### import packages ####################################
+import os
+import xml.etree.ElementTree as ET
+
+import numpy as np
+import argparse
+import glob, os
+import sqlite3
+import inspect
+
+import math
+
+import scipy as sp
+import matplotlib.pyplot as plt
+
+from scipy.sparse import lil_matrix
+from scipy.sparse.linalg import *
+
+import scipy.sparse
+import networkx as nx
+
+from functools import partial
+import itertools
+from itertools import repeat
+import  multiprocessing 
+
+from datetime import datetime
+
+import os.path
+import os.path
+from sklearn.cluster import KMeans
+from sklearn.neighbors import RadiusNeighborsClassifier
+
+############ need to change re
+re = 0.155563575 + 0.147270720
+N = 1000
+
+def report(xk):
+    frame = inspect.currentframe().f_back
+    if frame.f_locals['iter_']%100 == 0:
+        print("    ---INFO SOLVER, iteration:", frame.f_locals['iter_'], "residual:", frame.f_locals['resid'])
+
+def Marcus(E,J,re):
+    temp = 2*pi/hbar * J**2/math.sqrt(4*pi*(re*k_B*300))*math.exp(-(E-re)**2/(4*re*k_B*300) )
+    return temp
+
+def setup_1c_system(W1, sink_region):
+    # determine the two carrier state matrix in sparse from with the help of graph methods in networkx
+    n1 = W1.shape[0]
+    G = nx.from_numpy_array(W1, create_using=nx.DiGraph())
+
+    outflowrate = W1.sum(axis=0)
+    print("    ---INFO", datetime.now().strftime("%H:%M:%S"), "outflow rate vector" )
+
+    normalized_rate = W1 @ np.diag(np.reciprocal(outflowrate))
+    # set sink parts to zero
+    for sink in sink_region:
+        normalized_rate[:,sink] = 0.0
+
+    probability = np.identity(n1) - normalized_rate.T
+    print("    ---INFO", datetime.now().strftime("%H:%M:%S"), "probability matrix" )
+
[…]

### 2024-06-25 figs/kmeansRW.py

@@ -1,0 +1,104 @@
+from sklearn.cluster import KMeans
+from sklearn.neighbors import RadiusNeighborsClassifier
+import numpy as np
+import math
+import matplotlib.pyplot as plt
+
+N = 1000
+
+x1 = np.loadtxt("PBE0/eigenvec1RW.txt")
+x2 = np.loadtxt("PBE/eigenvec1RW.txt")
+x3 = np.loadtxt("B3LYP/eigenvec1RW.txt")
+x4 = np.loadtxt("BHANDHLYP/eigenvec1RW.txt")
+x5 = np.loadtxt("TPSS/eigenvec1RW.txt")
+x6 = np.loadtxt("BP86/eigenvec1RW.txt")
+x7 = np.loadtxt("wB97X/eigenvec1RW.txt")
+x8 = np.loadtxt("wB97X-D3/eigenvec1RW.txt")
+x9 = np.loadtxt("M06L/eigenvec1RW.txt")
+x10 = np.loadtxt("BHLYP/eigenvec1RW.txt")
+ToF = [1.23e-3,1.04e-3,4.28e-3,737.94,1.37e-2,7.46e-3,2.92e-2,0.0489,0.319,2.47]
+
+dict_eigVec = {1:x1,2:x2,3:x3,4:x4,5:x5,6:x6,7:x7,8:x8,9:x9,10:x10}
+dict_func = {1:"PBE0",2:"PBE",3:"B3LYP",4:"BHAND",5:"TPSS",6:"BP86",7:"wB97X",8:"wB97X-D3",9:"M06L",10:"BHLYP"}
+
+
+fig,ax = plt.subplots(figsize=(10, 6))
+for i in np.arange(1,11,1):
+    ax.scatter(np.ones(N)+i-1,dict_eigVec[i],label=dict_func[i])
+ax.set_xlim(0,15)
+ax.tick_params(axis='y', labelsize=16)
+
+ax.set_ylabel(r"eigenvector elements",fontsize=18)
+ax.legend()
+plt.tick_params(
+    axis='x',          # changes apply to the x-axis
+    which='both',      # both major and minor ticks are affected
+    bottom=False,      # ticks along the bottom edge are off
+    top=False,         # ticks along the top edge are off
+    labelbottom=False) 
+fig.savefig("fig_distri_eigenVecRW.pdf",dpi=300)
+##################################### get cost kMeans for 2c ######################
+all_cost = []
+
+for i in np.arange(1,11,1):
+    data = np.zeros((N,2))
[…]

### 2024-06-25 figs/kmeansW.py

@@ -1,0 +1,113 @@
+from sklearn.cluster import KMeans
+from sklearn.neighbors import RadiusNeighborsClassifier
+import numpy as np
+import math
+import matplotlib.pyplot as plt
+
+N = 1000
+
+x1 = np.loadtxt("PBE0/eigenvec1Lw.txt")
+x2 = np.loadtxt("PBE/eigenvec1Lw.txt")
+x3 = np.loadtxt("B3LYP/eigenvec1Lw.txt")
+x4 = np.loadtxt("BHANDHLYP/eigenvec1Lw.txt")
+x5 = np.loadtxt("TPSS/eigenvec1Lw.txt")
+x6 = np.loadtxt("BP86/eigenvec1Lw.txt")
+x7 = np.loadtxt("wB97X/eigenvec1Lw.txt")
+x8 = np.loadtxt("wB97X-D3/eigenvec1Lw.txt")
+x9 = np.loadtxt("M06L/eigenvec1Lw.txt")
+x10 = np.loadtxt("BHLYP/eigenvec1Lw.txt")
+ToF = [1.23e-3,1.04e-3,4.28e-3,737.94,1.37e-2,7.46e-3,2.92e-2,0.0489,0.319,2.47]
+dict_eigVec = {1:x1,2:x2,3:x3,4:x4,5:x5,6:x6,7:x7,8:x8,9:x9,10:x10}
+dict_func = {1:"PBE0",2:"PBE",3:"B3LYP",4:"BHAND",5:"TPSS",6:"BP86",7:"wB97X",8:"wB97X-D3",9:"M06L",10:"BHLYP"}
+
+egval1 = np.sort(np.loadtxt("PBE0/eigenvalLw.txt"))[0:7]
+egval2 = np.sort(np.loadtxt("PBE/eigenvalLw.txt"))[0:7]
+egval3 = np.sort(np.loadtxt("B3LYP/eigenvalLw.txt"))[0:7]
+egval4 = np.sort(np.loadtxt("BHANDHLYP/eigenvalLw.txt"))[0:7]
+egval5 = np.sort(np.loadtxt("TPSS/eigenvalLw.txt"))[0:7]
+egval6 = np.sort(np.loadtxt("BP86/eigenvalLw.txt"))[0:7]
+egval7 = np.sort(np.loadtxt("wB97X/eigenvalLw.txt"))[0:7]
[…]

### 2024-06-25 figs/plot_DeltaToF_W_KL.py

@@ -1,0 +1,109 @@
+from scipy.stats import wasserstein_distance
+from scipy.stats import entropy
+
+import numpy as np
+import scipy as sp
+import matplotlib.pyplot as plt
+
+J_data = np.loadtxt("PBE/J.txt")
+seg1 = J_data[:,0]
+seg2 = J_data[:,1]
+Js = J_data[:,2]
+J_PBE0 = np.loadtxt("PBE0/J.txt")
+J_PBE = np.loadtxt("PBE/J.txt")
+J_B3LYP = np.loadtxt("B3LYP/J.txt")
+J_BH = np.loadtxt("BHANDHLYP/J.txt")
+J_TPSS = np.loadtxt("TPSS/J.txt")
+J_BP86 = np.loadtxt("BP86/J.txt")
+J_wB97X = np.loadtxt("wB97X/J.txt")
+J_wB97XD3 = np.loadtxt("wB97X-D3/J.txt")
+J_M06L = np.loadtxt("M06L/J.txt")
+J_BHLYP = np.loadtxt("BHLYP/J.txt")
+
+E_PBE0 = np.loadtxt("PBE0/E.txt")
+E_PBE = np.loadtxt("PBE/E_PBE.txt")
+E_B3LYP = np.loadtxt("B3LYP/E_B3LYP.txt")
+E_BH = np.loadtxt("BHANDHLYP/E.txt")
+E_TPSS = np.loadtxt("TPSS/E.txt")
+E_BP86 = np.loadtxt("BP86/E_BP86.txt")
+E_wB97X = np.loadtxt("wB97X/E_wB97X.txt")
+E_wB97XD3 = np.loadtxt("wB97X-D3/E.txt")
+E_M06L = np.loadtxt("M06L/E.txt")
+E_BHLYP = np.loadtxt("BHLYP/E.txt")
+ToFs = [1.23e-3,1.04e-3,4.28e-3,737.94,1.37e-2,7.46e-3,0.02916,0.0489,0.319,2.47]
+lam = [0.388,0.303,0.375,0.494,0.310,0.304,0.505,0.495,0.312,0.493]
+dict_E = { 1:E_PBE0, 2:E_PBE, 3:E_B3LYP, 4:E_BH, 5:E_TPSS, 6:E_BP86, 7:E_wB97X, 8: E_wB97XD3, 9: E_M06L, 10: E_BHLYP}
[…]

### 2024-06-25 figs/plot_DeltaToF_W_all.py

@@ -1,0 +1,226 @@
+from scipy.stats import wasserstein_distance
+from scipy.stats import entropy
+import scipy.stats as stats
+
+import numpy as np
+import scipy as sp
+import matplotlib.pyplot as plt
+import math
+k_B = 8.617333 * 10**(-5) # ev/K
+pi = math.pi
+hbar = 6.582119569 * 1e-16 # eV*s
+T = 300
+
+def Marcus(E,J,re):
+    temp = 2*pi/hbar * J**2/math.sqrt(4*pi*(re*k_B*300))*math.exp(-(E-re)**2/(4*re*k_B*300) )
+    return temp
+
+J_data = np.loadtxt("PBE/J.txt")
+seg1 = J_data[:,0]
+seg2 = J_data[:,1]
+Js = J_data[:,2]
+J_PBE0 = np.loadtxt("PBE0/J.txt")
+J_PBE = np.loadtxt("PBE/J.txt")
+J_B3LYP = np.loadtxt("B3LYP/J.txt")
+J_BH = np.loadtxt("BHANDHLYP/J.txt")
+J_TPSS = np.loadtxt("TPSS/J.txt")
+J_BP86 = np.loadtxt("BP86/J.txt")
+J_wB97X = np.loadtxt("wB97X/J.txt")
+J_wB97XD3 = np.loadtxt("wB97X-D3/J.txt")
+J_M06L = np.loadtxt("M06L/J.txt")
+J_BHLYP = np.loadtxt("BHLYP/J.txt")
+
+E_PBE0 = np.loadtxt("PBE0/E.txt")
+E_PBE = np.loadtxt("PBE/E_PBE.txt")
+E_B3LYP = np.loadtxt("B3LYP/E_B3LYP.txt")
+E_BH = np.loadtxt("BHANDHLYP/E.txt")
+E_TPSS = np.loadtxt("TPSS/E.txt")
+E_BP86 = np.loadtxt("BP86/E_BP86.txt")
+E_wB97X = np.loadtxt("wB97X/E_wB97X.txt")
+E_wB97XD3 = np.loadtxt("wB97X-D3/E.txt")
+E_M06L = np.loadtxt("M06L/E.txt")
+E_BHLYP = np.loadtxt("BHLYP/E.txt")
+ToFs = [1.23e-3,1.04e-3,4.28e-3,737.94,1.37e-2,7.46e-3,0.02916,0.0489,0.319,2.47]
[…]

### 2024-06-25 figs/plot_E_ToF_Z_PBE.py

@@ -1,0 +1,81 @@
+from sklearn.cluster import KMeans
+from sklearn.neighbors import RadiusNeighborsClassifier
+import numpy as np
+import math
+import matplotlib.pyplot as plt
+
+E66 = np.loadtxt("PBE/E66_range.txt")
+all_cost = np.loadtxt("PBE/all_cost.txt")
+all_ToF = np.loadtxt("PBE/all_ToF.txt")
+
+size =23
+fig,(ax1,ax2) = plt.subplots(1,2,figsize=(16,8))
+ln1 = ax1.plot(E66, all_cost,"--o",markersize=9,color="red", label=r"$E_{t}$ vs $Z$")
+ax1.set_xlabel(r"$E_{t}$[eV]",fontsize=size)
+ax1.set_ylabel(r"$Z_{2c}(E_t)$",fontsize=size)
+ax1.set_yscale("log")
+ax1.tick_params(axis='both',labelsize=size)
+ax1.set_ylim(1e-18,1e3)
+ax1.annotate("(a)", xy=(-0.25,1), xycoords='axes fraction', size=30)
+
+#ax1.legend(fontsize=size,frameon=False)
+
+ax1_2 = ax1.twinx()
+ln1_2 = ax1_2.plot(E66,all_ToF,"--o",markersize=9,color="black",label=r"$E_{t}$ vs $ToF$")
+ax1_2.set_yscale("log")
+ax1_2.set_ylabel(r"$ToF(E_{t})$[s]",fontsize=size,color="red")
+ax1_2.tick_params(axis='y',labelsize=size,color="red")
+#ax1_2.spines['right'].set_color('red') 
+lns = ln1+ln1_2
+labs = [l.get_label() for l in lns]
+ax1.legend(lns, labs, loc=1,fontsize=21,frameon=False)
+
+ax2.plot(all_ToF, all_cost,"--*",markersize=9,color="black", label=r"$E_{t}$ vs $Z$")
+ax2.set_xlabel(r"$ToF(E_t)$ [s]",fontsize=size)
+ax2.set_ylabel(r"$Z_{2c}(E_t)$",fontsize=size)
+ax2.set_yscale("log")
+ax2.set_xscale("log")
+ax2.tick_params(axis='both',labelsize=size)
+ax2.annotate("(b)", xy=(-0.25,1), xycoords='axes fraction', size=30)
[…]

### 2024-06-25 figs/plot_PF.py

@@ -1,0 +1,47 @@
+import numpy as np
+import scipy as sp
+import matplotlib.pyplot as plt
+import math
+k_B = 8.617333 * 10**(-5) # ev/K
+pi = math.pi
+hbar = 6.582119569 * 1e-16 # eV*s
+
+x1 = [4e7,5e7,6e7,7e7,8e7,9e7]
+for i in range(len(x1)):
+    x1[i] = np.sqrt(x1[i]/100)
+    
+mu_PBE0 = np.loadtxt("PBE0/mu.txt")
+mu_PBE = np.loadtxt("PBE/mu.txt")
+mu_B3LYP = np.loadtxt("B3LYP/mu.txt")
+mu_BHANDHLYP = np.loadtxt("BHANDHLYP/mu.txt")
+mu_TPSS = np.loadtxt("TPSS/mu.txt")
+mu_BP86 = np.loadtxt("BP86/mu.txt")
+
+fig,ax = plt.subplots()
+
+
+#ax.plot(x1,mu_k10_cor,'k^-')#,label='k=1.0')
+#ax.plot(x1,mu_k0,'b--o',label='$k=0.0\,(\sigma=0.00\mathrm{eV})$',markersize=10, markerfacecolor='none')
+ax.plot(x1,mu_PBE0,'r--o',label='$PBE0$',markersize=10,markerfacecolor='none')
+ax.plot(x1,mu_PBE,'g--o', label='$PBE$',markersize=10,markerfacecolor='none')
+ax.plot(x1,mu_B3LYP,'k--o',label='$B3LYP$',markersize=10,markerfacecolor='none')
+ax.plot(x1,mu_BHANDHLYP,'--o',label='$BHANDHLYP$',markersize=10,markerfacecolor='none')
+ax.plot(x1,mu_TPSS,'--o', label='$TPSS$',markersize=10,markerfacecolor='none')
+ax.plot(x1,mu_BP86,'--o',label='$BP86$',markersize=10,markerfacecolor='none')
+
+# ax.set_xlabel(r'$F^{1/2}$ (V/cm)$^{1/2}$',fontsize=12)
+ax.set_xlabel('$F^{1/2} \; [(V/cm)^{1/2}]$',fontsize=14)
+ax.set_ylabel("$\mu \; [cm^2/(Vs)]$",size=14)
+ax.set_xlim(600,1100)
+#ax.set_ylim(1e-5,1e1)
[…]

### 2024-06-25 figs/plot_PFe.py

@@ -1,0 +1,46 @@
+import numpy as np
+import scipy as sp
+import matplotlib.pyplot as plt
+import math
+k_B = 8.617333 * 10**(-5) # ev/K
+pi = math.pi
+hbar = 6.582119569 * 1e-16 # eV*s
+
+x1 = [4e7,5e7,6e7,7e7,8e7,9e7]
+for i in range(len(x1)):
+    x1[i] = np.sqrt(x1[i]/100)
+    
+mu_PBE0 = np.loadtxt("PBE0/mu_e.txt")
+mu_PBE = np.loadtxt("PBE/mu_e.txt")
+mu_B3LYP = np.loadtxt("B3LYP/mu_e.txt")
+mu_BHANDHLYP = np.loadtxt("BHANDHLYP/mu_e.txt")
+mu_TPSS = np.loadtxt("TPSS/mu_e.txt")
+mu_BP86 = np.loadtxt("BP86/mu_e.txt")
+
+fig,ax = plt.subplots()
+
+
+#ax.plot(x1,mu_k10_cor,'k^-')#,label='k=1.0')
+#ax.plot(x1,mu_k0,'b--o',label='$k=0.0\,(\sigma=0.00\mathrm{eV})$',markersize=10, markerfacecolor='none')
+ax.plot(x1,mu_PBE0,'r--o',label='$PBE0$',markersize=10,markerfacecolor='none')
+ax.plot(x1,mu_PBE,'g--o', label='$PBE$',markersize=10,markerfacecolor='none')
+ax.plot(x1,mu_B3LYP,'k--o',label='$B3LYP$',markersize=10,markerfacecolor='none')
+ax.plot(x1,mu_BHANDHLYP,'--o',label='$BHANDHLYP$',markersize=10,markerfacecolor='none')
+ax.plot(x1,mu_TPSS,'--o', label='$TPSS$',markersize=10,markerfacecolor='none')
+ax.plot(x1,mu_BP86,'--o',label='$BP86$',markersize=10,markerfacecolor='none')
+
+# ax.set_xlabel(r'$F^{1/2}$ (V/cm)$^{1/2}$',fontsize=12)
+ax.set_xlabel('$F^{1/2} \; [(V/cm)^{1/2}]$',fontsize=14)
+ax.set_ylabel("$\mu_e \; [cm^2/(Vs)]$",size=14)
+ax.set_xlim(600,1100)
+#ax.set_ylim(1e-5,1e1)
[…]

### 2024-06-25 figs/plot_eigvalRatio.py

@@ -1,0 +1,108 @@
+from scipy.stats import wasserstein_distance
+from scipy.stats import entropy
+import scipy.stats as stats
+
+import numpy as np
+import scipy as sp
+import matplotlib.pyplot as plt
+import math
+k_B = 8.617333 * 10**(-5) # ev/K
+pi = math.pi
+hbar = 6.582119569 * 1e-16 # eV*s
+T = 300
+
+def Marcus(E,J,re):
+    temp = 2*pi/hbar * J**2/math.sqrt(4*pi*(re*k_B*300))*math.exp(-(E-re)**2/(4*re*k_B*300) )
+    return temp
+
+J_data = np.loadtxt("PBE/J.txt")
+seg1 = J_data[:,0]
+seg2 = J_data[:,1]
+Js = J_data[:,2]
+E_PBE0 = np.loadtxt("PBE0/E.txt")
+E_PBE = np.loadtxt("PBE/E_PBE.txt")
+E_B3LYP = np.loadtxt("B3LYP/E_B3LYP.txt")
+E_BH = np.loadtxt("BHANDHLYP/E.txt")
+E_TPSS = np.loadtxt("TPSS/E.txt")
+E_BP86 = np.loadtxt("BP86/E_BP86.txt")
+E_wB97X = np.loadtxt("wB97X/E_wB97X.txt")
+E_wB97XD3 = np.loadtxt("wB97X-D3/E.txt")
+E_M06L = np.loadtxt("M06L/E.txt")
+E_BHLYP = np.loadtxt("BHLYP/E.txt")
+ToFs = [1.23e-3,1.04e-3,4.28e-3,737.94,1.37e-2,7.46e-3,0.02916,0.0489,0.319,2.47]
+lam = [0.388,0.303,0.375,0.494,0.310,0.304,0.505,0.495,0.312,0.493]
+dict_E = { 1:E_PBE0, 2:E_PBE, 3:E_B3LYP, 4:E_BH, 5:E_TPSS, 6:E_BP86, 7:E_wB97X, 8: E_wB97XD3, 9: E_M06L, 10: E_BHLYP}
+
+#eigval_2nd = [3.08e10,6.47e10,1.25e11,6.65e09,6.16e+10,7.35e10,1.74e+10]
[…]

### 2024-06-25 figs/plot_kmeans.py

@@ -1,0 +1,182 @@
+from sklearn.cluster import KMeans
+from sklearn.neighbors import RadiusNeighborsClassifier
+import numpy as np
+import math
+import matplotlib.pyplot as plt
+
+N = 1000
+
+x1 = np.loadtxt("PBE0/eigenvec1RW.txt")
+x2 = np.loadtxt("PBE/eigenvec1RW.txt")
+x3 = np.loadtxt("B3LYP/eigenvec1RW.txt")
+x4 = np.loadtxt("BHANDHLYP/eigenvec1RW.txt")
+x5 = np.loadtxt("TPSS/eigenvec1RW.txt")
+x6 = np.loadtxt("BP86/eigenvec1RW.txt")
+x7 = np.loadtxt("wB97X/eigenvec1RW.txt")
+x8 = np.loadtxt("wB97X-D3/eigenvec1RW.txt")
+x9 = np.loadtxt("M06L/eigenvec1RW.txt")
+x10 = np.loadtxt("BHLYP/eigenvec1RW.txt")
+ToF = [1.23e-3,1.04e-3,4.28e-3,737.94,1.37e-2,7.46e-3,2.92e-2,0.0489,0.319,2.47]
+
+dict_eigVec = {1:x1,2:x2,3:x3,4:x4,5:x5,6:x6,7:x7,8:x8,9:x9,10:x10}
+dict_func = {1:"PBE0",2:"PBE",3:"B3LYP",4:"BHAND",5:"TPSS",6:"BP86",7:"wB97X",8:"wB97X-D3",9:"M06L",10:"BHLYP"}
+
+fig,ax = plt.subplots(figsize=(10, 6))
+for i in np.arange(1,11,1):
+    ax.scatter(np.ones(N)+i-1,dict_eigVec[i],label=dict_func[i])
+ax.set_xlim(0,15)
+ax.tick_params(axis='y', labelsize=16)
+
+ax.set_ylabel(r"eigenvector elements",fontsize=18)
+ax.legend(fontsize=13)
+plt.tick_params(
+    axis='x',          # changes apply to the x-axis
+    which='both',      # both major and minor ticks are affected
+    bottom=False,      # ticks along the bottom edge are off
+    top=False,         # ticks along the top edge are off
+    labelbottom=False) 
+fig.savefig("fig_distri_eigenVecRW.pdf",dpi=600)
+
+
+##################################### get cost kMeans for ######################
+################ for L_RW
+all_cost_2c_RW = []
+for i in np.arange(1,11,1):
[…]

### 2024-06-25 figs/plot_scatterE.py

@@ -1,0 +1,141 @@
+from scipy.stats import wasserstein_distance
+from scipy.stats import entropy
+import scipy.stats as stats
+
+import numpy as np
+import scipy as sp
+import matplotlib.pyplot as plt
+import math
+import matplotlib.gridspec as gridspec
+import matplotlib as mpl
+
+k_B = 8.617333 * 10**(-5) # ev/K
+pi = math.pi
+hbar = 6.582119569 * 1e-16 # eV*s
+T = 300
+
+def Marcus(E,J,re):
+    temp = 2*pi/hbar * J**2/math.sqrt(4*pi*(re*k_B*300))*math.exp(-(E-re)**2/(4*re*k_B*300) )
+    return temp
+
+tick_font_size = 10
+
+def scatter_hist(x, y, ax, ax_histx, ax_histy):
+    # no labels
+    ax.set_facecolor('white')
+    ax_histx.set_facecolor('white')
+    ax_histy.set_facecolor('white')
+
+    ax_histx.tick_params(axis="x", labelbottom=False,labelsize=tick_font_size)
+    ax_histx.tick_params(axis="y", labelleft=False,labelsize=tick_font_size)
+
+    ax_histy.tick_params(axis="y", labelleft=False,labelsize = tick_font_size)
+    ax_histy.tick_params(axis="x", labelbottom=False,labelsize = tick_font_size)
+    # plt.style.use('_mpl-gallery-nogrid')
+    # ax.hist2d(x, y,bins=50,norm=mpl.colors.LogNorm())
+    # fig.colorbar(ax.hist2d(x, y,bins=50,norm=mpl.colors.LogNorm())[3],location='left')
+    nbins = 30
+    # now determine nice limits by hand:
+    xmin = -2.0
+    xmax = -0.2
+    ax_histx.hist(x,bins=nbins, range=(xmin,xmax),color = "blue")
+    
+    ymin = -2.0
+    ymax = -0.2
+    width = 0.1
+    ax_histy.hist(y,bins=nbins, range=(ymin,ymax), orientation='horizontal',color = "blue")
+
[…]

### 2024-06-25 figs/plot_scatterEs.py

@@ -1,0 +1,141 @@
+from scipy.stats import wasserstein_distance
+from scipy.stats import entropy
+import scipy.stats as stats
+
+import numpy as np
+import scipy as sp
+import matplotlib.pyplot as plt
+import math
+import matplotlib.gridspec as gridspec
+import matplotlib as mpl
+
+k_B = 8.617333 * 10**(-5) # ev/K
+pi = math.pi
+hbar = 6.582119569 * 1e-16 # eV*s
+T = 300
+
+def Marcus(E,J,re):
+    temp = 2*pi/hbar * J**2/math.sqrt(4*pi*(re*k_B*300))*math.exp(-(E-re)**2/(4*re*k_B*300) )
+    return temp
+
+tick_font_size = 10
+
+def scatter_hist(x, y, ax, ax_histx, ax_histy):
+    # no labels
+    ax.set_facecolor('white')
+    ax_histx.set_facecolor('white')
+    ax_histy.set_facecolor('white')
+
+    ax_histx.tick_params(axis="x", labelbottom=False,labelsize=tick_font_size)
+    ax_histx.tick_params(axis="y", labelleft=False,labelsize=tick_font_size)
+
+    ax_histy.tick_params(axis="y", labelleft=False,labelsize = tick_font_size)
+    ax_histy.tick_params(axis="x", labelbottom=False,labelsize = tick_font_size)
+    # plt.style.use('_mpl-gallery-nogrid')
+    # ax.hist2d(x, y,bins=50,norm=mpl.colors.LogNorm())
+    # fig.colorbar(ax.hist2d(x, y,bins=50,norm=mpl.colors.LogNorm())[3],location='left')
+    nbins = 30
+    # now determine nice limits by hand:
+    xmin = -1.6
+    xmax = 1.1
+    ax_histx.hist(x,bins=nbins, range=(xmin,xmax),color = "blue")
+    
+    ymin = -1.6
+    ymax = 1.1
+    width = 0.1
+    ax_histy.hist(y,bins=nbins, range=(ymin,ymax), orientation='horizontal',color = "blue")
+
[…]

### 2024-06-25 figs/plot_scatterJ.py

@@ -1,0 +1,129 @@
+from scipy.stats import wasserstein_distance
+from scipy.stats import entropy
+import scipy.stats as stats
+
+import numpy as np
+import scipy as sp
+import matplotlib.pyplot as plt
+import math
+import matplotlib.gridspec as gridspec
+import matplotlib as mpl
+
+k_B = 8.617333 * 10**(-5) # ev/K
+pi = math.pi
+hbar = 6.582119569 * 1e-16 # eV*s
+T = 300
+
+def Marcus(E,J,re):
+    temp = 2*pi/hbar * J**2/math.sqrt(4*pi*(re*k_B*300))*math.exp(-(E-re)**2/(4*re*k_B*300) )
+    return temp
+
+tick_font_size = 10
+
+def scatter_hist2(x, y, ax, ax_histx, ax_histy):
+    # no labels
+    ax.set_facecolor('white')
+    ax_histx.set_facecolor('white')
+    ax_histy.set_facecolor('white')
+
+    ax_histx.tick_params(axis="x", labelbottom=False,labelsize=tick_font_size)
+    ax_histx.tick_params(axis="y", labelleft=False,labelsize=tick_font_size)
+
+    ax_histy.tick_params(axis="y", labelleft=False,labelsize = tick_font_size)
+    ax_histy.tick_params(axis="x", labelbottom=False,labelsize = tick_font_size)
+    # plt.style.use('_mpl-gallery-nogrid')
+    # ax.hist2d(x, y,bins=50,norm=mpl.colors.LogNorm())
+    # fig.colorbar(ax.hist2d(x, y,bins=50,norm=mpl.colors.LogNorm())[3],location='left')
+    nbins = 30
+    # now determine nice limits by hand:
+    xmin = -17
+    xmax = 0
+    ax_histx.hist(x,bins=nbins, range=(xmin,xmax),color = "blue")
+    
+    ymin = -17
+    ymax = 0
+    width = 5
+    ax_histy.hist(y,bins=nbins, range=(ymin,ymax), orientation='horizontal',color = "blue")
+
+    plt.style.use('ggplot')
+    plt.grid(False)
[…]

### 2024-07-14 paper.tex
update

@@
     Further investigation reveals that ToF can be sensitive to the energy of a single node, leading to the ToF being sensitive to DFT functionals.
-    And those nodes are effectively trap nodes.
+
     Further investigation reveals that the BHANDHLYP functional leads to a trap site, and the charge mobility is very sensitive to the trap sites' energy, so a small change in the site's energy results in a large deviation of ToF.
 
-    We further investigate the uncertainty effect of electronic structure properties on the charge mobility 
-    We find that the site energy has the most significant effect on the charge mobility and a confidence level of charge mobility is obtained encoding the maximum amount of uncertainty in electronic structure parameters.
+    We further estimate the charge mobility distribution due to the uncertainty in electronic structure properties.  
+    We find that the uncertainty in site energy has the most significant effect on the charge mobility.
+Ultimately, a confidence level of charge mobility is obtained encoding the maximum amount of uncertainty in electronic structure parameters.
 \end{abstract}
@@
 \section{Introduction}
-Charge mobility is one of the main quantities of interest for OSC.
+Random walk in random environments is often used to model physical processes taking into account the varying disorder levels and environmental factors that influence the walker's movement. 
+These disorders and environmental factors can introduce a level of uncertainty that significantly impacts the overall rates of the random walk, ultimately affecting the quantities of interest one aims to obtain.
 
-Since the charge transport in OSC involves electrons, quantum mechanics and Schr\"odinger equation are essential for the theoretical study of charge mobility.
+A specific type of random walk in random environments is the charge transport in organic semiconductors (OSC), which consists of the amorphous mesoscopic structure due to spatially disordered molecular arrangement.
+Such structural disorder translates into electronic structure disorder, including energy disorder and coupling element disorder, which eventually leads the charge transport processes to be modeled as continuous time random walks (CTRWs).
+By representing the molecule as vertexes, the edge weights are assigned as the transition rates between the corresponding molecules, and the charge carriers are random walkers.
+The uncertainty brought by electronic structure disorder and environmental factors is reflected in the transition rates, that is the edge weights of the CTRWs.
 
-Charge conductance is due to electron dynamics, so quantum mechanics and Schr\"odinger equation are essential for the theoretical study of charge mobility.
-
-Due to the complexity of Schr\"odinger Equation, one alternative theory is the density functional theory (DFT).
+While the transition rates in those CTRWs can be calculated in a first-principle multiscale approach, this method involves some level of approximations. 
+Since the charge transport in OSC involves electrons, quantum mechanics and Schr\"odinger equation are essential in providing a time-series behavior of the charge dynamics. 
+But due to the complexity of Schr\"odinger Equation, one alternative theory is the density functional theory (DFT).
 DFT has two challenges.
@@
 The second challenge is addressed by utilizing DFT functionals to represent the exchange-correlation potential. 
-Those functionals are benchmarked to achieve good consistency with many physical quantities, such as ionization potential, and density of states.
+While there are benchmark results concerning the molecular energy calculation using different DFT functionals as well as rich literature on charge transport in the multiscale model OSC, a quantitative study of DFT functionals' effect on the charge transport processes is missing.
+Also missing is the influence of the uncertainty in the electronic structure properties on the quantity of interest.
 
-In the framework of this multiscale model, the accuracy of the DFT functionals determine the accuracy of the calculated mobility.
+There are many challenges for this investigation.
+Firstly, due to the number of molecules ($\sim 1000$), since the CTRWs are usually of high dimensions, quantifying uncertainty in such high dimensions is numerically challenging.
+Secondly, simulating the CTRWs process itself can be a computationally challenging task due to some convergence issues.
+Last but not least, the exact DFT functionals are not known so as the distribution of the transition rates for any two specific molecules.
 
-We can use the steady state mobility,
+One of the main quantities of interest to characterize the charge transport in OSC is charge mobility. Using this as the quantity of interest,
+the goal of this work is to investigate how the DFT functionals affect the electronic structures and charge mobility.
+The uncertainty due to the environmental factors that cause a change in the molecules' position is not considered in this work, although this topic itself is very important.
+We want to answer the following questions: 
+\begin{itemize}
+    \item How do DFT functionals change the reorganization energy, distribution of molecule energies and coupling elements? 
+    \item How do DFT functionals change the charge mobility?
+    \item Which electronic structure (among energy, coupling element and reorganization energy) has the most impact on the uncertainty of charge mobility?
+    \item Can we estimate the range of the quantity of interest, given a confidence level?
+\end{itemize}
 
-The influence of the different functionals on ToF calculation is missing. 
-In this work, we want to study how the DFT functionals affect the electronic structures and ToF charge mobility.
+With an external electric field, the charge mobility can be calculated as $\mu = \frac{\vec{v} \vec{F}}{|\vec{F}|^2}$ where $\vec{v}$ is the average drift-diffusive velocity of the charge carrier(s).
+Without an electric field, $\vec{v}$ is the purely diffusive velocity. 
+In electronic devices, the velocity is obtained from \textit{time-of-flight} (ToF) experiments, where charge carriers are injected into the cathode and collected at the anode.
+The ToF, denoted as $\tau$, is the period from injection to detection of at least one charge carrier.
+Then the velocity is simply $|\vec{v}| = \frac{L}{\tau}$, where $L$ is the length of the sample, which is usually chosen to be along the electric field direction if there is any.
 
-The goal of this work is to investigate how the DFT functionals affect the electronic structures and ToF charge mobility.
-We want to answer questions:
+Analogously, the ToF calculation for multiscale modeled OSC sets up some molecules as \textit{Source} and some as \textit{Sink}.
+The key quantity for characterizing the charge transport, especially for uncertainty quantification, is the ToF, since the sample length $L$ is fixed and can be seen as a constant.
+
+In literature regarding multiscale modeled OSC, most works on charge transport reported steady-state charge mobility.
+This setting repeats the molecule graph infinitely in all three dimensions by periodic boundary conditions.
+Then, the CTRWs on the graph are simulated, usually by kinetic Monte Carlo numerically.
+However, this method suffers from challenges such as convergence issues.
+Namely, there is no guarantee that the number of Monte Carlo simulations will correctly present the charge carrier occupation in each molecule, and this becomes a problem if we want to calculate some quantities for a confidence level.
+
+Therefore, the charge mobility based on ToF is the focus to characterize charge transport.
+Specifically, diffusive ToF with one charge carrier is used as the quantities of interest, and its calculation is based on the hitting time of a continuous time Markov chain. 
+Diffusive ToF only considers electronic structures, without the influence of external electric fields, making clear the sensitivity effect path starting from DFT functional to electronic structures and eventually to ToF mobility.
+We only consider the CTRWs with one charge carrier, since multiple charge carriers will lead to a huge dimension, making the uncertainty quantification difficult to approach computationally, plus other issues.
+Also, since we only simulate a very limited-size system, using only one charge carrier is aligned with the low carrier density at the electric device level.
+Furthermore, multiple charge carriers will effectively disable some low-energy molecules which are important in uncertainty quantification.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Multiscale Model}
+\label{sec:MSM}
+To perform multiscale modeling, the BCP (dimethyl-diphenyl-1,10-phenanthroline) device is used as the OSC in this work, since BCP has small conductivity and has been used as hole-trapping materials \cite{tsung_carrier_2008}.
+A BCP device consisting of 1000 molecules is shown in Fig.\ref{fig:ToFFill}(b) with atomistic details.
+
+%\begin{figure}
+%    \centering
+%    \includegraphics[width=0.4\textwidth]{figs/BCP_trap.png}
+%   \caption{ BCP device simulated from MD.
+The Source and Sink molecules are highlighted by the blue color, and the molecule corresponding to node 66 is highlighted by the red color.
+The other BCP molecules are in grey.
+}
+%   \label{fig:BCP}
+%\end{figure}
+
+The atomistic coordinates as well as the center-of-mass (COM) of each BCP molecule are generated from atomistic Molecular dynamics simulation, whose details are given in the Appendix.
+For modeling purposes, this molecular system is modeled as a graph on which the random walk takes place.
+Each vertice represents a molecule, which also corresponds to a localized state mentioned in the introduction.
+Using a cutoff distance $r_\text{cutoff}$, any two molecules whose COM is within $r_\text{cutoff}=0.5$ [nm] are connected by directed edges with a weight $\omega_{i,j}$, and usually $\omega_{i,j} \neq \omega_{j,i}$.
+The directed edge weights $\omega_{i,j}$ takes the electron transfer rate from localized state of molecule $i$ to that of molecule $j$, commonly expressed as Marcus rate:
+%
+\begin{equation}
+    \omega_{ij} = \frac{2\pi}{\hbar} \frac{|J_{i,j}|^2}{\sqrt{4\pi \lambda_{i,j} k_\text{B}T}} \exp\left(-\frac{(\Delta E_{i,j} + q \cdot \vec{r}_{i,j} - \lambda_{i,j})^2}{4\lambda_{i,j} k_\text{B}T}\right) ,
+    \label{equ:Marcus}
+\end{equation}
+%
+where $\hbar$ is the reduced Planck constant, $k_\text{B}$ the Boltzmann constant.
+The temperature $T$ (in \unit[]{K}), and the charge of the carrier $q$ (in \unit[]{e}) can be considered as parameters of the simulation.
+The vector $\vec{r}_{i,j} = (r^x_{ij},r^y_{ij},r^z_{ij})^\text{T}$ connects the center-of-masses of molecules $i$ and $j$, which is calculated cyclic boundary conditions depending on the boundary condition.
+The remaining quantities are calculated for each molecule using principles from quantum mechanics and classical mechanics: the reorganization energy $\lambda_{i,j}$, the electronic coupling $J_{ij}$, and the energy difference $\Delta E_{i,j} = E_i - E_j$ (all in \unit[]{eV}).
+
+In summary, the multiscale model for ToF calculation refers to the process: Firstly, classical Molecular Dynamics is used to generate the atomistic coordinates from which the vertex and edge sets are defined,
+secondly, quantum electronic structure calculation is performed to obtain the parameter sets $\left\{\lambda_{i,j}\right\}$,  $\left\{J_{ij}\right\}$, and $\left\{\Delta E_{i,j}\right\}$ based on the atomistic details to define the edge weights.
+Finally from those parameters, ToF is evaluated.
+In the remaining section, we will introduce the calculation details of $\left\{\lambda_{i,j}\right\}$,  $\left\{J_{ij}\right\}$, $\left\{\Delta E_{i,j}\right\}$ and ToF.
+
+\subsection{Electronic Structure Calculation} 
+Each molecule is an $N_\text{el}$-electron system, and in quantum mechanics, the probability of finding electrons in space is described by the wavefunction.
+The energy eigenvalue from the standard Kohn–Sham model \cite{kohn_self_1965} for a molecule (consisting of electrons and nuclei) reads:
+\begin{equation}
+    E_0 = \text{inf}\{ E^\text{KS}(\psi),\psi=(\phi_1,\cdots,\phi_{N_\text{el}}) \in (L_2(\mathbb{R}^3))^N, \int_{\mathbb{R}^3} \phi_i \phi_j =\delta_{ij} \} 
+    \label{eq:KS_model}
+\end{equation}
+where the single-electron wavefunction $\phi_i$ satisfies $(-\frac{1}{2}\nabla^2_\mathbf{r} + \hat{V}_\text{ext} + \hat{V}_\text{H}[\rho] + \hat{V}_\text{XC}) \phi_i^\text{KS} =  E^\text{KS}_i[\rho] \phi^\text{KS}_i$ with electron density $\rho$.
+The kinetic energy operator is $-\frac{1}{2}\nabla^2_\mathbf{r}$, external potential energy operator $\hat{V}_\text{ext}$ includes all electrostatic background potentials such as the nuclear potential of all the atoms.
+The Coulomb interaction operator is $\hat{V}_\text{H}[\rho] = \int_{\mathbb{R}^3} \frac{\rho(\vec{r}')}{ |\vec{r} - \vec{r}'| }$, and Kohn-Sham energy $E^\text{KS}_i$ of electron $i$.
+The molecule wavefunction $\psi$ lives in squared integrable Lebesgue space $L_2(\mathbb{R}^3)$.
+
+The exchange-correlation operator $\hat{V}_\text{XC}$ accounts for all the nonclassical terms, namely, the potential and kinetic energy associated with electron exchange and correlation.
+Knowledge of the exact $\hat{V}_\text{XC}$ makes obtaining the exact energy eigenvalue of many-body ground state possible.
+However, the exact $\hat{V}_\text{XC}$ is unknown and approximations, such as local density approximation (LDA), generalized gradient approximation (GGA) or a mixture of those two approximations with other models, are used in practice as the form of DFT functionals.
+The ten DFT functionals are shown in Table \ref{tab:para}.
+
+The energy eigenvalue $E_0$ depends on the atomic coordinates of the molecule. The optimized geometry of a molecule refers to the atomic coordinates that minimize $E_0$.
+The reorganization energy $\lambda_{i,j}$ from molecule $i$ to molecule $j$ is given as:
+\begin{equation}
+    \lambda_{ij} = E_i^\text{nC} - E_i^\text{nN} + E_j^\text{cN} - E_j^\text{cC}
+\end{equation}
+where $E_i^\text{nC}$ is the energy eigenvalue of the neutral molecule $i$ with the optimized geometry of charged molecule.
+When charge carriers are holes, a charged molecule has one electron less compared to a neutral molecule.
+Similarly, $E_j^\text{cN}$ is the energy eigenvalue of the charged molecule with the optimized geometry of the neutral molecule.
+For the BCP device, we obtain $\lambda_{ij}=0.50$ eV since this is only one type of molecule.
+
+The site energy $E_i$ is calculated by:
+\begin{equation}
+    E_i = (E_i^\text{cC} - E_i^\text{nN}) + E_i^\text{el}
+    \label{eq:siteE}
+\end{equation}
+where $E_i^\text{nN}$ is single-point energy of the neutral molecule $i$ with the optimized geometry of neutral molecule.
+Similarly, $E_i^\text{cC}$ is the single-point energy of the charged molecule $i$ with the optimized geometry of the charged molecule.
+In physical interpretation, $E_i^\text{cC} - E_i^\text{nN}$ is the adiabatic ionization potential of molecule $i$.
+And $E_i^\text{el}$ is the electrostatic interactions given by:
+%
+\begin{equation}
+    E_i^\text{el} = \frac{1}{4 \pi \epsilon_0} \sum\limits_{a_i} \sum\limits_{b_k,k\neq i} 
+    \frac{(q_{a_i}^\text{c} - q_{a_i}^\text{n}) q_{b_k}^\text{n}}{\epsilon_s r_{a_i,b_k}}
+    \label{equ:Eel}
+\end{equation}
+%
+where $i,k$ index molecules, $a_i$ and $b_k$ refer to atoms belonging to molecule $i,k$, $r_{a_i,b_k} = || \vec{r}_{a_i} - \vec{r}_{b_k} ||_2$ is the distance between atoms $a_i$ and $b_k$, and $\epsilon_s$ represents the static relative dielectric constant and is a function of the dipole moment of the molecule.
+From the atomic charges, the dipole moment is calculated via $\mu_i = \sum\limits_{a_i} q_{a_i} \cdot \vec{r}_{a_i}$.
+The molecule energies and their distribution are shown in the appendix.
+
+%%%%%%%
+The coupling element $J_{i,j}$ between molecule $i$ and $j$ is calculated \cite{baumeier_density_2010} using the electron wave function of the molecules obtained from the Kohn-Sham equation: 
+\begin{equation}
+    J_{i,j} = \frac{ J^0_{i,j}- \frac{1}{2}(e_i+e_j)\mathbf{S}_{i,j} }{ 1- \mathbf{S}_{i,j}^2 }
+    \label{equ:JAB}
+\end{equation}
+where $J^0_{i,j} = \langle \psi^i | \hat{H} | \psi^j \rangle $, $e_i = \langle \psi^i | \hat{H} | \psi^i \rangle $, $e_j = \langle \psi^j | \hat{H} | \psi^j \rangle $, and $\mathbf{S}_{i,j}=\langle \psi^i | \psi^j \rangle $ with bra-ket notation, $\hat{H}$ is the Hamiltonian of the electron wave function, and $\psi^{i,(j)}$ is the electron wave function of molecule $i(j)$.
+A single molecule is called a monomer, and a pair of two molecules is called a dimer.
+
+Denote $\psi^\text{D}$ as the electron wave function of the two molecules,  $J^0_{i,j}$ can be calculated via:
+$
+    J^0_{i,j} = \mathbf{\gamma}^i \text{diag}(\mathcal{E}) \mathbf{\gamma}^j
+$, 
+where $\mathbf{\gamma}^i = \langle \psi^i | \psi^\text{D} \rangle$ and $\mathbf{\gamma}^j = \langle \psi^j | \psi^\text{D} \rangle$ are called the projections of the monomer orbitals $\psi^i, \psi^j$ on the dimer orbitals $\psi^\text{D}$.
+And $\text{diag}(\mathcal{E})$ is the diagonal matrix consisting of energy eigenvalues of the one-particle wave function of the dimer.
+The molecular coupling element distribution is shown in the appendix.
+
+\section{Time-of-flight Calculation}
+After defining the graph $\mathbf{G}=(\mathbf{W},\mathbf{E})$ and calculating the edge weights from the multiscale model, the charge dynamics can be modeled as a continuous-time random walk process on the graph.
+To model the Source-Sink conditions in many devices such as the neuromorphic devices mentioned in the introduction, some vertices are used as \textbf{Source} to represent the electrode where charge carriers are injected, and some vertices as \textbf{Sink} where charge carriers are detected and ToF recorded.
+Due to Coulomb repulsion, each node can be occupied by one charge carrier at most, so a system with $N$ molecules and $N_c$ charge carriers has a total of $C^N_{N_C}$ occupation situations.
+Each of these occupation situations is considered as a state $\mathbf{s}$.
+If all the carriers' occupations are in the Source node, the state is called the Source state, and if at least one of the Sink nodes is occupied, the state is called the Sink state. 
+The transition rates between the states can be obtained from the adjacency matrix $\mathbf{W}:\omega_{i,j}$, since the connectivity of states is encoded in the connectivity of the nodes, as detailed in ~\cite{chen_graph_2024}.
+According to such connectivity, 
+the transition rates $\Omega_{\mathbf{s} \mathbf{s}' }$ from state $\mathbf{s}$ to $\mathbf{s}'$ is:
+\begin{equation}\label{eq:transition_rates}
+	\Omega_{\mathbf{s} \mathbf{s}^\prime} =
+	\begin{cases}
+	     0			&  \mathbf{s} \text{ is not connected to } \mathbf{s}^\prime,\\
+	    \omega_{ij}	&  \mathbf{s} \text{ is connected to } \mathbf{s}^\prime \text{ due to } (i,j)
+	\end{cases}
+\end{equation}
+
+Then the transition probability from state $\mathbf{s}$ to $\mathbf{s}'$ is $p_{\mathbf{s} \mathbf{s}^\prime} = \Omega_{\mathbf{s} \mathbf{s}^\prime}/D_\mathbf{s}$ where $D_\mathbf{s} := \sum_{\mathbf{s}^\prime \ne \mathbf{s}} \Omega_{\mathbf{s} \mathbf{s}^\prime}$.
+And the expected time from state $\mathbf{s}$ to reach the Sink state $\tau_\mathbf{s}$ is calculated 
+~\cite{chen_graph_2024} via: 
+\begin{equation}\label{eq:hitting_time}
+	\tau_\mathbf{s} = \begin{cases}
+		\frac{1}{D_\mathbf{s}} + \sum_{\mathbf{s}^\prime \ne \mathbf{s}} p_{\mathbf{s} \mathbf{s}^\prime} \tau_{\mathbf{s}^\prime} &\text{if $\mathbf{s}$ is not a sink state},\\
+		0 &\text{else.} 
+	\end{cases}
+\end{equation}
+
+Since we need to consider all possible starting nodes of the carriers, all the Source states need to be considered. 
+The random walk process has been modeled as a parallel electric network of capacitors~\cite{doyle_random_2000}, and accordingly, we evaluate the ToF to be the harmonic mean:
+%
+\begin{equation}
+\tau = N_\text{source} \left[\sum_{\mathbf{s}\in \text{source}} (\tau_\mathbf{s}^\ast)^{-1}\right]^{-1},
+\end{equation}
+with $N_\text{source}$ the number of source states.
 

### 2024-07-14 paper.tex
update

@@
 \linenumbers
-\title{Uncertain Effects of DFT Functionals on Calculations of Organic semiconductor Charge Mobility}
+\title{Uncertain Effects of DFT Functionals on Time-of-flight Calculations of Organic semiconductor }
 \author{authors}
@@
 \begin{abstract}
-    We study the uncertainty effect from the DFT functional to the charge mobility calculations of organic semiconductors (OSC). 
-    The ToF mobilities of the BCP and MADN devices are calculated from the first principle multiscale model. 
-    BCP has a large energy disorder while MADN has a small energy disorder.
-    Using a total of 10 different DFT functionals, we find that the electronic structure properties have similar distributions as indicated by Wasserstein distance, while the charge mobility of the could have a relatively large deviation.
-    Further investigation reveals that ToF can be sensitive to the energy of a single node, leading to the ToF being sensitive to DFT functionals.
+In this paper, the time-of-flight (ToF) is used to quantify the charge mobility in OSC. 
+Using ToF as the quantity of interest, the uncertainty effect of the DFT functionals on the ToF in a BCP device is studied. 
+Using a total of 10 different DFT functionals, we find that the electronic structure properties have similar distributions as indicated by Wasserstein distance, while the ToF can have a relatively large deviation.
+Further investigation reveals that ToF can be sensitive to the energy of a single molecule, leading to the ToF being sensitive to DFT functionals.
 
@@
 
-    We further estimate the charge mobility distribution due to the uncertainty in electronic structure properties.  
-    We find that the uncertainty in site energy has the most significant effect on the charge mobility.
-Ultimately, a confidence level of charge mobility is obtained encoding the maximum amount of uncertainty in electronic structure parameters.
+We further estimate the charge mobility distribution due to the uncertainty in electronic structure properties, and those properties' uncertainty is obtained from the maximum likelihood estimation of the 10 data points calculated using the 10 DFT functionals.
+Ultimately, a confidence level of charge mobility is obtained, and it is found that the uncertainty in site energy has the most significant effect on the ToF. 
 \end{abstract}

### 2024-08-20 paper.tex
update
edit

@@
 Further investigation reveals that the BHANDHLYP functional leads to a trap site, and the charge mobility is very sensitive to the trap sites' energy, so a small change in the site's energy results in a large deviation of ToF.
-
 We further estimate the charge mobility distribution due to the uncertainty in electronic structure properties, and those properties' uncertainty is obtained from the maximum likelihood estimation of the 10 data points calculated using the 10 DFT functionals.
@@
 After defining the graph $\mathbf{G}=(\mathbf{W},\mathbf{E})$ and calculating the edge weights from the multiscale model, the charge dynamics can be modeled as a continuous-time random walk process on the graph.
+One of the quantity of interest in charge transport is the Time-of-flight from Source to Sink. 
 To model the Source-Sink conditions in many devices such as the neuromorphic devices mentioned in the introduction, some vertices are used as \textbf{Source} to represent the electrode where charge carriers are injected, and some vertices as \textbf{Sink} where charge carriers are detected and ToF recorded.
@@
 
+\section{Uncertainty in ToF}
+Now we need to answer which ToF is accurate. 
+Using the multiscale model to determine the ToF is a function $f: \mathbb{R}^d \rightarrow \mathbb{R}^+$, which maps the parameter vector $$\vec{x} = [ E_1,E_2,\cdots,E_N, R_1,R_2,\cdots,R_N,J_1,J_2,\cdots,J_{N_\text{pair}} ]$$ to a real value $\tau \in \mathbb{R}^+$.
+
+Due to noise and approximation in the multiscale model, each element in $\vec{x}$ can be considered as an exact value plus an error term, for example $$E_1 = \hat{E}_1 + \epsilon_{E_1} $$
+There is no prior knowledge about this error terms. 
+Since the normal distribution inserts the least amount of prior knowledge into a model and encodes the maximum amount of uncertainty, we want to quantify the uncertainty when those error terms are normally distributed.
 %\bibliographystyle{unsrt}

### 2024-09-17 paper.tex
edit

@@
 \usepackage{lineno}
+\usepackage{comment}
+\usepackage{float}
 %++++++++++++++++++++++++++++++++++++++++
@@
 \maketitle
-
 \begin{abstract}
@@
 \section{Introduction}
-Random walk in random environments is often used to model physical processes taking into account the varying disorder levels and environmental factors that influence the walker's movement. 
+Random walks in random environments (RWRE) are widely used to model physical processes, incorporating the varying levels of disorder and environmental factors that influence movement. 
 These disorders and environmental factors can introduce a level of uncertainty that significantly impacts the overall rates of the random walk, ultimately affecting the quantities of interest one aims to obtain.
 
-A specific type of random walk in random environments is the charge transport in organic semiconductors (OSC), which consists of the amorphous mesoscopic structure due to spatially disordered molecular arrangement.
-Such structural disorder translates into electronic structure disorder, including energy disorder and coupling element disorder, which eventually leads the charge transport processes to be modeled as continuous time random walks (CTRWs).
-By representing the molecule as vertexes, the edge weights are assigned as the transition rates between the corresponding molecules, and the charge carriers are random walkers.
-The uncertainty brought by electronic structure disorder and environmental factors is reflected in the transition rates, that is the edge weights of the CTRWs.
+A notable example of RWRE is charge transport in organic semiconductors (OSCs), characterized by an amorphous mesoscopic structure due to spatially disordered molecular arrangements. 
+This structural disorder translates into electronic structure disorder, including energy disorder and coupling element disorder, leading to the modeling of charge transport processes as continuous time random walks (CTRWs) on a graph.
+Specifically, the molecules can be represented as nodes in a graph, the transition rates between them (edge weights) correspond to the transition rates between the molecules, and the charge carriers become the random walkers.
+The details of specifying the graph will be introduced in the Section 2.
+The uncertainty from electronic structure disorder and environmental factors is reflected in these transition rates.
 
-While the transition rates in those CTRWs can be calculated in a first-principle multiscale approach, this method involves some level of approximations. 
+While the transition rates in those CTRWs can be calculated in a first-principle multiscale approach, but it involves some level of approximations. 
 Since the charge transport in OSC involves electrons, quantum mechanics and Schr\"odinger equation are essential in providing a time-series behavior of the charge dynamics. 
 But due to the complexity of Schr\"odinger Equation, one alternative theory is the density functional theory (DFT). 
-DFT has two challenges.
-Firstly, it is computationally impossible to perform electronic structure calculations for the whole OSC device.
-And secondly, the exchange-correlation potential in DFT has an unknown formula.
+DFT faces two main challenges: it is computationally impractical for entire OSC devices and the exchange-correlation potential lacks an explicit formula.
 
-The first challenge is overcome by approximating the electron dynamics as transition processes between the localized states, with the transition rates calculated as the temperature-activated bi-molecule transition rates, known as the Marcus rate.
-The second challenge is addressed by utilizing DFT functionals to represent the exchange-correlation potential. 
-While there are benchmark results concerning the molecular energy calculation using different DFT functionals as well as rich literature on charge transport in the multiscale model OSC, a quantitative study of DFT functionals' effect on the charge transport processes is missing.
-Also missing is the influence of the uncertainty in the electronic structure properties on the quantity of interest.
+The first challenge is mitigated by approximating electron dynamics as transition processes between localized states which contain most of the molecular electron, with transition rates calculated using the temperature-activated bi-molecular Marcus rate.
+The second challenge is addressed by employing DFT functionals to approximate the exchange-correlation potential. 
+Despite benchmark results on molecular energy calculations with various DFT functionals and extensive literature on charge transport in multiscale models of OSCs, there is a lack of quantitative studies on how DFT functionals affect charge transport processes, and the influence of uncertainty in electronic structure properties.
 
-There are many challenges for this investigation.
-Firstly, due to the number of molecules ($\sim 1000$), since the CTRWs are usually of high dimensions, quantifying uncertainty in such high dimensions is numerically challenging.
-Secondly, simulating the CTRWs process itself can be a computationally challenging task due to some convergence issues.
-Last but not least, the exact DFT functionals are not known so as the distribution of the transition rates for any two specific molecules.
+Several challenges arise in this investigation.
+The high dimensionality of CTRWs (due to the large number of molecules, typically around 1000) makes uncertainty quantification numerically challenging.
+Secondly, simulating CTRWs is also computationally demanding due to convergence issues.
+Additionally, the exact DFT exchange-correlation functional and the distribution of transition rates for specific molecules are unknown.
 
@@
 the goal of this work is to investigate how the DFT functionals affect the electronic structures and charge mobility.
-The uncertainty due to the environmental factors that cause a change in the molecules' position is not considered in this work, although this topic itself is very important.
-We want to answer the following questions: 
+The uncertainty due to the environmental factors that cause a change in the molecules' position is not considered in this work, although this topic deserves intensive studies.
+We want to focus on the following questions: 
 \begin{itemize}
@@
 
-With an external electric field, the charge mobility can be calculated as $\mu = \frac{\vec{v} \vec{F}}{|\vec{F}|^2}$ where $\vec{v}$ is the average drift-diffusive velocity of the charge carrier(s).
+Charge mobility, in the presence of an external electric field, can be calculated as $\mu = \frac{\vec{v} \cdot \vec{F}}{|\vec{F}|^2}$, where $\vec{v}$ is the average drift-diffusive velocity of the charge carrier(s).
 Without an electric field, $\vec{v}$ is the purely diffusive velocity.
-In electronic devices, the velocity is obtained from \textit{time-of-flight} (ToF) experiments, where charge carriers are injected into the cathode and collected at the anode.
+In electronic devices, velocity is obtained from time-of-flight (ToF) experiments, where charge carriers are injected into the cathode and collected at the anode.
 The ToF, denoted as $\tau$, is the period from injection to detection of at least one charge carrier.
-Then the velocity is simply $|\vec{v}| = \frac{L}{\tau}$, where $L$ is the length of the sample, which is usually chosen to be along the electric field direction if there is any.
+The velocity is given by $|\vec{v}| = \frac{L}{\tau}$, where $L$ is the sample length, usually aligned with the electric field direction if present.
 
-Analogously, the ToF calculation for multiscale modeled OSC sets up some molecules as \textit{Source} and some as \textit{Sink}.
-The key quantity for characterizing the charge transport, especially for uncertainty quantification, is the ToF, since the sample length $L$ is fixed and can be seen as a constant.
+For multiscale modeled OSCs, ToF calculations involve setting some molecules as \textit{Source} and some as \textit{Sink}.
+The key quantity for characterizing charge transport, especially for uncertainty quantification, is ToF, as the sample length $L$ is fixed and constant.
 
-In literature regarding multiscale modeled OSC, most works on charge transport reported steady-state charge mobility.
-This setting repeats the molecule graph infinitely in all three dimensions by periodic boundary conditions.
-Then, the CTRWs on the graph are simulated, usually by kinetic Monte Carlo numerically.
-However, this method suffers from challenges such as convergence issues.
-Namely, there is no guarantee that the number of Monte Carlo simulations will correctly present the charge carrier occupation in each molecule, and this becomes a problem if we want to calculate some quantities for a confidence level.
+Most literature on charge transport in multiscale modeled OSCs reports steady-state charge mobility, using periodic boundary conditions to simulate CTRWs on an infinitely repeating molecular graph, typically via kinetic Monte Carlo simulations.
+However, this method faces challenges, particularly convergence issues, which complicate the accurate calculation of quantities with a desired confidence level.
 
-Therefore, the charge mobility based on ToF is the focus to characterize charge transport.
-Specifically, diffusive ToF with one charge carrier is used as the quantities of interest, and its calculation is based on the hitting time of a continuous time Markov chain. 
-Diffusive ToF only considers electronic structures, without the influence of external electric fields, making clear the sensitivity effect path starting from DFT functional to electronic structures and eventually to ToF mobility.
-We only consider the CTRWs with one charge carrier, since multiple charge carriers will lead to a huge dimension, making the uncertainty quantification difficult to approach computationally, plus other issues.
-Also, since we only simulate a very limited-size system, using only one charge carrier is aligned with the low carrier density at the electric device level.
-Furthermore, multiple charge carriers will effectively disable some low-energy molecules which are important in uncertainty quantification.
+Therefore, this work focuses on characterizing charge mobility based on ToF, specifically diffusive ToF with a single charge carrier, calculated from the hitting time of a continuous time Markov chain.
+This approach excludes the effects of external electric fields, clarifying the sensitivity from DFT functional to electronic structures and ToF mobility.
+Furthermore, considering only one charge carrier aligns with the low carrier density in electronic devices and avoids the computational complexity of simulating multiple charge carriers, which can obscure important low-energy molecules in uncertainty quantification.
 
@@
 \label{sec:MSM}
-To perform multiscale modeling, the BCP (dimethyl-diphenyl-1,10-phenanthroline) device is used as the OSC in this work, since BCP has small conductivity and has been used as hole-trapping materials \cite{tsung_carrier_2008}.
-A BCP device consisting of 1000 molecules is shown in Fig.\ref{fig:ToFFill}(b) with atomistic details.
 
-%\begin{figure}
-%    \centering
-%    \includegraphics[width=0.4\textwidth]{figs/BCP_trap.png}
-%   \caption{ BCP device simulated from MD.
-The Source and Sink molecules are highlighted by the blue color, and the molecule corresponding to node 66 is highlighted by the red color.
-The other BCP molecules are in grey.
-}
-%   \label{fig:BCP}
-%\end{figure}
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.95\textwidth]{figs/MSM.png}
+    \caption{The multiscale model workflow for OSC.
+Step 1: MD simulation to generate atom coordinates.
+Step 2: Molecule energy $E_i$ calculation.
+Step 3: Calculation of Reorganization energy $\lambda_{i,j}$ and coupling element $J_{i,j}$ for pairs of molecule $i,j$ whose COM distance is less than $r_\text{cutoff}$.
+Step 4: Modelling dynamics on device level, such as ToF calculation.}
+    \label{fig:MSM}
+\end{figure}
 
-The atomistic coordinates as well as the center-of-mass (COM) of each BCP molecule are generated from atomistic Molecular dynamics simulation, whose details are given in the Appendix.
-For modeling purposes, this molecular system is modeled as a graph on which the random walk takes place.
-Each vertice represents a molecule, which also corresponds to a localized state mentioned in the introduction.
-Using a cutoff distance $r_\text{cutoff}$, any two molecules whose COM is within $r_\text{cutoff}=0.5$ [nm] are connected by directed edges with a weight $\omega_{i,j}$, and usually $\omega_{i,j} \neq \omega_{j,i}$.
-The directed edge weights $\omega_{i,j}$ takes the electron transfer rate from localized state of molecule $i$ to that of molecule $j$, commonly expressed as Marcus rate:
+Figure \ref{fig:scatterE} shows the workflow of the multiscale model for ToF calculation.
+In brief summary, the process includes: Firstly, classical Molecular Dynamics is used to generate the atomistic coordinates from which the vertex and edge sets are defined.
+Specifically, using a cutoff distance $r_\text{cutoff}$, any two molecules whose center of mass (COM) within $r_\text{cutoff}=0.5$ [nm] form a pair of molecules where directed edge weight can be calculated.
+Secondly, quantum electronic structure calculation is performed to obtain the electronic structure properties: The molecule energy $E_i$ of molecule $i$, the reorganization energy between $\left\{\lambda_{i,j}\right\}$ and coupling element $\left\{\Delta J_{i,j}\right\}$ between the pair of molecules $i$ and $j$.
+All in unit of eV.
+
+Then, those electronic structure properties are used to calculate the bi-molecular Marcus rate between the molecules:
 %
 \begin{equation}
-    \omega_{ij} = \frac{2\pi}{\hbar} \frac{|J_{i,j}|^2}{\sqrt{4\pi \lambda_{i,j} k_\text{B}T}} \exp\left(-\frac{(\Delta E_{i,j} + q \cdot \vec{r}_{i,j} - \lambda_{i,j})^2}{4\lambda_{i,j} k_\text{B}T}\right) ,
+    \omega_{ij} = \frac{2\pi}{\hbar} \frac{|J_{i,j}|^2}{\sqrt{4\pi \lambda_{i,j} k_\text{B}T}} \exp\left(-\frac{(\Delta E_{i,j} + q \vec{F} \cdot \vec{r}_{i,j} - \lambda_{i,j})^2}{4\lambda_{i,j} k_\text{B}T}\right) ,
     \label{equ:Marcus}
@@
 where $\hbar$ is the reduced Planck constant, $k_\text{B}$ the Boltzmann constant.
-The temperature $T$ (in \unit[]{K}), and the charge of the carrier $q$ (in \unit[]{e}) can be considered as parameters of the simulation.
-The vector $\vec{r}_{i,j} = (r^x_{ij},r^y_{ij},r^z_{ij})^\text{T}$ connects the center-of-masses of molecules $i$ and $j$, which is calculated cyclic boundary conditions depending on the boundary condition.
-The remaining quantities are calculated for each molecule using principles from quantum mechanics and classical mechanics: the reorganization energy $\lambda_{i,j}$, the electronic coupling $J_{ij}$, and the energy difference $\Delta E_{i,j} = E_i - E_j$ (all in \unit[]{eV}).
+The temperature $T$ (in \unit[]{K}), external electric field $\vec{F}$ and the charge of the carrier $q$ (in \unit[]{e}) can be considered as parameters of the simulation.
+The vector $\vec{r}_{i,j} = (r^x_{ij},r^y_{ij},r^z_{ij})^\text{T}$ connects the center-of-masses of molecules $i$ and $j$, which is calculated using cyclic boundary conditions depending on system setting.
+And $\Delta E_{i,j} = E_i - E_j$ is the energy difference between a pair of molecules.
+Finally, the quantity of interest, such as ToF $\tau$, can be calculated from the transition rates $\omega_{ij}$.
 
-In summary, the multiscale model for ToF calculation refers to the process: Firstly, classical Molecular Dynamics is used to generate the atomistic coordinates from which the vertex and edge sets are defined,
-secondly, quantum electronic structure calculation is performed to obtain the parameter sets $\left\{\lambda_{i,j}\right\}$,  $\left\{J_{ij}\right\}$, and $\left\{\Delta E_{i,j}\right\}$ based on the atomistic details to define the edge weights.
-Finally from those parameters, ToF is evaluated.
-In the remaining section, we will introduce the calculation details of $\left\{\lambda_{i,j}\right\}$,  $\left\{J_{ij}\right\}$, $\left\{\Delta E_{i,j}\right\}$ and ToF.
+\subsection{Molecule Dynamics Simulation}
+In a material system of $N_a$ atoms with mass and position denoted by $m_i$ and $\vec{r}_i$ respectively, molecular dynamics (MD) models the evolution of the atomic coordinate using Newton's second law, which is written in Hamilton equation:
+\begin{equation}
+    \begin{cases}
+        \frac{d \vec{r}_i}{dt} = \frac{\partial H }{\partial \vec{p}_i} \\
+        \frac{d \vec{p}_i}{dt} = -\frac{\partial H }{\partial \vec{r}_i}
+    \end{cases}
+    \label{eq:Hamilton}
+\end{equation}
+for $i=1,\cdots,N_a$, where the Hamiltonian $H$ reads:
+\begin{equation}
+    H=\sum\limits_{i} \frac{|\vec{p}_i|^2}{2 m_i} + U(\vec{r}_1,\cdots,\vec{r}_{N_a})
+    \label{eq:Hamilton2}
+\end{equation}
+
+In principle the potential energy function $U(\vec{r}_1,\cdots,\vec{r}_{N_a})$ of the system can be obtained from electronic structure models.
+In practice, it is a very computationally expensive procedure, and without too much loss in precision, MD use empirical potentials that are designed for specific purposes.
+In our work, constant the molecule number $N=1000$, a temperature $T=300$ K and a pressure at 1 atm is used to achieve an NPT ensemble. 
+One of the final BCP morphology is chosen as OSC for charge transport study.
 
 \subsection{Electronic Structure Calculation} 
-Each molecule is an $N_\text{el}$-electron system, and in quantum mechanics, the probability of finding electrons in space is described by the wavefunction.
-The energy eigenvalue from the standard Kohn–Sham model \cite{kohn_self_1965} for a molecule (consisting of electrons and nuclei) reads:
+The molecule energy $E_i$ in the multiscale model is calculated as:
 \begin{equation}
-    E_0 = \text{inf}\{ E^\text{KS}(\psi),\psi=(\phi_1,\cdots,\phi_{N_\text{el}}) \in (L_2(\mathbb{R}^3))^N, \int_{\mathbb{R}^3} \phi_i \phi_j =\delta_{ij} \} 
-    \label{eq:KS_model}
+E_i = (U^\text{cC}_i - U^\text{nN}_i) + (E^\text{c}_i - E^\text{n}_i)
+\label{eq:E_i}
 \end{equation}
-where the single-electron wavefunction $\phi_i$ satisfies $(-\frac{1}{2}\nabla^2_\mathbf{r} + \hat{V}_\text{ext} + \hat{V}_\text{H}[\rho] + \hat{V}_\text{XC}) \phi_i^\text{KS} =  E^\text{KS}_i[\rho] \phi^\text{KS}_i$ with electron density $\rho$.
-The kinetic energy operator is $-\frac{1}{2}\nabla^2_\mathbf{r}$, external potential energy operator $\hat{V}_\text{ext}$ includes all electrostatic background potentials such as the nuclear potential of all the atoms.
-The Coulomb interaction operator is $\hat{V}_\text{H}[\rho] = \int_{\mathbb{R}^3} \frac{\rho(\vec{r}')}{ |\vec{r} - \vec{r}'| }$, and Kohn-Sham energy $E^\text{KS}_i$ of electron $i$.
-The molecule wavefunction $\psi$ lives in squared integrable Lebesgue space $L_2(\mathbb{R}^3)$.
+where $U^\text{cC}_i$ is the internal energy of charged molecule $i$ in the optimized charged geometry, and $U^\text{nN}_i$ is the internal energy of neutral molecule $i$ in the optimized neutral geometry.
+The calculation of $U$ and how to obtain optimized geometry will be introduced in the subsection DFT Calculation.
+In the superscript the lowercase letter "c/n" represents the molecule state of being charged/neutral and uppercase letter "C/N" represents the geometry of the charged/neutral molecule.
+This notation also applies for $E^\text{c}_i$, $E^\text{n}_i$.
+And $E^\text{n}_i = E^\text{n,el}_i + E^\text{n,induce}_i$ is the energy due to the electrostatic and induced dipole moment effect.
+Compared with the electrostatic energy calculated using the dielectric constant, this energy in multiscale model is very sensitive to the molecule structure, making the uncertainty quantification of charge transport in multiscale model much more important.
+A precise method for calculating $E^\text{n}_i$ is to use the Thole Model as detailed in \cite{Baumeier2011}.
 
-The exchange-correlation operator $\hat{V}_\text{XC}$ accounts for all the nonclassical terms, namely, the potential and kinetic energy associated with electron exchange and correlation.
-Knowledge of the exact $\hat{V}_\text{XC}$ makes obtaining the exact energy eigenvalue of many-body ground state possible.
-However, the exact $\hat{V}_\text{XC}$ is unknown and approximations, such as local density approximation (LDA), generalized gradient approximation (GGA) or a mixture of those two approximations with other models, are used in practice as the form of DFT functionals.
-The ten DFT functionals are shown in Table \ref{tab:para}.
+This method has the steps include: first, each atom $a_i$ is initialized with charges $q_{a_i}$ and dipole moment $D_{a_i}$. 
+Then the induced dipoles of each atom are calculated using the electric field generated by other atoms $b_j$.
+This calculation continuous iteratively to update the induced dipoles of every atom by considering the fields due to other dipoles.
+Finally, it checks for convergence, if the induced dipoles have not changed significantly from one iteration to the next, the iterative process stops.
+Finally, the electrostatic energy and polarization energy using the final set of induced dipoles and atomic charges.
+So in summary, $E^\text{n}_i$ is a function of all atoms' charges and induced dipoles: $E^\text{n}_i = \sum\limits_{a_i} f(q_{a_i}, D_{a_i})$.
 
-The energy eigenvalue $E_0$ depends on the atomic coordinates of the molecule. The optimized geometry of a molecule refers to the atomic coordinates that minimize $E_0$.
-The reorganization energy $\lambda_{i,j}$ from molecule $i$ to molecule $j$ is given as:
+The reorganization energy $\lambda_{i,j}$ between molecule $i$ to molecule $j$ is given as:
 \begin{equation}
-    \lambda_{ij} = E_i^\text{nC} - E_i^\text{nN} + E_j^\text{cN} - E_j^\text{cC}
+    \lambda_{ij} = U_i^\text{nC} - U_i^\text{nN} + U_j^\text{cN} - U_j^\text{cC}
 \end{equation}
-where $E_i^\text{nC}$ is the energy eigenvalue of the neutral molecule $i$ with the optimized geometry of charged molecule.
-When charge carriers are holes, a charged molecule has one electron less compared to a neutral molecule.
-Similarly, $E_j^\text{cN}$ is the energy eigenvalue of the charged molecule with the optimized geometry of the neutral molecule.
-For the BCP device, we obtain $\lambda_{ij}=0.50$ eV since this is only one type of molecule.
-
-The site energy $E_i$ is calculated by:
-\begin{equation}
-    E_i = (E_i^\text{cC} - E_i^\text{nN}) + E_i^\text{el}
-    \label{eq:siteE}
-\end{equation}
-where $E_i^\text{nN}$ is single-point energy of the neutral molecule $i$ with the optimized geometry of neutral molecule.
-Similarly, $E_i^\text{cC}$ is the single-point energy of the charged molecule $i$ with the optimized geometry of the charged molecule.
-In physical interpretation, $E_i^\text{cC} - E_i^\text{nN}$ is the adiabatic ionization potential of molecule $i$.
-And $E_i^\text{el}$ is the electrostatic interactions given by:
-%
-\begin{equation}
-    E_i^\text{el} = \frac{1}{4 \pi \epsilon_0} \sum\limits_{a_i} \sum\limits_{b_k,k\neq i} 
-    \frac{(q_{a_i}^\text{c} - q_{a_i}^\text{n}) q_{b_k}^\text{n}}{\epsilon_s r_{a_i,b_k}}
-    \label{equ:Eel}
-\end{equation}
-%
-where $i,k$ index molecules, $a_i$ and $b_k$ refer to atoms belonging to molecule $i,k$, $r_{a_i,b_k} = || \vec{r}_{a_i} - \vec{r}_{b_k} ||_2$ is the distance between atoms $a_i$ and $b_k$, and $\epsilon_s$ represents the static relative dielectric constant and is a function of the dipole moment of the molecule.
-From the atomic charges, the dipole moment is calculated via $\mu_i = \sum\limits_{a_i} q_{a_i} \cdot \vec{r}_{a_i}$.
-The molecule energies and their distribution are shown in the appendix.
 
@@
 \begin{equation}
-    J_{i,j} = \frac{ J^0_{i,j}- \frac{1}{2}(e_i+e_j)\mathbf{S}_{i,j} }{ 1- \mathbf{S}_{i,j}^2 }
+    J_{i,j} = \frac{ J^0_{i,j}- \frac{1}{2}(e_i+e_j)S_{i,j} }{ 1- S_{i,j}^2 }
     \label{equ:JAB}
 \end{equation}
-where $J^0_{i,j} = \langle \psi^i | \hat{H} | \psi^j \rangle $, $e_i = \langle \psi^i | \hat{H} | \psi^i \rangle $, $e_j = \langle \psi^j | \hat{H} | \psi^j \rangle $, and $\mathbf{S}_{i,j}=\langle \psi^i | \psi^j \rangle $ with bra-ket notation, $\hat{H}$ is the Hamiltonian of the electron wave function, and $\psi^{i,(j)}$ is the electron wave function of molecule $i(j)$.
+where $J^0_{i,j} = \langle \psi^i | \hat{H} | \psi^j \rangle $, $e_i = \langle \psi^i | \hat{H} | \psi^i \rangle $, $e_j = \langle \psi^j | \hat{H} | \psi^j \rangle $, and $S_{i,j}=\langle \psi^i | \psi^j \rangle $ with bra-ket notation, $\hat{H}$ is the Hamiltonian of the electron wave function, and $\psi^{i,(j)}$ is the electron wave function of molecule $i(j)$.
 A single molecule is called a monomer, and a pair of two molecules is called a dimer.
@@
 And $\text{diag}(\mathcal{E})$ is the diagonal matrix consisting of energy eigenvalues of the one-particle wave function of the dimer.
-The molecular coupling element distribution is shown in the appendix.
+
+In conclusion, the calculation of electronic structure relies on the internal energy and electron wave function.
+As mentioned in the introduction, DFT is used to calculate these two quantities.
+The next subsection will introduce the details of DFT.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{DFT Calculation}
+In multiscale model, each molecule is an $N_\text{el}$-electron system, and the probability of finding electrons in space is described by the wavefunction.
+In DFT, the internal energy calculated from the Kohn–Sham equation \cite{kohn_self_1965} reads:
+
+\begin{equation}
+    U^\text{KS}[\rho] = T_s[\rho] + \int \hat{V}_\text{ext}(\vec{r}) \rho(\vec{r}) d \vec{r} + \hat{V}_\text{H}[\rho] + \hat{V}_\text{XC}[\rho]
+    \label{eq:KS_model}
+\end{equation}
+where the electron density is $\rho=\sum\limits_{i=1}^{N_\text{el}} \phi_i^\star(\vec{r}) \phi_i(\vec{r})$, $T_s[\rho]$ is the kinetic energy depending on $\rho$,  $\hat{V}_\text{ext}$ is the external potential energy,  $\hat{V}_\text{H}[\rho]$ is the Hartree energy accounting for the Coulomb interaction, $\hat{V}_\text{XC}[\rho]$ is the exchange-correlation energy accounting for the difference between classical and quantum effect.
+The exact form of $\hat{V}_\text{XC}[\rho]$ is not known, in practice, this energy term is approximated by DFT functionals.
+In our work, ten DFT functionals are used to represent this energy term.
+The single-electron wave function $\phi_i$ satisfies: 
+\begin{equation}
+    (-\frac{1}{2}\nabla^2_{\vec{r}} + \hat{V}_\text{ext} + \frac{\delta \hat{V}_\text{H}[\rho]}{\delta \rho} + \frac{\hat{V}_\text{XC}[\rho]}{\delta \rho}) \phi_i^\text{KS}(\vec{r}) =  \epsilon^\text{KS}_i[\rho] \phi^\text{KS}_i (\vec{r})
+    \label{eq:KS2}
+\end{equation}
+with $\epsilon^\text{KS}_i[\rho]$ being the energy eigenvalue of electron $i$. 
+In practice, Equation \ref{eq:KS2} is solved iteratively, and the wave function is represented by a linear combination of basis functions call basic sets. 
+In this work, the basic set def2-tzvp \cite{weigend_accurate_2006} is used. The DFT computation is performed by VOTCA \cite{Baumeier2011} which internally calls ORCA software.
+The internal energy $U^\text{KS}$ depends on the atomic coordinates of the molecule. The optimized geometry of a molecule refers to the atomic coordinates that minimize $U^\text{KS}$.
 
 \section{Time-of-flight Calculation}
-After defining the graph $\mathbf{G}=(\mathbf{W},\mathbf{E})$ and calculating the edge weights from the multiscale model, the charge dynamics can be modeled as a continuous-time random walk process on the graph.
-One of the quantity of interest in charge transport is the Time-of-flight from Source to Sink. 
-To model the Source-Sink conditions in many devices such as the neuromorphic devices mentioned in the introduction, some vertices are used as \textbf{Source} to represent the electrode where charge carriers are injected, and some vertices as \textbf{Sink} where charge carriers are detected and ToF recorded.
-Due to Coulomb repulsion, each node can be occupied by one charge carrier at most, so a system with $N$ molecules and $N_c$ charge carriers has a total of $C^N_{N_C}$ occupation situations.
-Each of these occupation situations is considered as a state $\mathbf{s}$.
-If all the carriers' occupations are in the Source node, the state is called the Source state, and if at least one of the Sink nodes is occupied, the state is called the Sink state. 
+The multiscale model defines a graph $\mathbf{G}$ with an adjacency matrix $\mathbf{W}$, where the edge weights $\omega_{i,j}$ represent the Marcus rate from molecule $i$ to molecule $j$.
+The charge dynamics are modeled as a continuous-time random walk on this graph.
+In the time-of-flight (ToF) model, some vertices serve as \textit{Source} nodes, representing the electrode where charge carriers are injected, and some as \textit{Sink} nodes, where charge carriers are detected and the ToF is recorded.
+
+As mentioned in the introduction, a quantity of interest in modeling charge dynamics is the ToF, which is the time for charges carriers injected into the Source to be detected at the Sink.
+A typical method to obtain the ToF is to use the kinetic Monte Carlo (KMC) method to simulate the CTRW for many times and record ToFs, which are random variables. 
+To be detailed: 
+But a challenge with this KMC is that one need to repeat a large number $N_\text{KMC}$ of KMC simulation to guarantee an converged ToF.
+Furthermore, $N_\text{KMC}$ is not known before running KMC, posing a great challenge to quantify the uncertainty of ToF from the multiscale model.
+An alternative method to overcome the convergence challenge is to obtain ToF as the hitting time a continuous time Markov chain.
+
+Due to Pauli repulsion, each node can be occupied by at most one charge carrier.
+For a system with $N$ molecules and $N_c$ charge carriers, there are ${N \choose N_c}$ possible occupation states.
+Each occupation state is denoted as $\mathbf{s}$.
+A state is called the Source state if all carriers occupy the Source nodes, and a Sink state if at least one of the Sink nodes is occupied.
+
 The transition rates between the states can be obtained from the adjacency matrix $\mathbf{W}:\omega_{i,j}$, since the connectivity of states is encoded in the connectivity of the nodes, as detailed in ~\cite{chen_graph_2024}.
@@
 Then the transition probability from state $\mathbf{s}$ to $\mathbf{s}'$ is $p_{\mathbf{s} \mathbf{s}^\prime} = \Omega_{\mathbf{s} \mathbf{s}^\prime}/D_\mathbf{s}$ where $D_\mathbf{s} := \sum_{\mathbf{s}^\prime \ne \mathbf{s}} \Omega_{\mathbf{s} \mathbf{s}^\prime}$.
-And the expected time from state $\mathbf{s}$ to reach the Sink state $\tau_\mathbf{s}$ is calculated 
-~\cite{chen_graph_2024} via: 
+And the expected time from state $\mathbf{s}$ to reach the Sink state $\tau_\mathbf{s}$ is calculated via: 
 \begin{equation}\label{eq:hitting_time}
@@
 
-Since we need to consider all possible starting nodes of the carriers, all the Source states need to be considered. 
-The random walk process has been modeled as a parallel electric network of capacitors~\cite{doyle_random_2000}, and accordingly, we evaluate the ToF to be the harmonic mean:
-%
+To account for all possible starting nodes of the carriers, all Source states must be considered.
+The random walk process can be modeled as a parallel electric network of capacitors \cite{doyle_random_2000}.
+Accordingly, the ToF is evaluated using the harmonic mean:
 \begin{equation} 
-\tau = N_\text{source} \left[\sum_{\mathbf{s}\in \text{source}} (\tau_\mathbf{s}^\ast)^{-1}\right]^{-1},
+\tau = N_\text{source} \left[\sum_{\mathbf{s} \in \text{Source}} (\tau_\mathbf{s}^\ast)^{-1}\right]^{-1},
+\label{eq:ToF}
 \end{equation}
-with $N_\text{source}$ the number of source states.
+where $N_\text{source}$ is the number of Source states.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
+\section{Results on BCP}
 \label{sec:result}
 
-\subsection{Distribution Distance and ToF Differences}
-A summary of the Time-of-Flight (ToF) and molecular energies using different functionals is provided in Table \ref{tab:para}, with the drift ToF detailed in Table \ref{tab:para2}.
-The tables indicate that while the energy standard deviations $\sigma(E)$ are similar across different functionals, the ToF values vary significantly, notably for functionals like BHANDHLYP, M06L, and BHLYP.
+A OSC device consisting of 1000 BCP molecules arranged in $8 \times 8 \times 8$ cubic box is simulated using MD, as shown in Fig. \ref{fig:MSM}(a).
+The \textit{Source} contains molecules whose COM have X-coordinates $0 < r^x_i < 0.5$ nm, and \textit{Sink} molecules $7.5 < r^x_i < 8$. 
+This section presents the molecule energy distribution, coupling element distribution, reorganization energies and ToFs calculated using the 12 DFT functionals. 
+Using the PBE0 functional as a reference, the difference in electronic structure distributions due to DFT functionals is measured by the Wasserstein distance.
+In contrast to the small Wasserstein distance between the electronic structure distributions, the difference in ToF $\Delta \tau$ is relatively large.
+Next, the change of the graph connectivity due to different DFT functionals is used to explain the $\Delta \tau$.
+Following this, a normal distribution estimated from maximum likelihood is used to represent the uncertainty in each electronic structure parameters.
+Then distributions of ToF are obtained using the electronic structure parameters generated by Monte Carlo sampling from the estimated distributions.
+Finally, the sensitivities of $E_i,J_{i,j},\lambda_{i,j}$ to ToF are compared, confidence level of ToFs are estimated.
+
+\subsection{Electronic Structure Parameters and ToFs}
+Using ten different functionals, the molecule energies, coupling elements and reorganization energies are calculated from the multiscale model with ten different DFT functional.
+
+Table \ref{tab:para} summarizes the names of the DFT functionals, the amount of Hartree-Fock exchange (HFX), the reorganization energies, ToFs, the standard deviation of the molecule energy distributions, the drift ToFs under an electric field $6 \times 10^7$ V/m and mobility.
+The table indicates that while the energy standard deviations $\sigma(E)$ are similar across different functionals, the ToF vary significantly, notably for functionals like BHANDHLYP, M06L, and BHLYP.
 
@@
     \centering
-    \begin{tabular}{c c c c c }
+    \begin{tabular}{c c c c c c c}
     \hline
-        Functional & ScaleHFX & $\lambda_h$ [eV] & ToF [s] & $\sigma(E)$ \\ 
+        Functional & HFX & $\lambda_{i,j}$ [eV] & ToF [s] & $\sigma(E)$ & drift ToF [s] & $\mu$ [m/s] \\ 
         \hline
-        PBE0 & 0.25 & 0.388 & 1.23e-3 & 0.175 \\
-        PBE & 0 & 0.303 & 1.04e-3 & 0.172 \\ 
-        B3LYP & 0.20 & 0.375 & 4.28e-3 & 0.175 \\
-        BHANDHLYP & 0.5 & 0.494 & \textbf{737.94} & 0.192 \\
-        TPSS & 0 & 0.310 & 1.37e-2 & 0.168 \\
-        BP86 & 0 & 0.304 & 7.46e-3 & 0.175 \\
-        wB97X & 0.157 & 0.505 & 2.92e-2 & 0.191 \\
-        wB97X-D3 & 0.195 & 0.496 & 4.89e-2 & 0.180 \\
-        M06L & 0 & 0.312 & 3.19e-1 & 0.165 \\
-        BHLYP & 0.5 & 0.493 & 2.47 & 0.192 \\
+        PBE0 & 0.25 & 0.388 & $1.23\times 10^{-3}$ & 0.175 & $1.44 \times 10^{-6}$ & $9.40\times 10^{-7}$ \\
+        PBE & 0 & 0.303 & $1.04\times 10^{-3}$ & 0.172 & $2.27 \times 10^{-7}$ & $5.95 \times 10^{-6}$ \\ 
+        B3LYP & 0.20 & 0.375 & $4.28\times 10^{-3}$ & 0.175  & $3.22\times 10^{-7}$ & $4.08 \times 10^{-6}$ \\
+        BHANDHLYP & 0.5 & 0.494 & \textbf{737.94} & 0.192  & $4.75\times 10^{-2}$ & $2.86\times 10^{-11}$ \\
+        TPSS & 0 & 0.310 & $1.37\times 10^{-2}$ & 0.168  & $1.03 \times 10^{-6}$ & $1.30\times 10^{-7}$ \\
+        BP86 & 0 & 0.304 & $7.46\times 10^{-3}$ & 0.175  & $5.81 \times 10^{-7}$ & $2.33\times 10^{-6}$ \\
+        wB97X & 0.157 & 0.505 & $2.92\times 10^{-2}$ & 0.191  & $2.01\times 10^{-6}$  & $6.74\times 10^{-7}$ \\
+        wB97X-D3 & 0.195 & 0.496 & $4.89\times 10^{-2}$ & 0.180  & $2.50 \times 10^{-6}$ & $5.42 \times 10^{-7}$ \\
+        M06L & 0 & 0.312 & 0.319 & 0.165 & $2.11 \times 10^{-5}$ & $6.42 \times 10^{-8}$ \\
+        BHLYP & 0.5 & 0.493 & 2.47 & 0.192  & $5.96 \times 10^{-5}$ & $ 2.28\times 10^{-8}$  \\
     \hline
     \end{tabular}
-    \caption{Values of $\lambda_h$, ToF, stationary state velocity, and energy standard deviation of BCP molecules calculated from different functionals.}
+    \caption{DFT functional HF exchange scaling (HFX), calculated values of reorganization energy ($\lambda_{i,j}$), diffusive ToF, energy disorder ($\sigma(E)$), drift ToF, and mobility ($\mu$) for BCP molecules for different DFT functionals.}
     \label{tab:para}
@@
 
+The functional BHANDHLYP gives a ToF much larger than the rest of the 9 functionals. 
+The reason for this large ToF in BHANDHLYP is that one molecule has relatively low energy, and the out-going rate for this molecule is very small, eventually leading to large ToF. 
+However, such large difference in a material system is non-physical, and studying the uncertain quantification based on those ToF data can not indicate anything on the robustness of the multiscale model.
+
+A noticeable difference in all the different functional is the amount of HF for approximating the exchange-correlations.
+
+So by fixing the functional to be the commonly used PBE0 functional, the HFX is varied to investigate the effect of HFX to the molecular properties and ToF. 
+Hybrid functionals like PBE0 or B3LYP use a specific, empirically determined fraction of HF exchange that generally works well for a broad range of applications.
+PBE0 is constructed by combining 25\% of the exact exchange from HF theory with 75\% of the exchange from the Perdew-Burke-Ernzerhof (PBE) GGA exchange functional, along with the full PBE correlation functional.
+
+When correlation effects are strong and electron-electron interactions play a significant role in determining their physical properties, the exact exchange overly localize electrons, and a lower HFX percentage or even pure DFT might perform better.
+The $\pi$-electron conjugation and interactions in OSC such as BCP and MADN leads to significant electronic correlation effects within those materials.
+
+\subsection{BCP molecule with different HFX}
+So our first investigation use the range of HFX=$0.05,0.15,0.23,0.24,0.25,0.26,0.27,0.35,0.45,0.55$.
+The values of HFX=$0.23,0.24,0.26,0.27$ are used because we want to see if a small perturbation in HFX would affect ToF significantly.
+
+Since ToF is sensitively affected by site energy, which is affected by the isotropic polarizability $P_\text{iso}$ and dipole moment $\mu$ of the molecules, we plot the those molecular properties as a function of HFX.
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.9\textwidth]{figs/BCP_HFX/fig_autogen_BCP.png}
+    \caption{(a) The neutral state BCP molecule dipole moment $\mu$, (b) isotropic polarizability $P_\text{iso}$, (c) reorganization energies $\lambda$ and (d) energy disorder $\sigma(E)$ as a function of the HFX parameters.
+}
+    \label{fig:autogen}
+\end{figure}
+The Fig.\ref{fig:autogen}(a) shows that as HFX increase, the dipole moment increases first linear in the range of HFX=0.05 to 0.35, then a relatively large increase at HFX=0.35 to 0.55.
+
+Figure \ref{fig:autogen}(b) shows that as HFX increase, the n state and h state BCP molecule has decreasing isotropic polarizability, showing that the molecule is getting more difficult to be polarized.
+Since the isotropic polarizability is decreasing as HFX increases, the screening effects are weaker for large HFX.
+
+Fig.\ref{fig:autogen}(c) shows that as HFX increase, reorganization energies are higher.
+Since the molecule requires more energy to reorient itself during the charge transfer process, the higher reorganization energy can slow down charge transport by making it energetically more costly for charges to move between molecules.
+
+Fig.\ref{fig:autogen}(d) shows that when HFX=0.05-0.3 the energy disorder is relatively small (less than 0.2 eV). When HFX=0.35-0.55, the energy disorder $\sigma(E)>0.22$.
+
+The ToF of the BCP molecular system calculated using different HFX is shown in table \ref{tab:ToF_BCP_HFX}.
+This table shows that for HFX=0.35,0.45,0.55, the ToFs are extremely large compared to the ToFs for HFX<0.3.
+In contrast to the almost linear HFX-$\lambda$ relationship, those large ToFs are not physical.
+
 \begin{table}[h]
     \centering
-    \begin{tabular}{c c c}
+    \begin{tabular}{c c c }
     \hline
-        Functional & ToF [s] & $\mu$ [m/s] \\ 
+        HFX & ToF [s] & ToF(no $E$) [s] \\
     \hline
-        PBE0 & 2.39e-8 & 5.68e-5 \\
-        PBE & 6.03e-9 & 2.25e-4 \\ 
-        B3LYP & 1.67e-8 & 8.13e-5 \\
-        BHANDHLYP & 3.36e-4 & 4.04e-9 \\
-        TPSS & 1.23e-8 & 1.10e-4 \\
-        BP86 & 3.77e-7 & 3.59e-6 \\
-        wB97X & 1.68e-6 & 8.08e-7 \\
-        wB97X-D3 & 6.92e-7 & 1.96e-6 \\
-        M06L & 3.90e-3 & 3.47e-10 \\
+        0.05 &  0.32010 & $3.004 \times 10^{-10}$ \\
+        0.15 & 0.3879 & $4.668 \times 10^{-10}$ \\
+        0.23 & 0.0200 & $6.787 \times 10^{-10} $ \\
+        0.24 & 0.02977 & $7.0290 \times 10^{-10} $ \\
+        0.25 & 0.02648 & $7.633 \times 10^{-10}$ \\
+        0.26 & 3.259 & $7.824 \times 10^{-10}$ \\
+        0.27 & 0.0359 &  $9.162 \times 10^{-10}$ \\
+        0.35 & $1.72 \times 10^7 $ & $1.00 \times 10^{-9}$ \\
+        0.45 & $1.8 \times 10^4$ & $1.32\times 10^{-9}$ \\
+        0.55 & $1.23 \times 10^9 $ & $1.880 \times 10^{-9} $ \\
     \hline
     \end{tabular}
-    \caption{Mobility and ToF with drift electric field $6 \times 10^7$ V/m.}
-    \label{tab:para2}
+    \caption{The ToF with and without energy disorder of the BCP system as a function of the HFX. }
+    \label{tab:ToF_BCP_HFX}
 \end{table}
 
+The reason for this non-physical ToF is that the site energy calculation use the atomic charges and molecular polarizability from the optimized BCP structure.
+However, each molecule in the BCP system has its own topology with different atomic charges and polarizability compared to the optimized BCP structure.
+Those difference in atomic charges and polarizability affect the site energy calculations.
+
+So the atomic charges and polarizability in the optimized structure can not be transferred to the BCP molecules generated from the MD simulation. 
+For very disorder material system such as BCP, using the atomic charges and polarizability in the optimized structure can result in site energies that are deviated from the majority of the molecules.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.95\textwidth]{figs/BCP_HFX/scatterE_qmmm.png}
+    \caption{Scatter plot of site energy calculated from different HFX, compared to the site energy calculated from HFX=0.25 (The PBE0 functional).
+The brighter color near the diagonal lines indicates denser population of the molecules.
+The top and right histogram show the energy distributions.}
+    \label{fig:E_qmmm_BCP}
+\end{figure}
+
+Figure \ref{fig:E_qmmm_BCP} shows that for HFX<0.3, the site energies of all molecules are relatively close to the site energy obtained from PBE0 functional.
+When HFX=0.35, 0.45, 0.55, there are obvious low-energy molecules.
+Those low molecules results in the large energy disorder $\sigma(E)$ as shown in table \ref{tab:para}. 
+For those three systems the ToFs are extremely large.
+
+The site energy has the contribution from the electrostatic effect and polarization effect due to the dipole moment of the molecules. 
+The Heat map of the electrostatic energy and polarization energy are shown in Fig.\ref{fig:Estat_qmmm_BCP} and Fig.\ref{fig:Edip_qmmm_BCP}.
+
+Figure \ref{fig:Estat_qmmm_BCP} shows that for all HFX parameters, the electrostatic energy are relatively close, while Fig.\ref{fig:Edip_qmmm_BCP} shows that for HFX=0.35,0.45,0.55, there are molecules that have small polarization energy, contributing to the small site energies, and the extremely large ToF.
+Those small polarization energies and site energies are not physical. 
+When HFX is varied, the change of the polarizability and reorganization energy are almost linear, while there is huge jumps in those site energies due to the huge jumps in the polarization energy.
+
+So for correlated system such as OSCs, large range of HFX leads to non-physical results. 
+In the next section, we will use the range with small HFX values for the investigation of a less disorder molecular system, MADN.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.95\textwidth]{figs/BCP_HFX/scatterEstat_qmmm.png}
+    \caption{Scatter plot of electrostatic energy calculated from different HFX, compared to the electrostatic energy calculated from HFX=0.25 (The PBE0 functional).
+The brighter color near the diagonal lines indicates denser population of the molecules.
+The top and right histogram show the energy distributions.}
+    \label{fig:Estat_qmmm_BCP}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.95\textwidth]{figs/BCP_HFX/scatterEdip_qmmm.png}
+    \caption{Scatter plot of polarization energy calculated from different HFX, compared to the polarization energy calculated from HFX=0.25 (The PBE0 functional).
+The brighter color near the diagonal lines indicates denser population of the molecules.
+The top and right histogram show the energy distributions.}
+    \label{fig:Edip_qmmm_BCP}
+\end{figure}
+
+\section{Results on MADN}
+MADN (2-Methyl-9,10-di(naphth-2-yl)anthracene) is another type of OSC. 
+The ToFs with and without energy disorder for HFX = 0.0, 0.05, 0.10, 0.15, 0.20, 0.25 are shown in 
+\begin{table}[h]
+    \centering
+    \begin{tabular}{c c c }
+    \hline
+        HFX & ToF [s] & ToF(no $E$) [s] \\
+    \hline
+        0.00 &  $6.41 \times 10^{-9}$ & $1.88 \times 10^{-10}$ \\
+        0.05 & $ 6.37 \times 10^{-9}$ (estimate) & $2.63 \times 10^{-10}$ \\
+        0.10 & $ 1.74 \times 10^{-8}$ (estimate) & $3.31 \times 10^{-10} $ \\
+        0.15 & $ 3.03 \times 10^{-8}$ & $3.96 \times 10^{-10} $ \\
+        0.20 & $ 2.61 \times 10^{-8}$ (estimate) & $7.06 \times 10^{-10}$ \\
+        0.25 & $ 9.54 \times 10^{-8}$ & $7.24 \times 10^{-10}$ \\
+    \hline
+    \end{tabular}
+    \caption{The ToF with and without energy disorder of the MADN system as a function of the HFX. }
+    \label{tab:ToF_MADN_HFX}
+\end{table}
+
+\bibliographystyle{unsrt}
+\bibliography{references}
+
+\begin{comment}
 \textbf{Point 1:} To investigate the effect of different functionals $f^\text{DFT}$ on electronic structures, we compare the energies $E_i$ and couplings $J_{i,j}$ for all molecule indices $i,j$.
@@
 Since the normal distribution inserts the least amount of prior knowledge into a model and encodes the maximum amount of uncertainty, we want to quantify the uncertainty when those error terms are normally distributed.
-%\bibliographystyle{unsrt}
-%\bibliography{references}
+\end{comment}
 

### 2024-10-02 paper.tex
update

@@
 \usepackage[final]{hyperref} % adds hyper links inside the generated pdf file
+
+\usepackage{booktabs}
+
 \hypersetup{
@@
 \linenumbers
-\title{Uncertain Effects of DFT Functionals on Time-of-flight Calculations of Organic semiconductor }
+\title{Uncertain Effects of DFT Functionals on Charge Dynamic of Organic Semiconductor }
 \author{authors}
@@
 \section{Introduction}
+
+Theoretical model and computer simulation for understanding a physical system must contain some uncertainties in predicting the system features. 
+For example, the theoretical model does not encompass all relevant physical factors, the theoretical model incorporates empirical parameters that include noise, the numerical scheme contains approximation, etc.
+Nevertheless, those uncertainties should not affect the validity of the model or the accuracy for the predicting system in terms of some quantities of interest (QoI). 
+Here the terminology "uncertainties" refers to the impossibility of getting a deterministic QoI, and excludes theoretical or numerical errors.
+
+In this work, an investigated model containing uncertainties is the first-principle multiscale model for charge dynamics in organic semiconductors (OSCs).
+From a broad perspective, this model contains uncertainties due to the limitation of the model, the randomness nature of the QoI, and the limitation of the numerical simulations.
+
+To explain in detail those uncertainties, the first-principle multiscale model is briefly reviewed. 
+Fundamentally, quantum-mechanical description is needed to model charge dynamics due to the motion of electrons.
+However, the resulting full many-electron schr\"{o}dinger equation is too complex to solve due to complexity, so Density Functional Theory (DFT) appears as a manageable way to model electrons.
+DFT has its own challenges that introduce uncertainties into the first-principle multiscale model. 
+{\huge Here}
+
+A commonly used model for theoretical investigation of organic semiconductors is the first-principle multiscale model, which contains uncertainties in terms of the comprehensiveness of the theory, the mo
+
 Random walks in random environments (RWRE) are widely used to model physical processes, incorporating the varying levels of disorder and environmental factors that influence movement. 
@@
 
-\begin{table}[h]
+\begin{table}[H]
     \centering
@@
 Since ToF is sensitively affected by site energy, which is affected by the isotropic polarizability $P_\text{iso}$ and dipole moment $\mu$ of the molecules, we plot the those molecular properties as a function of HFX.
-\begin{figure}[h]
+\begin{figure}[H]
     \centering
-    \includegraphics[width=0.9\textwidth]{figs/BCP_HFX/fig_autogen_BCP.png}
+    \includegraphics[width=0.9\textwidth]{figs/BCP_HFX/fig_autogen_BCP.pdf}
     \caption{(a) The neutral state BCP molecule dipole moment $\mu$, (b) isotropic polarizability $P_\text{iso}$, (c) reorganization energies $\lambda$ and (d) energy disorder $\sigma(E)$ as a function of the HFX parameters.
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
     \centering
-    \includegraphics[width=0.95\textwidth]{figs/BCP_HFX/scatterE_qmmm.png}
-    \caption{Scatter plot of site energy calculated from different HFX, compared to the site energy calculated from HFX=0.25 (The PBE0 functional).
+    \includegraphics[width=0.95\textwidth]{figs/BCP_HFX/scatterE_qmmm.pdf}
+    \caption{Scatter plot of BCP site energy calculated from different HFX, compared to the site energy calculated from HFX=0.25 (The PBE0 functional).
 The brighter color near the diagonal lines indicates denser population of the molecules.
@@
 
-Figure \ref{fig:E_qmmm_BCP} shows that for HFX<0.3, the site energies of all molecules are relatively close to the site energy obtained from PBE0 functional.
-When HFX=0.35, 0.45, 0.55, there are obvious low-energy molecules.
+Figure \ref{fig:E_qmmm_BCP} shows that for HFX$<0.3$, the site energies of all molecules are relatively close to the site energy obtained from PBE0 functional.
+When HFX=0.35, 0.45, 0.55, there are obvious low-energy molecules as shown by the points below the diagonal line.
 Those low molecules results in the large energy disorder $\sigma(E)$ as shown in table \ref{tab:para}. 
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
     \centering
-    \includegraphics[width=0.95\textwidth]{figs/BCP_HFX/scatterEstat_qmmm.png}
-    \caption{Scatter plot of electrostatic energy calculated from different HFX, compared to the electrostatic energy calculated from HFX=0.25 (The PBE0 functional).
+    \includegraphics[width=0.95\textwidth]{figs/BCP_HFX/scatterEstat_qmmm.pdf}
+    \caption{Scatter plot of BCP electrostatic energy calculated from different HFX, compared to the electrostatic energy calculated from HFX=0.25 (The PBE0 functional).
 The brighter color near the diagonal lines indicates denser population of the molecules.
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
     \centering
-    \includegraphics[width=0.95\textwidth]{figs/BCP_HFX/scatterEdip_qmmm.png}
-    \caption{Scatter plot of polarization energy calculated from different HFX, compared to the polarization energy calculated from HFX=0.25 (The PBE0 functional).
+    \includegraphics[width=0.95\textwidth]{figs/BCP_HFX/scatterEdip_qmmm.pdf}
+    \caption{Scatter plot of BCP polarization energy calculated from different HFX, compared to the polarization energy calculated from HFX=0.25 (The PBE0 functional).
 The brighter color near the diagonal lines indicates denser population of the molecules.
@@
 The ToFs with and without energy disorder for HFX = 0.0, 0.05, 0.10, 0.15, 0.20, 0.25 are shown in 
-\begin{table}[h]
+\begin{table}[H]
     \centering
@@
         0.00 &  $6.41 \times 10^{-9}$ & $1.88 \times 10^{-10}$ \\
-        0.05 & $ 6.37 \times 10^{-9}$ (estimate) & $2.63 \times 10^{-10}$ \\
-        0.10 & $ 1.74 \times 10^{-8}$ (estimate) & $3.31 \times 10^{-10} $ \\
+        0.05 & $ 7.86 \times 10^{-9}$ & $4.07 \times 10^{-10}$  \\
+        0.10 & $ 1.56 \times 10^{-8}$ & $3.97 \times 10^{-10} $  \\
         0.15 & $ 3.03 \times 10^{-8}$ & $3.96 \times 10^{-10} $ \\
-        0.20 & $ 2.61 \times 10^{-8}$ (estimate) & $7.06 \times 10^{-10}$ \\
+        0.20 & $ 2.05 \times 10^{-8}$ & $4.48 \times 10^{-10}$  \\
         0.25 & $ 9.54 \times 10^{-8}$ & $7.24 \times 10^{-10}$ \\
@@
 \end{table}
+
+%
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.80\textwidth]{figs/MADN_HFX/fig_autogen.pdf}
+    \caption{(a) The dipole moment of neutral state MAND molecule $\mu$, (b) isotropic polarizability $P_\text{iso}$, (c) reorganization energies $\lambda$ and (d) energy disorder $\sigma(E)$ as a function of the HFX parameters.}
+    \label{fig:autogen_MADN}
+\end{figure}
+% 
+As HFX increase from 0 to 0.25, the ToF with and without energy disorder increase eventually by a factor of 10. 
+The dipole moment of the neutral state molecule, isotropic polarizability, and reorganization energies are shown in Fig.\ref{fig:autogen_MADN}.
+The dipole moment decrease as HFX increase as shown by Fig.\ref{fig:autogen_MADN}(a).
+At HFX=0.25, there is a relatively sharp decrease.
+The dipole moment decreases as the HFX increase, this HFX effect on dipole moment is different that of the BCP molecule, which has the dipole moment increases as the HFX increases.
+
+Fig.\ref{fig:autogen_MADN}(b) shows that the isotropic polarizability for n,e,h state MADN molecule decrease linearly as HFX increase from 0 to 0.25. 
+So the molecules are getting more difficult to be polarized. 
+Accordingly, the reorganization energy also increases as HFX increases as shown by Fig.\ref{fig:autogen_MADN}(c).
+This increase is nonlinear compared to the linear increase of BCP reorganization energy in the range HFX=0.05 to 0.25.
+
+All the sites energies are relatively close with varying HFX as revealed by the similar energy disorder $\sigma(E)$.
+The scatter plot of site energies compared to that of PBE0 are shown in Fig.\ref{fig:E_qmmm_MADN}.
+The scatter plots of the electrostatic energy and polarization energy are also close for different HFX, as shown in Fig.
+\ref{fig:Estat_qmmm_MADN} and \ref{fig:Edip_qmmm_MADN}.
+All of those close energies leads to the close ToF shown in Table \ref{tab:ToF_MADN_HFX}.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.95\textwidth]{figs/MADN_HFX/scatterE_qmmm.pdf}
+    \caption{Scatter plot of site energy of MADN molecules calculated from different HFX, compared to the site energy calculated from HFX=0.25 (The PBE0 functional).
+The brighter color near the diagonal lines indicates denser population of the molecules.
+The top and right histogram show the energy distributions.}
+    \label{fig:E_qmmm_MADN}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.95\textwidth]{figs/MADN_HFX/scatterEstat_qmmm.pdf}
+    \caption{Scatter plot of MADN electrostatic energy calculated from different HFX, compared to the electrostatic energy calculated from HFX=0.25 (The PBE0 functional).
+The brighter color near the diagonal lines indicates denser population of the molecules.
+The top and right histogram show the energy distributions.}
+    \label{fig:Estat_qmmm_MADN}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.95\textwidth]{figs/MADN_HFX/scatterEdip_qmmm.pdf}
+    \caption{Scatter plot of MADN polarization energy calculated from different HFX, compared to the polarization energy calculated from HFX=0.25 (The PBE0 functional).
+The brighter color near the diagonal lines indicates denser population of the molecules.
+The top and right histogram show the energy distributions.}
+    \label{fig:Edip_qmmm_MADN}
+\end{figure}
+
+\section{Diffusive Charge velocity Estimation}
+The following table shows the diffusive charge velocity, calculated using the ToF setting and steady state setting.
+For ToF setting, we investigate the situations where the charge transport direction is along the X-axis, Y-axis and Z-axis.
+\begin{table}[htbp]
+\centering
+\begin{tabular}{c c c c c c c}
+    \toprule
+     &
+        \multicolumn{3}{c}{ with energy $E$} &
+        \multicolumn{3}{c}{all $E=0$}  \\
+    HFX & MADN & BCP & ratio & MADN & BCP & ratio  \\
+    \cmidrule(r){1-7}
+    0.05 & $7.87 \times 10^{-9}$ & 0.32 & 0 & $4.07 \times 10^{-10}$ & $3.00 \times 10^{-10}$ & 0 \\
+    0.15 & $3.03 \times 10^{-8}$ & 0.38 & 0 & $3.96 \times 10^{-10}$ & $4.67 \times 10^{-10}$ & 0 \\
+    0.25 & $9.54 \times 10^{-8}$ & 0.026 & 0 & $7.24 \times 10^{-10}$ & $7.63 \times 10^{-10}$ & 0 \\
+    \bottomrule
+    \end{tabular}
+    \caption{Diffusive $\tau_X$ comparison between multiscale modeled BCP and MADN molecular system with PBE0 functional. }
+\end{table}
+
+\begin{table}[htbp]
+\centering
+\begin{tabular}{c c c c c c c}
+    \toprule
+        &
+        \multicolumn{3}{c}{ with energy $E$} &
+        \multicolumn{3}{c}{all $E=0$}  \\
+    HFX & MADN & BCP & ratio & MADN & BCP & ratio  \\
+    \cmidrule(r){1-7}
+    0.05 & 1.0 & $2.2 \times 10^{-8}$ & 0 & 19 & 24 & 0 \\
+    0.15 & 0.26 & $1.8 \times 10^{-8}$ & 0 & 20 & 15 & 0 \\
+    0.25 & 0.083 & $2.7 \times 10^{-7}$ & 0 & 11 & 9.4 & 0 \\
+    \bottomrule
+    \end{tabular}
+    \caption{Diffusive ToF velocity $v_\text{ToF,X}=\frac{L_X}{\tau_X}$ [m/s] comparison between multiscale modeled BCP and MADN molecular system with PBE0 functional. }
+\end{table}
+
+\begin{table}[htbp]
+\centering
+\begin{tabular}{c c c c c c c}
+    \toprule
+        &
+        \multicolumn{3}{c}{ with energy $E$} &
+        \multicolumn{3}{c}{all $E=0$}  \\
+    HFX & MADN & BCP & ratio & MADN & BCP & ratio  \\
+    \cmidrule(r){1-7}
+    0.05 & 0.44 & $5.8 \times 10^{-8}$ & 0 & 17 & 24 & 0 \\
+    0.15 & 0.057& $1.0 \times 10^{-7}$  & 0 & 17 & 15 & 0 \\
+    0.25 & 0.041 & $2.8 \times 10^{-7}$ & 0 & 10 & 9.5 & 0 \\
+    \bottomrule
+    \end{tabular}
+    \caption{Diffusive ToF velocity $v_\text{ToF,Y}=\frac{L_Y}{\tau_Y}$ [m/s] comparison between multiscale modeled BCP and MADN molecular system with PBE0 functional. }
+\end{table}
+
+\begin{table}[htbp]
+\centering
+\begin{tabular}{c c c c c c c}
+    \toprule
+        &
+        \multicolumn{3}{c}{ with energy $E$} &
+        \multicolumn{3}{c}{all $E=0$}  \\
+    HFX & MADN & BCP & ratio & MADN & BCP & ratio  \\
+    \cmidrule(r){1-7}
+    0.05 & 2.0 & $5.6 \times 10^{-7}$ & 0 & 19 & 24 & 0 \\
+    0.15 & 2.6 & $1.2 \times 10^{-6}$ & 0 & 19 & 15 & 0 \\
+    0.25 & 1.0 & $5.4 \times 10^{-6}$ & 0 & 10 & 9.4 & 0 \\
+    \bottomrule
+    \end{tabular}
+    \caption{Diffusive ToF velocity $v_\text{ToF,Z}=\frac{L_Z}{\tau_Z}$ [m/s] comparison between multiscale modeled BCP and MADN molecular system with PBE0 functional. }
+\end{table}
+
+\begin{table}[htbp]
+\centering
+\begin{tabular}{c c c c c c c}
+    \toprule
+        &
+        \multicolumn{3}{c}{ with energy $E$} &
+        \multicolumn{3}{c}{all $E=0$}  \\
+    HFX & MADN & BCP & ratio & MADN & BCP & ratio  \\
+    \cmidrule(r){1-7}
+    0.05 & 0.10 & $1.5 \times 10^{-7}$ & 0 & 3.8 & 2.4 & 0 \\
+    0.15 & 0.031 & $1.5 \times 10^{-8}$ & 0 & 13 & 0.58 & 0 \\
+    0.25 & 0.0043 & $3.6 \times 10^{-7}$ & 0 & 4.0 & 1.07 & 0 \\
+    \bottomrule
+    \end{tabular}
+    \caption{Steady state diffusive velocity $v_\text{SS}$ [m/s] comparison between multiscale modeled BCP and MADN molecular system with PBE0 functional. }
+\end{table}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The ToF is estimated from electronic structure ($E$, $\lambda$ and $\log_{10}(J^2)$) data obtained using different HFX. Each HFX gives an electronic structure. 
+For the BCP systems:
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.85\textwidth]{figs/BCP_HFX/fig_mle_BCP_withE.pdf}
+    \caption{Distribution of ToFs in the multiscale modeled BCP system using PBE0 functional when (a) the molecule site energy $E$ are sampled from a normal distribution $E \sim N(E_\text{ave},E^2_\text{std})$, (b) the reorganization energy $\lambda$ are sampled from a normal distribution $\lambda \sim N(\lambda_\text{ave},\lambda^2_\text{std})$, (c) the quantity $\log_{10}(J^2)$ are sampled from a normal distribution $\log_{10}(J^2) \sim N(\mathbb{E}[\log_{10}(J^2)], \textbf{Var}[\log_{10}(J^2)] )$.
+(d) Both $E$, $\lambda$ and $\log_{10}(J^2)$ are sampled from the normal distribution.
+}
+    \label{fig:mle_BCP_withE}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.99\textwidth]{figs/BCP_HFX/fig_mle_BCP_noE.pdf}
+    \caption{Distribution of ToFs in the multiscale modeled BCP system using PBE0 functional. All molecule energies are set to be zero.  
+    The plots are for the situation: (a) The reorganization energy $\lambda$ are sampled from a normal distribution $\lambda \sim N(\lambda_\text{ave},\lambda^2_\text{std})$.
+(b) the quantity $\log_{10}(J^2)$ are sampled from a normal distribution $\log_{10}(J^2) \sim N(\mathbb{E}[\log_{10}(J^2)], \textbf{Var}[\log_{10}(J^2)] )$.
+(c) Both $\lambda$ and $\log_{10}(J^2)$ are sampled from the normal distribution.
+}
+    \label{fig:mle_BCP_noE}
+\end{figure}
+
+For the MADN system:
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.85\textwidth]{figs/MADN_HFX/fig_mle_MADN_withE.pdf}
+    \caption{Distribution of ToFs in the multiscale modeled MADN system using PBE0 functional when (a) the molecule site energy $E$ are sampled from a normal distribution $E \sim N(E_\text{ave},E^2_\text{std})$, (b) the reorganization energy $\lambda$ are sampled from a normal distribution $\lambda \sim N(\lambda_\text{ave},\lambda^2_\text{std})$, (c) the quantity $\log_{10}(J^2)$ are sampled from a normal distribution $\log_{10}(J^2) \sim N(\mathbb{E}[\log_{10}(J^2)], \textbf{Var}[\log_{10}(J^2)] )$.
+(d) Both $E$, $\lambda$ and $\log_{10}(J^2)$ are sampled from the normal distribution.
+}
+    \label{fig:mle_MADN_withE}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.99\textwidth]{figs/MADN_HFX/fig_mle_MADN_noE.pdf}
+    \caption{Distribution of ToFs in the multiscale modeled MADN system using PBE0 functional. All molecule energies are set to be zero.  
+    The plots are for the situation: (a) The reorganization energy $\lambda$ are sampled from a normal distribution $\lambda \sim N(\lambda_\text{ave},\lambda^2_\text{std})$.
+(b) the quantity $\log_{10}(J^2)$ are sampled from a normal distribution $\log_{10}(J^2) \sim N(\mathbb{E}[\log_{10}(J^2)], \textbf{Var}[\log_{10}(J^2)] )$.
+(c) Both $\lambda$ and $\log_{10}(J^2)$ are sampled from the normal distribution.
+}
+    \label{fig:mle_MADN_noE}
+\end{figure}
 

### 2024-10-08 paper.tex
update

@@
 However, the resulting full many-electron schr\"{o}dinger equation is too complex to solve due to complexity, so Density Functional Theory (DFT) appears as a manageable way to model electrons.
-DFT has its own challenges that introduce uncertainties into the first-principle multiscale model. 
-{\huge Here}
+DFT has its own challenges in achieving multiscale modeling.
 
-A commonly used model for theoretical investigation of organic semiconductors is the first-principle multiscale model, which contains uncertainties in terms of the comprehensiveness of the theory, the mo
+The first challenge relates to the Born-Oppenheimer approximation in quantum
+mechanics, which simplifies the problem by separating the electronic and nuclear
+coordinates.
+As a result, the time evolution of the atomic coordinates can be modeled by solving the Newton's equation using empirical force field to approximate the potential energy surfaces (need citation).
 
-Random walks in random environments (RWRE) are widely used to model physical processes, incorporating the varying levels of disorder and environmental factors that influence movement. 
-These disorders and environmental factors can introduce a level of uncertainty that significantly impacts the overall rates of the random walk, ultimately affecting the quantities of interest one aims to obtain.
+The next challenge is the infeasibility of solving the DFT equations for the entire system even at a fixed time.
+To address this challenge, state localization is used and the electron's wavefunction becomes localized in space around the nuclei.
+As a result, the charge dynamic is modeled as a continuous time random walk (CTRW) process, with transition rates between the molecules determined by their electronic structures, namely, the molecule energy, reorganization energy and coupling elements which will be explained in the methodology section.
 
-A notable example of RWRE is charge transport in organic semiconductors (OSCs), characterized by an amorphous mesoscopic structure due to spatially disordered molecular arrangements. 
-This structural disorder translates into electronic structure disorder, including energy disorder and coupling element disorder, leading to the modeling of charge transport processes as continuous time random walks (CTRWs) on a graph.
-Specifically, the molecules can be represented as nodes in a graph, the transition rates between them (edge weights) correspond to the transition rates between the molecules, and the charge carriers become the random walkers.
-The details of specifying the graph will be introduced in the Section 2.
-The uncertainty from electronic structure disorder and environmental factors is reflected in these transition rates.
+In brief summary, the multiscale model can be summarized in Fig. \ref{fig:MSM}.
+The process includes: Firstly, classical Molecular Dynamics is used to generate the atomistic coordinates.
+Then DFT is used to attain electronic structures.
+Finally the charge dynamic is model as a CTRW among the molecules.
 
-While the transition rates in those CTRWs can be calculated in a first-principle multiscale approach, but it involves some level of approximations. 
-Since the charge transport in OSC involves electrons, quantum mechanics and Schr\"odinger equation are essential in providing a time-series behavior of the charge dynamics. 
-But due to the complexity of Schr\"odinger Equation, one alternative theory is the density functional theory (DFT). 
-DFT faces two main challenges: it is computationally impractical for entire OSC devices and the exchange-correlation potential lacks an explicit formula.
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.95\textwidth]{figs/MSM.png}
+    \caption{The multiscale model workflow for OSC.
+Step 1: MD simulation to generate atom coordinates.
+Step 2: Molecule energy $E_i$ calculation.
+Step 3: Calculation of Reorganization energy $\lambda_{i,j}$ and coupling element $J_{i,j}$ for pairs of molecule $i,j$ whose COM distance is less than $r_\text{cutoff}$.
+Step 4: Modelling dynamics on device level, such as ToF calculation.}
+    \label{fig:MSM}
+\end{figure}
 
-The first challenge is mitigated by approximating electron dynamics as transition processes between localized states which contain most of the molecular electron, with transition rates calculated using the temperature-activated bi-molecular Marcus rate.
-The second challenge is addressed by employing DFT functionals to approximate the exchange-correlation potential. 
-Despite benchmark results on molecular energy calculations with various DFT functionals and extensive literature on charge transport in multiscale models of OSCs, there is a lack of quantitative studies on how DFT functionals affect charge transport processes, and the influence of uncertainty in electronic structure properties.
+In overcoming the challenges and achieving the multiscale model, uncertainties are introduced.
 
-Several challenges arise in this investigation.
-The high dimensionality of CTRWs (due to the large number of molecules, typically around 1000) makes uncertainty quantification numerically challenging.
-Secondly, simulating CTRWs is also computationally demanding due to convergence issues.
-Additionally, the exact DFT exchange-correlation functional and the distribution of transition rates for specific molecules are unknown.
+While Born-Oppenheimer approximation allows for the use of force field to approximate the potential energy surfaces (need citation) and model the atomic coordinates using Newton’s equations, the atomic coordinates are not exactly the same as that modeled by the many-electron schr\"{o}dinger equation.
+So the atomic coordinates, that is the molecule structures contain uncertainty which ultimately affects the charge dynamics. 
+This is one source of uncertainty that have not been investigated.
+But in our investigation, a fixed molecule structure is used and we do not consider this source of uncertainty.
 
-One of the main quantities of interest to characterize the charge transport in OSC is charge mobility. Using this as the quantity of interest,
-the goal of this work is to investigate how the DFT functionals affect the electronic structures and charge mobility.
-The uncertainty due to the environmental factors that cause a change in the molecules' position is not considered in this work, although this topic deserves intensive studies.
-We want to focus on the following questions: 
+Secondly, state localization is not exactly a time dependent DFT process. 
+But for amorphous OSCs, model noise from state localization is negligible and we do not consider the uncertainty brought by state localization.
+
+Lastly, the exchange-correlation functional in DFT do not have explicit formula and common practice is to use empirical functional, whose suitability is usually unknown for most molecules.
+
+The charge dynamics is determined by CTRW transition rates, which depend on the electronic structures.
+Since DFT is used to calculate the molecular electronic structures, the unknown exchange-correlation functional in DFT will bring uncertainties to the multiscale model. 
+The effect of the uncertainty from the DFT exchange-correlation functional on the multiscale model is not yet explored in literatures. 
+The goal of this work is to quantify the uncertainty effect of the DFT exchange-correlation functional on the charge dynamics in OSCs and to study the robustness of the multiscale model.
+
+To perform this goal of uncertainty quantification, a first step is to choose a QoI.
+A quantity commonly seen in OSC investigation is the charge mobility, which is the distance traveled by the charge carrier divided by the time period.
+The charge mobility is calculated in a \textit{time-of-flight} (ToF) setting. 
+As shown in Fig.\ref{fig:MSM}(d), charge carriers are injected into one electrode called \textit{Source} and they are collected by another electrode at the opposite end called \textit{Sink}. 
+Knowing the length of the sample $L$ and the time-of-flight $\tau$, the diffusive velocity is calculated as $v_\text{ToF}=\frac{L}{\tau}$.
+
+Most literature report the charge mobility in a steady state setting, where no electrodes are used and the molecular system is infinitely repeated in all three dimensions by periodic boundary conditions.
+Over a long time period, the charge occupation on each molecule $\pi_i$ reach equilibrium, and the steady state diffusive velocity is calculated via:
+\begin{equation}
+    v_\text{SS} = \sum_i \pi_i \sum_j \omega_{ij} \vec{r}_{ij} = \mathbb{E}f(M_{\infty})
+\end{equation} 
+Specifically, the focus will be placed on following questions: 
 \begin{itemize}
-    \item How do DFT functionals change the reorganization energy, distribution of molecule energies and coupling elements? 
+    \item How do DFT functionals change the electronic structures: reorganization energy, distribution of molecule energies and coupling elements? 
     \item How do DFT functionals change the charge mobility?
-    \item Which electronic structure (among energy, coupling element and reorganization energy) has the most impact on the uncertainty of charge mobility?
+    \item Which electronic structure (among energy, coupling element and reorganization energy) uncertainty has the most impact on the charge mobility distribution?
     \item Can we estimate the range of the quantity of interest, given a confidence level?
@@
 
-Charge mobility, in the presence of an external electric field, can be calculated as $\mu = \frac{\vec{v} \cdot \vec{F}}{|\vec{F}|^2}$, where $\vec{v}$ is the average drift-diffusive velocity of the charge carrier(s).
-Without an electric field, $\vec{v}$ is the purely diffusive velocity.
-In electronic devices, velocity is obtained from time-of-flight (ToF) experiments, where charge carriers are injected into the cathode and collected at the anode.
-The ToF, denoted as $\tau$, is the period from injection to detection of at least one charge carrier.
-The velocity is given by $|\vec{v}| = \frac{L}{\tau}$, where $L$ is the sample length, usually aligned with the electric field direction if present.
+Calculation of $v_\text{ToF}$ or $v_\text{SS}$ commonly use kinetic Monte Carlo (KMC) to obtain multiple realizations of full charge dynamic trajectories 
+or numerically solving the master equation. 
+However, those two commonly used methods are not suitable for quantifying the uncertainty effect of multiscale model charge dynamics for the following reasons.
 
-For multiscale modeled OSCs, ToF calculations involve setting some molecules as \textit{Source} and some as \textit{Sink}.
-The key quantity for characterizing charge transport, especially for uncertainty quantification, is ToF, as the sample length $L$ is fixed and constant.
+Firstly, KMC produces random variables whose expectation is the charge mobility.
+The prior knowledge of the random variable distribution as well as the required KMC samples to achieve converged expectation is unknown.
+So this method itself pose further challenge for our uncertainty quantification.
+Secondly, the numerical solution of the master equation has stability and convergence issue, that is, a small integration time step is required to achieve stability and a long computational time to achieve convergence result.
+These aspects add additional difficulty for uncertainty quantification.
 
-Most literature on charge transport in multiscale modeled OSCs reports steady-state charge mobility, using periodic boundary conditions to simulate CTRWs on an infinitely repeating molecular graph, typically via kinetic Monte Carlo simulations.
-However, this method faces challenges, particularly convergence issues, which complicate the accurate calculation of quantities with a desired confidence level.
-
-Therefore, this work focuses on characterizing charge mobility based on ToF, specifically diffusive ToF with a single charge carrier, calculated from the hitting time of a continuous time Markov chain.
-This approach excludes the effects of external electric fields, clarifying the sensitivity from DFT functional to electronic structures and ToF mobility.
-Furthermore, considering only one charge carrier aligns with the low carrier density in electronic devices and avoids the computational complexity of simulating multiple charge carriers, which can obscure important low-energy molecules in uncertainty quantification.
+{\huge Here}
 

### 2024-10-10 paper.tex
update

@@
 
-\section{Introduction}
+\section{Background}
 
@@
 coordinates.
-As a result, the time evolution of the atomic coordinates can be modeled by solving the Newton's equation using empirical force field to approximate the potential energy surfaces (need citation).
+As a result, the time evolution of the atomic coordinates can be modeled in molecular dynamics (MD) by solving the Newton's equation using empirical force field to approximate the potential energy surfaces (need citation).
 
@@
 Step 2: Molecule energy $E_i$ calculation.
-Step 3: Calculation of Reorganization energy $\lambda_{i,j}$ and coupling element $J_{i,j}$ for pairs of molecule $i,j$ whose COM distance is less than $r_\text{cutoff}$.
+Step 3: Calculation of Reorganization energy $\lambda_{ij}$ and coupling element $J_{ij}$ for pairs of molecule $i,j$ whose COM distance is less than $r_\text{cutoff}$.
 Step 4: Modelling dynamics on device level, such as ToF calculation.}
@@
 In overcoming the challenges and achieving the multiscale model, uncertainties are introduced. 
-
 While Born-Oppenheimer approximation allows for the use of force field to approximate the potential energy surfaces (need citation) and model the atomic coordinates using Newton’s equations, the atomic coordinates are not exactly the same as that modeled by the many-electron schr\"{o}dinger equation.
@@
 But in our investigation, a fixed molecule structure is used and we do not consider this source of uncertainty. 
-
 Secondly, state localization is not exactly a time dependent DFT process. 
-But for amorphous OSCs, model noise from state localization is negligible and we do not consider the uncertainty brought by state localization.
-
-Lastly, the exchange-correlation functional in DFT do not have explicit formula and common practice is to use empirical functional, whose suitability is usually unknown for most molecules.
+But for amorphous OSCs used in this work, model noise from state localization is negligible and we do not consider the uncertainty brought by state localization.
+Lastly, the exchange-correlation potential in DFT do not have explicit formula and common practice is to use empirical functional, whose suitability is usually unknown for most molecules.
 
@@
 Since DFT is used to calculate the molecular electronic structures, the unknown exchange-correlation functional in DFT will bring uncertainties to the multiscale model. 
+In particular, different DFT functionals contain varying levels of Hartree Fock (HF) to represent the exchange-correlation potential. 
 The effect of the uncertainty from the DFT exchange-correlation functional on the multiscale model is not yet explored in literatures. 
@@
 \end{equation}
+
 Specifically, the focus will be placed on following questions: 
-\begin{itemize}
+\begin{enumerate}
     \item How do DFT functionals change the electronic structures: reorganization energy, distribution of molecule energies and coupling elements? 
@@
     \item Can we estimate the range of the quantity of interest, given a confidence level?
-\end{itemize}
+\end{enumerate}
 
@@
 However, those two commonly used methods are not suitable for quantifying the uncertainty effect of multiscale model charge dynamics for the following reasons. 
-
 Firstly, KMC produces random variables whose expectation is the charge mobility.
@@
 These aspects add additional difficulty for uncertainty quantification.
-
-{\huge Here}
+Considering those aspects, the ToF $\tau$ and $v_\text{ToF}$ are obtained via a graph random walk method
+\cite{chen_graph_2024}. Once the $v_\text{ToF}$ is calculated using this method, it is considered to be converged. 
+Similarly, the steady state occupation $\pi_i$ will be calculated as the null-space of the transition matrix.
 
@@
 \section{Multiscale Model}
-\label{sec:MSM}
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.95\textwidth]{figs/MSM.png}
-    \caption{The multiscale model workflow for OSC.
-Step 1: MD simulation to generate atom coordinates.
-Step 2: Molecule energy $E_i$ calculation.
-Step 3: Calculation of Reorganization energy $\lambda_{i,j}$ and coupling element $J_{i,j}$ for pairs of molecule $i,j$ whose COM distance is less than $r_\text{cutoff}$.
-Step 4: Modelling dynamics on device level, such as ToF calculation.}
-    \label{fig:MSM}
-\end{figure}
-
-Figure \ref{fig:scatterE} shows the workflow of the multiscale model for ToF calculation.
-In brief summary, the process includes: Firstly, classical Molecular Dynamics is used to generate the atomistic coordinates from which the vertex and edge sets are defined.
-Specifically, using a cutoff distance $r_\text{cutoff}$, any two molecules whose center of mass (COM) within $r_\text{cutoff}=0.5$ [nm] form a pair of molecules where directed edge weight can be calculated.
-Secondly, quantum electronic structure calculation is performed to obtain the electronic structure properties: The molecule energy $E_i$ of molecule $i$, the reorganization energy between $\left\{\lambda_{i,j}\right\}$ and coupling element $\left\{\Delta J_{i,j}\right\}$ between the pair of molecules $i$ and $j$.
-All in unit of eV.
-
-Then, those electronic structure properties are used to calculate the bi-molecular Marcus rate between the molecules:
+The multiscale model results in the charge dynamics becoming CTRW.
+When there in one charge carrier, each state in CTRW corresponds to the charge occupation in each molecule.
+The transition rates between the state, that is the rate for charge transfer rates between two molecules $i$ and $j$ is calculated as the Marcus rate:
 %
 \begin{equation}
-    \omega_{ij} = \frac{2\pi}{\hbar} \frac{|J_{i,j}|^2}{\sqrt{4\pi \lambda_{i,j} k_\text{B}T}} \exp\left(-\frac{(\Delta E_{i,j} + q \vec{F} \cdot \vec{r}_{i,j} - \lambda_{i,j})^2}{4\lambda_{i,j} k_\text{B}T}\right) ,
+    \omega_{ij} = \frac{2\pi}{\hbar} \frac{|J_{ij}|^2}{\sqrt{4\pi R_{ij} k_\text{B}T}} \exp\left(-\frac{(E_{ij} + q \vec{F} \cdot \vec{r}_{ij} - R_{ij})^2}{4R_{ij} k_\text{B}T}\right) ,
     \label{equ:Marcus}
@@
 %
-where $\hbar$ is the reduced Planck constant, $k_\text{B}$ the Boltzmann constant.
-The temperature $T$ (in \unit[]{K}), external electric field $\vec{F}$ and the charge of the carrier $q$ (in \unit[]{e}) can be considered as parameters of the simulation.
-The vector $\vec{r}_{i,j} = (r^x_{ij},r^y_{ij},r^z_{ij})^\text{T}$ connects the center-of-masses of molecules $i$ and $j$, which is calculated using cyclic boundary conditions depending on system setting.
-And $\Delta E_{i,j} = E_i - E_j$ is the energy difference between a pair of molecules.
-Finally, the quantity of interest, such as ToF $\tau$, can be calculated from the transition rates $\omega_{ij}$.
+where $\hbar$ is the reduced Planck constant and $k_\text{B}$ the Boltzmann constant.
+The temperature $T$ (in \unit[]{K}), the charge of the carrier $q$ (in \unit[]{e}) and the external electric field $\vec{F}$ (in V/m) can be considered the external, environmental parameters of the simulation.
+The vector $\vec{r}_{ij} = (r^x_{ij},r^y_{ij},r^z_{ij})^\text{T}$ connects the center-of-masses (COMs) of molecules $i$ and $j$, which is calculated cyclic boundary conditions depending on the boundary condition.
+The remaining physical, material-specific (or rather transfer-pair-specific) quantities are the reorganization energy $R_{ij}$, the electronic coupling $J_{ij}$, and the energy difference $E_{ij} = E_i - E_j$ (all in \unit[]{eV}).
+With the information about the molecular COMs and the rates, one can construct the graph $\mathbf{G}=(\mathbf{V}, \mathbf{W})$ on which the CTRW takes place.
+$\mathbf{V}$ is a set of nodes (molecules) and $\mathbf{W}: \omega_{ij}$ is the adjacency matrix.
+A rate is only considered between molecules $i$ and $j$ if their closest-contact distance is smaller than $r_\text{cutoff}=\unit[0.5]{nm}$.
 
+In the section, the components of the multiscale model will be introduced: molecule dynamics, calculation of reorganization energy, molecule energy, coupling element, $v_\text{SS}$ and $v_\text{ToF}$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Molecule Dynamics Simulation}
@@
 
-\subsection{Electronic Structure Calculation} 
-The molecule energy $E_i$ in the multiscale model is calculated as:
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Electronic Structure Calculations} 
+%Each molecule is an $N_\text{el}$-electron system, and in quantum mechanics, the probability of finding electrons in space is described by the electron wavefunction $\phi(\vec{r})$.
+Effective single-electronic wave functions $\phi_l (\vec{r})$ and associated energies $\epsilon_l$ for a system with $N_\text{el}$ electrons are determined as solutions to the Kohn--Sham equations~\cite{kohn_self_1965}
+%
 \begin{equation}
-E_i = (U^\text{cC}_i - U^\text{nN}_i) + (E^\text{c}_i - E^\text{n}_i)
-\label{eq:E_i}
+    \left(-\frac{1}{2}\nabla^2_{\vec{r}} + v_\text{ext}(\vec{r}) + v_\text{H}[\rho](\vec{r}) + v_\text{XC}[\rho](\vec{r})\right) \phi_l(\vec{r}) =  \epsilon_l \phi_l (\vec{r}) ,
+    \label{eq:KS2}
 \end{equation}
-where $U^\text{cC}_i$ is the internal energy of charged molecule $i$ in the optimized charged geometry, and $U^\text{nN}_i$ is the internal energy of neutral molecule $i$ in the optimized neutral geometry.
-The calculation of $U$ and how to obtain optimized geometry will be introduced in the subsection DFT Calculation.
-In the superscript the lowercase letter "c/n" represents the molecule state of being charged/neutral and uppercase letter "C/N" represents the geometry of the charged/neutral molecule.
-This notation also applies for $E^\text{c}_i$, $E^\text{n}_i$.
-And $E^\text{n}_i = E^\text{n,el}_i + E^\text{n,induce}_i$ is the energy due to the electrostatic and induced dipole moment effect.
-Compared with the electrostatic energy calculated using the dielectric constant, this energy in multiscale model is very sensitive to the molecule structure, making the uncertainty quantification of charge transport in multiscale model much more important.
-A precise method for calculating $E^\text{n}_i$ is to use the Thole Model as detailed in \cite{Baumeier2011}.
+%
+where $v_\text{ext}$ in an external potential (typically from the nuclei), $v_\text{H}[\rho]$ the electrostatic Hartree potential of a classical charge density $\rho(\vec{r})$, and $v_{XC}[\rho]$ the exchange-correlation functional containing explicit quantum-mechanical electron-electron interactions.
+The charge density is determined from the single-particle wave functions as $\rho(\vec{r})=\sum\limits_{l=1}^{N_\text{el}} \left\vert\phi_l(\vec{r})\right\vert^2$.
 
-This method has the steps include: first, each atom $a_i$ is initialized with charges $q_{a_i}$ and dipole moment $D_{a_i}$. 
-Then the induced dipoles of each atom are calculated using the electric field generated by other atoms $b_j$.
-This calculation continuous iteratively to update the induced dipoles of every atom by considering the fields due to other dipoles.
-Finally, it checks for convergence, if the induced dipoles have not changed significantly from one iteration to the next, the iterative process stops.
-Finally, the electrostatic energy and polarization energy using the final set of induced dipoles and atomic charges.
-So in summary, $E^\text{n}_i$ is a function of all atoms' charges and induced dipoles: $E^\text{n}_i = \sum\limits_{a_i} f(q_{a_i}, D_{a_i})$.
+%
+\begin{equation}
+    U[\rho] = T_s[\rho] + \int \hat{V}_\text{ext}(\vec{r}) \rho(\vec{r}) d \vec{r} + \hat{V}_\text{H}[\rho] + \hat{V}_\text{XC}[\rho]
+    \label{eq:KS_model}
+\end{equation}
+%
+where the electron density is , $T_s[\rho]$ is the kinetic energy depending on $\rho$,  $\hat{V}_\text{ext}$ is the external potential energy,  $\hat{V}_\text{H}[\rho]$ is the Hartree energy accounting for the Coulomb interaction, $\hat{V}_\text{XC}[\rho]$ is the exchange-correlation energy accounting for the difference between classical and quantum effect.
+The exact form of $\hat{V}_\text{XC}[\rho]$ is not known, in practice, this energy term is approximated by DFT functionals.
+In our work, different functionals are tested on BCP molecular system to check the effect of different functionals' impact on charge mobility.
+Different functionals have different ways to represent the exchange-correlation potentials, such as different level of HF exchange potential.
+Then PBE0 functional is used with varying HF component in the exchange-correlation potentials.
 
-The reorganization energy $\lambda_{i,j}$ between molecule $i$ to molecule $j$ is given as:
+In practice, Equation \ref{eq:KS2} is solved iteratively, and the wave function is represented by a linear combination of basis functions call basic sets. 
+In this work, the basic set def2-tzvp \cite{weigend_accurate_2006} is used. The DFT computation is performed by VOTCA \cite{Baumeier2011} which internally calls ORCA software.
+
+The internal energy $U_i$ of molecule $i$ depends on the charge states and atomic coordinate (also called geometry) of the molecule. 
+The optimized geometry of a molecule refers to the atomic coordinates that minimize $U_i$.
+Here we use $U_i^\text{xX}$ to denote the internal energy of molecule $i$ at charge state x in the optimized geometry X.
+Neutral and charge states are represented as x=n and c, respectively.
+Similarly, optimized neutral molecular geometry and optimized charge molecular geometry are represented by X=N and C, respectively.
+
+The reorganization energy $R_{ij}$ from molecule $i$ to molecule $j$ is given as:
 \begin{equation}
-    \lambda_{ij} = U_i^\text{nC} - U_i^\text{nN} + U_j^\text{cN} - U_j^\text{cC}
+    R_{ij} = U_i^\text{nC} - U_i^\text{nN} + U_j^\text{cN} - U_j^\text{cC}
 \end{equation}
+where $U_i^\text{nC}$ is the internal energy of the neutral molecule $i$ in optimized geometry of charged molecule, calculated from Equation \ref{eq:KS_model}. 
+And $U_i^\text{nN}$ the internal energy of the neutral molecule $i$ in optimized geometry of neutral molecule. Similarly, $U_j^\text{cN}, U_j^\text{cC}$ are defined in this way.
+When charge carriers are holes, a charged molecule has one electron less compared to a neutral molecule. 
+For the BCP device, we obtain $R_{ij}=0.50$ eV since this is only one type of molecule.
+
+In a single-component system where internal energy difference of molecule $i$ and $j$ is equal, the energy difference $E_{ij}$ is calculated by:
+\begin{equation}
+    E_{ij} = E_i - E_j
+    \label{eq:siteE}
+\end{equation}
+where $E_i = E_i^\text{c} - E_i^\text{n},E_j = E_j^\text{c} - E_j^\text{n}$ are the molecule energies, the superscript represents charge state or neutral state molecule as mentioned above.
+And $E_i^\text{n} = E_i^\text{n,el} + E_i^\text{n,induce}$ considers the electrostatic energy as well as the energy from the induced dipole moment.
+In multiscale model, $E_i^\text{n} = E_i^\text{n,el} + E_i^\text{n,induce}$ is calculated iteratively from the Thole Model as detailed in \cite{thole_molecular_1981}.
+% instead of using a dielectric constant as been done in the bulk system at macroscopic scale. 
+Specifically, the first step is to calculate the induced dipole at atom $a_i$ by electrostatic field.
+This induced dipole will change the dipole moment at all other atoms $b_j \neq a_i$.
+Then repeat this step and recalculate the induced dipole at atom $a_i$, followed by induced dipoles at all other atoms $b_j$.
+This process is repeated until the induced dipole converge to a fix value.
+In short summary, the $E_i$ is a function of all individual atoms' charges $q$ and induced dipole $\mu$: $E_i^\text{n,el} + E_i^\text{n,induce} = \sum\limits_{a_i} f(q_{a_i}, \mu_{a_i})$ where $a_i$ goes over all the atoms in the system.
+The calculation of $E_i^\text{c} = E_i^\text{c,el} + E_i^\text{c,induce}$ uses similar iteratively process as $E_i^\text{n}$.
+The molecule energies and their distribution are shown in the appendix.
 
 %%%%%%%
-The coupling element $J_{i,j}$ between molecule $i$ and $j$ is calculated \cite{baumeier_density_2010} using the electron wave function of the molecules obtained from the Kohn-Sham equation: 
+The coupling element $J_{ij}$ between molecule $i$ and $j$ is calculated \cite{baumeier_density_2010} using the electron wave function of the molecules obtained from the Kohn-Sham equation: 
 \begin{equation}
-    J_{i,j} = \frac{ J^0_{i,j}- \frac{1}{2}(e_i+e_j)S_{i,j} }{ 1- S_{i,j}^2 }
+    J_{ij} = \frac{ J^0_{ij}- \frac{1}{2}(e_i+e_j) S_{ij} }{ 1- S_{ij}^2 }
     \label{equ:JAB}
 \end{equation}
-where $J^0_{i,j} = \langle \psi^i | \hat{H} | \psi^j \rangle $, $e_i = \langle \psi^i | \hat{H} | \psi^i \rangle $, $e_j = \langle \psi^j | \hat{H} | \psi^j \rangle $, and $S_{i,j}=\langle \psi^i | \psi^j \rangle $ with bra-ket notation, $\hat{H}$ is the Hamiltonian of the electron wave function, and $\psi^{i,(j)}$ is the electron wave function of molecule $i(j)$.
+where $J^0_{ij} = \langle \phi^\text{HOMO}_i | \hat{H} | \phi^\text{HOMO}_j \rangle $, $e_i = \langle \phi^\text{HOMO}_i | \hat{H} | \phi^\text{HOMO}_i \rangle $, $e_j = \langle \phi^\text{HOMO}_j | \hat{H} | \phi^\text{HOMO}_j \rangle $, and $S_{ij}=\langle \phi^\text{HOMO}_i | \phi^\text{HOMO}_j \rangle $ with bra-ket notation.
+For hole-transporting OSCs system such as the BCP used in this work, $\phi^\text{HOMO}_i$ is the HOMO electron wave function of molecule $i$. 
+The Kohn-Sham Hamiltonian is $\hat{H} = -\frac{1}{2}\nabla^2_{\vec{r}} + \hat{V}_\text{ext} + \hat{V}_\text{H}[\rho] + \hat{V}_\text{XC}[\rho]$. 
 A single molecule is called a monomer, and a pair of two molecules is called a dimer.
 
-Denote $\psi^\text{D}$ as the electron wave function of the two molecules,  $J^0_{i,j}$ can be calculated via:
+Denote $\phi^\text{HOMO}_\text{D}$ as the HOMO electron wave function of the dimer,  $J^0_{ij}$ can be calculated via:
 $
-    J^0_{i,j} = \mathbf{\gamma}^i \text{diag}(\mathcal{E}) \mathbf{\gamma}^j
+    J^0_{ij} = \mathbf{p}^i \text{diag}(\mathcal{E}) \mathbf{p}^j
 $, 
-where $\mathbf{\gamma}^i = \langle \psi^i | \psi^\text{D} \rangle$ and $\mathbf{\gamma}^j = \langle \psi^j | \psi^\text{D} \rangle$ are called the projections of the monomer orbitals $\psi^i, \psi^j$ on the dimer orbitals $\psi^\text{D}$.
-And $\text{diag}(\mathcal{E})$ is the diagonal matrix consisting of energy eigenvalues of the one-particle wave function of the dimer.
+where the vector $\mathbf{p}^i = \langle \phi_i^\text{HOMO} | \phi^\text{HOMO}_\text{D} \rangle$ and $\mathbf{p}^j = \langle \phi_j^\text{HOMO} | \phi_\text{D}^\text{HOMO} \rangle$ are called the projections of the monomer orbitals $\phi_i^\text{HOMO}, \phi_j^\text{HOMO}$ onto the dimer orbitals $\phi^\text{HOMO}_\text{D}$.
+And $\text{diag}(\mathcal{E})$ is the diagonal matrix consisting eigenvalues of the basis function of $\phi_\text{D}^\text{HOMO}$.
+The molecular coupling element distribution is shown in the appendix.
 
-In conclusion, the calculation of electronic structure relies on the internal energy and electron wave function.
-As mentioned in the introduction, DFT is used to calculate these two quantities.
-The next subsection will introduce the details of DFT.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{DFT Calculation}
-In multiscale model, each molecule is an $N_\text{el}$-electron system, and the probability of finding electrons in space is described by the wavefunction.
-In DFT, the internal energy calculated from the Kohn–Sham equation \cite{kohn_self_1965} reads:
-
-\begin{equation}
-    U^\text{KS}[\rho] = T_s[\rho] + \int \hat{V}_\text{ext}(\vec{r}) \rho(\vec{r}) d \vec{r} + \hat{V}_\text{H}[\rho] + \hat{V}_\text{XC}[\rho]
-    \label{eq:KS_model}
-\end{equation}
-where the electron density is $\rho=\sum\limits_{i=1}^{N_\text{el}} \phi_i^\star(\vec{r}) \phi_i(\vec{r})$, $T_s[\rho]$ is the kinetic energy depending on $\rho$,  $\hat{V}_\text{ext}$ is the external potential energy,  $\hat{V}_\text{H}[\rho]$ is the Hartree energy accounting for the Coulomb interaction, $\hat{V}_\text{XC}[\rho]$ is the exchange-correlation energy accounting for the difference between classical and quantum effect.
-The exact form of $\hat{V}_\text{XC}[\rho]$ is not known, in practice, this energy term is approximated by DFT functionals.
-In our work, ten DFT functionals are used to represent this energy term.
-The single-electron wave function $\phi_i$ satisfies: 
-\begin{equation}
-    (-\frac{1}{2}\nabla^2_{\vec{r}} + \hat{V}_\text{ext} + \frac{\delta \hat{V}_\text{H}[\rho]}{\delta \rho} + \frac{\hat{V}_\text{XC}[\rho]}{\delta \rho}) \phi_i^\text{KS}(\vec{r}) =  \epsilon^\text{KS}_i[\rho] \phi^\text{KS}_i (\vec{r})
-    \label{eq:KS2}
-\end{equation}
-with $\epsilon^\text{KS}_i[\rho]$ being the energy eigenvalue of electron $i$. 
-In practice, Equation \ref{eq:KS2} is solved iteratively, and the wave function is represented by a linear combination of basis functions call basic sets. 
-In this work, the basic set def2-tzvp \cite{weigend_accurate_2006} is used. The DFT computation is performed by VOTCA \cite{Baumeier2011} which internally calls ORCA software.
-The internal energy $U^\text{KS}$ depends on the atomic coordinates of the molecule. The optimized geometry of a molecule refers to the atomic coordinates that minimize $U^\text{KS}$.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \section{Time-of-flight Calculation}
-The multiscale model defines a graph $\mathbf{G}$ with an adjacency matrix $\mathbf{W}$, where the edge weights $\omega_{i,j}$ represent the Marcus rate from molecule $i$ to molecule $j$.
+The multiscale model defines a graph $\mathbf{G}$ with an adjacency matrix $\mathbf{W}$, where the nodes represent molecules and the edge weights $\omega_{ij}$ represent the Marcus rate from molecule $i$ to molecule $j$.
 The charge dynamics are modeled as a continuous-time random walk on this graph.
@@
 
-As mentioned in the introduction, a quantity of interest in modeling charge dynamics is the ToF, which is the time for charges carriers injected into the Source to be detected at the Sink.
-A typical method to obtain the ToF is to use the kinetic Monte Carlo (KMC) method to simulate the CTRW for many times and record ToFs, which are random variables. 
-To be detailed: 
-But a challenge with this KMC is that one need to repeat a large number $N_\text{KMC}$ of KMC simulation to guarantee an converged ToF.
-Furthermore, $N_\text{KMC}$ is not known before running KMC, posing a great challenge to quantify the uncertainty of ToF from the multiscale model.
-An alternative method to overcome the convergence challenge is to obtain ToF as the hitting time a continuous time Markov chain.
+In CTRW the ToF is calculated as the expected hitting time of a continuous time Markov chain.
 
-Due to Pauli repulsion, each node can be occupied by at most one charge carrier.
-For a system with $N$ molecules and $N_c$ charge carriers, there are ${N \choose N_c}$ possible occupation states.
-Each occupation state is denoted as $\mathbf{s}$.
-A state is called the Source state if all carriers occupy the Source nodes, and a Sink state if at least one of the Sink nodes is occupied.
+For a system with $N$ molecules and one charge carriers, there are $N$ possible occupation states.
+A state is called the Source state if one of the Source molecule is occupied, and a Sink state is the one when one of the Sink molecule is occupied.
 
-The transition rates between the states can be obtained from the adjacency matrix $\mathbf{W}:\omega_{i,j}$, since the connectivity of states is encoded in the connectivity of the nodes, as detailed in ~\cite{chen_graph_2024}.
-According to such connectivity, 
-the transition rates $\Omega_{\mathbf{s} \mathbf{s}' }$ from state $\mathbf{s}$ to $\mathbf{s}'$ is:
+The transition rates between the states defines the adjacency matrix $\mathbf{W}:\omega_{ij}$.
+According to such connectivity between the molecules, the transition rates $\mathbf{W}_{ij}$ from state $i$ to $j$ is:
 \begin{equation}\label{eq:transition_rates}
-	\Omega_{\mathbf{s} \mathbf{s}^\prime} =
+	\mathbf{W}_{ij} =
 	\begin{cases}
-	     0			&  \mathbf{s} \text{ is not connected to } \mathbf{s}^\prime,\\
-	    \omega_{ij}	&  \mathbf{s} \text{ is connected to } \mathbf{s}^\prime \text{ due to } (i,j)
+	     0			&  i \text{ is not connected to } j,\\
+         \omega_{ij}   &  i \text{ is connected to } j,
 	\end{cases}
@@
 
-Then the transition probability from state $\mathbf{s}$ to $\mathbf{s}'$ is $p_{\mathbf{s} \mathbf{s}^\prime} = \Omega_{\mathbf{s} \mathbf{s}^\prime}/D_\mathbf{s}$ where $D_\mathbf{s} := \sum_{\mathbf{s}^\prime \ne \mathbf{s}} \Omega_{\mathbf{s} \mathbf{s}^\prime}$.
-And the expected time from state $\mathbf{s}$ to reach the Sink state $\tau_\mathbf{s}$ is calculated via: 
+Then the transition probability from state $i$ to $j$ is $p_{ij} = \mathbf{W}_{ij}/D_i$ where $D_i := \sum_{j} \mathbf{W}_{ij}$.
+And the expected time from state $i$ to reach the Sink state $\tau_i$ is calculated via: 
 \begin{equation}\label{eq:hitting_time}
-	\tau_\mathbf{s} = \begin{cases}
-		\frac{1}{D_\mathbf{s}} + \sum_{\mathbf{s}^\prime \ne \mathbf{s}} p_{\mathbf{s} \mathbf{s}^\prime} \tau_{\mathbf{s}^\prime} &\text{if $\mathbf{s}$ is not a sink state},\\
+	\tau_i = \begin{cases}
+		\frac{1}{D_i} + \sum_{j \ne i} p_{ij} \tau_{j} &\text{if $i$ is not a sink state},\\
 		0 &\text{else.} 
@@
 \begin{equation} 
-\tau = N_\text{source} \left[\sum_{\mathbf{s} \in \text{Source}} (\tau_\mathbf{s}^\ast)^{-1}\right]^{-1},
+\tau = N_\text{source} \left[\sum_{i \in \text{Source}} (\tau_i)^{-1}\right]^{-1},
 \label{eq:ToF}
@@
 
+To calculate $v_\text{SS}$ the steady state distribution $\pi_i$ is required.
+In continuous time Markov chain, the steady state distribution vector $\vec{\pi}: \pi_i$ is the null-space of $\mathbf{W}-\mathbf{D}$:
+\begin{equation}
+    (\mathbf{W}-\mathbf{D} )\vec{\pi} = \mathbf{0}
+\end{equation}
+where $\mathbf{D} = \text{diag}(D_i)$ is the out-degree matrix of $\mathbf{W}$.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The \textit{Source} contains molecules whose COM have X-coordinates $0 < r^x_i < 0.5$ nm, and \textit{Sink} molecules $7.5 < r^x_i < 8$. 
-This section presents the molecule energy distribution, coupling element distribution, reorganization energies and ToFs calculated using the 12 DFT functionals. 
+This section presents the molecule energy distribution, coupling element distribution, reorganization energies and ToFs calculated using the 10 DFT functionals. 
 Using the PBE0 functional as a reference, the difference in electronic structure distributions due to DFT functionals is measured by the Wasserstein distance.
@@
 Then distributions of ToF are obtained using the electronic structure parameters generated by Monte Carlo sampling from the estimated distributions.
-Finally, the sensitivities of $E_i,J_{i,j},\lambda_{i,j}$ to ToF are compared, confidence level of ToFs are estimated.
+Finally, the sensitivities of $E_i,J_{ij},\lambda_{ij}$ to ToF are compared, confidence level of ToFs are estimated.
 
@@
     \hline
-        Functional & HFX & $\lambda_{i,j}$ [eV] & ToF [s] & $\sigma(E)$ & drift ToF [s] & $\mu$ [m/s] \\ 
+        Functional & HFX & $\lambda_{ij}$ [eV] & ToF [s] & $\sigma(E)$ & drift ToF [s] & $\mu$ [m/s] \\ 
         \hline
@@
     \end{tabular}
-    \caption{DFT functional HF exchange scaling (HFX), calculated values of reorganization energy ($\lambda_{i,j}$), diffusive ToF, energy disorder ($\sigma(E)$), drift ToF, and mobility ($\mu$) for BCP molecules for different DFT functionals.}
+    \caption{DFT functional HF exchange scaling (HFX), calculated values of reorganization energy ($\lambda_{ij}$), diffusive ToF, energy disorder ($\sigma(E)$), drift ToF, and mobility ($\mu$) for BCP molecules for different DFT functionals.}
     \label{tab:para}
@@
 A noticeable difference in all the different functional is the amount of HF for approximating the exchange-correlations. 
+The large HFX cases (BHANDHLYP and BHLYP) have large ToF, while other functionals have smaller HFX. In commonly practices, most functionals use small HFX.
 
-So by fixing the functional to be the commonly used PBE0 functional, the HFX is varied to investigate the effect of HFX to the molecular properties and ToF. 
-Hybrid functionals like PBE0 or B3LYP use a specific, empirically determined fraction of HF exchange that generally works well for a broad range of applications.
-PBE0 is constructed by combining 25\% of the exact exchange from HF theory with 75\% of the exchange from the Perdew-Burke-Ernzerhof (PBE) GGA exchange functional, along with the full PBE correlation functional.
-
-When correlation effects are strong and electron-electron interactions play a significant role in determining their physical properties, the exact exchange overly localize electrons, and a lower HFX percentage or even pure DFT might perform better.
-The $\pi$-electron conjugation and interactions in OSC such as BCP and MADN leads to significant electronic correlation effects within those materials.
+In our next step, the functional is fixed to be the commonly used PBE0 functional, the HFX is varied to investigate the effect of HFX on the molecular properties and ToF.
 
 \subsection{BCP molecule with different HFX}
-So our first investigation use the range of HFX=$0.05,0.15,0.23,0.24,0.25,0.26,0.27,0.35,0.45,0.55$.
+Our first investigation use the range of HFX=$0.05,0.15,0.23,0.24,0.25,0.26,0.27,0.35,0.45,0.55$.
 The values of HFX=$0.23,0.24,0.26,0.27$ are used because we want to see if a small perturbation in HFX would affect ToF significantly.
@@
 Figure \ref{fig:autogen}(b) shows that as HFX increase, the n state and h state BCP molecule has decreasing isotropic polarizability, showing that the molecule is getting more difficult to be polarized.
-Since the isotropic polarizability is decreasing as HFX increases, the screening effects are weaker for large HFX.
+However, the change of $P_\text{iso}$ is more dramatic in the h state molecules. 
+Since the difference between the n state $P_\text{iso}$ and h state $P_\text{iso}$ is getting smaller, the contribution of polarizability effect on the energy disorder is weaker.
+This results in a large energy disorder as HFX increase.
 
 Fig.\ref{fig:autogen}(c) shows that as HFX increase, reorganization energies are higher.
-Since the molecule requires more energy to reorient itself during the charge transfer process, the higher reorganization energy can slow down charge transport by making it energetically more costly for charges to move between molecules.
+Since the molecule requires more energy to reorient itself during the charge transfer process, the higher reorganization energy can potentially slow down charge transport when there is no energy disorder present.
 
-Fig.\ref{fig:autogen}(d) shows that when HFX=0.05-0.3 the energy disorder is relatively small (less than 0.2 eV). When HFX=0.35-0.55, the energy disorder $\sigma(E)>0.22$.
+Fig.\ref{fig:autogen}(d) shows that when HFX=0.05-0.3 the energy disorder is relatively small (less than 0.2 eV).
+When HFX=0.35-0.55, the energy disorder $\sigma(E)>0.22$.
+This pattern is consistent with the change of $P_\text{iso}$ as shown in Fig.
+\ref{fig:autogen}(b)
 
@@
     \centering
-    \begin{tabular}{c c c }
+    \begin{tabular}{c c c c c}
     \hline
-        HFX & ToF [s] & ToF(no $E$) [s] \\
+        HFX & ToF [s] & $v_\text{ToF}$ [m/s] & ToF(no $E$) [s] & $v_\text{ToF}$(no $E$) [m/s] \\
     \hline
-        0.05 &  0.32010 & $3.004 \times 10^{-10}$ \\
-        0.15 & 0.3879 & $4.668 \times 10^{-10}$ \\
-        0.23 & 0.0200 & $6.787 \times 10^{-10} $ \\
-        0.24 & 0.02977 & $7.0290 \times 10^{-10} $ \\
-        0.25 & 0.02648 & $7.633 \times 10^{-10}$ \\
-        0.26 & 3.259 & $7.824 \times 10^{-10}$ \\
-        0.27 & 0.0359 &  $9.162 \times 10^{-10}$ \\
-        0.35 & $1.72 \times 10^7 $ & $1.00 \times 10^{-9}$ \\
-        0.45 & $1.8 \times 10^4$ & $1.32\times 10^{-9}$ \\
-        0.55 & $1.23 \times 10^9 $ & $1.880 \times 10^{-9} $ \\
+        0.05 & 0.32 & $2.2 \times 10^{-8}$ & $3.0 \times 10^{-10}$ & 24 \\
+        0.15 & 0.39 & $1.8 \times 10^{-8}$ & $4.7 \times 10^{-10}$ & 15 \\
+        0.23 & 0.020 & $3.6 \times 10^{-7}$ & $6.8 \times 10^{-10} $ & 10 \\
+        0.24 & 0.030 & $2.4 \times 10^{-7}$ & $7.0 \times 10^{-10} $ & 10 \\
+        0.25 & 0.026 & $2.7 \times 10^{-7}$ & $7.6 \times 10^{-10}$ & 9.4 \\
+        0.26 & 3.2 & $4.5 \times 10^{-9}$ & $7.8 \times 10^{-10}$ & 22 \\
+        0.27 & 0.036 & $2.0 \times 10^{-7}$ & $9.2 \times 10^{-10}$ & 7.8 \\
+        0.35 & $1.7 \times 10^7 $ & $4.1 \times 10^{-16}$ & $1.0 \times 10^{-9}$ & 7.1 \\
+        0.45 & $1.8 \times 10^4$ & $3.6 \times 10^{-12}$ & $1.3 \times 10^{-9}$ & 5.4\\
+        0.55 & $1.2 \times 10^9 $ & $5.7 \times 10^{-18}$ & $1.9 \times 10^{-9} $ & 3.8 \\
     \hline
     \end{tabular}
-    \caption{The ToF with and without energy disorder of the BCP system as a function of the HFX. }
+    \caption{The ToF and diffusive velocity calculated by ToF along a distance $L_x = 7.1$ [nm] with and without energy disorder of the BCP system as a function of the HFX. }
     \label{tab:ToF_BCP_HFX}
@@
 
-The reason for this non-physical ToF is that the site energy calculation use the atomic charges and molecular polarizability from the optimized BCP structure.
-However, each molecule in the BCP system has its own topology with different atomic charges and polarizability compared to the optimized BCP structure.
-Those difference in atomic charges and polarizability affect the site energy calculations.
+The reason for this non-physical ToF is that some molecules have extremely small calculated energies.
 
-So the atomic charges and polarizability in the optimized structure can not be transferred to the BCP molecules generated from the MD simulation. 
-For very disorder material system such as BCP, using the atomic charges and polarizability in the optimized structure can result in site energies that are deviated from the majority of the molecules.
+BCP contains two N atoms which are very difficult to be polarized, resulting the BCP molecule energy and the Thole model being very sensitive to the atomic charges and polarizability.
+
+Furthermore, each molecule in the BCP system has its own topology with different atomic charges and polarizability compared to the optimized BCP structure.  
+Those factors result in the fact that when the atomic charges or polarizability exceeds a certain range, the energy calculation will be very non-physical.
 
@@
 
-Figure \ref{fig:E_qmmm_BCP} shows that for HFX$<0.3$, the site energies of all molecules are relatively close to the site energy obtained from PBE0 functional.
-When HFX=0.35, 0.45, 0.55, there are obvious low-energy molecules as shown by the points below the diagonal line.
-Those low molecules results in the large energy disorder $\sigma(E)$ as shown in table \ref{tab:para}. 
-For those three systems the ToFs are extremely large.
+Figure \ref{fig:E_qmmm_BCP} shows that the molecule energy calculated by the PBE0 functional has a range of -0.3 to -1.7 eV.
+When $ 0.05 \leq HFX \leq 0.27 $, the molecule energies also have a range of -0.3 to -1.7 eV.
 
-The site energy has the contribution from the electrostatic effect and polarization effect due to the dipole moment of the molecules. 
-The Heat map of the electrostatic energy and polarization energy are shown in Fig.\ref{fig:Estat_qmmm_BCP} and Fig.\ref{fig:Edip_qmmm_BCP}.
+For HFX=0.35,0.45, there are molecules energies close to -2.0 eV, and for HFX=0.55, there is one molecule energy being relatively far from the diagonal line. 
+Those mentioned low molecules results in the large energy disorder $\sigma(E)$ as shown in table \ref{tab:para}. 
+and they are very different from other energies obtained by $ 0.05 \leq \text{HFX} \leq 0.27 $.
 
-Figure \ref{fig:Estat_qmmm_BCP} shows that for all HFX parameters, the electrostatic energy are relatively close, while Fig.\ref{fig:Edip_qmmm_BCP} shows that for HFX=0.35,0.45,0.55, there are molecules that have small polarization energy, contributing to the small site energies, and the extremely large ToF.
-Those small polarization energies and site energies are not physical. 
-When HFX is varied, the change of the polarizability and reorganization energy are almost linear, while there is huge jumps in those site energies due to the huge jumps in the polarization energy.
-
-So for correlated system such as OSCs, large range of HFX leads to non-physical results. 
-In the next section, we will use the range with small HFX values for the investigation of a less disorder molecular system, MADN.
+Molecule energy are determined by the atomic charges and polarizability.
+Those physical properties as shown in Fig.\ref{fig:autogen} follow is linearly dependent on HFX.
+Since molecular energy for individual molecule are similar as shown by the scatter points cluster around the diagonal line, the deviated molecule energy for HFX=0.35,0.45,0.55 are non-physical.
+When those low energies molecules are filled by charge carriers, the ToF has a huge change and become close to the ToF obtained by $0.05 \leq \text{HFX} \leq 0.27$.
 
@@
 
+The molecule energy has the contribution from the electrostatic effect and polarization effect due to the dipole moment of the molecules.
+To further understand how the HFX affect molecule energy, the comparison scatter plots of electrostatic energy and polarization energy are shown in Fig.\ref{fig:Estat_qmmm_BCP} and Fig.\ref{fig:Edip_qmmm_BCP}.
+
+Figure \ref{fig:Estat_qmmm_BCP} shows that for all HFX parameters, the electrostatic energy has a range of 0.2 to -1.3 eV.
+Different $0.05 \leq \text{HFX} \leq 0.55$ values produce relatively close electrostatic energy compared to that of HFX=0.25.
+The large HFX$>0.27$ does not cause deviated electrostatic energy.
+
+Figure \ref{fig:Edip_qmmm_BCP} shows that polarization energy has a range of -0.3 to -1.0 eV.
+When $0.05 \leq \text{HFX} \leq 0.27$, the polarization energies are very close and the scatter points are cluster along the diagonal line.
+In contrast to the electrostatic energy, Fig.\ref{fig:Edip_qmmm_BCP} shows that for HFX=0.35,0.45,0.55, there are molecules that have small polarization energy, contributing to the small site energies, and the extremely large ToF.
+
+Those small polarization energies and site energies are not physical, because 
+when HFX is varied, the change of the polarizability and reorganization energy are almost linear.
+In contrast, there is huge jumps in those site energies due to the huge jumps in the polarization energy.
+
+In conclustion, the HFX affects the molecular polarizability, which affects the polarization energies and eventually leads to non-physical molecule energy. 
+And large range of HFX leads to non-physical results. 
+In the next section, we will use the range with small HFX values for the investigation of a less disorder molecular system, MADN.
+
 \section{Results on MADN}
-MADN (2-Methyl-9,10-di(naphth-2-yl)anthracene) is another type of OSC. 
-The ToFs with and without energy disorder for HFX = 0.0, 0.05, 0.10, 0.15, 0.20, 0.25 are shown in 
+MADN (2-Methyl-9,10-di(naphth-2-yl)anthracene) is another type of OSC. MADN has more efficient hole transport compared to BCP. 
 \begin{table}[H]
     \centering
-    \begin{tabular}{c c c }
+    \begin{tabular}{c c c c c}
     \hline
-        HFX & ToF [s] & ToF(no $E$) [s] \\
+        HFX & ToF [s] & $v_\text{ToF}$ [m/s] & ToF(no $E$) [s] & $v_\text{ToF}$ (no $E$) [m/s] \\
     \hline
-        0.00 &  $6.41 \times 10^{-9}$ & $1.88 \times 10^{-10}$ \\
-        0.05 & $ 7.86 \times 10^{-9}$ & $4.07 \times 10^{-10}$  \\
-        0.10 & $ 1.56 \times 10^{-8}$ & $3.97 \times 10^{-10} $  \\
-        0.15 & $ 3.03 \times 10^{-8}$ & $3.96 \times 10^{-10} $ \\
-        0.20 & $ 2.05 \times 10^{-8}$ & $4.48 \times 10^{-10}$  \\
-        0.25 & $ 9.54 \times 10^{-8}$ & $7.24 \times 10^{-10}$ \\
+        0.00 &  $6.4 \times 10^{-9}$ & 1.2 & $1.9 \times 10^{-10}$ & 42 \\
+        0.05 & $ 7.9 \times 10^{-9}$ & 1.0 & $4.1 \times 10^{-10}$ & 20 \\
+        0.10 & $ 1.6 \times 10^{-8}$ & 0.51 & $4.0 \times 10^{-10} $ & 20 \\
+        0.15 & $ 3.0 \times 10^{-8}$ & 0.31 & $4.0 \times 10^{-10} $ & 25 \\
+        0.20 & $ 2.1 \times 10^{-8}$ & 0.39 & $4.5 \times 10^{-10}$ & 18 \\
+        0.25 & $ 9.5 \times 10^{-8}$ & 0.083 & $7.2 \times 10^{-10}$ & 11 \\
     \hline
     \end{tabular}
-    \caption{The ToF with and without energy disorder of the MADN system as a function of the HFX. }
+    \caption{The ToF and diffusive velocity calculated by ToF along a distance $L_x = 8$ [nm] with and without energy disorder of the MADN system as a function of the HFX. }
     \label{tab:ToF_MADN_HFX}
 \end{table}
+Table \ref{tab:ToF_MADN_HFX} shows the ToF and $v_\text{ToF}$ obtained with and without energy disorder. 
+Compared to the mobility of BCP, MADN has significantly larger $v_\text{ToF}$. When the molecule energy are not considered, $v_\text{ToF}$ of MADN is close to that of BCP. 
+So the better hole mobility, that is the larger $v_\text{ToF}$ in MADN compared to BCP is accredited to the energy disorder. 
+As HFX increase from 0 to 0.25, the ToF with and without energy disorder increase eventually by a factor of around 10.
 
+Figure \ref{fig:autogen_MADN} shows the dipole moment $\mu$, isotropic polarizability $P_\text{iso}$,  reorganization energies $\lambda$ and energy disorder $\sigma(E)$ as a function of the HFX parameters.
 %
@@
 %
-As HFX increase from 0 to 0.25, the ToF with and without energy disorder increase eventually by a factor of 10. 
-The dipole moment of the neutral state molecule, isotropic polarizability, and reorganization energies are shown in Fig.\ref{fig:autogen_MADN}.
-The dipole moment decrease as HFX increase as shown by Fig.\ref{fig:autogen_MADN}(a).
+
+Fig.\ref{fig:autogen_MADN}(a) shows that the dipole moment decreases as HFX increase.
 At HFX=0.25, there is a relatively sharp decrease.
-The dipole moment decreases as the HFX increase, this HFX effect on dipole moment is different that of the BCP molecule, which has the dipole moment increases as the HFX increases.
+This HFX effect on dipole moment is opposite to that of the BCP molecule, which has the dipole moment increases as the HFX increases.
 
-Fig.\ref{fig:autogen_MADN}(b) shows that the isotropic polarizability for n,e,h state MADN molecule decrease linearly as HFX increase from 0 to 0.25. 
+Fig.\ref{fig:autogen_MADN}(b) shows that the isotropic polarizability for n and h state MADN molecule decrease linearly as HFX increase from 0 to 0.25. 
 So the molecules are getting more difficult to be polarized. 
@@
 
-All the sites energies are relatively close with varying HFX as revealed by the similar energy disorder $\sigma(E)$.
-The scatter plot of site energies compared to that of PBE0 are shown in Fig.\ref{fig:E_qmmm_MADN}.
-The scatter plots of the electrostatic energy and polarization energy are also close for different HFX, as shown in Fig.
-\ref{fig:Estat_qmmm_MADN} and \ref{fig:Edip_qmmm_MADN}.
-All of those close energies leads to the close ToF shown in Table \ref{tab:ToF_MADN_HFX}.
+Fig.\ref{fig:autogen_MADN}(d) shows that the energy disorders for the used HFX are smaller compared with that of BCP. And they have a relatively similar range.
+
+Using the energy obtained from PBE0 functional with HFX=0.25 as a reference, the scatter plot in Fig.\ref{fig:E_qmmm_MADN} shows that all HFX values produce molecule energies in the range -0.5 to -1.1 eV.
+And different HFX has similar molecular energy, as all the points are group close to the diagonal line.
+
+The scatter plots of the electrostatic energy and polarization energy as shown in Fig.
+\ref{fig:Estat_qmmm_MADN} and \ref{fig:Edip_qmmm_MADN} also shows that those two energy terms are similar when HFX varies from 0 to 0.25.
+That is, there is no obvious small data points deviated from the diagonal line.
 
@@
 \end{figure}
+
+Furthermore, the plot comparing  electrostatic energy and polarization energy are shown in Fig.\ref{fig:Estat_qmmm_MADN} and Fig.\ref{fig:Edip_qmmm_MADN}.
+The electrostatic energy has a range of 0.1 to -0.6 eV. And there are no small data points deviated from the diagonal line. 
+The polarization energy has a range of -0.5 to -0.8 eV. And the data points are again clustered near the diagonal line.
 
@@
 
-\section{Diffusive Charge velocity Estimation}
-The following table shows the diffusive charge velocity, calculated using the ToF setting and steady state setting.
-For ToF setting, we investigate the situations where the charge transport direction is along the X-axis, Y-axis and Z-axis.
-\begin{table}[htbp]
+\section{Comparison of Diffusive Charge Velocity Between BCP and MADN}
+In this section we compare the diffusive charge velocity between BCP and MADN. 
+The following tables show the diffusive charge velocity for BCP and MADN with HFX=0.05, 0.15, 0.25. The situations of using energy disorder and without energy disorder are considered.
+For the ToF setting, we investigate the situations where the charge transport direction is along the X-axis, Y-axis and Z-axis, as shown in Table \ref{tab:compare_Lx}, \ref{tab:compare_Ly}, and \ref{tab:compare_Lz}.
+
+The diffusive velocity calculated using steady state setting is $v_\text{SS}$, and the comparison is shown in Table \ref{tab:compare_SS}.
+\begin{table}[H]
 \centering
@@
     \cmidrule(r){1-7}
-    0.05 & $7.87 \times 10^{-9}$ & 0.32 & 0 & $4.07 \times 10^{-10}$ & $3.00 \times 10^{-10}$ & 0 \\
-    0.15 & $3.03 \times 10^{-8}$ & 0.38 & 0 & $3.96 \times 10^{-10}$ & $4.67 \times 10^{-10}$ & 0 \\
-    0.25 & $9.54 \times 10^{-8}$ & 0.026 & 0 & $7.24 \times 10^{-10}$ & $7.63 \times 10^{-10}$ & 0 \\
+    0.05 & $7.87 \times 10^{-9}$ & 0.32 & NA & $4.07 \times 10^{-10}$ & $3.00 \times 10^{-10}$ & NA \\
+    0.15 & $3.03 \times 10^{-8}$ & 0.38 & NA & $3.96 \times 10^{-10}$ & $4.67 \times 10^{-10}$ & NA \\
+    0.25 & $9.54 \times 10^{-8}$ & 0.026 & NA & $7.24 \times 10^{-10}$ & $7.63 \times 10^{-10}$ & NA \\
     \bottomrule
     \end{tabular}
-    \caption{Diffusive $\tau_X$ comparison between multiscale modeled BCP and MADN molecular system with PBE0 functional. }
+    \caption{Diffusive $\tau_X$ comparison between multiscale modeled BCP and MADN molecular system with PBE0 functional. The ratio does not apply because the BCP and MADN has different length $L_x$.}
+    \label{tab:compare}
+\end{table}
+
+\begin{table}[H]
+\centering
+\begin{tabular}{c c c c c c c}
+    \toprule
+        &
+        \multicolumn{3}{c}{ with energy $E$} &
+        \multicolumn{3}{c}{all $E=0$}  \\
+    HFX & MADN & BCP & ratio & MADN & BCP & ratio  \\
+    \cmidrule(r){1-7}
+    0.05 & 1.0 & $2.2 \times 10^{-8}$ & $4.5 \times 10^{7}$ & 19 & 24 & 0.80 \\
+    0.15 & 0.31 & $1.8 \times 10^{-8}$ & $1.7 \times 10^{7}$ & 25 & 15 & 1.7 \\
+    0.25 & 0.083 & $2.7 \times 10^{-7}$ & $3.1 \times 10^{5}$ & 11 & 9.4 & 1.2 \\
+    \bottomrule
+    \end{tabular}
+    \caption{Diffusive ToF velocity $v_\text{ToF,X}=\frac{L_X}{\tau_X}$ [m/s] comparison between multiscale modeled BCP and MADN molecular system with PBE0 functional. }
+    \label{tab:compare_Lx}
+\end{table}
+
+\begin{table}[H]
+\centering
+\begin{tabular}{c c c c c c c}
+    \toprule
+        &
+        \multicolumn{3}{c}{ with energy $E$} &
+        \multicolumn{3}{c}{all $E=0$}  \\
+    HFX & MADN & BCP & ratio & MADN & BCP & ratio  \\
+    \cmidrule(r){1-7}
+    0.05 & 0.44 & $5.8 \times 10^{-8}$ & $7.6 \times 10^{6}$ & 17 & 24 & 0.71 \\
+    0.15 & 0.057& $1.0 \times 10^{-7}$  & $5.7 \times 10^{5}$ & 17 & 15 & 1.1 \\
+    0.25 & 0.041 & $2.8 \times 10^{-7}$ & $1.4 \times 10^{5}$ & 10 & 9.5 & 1.0 \\
+    \bottomrule
+    \end{tabular}
+    \caption{Diffusive ToF velocity $v_\text{ToF,Y}=\frac{L_Y}{\tau_Y}$ [m/s] comparison between multiscale modeled BCP and MADN molecular system with PBE0 functional. }
+    \label{tab:compare_Ly}
+\end{table}
+
+\begin{table}[H]
+\centering
+\begin{tabular}{c c c c c c c}
+    \toprule
+        &
+        \multicolumn{3}{c}{ with energy $E$} &
+        \multicolumn{3}{c}{all $E=0$}  \\
+    HFX & MADN & BCP & ratio & MADN & BCP & ratio  \\
+    \cmidrule(r){1-7}
+    0.05 & 2.0 & $5.6 \times 10^{-7}$ & $3.4 \times 10^{6}$ & 19 & 24 & 0.80 \\
+    0.15 & 2.6 & $1.2 \times 10^{-6}$ & $2.2 \times 10^{6}$ & 19 & 15 & 1.3 \\
+    0.25 & 1.0 & $5.4 \times 10^{-6}$ & $1.0 \times 10^{6}$ & 10 & 9.4 & 1.1 \\
+    \bottomrule
+    \end{tabular}
+    \caption{Diffusive ToF velocity $v_\text{ToF,Z}=\frac{L_Z}{\tau_Z}$ [m/s] comparison between multiscale modeled BCP and MADN molecular system with PBE0 functional. }
+    \label{tab:compare_Lz}
 \end{table}
@@
     \cmidrule(r){1-7}
-    0.05 & 1.0 & $2.2 \times 10^{-8}$ & 0 & 19 & 24 & 0 \\
-    0.15 & 0.26 & $1.8 \times 10^{-8}$ & 0 & 20 & 15 & 0 \\
-    0.25 & 0.083 & $2.7 \times 10^{-7}$ & 0 & 11 & 9.4 & 0 \\
-    \bottomrule
-    \end{tabular}
-    \caption{Diffusive ToF velocity $v_\text{ToF,X}=\frac{L_X}{\tau_X}$ [m/s] comparison between multiscale modeled BCP and MADN molecular system with PBE0 functional. }
-\end{table}
-
-\begin{table}[htbp]
-\centering
-\begin{tabular}{c c c c c c c}
-    \toprule
-        &
-        \multicolumn{3}{c}{ with energy $E$} &
-        \multicolumn{3}{c}{all $E=0$}  \\
-    HFX & MADN & BCP & ratio & MADN & BCP & ratio  \\
-    \cmidrule(r){1-7}
-    0.05 & 0.44 & $5.8 \times 10^{-8}$ & 0 & 17 & 24 & 0 \\
-    0.15 & 0.057& $1.0 \times 10^{-7}$  & 0 & 17 & 15 & 0 \\
-    0.25 & 0.041 & $2.8 \times 10^{-7}$ & 0 & 10 & 9.5 & 0 \\
-    \bottomrule
-    \end{tabular}
-    \caption{Diffusive ToF velocity $v_\text{ToF,Y}=\frac{L_Y}{\tau_Y}$ [m/s] comparison between multiscale modeled BCP and MADN molecular system with PBE0 functional. }
-\end{table}
-
-\begin{table}[htbp]
-\centering
-\begin{tabular}{c c c c c c c}
-    \toprule
-        &
-        \multicolumn{3}{c}{ with energy $E$} &
-        \multicolumn{3}{c}{all $E=0$}  \\
-    HFX & MADN & BCP & ratio & MADN & BCP & ratio  \\
-    \cmidrule(r){1-7}
-    0.05 & 2.0 & $5.6 \times 10^{-7}$ & 0 & 19 & 24 & 0 \\
-    0.15 & 2.6 & $1.2 \times 10^{-6}$ & 0 & 19 & 15 & 0 \\
-    0.25 & 1.0 & $5.4 \times 10^{-6}$ & 0 & 10 & 9.4 & 0 \\
-    \bottomrule
-    \end{tabular}
-    \caption{Diffusive ToF velocity $v_\text{ToF,Z}=\frac{L_Z}{\tau_Z}$ [m/s] comparison between multiscale modeled BCP and MADN molecular system with PBE0 functional. }
-\end{table}
-
-\begin{table}[htbp]
-\centering
-\begin{tabular}{c c c c c c c}
-    \toprule
-        &
-        \multicolumn{3}{c}{ with energy $E$} &
-        \multicolumn{3}{c}{all $E=0$}  \\
-    HFX & MADN & BCP & ratio & MADN & BCP & ratio  \\
-    \cmidrule(r){1-7}
-    0.05 & 0.10 & $1.5 \times 10^{-7}$ & 0 & 3.8 & 2.4 & 0 \\
-    0.15 & 0.031 & $1.5 \times 10^{-8}$ & 0 & 13 & 0.58 & 0 \\
-    0.25 & 0.0043 & $3.6 \times 10^{-7}$ & 0 & 4.0 & 1.07 & 0 \\
+    0.05 & 0.10 & $1.5 \times 10^{-7}$ & $6.7 \times 10^{5}$ & 3.8 & 2.4 & 1.6 \\
+    0.15 & 0.031 & $1.5 \times 10^{-8}$ & $2.1 \times 10^{6}$ & 13 & 0.58 & 22 \\
+    0.25 & 0.0043 & $3.6 \times 10^{-7}$ & $1.2 \times 10^{4}$ & 4.0 & 1.07 & 3.7 \\
     \bottomrule
@@
     \caption{Steady state diffusive velocity $v_\text{SS}$ [m/s] comparison between multiscale modeled BCP and MADN molecular system with PBE0 functional. }
+    \label{tab:compare_SS}
 \end{table}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The ToF is estimated from electronic structure ($E$, $\lambda$ and $\log_{10}(J^2)$) data obtained using different HFX. Each HFX gives an electronic structure. 
-For the BCP systems:
+\section{ToF distribution of BCP and MAND}
+Different HFX affect the calculated ToF. 
+The ToF is calculated from electronic structure ($E$, $\lambda$ and $\log_{10}(J^2)$) data, that is, ToF is a function with the input of all electronic structure parameters:
+\begin{equation}
+    \tau = g(x_1, x_2, \cdots, x_N)
+\end{equation}
+where each electronic structure parameter $x_i$ for $i=1,2,\cdots,N$ contains uncertainties. 
+Each of those parameters are obtained using different HFX.
+
+So the multiscale model use different HFX values to general samples of the paramters $(x_1, x_2, \cdots, x_N)$ and eventually different ToF.
+
+Since the exchange-correlation functional is not known, each parameter $x_i$ has uncertain. 
+To consider the maximum amount of uncertainties according to the obtained $x_i$ with different HFX, $x_i$ can be modeled as a normal distribution with the mean $\bar{x}_i$ and standard deviation $\sigma_{x_i}$ being the HFX sample mean and standard deviation, respectively.
+
+Then we use Monte Carlo scheme to estimate the distribution of the ToF:
+\begin{enumerate}
+\item For all $i=1,2,\cdots, N$, sample a realization $(x_1, x_2,\cdots, x_N)$ where $x_i \in \mathcal{N}(\bar{x}_i, \sigma_{x_i})$. 
+\item Calculate ToF using the sampled data set $(x_1, x_2,\cdots, x_N)$. 
+\item Repeat step 1 and 2 for $N_\text{MC} = 50000$ times to obtain $N_\text{MC}$ ToF. Plot the distribution of the ToF.
+\item Fit the distribution of $log_{10}(\text{ToF})$ to Gamma distribution.
+\end{enumerate}
+
+The distribution of ToF calculated as the CTMC where transition parameters are varied is unknown, so we attempt to fit the distribution of ToF to Gamma distribution. The reason is as followed.
+
+From equation \ref{eq:hitting_time}, the ToF can be considered as the some combination of occupation time in the molecules, which is $log_{10}(\omega_{i}^{-1})$. 
+When the parameters $E, J_{ij}, \lambda_{ij}$ are normally distributed random variables, the calculated ToF shows that variables $E,\lambda_{ij}$ has a larger influence than $J_{ij}$. 
+The Marcus rate uses $E,\lambda_{ij}$ in the exponential form. If $\Delta E$ is normally distributed, then $log_{10}(\omega_{i}^{-1})$ is Gamma distributed. 
+Since $E$ has greater influence to ToF than $\lambda_{ij}, J_{ij}$ and to be consistent, Gamma distribution is used to fit the Monte Carlo sampled ToF in all the investigated cases.
+
+To understand which uncertainty among $E, \lambda, J_{ij}$ has a greater impact on the ToF, we study the following distribution of ToF:
+\begin{enumerate}
+    \item Fixed the $\lambda$ to be the averaged $\bar{\lambda}$, and $J_{ij}$ to be the averaged $\bar{J}_{ij}$.
+Then each molecule energy $E_i$ is sampled from the normal distribution $\mathcal{N}(\bar{E}_i, \sigma^2_{E_i})$.
+Finally obtain and plot $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|E_i \text{ uncertain})$.
+    \item Fixed the $E_i$ to be the average $\bar{E}_i$ and and $J_{ij}$ to be the averaged $\bar{J}_{ij}$.
+Then $\lambda$ is sampled from the normal distribution $\mathcal{N}(\bar{\lambda}, \sigma^2_{\lambda})$.
+Finally obtain and plot $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|\lambda \text{ uncertain})$.
+    \item Fixed the $E_i$ to be the average $\bar{E}_i$ and $\lambda$ to be the averaged $\bar{\lambda}$.
+Then $J_{ij}$ is sampled from the normal distribution $\mathcal{N}(\bar{J}_{ij}, \sigma^2_{J_{ij}})$.
+Finally obtain and plot $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$.
+    \item Both $E_i$, $\lambda$ and $J_{ij}$ are sample from their normal distribution: $\mathcal{N}(\bar{E}_i, \sigma^2_{E_i})$, $\mathcal{N}(\bar{\lambda}, \sigma^2_{\lambda})$ and $\mathcal{N}(\bar{J}_{ij}, \sigma^2_{J_{ij}})$.
+Then obtain and plot $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$.
+\end{enumerate}
+
+Then we compute the Wasserstein distance $D(\cdot, \cdot)$ for the following pair of distribution: 
+\begin{itemize}
+    \item $(P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain}),P(\log_{10}(\tau)|E_i \text{ uncertain}))$
+    \item $(P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain}),P(\log_{10}(\tau)|\lambda \text{ uncertain}))$
+    \item $(P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain}),P(\log_{10}(\tau)|J_{ij} \text{ uncertain}))$
+\end{itemize}
+The Wasserstein distance quantifies similarity between two distribution and thus can be used to find which parameter variation has a greater contribution to the total distribution $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$.
+
+The ToF distribution and Gamma fitted results for the BCP systems with energy disorder is shown in Fig.\ref{fig:mle_BCP_withE}.
 \begin{figure}[H]
@@
     \includegraphics[width=0.85\textwidth]{figs/BCP_HFX/fig_mle_BCP_withE.pdf}
-    \caption{Distribution of ToFs in the multiscale modeled BCP system using PBE0 functional when (a) the molecule site energy $E$ are sampled from a normal distribution $E \sim N(E_\text{ave},E^2_\text{std})$, (b) the reorganization energy $\lambda$ are sampled from a normal distribution $\lambda \sim N(\lambda_\text{ave},\lambda^2_\text{std})$, (c) the quantity $\log_{10}(J^2)$ are sampled from a normal distribution $\log_{10}(J^2) \sim N(\mathbb{E}[\log_{10}(J^2)], \textbf{Var}[\log_{10}(J^2)] )$.
+    \caption{Distribution of ToFs in the multiscale modeled BCP system using PBE0 functional and varying HFX,  when 
+    (a) $P(\log_{10}(\tau)|E_i \text{ uncertain})$, 
+    (b) $P(\log_{10}(\tau)|\lambda \text{ uncertain})$, 
+    (c) $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$, 
+    (d) $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$.
+The red star indicates the ToF calculated using the average $\bar{E_i}, \bar{J}_{ij}, \bar{\lambda}$, and the red circles indicate the ToF obtained using different HFX.}
+    \label{fig:mle_BCP_withE}
+\end{figure}
+
+When the energy disorder in BCP system is not considered, that is, all the molecule energy are zero, the distribution of ToF is shown in Fig.\ref{fig:mle_BCP_noE}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.99\textwidth]{figs/BCP_HFX/fig_mle_BCP_noE.pdf}
+    \caption{Distribution of ToFs in the multiscale modeled BCP system using PBE0 functional and varying HFX. Energy disorder is not consider. 
+    (a) $P(\log_{10}(\tau)|\lambda \text{ uncertain})$, 
+    (b) $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$, 
+    (c) $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$.
+The red star indicates the ToF calculated using the average $\bar{E_i}, \bar{J}_{ij}, \bar{\lambda}$, and the red circles indicate the ToF obtained using different HFX.}
+    \label{fig:mle_BCP_noE}
+\end{figure}
+
+The ToF distribution and Gamma fitted results for the MADN systems are as followed:
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.85\textwidth]{figs/MADN_HFX/fig_mle_MADN_withE.pdf}
+    \caption{Distribution of ToFs in the multiscale modeled MADN system using PBE0 functional and varying HFX. 
+    (a) $P(\log_{10}(\tau)|E_i \text{ uncertain})$, 
+    (b) $P(\log_{10}(\tau)|\lambda \text{ uncertain})$, 
+    (c) $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$, 
+    (d) $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$.
+The red star indicates the ToF calculated using the average $\bar{E_i}, \bar{J}_{ij}, \bar{\lambda}$, and the red circles indicate the ToF obtained using different HFX.}
+    \label{fig:mle_MADN_withE}
+\end{figure}
+
+When the energy disorder in MADN system is not considered, that is, all the MADN molecule energy are zero, the distribution of ToF is shown in Fig.\ref{fig:mle_MADN_noE}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.99\textwidth]{figs/MADN_HFX/fig_mle_MADN_noE.pdf}
+    \caption{Distribution of ToFs in the multiscale modeled MADN system using PBE0 functional and varying HFX. Energy disorder is not consider. 
+    (a) $P(\log_{10}(\tau)|\lambda \text{ uncertain})$, 
+    (b) $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$, 
+    (c) $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$.
+The red star indicates the ToF calculated using the average $\bar{E_i}, \bar{J}_{ij}, \bar{\lambda}$, and the red circles indicate the ToF obtained using different HFX.}
+    \label{fig:mle_MADN_noE}
+\end{figure}
+
+\section{Distribution of Steady State Velocity}
+The distribution of steady state velocity of MADN is shown as Fig.\ref{fig:mle_MADN_withE_SS} and \ref{fig:mle_MADN_noE_SS}. 
+Those distribution shows that the variation in $v_\text{SS}$ distribution is greater than ToF distribution.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.85\textwidth]{figs/MADN_HFX/fig_mle_MADN_withE_SS.pdf}
+    \caption{Distribution of steady state velocity $v_\text{SS}$ in the multiscale modeled MADN system using PBE0 functional when (a) the molecule site energy $E$ are sampled from a normal distribution $E \sim N(E_\text{ave},E^2_\text{std})$, (b) the reorganization energy $\lambda$ are sampled from a normal distribution $\lambda \sim N(\lambda_\text{ave},\lambda^2_\text{std})$, (c) the quantity $\log_{10}(J^2)$ are sampled from a normal distribution $\log_{10}(J^2) \sim N(\mathbb{E}[\log_{10}(J^2)], \textbf{Var}[\log_{10}(J^2)] )$.
 (d) Both $E$, $\lambda$ and $\log_{10}(J^2)$ are sampled from the normal distribution.
 }
-    \label{fig:mle_BCP_withE}
+    \label{fig:mle_MADN_withE_SS}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.99\textwidth]{figs/BCP_HFX/fig_mle_BCP_noE.pdf}
-    \caption{Distribution of ToFs in the multiscale modeled BCP system using PBE0 functional. All molecule energies are set to be zero.  
+    \includegraphics[width=0.99\textwidth]{figs/MADN_HFX/fig_mle_MADN_noE_SS.pdf}
+    \caption{Distribution of steady state velocity $v_\text{SS}$ in the multiscale modeled MADN system using PBE0 functional. All molecule energies are set to be zero.  
     The plots are for the situation: (a) The reorganization energy $\lambda$ are sampled from a normal distribution $\lambda \sim N(\lambda_\text{ave},\lambda^2_\text{std})$.
@@
 }
-    \label{fig:mle_BCP_noE}
-\end{figure}
-
-For the MADN system:
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.85\textwidth]{figs/MADN_HFX/fig_mle_MADN_withE.pdf}
-    \caption{Distribution of ToFs in the multiscale modeled MADN system using PBE0 functional when (a) the molecule site energy $E$ are sampled from a normal distribution $E \sim N(E_\text{ave},E^2_\text{std})$, (b) the reorganization energy $\lambda$ are sampled from a normal distribution $\lambda \sim N(\lambda_\text{ave},\lambda^2_\text{std})$, (c) the quantity $\log_{10}(J^2)$ are sampled from a normal distribution $\log_{10}(J^2) \sim N(\mathbb{E}[\log_{10}(J^2)], \textbf{Var}[\log_{10}(J^2)] )$.
-(d) Both $E$, $\lambda$ and $\log_{10}(J^2)$ are sampled from the normal distribution.
-}
-    \label{fig:mle_MADN_withE}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.99\textwidth]{figs/MADN_HFX/fig_mle_MADN_noE.pdf}
-    \caption{Distribution of ToFs in the multiscale modeled MADN system using PBE0 functional. All molecule energies are set to be zero.  
-    The plots are for the situation: (a) The reorganization energy $\lambda$ are sampled from a normal distribution $\lambda \sim N(\lambda_\text{ave},\lambda^2_\text{std})$.
-(b) the quantity $\log_{10}(J^2)$ are sampled from a normal distribution $\log_{10}(J^2) \sim N(\mathbb{E}[\log_{10}(J^2)], \textbf{Var}[\log_{10}(J^2)] )$.
-(c) Both $\lambda$ and $\log_{10}(J^2)$ are sampled from the normal distribution.
-}
-    \label{fig:mle_MADN_noE}
+    \label{fig:mle_MADN_noE_SS}
 \end{figure}
@@
 \begin{comment}
-\textbf{Point 1:} To investigate the effect of different functionals $f^\text{DFT}$ on electronic structures, we compare the energies $E_i$ and couplings $J_{i,j}$ for all molecule indices $i,j$.
+\textbf{Point 1:} To investigate the effect of different functionals $f^\text{DFT}$ on electronic structures, we compare the energies $E_i$ and couplings $J_{ij}$ for all molecule indices $i,j$.
 Scatter plots in Figures \ref{fig:scatterE} and \ref{fig:scatterJ} illustrate these comparisons.
@@
 
-\textbf{Point 2:} Both $E_i$ and $J_{i,j}$ are distributions.
+\textbf{Point 2:} Both $E_i$ and $J_{ij}$ are distributions.
 To quantify the impact of these distributions on $\Delta$ToF, we plot the Wasserstein distance versus $\Delta$ToF.
@@
 \textbf{Point8:} For each molecule energy $E_i$, we use maximum likelihood estimation to obtain the $N(\bar{E_i},\sigma(E_i))$.
-Then use sample a set of $E_i$ and calculate the ToF, with $\lambda,J_{i,j}$ fixed at the average values.
+Then use sample a set of $E_i$ and calculate the ToF, with $\lambda,J_{ij}$ fixed at the average values.
 Repeat the $E_i$ sampling and ToF calculation for 100000 times, and plot ToF distribution. This process is called the Monte Carlo sampling.
 
-Similarly, for $\lambda,J_{i,j}$, we perform the Monte Carlo sampling as been done for $E_i$. The resulting ToF is shown in Fig.\ref{fig:ToFs}.
+Similarly, for $\lambda,J_{ij}$, we perform the Monte Carlo sampling as been done for $E_i$. The resulting ToF is shown in Fig.\ref{fig:ToFs}.
 
@@
 The red curve is fitted to a gamma distribution.
-(b)The ToF distribution for 100000 samples where each $\lambda$ is drawn from $N(\bar{\lambda},\sigma(\lambda))$.(c)The ToF distribution for 100000 samples when each $J_{i,j}$ is drawn from $N(\bar{J_{i,j}},\sigma(J_{i,j}))$.}
+(b)The ToF distribution for 100000 samples where each $\lambda$ is drawn from $N(\bar{\lambda},\sigma(\lambda))$.(c)The ToF distribution for 100000 samples when each $J_{ij}$ is drawn from $N(\bar{J_{ij}},\sigma(J_{ij}))$.}
     \label{fig:ToFs}
@@
 
-This figure shows that ToF is more sensitive to change in $E_i$ and least sensitive to $J_{i,j}$, even though from the scatter plots Fig.\ref{fig:scatterJ} the $J_{i,j}$ has a very large magnitude deviation.
+This figure shows that ToF is more sensitive to change in $E_i$ and least sensitive to $J_{ij}$, even though from the scatter plots Fig.\ref{fig:scatterJ} the $J_{ij}$ has a very large magnitude deviation.
 
@@
     \item When $\lambda \in N(\bar{\lambda},\sigma(\lambda))$, the $\log_{10}(\text{ToF})$ has mean -1.91 and a standard deviation of 0.34.
-    \item When $J_{i,j} \in N(\bar{J_{i,j}},\sigma(J_{i,j}))$, the $\log_{10}(\text{ToF})$ has mean -2.92 and a standard deviation of 0.08.
+    \item When $J_{ij} \in N(\bar{J_{ij}},\sigma(J_{ij}))$, the $\log_{10}(\text{ToF})$ has mean -2.92 and a standard deviation of 0.08.
 \end{itemize}
 
-When we use $E_i \in N(\bar{E_i},\sigma(E_i))$, $\lambda \in N(\bar{\lambda},\sigma(\lambda))$, $J_{i,j} \in N(\bar{J_{i,j}},\sigma(J_{i,j}))$ at the same to perform the Monte Carlo sampling of ToF calculation, the ToF is shown in Fig.\ref{fig:ToFs2}.
+When we use $E_i \in N(\bar{E_i},\sigma(E_i))$, $\lambda \in N(\bar{\lambda},\sigma(\lambda))$, $J_{ij} \in N(\bar{J_{ij}},\sigma(J_{ij}))$ at the same to perform the Monte Carlo sampling of ToF calculation, the ToF is shown in Fig.\ref{fig:ToFs2}.
 the $\log_{10}(\text{ToF})$ has mean -2.72 and a standard deviation of 0.80.
@@
     \includegraphics[width=0.6\textwidth]{figs/fig_mle2.png}
-    \caption{The ToF distribution for 100000 samples where each $E_i$ is drawn from $N(\bar{E}_i,\sigma(E_i))$, $\lambda$ is drawn from $N(\bar{\lambda},\sigma(\lambda))$, and each $J_{i,j}$ is drawn from $N(\bar{J_{i,j}},\sigma(J_{i,j}))$.
+    \caption{The ToF distribution for 100000 samples where each $E_i$ is drawn from $N(\bar{E}_i,\sigma(E_i))$, $\lambda$ is drawn from $N(\bar{\lambda},\sigma(\lambda))$, and each $J_{ij}$ is drawn from $N(\bar{J_{ij}},\sigma(J_{ij}))$.
 The red curve is fitted to a gamma distribution.}

### 2024-10-16 paper.tex
update

@@
 \begin{abstract}
-In this paper, the time-of-flight (ToF) is used to quantify the charge mobility in OSC. 
-Using ToF as the quantity of interest, the uncertainty effect of the DFT functionals on the ToF in a BCP device is studied. 
-Using a total of 10 different DFT functionals, we find that the electronic structure properties have similar distributions as indicated by Wasserstein distance, while the ToF can have a relatively large deviation.
-Further investigation reveals that ToF can be sensitive to the energy of a single molecule, leading to the ToF being sensitive to DFT functionals.
 
-Further investigation reveals that the BHANDHLYP functional leads to a trap site, and the charge mobility is very sensitive to the trap sites' energy, so a small change in the site's energy results in a large deviation of ToF.
-We further estimate the charge mobility distribution due to the uncertainty in electronic structure properties, and those properties' uncertainty is obtained from the maximum likelihood estimation of the 10 data points calculated using the 10 DFT functionals.
-Ultimately, a confidence level of charge mobility is obtained, and it is found that the uncertainty in site energy has the most significant effect on the ToF. 
 \end{abstract}
@@
 The effect of the uncertainty from the DFT exchange-correlation functional on the multiscale model is not yet explored in literatures. 
-The goal of this work is to quantify the uncertainty effect of the DFT exchange-correlation functional on the charge dynamics in OSCs and to study the robustness of the multiscale model.
+The goal of this work is to quantify the uncertainty effect of the DFT exchange-correlation functional on the charge dynamics in OSCs and to study the robustness of the multiscale model, with a particular focus on the uncertainty represented by the HF level.
 
@@
 \begin{enumerate}
-    \item How do DFT functionals change the electronic structures: reorganization energy, distribution of molecule energies and coupling elements? 
-    \item How do DFT functionals change the charge mobility?
+    \item How does HF level change the electronic structures: reorganization energy, distribution of molecule energies and coupling elements? 
+    \item How does HF level change the charge mobility?
     \item Which electronic structure (among energy, coupling element and reorganization energy) uncertainty has the most impact on the charge mobility distribution?
@@
 where $\mathbf{D} = \text{diag}(D_i)$ is the out-degree matrix of $\mathbf{W}$.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results on BCP}
-\label{sec:result}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-A OSC device consisting of 1000 BCP molecules arranged in $8 \times 8 \times 8$ cubic box is simulated using MD, as shown in Fig. \ref{fig:MSM}(a).
-The \textit{Source} contains molecules whose COM have X-coordinates $0 < r^x_i < 0.5$ nm, and \textit{Sink} molecules $7.5 < r^x_i < 8$. 
-This section presents the molecule energy distribution, coupling element distribution, reorganization energies and ToFs calculated using the 10 DFT functionals. 
-Using the PBE0 functional as a reference, the difference in electronic structure distributions due to DFT functionals is measured by the Wasserstein distance.
-In contrast to the small Wasserstein distance between the electronic structure distributions, the difference in ToF $\Delta \tau$ is relatively large.
-Next, the change of the graph connectivity due to different DFT functionals is used to explain the $\Delta \tau$.
-Following this, a normal distribution estimated from maximum likelihood is used to represent the uncertainty in each electronic structure parameters.
-Then distributions of ToF are obtained using the electronic structure parameters generated by Monte Carlo sampling from the estimated distributions.
-Finally, the sensitivities of $E_i,J_{ij},\lambda_{ij}$ to ToF are compared, confidence level of ToFs are estimated.
+\section{Results on MADN}
 
-\subsection{Electronic Structure Parameters and ToFs}
-Using ten different functionals, the molecule energies, coupling elements and reorganization energies are calculated from the multiscale model with ten different DFT functional.
+In this study, we investigate the hole-transporting organic semiconductor MADN (2-Methyl-9,10-di(naphth-2-yl)anthracene).
+Essential steps in our multiscale model involve calculating the dipole moment $\mu$ and the isotropic polarizability $P_\text{iso}$ for both neutral and charged states in the optimized geometry MADN molecule.
+These properties are crucial for evaluating molecular energy contributions from electrostatic and polarization effects.
 
-Table \ref{tab:para} summarizes the names of the DFT functionals, the amount of Hartree-Fock exchange (HFX), the reorganization energies, ToFs, the standard deviation of the molecule energy distributions, the drift ToFs under an electric field $6 \times 10^7$ V/m and mobility.
-The table indicates that while the energy standard deviations $\sigma(E)$ are similar across different functionals, the ToF vary significantly, notably for functionals like BHANDHLYP, M06L, and BHLYP.
+Figure \ref{fig:autogen_MADN} illustrates the dependence of the dipole moment $\mu$, isotropic polarizability $P_\text{iso}$, reorganization energy $\lambda$, and energy disorder $\sigma(E)$ on the Hartree-Fock exchange (HFX) parameter.
 
-\begin{table}[H]
-    \centering
-    \begin{tabular}{c c c c c c c}
-    \hline
-        Functional & HFX & $\lambda_{ij}$ [eV] & ToF [s] & $\sigma(E)$ & drift ToF [s] & $\mu$ [m/s] \\ 
-        \hline
-        PBE0 & 0.25 & 0.388 & $1.23\times 10^{-3}$ & 0.175 & $1.44 \times 10^{-6}$ & $9.40\times 10^{-7}$ \\
-        PBE & 0 & 0.303 & $1.04\times 10^{-3}$ & 0.172 & $2.27 \times 10^{-7}$ & $5.95 \times 10^{-6}$ \\ 
-        B3LYP & 0.20 & 0.375 & $4.28\times 10^{-3}$ & 0.175  & $3.22\times 10^{-7}$ & $4.08 \times 10^{-6}$ \\
-        BHANDHLYP & 0.5 & 0.494 & \textbf{737.94} & 0.192  & $4.75\times 10^{-2}$ & $2.86\times 10^{-11}$ \\
-        TPSS & 0 & 0.310 & $1.37\times 10^{-2}$ & 0.168  & $1.03 \times 10^{-6}$ & $1.30\times 10^{-7}$ \\
-        BP86 & 0 & 0.304 & $7.46\times 10^{-3}$ & 0.175  & $5.81 \times 10^{-7}$ & $2.33\times 10^{-6}$ \\
-        wB97X & 0.157 & 0.505 & $2.92\times 10^{-2}$ & 0.191  & $2.01\times 10^{-6}$  & $6.74\times 10^{-7}$ \\
-        wB97X-D3 & 0.195 & 0.496 & $4.89\times 10^{-2}$ & 0.180  & $2.50 \times 10^{-6}$ & $5.42 \times 10^{-7}$ \\
-        M06L & 0 & 0.312 & 0.319 & 0.165 & $2.11 \times 10^{-5}$ & $6.42 \times 10^{-8}$ \\
-        BHLYP & 0.5 & 0.493 & 2.47 & 0.192  & $5.96 \times 10^{-5}$ & $ 2.28\times 10^{-8}$  \\
-    \hline
-    \end{tabular}
-    \caption{DFT functional HF exchange scaling (HFX), calculated values of reorganization energy ($\lambda_{ij}$), diffusive ToF, energy disorder ($\sigma(E)$), drift ToF, and mobility ($\mu$) for BCP molecules for different DFT functionals.}
-    \label{tab:para}
-\end{table}
-
-The functional BHANDHLYP gives a ToF much larger than the rest of the 9 functionals. 
-The reason for this large ToF in BHANDHLYP is that one molecule has relatively low energy, and the out-going rate for this molecule is very small, eventually leading to large ToF. 
-However, such large difference in a material system is non-physical, and studying the uncertain quantification based on those ToF data can not indicate anything on the robustness of the multiscale model.
-
-A noticeable difference in all the different functional is the amount of HF for approximating the exchange-correlations. 
-The large HFX cases (BHANDHLYP and BHLYP) have large ToF, while other functionals have smaller HFX. In commonly practices, most functionals use small HFX.
-
-In our next step, the functional is fixed to be the commonly used PBE0 functional, the HFX is varied to investigate the effect of HFX on the molecular properties and ToF.
-
-\subsection{BCP molecule with different HFX}
-Our first investigation use the range of HFX=$0.05,0.15,0.23,0.24,0.25,0.26,0.27,0.35,0.45,0.55$.
-The values of HFX=$0.23,0.24,0.26,0.27$ are used because we want to see if a small perturbation in HFX would affect ToF significantly.
-
-Since ToF is sensitively affected by site energy, which is affected by the isotropic polarizability $P_\text{iso}$ and dipole moment $\mu$ of the molecules, we plot the those molecular properties as a function of HFX.
+%
 \begin{figure}[H]
     \centering
-    \includegraphics[width=0.9\textwidth]{figs/BCP_HFX/fig_autogen_BCP.pdf}
-    \caption{(a) The neutral state BCP molecule dipole moment $\mu$, (b) isotropic polarizability $P_\text{iso}$, (c) reorganization energies $\lambda$ and (d) energy disorder $\sigma(E)$ as a function of the HFX parameters.
-}
-    \label{fig:autogen}
+    \includegraphics[width=0.80\textwidth]{figs/MADN_HFX/fig_autogen.pdf}
+    \caption{(a) The dipole moment of neutral state MAND molecule $\mu$, (b) isotropic polarizability $P_\text{iso}$, (c) reorganization energies $\lambda$ and (d) energy disorder $\sigma(E)$ as a function of the HFX parameters (denoted by $\alpha$).}
+    \label{fig:autogen_MADN}
 \end{figure}
-The Fig.\ref{fig:autogen}(a) shows that as HFX increase, the dipole moment increases first linear in the range of HFX=0.05 to 0.35, then a relatively large increase at HFX=0.35 to 0.55.
+%
 
-Figure \ref{fig:autogen}(b) shows that as HFX increase, the n state and h state BCP molecule has decreasing isotropic polarizability, showing that the molecule is getting more difficult to be polarized.
-However, the change of $P_\text{iso}$ is more dramatic in the h state molecules. 
-Since the difference between the n state $P_\text{iso}$ and h state $P_\text{iso}$ is getting smaller, the contribution of polarizability effect on the energy disorder is weaker.
-This results in a large energy disorder as HFX increase.
+Figure \ref{fig:autogen_MADN}(a) shows a decrease in the dipole moment with increasing HFX, exhibiting a notable drop at HFX = 0.25.
 
-Fig.\ref{fig:autogen}(c) shows that as HFX increase, reorganization energies are higher.
-Since the molecule requires more energy to reorient itself during the charge transfer process, the higher reorganization energy can potentially slow down charge transport when there is no energy disorder present.
+Figure \ref{fig:autogen_MADN}(b) demonstrates a linear decrease in isotropic polarizability for both neutral and charged MADN states as HFX increases from 0 to 0.25, indicating reduced molecular polarizability.
 
-Fig.\ref{fig:autogen}(d) shows that when HFX=0.05-0.3 the energy disorder is relatively small (less than 0.2 eV).
-When HFX=0.35-0.55, the energy disorder $\sigma(E)>0.22$.
-This pattern is consistent with the change of $P_\text{iso}$ as shown in Fig.
-\ref{fig:autogen}(b)
+Figure \ref{fig:autogen_MADN}(c) indicates an increase in reorganization energy $\lambda$ with higher HFX, reflecting greater energy requirements for electronic adjustments during charge transfer.
+This increase is nonlinear compared to the linear decrease in $P_\text{iso}$.
 
-The ToF of the BCP molecular system calculated using different HFX is shown in table \ref{tab:ToF_BCP_HFX}.
-This table shows that for HFX=0.35,0.45,0.55, the ToFs are extremely large compared to the ToFs for HFX<0.3.
-In contrast to the almost linear HFX-$\lambda$ relationship, those large ToFs are not physical.
+Figure \ref{fig:autogen_MADN}(d) shows that the energy disorder $\sigma(E)$ for MADN are similar and close to \unit[0.08]{eV} under different HFX values.
+
+The ToF and corresponding diffusive velocity $v_\text{ToF}$ are presented in Table \ref{tab:ToF_MADN_HFX}.
+For boundary conditions, the \textit{Source} region contains molecules with X-coordinates $0 < r^x_i < 0.5$ nm, and the \textit{Sink} region contains molecules with X-coordinates $8.5 < r^x_i < 9$ nm.
+We also consider scenarios without energy disorder to model systems where all molecules have uniform energy.
 
@@
     \hline
-        HFX & ToF [s] & $v_\text{ToF}$ [m/s] & ToF(no $E$) [s] & $v_\text{ToF}$(no $E$) [m/s] \\
-    \hline
-        0.05 & 0.32 & $2.2 \times 10^{-8}$ & $3.0 \times 10^{-10}$ & 24 \\
-        0.15 & 0.39 & $1.8 \times 10^{-8}$ & $4.7 \times 10^{-10}$ & 15 \\
-        0.23 & 0.020 & $3.6 \times 10^{-7}$ & $6.8 \times 10^{-10} $ & 10 \\
-        0.24 & 0.030 & $2.4 \times 10^{-7}$ & $7.0 \times 10^{-10} $ & 10 \\
-        0.25 & 0.026 & $2.7 \times 10^{-7}$ & $7.6 \times 10^{-10}$ & 9.4 \\
-        0.26 & 3.2 & $4.5 \times 10^{-9}$ & $7.8 \times 10^{-10}$ & 22 \\
-        0.27 & 0.036 & $2.0 \times 10^{-7}$ & $9.2 \times 10^{-10}$ & 7.8 \\
-        0.35 & $1.7 \times 10^7 $ & $4.1 \times 10^{-16}$ & $1.0 \times 10^{-9}$ & 7.1 \\
-        0.45 & $1.8 \times 10^4$ & $3.6 \times 10^{-12}$ & $1.3 \times 10^{-9}$ & 5.4\\
-        0.55 & $1.2 \times 10^9 $ & $5.7 \times 10^{-18}$ & $1.9 \times 10^{-9} $ & 3.8 \\
-    \hline
-    \end{tabular}
-    \caption{The ToF and diffusive velocity calculated by ToF along a distance $L_x = 7.1$ [nm] with and without energy disorder of the BCP system as a function of the HFX. }
-    \label{tab:ToF_BCP_HFX}
-\end{table}
-
-The reason for this non-physical ToF is that some molecules have extremely small calculated energies.
-
-BCP contains two N atoms which are very difficult to be polarized, resulting the BCP molecule energy and the Thole model being very sensitive to the atomic charges and polarizability.
-
-Furthermore, each molecule in the BCP system has its own topology with different atomic charges and polarizability compared to the optimized BCP structure.  
-Those factors result in the fact that when the atomic charges or polarizability exceeds a certain range, the energy calculation will be very non-physical.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.95\textwidth]{figs/BCP_HFX/scatterE_qmmm.pdf}
-    \caption{Scatter plot of BCP site energy calculated from different HFX, compared to the site energy calculated from HFX=0.25 (The PBE0 functional).
-The brighter color near the diagonal lines indicates denser population of the molecules.
-The top and right histogram show the energy distributions.}
-    \label{fig:E_qmmm_BCP}
-\end{figure}
-
-Figure \ref{fig:E_qmmm_BCP} shows that the molecule energy calculated by the PBE0 functional has a range of -0.3 to -1.7 eV.
-When $ 0.05 \leq HFX \leq 0.27 $, the molecule energies also have a range of -0.3 to -1.7 eV.
-
-For HFX=0.35,0.45, there are molecules energies close to -2.0 eV, and for HFX=0.55, there is one molecule energy being relatively far from the diagonal line. 
-Those mentioned low molecules results in the large energy disorder $\sigma(E)$ as shown in table \ref{tab:para}. 
-and they are very different from other energies obtained by $ 0.05 \leq \text{HFX} \leq 0.27 $.
-
-Molecule energy are determined by the atomic charges and polarizability.
-Those physical properties as shown in Fig.\ref{fig:autogen} follow is linearly dependent on HFX.
-Since molecular energy for individual molecule are similar as shown by the scatter points cluster around the diagonal line, the deviated molecule energy for HFX=0.35,0.45,0.55 are non-physical.
-When those low energies molecules are filled by charge carriers, the ToF has a huge change and become close to the ToF obtained by $0.05 \leq \text{HFX} \leq 0.27$.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.95\textwidth]{figs/BCP_HFX/scatterEstat_qmmm.pdf}
-    \caption{Scatter plot of BCP electrostatic energy calculated from different HFX, compared to the electrostatic energy calculated from HFX=0.25 (The PBE0 functional).
-The brighter color near the diagonal lines indicates denser population of the molecules.
-The top and right histogram show the energy distributions.}
-    \label{fig:Estat_qmmm_BCP}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.95\textwidth]{figs/BCP_HFX/scatterEdip_qmmm.pdf}
-    \caption{Scatter plot of BCP polarization energy calculated from different HFX, compared to the polarization energy calculated from HFX=0.25 (The PBE0 functional).
-The brighter color near the diagonal lines indicates denser population of the molecules.
-The top and right histogram show the energy distributions.}
-    \label{fig:Edip_qmmm_BCP}
-\end{figure}
-
-The molecule energy has the contribution from the electrostatic effect and polarization effect due to the dipole moment of the molecules.
-To further understand how the HFX affect molecule energy, the comparison scatter plots of electrostatic energy and polarization energy are shown in Fig.\ref{fig:Estat_qmmm_BCP} and Fig.\ref{fig:Edip_qmmm_BCP}.
-
-Figure \ref{fig:Estat_qmmm_BCP} shows that for all HFX parameters, the electrostatic energy has a range of 0.2 to -1.3 eV.
-Different $0.05 \leq \text{HFX} \leq 0.55$ values produce relatively close electrostatic energy compared to that of HFX=0.25.
-The large HFX$>0.27$ does not cause deviated electrostatic energy.
-
-Figure \ref{fig:Edip_qmmm_BCP} shows that polarization energy has a range of -0.3 to -1.0 eV.
-When $0.05 \leq \text{HFX} \leq 0.27$, the polarization energies are very close and the scatter points are cluster along the diagonal line.
-In contrast to the electrostatic energy, Fig.\ref{fig:Edip_qmmm_BCP} shows that for HFX=0.35,0.45,0.55, there are molecules that have small polarization energy, contributing to the small site energies, and the extremely large ToF.
-
-Those small polarization energies and site energies are not physical, because 
-when HFX is varied, the change of the polarizability and reorganization energy are almost linear.
-In contrast, there is huge jumps in those site energies due to the huge jumps in the polarization energy.
-
-In conclustion, the HFX affects the molecular polarizability, which affects the polarization energies and eventually leads to non-physical molecule energy. 
-And large range of HFX leads to non-physical results. 
-In the next section, we will use the range with small HFX values for the investigation of a less disorder molecular system, MADN.
-
-\section{Results on MADN}
-MADN (2-Methyl-9,10-di(naphth-2-yl)anthracene) is another type of OSC. MADN has more efficient hole transport compared to BCP. 
-\begin{table}[H]
-    \centering
-    \begin{tabular}{c c c c c}
-    \hline
-        HFX & ToF [s] & $v_\text{ToF}$ [m/s] & ToF(no $E$) [s] & $v_\text{ToF}$ (no $E$) [m/s] \\
+        $\alpha$ & ToF [s] & $v_\text{ToF}$ [m/s] & ToF(no $E$) [s] & $v_\text{ToF}$ (no $E$) [m/s] \\
     \hline
@@
 \end{table}
-Table \ref{tab:ToF_MADN_HFX} shows the ToF and $v_\text{ToF}$ obtained with and without energy disorder. 
-Compared to the mobility of BCP, MADN has significantly larger $v_\text{ToF}$. When the molecule energy are not considered, $v_\text{ToF}$ of MADN is close to that of BCP. 
-So the better hole mobility, that is the larger $v_\text{ToF}$ in MADN compared to BCP is accredited to the energy disorder. 
-As HFX increase from 0 to 0.25, the ToF with and without energy disorder increase eventually by a factor of around 10.
 
-Figure \ref{fig:autogen_MADN} shows the dipole moment $\mu$, isotropic polarizability $P_\text{iso}$,  reorganization energies $\lambda$ and energy disorder $\sigma(E)$ as a function of the HFX parameters.
-%
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.80\textwidth]{figs/MADN_HFX/fig_autogen.pdf}
-    \caption{(a) The dipole moment of neutral state MAND molecule $\mu$, (b) isotropic polarizability $P_\text{iso}$, (c) reorganization energies $\lambda$ and (d) energy disorder $\sigma(E)$ as a function of the HFX parameters.}
-    \label{fig:autogen_MADN}
-\end{figure}
-%
+Table \ref{tab:ToF_MADN_HFX} shows that as HFX increases from 0 to 0.25, the ToF with energy disorder increases by a factor of approximately 15, while without energy disorder, the increase factor is about 4.
+This increase in ToF is attributed to the rise in $\lambda$, changes in molecular energies, and variations in coupling elements.
 
-Fig.\ref{fig:autogen_MADN}(a) shows that the dipole moment decreases as HFX increase.
-At HFX=0.25, there is a relatively sharp decrease.
-This HFX effect on dipole moment is opposite to that of the BCP molecule, which has the dipole moment increases as the HFX increases.
-
-Fig.\ref{fig:autogen_MADN}(b) shows that the isotropic polarizability for n and h state MADN molecule decrease linearly as HFX increase from 0 to 0.25. 
-So the molecules are getting more difficult to be polarized. 
-Accordingly, the reorganization energy also increases as HFX increases as shown by Fig.\ref{fig:autogen_MADN}(c).
-This increase is nonlinear compared to the linear increase of BCP reorganization energy in the range HFX=0.05 to 0.25.
-
-Fig.\ref{fig:autogen_MADN}(d) shows that the energy disorders for the used HFX are smaller compared with that of BCP. And they have a relatively similar range.
-
-Using the energy obtained from PBE0 functional with HFX=0.25 as a reference, the scatter plot in Fig.\ref{fig:E_qmmm_MADN} shows that all HFX values produce molecule energies in the range -0.5 to -1.1 eV.
-And different HFX has similar molecular energy, as all the points are group close to the diagonal line.
-
-The scatter plots of the electrostatic energy and polarization energy as shown in Fig.
-\ref{fig:Estat_qmmm_MADN} and \ref{fig:Edip_qmmm_MADN} also shows that those two energy terms are similar when HFX varies from 0 to 0.25.
-That is, there is no obvious small data points deviated from the diagonal line.
+Figure \ref{fig:E_qmmm_MADN} presents a scatter plot comparing the site energies of MADN molecules across different HFX values, using HFX = 0.25 (PBE0 functional) as a reference.
+The energies consistently fall within the range of -0.5 to -1.1 eV, with data points clustering near the diagonal line, indicating similar molecular energies regardless of HFX variation.
 
@@
 
-Furthermore, the plot comparing  electrostatic energy and polarization energy are shown in Fig.\ref{fig:Estat_qmmm_MADN} and Fig.\ref{fig:Edip_qmmm_MADN}.
-The electrostatic energy has a range of 0.1 to -0.6 eV. And there are no small data points deviated from the diagonal line. 
-The polarization energy has a range of -0.5 to -0.8 eV. And the data points are again clustered near the diagonal line.
+Figures \ref{fig:Estat_qmmm_MADN} and \ref{fig:Edip_qmmm_MADN} show that both electrostatic and polarization energies remain consistent across HFX values from 0 to 0.25, further clustering near the diagonal.
 
@@
 
+The electrostatic energy ranges from 0.1 to -0.6 eV, while polarization energy spans -0.5 to -0.8 eV.  Similar to the molecule energy, the data points are clustered near the diagonal line. 
+The standard deviations of the electrostatic energy are 0.099, 0.094, 0.099, 0.11, 0.10, \unit[0.10]{eV}, and the standard deviations of the polarization energies are 0.044, 0.043, 0.043, 0.047, 0.045, \unit[0.045]{eV}.
+So the disorder in electrostatic energies is consistently larger than than in molecule energies, and the palorization effect reduces the electrostatic energy disorder.
+Each individual molecule has similar polarization energies under different HFX calculation, in spite of $P_\text{iso}$ is linearly dependent on HFX.
+
+The coupling element obtained with different HFX for each molecular pair compared to that obtained with HFX=0.25 is shown in the scatter plot Fig. \ref{fig:J_MADN}.
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.95\textwidth]{figs/MADN_HFX/scatterJ_all.pdf}
+    \caption{Scatter plot of MADN coupling element $\log_{10} J^2$ calculated from different HFX, compared to the polarization energy calculated from HFX=0.25 (The PBE0 functional).
+The brighter color near the diagonal lines indicates denser population of the molecules.
+The top and right histogram show the energy distributions.}
+    \label{fig:J_MADN}
+\end{figure}
+
+The distribution of $\log_{10} J^2$ has a range of -14 to -2, and for all HFX values, the distribution has a peak at around -5. 
+For large values $\log_{10} J^2 < -5$ the coupling element remains consistent across HFX values from 0 to 0.25, while for large values $\log_{10} J^2 > -5$, the calculated coupling elements for a specific molecular pair can have large variation due to HFX values.
+
+In charge transport network, $J^2$ undirectional for a molecular pair, and decays exponentially as the mutual center-of-mass distance increases.
+The large $\log_{10} J^2$ are usually observed for molecular pairs with small center-of-mass distance.
+And the charge dynamics is more dominated by those large $\log_{10} J^2$ compared to the small $\log_{10} J^2$.
+
+To determine the range of $\log_{10} J^2$ that are significant for the charge dynamics, a percolation algorithm is performed with procedure as:
+\begin{enumerate}
+    \item A critical value $J_c$ is chosen,
+    \item In graph $\mathbf{G}$ remove all the edges with $J^2 < J_c^2$
+    \item Calculate the maximum size $\max({N_\text{sub}})$ of the connected subgraphs
+\end{enumerate}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.75\textwidth]{figs/MADN_HFX/fig_network_all.pdf}
+    \caption{The maximum size of the subgraphs obtained in the percolation algorithm as a function of critical value $J_c$.
+The molecular systems obtained by different HFX are colored according to the legend.}
+    \label{fig:J_percolate}
+\end{figure}
+Figure \ref{fig:J_percolate} shows the dependence of $\max({N_\text{sub}})$ on the critical value $J_c$.
+When $\log_{10} J_c^2 < -4.5$, $\max({N_\text{sub}})$ is 1000, meaning that removing all the edges with $J^2 < 3.1 \times 10^{-5}$ the 1000 vertexes still form a connected graph.
+But when removing the edges with $J^2 < 3.1 \times 10^{-4}$ ( corresponding to $J_c > -3.5$), the maximum size subgraph is 600, and it quickly decreases as $J_c$ increases, showing a phase transition.
+So the dominated coupling elements are those with $\log_{10} J_c^2 > -4.5$. 
+And the variation in small $J$ due to HFX has less impact on the charge dynamics.
+
+In this section we answer the question of how does HF level change the electronic structures and 
+how does HF level change the charge mobility. 
+In the next section, uncertainty quantification via Monte Carlo method and sensitivity analysis is perform to answer which electronic structure (among energy, coupling element and reorganization energy) uncertainty has the most impact on the charge mobility distribution.
+And further estimate the range of the quantity of interest, given a confidence level.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{ToF Distribution and Sensitivity Analysis}
+The previous section shows that different HFX affect the calculated ToF.
+In this section, we use the Monte Carlo method to estimate the range of the ToF given a confidence level, followed by a sensitivity analysis to determine which parameter contributes more to the variance of ToF.
+
+\subsection{ToF Distribution}
+The ToF is calculated from electronic structure ($E$, $\lambda$ and $\log_{10}(J^2)$) data, that is, ToF is a function with the input of all electronic structure parameters:
+\begin{equation}
+    \tau = g(x_1,x_2,\cdots, x_N) \; 
+\end{equation}
+where the parameters $(x_1,x_2,\cdots, x_N)$ represents $(E_i, J_{ij}, \lambda)$ for all $i,j=1,2,\cdots,N$ and $J_{ij}>0$.
+
+Since the exchange-correlation functional is not known and each molecule has a slightly different structure compared to the optimized structure, each parameter $(x_1,x_2,\cdots, x_N)$ has uncertain. 
+To estimate the uncertainty, we consider the maximum amount of uncertainties according to the obtained $(E_i, J_{ij}, \lambda)$ with the six different HFX.
+To achieve this, each parameter can be modeled as a normal distribution with the mean and standard deviation being the HFX sample mean and standard deviation, respectively.
+
+Then Monte Carlo scheme is used to estimate the distribution of the ToF. The Monte Carlo scheme has the procedure:
+\begin{enumerate}
+\item For all $i=1,2,\cdots, N$, sample a realization $(x_1,x_2,\cdots, x_N)$ where each parameter $x_i \in (x_1,x_2,\cdots, x_N)$ has the normal distribution $x_i \in \mathcal{N}(\bar{x}_i, \sigma_{x_i})$.
+\item Calculate ToF using the sampled data set $(x_1,x_2,\cdots, x_N)$. 
+\item Repeat step 1 and 2 for $N_\text{MC} = 50000$ times to obtain ToFs. Plot the distribution of the ToFs.
+\item Fit the distribution of $log_{10}(\text{ToF})$ to Gamma distribution.
+\end{enumerate}
+
+The distribution of ToF calculated as the CTMC where transition parameters are varied is unknown, so we attempt to fit the distribution of ToF to Gamma distribution. The reason is as followed.
+
+From equation \ref{eq:hitting_time}, the ToF can be considered as the some combination of occupation time in the molecules, which is $log_{10}(\omega_{i}^{-1})$. 
+When the parameters $E, J_{ij}, \lambda_{ij}$ are normally distributed random variables, the calculated ToF shows that variables $E,\lambda_{ij}$ has a larger influence than $J_{ij}$. 
+The Marcus rate uses $E,\lambda_{ij}$ in the exponential form. If $\Delta E$ is normally distributed, then $log_{10}(\omega_{i}^{-1})$ is Gamma distributed. 
+Since $E$ has greater influence to ToF than $\lambda_{ij}, J_{ij}$ and to be consistent, Gamma distribution is used to fit the Monte Carlo sampled ToF in all the investigated cases.
+
+To understand which uncertainty among $E, \lambda, J_{ij}$ has a greater impact on the ToF, we study the following distribution of ToF:
+\begin{enumerate}
+    \item Fixed the $\lambda$ to be the averaged $\bar{\lambda}$, and $J_{ij}$ to be the averaged $\bar{J}_{ij}$.
+Then each molecule energy $E_i$ is sampled from the normal distribution $\mathcal{N}(\bar{E}_i, \sigma^2_{E_i})$.
+Finally obtain and plot $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|E_i \text{ uncertain})$.
+    \item Fixed the $E_i$ to be the average $\bar{E}_i$ and and $J_{ij}$ to be the averaged $\bar{J}_{ij}$.
+Then $\lambda$ is sampled from the normal distribution $\mathcal{N}(\bar{\lambda}, \sigma^2_{\lambda})$.
+Finally obtain and plot $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|\lambda \text{ uncertain})$.
+    \item Fixed the $E_i$ to be the average $\bar{E}_i$ and $\lambda$ to be the averaged $\bar{\lambda}$.
+Then $J_{ij}$ is sampled from the normal distribution $\mathcal{N}(\bar{J}_{ij}, \sigma^2_{J_{ij}})$.
+Finally obtain and plot $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$.
+    \item Both $E_i$, $\lambda$ and $J_{ij}$ are sample from their normal distribution: $\mathcal{N}(\bar{E}_i, \sigma^2_{E_i})$, $\mathcal{N}(\bar{\lambda}, \sigma^2_{\lambda})$ and $\mathcal{N}(\bar{J}_{ij}, \sigma^2_{J_{ij}})$.
+Then obtain and plot $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$.
+\end{enumerate}
+
+The ToF distribution and Gamma fitted results for the MADN systems with energy disorder is shown in Fig.\ref{fig:mle_MADN_withE}.
+%
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.75\textwidth]{figs/MADN_HFX/fig_mle_MADN_withE.pdf}
+    \caption{Distribution of ToFs in the multiscale modeled MADN system using PBE0 functional and varying HFX. 
+    (a) $P(\log_{10}(\tau)|E_i \text{ uncertain})$, 
+    (b) $P(\log_{10}(\tau)|\lambda \text{ uncertain})$, 
+    (c) $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$, 
+    (d) $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$.
+The red star indicates the ToF calculated using the average $\bar{E_i}, \bar{J}_{ij}, \bar{\lambda}$, and the red circles indicate the ToF obtained using different HFX.}
+    \label{fig:mle_MADN_withE}
+\end{figure}
+%
+
+When the energy disorder in MADN system is not considered, that is, all the MADN molecule energy are set to be equal giving $\Delta E=0$, the distribution of ToF is shown in Fig.\ref{fig:mle_MADN_noE}
+%
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.99\textwidth]{figs/MADN_HFX/fig_mle_MADN_noE.pdf}
+    \caption{Distribution of ToFs in the multiscale modeled MADN system using PBE0 functional and varying HFX. Energy disorder is not consider. 
+    (a) $P(\log_{10}(\tau)|\lambda \text{ uncertain})$, 
+    (b) $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$, 
+    (c) $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$.
+The red star indicates the ToF calculated using the average $\bar{E_i}, \bar{J}_{ij}, \bar{\lambda}$, and the red circles indicate the ToF obtained using different HFX.}
+    \label{fig:mle_MADN_noE}
+\end{figure}
+%
+
+Measuring the sensitivity of each electronic parameter to ToF is to measure each electronic parameter's contribution to the variance of ToF. 
+That is, if ToF is most sensitive to one parameter, the variance in this particular parameter will contribute most to the ToF variance.
+
+One way of decomposing the variance of the model output into fractions attributed to input parameters is the variance-based sensitivity analysis.
+The local sensitive analysis is to use the partial derivative $\frac{\partial \tau}{\partial x_i}$.
+While the global sensitivity analysis can use Sobol's indices.
+Specifically, to measure the parameter $x_i$'s contribution to $\tau$, including all variance caused by its interaction with other parameters $\{x_k, k \neq i \}$, the total effect Sobol's index is calculated as
+\begin{equation}
+    S_{Ti} = \frac{ \mathbb{E}_{x_{\sim i}}[ \text{Var}_{x_i}(\tau|x_{\sim i}) ] }{ \text{Var}(\tau) }
+    \label{eq:STi}
+\end{equation}
+
+\section{Distribution of Steady State Velocity}
+The distribution of steady state velocity of MADN is shown as Fig.\ref{fig:mle_MADN_withE_SS} and \ref{fig:mle_MADN_noE_SS}. 
+Those distribution shows that the variation in $v_\text{SS}$ distribution is greater than ToF distribution.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{figs/MADN_HFX/fig_mle_MADN_withE_SS.pdf}
+    \caption{Distribution of steady state velocity $v_\text{SS}$ in the multiscale modeled MADN system using PBE0 functional when (a) the molecule site energy $E$ are sampled from a normal distribution $E \sim N(E_\text{ave},E^2_\text{std})$, (b) the reorganization energy $\lambda$ are sampled from a normal distribution $\lambda \sim N(\lambda_\text{ave},\lambda^2_\text{std})$, (c) the quantity $\log_{10}(J^2)$ are sampled from a normal distribution $\log_{10}(J^2) \sim N(\mathbb{E}[\log_{10}(J^2)], \textbf{Var}[\log_{10}(J^2)] )$.
+(d) Both $E$, $\lambda$ and $\log_{10}(J^2)$ are sampled from the normal distribution.
+}
+    \label{fig:mle_MADN_withE_SS}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.99\textwidth]{figs/MADN_HFX/fig_mle_MADN_noE_SS.pdf}
+    \caption{Distribution of steady state velocity $v_\text{SS}$ in the multiscale modeled MADN system using PBE0 functional. All molecule energies are set to be zero.  
+    The plots are for the situation: (a) The reorganization energy $\lambda$ are sampled from a normal distribution $\lambda \sim N(\lambda_\text{ave},\lambda^2_\text{std})$.
+(b) the quantity $\log_{10}(J^2)$ are sampled from a normal distribution $\log_{10}(J^2) \sim N(\mathbb{E}[\log_{10}(J^2)], \textbf{Var}[\log_{10}(J^2)] )$.
+(c) Both $\lambda$ and $\log_{10}(J^2)$ are sampled from the normal distribution.
+}
+    \label{fig:mle_MADN_noE_SS}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Comparison of Diffusive Charge Velocity Between BCP and MADN}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{ToF distribution of BCP and MAND}
-Different HFX affect the calculated ToF. 
-The ToF is calculated from electronic structure ($E$, $\lambda$ and $\log_{10}(J^2)$) data, that is, ToF is a function with the input of all electronic structure parameters:
-\begin{equation}
-    \tau = g(x_1, x_2, \cdots, x_N)
-\end{equation}
-where each electronic structure parameter $x_i$ for $i=1,2,\cdots,N$ contains uncertainties. 
-Each of those parameters are obtained using different HFX.
-
-So the multiscale model use different HFX values to general samples of the paramters $(x_1, x_2, \cdots, x_N)$ and eventually different ToF.
-
-Since the exchange-correlation functional is not known, each parameter $x_i$ has uncertain. 
-To consider the maximum amount of uncertainties according to the obtained $x_i$ with different HFX, $x_i$ can be modeled as a normal distribution with the mean $\bar{x}_i$ and standard deviation $\sigma_{x_i}$ being the HFX sample mean and standard deviation, respectively.
-
-Then we use Monte Carlo scheme to estimate the distribution of the ToF:
-\begin{enumerate}
-\item For all $i=1,2,\cdots, N$, sample a realization $(x_1, x_2,\cdots, x_N)$ where $x_i \in \mathcal{N}(\bar{x}_i, \sigma_{x_i})$. 
-\item Calculate ToF using the sampled data set $(x_1, x_2,\cdots, x_N)$. 
-\item Repeat step 1 and 2 for $N_\text{MC} = 50000$ times to obtain $N_\text{MC}$ ToF. Plot the distribution of the ToF.
-\item Fit the distribution of $log_{10}(\text{ToF})$ to Gamma distribution.
-\end{enumerate}
-
-The distribution of ToF calculated as the CTMC where transition parameters are varied is unknown, so we attempt to fit the distribution of ToF to Gamma distribution. The reason is as followed.
-
-From equation \ref{eq:hitting_time}, the ToF can be considered as the some combination of occupation time in the molecules, which is $log_{10}(\omega_{i}^{-1})$. 
-When the parameters $E, J_{ij}, \lambda_{ij}$ are normally distributed random variables, the calculated ToF shows that variables $E,\lambda_{ij}$ has a larger influence than $J_{ij}$. 
-The Marcus rate uses $E,\lambda_{ij}$ in the exponential form. If $\Delta E$ is normally distributed, then $log_{10}(\omega_{i}^{-1})$ is Gamma distributed. 
-Since $E$ has greater influence to ToF than $\lambda_{ij}, J_{ij}$ and to be consistent, Gamma distribution is used to fit the Monte Carlo sampled ToF in all the investigated cases.
-
-To understand which uncertainty among $E, \lambda, J_{ij}$ has a greater impact on the ToF, we study the following distribution of ToF:
-\begin{enumerate}
-    \item Fixed the $\lambda$ to be the averaged $\bar{\lambda}$, and $J_{ij}$ to be the averaged $\bar{J}_{ij}$.
-Then each molecule energy $E_i$ is sampled from the normal distribution $\mathcal{N}(\bar{E}_i, \sigma^2_{E_i})$.
-Finally obtain and plot $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|E_i \text{ uncertain})$.
-    \item Fixed the $E_i$ to be the average $\bar{E}_i$ and and $J_{ij}$ to be the averaged $\bar{J}_{ij}$.
-Then $\lambda$ is sampled from the normal distribution $\mathcal{N}(\bar{\lambda}, \sigma^2_{\lambda})$.
-Finally obtain and plot $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|\lambda \text{ uncertain})$.
-    \item Fixed the $E_i$ to be the average $\bar{E}_i$ and $\lambda$ to be the averaged $\bar{\lambda}$.
-Then $J_{ij}$ is sampled from the normal distribution $\mathcal{N}(\bar{J}_{ij}, \sigma^2_{J_{ij}})$.
-Finally obtain and plot $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$.
-    \item Both $E_i$, $\lambda$ and $J_{ij}$ are sample from their normal distribution: $\mathcal{N}(\bar{E}_i, \sigma^2_{E_i})$, $\mathcal{N}(\bar{\lambda}, \sigma^2_{\lambda})$ and $\mathcal{N}(\bar{J}_{ij}, \sigma^2_{J_{ij}})$.
-Then obtain and plot $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$.
-\end{enumerate}
-
-Then we compute the Wasserstein distance $D(\cdot, \cdot)$ for the following pair of distribution: 
-\begin{itemize}
-    \item $(P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain}),P(\log_{10}(\tau)|E_i \text{ uncertain}))$
-    \item $(P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain}),P(\log_{10}(\tau)|\lambda \text{ uncertain}))$
-    \item $(P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain}),P(\log_{10}(\tau)|J_{ij} \text{ uncertain}))$
-\end{itemize}
-The Wasserstein distance quantifies similarity between two distribution and thus can be used to find which parameter variation has a greater contribution to the total distribution $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$.
-
-The ToF distribution and Gamma fitted results for the BCP systems with energy disorder is shown in Fig.\ref{fig:mle_BCP_withE}.
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.85\textwidth]{figs/BCP_HFX/fig_mle_BCP_withE.pdf}
-    \caption{Distribution of ToFs in the multiscale modeled BCP system using PBE0 functional and varying HFX,  when 
-    (a) $P(\log_{10}(\tau)|E_i \text{ uncertain})$, 
-    (b) $P(\log_{10}(\tau)|\lambda \text{ uncertain})$, 
-    (c) $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$, 
-    (d) $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$.
-The red star indicates the ToF calculated using the average $\bar{E_i}, \bar{J}_{ij}, \bar{\lambda}$, and the red circles indicate the ToF obtained using different HFX.}
-    \label{fig:mle_BCP_withE}
-\end{figure}
-
-When the energy disorder in BCP system is not considered, that is, all the molecule energy are zero, the distribution of ToF is shown in Fig.\ref{fig:mle_BCP_noE}
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.99\textwidth]{figs/BCP_HFX/fig_mle_BCP_noE.pdf}
-    \caption{Distribution of ToFs in the multiscale modeled BCP system using PBE0 functional and varying HFX. Energy disorder is not consider. 
-    (a) $P(\log_{10}(\tau)|\lambda \text{ uncertain})$, 
-    (b) $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$, 
-    (c) $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$.
-The red star indicates the ToF calculated using the average $\bar{E_i}, \bar{J}_{ij}, \bar{\lambda}$, and the red circles indicate the ToF obtained using different HFX.}
-    \label{fig:mle_BCP_noE}
-\end{figure}
-
-The ToF distribution and Gamma fitted results for the MADN systems are as followed:
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.85\textwidth]{figs/MADN_HFX/fig_mle_MADN_withE.pdf}
-    \caption{Distribution of ToFs in the multiscale modeled MADN system using PBE0 functional and varying HFX. 
-    (a) $P(\log_{10}(\tau)|E_i \text{ uncertain})$, 
-    (b) $P(\log_{10}(\tau)|\lambda \text{ uncertain})$, 
-    (c) $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$, 
-    (d) $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$.
-The red star indicates the ToF calculated using the average $\bar{E_i}, \bar{J}_{ij}, \bar{\lambda}$, and the red circles indicate the ToF obtained using different HFX.}
-    \label{fig:mle_MADN_withE}
-\end{figure}
-
-When the energy disorder in MADN system is not considered, that is, all the MADN molecule energy are zero, the distribution of ToF is shown in Fig.\ref{fig:mle_MADN_noE}
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.99\textwidth]{figs/MADN_HFX/fig_mle_MADN_noE.pdf}
-    \caption{Distribution of ToFs in the multiscale modeled MADN system using PBE0 functional and varying HFX. Energy disorder is not consider. 
-    (a) $P(\log_{10}(\tau)|\lambda \text{ uncertain})$, 
-    (b) $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$, 
-    (c) $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$.
-The red star indicates the ToF calculated using the average $\bar{E_i}, \bar{J}_{ij}, \bar{\lambda}$, and the red circles indicate the ToF obtained using different HFX.}
-    \label{fig:mle_MADN_noE}
-\end{figure}
-
-\section{Distribution of Steady State Velocity}
-The distribution of steady state velocity of MADN is shown as Fig.\ref{fig:mle_MADN_withE_SS} and \ref{fig:mle_MADN_noE_SS}. 
-Those distribution shows that the variation in $v_\text{SS}$ distribution is greater than ToF distribution.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.85\textwidth]{figs/MADN_HFX/fig_mle_MADN_withE_SS.pdf}
-    \caption{Distribution of steady state velocity $v_\text{SS}$ in the multiscale modeled MADN system using PBE0 functional when (a) the molecule site energy $E$ are sampled from a normal distribution $E \sim N(E_\text{ave},E^2_\text{std})$, (b) the reorganization energy $\lambda$ are sampled from a normal distribution $\lambda \sim N(\lambda_\text{ave},\lambda^2_\text{std})$, (c) the quantity $\log_{10}(J^2)$ are sampled from a normal distribution $\log_{10}(J^2) \sim N(\mathbb{E}[\log_{10}(J^2)], \textbf{Var}[\log_{10}(J^2)] )$.
-(d) Both $E$, $\lambda$ and $\log_{10}(J^2)$ are sampled from the normal distribution.
-}
-    \label{fig:mle_MADN_withE_SS}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.99\textwidth]{figs/MADN_HFX/fig_mle_MADN_noE_SS.pdf}
-    \caption{Distribution of steady state velocity $v_\text{SS}$ in the multiscale modeled MADN system using PBE0 functional. All molecule energies are set to be zero.  
-    The plots are for the situation: (a) The reorganization energy $\lambda$ are sampled from a normal distribution $\lambda \sim N(\lambda_\text{ave},\lambda^2_\text{std})$.
-(b) the quantity $\log_{10}(J^2)$ are sampled from a normal distribution $\log_{10}(J^2) \sim N(\mathbb{E}[\log_{10}(J^2)], \textbf{Var}[\log_{10}(J^2)] )$.
-(c) Both $\lambda$ and $\log_{10}(J^2)$ are sampled from the normal distribution.
-}
-    \label{fig:mle_MADN_noE_SS}
-\end{figure}
 

### 2024-10-20 paper.tex
update

@@
 \section{Multiscale Model}
-The multiscale model results in the charge dynamics becoming CTRW.
-When there in one charge carrier, each state in CTRW corresponds to the charge occupation in each molecule.
+The multiscale model results in the charge dynamics being modeled by CTRW.
+When there is one charge carrier, each state in CTRW corresponds to the charge occupation in each molecule.
 The transition rates between the state, that is the rate for charge transfer rates between two molecules $i$ and $j$ is calculated as the Marcus rate:
@@
 
-In charge transport network, $J^2$ undirectional for a molecular pair, and decays exponentially as the mutual center-of-mass distance increases.
+In charge transport network, $J^2$ is undirectional for a molecular pair, and decays exponentially as the mutual center-of-mass distance increases.
 The large $\log_{10} J^2$ are usually observed for molecular pairs with small center-of-mass distance.
-And the charge dynamics is more dominated by those large $\log_{10} J^2$ compared to the small $\log_{10} J^2$.
+When the center-of-mass distance is very large, the $\log_{10} J^2$ is small and some of those small $\log_{10} J^2$ are sensitive to $\alpha$.
 
-To determine the range of $\log_{10} J^2$ that are significant for the charge dynamics, a percolation algorithm is performed with procedure as:
+However, the charge dynamics is dominated by large $\log_{10} J^2$ which are found between molecule pair having large center-of-mass.
+As the center-of-mass distance increases, $\log_{10} J^2$ becomes small and negligible for the charge dynamics.
+
+To determine the range of $\log_{10} J^2$ that are significant for the charge dynamics, a percolation algorithm is performed.
+This algorithm aims to find the largest size of subgraphs after removing the edges whose coupling elements are below a critical value.
+The procedure is as follows:
 \begin{enumerate}
@@
 \end{figure}
-Figure \ref{fig:J_percolate} shows the dependence of $\max({N_\text{sub}})$ on the critical value $J_c$.
+After performing percolation algorithm, Figure \ref{fig:J_percolate} shows the dependence of $\max({N_\text{sub}})$ on the critical value $J_c$.
 When $\log_{10} J_c^2 < -4.5$, $\max({N_\text{sub}})$ is 1000, meaning that removing all the edges with $J^2 < 3.1 \times 10^{-5}$ the 1000 vertexes still form a connected graph.
@@
 In the next section, uncertainty quantification via Monte Carlo method and sensitivity analysis is perform to answer which electronic structure (among energy, coupling element and reorganization energy) uncertainty has the most impact on the charge mobility distribution.
-And further estimate the range of the quantity of interest, given a confidence level.
+And further we estimate the range of the quantity of interest, given a confidence level.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{equation}
-    \tau = g(x_1,x_2,\cdots, x_N) \; 
+    \tau = g(\lambda, \{E_i|i=1,2,\cdots,N \}, \{J_{ij}|i,j=1,2,\cdots,N \}) \;
 \end{equation}
-where the parameters $(x_1,x_2,\cdots, x_N)$ represents $(E_i, J_{ij}, \lambda)$ for all $i,j=1,2,\cdots,N$ and $J_{ij}>0$.
+where $\{E_i|i=1,2,\cdots,N \}$ is the ordered set whose elements are the molecule energy,
+$\{J_{ij}|i,j=1,2,\cdots,N \}$ is the ordered set whose elements are the coupling elements.
 
-Since the exchange-correlation functional is not known and each molecule has a slightly different structure compared to the optimized structure, each parameter $(x_1,x_2,\cdots, x_N)$ has uncertain. 
-To estimate the uncertainty, we consider the maximum amount of uncertainties according to the obtained $(E_i, J_{ij}, \lambda)$ with the six different HFX.
-To achieve this, each parameter can be modeled as a normal distribution with the mean and standard deviation being the HFX sample mean and standard deviation, respectively.
+Since the exchange-correlation functional is not known and each molecule has a slightly different structure compared to the optimized structure, each parameter has uncertain. 
+To estimate the uncertainty, we consider the maximum amount of uncertainties according to the obtained $(\lambda, \{E_i|i=1,2,\cdots,N \}, \{J_{ij}|i,j=1,2,\cdots,N \})$ with the six different HFX.
+To achieve this, each parameter can be modeled as a normal distribution with the mean and standard deviation obtained by the maximum likelihood estimation.
+For a normal distribution, they are the HFX sample mean and standard deviation, respectively.
 
@@
 \begin{enumerate}
-\item For all $i=1,2,\cdots, N$, sample a realization $(x_1,x_2,\cdots, x_N)$ where each parameter $x_i \in (x_1,x_2,\cdots, x_N)$ has the normal distribution $x_i \in \mathcal{N}(\bar{x}_i, \sigma_{x_i})$.
-\item Calculate ToF using the sampled data set $(x_1,x_2,\cdots, x_N)$. 
+\item For all $i,j=1,2,\cdots, N$, sample a realization $(\lambda, \{E_i \}, \{J_{ij} \})$ where each parameter has the normal distribution: $\lambda_i \in \mathcal{N}(\bar{\lambda}_i, \sigma_{\lambda_i})$, $E_i \in \mathcal{N}(\bar{E}_i, \sigma_{E_i})$, $J_{ij} \in \mathcal{N}(\bar{J}_{ij}, \sigma_{J_{ij}})$.
+\item Calculate ToF using the sampled data set $(\lambda, \{E_i \}, \{J_{ij} \})$. 
 \item Repeat step 1 and 2 for $N_\text{MC} = 50000$ times to obtain ToFs. Plot the distribution of the ToFs.
@@
 Since $E$ has greater influence to ToF than $\lambda_{ij}, J_{ij}$ and to be consistent, Gamma distribution is used to fit the Monte Carlo sampled ToF in all the investigated cases.
+
+Sampling the molecule energy as a normal distribution $E_i \sim \mathcal{N}(\bar{E}_i, \sigma_{E_i})$ will potentially destroy the energy correlation, especially for correlated systems, resulting a shift in the ToF calculation.
+But we will show that making the molecule energy uncorrelated in the MADN system will not cause such a shift in ToF. 
+To do so, let $\{E_1, E_2, \cdots, E_N\}^{\alpha}$ be an ordered set with elements being the energy calculated using a specific $\alpha$ value. 
+Then the order of the energies are randomly shuffled so that they are no longer correlated, and denote it as $\{E_1, E_2, \cdots, E_N\}^{\alpha}_{\text{shuffle}}$.
+The ToF calculated using the shuffled energy is $ \tau_{\text{sh}} = \tau(\{E_1, E_2, \cdots, E_N\}^{\alpha}_{\text{shuffle}}) $.
+%
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\textwidth]{figs/MADN_HFX/ToFx_shuffle.pdf}
+    \caption{Distribution of $\tau_{\text{sh}}$ calculated using shuffle energies.
+Each distribution are a sample of 10000 $\tau_{\text{shuffle}}$.
+The position of the solid circle indicates the ToF calculated from the specific $\alpha$ value, and the position of the solid square indicates the average $\tau_{\text{shuffle}}$ over the 10000 samples.}
+    \label{fig:ToF_shuffle_MADN}
+\end{figure}
+%
+After such shuffling energy and ToF calculation for 10000 times, the distribution of $\tau_{\text{sh}}$ are shown in Fig.\ref{fig:ToF_shuffle_MADN}. 
+For the chosen $\alpha=0.05, 0.15, 0.25$, the $\tau_{\text{sh}}$ does not overall shift to smaller or large values, and the averaged $\tau_{\text{sh}}$ is close to the ToF obtained without energy shuffle.
+So making the energy uncorrelated will not shift the ToF to smaller or larger values.
+This enables represent the parameter uncertainties in $\lambda, \{E_i\}, \{ J_{ij}\}$ using the normal distribution without shift the ToF.
 
@@
 %
+
+The 90\% confidence interval of each distribution and the fitted Gamma distribution is summarized in table
 

### 2024-10-27 paper.tex
update

@@
 \linenumbers
-\title{Uncertain Effects of DFT Functionals on Charge Dynamic of Organic Semiconductor }
+\title{Uncertainty Quantification in Multiscale Model }
 \author{authors}
@@
 \begin{abstract}
+    This work quantifies uncertainties in a multiscale model for charge dynamics in organic semiconductors (OSCs).
+A first-principle multiscale model integrates classical molecular dynamics (MD), density functional theory (DFT), and continuous-time random walk (CTRW) processes to allow the simulation of charge transport in OSCs.
+The model brings inherent uncertainties arising from the empirical approximations and numerical simulations.
+Our work particularly focusing on quantifying the uncertainty in DFT exchange-correlation functional.
 
+    By investigating the effects of varying Hartree-Fock (HF) levels within DFT functionals, we analyze the impact on electronic structures such as reorganization energy, molecule energy distribution, and coupling elements.
+The primary goal is to assess the robustness of predicting the quantity of interest (QoI), that is time-of-flight and charge mobility, under these uncertainties.
+
+    Monte Carlo simulations and sensitivity analysis are employed to estimate the range and confidence levels of the predicted charge mobility.
+As shown by Sobol indices, the QoI is most sensitive to molecule energy, then reorganization energy and least sensitive to coupling elements.
 \end{abstract}
@@
 
-In brief summary, the multiscale model can be summarized in Fig. \ref{fig:MSM}.
-The process includes: Firstly, classical Molecular Dynamics is used to generate the atomistic coordinates.
+In brief summary, the multiscale model can be summarized in Fig. \ref{fig:MSM} using MADN, a type of OSC as an example.
+The process includes: Firstly, classical Molecular Dynamics is used to generate the atomistic coordinates of all molecules.
 Then DFT is used to attain electronic structures.
@@
     \centering
-    \includegraphics[width=0.95\textwidth]{figs/MSM.png}
+    \includegraphics[width=0.99\textwidth]{figs/MSM.pdf}
     \caption{The multiscale model workflow for OSC.
@@
 But for amorphous OSCs used in this work, model noise from state localization is negligible and we do not consider the uncertainty brought by state localization.
-Lastly, the exchange-correlation potential in DFT do not have explicit formula and common practice is to use empirical functional, whose suitability is usually unknown for most molecules.
+Lastly, the exact functional for the exchange-correlation energy is unknown so approximations like the Local Density Approximation (LDA) or the Generalized Gradient Approximation (GGA) are used, resulting in exchange-correlation functional in practice.
+The accuracy of DFT depends heavily on the choice of the exchange-correlation functional whose accuracy is usually unknown for new synthesized molecules. 
+As an advancement to improve accuracy, Hybrid-DFT incorporates a portion of exact HF exchange functional (HFX) from Hartree-Fock (HF) theory into the exchange-correlation functional, particularly for systems where DFT falls short.
+For example, the PBE0 functional has a portion of 0.25 HF exchange functional.
 
 The charge dynamics is determined by CTRW transition rates, which depend on the electronic structures.
-Since DFT is used to calculate the molecular electronic structures, the unknown exchange-correlation functional in DFT will bring uncertainties to the multiscale model. 
-In particular, different DFT functionals contain varying levels of Hartree Fock (HF) to represent the exchange-correlation potential. 
-The effect of the uncertainty from the DFT exchange-correlation functional on the multiscale model is not yet explored in literatures. 
-The goal of this work is to quantify the uncertainty effect of the DFT exchange-correlation functional on the charge dynamics in OSCs and to study the robustness of the multiscale model, with a particular focus on the uncertainty represented by the HF level.
+Since DFT is used to calculate the molecular electronic structures, the unknown exchange-correlation functional will bring uncertainties to the multiscale model. 
+In particular, different hybrid-DFT functionals contain varying levels of Hartree Fock (HF) to represent the exchange-correlation potential. 
+The effect of the uncertainty from the electronic structure level on the multiscale model is not yet explored in literatures. 
+The goal of this work is to quantify the uncertainty effect of the exchange-correlation functional on the charge dynamics in OSCs and to study the robustness of the multiscale model, with a particular focus on the uncertainty represented by different portional of HF exchange functional.
 
@@
 Knowing the length of the sample $L$ and the time-of-flight $\tau$, the diffusive velocity is calculated as $v_\text{ToF}=\frac{L}{\tau}$.
+When electric field $\vec{F}$ is used to drift the charge transport, the charge mobility is calculated as $\mu_\text{ToF}=\frac{\vec{v}_\text{ToF} \vec{F}}{|\vec{F}|^2}$.
 
-Most literature report the charge mobility in a steady state setting, where no electrodes are used and the molecular system is infinitely repeated in all three dimensions by periodic boundary conditions.
-Over a long time period, the charge occupation on each molecule $\pi_i$ reach equilibrium, and the steady state diffusive velocity is calculated via:
-\begin{equation}
-    v_\text{SS} = \sum_i \pi_i \sum_j \omega_{ij} \vec{r}_{ij} = \mathbb{E}f(M_{\infty})
-\end{equation}
+Some literatures also report the charge mobility in a steady state setting, where no electrodes are used and the molecular system is infinitely repeated in all three dimensions by periodic boundary conditions.
+Over a long time period, the charge occupation on each molecule $\pi_i$ reach equilibrium.
+The steady state charge mobility $\mu_\text{SS}$ is calculated as the charge velocity along the direction of the electric field normalized by the steady state charge occupation $\vec{\pi}:\pi_i$. 
+The calculation for $v_\text{ToF}$ and $\mu_\text{SS}$ will be detailed in the method section.
 
-Specifically, the focus will be placed on following questions: 
+To quantify the uncertainty for QoI, the focus of our work will be placed on the following questions: 
 \begin{enumerate}
-    \item How does HF level change the electronic structures: reorganization energy, distribution of molecule energies and coupling elements? 
-    \item How does HF level change the charge mobility?
-    \item Which electronic structure (among energy, coupling element and reorganization energy) uncertainty has the most impact on the charge mobility distribution?
-    \item Can we estimate the range of the quantity of interest, given a confidence level?
+    \item How does HFX level change the electronic structures: reorganization energy, distribution of molecule energies and coupling elements? 
+    \item How does HFX level change the charge mobility?
+    \item Which electronic structure (among energy, coupling element and reorganization energy) uncertainty has the most impact on the QoI distribution?
+    \item Can we estimate the range of the QoI, given a confidence level?
 \end{enumerate}
-
-Calculation of $v_\text{ToF}$ or $v_\text{SS}$ commonly use kinetic Monte Carlo (KMC) to obtain multiple realizations of full charge dynamic trajectories 
-or numerically solving the master equation. 
-However, those two commonly used methods are not suitable for quantifying the uncertainty effect of multiscale model charge dynamics for the following reasons. 
-Firstly, KMC produces random variables whose expectation is the charge mobility.
-The prior knowledge of the random variable distribution as well as the required KMC samples to achieve converged expectation is unknown.
-So this method itself pose further challenge for our uncertainty quantification.
-Secondly, the numerical solution of the master equation has stability and convergence issue, that is, a small integration time step is required to achieve stability and a long computational time to achieve convergence result.
-These aspects add additional difficulty for uncertainty quantification.
-Considering those aspects, the ToF $\tau$ and $v_\text{ToF}$ are obtained via a graph random walk method
-\cite{chen_graph_2024}. Once the $v_\text{ToF}$ is calculated using this method, it is considered to be converged. 
-Similarly, the steady state occupation $\pi_i$ will be calculated as the null-space of the transition matrix.
 
@@
 \begin{equation}
-    \omega_{ij} = \frac{2\pi}{\hbar} \frac{|J_{ij}|^2}{\sqrt{4\pi R_{ij} k_\text{B}T}} \exp\left(-\frac{(E_{ij} + q \vec{F} \cdot \vec{r}_{ij} - R_{ij})^2}{4R_{ij} k_\text{B}T}\right) ,
+    \omega_{ij} = \frac{2\pi}{\hbar} \frac{|J_{ij}|^2}{\sqrt{4\pi \lambda_{ij} k_\text{B}T}} \exp\left(-\frac{(E_{ij} + q \vec{F} \cdot \vec{r}_{ij} - \lambda_{ij})^2}{4\lambda_{ij} k_\text{B}T}\right) ,
     \label{equ:Marcus}
@@
 The vector $\vec{r}_{ij} = (r^x_{ij},r^y_{ij},r^z_{ij})^\text{T}$ connects the center-of-masses (COMs) of molecules $i$ and $j$, which is calculated cyclic boundary conditions depending on the boundary condition.
-The remaining physical, material-specific (or rather transfer-pair-specific) quantities are the reorganization energy $R_{ij}$, the electronic coupling $J_{ij}$, and the energy difference $E_{ij} = E_i - E_j$ (all in \unit[]{eV}).
+The remaining physical, material-specific (or rather transfer-pair-specific) quantities are the reorganization energy $\lambda_{ij}$, the electronic coupling $J_{ij}$, and the energy difference $E_{ij} = E_i - E_j$ (all in \unit[]{eV}).
 With the information about the molecular COMs and the rates, one can construct the graph $\mathbf{G}=(\mathbf{V}, \mathbf{W})$ on which the CTRW takes place.
@@
 \subsection{Molecule Dynamics Simulation}
-In a material system of $N_a$ atoms with mass and position denoted by $m_i$ and $\vec{r}_i$ respectively, molecular dynamics (MD) models the evolution of the atomic coordinate using Newton's second law, which is written in Hamilton equation:
+The MD in the multiscale model is to use Newton's second law to update the atomic coordinate. Written in Hamilton equation, the equation of motion reads:
 \begin{equation}
     \begin{cases}
-        \frac{d \vec{r}_i}{dt} = \frac{\partial H }{\partial \vec{p}_i} \\
-        \frac{d \vec{p}_i}{dt} = -\frac{\partial H }{\partial \vec{r}_i}
+        \frac{d \vec{r}_i}{dt} = \frac{\partial H^\text{MD} }{\partial \vec{p}_i} \\
+        \frac{d \vec{p}_i}{dt} = -\frac{\partial H^\text{MD} }{\partial \vec{r}_i}
     \end{cases}
@@
 \end{equation}
-for $i=1,\cdots,N_a$, where the Hamiltonian $H$ reads:
-\begin{equation}
-    H=\sum\limits_{i} \frac{|\vec{p}_i|^2}{2 m_i} + U(\vec{r}_1,\cdots,\vec{r}_{N_a})
-    \label{eq:Hamilton2}
-\end{equation}
+for $i=1,\cdots,N_a$. Where $N_a$, $m_i$, $\vec{r}_i$, $\vec{p}_i$ are the atom number, atomic mass,  position vector and momentum, respectively. 
+And the Hamiltonian $H$ reads:
+$H^\text{MD}=\sum\limits_{i} \frac{|\vec{p}_i|^2}{2 m_i} + U(\vec{r}_1,\cdots,\vec{r}_{N_a})$.
 
 In principle the potential energy function $U(\vec{r}_1,\cdots,\vec{r}_{N_a})$ of the system can be obtained from electronic structure models.
-In practice, it is a very computationally expensive procedure, and without too much loss in precision, MD use empirical potentials that are designed for specific purposes.
-In our work, constant the molecule number $N=1000$, a temperature $T=300$ K and a pressure at 1 atm is used to achieve an NPT ensemble. 
-One of the final BCP morphology is chosen as OSC for charge transport study.
+As mentioned in the introduction, it is a very computationally expensive procedure, and without too much loss in precision, MD use empirical potentials that are designed for specific purposes.
+The MD simulation performed using the GROMACS software package~\cite{berendsen_gromacs_1995}, employing a gromos54a7 type force field obtained via the tool Automated Topology Builder~\cite{stroet_automated_2018}.
+The procedure of the MD simulation in this work is as followed:...
 
@@
 \subsection{Electronic Structure Calculations} 
-%Each molecule is an $N_\text{el}$-electron system, and in quantum mechanics, the probability of finding electrons in space is described by the electron wavefunction $\phi(\vec{r})$.
-Effective single-electronic wave functions $\phi_l (\vec{r})$ and associated energies $\epsilon_l$ for a system with $N_\text{el}$ electrons are determined as solutions to the Kohn--Sham equations~\cite{kohn_self_1965}
+A first essential step in first-principle multiscale model is to determine the single-electronic wave function and the associated energy $\epsilon_l$, which are used to obtain atomic charges, reorganization energy, molecule energy, and coupling elements.
+
+Each electron $l$ in a system with $N_\text{el}$ electrons has a single-electronic wave function $\phi_l (\vec{r})$ and associated energies $\epsilon_l$ determined as solutions to the Kohn--Sham equations~\cite{kohn_self_1965}
 %
 \begin{equation}
-    \left(-\frac{1}{2}\nabla^2_{\vec{r}} + v_\text{ext}(\vec{r}) + v_\text{H}[\rho](\vec{r}) + v_\text{XC}[\rho](\vec{r})\right) \phi_l(\vec{r}) =  \epsilon_l \phi_l (\vec{r}) ,
+    \left(-\frac{1}{2}\nabla^2_{\vec{r}} + v_\text{ext}(\vec{r}) + v_\text{H}[\rho](\vec{r}) + v_\text{XC}[\rho](\vec{r})\right) \phi_l(\vec{r}) = H^\text{KS} \phi_l(\vec{r}) = \epsilon_l \phi_l (\vec{r}) ,
     \label{eq:KS2}
@@
 %
-where $v_\text{ext}$ in an external potential (typically from the nuclei), $v_\text{H}[\rho]$ the electrostatic Hartree potential of a classical charge density $\rho(\vec{r})$, and $v_{XC}[\rho]$ the exchange-correlation functional containing explicit quantum-mechanical electron-electron interactions.
+where $v_\text{ext}$ in an external potential (typically from the nuclei), $v_\text{H}[\rho]$ the electrostatic Hartree potential of a classical charge density $\rho(\vec{r})$, and $v_\text{XC}[\rho]$ the exchange-correlation functional containing explicit quantum-mechanical electron-electron interactions.
 The charge density is determined from the single-particle wave functions as $\rho(\vec{r})=\sum\limits_{l=1}^{N_\text{el}} \left\vert\phi_l(\vec{r})\right\vert^2$.
-
+As the Hartree and exchange-correlation potential depend on the thus defined density, solutions to Eq.~\ref{eq:KS2} have to be found self-consistently.
+This corresponds to finding the ground-state density $\rho_0$ that minimized the total energy of the system
 %
 \begin{equation}
-    U[\rho] = T_s[\rho] + \int \hat{V}_\text{ext}(\vec{r}) \rho(\vec{r}) d \vec{r} + \hat{V}_\text{H}[\rho] + \hat{V}_\text{XC}[\rho]
+    U[\rho] = T_s[\rho] + \int v_\text{ext}(\vec{r}) \rho(\vec{r}) d \vec{r} + E_\text{H}[\rho] + E_\text{XC}[\rho]
     \label{eq:KS_model}
@@
 %
-where the electron density is , $T_s[\rho]$ is the kinetic energy depending on $\rho$,  $\hat{V}_\text{ext}$ is the external potential energy,  $\hat{V}_\text{H}[\rho]$ is the Hartree energy accounting for the Coulomb interaction, $\hat{V}_\text{XC}[\rho]$ is the exchange-correlation energy accounting for the difference between classical and quantum effect.
-The exact form of $\hat{V}_\text{XC}[\rho]$ is not known, in practice, this energy term is approximated by DFT functionals.
-In our work, different functionals are tested on BCP molecular system to check the effect of different functionals' impact on charge mobility.
-Different functionals have different ways to represent the exchange-correlation potentials, such as different level of HF exchange potential.
-Then PBE0 functional is used with varying HF component in the exchange-correlation potentials.
+where $T_s[\rho]$ is the kinetic energy, $E_\text{H}[\rho]$ and $E_\text{XC}[\rho]$ the Hartree and exchange-correlation energies, respectively.
+Equations \ref{eq:KS2} and \ref{eq:KS_model} can be solved for different total charge states $x=\text{n,c}$ and corresponding  equilibrium geometries $X=\text{N,C}$, where $\text{n}$ and $\text{N}$ stand for ''neutral'' and $\text{c}$ and $\text{C}$ for ''charged''.
+The respective total energies will be denoted in the following as $U^\text{xX}$.
 
-In practice, Equation \ref{eq:KS2} is solved iteratively, and the wave function is represented by a linear combination of basis functions call basic sets. 
-In this work, the basic set def2-tzvp \cite{weigend_accurate_2006} is used. The DFT computation is performed by VOTCA \cite{Baumeier2011} which internally calls ORCA software.
-
-The internal energy $U_i$ of molecule $i$ depends on the charge states and atomic coordinate (also called geometry) of the molecule. 
-The optimized geometry of a molecule refers to the atomic coordinates that minimize $U_i$.
-Here we use $U_i^\text{xX}$ to denote the internal energy of molecule $i$ at charge state x in the optimized geometry X.
-Neutral and charge states are represented as x=n and c, respectively.
-Similarly, optimized neutral molecular geometry and optimized charge molecular geometry are represented by X=N and C, respectively.
-
-The reorganization energy $R_{ij}$ from molecule $i$ to molecule $j$ is given as:
-\begin{equation}
-    R_{ij} = U_i^\text{nC} - U_i^\text{nN} + U_j^\text{cN} - U_j^\text{cC}
-\end{equation}
-where $U_i^\text{nC}$ is the internal energy of the neutral molecule $i$ in optimized geometry of charged molecule, calculated from Equation \ref{eq:KS_model}. 
-And $U_i^\text{nN}$ the internal energy of the neutral molecule $i$ in optimized geometry of neutral molecule. Similarly, $U_j^\text{cN}, U_j^\text{cC}$ are defined in this way.
-When charge carriers are holes, a charged molecule has one electron less compared to a neutral molecule. 
-For the BCP device, we obtain $R_{ij}=0.50$ eV since this is only one type of molecule.
-
-In a single-component system where internal energy difference of molecule $i$ and $j$ is equal, the energy difference $E_{ij}$ is calculated by:
-\begin{equation}
-    E_{ij} = E_i - E_j
-    \label{eq:siteE}
-\end{equation}
-where $E_i = E_i^\text{c} - E_i^\text{n},E_j = E_j^\text{c} - E_j^\text{n}$ are the molecule energies, the superscript represents charge state or neutral state molecule as mentioned above.
-And $E_i^\text{n} = E_i^\text{n,el} + E_i^\text{n,induce}$ considers the electrostatic energy as well as the energy from the induced dipole moment.
-In multiscale model, $E_i^\text{n} = E_i^\text{n,el} + E_i^\text{n,induce}$ is calculated iteratively from the Thole Model as detailed in \cite{thole_molecular_1981}.
-% instead of using a dielectric constant as been done in the bulk system at macroscopic scale. 
-Specifically, the first step is to calculate the induced dipole at atom $a_i$ by electrostatic field.
-This induced dipole will change the dipole moment at all other atoms $b_j \neq a_i$.
-Then repeat this step and recalculate the induced dipole at atom $a_i$, followed by induced dipoles at all other atoms $b_j$.
-This process is repeated until the induced dipole converge to a fix value.
-In short summary, the $E_i$ is a function of all individual atoms' charges $q$ and induced dipole $\mu$: $E_i^\text{n,el} + E_i^\text{n,induce} = \sum\limits_{a_i} f(q_{a_i}, \mu_{a_i})$ where $a_i$ goes over all the atoms in the system.
-The calculation of $E_i^\text{c} = E_i^\text{c,el} + E_i^\text{c,induce}$ uses similar iteratively process as $E_i^\text{n}$.
-The molecule energies and their distribution are shown in the appendix.
-
-%%%%%%%
-The coupling element $J_{ij}$ between molecule $i$ and $j$ is calculated \cite{baumeier_density_2010} using the electron wave function of the molecules obtained from the Kohn-Sham equation: 
-\begin{equation}
-    J_{ij} = \frac{ J^0_{ij}- \frac{1}{2}(e_i+e_j) S_{ij} }{ 1- S_{ij}^2 }
-    \label{equ:JAB}
-\end{equation}
-where $J^0_{ij} = \langle \phi^\text{HOMO}_i | \hat{H} | \phi^\text{HOMO}_j \rangle $, $e_i = \langle \phi^\text{HOMO}_i | \hat{H} | \phi^\text{HOMO}_i \rangle $, $e_j = \langle \phi^\text{HOMO}_j | \hat{H} | \phi^\text{HOMO}_j \rangle $, and $S_{ij}=\langle \phi^\text{HOMO}_i | \phi^\text{HOMO}_j \rangle $ with bra-ket notation.
-For hole-transporting OSCs system such as the BCP used in this work, $\phi^\text{HOMO}_i$ is the HOMO electron wave function of molecule $i$. 
-The Kohn-Sham Hamiltonian is $\hat{H} = -\frac{1}{2}\nabla^2_{\vec{r}} + \hat{V}_\text{ext} + \hat{V}_\text{H}[\rho] + \hat{V}_\text{XC}[\rho]$. 
-A single molecule is called a monomer, and a pair of two molecules is called a dimer.
-
-Denote $\phi^\text{HOMO}_\text{D}$ as the HOMO electron wave function of the dimer,  $J^0_{ij}$ can be calculated via:
-$
-    J^0_{ij} = \mathbf{p}^i \text{diag}(\mathcal{E}) \mathbf{p}^j
-$, 
-where the vector $\mathbf{p}^i = \langle \phi_i^\text{HOMO} | \phi^\text{HOMO}_\text{D} \rangle$ and $\mathbf{p}^j = \langle \phi_j^\text{HOMO} | \phi_\text{D}^\text{HOMO} \rangle$ are called the projections of the monomer orbitals $\phi_i^\text{HOMO}, \phi_j^\text{HOMO}$ onto the dimer orbitals $\phi^\text{HOMO}_\text{D}$.
-And $\text{diag}(\mathcal{E})$ is the diagonal matrix consisting eigenvalues of the basis function of $\phi_\text{D}^\text{HOMO}$.
-The molecular coupling element distribution is shown in the appendix.
+The practical calculations in this work have been performed with the ORCA software~\cite{Neese2012a} using the def2-tzvp~\cite{weigend_accurate_2006} basis set to represent the Kohn--Sham wave functions $\phi_l(\vec{r})$.
+The correlation potential is represented by PBE0 functional, and the exchange potential is represented by a portion $\alpha$ of (HFX) potential and another portion $(1-\alpha)$ from PBE0 functional.
+In common practice, $\alpha$ is small and below 0.25.
+For our uncertain quantification study, $\alpha=0,0.05,0.10,0.15,0.20,0.25$ is chosen for the multiscale model.
 
@@
 where $\mathbf{D} = \text{diag}(D_i)$ is the out-degree matrix of $\mathbf{W}$.
+
+\begin{equation}
+    v_\text{SS} = \sum_i \pi_i \sum_j \omega_{ij} || \vec{r}_{ij}||_2 = \mathbb{E}f(M_{\infty})
+\end{equation} 
+where $\omega_{ij}$ is the charge transition rate from molecule $i$ to molecule $j$, and $\vec{r}_{ij}=\vec{r}_j - \vec{r}_i$ is the center-of-mass (COM) distance vector. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 In this study, we investigate the hole-transporting organic semiconductor MADN (2-Methyl-9,10-di(naphth-2-yl)anthracene).
-Essential steps in our multiscale model involve calculating the dipole moment $\mu$ and the isotropic polarizability $P_\text{iso}$ for both neutral and charged states in the optimized geometry MADN molecule.
-These properties are crucial for evaluating molecular energy contributions from electrostatic and polarization effects.
 
+Atomic charges and molecule polarizability $P_\text{iso}$ are crucial for evaluating molecular energy contributions from electrostatic and polarization effects.
+A physical property related to the overall atomic charges dipole moment at charge neutral state.
+To demonstration the effect of HFX on the atomic charges and molecule polarizability $P_\text{iso}$,
 Figure \ref{fig:autogen_MADN} illustrates the dependence of the dipole moment $\mu$, isotropic polarizability $P_\text{iso}$, reorganization energy $\lambda$, and energy disorder $\sigma(E)$ on the Hartree-Fock exchange (HFX) parameter.
@@
 
-However, the charge dynamics is dominated by large $\log_{10} J^2$ which are found between molecule pair having large center-of-mass.
+However, the charge dynamics is dominated by large $\log_{10} J^2$ which are found between molecule pair having small center-of-mass.
 As the center-of-mass distance increases, $\log_{10} J^2$ becomes small and negligible for the charge dynamics.
@@
 \begin{equation}
-    \tau = g(\lambda, \{E_i|i=1,2,\cdots,N \}, \{J_{ij}|i,j=1,2,\cdots,N \}) \;
+    %\tau = g(\lambda, \{E_i|i=1,2,\cdots,N \}, \{J_{ij}|i,j=1,2,\cdots,N \}) \;
+    \tau = g(x_1, x_2, \cdots, x_{N_d})
 \end{equation}
-where $\{E_i|i=1,2,\cdots,N \}$ is the ordered set whose elements are the molecule energy,
+The input $(x_1, x_2, \cdots, x_{N_d})$ represents the collection of the parameters $$(\lambda, \{E_i|i=1,2,\cdots,N \}, \{J_{ij}|i,j=1,2,\cdots,N \})$$  where $N_d$ is the parameter dimension, that is the number of input parameters.
+And $\{E_i|i=1,2,\cdots,N \}$ is the ordered set whose elements are the molecule energy,
 $\{J_{ij}|i,j=1,2,\cdots,N \}$ is the ordered set whose elements are the coupling elements.
@@
 \begin{enumerate}
-\item For all $i,j=1,2,\cdots, N$, sample a realization $(\lambda, \{E_i \}, \{J_{ij} \})$ where each parameter has the normal distribution: $\lambda_i \in \mathcal{N}(\bar{\lambda}_i, \sigma_{\lambda_i})$, $E_i \in \mathcal{N}(\bar{E}_i, \sigma_{E_i})$, $J_{ij} \in \mathcal{N}(\bar{J}_{ij}, \sigma_{J_{ij}})$.
-\item Calculate ToF using the sampled data set $(\lambda, \{E_i \}, \{J_{ij} \})$. 
+\item For all $i,j=1,2,\cdots, Nd$, obtain a realization $(x_1, x_2, \cdots, x_{N_d})$ where each parameter has the normal distribution, meaning: $\lambda_i \in \mathcal{N}(\bar{\lambda}_i, \sigma_{\lambda_i})$, $E_i \in \mathcal{N}(\bar{E}_i, \sigma_{E_i})$, $J_{ij} \in \mathcal{N}(\bar{J}_{ij}, \sigma_{J_{ij}})$.
+\item Calculate ToF using the sampled data set $(x_1, x_2, \cdots, x_{Nd})$. 
 \item Repeat step 1 and 2 for $N_\text{MC} = 50000$ times to obtain ToFs. Plot the distribution of the ToFs.
@@
 So making the energy uncorrelated will not shift the ToF to smaller or larger values.
-This enables represent the parameter uncertainties in $\lambda, \{E_i\}, \{ J_{ij}\}$ using the normal distribution without shift the ToF.
+This enables representing the parameter uncertainties in $\lambda, \{E_i\}, \{ J_{ij}\}$ by the normal distribution without shift the ToF.
 
-To understand which uncertainty among $E, \lambda, J_{ij}$ has a greater impact on the ToF, we study the following distribution of ToF:
+To understand how the uncertainty pass from $E, \lambda, J_{ij}$ to ToF, and 
+which uncertainty among $E, \lambda, J_{ij}$ has a greater impact on the ToF, 
+firstly we study the following distribution of ToF:
 \begin{enumerate}
@@
 Then each molecule energy $E_i$ is sampled from the normal distribution $\mathcal{N}(\bar{E}_i, \sigma^2_{E_i})$.
-Finally obtain and plot $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|E_i \text{ uncertain})$.
-    \item Fixed the $E_i$ to be the average $\bar{E}_i$ and and $J_{ij}$ to be the averaged $\bar{J}_{ij}$.
+Finally obtain and plot the histogram $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|E_i \text{ uncertain})$.
+    \item Fixed all $E_i$ to be the average $\bar{E}_i$ and all $J_{ij}$ to be the averaged $\bar{J}_{ij}$.
 Then $\lambda$ is sampled from the normal distribution $\mathcal{N}(\bar{\lambda}, \sigma^2_{\lambda})$.
-Finally obtain and plot $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|\lambda \text{ uncertain})$.
+Finally obtain and plot the histogram  $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|\lambda \text{ uncertain})$.
     \item Fixed the $E_i$ to be the average $\bar{E}_i$ and $\lambda$ to be the averaged $\bar{\lambda}$.
 Then $J_{ij}$ is sampled from the normal distribution $\mathcal{N}(\bar{J}_{ij}, \sigma^2_{J_{ij}})$.
-Finally obtain and plot $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$.
-    \item Both $E_i$, $\lambda$ and $J_{ij}$ are sample from their normal distribution: $\mathcal{N}(\bar{E}_i, \sigma^2_{E_i})$, $\mathcal{N}(\bar{\lambda}, \sigma^2_{\lambda})$ and $\mathcal{N}(\bar{J}_{ij}, \sigma^2_{J_{ij}})$.
-Then obtain and plot $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$.
+Finally obtain and plot the histogram  $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$.
+    \item Both $E_i$, $\lambda$ and $J_{ij}$ are sampled from their normal distribution: $\mathcal{N}(\bar{E}_i, \sigma^2_{E_i})$, $\mathcal{N}(\bar{\lambda}, \sigma^2_{\lambda})$ and $\mathcal{N}(\bar{J}_{ij}, \sigma^2_{J_{ij}})$.
+Then obtain and plot the histogram $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$.
 \end{enumerate}
@@
     \caption{Distribution of ToFs in the multiscale modeled MADN system using PBE0 functional and varying HFX.
+Monte Carlo sampling with a sample size $N_\text{MC}=50000$ is used to obtain the sampled distribution.
     (a) $P(\log_{10}(\tau)|E_i \text{ uncertain})$, 
@@
 
-The 90\% confidence interval of each distribution and the fitted Gamma distribution is summarized in table
+% The 90\% confidence interval of each distribution and the fitted Gamma distribution is summarized in table
 
@@
     \includegraphics[width=0.99\textwidth]{figs/MADN_HFX/fig_mle_MADN_noE.pdf}
-    \caption{Distribution of ToFs in the multiscale modeled MADN system using PBE0 functional and varying HFX. Energy disorder is not consider. 
+    \caption{Distribution of ToFs in the multiscale modeled MADN system using PBE0 functional and varying HFX.
+Energy disorder is not consider.
+Monte Carlo sampling with a sample size $N_\text{MC}=50000$ is used to obtain the sampled distribution.
     (a) $P(\log_{10}(\tau)|\lambda \text{ uncertain})$, 
@@
 \begin{equation}
-    S_{Ti} = \frac{ \mathbb{E}_{x_{\sim i}}[ \text{Var}_{x_i}(\tau|x_{\sim i}) ] }{ \text{Var}(\tau) }
+    S_{T,i} = \frac{ \mathbb{E}_{x_{\sim i}}[ \text{Var}_{x_i}(\tau|x_{\sim i}) ] }{ \text{Var}(\tau) }
     \label{eq:STi}
 \end{equation}
+Then the $\lambda$ contribution to the total variance is $S_{T,i=1}$.
+The energy contribution to the total variance is $S_{T,E} = \sum\limits_{i=1}^{N+1} S_{T,i}$ where $N=1000$ is the number of energy parameter, and the coupling element contribution to the total variance is $S_{T,J}=\sum\limits_{i=N+2}^{N_d} S_{T,i}$.
+Using the quasi Monte Carlo method\cite{sobol_global_2001} with a sample size $N_\text{QMC}=1000$ to calculate $S_{T,i}$, the results are shown in the table \ref{tab:Sobol}.
+%
+\begin{table}[H]
+    \centering
+    \begin{tabular}{c c c c }
+        \toprule
+        parameter & $\lambda$ & $E$ & $\log_{10} J^2$   \\
+        \midrule
+        $S_T$ & 0.097 & 0.95 & 0.018\\
+        \bottomrule
+    \end{tabular}
+        \caption{Sobol indices of $\lambda$, $E$ and $\log_{10} J^2$.}
+        \label{tab:Sobol}
+\end{table}
+%
+The table \ref{tab:Sobol} shows that most of the total variance can be attributed to the energy $E$.
+In contrast to $E$, the uncertainty in $\log_{10} J^2$ contributes much less compared to $E$, this is consistent to the Fig.\ref{fig:mle_MADN_withE}, where the distribution in Fig.\ref{fig:mle_MADN_withE}(d) resembles the distribution in Fig.\ref{fig:mle_MADN_withE}(a).
+And Fig.\ref{fig:mle_MADN_withE}(c) shows that the uncertainty in $\log_{10}(J^2)$ only leads to small variances.
 
@@
     \includegraphics[width=0.8\textwidth]{figs/MADN_HFX/fig_mle_MADN_withE_SS.pdf}
-    \caption{Distribution of steady state velocity $v_\text{SS}$ in the multiscale modeled MADN system using PBE0 functional when (a) the molecule site energy $E$ are sampled from a normal distribution $E \sim N(E_\text{ave},E^2_\text{std})$, (b) the reorganization energy $\lambda$ are sampled from a normal distribution $\lambda \sim N(\lambda_\text{ave},\lambda^2_\text{std})$, (c) the quantity $\log_{10}(J^2)$ are sampled from a normal distribution $\log_{10}(J^2) \sim N(\mathbb{E}[\log_{10}(J^2)], \textbf{Var}[\log_{10}(J^2)] )$.
-(d) Both $E$, $\lambda$ and $\log_{10}(J^2)$ are sampled from the normal distribution.
+    \caption{Distribution of steady state velocity $v_\text{SS}$ in the multiscale modeled MADN system using PBE0 functional.
+    Monte Carlo sampling with a sample size $N_\text{MC}=50000$ is used to obtain the sampled distribution.
+    (a) the molecule site energy $E$ are sampled from a normal distribution $E \sim N(E_\text{ave},E^2_\text{std})$, (b) the reorganization energy $\lambda$ are sampled from a normal distribution $\lambda \sim N(\lambda_\text{ave},\lambda^2_\text{std})$, (c) the quantity $\log_{10}(J^2)$ are sampled from a normal distribution $\log_{10}(J^2) \sim N(\mathbb{E}[\log_{10}(J^2)], \textbf{Var}[\log_{10}(J^2)] )$.
+(d) Both$E$, $\lambda$ and $\log_{10}(J^2)$ are sampled from the normal distribution.
 }
@@
     \caption{Distribution of steady state velocity $v_\text{SS}$ in the multiscale modeled MADN system using PBE0 functional. All molecule energies are set to be zero.  
+    Monte Carlo sampling with a sample size $N_\text{MC}=50000$ is used to obtain the sampled distribution.
     The plots are for the situation: (a) The reorganization energy $\lambda$ are sampled from a normal distribution $\lambda \sim N(\lambda_\text{ave},\lambda^2_\text{std})$.
@@
 \section{Comparison of Diffusive Charge Velocity Between BCP and MADN}
+
 In this section we compare the diffusive charge velocity between BCP and MADN.
+
+The energy in BCP system is correlated, and making the energy uncorrelated by shuffling the molecule energy leads to a shift in ToF, as shown in Fig.\ref{fig:ToF_shuffle_BCP}
+%
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\textwidth]{figs/BCP_HFX/ToFx_shuffle.pdf}
+    \caption{Distribution of $\tau_{\text{sh}}$ in BCP calculated using shuffle energies.
+Each distribution are a sample of 10000 $\tau_{\text{shuffle}}$.
+The position of the solid circle indicates the ToF calculated from the specific $\alpha$ value, and the position of the solid square indicates the average $\tau_{\text{shuffle}}$ over the 10000 samples.}
+    \label{fig:ToF_shuffle_BCP}
+\end{figure}
+%
+This figure shows that the ToF $\tau$ obtained with the specific HFX is always larger than the $\tau_\text{sh}$.
+So there is a shift in ToF when making the energies uncorrelated.
+
 The following tables show the diffusive charge velocity for BCP and MADN with HFX=0.05, 0.15, 0.25. The situations of using energy disorder and without energy disorder are considered.

### 2024-11-06 figs/2CC-RW-TOF.py
Delete figs directory

@@ -1,755 +1,0 @@
-#!/usr/bin/env python
-# coding: utf-8
-
-#!/usr/bin/env python
-import numpy as np
-import argparse
-import glob, os
-import sqlite3
-import inspect
-
-import math
-
-import scipy as sp
-import matplotlib.pyplot as plt
-
-from scipy.sparse import lil_matrix
-from scipy.sparse.linalg import *
-
-import scipy.sparse
-import networkx as nx
-
-from functools import partial
-import itertools
-from itertools import repeat
-import  multiprocessing 
-
-from datetime import datetime
-
-import os.path
-
- 
- 
-
-k_B = 8.617333 * 10**(-5) # ev/K
-pi = math.pi
-hbar = 6.582119569 * 1e-16 # eV*s
-
-
-def report(xk):
-    frame = inspect.currentframe().f_back
-    if frame.f_locals['iter_']%100 == 0:
-        print("    ---INFO SOLVER, iteration:", frame.f_locals['iter_'], "residual:", frame.f_locals['resid'])
-
-#rate Matrix calculator
-def calculate_1c_ratematrix(J2, E1, lam, n_sites, seg1, seg2, drX, drY, drZ, efield):
-
-    W1 = np.zeros((int(n_sites),int(n_sites)))
-
-    fieldVector = [efield,0,0] # field in x direction
-            
-    for i in range(len(seg1)):
-        if seg1[i] < seg2[i]:
-            # marcus rate seg2[i] -> seg1[i]
-            dE_field = 1E-9*(fieldVector[0]*drX[i] + fieldVector[1]*drY[i] + fieldVector[2]*drZ[i])
-            dE = dE_field  +  (E1[seg2[i]]-E1[seg1[i]])
-            W1[seg2[i],seg1[i]] = Marcus(dE, J2[i], lam)
-            W1[seg1[i],seg2[i]] = Marcus(-dE, J2[i], lam)
-
-    return W1
-
-# marcus rate
-def Marcus(dE,Jsq,re):
-    temp = 2*pi/hbar * Jsq/math.sqrt(4*pi*(re*k_B*T))*math.exp(-(dE-re)**2/(4*re*k_B*T) )
-    return temp
-
-
-def parse_SQL(statefile):
-
-    con = sqlite3.connect(statefile)
-    c=con.cursor()
-    id = []
-    posX = []
-    posY = []
-    posZ = []
-    eCation = []
-    sql = "SELECT id, posX, posY, posZ, eCation FROM segments"
-
[…]

### 2024-11-06 figs/KDE.py

@@ -1,48 +1,0 @@
-from sklearn.cluster import KMeans
-from sklearn.neighbors import RadiusNeighborsClassifier
-import numpy as np
-import math
-import matplotlib.pyplot as plt
-
-N = 1000
-
-def kde(data):
-    h = 1e-5
-    input = np.arange(-2,2,0.002)
-    kde_result = []
-    for i in range(2000):
-        temp = 0
-        for j in range(data.shape[0]):
-            temp += 1/ (h * np.sqrt(2 * math.pi)) * np.exp(-(input[i] - data[j])**2/(2*h))
-        kde_result.append(temp/N)
-    return input, kde_result
-
-fig,ax = plt.subplots(2,3,figsize=(15,10))
-x,y = kde(np.loadtxt("PBE0/eigenvec1.txt"))
-ax[0][0].plot(x,y,label="PBE0",color="black",linewidth=3.0)
-ax[0][0].set_yscale("log")
-x,y = kde(np.loadtxt("PBE/eigenvec1.txt"))
-ax[0][1].plot(x,y,label="PBE",color="black",linewidth=3.0)
-ax[0][1].set_yscale("log")
-x,y = kde(np.loadtxt("B3LYP/eigenvec1.txt"))
-ax[0][2].plot(x,y,label="B3LYP",color="black",linewidth=3.0)
-ax[0][2].set_yscale("log")
-x,y = kde(np.loadtxt("BHANDHLYP/eigenvec1.txt"))
-ax[1][0].plot(x,y,label="BH",color="black",linewidth=3.0)
-ax[1][0].set_yscale("log")
-x,y = kde(np.loadtxt("TPSS/eigenvec1.txt"))
-ax[1][1].plot(x,y,label="TPSS",color="black",linewidth=3.0)
-ax[1][1].set_yscale("log")
-x,y = kde(np.loadtxt("BP86/eigenvec1.txt"))
-ax[1][2].plot(x,y,label="BP86",color="black",linewidth=3.0)
-ax[1][2].set_yscale("log")
-for i in range(2):
-    for j in range(3):
-        ax[i][j].set_yscale("log")
-        ax[i][j].legend(frameon=False,fontsize=14)
-        ax[i][j].set_xlabel(r"$x$",fontsize=16)
-        ax[i][j].set_ylabel(r"$\hat{f}(x)$",fontsize=16)
-        ax[i][j].tick_params(axis='both', which='major', labelsize=14)
-
-plt.tight_layout()
-plt.savefig("kde.png",dpi=300)

### 2024-11-06 figs/PBE/metric3.py

@@ -1,255 +1,0 @@
-import math
-k_B = 8.617333 * 10**(-5) # ev/K
-pi = math.pi
-hbar = 6.582119569 * 1e-16 # eV*s
-###### import packages ####################################
-import os
-import xml.etree.ElementTree as ET
-
-import numpy as np
-import argparse
-import glob, os
-import sqlite3
-import inspect
-
-import math
-
-import scipy as sp
-import matplotlib.pyplot as plt
-
-from scipy.sparse import lil_matrix
-from scipy.sparse.linalg import *
-
-import scipy.sparse
-import networkx as nx
-
-from functools import partial
-import itertools
-from itertools import repeat
-import  multiprocessing 
-
-from datetime import datetime
-
-import os.path
-import os.path
-from sklearn.cluster import KMeans
-from sklearn.neighbors import RadiusNeighborsClassifier
-
-############ need to change re
-re = 0.155563575 + 0.147270720
-N = 1000
-
-def report(xk):
-    frame = inspect.currentframe().f_back
-    if frame.f_locals['iter_']%100 == 0:
-        print("    ---INFO SOLVER, iteration:", frame.f_locals['iter_'], "residual:", frame.f_locals['resid'])
-
-def Marcus(E,J,re):
-    temp = 2*pi/hbar * J**2/math.sqrt(4*pi*(re*k_B*300))*math.exp(-(E-re)**2/(4*re*k_B*300) )
-    return temp
-
-def setup_1c_system(W1, sink_region):
-    # determine the two carrier state matrix in sparse from with the help of graph methods in networkx
-    n1 = W1.shape[0]
-    G = nx.from_numpy_array(W1, create_using=nx.DiGraph())
-
-    outflowrate = W1.sum(axis=0)
-    print("    ---INFO", datetime.now().strftime("%H:%M:%S"), "outflow rate vector" )
-
-    normalized_rate = W1 @ np.diag(np.reciprocal(outflowrate))
-    # set sink parts to zero
-    for sink in sink_region:
-        normalized_rate[:,sink] = 0.0
-
-    probability = np.identity(n1) - normalized_rate.T
-    print("    ---INFO", datetime.now().strftime("%H:%M:%S"), "probability matrix" )
-
[…]

### 2024-11-06 figs/kmeansRW.py

@@ -1,104 +1,0 @@
-from sklearn.cluster import KMeans
-from sklearn.neighbors import RadiusNeighborsClassifier
-import numpy as np
-import math
-import matplotlib.pyplot as plt
-
-N = 1000
-
-x1 = np.loadtxt("PBE0/eigenvec1RW.txt")
-x2 = np.loadtxt("PBE/eigenvec1RW.txt")
-x3 = np.loadtxt("B3LYP/eigenvec1RW.txt")
-x4 = np.loadtxt("BHANDHLYP/eigenvec1RW.txt")
-x5 = np.loadtxt("TPSS/eigenvec1RW.txt")
-x6 = np.loadtxt("BP86/eigenvec1RW.txt")
-x7 = np.loadtxt("wB97X/eigenvec1RW.txt")
-x8 = np.loadtxt("wB97X-D3/eigenvec1RW.txt")
-x9 = np.loadtxt("M06L/eigenvec1RW.txt")
-x10 = np.loadtxt("BHLYP/eigenvec1RW.txt")
-ToF = [1.23e-3,1.04e-3,4.28e-3,737.94,1.37e-2,7.46e-3,2.92e-2,0.0489,0.319,2.47]
-
-dict_eigVec = {1:x1,2:x2,3:x3,4:x4,5:x5,6:x6,7:x7,8:x8,9:x9,10:x10}
-dict_func = {1:"PBE0",2:"PBE",3:"B3LYP",4:"BHAND",5:"TPSS",6:"BP86",7:"wB97X",8:"wB97X-D3",9:"M06L",10:"BHLYP"}
-
-
-fig,ax = plt.subplots(figsize=(10, 6))
-for i in np.arange(1,11,1):
-    ax.scatter(np.ones(N)+i-1,dict_eigVec[i],label=dict_func[i])
-ax.set_xlim(0,15)
-ax.tick_params(axis='y', labelsize=16)
-
-ax.set_ylabel(r"eigenvector elements",fontsize=18)
-ax.legend()
-plt.tick_params(
-    axis='x',          # changes apply to the x-axis
-    which='both',      # both major and minor ticks are affected
-    bottom=False,      # ticks along the bottom edge are off
-    top=False,         # ticks along the top edge are off
-    labelbottom=False) 
-fig.savefig("fig_distri_eigenVecRW.pdf",dpi=300)
-##################################### get cost kMeans for 2c ######################
-all_cost = []
-
-for i in np.arange(1,11,1):
-    data = np.zeros((N,2))
[…]

### 2024-11-06 figs/kmeansW.py

@@ -1,113 +1,0 @@
-from sklearn.cluster import KMeans
-from sklearn.neighbors import RadiusNeighborsClassifier
-import numpy as np
-import math
-import matplotlib.pyplot as plt
-
-N = 1000
-
-x1 = np.loadtxt("PBE0/eigenvec1Lw.txt")
-x2 = np.loadtxt("PBE/eigenvec1Lw.txt")
-x3 = np.loadtxt("B3LYP/eigenvec1Lw.txt")
-x4 = np.loadtxt("BHANDHLYP/eigenvec1Lw.txt")
-x5 = np.loadtxt("TPSS/eigenvec1Lw.txt")
-x6 = np.loadtxt("BP86/eigenvec1Lw.txt")
-x7 = np.loadtxt("wB97X/eigenvec1Lw.txt")
-x8 = np.loadtxt("wB97X-D3/eigenvec1Lw.txt")
-x9 = np.loadtxt("M06L/eigenvec1Lw.txt")
-x10 = np.loadtxt("BHLYP/eigenvec1Lw.txt")
-ToF = [1.23e-3,1.04e-3,4.28e-3,737.94,1.37e-2,7.46e-3,2.92e-2,0.0489,0.319,2.47]
-dict_eigVec = {1:x1,2:x2,3:x3,4:x4,5:x5,6:x6,7:x7,8:x8,9:x9,10:x10}
-dict_func = {1:"PBE0",2:"PBE",3:"B3LYP",4:"BHAND",5:"TPSS",6:"BP86",7:"wB97X",8:"wB97X-D3",9:"M06L",10:"BHLYP"}
-
-egval1 = np.sort(np.loadtxt("PBE0/eigenvalLw.txt"))[0:7]
-egval2 = np.sort(np.loadtxt("PBE/eigenvalLw.txt"))[0:7]
-egval3 = np.sort(np.loadtxt("B3LYP/eigenvalLw.txt"))[0:7]
-egval4 = np.sort(np.loadtxt("BHANDHLYP/eigenvalLw.txt"))[0:7]
-egval5 = np.sort(np.loadtxt("TPSS/eigenvalLw.txt"))[0:7]
-egval6 = np.sort(np.loadtxt("BP86/eigenvalLw.txt"))[0:7]
-egval7 = np.sort(np.loadtxt("wB97X/eigenvalLw.txt"))[0:7]
[…]

### 2024-11-06 figs/plot_DeltaToF_W_KL.py

@@ -1,109 +1,0 @@
-from scipy.stats import wasserstein_distance
-from scipy.stats import entropy
-
-import numpy as np
-import scipy as sp
-import matplotlib.pyplot as plt
-
-J_data = np.loadtxt("PBE/J.txt")
-seg1 = J_data[:,0]
-seg2 = J_data[:,1]
-Js = J_data[:,2]
-J_PBE0 = np.loadtxt("PBE0/J.txt")
-J_PBE = np.loadtxt("PBE/J.txt")
-J_B3LYP = np.loadtxt("B3LYP/J.txt")
-J_BH = np.loadtxt("BHANDHLYP/J.txt")
-J_TPSS = np.loadtxt("TPSS/J.txt")
-J_BP86 = np.loadtxt("BP86/J.txt")
-J_wB97X = np.loadtxt("wB97X/J.txt")
-J_wB97XD3 = np.loadtxt("wB97X-D3/J.txt")
-J_M06L = np.loadtxt("M06L/J.txt")
-J_BHLYP = np.loadtxt("BHLYP/J.txt")
-
-E_PBE0 = np.loadtxt("PBE0/E.txt")
-E_PBE = np.loadtxt("PBE/E_PBE.txt")
-E_B3LYP = np.loadtxt("B3LYP/E_B3LYP.txt")
-E_BH = np.loadtxt("BHANDHLYP/E.txt")
-E_TPSS = np.loadtxt("TPSS/E.txt")
-E_BP86 = np.loadtxt("BP86/E_BP86.txt")
-E_wB97X = np.loadtxt("wB97X/E_wB97X.txt")
-E_wB97XD3 = np.loadtxt("wB97X-D3/E.txt")
-E_M06L = np.loadtxt("M06L/E.txt")
-E_BHLYP = np.loadtxt("BHLYP/E.txt")
-ToFs = [1.23e-3,1.04e-3,4.28e-3,737.94,1.37e-2,7.46e-3,0.02916,0.0489,0.319,2.47]
-lam = [0.388,0.303,0.375,0.494,0.310,0.304,0.505,0.495,0.312,0.493]
-dict_E = { 1:E_PBE0, 2:E_PBE, 3:E_B3LYP, 4:E_BH, 5:E_TPSS, 6:E_BP86, 7:E_wB97X, 8: E_wB97XD3, 9: E_M06L, 10: E_BHLYP}
[…]

### 2024-11-06 figs/plot_DeltaToF_W_all.py

@@ -1,226 +1,0 @@
-from scipy.stats import wasserstein_distance
-from scipy.stats import entropy
-import scipy.stats as stats
-
-import numpy as np
-import scipy as sp
-import matplotlib.pyplot as plt
-import math
-k_B = 8.617333 * 10**(-5) # ev/K
-pi = math.pi
-hbar = 6.582119569 * 1e-16 # eV*s
-T = 300
-
-def Marcus(E,J,re):
-    temp = 2*pi/hbar * J**2/math.sqrt(4*pi*(re*k_B*300))*math.exp(-(E-re)**2/(4*re*k_B*300) )
-    return temp
-
-J_data = np.loadtxt("PBE/J.txt")
-seg1 = J_data[:,0]
-seg2 = J_data[:,1]
-Js = J_data[:,2]
-J_PBE0 = np.loadtxt("PBE0/J.txt")
-J_PBE = np.loadtxt("PBE/J.txt")
-J_B3LYP = np.loadtxt("B3LYP/J.txt")
-J_BH = np.loadtxt("BHANDHLYP/J.txt")
-J_TPSS = np.loadtxt("TPSS/J.txt")
-J_BP86 = np.loadtxt("BP86/J.txt")
-J_wB97X = np.loadtxt("wB97X/J.txt")
-J_wB97XD3 = np.loadtxt("wB97X-D3/J.txt")
-J_M06L = np.loadtxt("M06L/J.txt")
-J_BHLYP = np.loadtxt("BHLYP/J.txt")
-
-E_PBE0 = np.loadtxt("PBE0/E.txt")
-E_PBE = np.loadtxt("PBE/E_PBE.txt")
-E_B3LYP = np.loadtxt("B3LYP/E_B3LYP.txt")
-E_BH = np.loadtxt("BHANDHLYP/E.txt")
-E_TPSS = np.loadtxt("TPSS/E.txt")
-E_BP86 = np.loadtxt("BP86/E_BP86.txt")
-E_wB97X = np.loadtxt("wB97X/E_wB97X.txt")
-E_wB97XD3 = np.loadtxt("wB97X-D3/E.txt")
-E_M06L = np.loadtxt("M06L/E.txt")
-E_BHLYP = np.loadtxt("BHLYP/E.txt")
-ToFs = [1.23e-3,1.04e-3,4.28e-3,737.94,1.37e-2,7.46e-3,0.02916,0.0489,0.319,2.47]
[…]

### 2024-11-06 figs/plot_E_ToF_Z_PBE.py

@@ -1,81 +1,0 @@
-from sklearn.cluster import KMeans
-from sklearn.neighbors import RadiusNeighborsClassifier
-import numpy as np
-import math
-import matplotlib.pyplot as plt
-
-E66 = np.loadtxt("PBE/E66_range.txt")
-all_cost = np.loadtxt("PBE/all_cost.txt")
-all_ToF = np.loadtxt("PBE/all_ToF.txt")
-
-size =23
-fig,(ax1,ax2) = plt.subplots(1,2,figsize=(16,8))
-ln1 = ax1.plot(E66, all_cost,"--o",markersize=9,color="red", label=r"$E_{t}$ vs $Z$")
-ax1.set_xlabel(r"$E_{t}$[eV]",fontsize=size)
-ax1.set_ylabel(r"$Z_{2c}(E_t)$",fontsize=size)
-ax1.set_yscale("log")
-ax1.tick_params(axis='both',labelsize=size)
-ax1.set_ylim(1e-18,1e3)
-ax1.annotate("(a)", xy=(-0.25,1), xycoords='axes fraction', size=30)
-
-#ax1.legend(fontsize=size,frameon=False)
-
-ax1_2 = ax1.twinx()
-ln1_2 = ax1_2.plot(E66,all_ToF,"--o",markersize=9,color="black",label=r"$E_{t}$ vs $ToF$")
-ax1_2.set_yscale("log")
-ax1_2.set_ylabel(r"$ToF(E_{t})$[s]",fontsize=size,color="red")
-ax1_2.tick_params(axis='y',labelsize=size,color="red")
-#ax1_2.spines['right'].set_color('red') 
-lns = ln1+ln1_2
-labs = [l.get_label() for l in lns]
-ax1.legend(lns, labs, loc=1,fontsize=21,frameon=False)
-
-ax2.plot(all_ToF, all_cost,"--*",markersize=9,color="black", label=r"$E_{t}$ vs $Z$")
-ax2.set_xlabel(r"$ToF(E_t)$ [s]",fontsize=size)
-ax2.set_ylabel(r"$Z_{2c}(E_t)$",fontsize=size)
-ax2.set_yscale("log")
-ax2.set_xscale("log")
-ax2.tick_params(axis='both',labelsize=size)
-ax2.annotate("(b)", xy=(-0.25,1), xycoords='axes fraction', size=30)
[…]

### 2024-11-06 figs/plot_PF.py

@@ -1,47 +1,0 @@
-import numpy as np
-import scipy as sp
-import matplotlib.pyplot as plt
-import math
-k_B = 8.617333 * 10**(-5) # ev/K
-pi = math.pi
-hbar = 6.582119569 * 1e-16 # eV*s
-
-x1 = [4e7,5e7,6e7,7e7,8e7,9e7]
-for i in range(len(x1)):
-    x1[i] = np.sqrt(x1[i]/100)
-    
-mu_PBE0 = np.loadtxt("PBE0/mu.txt")
-mu_PBE = np.loadtxt("PBE/mu.txt")
-mu_B3LYP = np.loadtxt("B3LYP/mu.txt")
-mu_BHANDHLYP = np.loadtxt("BHANDHLYP/mu.txt")
-mu_TPSS = np.loadtxt("TPSS/mu.txt")
-mu_BP86 = np.loadtxt("BP86/mu.txt")
-
-fig,ax = plt.subplots()
-
-
-#ax.plot(x1,mu_k10_cor,'k^-')#,label='k=1.0')
-#ax.plot(x1,mu_k0,'b--o',label='$k=0.0\,(\sigma=0.00\mathrm{eV})$',markersize=10, markerfacecolor='none')
-ax.plot(x1,mu_PBE0,'r--o',label='$PBE0$',markersize=10,markerfacecolor='none')
-ax.plot(x1,mu_PBE,'g--o', label='$PBE$',markersize=10,markerfacecolor='none')
-ax.plot(x1,mu_B3LYP,'k--o',label='$B3LYP$',markersize=10,markerfacecolor='none')
-ax.plot(x1,mu_BHANDHLYP,'--o',label='$BHANDHLYP$',markersize=10,markerfacecolor='none')
-ax.plot(x1,mu_TPSS,'--o', label='$TPSS$',markersize=10,markerfacecolor='none')
-ax.plot(x1,mu_BP86,'--o',label='$BP86$',markersize=10,markerfacecolor='none')
-
-# ax.set_xlabel(r'$F^{1/2}$ (V/cm)$^{1/2}$',fontsize=12)
-ax.set_xlabel('$F^{1/2} \; [(V/cm)^{1/2}]$',fontsize=14)
-ax.set_ylabel("$\mu \; [cm^2/(Vs)]$",size=14)
-ax.set_xlim(600,1100)
-#ax.set_ylim(1e-5,1e1)
[…]

### 2024-11-06 figs/plot_PFe.py

@@ -1,46 +1,0 @@
-import numpy as np
-import scipy as sp
-import matplotlib.pyplot as plt
-import math
-k_B = 8.617333 * 10**(-5) # ev/K
-pi = math.pi
-hbar = 6.582119569 * 1e-16 # eV*s
-
-x1 = [4e7,5e7,6e7,7e7,8e7,9e7]
-for i in range(len(x1)):
-    x1[i] = np.sqrt(x1[i]/100)
-    
-mu_PBE0 = np.loadtxt("PBE0/mu_e.txt")
-mu_PBE = np.loadtxt("PBE/mu_e.txt")
-mu_B3LYP = np.loadtxt("B3LYP/mu_e.txt")
-mu_BHANDHLYP = np.loadtxt("BHANDHLYP/mu_e.txt")
-mu_TPSS = np.loadtxt("TPSS/mu_e.txt")
-mu_BP86 = np.loadtxt("BP86/mu_e.txt")
-
-fig,ax = plt.subplots()
-
-
-#ax.plot(x1,mu_k10_cor,'k^-')#,label='k=1.0')
-#ax.plot(x1,mu_k0,'b--o',label='$k=0.0\,(\sigma=0.00\mathrm{eV})$',markersize=10, markerfacecolor='none')
-ax.plot(x1,mu_PBE0,'r--o',label='$PBE0$',markersize=10,markerfacecolor='none')
-ax.plot(x1,mu_PBE,'g--o', label='$PBE$',markersize=10,markerfacecolor='none')
-ax.plot(x1,mu_B3LYP,'k--o',label='$B3LYP$',markersize=10,markerfacecolor='none')
-ax.plot(x1,mu_BHANDHLYP,'--o',label='$BHANDHLYP$',markersize=10,markerfacecolor='none')
-ax.plot(x1,mu_TPSS,'--o', label='$TPSS$',markersize=10,markerfacecolor='none')
-ax.plot(x1,mu_BP86,'--o',label='$BP86$',markersize=10,markerfacecolor='none')
-
-# ax.set_xlabel(r'$F^{1/2}$ (V/cm)$^{1/2}$',fontsize=12)
-ax.set_xlabel('$F^{1/2} \; [(V/cm)^{1/2}]$',fontsize=14)
-ax.set_ylabel("$\mu_e \; [cm^2/(Vs)]$",size=14)
-ax.set_xlim(600,1100)
-#ax.set_ylim(1e-5,1e1)
[…]

### 2024-11-06 figs/plot_eigvalRatio.py

@@ -1,108 +1,0 @@
-from scipy.stats import wasserstein_distance
-from scipy.stats import entropy
-import scipy.stats as stats
-
-import numpy as np
-import scipy as sp
-import matplotlib.pyplot as plt
-import math
-k_B = 8.617333 * 10**(-5) # ev/K
-pi = math.pi
-hbar = 6.582119569 * 1e-16 # eV*s
-T = 300
-
-def Marcus(E,J,re):
-    temp = 2*pi/hbar * J**2/math.sqrt(4*pi*(re*k_B*300))*math.exp(-(E-re)**2/(4*re*k_B*300) )
-    return temp
-
-J_data = np.loadtxt("PBE/J.txt")
-seg1 = J_data[:,0]
-seg2 = J_data[:,1]
-Js = J_data[:,2]
-E_PBE0 = np.loadtxt("PBE0/E.txt")
-E_PBE = np.loadtxt("PBE/E_PBE.txt")
-E_B3LYP = np.loadtxt("B3LYP/E_B3LYP.txt")
-E_BH = np.loadtxt("BHANDHLYP/E.txt")
-E_TPSS = np.loadtxt("TPSS/E.txt")
-E_BP86 = np.loadtxt("BP86/E_BP86.txt")
-E_wB97X = np.loadtxt("wB97X/E_wB97X.txt")
-E_wB97XD3 = np.loadtxt("wB97X-D3/E.txt")
-E_M06L = np.loadtxt("M06L/E.txt")
-E_BHLYP = np.loadtxt("BHLYP/E.txt")
-ToFs = [1.23e-3,1.04e-3,4.28e-3,737.94,1.37e-2,7.46e-3,0.02916,0.0489,0.319,2.47]
-lam = [0.388,0.303,0.375,0.494,0.310,0.304,0.505,0.495,0.312,0.493]
-dict_E = { 1:E_PBE0, 2:E_PBE, 3:E_B3LYP, 4:E_BH, 5:E_TPSS, 6:E_BP86, 7:E_wB97X, 8: E_wB97XD3, 9: E_M06L, 10: E_BHLYP}
-
-#eigval_2nd = [3.08e10,6.47e10,1.25e11,6.65e09,6.16e+10,7.35e10,1.74e+10]
[…]

### 2024-11-06 figs/plot_kmeans.py

@@ -1,182 +1,0 @@
-from sklearn.cluster import KMeans
-from sklearn.neighbors import RadiusNeighborsClassifier
-import numpy as np
-import math
-import matplotlib.pyplot as plt
-
-N = 1000
-
-x1 = np.loadtxt("PBE0/eigenvec1RW.txt")
-x2 = np.loadtxt("PBE/eigenvec1RW.txt")
-x3 = np.loadtxt("B3LYP/eigenvec1RW.txt")
-x4 = np.loadtxt("BHANDHLYP/eigenvec1RW.txt")
-x5 = np.loadtxt("TPSS/eigenvec1RW.txt")
-x6 = np.loadtxt("BP86/eigenvec1RW.txt")
-x7 = np.loadtxt("wB97X/eigenvec1RW.txt")
-x8 = np.loadtxt("wB97X-D3/eigenvec1RW.txt")
-x9 = np.loadtxt("M06L/eigenvec1RW.txt")
-x10 = np.loadtxt("BHLYP/eigenvec1RW.txt")
-ToF = [1.23e-3,1.04e-3,4.28e-3,737.94,1.37e-2,7.46e-3,2.92e-2,0.0489,0.319,2.47]
-
-dict_eigVec = {1:x1,2:x2,3:x3,4:x4,5:x5,6:x6,7:x7,8:x8,9:x9,10:x10}
-dict_func = {1:"PBE0",2:"PBE",3:"B3LYP",4:"BHAND",5:"TPSS",6:"BP86",7:"wB97X",8:"wB97X-D3",9:"M06L",10:"BHLYP"}
-
-fig,ax = plt.subplots(figsize=(10, 6))
-for i in np.arange(1,11,1):
-    ax.scatter(np.ones(N)+i-1,dict_eigVec[i],label=dict_func[i])
-ax.set_xlim(0,15)
-ax.tick_params(axis='y', labelsize=16)
-
-ax.set_ylabel(r"eigenvector elements",fontsize=18)
-ax.legend(fontsize=13)
-plt.tick_params(
-    axis='x',          # changes apply to the x-axis
-    which='both',      # both major and minor ticks are affected
-    bottom=False,      # ticks along the bottom edge are off
-    top=False,         # ticks along the top edge are off
-    labelbottom=False) 
-fig.savefig("fig_distri_eigenVecRW.pdf",dpi=600)
-
-
-##################################### get cost kMeans for ######################
-################ for L_RW
-all_cost_2c_RW = []
-for i in np.arange(1,11,1):
[…]

### 2024-11-06 figs/plot_scatterE.py

@@ -1,141 +1,0 @@
-from scipy.stats import wasserstein_distance
-from scipy.stats import entropy
-import scipy.stats as stats
-
-import numpy as np
-import scipy as sp
-import matplotlib.pyplot as plt
-import math
-import matplotlib.gridspec as gridspec
-import matplotlib as mpl
-
-k_B = 8.617333 * 10**(-5) # ev/K
-pi = math.pi
-hbar = 6.582119569 * 1e-16 # eV*s
-T = 300
-
-def Marcus(E,J,re):
-    temp = 2*pi/hbar * J**2/math.sqrt(4*pi*(re*k_B*300))*math.exp(-(E-re)**2/(4*re*k_B*300) )
-    return temp
-
-tick_font_size = 10
-
-def scatter_hist(x, y, ax, ax_histx, ax_histy):
-    # no labels
-    ax.set_facecolor('white')
-    ax_histx.set_facecolor('white')
-    ax_histy.set_facecolor('white')
-
-    ax_histx.tick_params(axis="x", labelbottom=False,labelsize=tick_font_size)
-    ax_histx.tick_params(axis="y", labelleft=False,labelsize=tick_font_size)
-
-    ax_histy.tick_params(axis="y", labelleft=False,labelsize = tick_font_size)
-    ax_histy.tick_params(axis="x", labelbottom=False,labelsize = tick_font_size)
-    # plt.style.use('_mpl-gallery-nogrid')
-    # ax.hist2d(x, y,bins=50,norm=mpl.colors.LogNorm())
-    # fig.colorbar(ax.hist2d(x, y,bins=50,norm=mpl.colors.LogNorm())[3],location='left')
-    nbins = 30
-    # now determine nice limits by hand:
-    xmin = -2.0
-    xmax = -0.2
-    ax_histx.hist(x,bins=nbins, range=(xmin,xmax),color = "blue")
-    
-    ymin = -2.0
-    ymax = -0.2
-    width = 0.1
-    ax_histy.hist(y,bins=nbins, range=(ymin,ymax), orientation='horizontal',color = "blue")
-
[…]

### 2024-11-06 figs/plot_scatterEs.py

@@ -1,141 +1,0 @@
-from scipy.stats import wasserstein_distance
-from scipy.stats import entropy
-import scipy.stats as stats
-
-import numpy as np
-import scipy as sp
-import matplotlib.pyplot as plt
-import math
-import matplotlib.gridspec as gridspec
-import matplotlib as mpl
-
-k_B = 8.617333 * 10**(-5) # ev/K
-pi = math.pi
-hbar = 6.582119569 * 1e-16 # eV*s
-T = 300
-
-def Marcus(E,J,re):
-    temp = 2*pi/hbar * J**2/math.sqrt(4*pi*(re*k_B*300))*math.exp(-(E-re)**2/(4*re*k_B*300) )
-    return temp
-
-tick_font_size = 10
-
-def scatter_hist(x, y, ax, ax_histx, ax_histy):
-    # no labels
-    ax.set_facecolor('white')
-    ax_histx.set_facecolor('white')
-    ax_histy.set_facecolor('white')
-
-    ax_histx.tick_params(axis="x", labelbottom=False,labelsize=tick_font_size)
-    ax_histx.tick_params(axis="y", labelleft=False,labelsize=tick_font_size)
-
-    ax_histy.tick_params(axis="y", labelleft=False,labelsize = tick_font_size)
-    ax_histy.tick_params(axis="x", labelbottom=False,labelsize = tick_font_size)
-    # plt.style.use('_mpl-gallery-nogrid')
-    # ax.hist2d(x, y,bins=50,norm=mpl.colors.LogNorm())
-    # fig.colorbar(ax.hist2d(x, y,bins=50,norm=mpl.colors.LogNorm())[3],location='left')
-    nbins = 30
-    # now determine nice limits by hand:
-    xmin = -1.6
-    xmax = 1.1
-    ax_histx.hist(x,bins=nbins, range=(xmin,xmax),color = "blue")
-    
-    ymin = -1.6
-    ymax = 1.1
-    width = 0.1
-    ax_histy.hist(y,bins=nbins, range=(ymin,ymax), orientation='horizontal',color = "blue")
-
[…]

### 2024-11-06 figs/plot_scatterJ.py

@@ -1,129 +1,0 @@
-from scipy.stats import wasserstein_distance
-from scipy.stats import entropy
-import scipy.stats as stats
-
-import numpy as np
-import scipy as sp
-import matplotlib.pyplot as plt
-import math
-import matplotlib.gridspec as gridspec
-import matplotlib as mpl
-
-k_B = 8.617333 * 10**(-5) # ev/K
-pi = math.pi
-hbar = 6.582119569 * 1e-16 # eV*s
-T = 300
-
-def Marcus(E,J,re):
-    temp = 2*pi/hbar * J**2/math.sqrt(4*pi*(re*k_B*300))*math.exp(-(E-re)**2/(4*re*k_B*300) )
-    return temp
-
-tick_font_size = 10
-
-def scatter_hist2(x, y, ax, ax_histx, ax_histy):
-    # no labels
-    ax.set_facecolor('white')
-    ax_histx.set_facecolor('white')
-    ax_histy.set_facecolor('white')
-
-    ax_histx.tick_params(axis="x", labelbottom=False,labelsize=tick_font_size)
-    ax_histx.tick_params(axis="y", labelleft=False,labelsize=tick_font_size)
-
-    ax_histy.tick_params(axis="y", labelleft=False,labelsize = tick_font_size)
-    ax_histy.tick_params(axis="x", labelbottom=False,labelsize = tick_font_size)
-    # plt.style.use('_mpl-gallery-nogrid')
-    # ax.hist2d(x, y,bins=50,norm=mpl.colors.LogNorm())
-    # fig.colorbar(ax.hist2d(x, y,bins=50,norm=mpl.colors.LogNorm())[3],location='left')
-    nbins = 30
-    # now determine nice limits by hand:
-    xmin = -17
-    xmax = 0
-    ax_histx.hist(x,bins=nbins, range=(xmin,xmax),color = "blue")
-    
-    ymin = -17
-    ymax = 0
-    width = 5
-    ax_histy.hist(y,bins=nbins, range=(ymin,ymax), orientation='horizontal',color = "blue")
-
-    plt.style.use('ggplot')
-    plt.grid(False)
[…]

### 2024-11-06 paper.tex
update

@@
 The accuracy of DFT depends heavily on the choice of the exchange-correlation functional whose accuracy is usually unknown for new synthesized molecules. 
-As an advancement to improve accuracy, Hybrid-DFT incorporates a portion of exact HF exchange functional (HFX) from Hartree-Fock (HF) theory into the exchange-correlation functional, particularly for systems where DFT falls short.
+As an advancement to improve accuracy, Hybrid-DFT incorporates a portion $\alpha$ of exact HF exchange functional (HFX) from Hartree-Fock (HF) theory into the exchange-correlation functional, particularly for systems where DFT falls short.
 For example, the PBE0 functional has a portion of 0.25 HF exchange functional.
@@
 Since DFT is used to calculate the molecular electronic structures, the unknown exchange-correlation functional will bring uncertainties to the multiscale model. 
-In particular, different hybrid-DFT functionals contain varying levels of Hartree Fock (HF) to represent the exchange-correlation potential. 
+In particular, different hybrid-DFT functionals contain varying levels of HFX to represent the exchange-correlation potential. 
 The effect of the uncertainty from the electronic structure level on the multiscale model is not yet explored in literatures. 
-The goal of this work is to quantify the uncertainty effect of the exchange-correlation functional on the charge dynamics in OSCs and to study the robustness of the multiscale model, with a particular focus on the uncertainty represented by different portional of HF exchange functional.
+The goal of this work is to quantify the uncertainty effect of the exchange-correlation functional on the charge dynamics in OSCs and to study the robustness of the multiscale model, with a particular focus on the uncertainty represented by different portional of HFX.
 
@@
 \subsection{Molecule Dynamics Simulation}
+\begin{comment}
     The MD in the multiscale model is to use Newton's second law to update the atomic coordinate. Written in Hamilton equation, the equation of motion reads:
@@
 The procedure of the MD simulation in this work is as followed:...
+\end{comment}
 
@@
 
+\subsection{Transition Rate Calculation}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\section{Time-of-flight Calculation}
+\subsection{Time-of-flight and Steady State Velocity Calculation}
 The multiscale model defines a graph $\mathbf{G}$ with an adjacency matrix $\mathbf{W}$, where the nodes represent molecules and the edge weights $\omega_{ij}$ represent the Marcus rate from molecule $i$ to molecule $j$.
@@
 \begin{equation}
-    v_\text{SS} = \sum_i \pi_i \sum_j \omega_{ij} || \vec{r}_{ij}||_2 = \mathbb{E}f(M_{\infty})
+    v_\text{SS} = \sum_i \pi_i \sum_j \omega_{ij} || \vec{r}_{ij}||_2
 \end{equation} 
@@
 
-In this study, we investigate the hole-transporting organic semiconductor MADN (2-Methyl-9,10-di(naphth-2-yl)anthracene).
+In this study, we investigate the hole-transporting organic semiconductor MADN (2-Methyl-9,10-di(naphth-2-yl)anthracene) and study its charge mobility's dependence on HFX.
 
 Atomic charges and molecule polarizability $P_\text{iso}$ are crucial for evaluating molecular energy contributions from electrostatic and polarization effects.
-A physical property related to the overall atomic charges dipole moment at charge neutral state.
+A physical property related to the overall atomic charges is dipole moment at charge neutral state.
 To demonstration the effect of HFX on the atomic charges and molecule polarizability $P_\text{iso}$,
-Figure \ref{fig:autogen_MADN} illustrates the dependence of the dipole moment $\mu$, isotropic polarizability $P_\text{iso}$, reorganization energy $\lambda$, and energy disorder $\sigma(E)$ on the Hartree-Fock exchange (HFX) parameter.
+Figure \ref{fig:autogen_MADN}(a)(b) illustrates the dependence of the dipole moment $\mu$ and isotropic polarizability $P_\text{iso}$ on HFX.
+Figure \ref{fig:autogen_MADN}(c)(d) show 
+The reorganization energy $\lambda$ and energy disorder $\sigma(E)$ as a function of HFX parameter are also shown in Fig .\ref{fig:autogen_MADN}(c)(d).
 
@@
     \centering
-    \includegraphics[width=0.80\textwidth]{figs/MADN_HFX/fig_autogen.pdf}
+    \includegraphics[width=0.80\textwidth]{figs/fig_autogen.pdf}
     \caption{(a) The dipole moment of neutral state MAND molecule $\mu$, (b) isotropic polarizability $P_\text{iso}$, (c) reorganization energies $\lambda$ and (d) energy disorder $\sigma(E)$ as a function of the HFX parameters (denoted by $\alpha$).}
@@
 
-Figure \ref{fig:autogen_MADN}(a) shows a decrease in the dipole moment with increasing HFX, exhibiting a notable drop at HFX = 0.25.
-
-Figure \ref{fig:autogen_MADN}(b) demonstrates a linear decrease in isotropic polarizability for both neutral and charged MADN states as HFX increases from 0 to 0.25, indicating reduced molecular polarizability.
-
+From Fig.
+\ref{fig:autogen_MADN}(a) one can notice a mild decrease in the dipole moment with increasing HFX and in Fig.
+\ref{fig:autogen_MADN}(b) a linear decrease in isotropic polarizability for both neutral and charged MADN states as HFX increases from 0 to 0.25, indicating reduced molecular polarizability.
 Figure \ref{fig:autogen_MADN}(c) indicates an increase in reorganization energy $\lambda$ with higher HFX, reflecting greater energy requirements for electronic adjustments during charge transfer.
 This increase is nonlinear compared to the linear decrease in $P_\text{iso}$.
-
 Figure \ref{fig:autogen_MADN}(d) shows that the energy disorder $\sigma(E)$ for MADN are similar and close to \unit[0.08]{eV} under different HFX values.
 
-The ToF and corresponding diffusive velocity $v_\text{ToF}$ are presented in Table \ref{tab:ToF_MADN_HFX}.
-For boundary conditions, the \textit{Source} region contains molecules with X-coordinates $0 < r^x_i < 0.5$ nm, and the \textit{Sink} region contains molecules with X-coordinates $8.5 < r^x_i < 9$ nm.
-We also consider scenarios without energy disorder to model systems where all molecules have uniform energy.
+To calculate the ToF from the electronic structures, the \textit{Source} region contains molecules with X-coordinate $0 < r^x_i < 0.5$ nm, and the \textit{Sink} region contains molecules with X-coordinate $8.5 < r^x_i < 9$ nm.
+
+The ToF is also calculated without energy disorder, meaning $\Delta E_{ij}=0$ for all $i,j$.
+Table \ref{tab:ToF_MADN_HFX} shows the ToF and corresponding diffusive velocity $v_\text{ToF}$.
+With energy disorder, the ToF increases by a factor of approximately 15 as $\alpha$ increases from 0 to 0.25.  
+While without energy disorder, the increase factor is about 4. This increase in ToF is attributed to the rise in $\lambda$, changes in molecular energies, and variations in coupling elements.
 
@@
 
-Table \ref{tab:ToF_MADN_HFX} shows that as HFX increases from 0 to 0.25, the ToF with energy disorder increases by a factor of approximately 15, while without energy disorder, the increase factor is about 4.
-This increase in ToF is attributed to the rise in $\lambda$, changes in molecular energies, and variations in coupling elements.
+Figure \ref{fig:E_qmmm_MADN} presents a scatter plot comparing the site energies of MADN molecules across different HFX values, using $\alpha$ = 0.25 (PBE0 functional) as a reference.
+The energies consistently fall within the range of -0.5 to -1.1 eV, with data points clustering near the diagonal line, indicating similar molecular energies regardless of HFX variation.
+To quantify the similarity between two empirical distribution, Wasserstein distance is used.
+Denote the empirical distribution of molecular energy $E$ at $\alpha=0$ to be $P_{E(\alpha=0)}$. 
+The 1-Wasserstein distance between $P_{E(\alpha=0)}$ and $P_{E(\alpha=0.25)}$ is calculated as:
+\begin{equation}
+    W_1 (P_{E(\alpha=0)}, P_{E(\alpha=0.25)}) = (\frac{1}{N} \sum\limits_{i=1}^N | E_{i,\text{order}}(\alpha=0) - E_{i,\text{order}}(\alpha=0.25) |)
+\end{equation}
+where $E_{i,\text{order}}(\alpha=0)$ is the order statistics of $E_i(\alpha=0)$.
+The 1-Wasserstein distance between two empirical distributions for each plot in Fig.
+\ref{fig:E_qmmm_MADN} is shown in Table \ref{tab:W2_E}.
+$W_1 (P_{E(\alpha=0)}, P_{E(\alpha=0.25)})$ has range between 0.0045 to 0.0091, indicating that such molecule energy on average has difference less than 2\% since the energy has range from -0.5 to -1.1 eV.
 
-Figure \ref{fig:E_qmmm_MADN} presents a scatter plot comparing the site energies of MADN molecules across different HFX values, using HFX = 0.25 (PBE0 functional) as a reference.
-The energies consistently fall within the range of -0.5 to -1.1 eV, with data points clustering near the diagonal line, indicating similar molecular energies regardless of HFX variation.
+\begin{table}[H]
+    \centering
+    \begin{tabular}{c c c c c c}
+    \hline
+ $\alpha'$ & 0 & 0.05 & 0.10 & 0.15 & 0.20 \\
+    \hline
+ $W_1 (P_{E(\alpha')}, P_{E(\alpha=0.25)})$ &  0.0054 & 0.0091 & 0.0067 & 0.0053 & 0.0045 \\
+ $W_1 (P_{E^\text{el}(\alpha')}, P_{E^\text{el}(\alpha=0.25)})$ &  0.010 & 0.012 & 0.0089 & 0.0070 & 0.0032 \\
+ $W_1 (P_{E^\text{polar}(\alpha')}, P_{E^\text{polar}(\alpha=0.25)})$ &  0.0065 & 0.0043 & 0.0027 & 0.0023 & 0.0031 \\
+ $W_1 (P_{\log_{10}(J_{ij}^2)(\alpha')}, P_{\log_{10}(J_{ij}^2)(\alpha=0.25)})$ &  0.0054 & 0.0091 & 0.0067 & 0.0053 & 0.0045 \\
+    \hline
+    \end{tabular}
+    \caption{The 1-Wasserstein distance between the distributions pair of molecule energy $P_{E(\alpha)}$, electrostatic energy $P_{E^\text{el}(\alpha)}$, polar energy $P_{E^\text{polar}(\alpha)}$ and $P_{\log_{10}(J_{ij}^2)(\alpha)}$.
+}
+    \label{tab:W2_E}
+\end{table}
 
@@
     \centering
-    \includegraphics[width=0.95\textwidth]{figs/MADN_HFX/scatterE_qmmm.pdf}
+    \includegraphics[width=0.99\textwidth]{figs/scatterE_qmmm.pdf}
     \caption{Scatter plot of site energy of MADN molecules calculated from different HFX, compared to the site energy calculated from HFX=0.25 (The PBE0 functional).
@@
 
-Figures \ref{fig:Estat_qmmm_MADN} and \ref{fig:Edip_qmmm_MADN} show that both electrostatic and polarization energies remain consistent across HFX values from 0 to 0.25, further clustering near the diagonal.
+Figures \ref{fig:Estat_qmmm_MADN} and \ref{fig:Edip_qmmm_MADN} show that both electrostatic and polarization energies remain consistent close across HFX values from 0 to 0.25, since all the points comparing $E_i(\alpha')$ and $E_i(\alpha=0.25)$ in the scatter plot are close to the diagonal line.
+The 1-Wasserstein distance between the distribution of $E^\text{el}$ calculated by $\alpha'$ and that calculated by $\alpha=0.25$, $W_1(P_{E^\text{el}(\alpha')}, P_{E^\text{el}(\alpha=0.25)})$, is shown at Table \ref{tab:W2_E}.
+It shows that $W_1(P_{E^\text{el}(\alpha')}, P_{E^\text{el}(\alpha=0.25)})$ is at maximum 0.012.
+The 1-Wasserstein distance between the $E^\text{polar}$ distribution calculated by $\alpha'$ and that calculated by $\alpha=0.25$ is also shown in Table .\ref{tab:W2_E}, with a maximum of 0.006.
+So the small Wasserstein distances suggest that the using different $\alpha'$ other than $\alpha=0.25$, the data of $E, E^\text{el}, E^\text{polar}$ have not changed significantly.
 
@@
     \centering
-    \includegraphics[width=0.95\textwidth]{figs/MADN_HFX/scatterEstat_qmmm.pdf}
+    \includegraphics[width=0.99\textwidth]{figs/scatterEstat_qmmm.pdf}
     \caption{Scatter plot of MADN electrostatic energy calculated from different HFX, compared to the electrostatic energy calculated from HFX=0.25 (The PBE0 functional).
@@
     \centering
-    \includegraphics[width=0.95\textwidth]{figs/MADN_HFX/scatterEdip_qmmm.pdf}
+    \includegraphics[width=0.99\textwidth]{figs/scatterEdip_qmmm.pdf}
     \caption{Scatter plot of MADN polarization energy calculated from different HFX, compared to the polarization energy calculated from HFX=0.25 (The PBE0 functional).
@@
     \centering
-    \includegraphics[width=0.95\textwidth]{figs/MADN_HFX/scatterJ_all.pdf}
+    \includegraphics[width=0.95\textwidth]{figs/scatterJ_all.pdf}
     \caption{Scatter plot of MADN coupling element $\log_{10} J^2$ calculated from different HFX, compared to the polarization energy calculated from HFX=0.25 (The PBE0 functional).
@@
 The distribution of $\log_{10} J^2$ has a range of -14 to -2, and for all HFX values, the distribution has a peak at around -5. 
-For large values $\log_{10} J^2 < -5$ the coupling element remains consistent across HFX values from 0 to 0.25, while for large values $\log_{10} J^2 > -5$, the calculated coupling elements for a specific molecular pair can have large variation due to HFX values.
+For large values $\log_{10} J^2 < -5$ the coupling element calculated from $\alpha'=0, 0.05, 0.10, 0.15, 0.2$ remains consistently close to that calculated by $\alpha=0.25$.
+While for small values $\log_{10} J^2 > -5$, the $\alpha'$ calculated coupling elements for a specific molecular pair can have large variation compared to $\log_{10} J^2$ calculated using $\alpha=0.25$.
 
@@
     \centering
-    \includegraphics[width=0.75\textwidth]{figs/MADN_HFX/fig_network_all.pdf}
+    \includegraphics[width=0.75\textwidth]{figs/fig_network_all.pdf}
     \caption{The maximum size of the subgraphs obtained in the percolation algorithm as a function of critical value $J_c$.
@@
     \tau = g(x_1, x_2, \cdots, x_{N_d})
+    \label{eq:tau1}
 \end{equation}
@@
 To achieve this, each parameter can be modeled as a normal distribution with the mean and standard deviation obtained by the maximum likelihood estimation.
-For a normal distribution, they are the HFX sample mean and standard deviation, respectively.
+For a normal distribution, they are respectively the sample mean and standard deviation obtained by six varying HFXs.
 
@@
 \begin{enumerate}
-\item For all $i,j=1,2,\cdots, Nd$, obtain a realization $(x_1, x_2, \cdots, x_{N_d})$ where each parameter has the normal distribution, meaning: $\lambda_i \in \mathcal{N}(\bar{\lambda}_i, \sigma_{\lambda_i})$, $E_i \in \mathcal{N}(\bar{E}_i, \sigma_{E_i})$, $J_{ij} \in \mathcal{N}(\bar{J}_{ij}, \sigma_{J_{ij}})$.
+\item For all $i,j=1,2,\cdots, N_d$, obtain a realization $(x_1, x_2, \cdots, x_{N_d})$ where each parameter has the normal distribution, meaning the corresponding electronic parameters are sampled from the distribution $\lambda_i \in \mathcal{N}(\mathbb{E}(\lambda), \mathbb{V}(\lambda))$, $E_i \in \mathcal{N}(\mathbb{E}(E_i), \mathbb{V}(E_i))$, $\log_{10}(J_{ij}^2) \in \mathcal{N}(\mathbb{E}(\log_{10}(J_{ij}^2)), \mathbb{V}(\log_{10}(J_{ij}^2)))$.
 \item Calculate ToF using the sampled data set $(x_1, x_2, \cdots, x_{Nd})$. 
 \item Repeat step 1 and 2 for $N_\text{MC} = 50000$ times to obtain ToFs. Plot the distribution of the ToFs.
-\item Fit the distribution of $log_{10}(\text{ToF})$ to Gamma distribution.
+\item Estimate the 99\% confidence interval around the median.
 \end{enumerate}
 
-The distribution of ToF calculated as the CTMC where transition parameters are varied is unknown, so we attempt to fit the distribution of ToF to Gamma distribution. The reason is as followed.
+%From equation \ref{eq:hitting_time}, the ToF can be considered as the some combination of occupation time in the molecules, which is $log_{10}(\omega_{i}^{-1})$. 
+%When the parameters $E, J_{ij}, \lambda_{ij}$ are normally distributed random variables, the calculated ToF shows that variables $E,\lambda_{ij}$ has a larger influence than $J_{ij}$. 
+%The Marcus rate uses $E,\lambda_{ij}$ in the exponential form. If $\Delta E$ is normally distributed, then $log_{10}(\omega_{i}^{-1})$ is Gamma distributed. 
+%Since $E$ has greater influence to ToF than $\lambda_{ij}, J_{ij}$ and to be consistent, Gamma distribution is used to fit the Monte Carlo sampled ToF in all the investigated cases.
 
-From equation \ref{eq:hitting_time}, the ToF can be considered as the some combination of occupation time in the molecules, which is $log_{10}(\omega_{i}^{-1})$. 
-When the parameters $E, J_{ij}, \lambda_{ij}$ are normally distributed random variables, the calculated ToF shows that variables $E,\lambda_{ij}$ has a larger influence than $J_{ij}$. 
-The Marcus rate uses $E,\lambda_{ij}$ in the exponential form. If $\Delta E$ is normally distributed, then $log_{10}(\omega_{i}^{-1})$ is Gamma distributed. 
-Since $E$ has greater influence to ToF than $\lambda_{ij}, J_{ij}$ and to be consistent, Gamma distribution is used to fit the Monte Carlo sampled ToF in all the investigated cases.
-
+\begin{comment}
     Sampling the molecule energy as a normal distribution $E_i \sim \mathcal{N}(\bar{E}_i, \sigma_{E_i})$ will potentially destroy the energy correlation, especially for correlated systems, resulting a shift in the ToF calculation.
@@
     \centering
-    \includegraphics[width=\textwidth]{figs/MADN_HFX/ToFx_shuffle.pdf}
+    \includegraphics[width=\textwidth]{figs/ToFx_shuffle.pdf}
     \caption{Distribution of $\tau_{\text{sh}}$ calculated using shuffle energies.
@@
 This enables representing the parameter uncertainties in $\lambda, \{E_i\}, \{ J_{ij}\}$ by the normal distribution without shift the ToF.
+\end{comment}
 
-To understand how the uncertainty pass from $E, \lambda, J_{ij}$ to ToF, and 
+To understand how the uncertainty pass from $E, \lambda, J_{ij}$ to ToF, the parameter control is used.
+That is, a set of parameter, such as $E_i$ for all $i=1,2,\cdots,N$ is choose while keeping other parameter fixed, then performed Monte Carlo sampling to obtain ToF distribution and estimate upper and lower confidence bound.
+Then we use Sobol total indices to analyze and quantify 
 which uncertainty among $E, \lambda, J_{ij}$ has a greater impact on the ToF,
-firstly we study the following distribution of ToF:
+
+The distribution that we want to obtained during the parameter control are as followed:
 \begin{enumerate}
-    \item Fixed the $\lambda$ to be the averaged $\bar{\lambda}$, and $J_{ij}$ to be the averaged $\bar{J}_{ij}$.
-Then each molecule energy $E_i$ is sampled from the normal distribution $\mathcal{N}(\bar{E}_i, \sigma^2_{E_i})$.
+    \item Fixed the $\lambda$ to be $\mathbb{E}(\lambda)$, and $\log_{10}(J_{ij}^2)$ to be $\mathbb{E}(\log_{10}(J_{ij}^2))$.
+Then each molecule energy $E_i$ is sampled from the normal distribution $\mathcal{N}(\mathbb{E}(E_i), \mathbb{V}(E_i))$.
 Finally obtain and plot the histogram $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|E_i \text{ uncertain})$.
-    \item Fixed all $E_i$ to be the average $\bar{E}_i$ and all $J_{ij}$ to be the averaged $\bar{J}_{ij}$.
-Then $\lambda$ is sampled from the normal distribution $\mathcal{N}(\bar{\lambda}, \sigma^2_{\lambda})$.
+    \item Fixed all $E_i$ to be $\mathbb{E}(E_i)$ and all $\log_{10}(J_{ij}^2)$ to be $\mathbb{E}(\log_{10}(J_{ij}^2))$.
+Then $\lambda$ is sampled from the normal distribution $\mathcal{N}(\mathbb{E}(\lambda), \mathbb{V}(\lambda))$.
 Finally obtain and plot the histogram  $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|\lambda \text{ uncertain})$.
-    \item Fixed the $E_i$ to be the average $\bar{E}_i$ and $\lambda$ to be the averaged $\bar{\lambda}$.
-Then $J_{ij}$ is sampled from the normal distribution $\mathcal{N}(\bar{J}_{ij}, \sigma^2_{J_{ij}})$.
+    \item Fixed the $\lambda$ to be $\mathbb{E}(\lambda)$ and all $E_i$ to be $\mathbb{E}(E_i)$.
+Then $J_{ij}$ is sampled from the normal distribution $\log_{10}(J_{ij}^2) \in \mathcal{N}(\mathbb{E}(\log_{10}(J_{ij}^2)), \mathbb{V}(\log_{10}(J_{ij}^2)))$.
 Finally obtain and plot the histogram  $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$.
-    \item Both $E_i$, $\lambda$ and $J_{ij}$ are sampled from their normal distribution: $\mathcal{N}(\bar{E}_i, \sigma^2_{E_i})$, $\mathcal{N}(\bar{\lambda}, \sigma^2_{\lambda})$ and $\mathcal{N}(\bar{J}_{ij}, \sigma^2_{J_{ij}})$.
-Then obtain and plot the histogram $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$.
+    \item Both $E_i$, $\lambda$ and $J_{ij}$ are sampled from their normal distribution:$\lambda_i \in \mathcal{N}(\mathbb{E}(\lambda), \mathbb{V}(\lambda))$, $E_i \in \mathcal{N}(\mathbb{E}(E), \mathbb{V}(E))$, $\log_{10}J_{ij}^2 \in \mathcal{N}(\mathbb{E}(\log_{10}J_{ij}^2), \mathbb{V}(\log_{10}J_{ij}^2))$.
+Then obtain and plot the histogram $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as the following distribution:
+    $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$.
 \end{enumerate}
 
-The ToF distribution and Gamma fitted results for the MADN systems with energy disorder is shown in Fig.\ref{fig:mle_MADN_withE}.
+The ToF distribution for the MADN systems with energy disorder is shown in Fig.\ref{fig:mle_MADN_withE}.
+The lower and upper bounds in Fig.
+\ref{fig:mle_MADN_withE} shows that when only the energies $E_i$ are uncertain, the $\log_{10}(\tau)$ has lower -8.0 and upper bound -6.5.
+This lower and upper bound is close to that of $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$, meaning that varying the energy alone generates a $\tau$ distribution close to that when $E_i, \lambda, J_{ij}$ are uncertain.
+
+Figure .\ref{fig:mle_MADN_withE}(b) shows that $\log_{10}(\tau)$ has a confidence interval of -8.0 to -7.4 when $\lambda$ is varied. 
+Figure \ref{fig:mle_MADN_withE}(c) show that when $J_{ij}$ is uncertain $\log_{10}(\tau)$ has a sharp confidence interval of -7.9 to -7.7, suggesting that the variation in $J_{ij}$ leads to relatively small change in $\log_{10}(\tau)$ compared to $E_i$ and $\lambda$.
 %
@@
     \centering
-    \includegraphics[width=0.75\textwidth]{figs/MADN_HFX/fig_mle_MADN_withE.pdf}
-    \caption{Distribution of ToFs in the multiscale modeled MADN system using PBE0 functional and varying HFX.
+    \includegraphics[width=0.70\textwidth]{figs/fig_mle_MADN_withE.pdf}
+    \caption{Distribution of ToFs in the multiscale modeled MADN system.
     Monte Carlo sampling with a sample size $N_\text{MC}=50000$ is used to obtain the sampled distribution.
+The red vertical lines indicate the lower bound and upper bound of the 99\% confidence interval around the median.
+    The black circles indicate the ToF obtained using varying HFX values.
     (a) $P(\log_{10}(\tau)|E_i \text{ uncertain})$, 
@@
     (c) $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$, 
-    (d) $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$.
-The red star indicates the ToF calculated using the average $\bar{E_i}, \bar{J}_{ij}, \bar{\lambda}$, and the red circles indicate the ToF obtained using different HFX.}
+    (d) $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$. }
     \label{fig:mle_MADN_withE}
@@
 % The 90\% confidence interval of each distribution and the fitted Gamma distribution is summarized in table 
+When the energy disorder in MADN system is not considered, that is, all the MADN molecule energy are set to be equal giving $\Delta E=0$, the distribution of ToF is shown in Fig.\ref{fig:mle_MADN_noE}
 
-When the energy disorder in MADN system is not considered, that is, all the MADN molecule energy are set to be equal giving $\Delta E=0$, the distribution of ToF is shown in Fig.\ref{fig:mle_MADN_noE}
+Measuring the sensitivity of each electronic parameter to ToF is to measure each electronic parameter's contribution to the variance of ToF. 
+That is, if ToF is most sensitive to one parameter, the variance in this particular parameter will contribute most to the ToF variance.
+
 %
@@
     \centering
-    \includegraphics[width=0.99\textwidth]{figs/MADN_HFX/fig_mle_MADN_noE.pdf}
-    \caption{Distribution of ToFs in the multiscale modeled MADN system using PBE0 functional and varying HFX.
+    \includegraphics[width=0.99\textwidth]{figs/fig_mle_MADN_noE.pdf}
+    \caption{Distribution of ToFs in the multiscale modeled MADN system.
+    Monte Carlo sampling with a sample size $N_\text{MC}=50000$ is used to obtain the sampled distribution.
+The red vertical lines indicate the lower bound and upper bound of the 99\% confidence interval around the median.
     Energy disorder is not consider. 
-Monte Carlo sampling with a sample size $N_\text{MC}=50000$ is used to obtain the sampled distribution.
+    The black circles indicate the ToF obtained using varying HFX values.
     (a) $P(\log_{10}(\tau)|\lambda \text{ uncertain})$, 
     (b) $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$, 
-    (c) $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$.
-The red star indicates the ToF calculated using the average $\bar{E_i}, \bar{J}_{ij}, \bar{\lambda}$, and the red circles indicate the ToF obtained using different HFX.}
+    (c) $P(\log_{10}(\tau)|\lambda, J_{ij} \text{ uncertain})$. }
     \label{fig:mle_MADN_noE}
@@
 
-Measuring the sensitivity of each electronic parameter to ToF is to measure each electronic parameter's contribution to the variance of ToF. 
-That is, if ToF is most sensitive to one parameter, the variance in this particular parameter will contribute most to the ToF variance.
-
 One way of decomposing the variance of the model output into fractions attributed to input parameters is the variance-based sensitivity analysis.
@@
 While the global sensitivity analysis can use Sobol's indices.
-Specifically, to measure the parameter $x_i$'s contribution to $\tau$, including all variance caused by its interaction with other parameters $\{x_k, k \neq i \}$, the total effect Sobol's index is calculated as
+Given a model of Equation \ref{eq:tau1}, to measure the parameter $x_i$'s contribution to $\tau$ including all variance caused by its interaction with other parameters $\{x_k, k \neq i \}$, the total effect Sobol's index is calculated as \cite{saltelli_variance_2010}:
 \begin{equation}
-    S_{T,i} = \frac{ \mathbb{E}_{x_{\sim i}}[ \text{Var}_{x_i}(\tau|x_{\sim i}) ] }{ \text{Var}(\tau) }
+    S_{T,i} = \frac{ \mathbb{E}_{\mathbf{x}_{\sim i}}[ \mathbb{V}_{x_i}(\tau|\mathbf{x}_{\sim i}) ] }{ \mathbb{V}(\tau) }
     \label{eq:STi}
 \end{equation}
+The details of the notation is as followed: the vector $\mathbf{x}=(x_1, x_2, \cdots, x_{N_d})$, and $\mathbf{x}_{\sim i}$ denotes the vector of all entries but $x_i$. 
+$\mathbb{V}_{x_i}(\tau|\mathbf{x}_{\sim i})$ means the variance of $\tau$ given a set of $\mathbf{x}_{\sim i}$ taken over $x_i$.
+And $ \mathbb{E}_{\mathbf{x}_{\sim i}}[\cdot]$ denotes the mean of argument $(\cdot)$ taken over all factors but $x_i$.
+
 Then the $\lambda$ contribution to the total variance is $S_{T,i=1}$.
-The energy contribution to the total variance is $S_{T,E} = \sum\limits_{i=1}^{N+1} S_{T,i}$ where $N=1000$ is the number of energy parameter, and the coupling element contribution to the total variance is $S_{T,J}=\sum\limits_{i=N+2}^{N_d} S_{T,i}$.
+The energy contribution to the total variance is $S_{T,E} = \sum\limits_{i=1}^{N+1} S_{T,i}$ where $N=1000$ is the number of energy parameter, and the coupling element contribution due to variation in $\log_{10}(J_{ij}^2)$ to the total variance is $S_{T,J}=\sum\limits_{i=N+2}^{N_d} S_{T,i}$.
 Using the quasi Monte Carlo method\cite{sobol_global_2001} with a sample size $N_\text{QMC}=1000$ to calculate $S_{T,i}$, the results are shown in the table \ref{tab:Sobol}.
 %
+%\begin{table}[H]
+%    \centering
+%    \begin{tabular}{c c c c }
+%        \toprule
+%        parameter & $\lambda$ & $E$ & $\log_{10} J^2$   \\
+%        \midrule
+%        $S_T$ & 0.097 & 0.95 & 0.018\\
+%        \bottomrule
+%    \end{tabular}
+%        \caption{Sobol indices of $\lambda$, $E$ and $\log_{10} J^2$.}
+%        \label{tab:Sobol}
+%\end{table}
+%
+
 \begin{table}[H]
-    \centering
-    \begin{tabular}{c c c c }
-        \toprule
-        parameter & $\lambda$ & $E$ & $\log_{10} J^2$   \\
-        \midrule
-        $S_T$ & 0.097 & 0.95 & 0.018\\
-        \bottomrule
+    \caption{Sobol indices of $\lambda$, $E$ and $\log_{10} J^2$ when ToF is calculated with energy disorder, and Sobol indices of $\lambda$ and $\log_{10} J^2$ when ToF is calculated without energy disorder.}\label{tab:Sobol}
+    \begin{center}
+      \begin{tabular}{c c c c c c c} \hline
+        &  \multicolumn{3}{c}{\bf Energy Disorder} & &\multicolumn{2}{c}{\bf no Disorder}\\\cline{2-4}  \cline{6-7}
+        parameter  & $\lambda$ & $ E_i$ & $ \log_{10}(J_{ij}^2)$ && $\lambda$ & $ \log_{10}(J_{ij}^2)$ \\ \hline
+        %\multicolumn{6}{c}{\bf GRW for $\mathbf{N_c=1}$}\\
+     $S_T$  & 0.097 & 0.95 & 0.018 && 0.96 & 0.11 \\
+    \hline
       \end{tabular}
-        \caption{Sobol indices of $\lambda$, $E$ and $\log_{10} J^2$.}
-        \label{tab:Sobol}
+    \end{center}
 \end{table}
-%
-The table \ref{tab:Sobol} shows that most of the total variance can be attributed to the energy $E$.
-In contrast to $E$, the uncertainty in $\log_{10} J^2$ contributes much less compared to $E$, this is consistent to the Fig.\ref{fig:mle_MADN_withE}, where the distribution in Fig.\ref{fig:mle_MADN_withE}(d) resembles the distribution in Fig.\ref{fig:mle_MADN_withE}(a).
+
+From table \ref{tab:Sobol} one can see that most of the total variance can be attributed to the energy $E$.
+In contrast to $E$, the uncertainty in $\lambda$ and $\log_{10} J^2$ contributes much less compared to $E$, this is consistent to the Fig.\ref{fig:mle_MADN_withE}, where the distribution in Fig.\ref{fig:mle_MADN_withE}(d) resembles the distribution in Fig.\ref{fig:mle_MADN_withE}(a).
 And Fig.\ref{fig:mle_MADN_withE}(c) shows that the uncertainty in $\log_{10}(J^2)$ only leads to small variances.
+When there is no energy disorder, the variance in $\lambda$ has the most contribution to the total variance as shown in Table \ref{tab:Sobol}.
 
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{figs/MADN_HFX/fig_mle_MADN_withE_SS.pdf}
-    \caption{Distribution of steady state velocity $v_\text{SS}$ in the multiscale modeled MADN system using PBE0 functional.
+    \includegraphics[width=0.7\textwidth]{figs/fig_mle_MADN_withE_SS.pdf}
+    \caption{Distribution of steady state velocity $v_\text{SS}$ in the multiscale modeled MADN.
     Monte Carlo sampling with a sample size $N_\text{MC}=50000$ is used to obtain the sampled distribution.
-    (a) the molecule site energy $E$ are sampled from a normal distribution $E \sim N(E_\text{ave},E^2_\text{std})$, (b) the reorganization energy $\lambda$ are sampled from a normal distribution $\lambda \sim N(\lambda_\text{ave},\lambda^2_\text{std})$, (c) the quantity $\log_{10}(J^2)$ are sampled from a normal distribution $\log_{10}(J^2) \sim N(\mathbb{E}[\log_{10}(J^2)], \textbf{Var}[\log_{10}(J^2)] )$.
-(d) Both$E$, $\lambda$ and $\log_{10}(J^2)$ are sampled from the normal distribution.
-}
+    The red vertical lines indicate the lower bound and upper bound of the 99\% confidence interval around the median.
+    The black circles indicate the $v_\text{SS}$ obtained using varying HFX values.
+    (a) $P(\log_{10}(v_\text{SS})|E_i \text{ uncertain})$, 
+    (b) $P(\log_{10}(v_\text{SS})|\lambda \text{ uncertain})$, 
+    (c) $P(\log_{10}(v_\text{SS})|J_{ij} \text{ uncertain})$, 
+    (d) $P(\log_{10}(v_\text{SS})|E_i, \lambda, J_{ij} \text{ uncertain})$. }
     \label{fig:mle_MADN_withE_SS}
@@
     \centering
-    \includegraphics[width=0.99\textwidth]{figs/MADN_HFX/fig_mle_MADN_noE_SS.pdf}
-    \caption{Distribution of steady state velocity $v_\text{SS}$ in the multiscale modeled MADN system using PBE0 functional. All molecule energies are set to be zero.  
+    \includegraphics[width=0.90\textwidth]{figs/fig_mle_MADN_noE_SS.pdf}
+    \caption{Distribution of steady state velocity $v_\text{SS}$ in the multiscale modeled MADN. All molecule energies are set to be zero.  
     Monte Carlo sampling with a sample size $N_\text{MC}=50000$ is used to obtain the sampled distribution.
-    The plots are for the situation: (a) The reorganization energy $\lambda$ are sampled from a normal distribution $\lambda \sim N(\lambda_\text{ave},\lambda^2_\text{std})$.
-(b) the quantity $\log_{10}(J^2)$ are sampled from a normal distribution $\log_{10}(J^2) \sim N(\mathbb{E}[\log_{10}(J^2)], \textbf{Var}[\log_{10}(J^2)] )$.
-(c) Both $\lambda$ and $\log_{10}(J^2)$ are sampled from the normal distribution.
-}
+    The red vertical lines indicate the lower bound and upper bound of the 99\% confidence interval around the median.
+    The black circles indicate the $v_\text{SS}$ obtained using varying HFX values.
+    (a) $P(\log_{10}(v_\text{SS})|\lambda \text{ uncertain})$, 
+    (b) $P(\log_{10}(v_\text{SS})|J_{ij} \text{ uncertain})$, 
+    (c) $P(\log_{10}(v_\text{SS})|\lambda, J_{ij} \text{ uncertain})$.  }
     \label{fig:mle_MADN_noE_SS}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Comparison of Diffusive Charge Velocity Between BCP and MADN}
+\section{Charge mobility and PF Behavior}
+In this section, we want to study the dependence of drift mobility on the HFX. The charge mobility is calculated as:
+\begin{equation}
+    \mu = \frac{\vec{v} \vec{F} }{ |\vec{F}|^2}
+    \label{eq:mu}
+\end{equation}
+To consider the charge dynamics along X, Y and Z axis in the ToF setting, the ToF is calculated with different settings of \textit{Source}-\textit{Sink} and $\vec{F}$ combinations.
 
-In this section we compare the diffusive charge velocity between BCP and MADN.
+\begin{itemize}
+    \item Setting the molecules with $r^x < \min(r^x)+0.5$ as \textit{Source}, and the molecules with $r^x > \max(r^x)-0.5$ as \textit{Sink}, and $\vec{F}^T = (F,0,0)$, denote the calculated the ToF as $\tau_\text{Xmin}$, and the mobility is as $\mu_\text{Xmin} = \frac{L_x }{\tau_\text{Xmin} |\vec{F}|}$.
+    \item Setting the molecules with $r^x > \max(r^x)-0.5$ as \textit{Source}, and the molecules with $r^x < \min(r^x)+0.5$ as \textit{Sink}, and $\vec{F}^T = (-F,0,0)$, denote the calculated the ToF as $\tau_\text{Xmax}$, and the mobility is as $\mu_\text{Xmax} = \frac{L_x }{\tau_\text{Xmax} |\vec{F}|}$.
+    \item Setting the molecules with $r^y < \min(r^y)+0.5$ as \textit{Source}, and the molecules with $r^y > \max(r^y)-0.5$ as \textit{Sink}, and $\vec{F}^T = (0,F,0)$, denote the calculated the ToF as $\tau_\text{Ymin}$, and the mobility is as $\mu_\text{Ymin} = \frac{L_y }{\tau_\text{Ymin} |\vec{F}|}$.
+    \item Setting the molecules with $r^y > \max(r^y)-0.5$ as \textit{Source}, and the molecules with $r^y > \max(r^y)-0.5$ as \textit{Sink}, and $\vec{F}^T = (0,-F,0)$, denote the calculated the ToF as $\tau_\text{Ymax}$, and the mobility is as $\mu_\text{Ymax} = \frac{L_y }{\tau_\text{Ymax} |\vec{F}|}$.
+    \item Setting the molecules with $r^z < \min(r^z)+0.5$ as \textit{Source}, and the molecules with $r^z > \max(r^z)-0.5$ as \textit{Sink}, and $\vec{F}^T = (0,0,F)$, denote the calculated the ToF as $\tau_\text{Zmin}$, and the mobility is as $\mu_\text{Zmin} = \frac{L_z }{\tau_\text{Zmin} |\vec{F}|}$.
+    \item Setting the molecules with $r^z > \max(r^z)-0.5$ as \textit{Source}, and the molecules with $r^z > \min(r^z)+0.5$ as \textit{Sink}, and $\vec{F}^T = (0,0,-F)$, denote the calculated the ToF as $\tau_\text{Zmax}$, and the mobility is as $\mu_\text{Zmax} = \frac{L_z }{\tau_\text{Zmax} |\vec{F}|}$.
+\end{itemize}
+Finally the ToF drift mobility is calculated as:
+\begin{equation}
+    \mu_\text{PF} = \frac{1}{6} (\mu_\text{Xmin}+\mu_\text{Xmax}+\mu_\text{Ymin}+\mu_\text{Ymax}+\mu_\text{Zmin}+\mu_\text{Zmax})
+\end{equation}
 
-The energy in BCP system is correlated, and making the energy uncorrelated by shuffling the molecule energy leads to a shift in ToF, as shown in Fig.\ref{fig:ToF_shuffle_BCP}
+When the $\lambda, E_i, J_{ij}$ are uncertain and sampled from the normal distribution, the distributions of charge mobility obtained from MC sample under specific electric field are shown in Fig.\ref{fig:fig_mle_withE_mu2_ave}.
 %
@@
     \centering
-    \includegraphics[width=\textwidth]{figs/BCP_HFX/ToFx_shuffle.pdf}
-    \caption{Distribution of $\tau_{\text{sh}}$ in BCP calculated using shuffle energies.
-Each distribution are a sample of 10000 $\tau_{\text{shuffle}}$.
-The position of the solid circle indicates the ToF calculated from the specific $\alpha$ value, and the position of the solid square indicates the average $\tau_{\text{shuffle}}$ over the 10000 samples.}
-    \label{fig:ToF_shuffle_BCP}
+    \includegraphics[width=1.05\textwidth]{figs/fig_mle_withE_mu2_ave.pdf}
+    \caption{Distribution of $\mu_\text{PF}$ in the multiscale modeled MADN system.
+    Monte Carlo sampling with a sample size $N_\text{MC}=10000$ is used to obtain the sampled distribution.
+The red vertical lines indicate the lower bound and upper bound of the 99\% confidence interval around the median.}
+    \label{fig:fig_mle_withE_mu2_ave}
 \end{figure}
 %
-This figure shows that the ToF $\tau$ obtained with the specific HFX is always larger than the $\tau_\text{sh}$.
-So there is a shift in ToF when making the energies uncorrelated.
 
-The following tables show the diffusive charge velocity for BCP and MADN with HFX=0.05, 0.15, 0.25. The situations of using energy disorder and without energy disorder are considered.
-For the ToF setting, we investigate the situations where the charge transport direction is along the X-axis, Y-axis and Z-axis, as shown in Table \ref{tab:compare_Lx}, \ref{tab:compare_Ly}, and \ref{tab:compare_Lz}.
-
-The diffusive velocity calculated using steady state setting is $v_\text{SS}$, and the comparison is shown in Table \ref{tab:compare_SS}.
-\begin{table}[H]
+The ToF depends on the electric field through the Marcus rate. 
+Poole and Frenkel predicted the electric-field dependence of charge mobility as $\mu_\text{PF}(F)=\mu_0 \exp (\beta \sqrt{|\vec{F}|})$.
+So it is common to plot the mobility $\mu_\text{PF}$ against $\sqrt{|\vec{F}|}$ in a so-called Poole–Frenkel plot.
+which is shown in Fig. \ref{fig:PF_plot_ave} for specifie HFX values. The 99\% confidence interval obtained via MC sampled in shown in the green shadow. 
+%
+\begin{figure}[H]
     \centering
-\begin{tabular}{c c c c c c c}
-    \toprule
-     &
-        \multicolumn{3}{c}{ with energy $E$} &
-        \multicolumn{3}{c}{all $E=0$}  \\
-    HFX & MADN & BCP & ratio & MADN & BCP & ratio  \\
-    \cmidrule(r){1-7}
-    0.05 & $7.87 \times 10^{-9}$ & 0.32 & NA & $4.07 \times 10^{-10}$ & $3.00 \times 10^{-10}$ & NA \\
-    0.15 & $3.03 \times 10^{-8}$ & 0.38 & NA & $3.96 \times 10^{-10}$ & $4.67 \times 10^{-10}$ & NA \\
-    0.25 & $9.54 \times 10^{-8}$ & 0.026 & NA & $7.24 \times 10^{-10}$ & $7.63 \times 10^{-10}$ & NA \\
-    \bottomrule
-    \end{tabular}
-    \caption{Diffusive $\tau_X$ comparison between multiscale modeled BCP and MADN molecular system with PBE0 functional. The ratio does not apply because the BCP and MADN has different length $L_x$.}
-    \label{tab:compare}
-\end{table}
-
-\begin{table}[H]
-\centering
-\begin{tabular}{c c c c c c c}
-    \toprule
-        &
-        \multicolumn{3}{c}{ with energy $E$} &
-        \multicolumn{3}{c}{all $E=0$}  \\
-    HFX & MADN & BCP & ratio & MADN & BCP & ratio  \\
-    \cmidrule(r){1-7}
-    0.05 & 1.0 & $2.2 \times 10^{-8}$ & $4.5 \times 10^{7}$ & 19 & 24 & 0.80 \\
-    0.15 & 0.31 & $1.8 \times 10^{-8}$ & $1.7 \times 10^{7}$ & 25 & 15 & 1.7 \\
-    0.25 & 0.083 & $2.7 \times 10^{-7}$ & $3.1 \times 10^{5}$ & 11 & 9.4 & 1.2 \\
-    \bottomrule
-    \end{tabular}
-    \caption{Diffusive ToF velocity $v_\text{ToF,X}=\frac{L_X}{\tau_X}$ [m/s] comparison between multiscale modeled BCP and MADN molecular system with PBE0 functional. }
-    \label{tab:compare_Lx}
-\end{table}
-
-\begin{table}[H]
-\centering
-\begin{tabular}{c c c c c c c}
-    \toprule
-        &
-        \multicolumn{3}{c}{ with energy $E$} &
-        \multicolumn{3}{c}{all $E=0$}  \\
-    HFX & MADN & BCP & ratio & MADN & BCP & ratio  \\
-    \cmidrule(r){1-7}
-    0.05 & 0.44 & $5.8 \times 10^{-8}$ & $7.6 \times 10^{6}$ & 17 & 24 & 0.71 \\
-    0.15 & 0.057& $1.0 \times 10^{-7}$  & $5.7 \times 10^{5}$ & 17 & 15 & 1.1 \\
-    0.25 & 0.041 & $2.8 \times 10^{-7}$ & $1.4 \times 10^{5}$ & 10 & 9.5 & 1.0 \\
-    \bottomrule
-    \end{tabular}
-    \caption{Diffusive ToF velocity $v_\text{ToF,Y}=\frac{L_Y}{\tau_Y}$ [m/s] comparison between multiscale modeled BCP and MADN molecular system with PBE0 functional. }
-    \label{tab:compare_Ly}
-\end{table}
-
-\begin{table}[H]
-\centering
-\begin{tabular}{c c c c c c c}
-    \toprule
-        &
-        \multicolumn{3}{c}{ with energy $E$} &
-        \multicolumn{3}{c}{all $E=0$}  \\
-    HFX & MADN & BCP & ratio & MADN & BCP & ratio  \\
-    \cmidrule(r){1-7}
-    0.05 & 2.0 & $5.6 \times 10^{-7}$ & $3.4 \times 10^{6}$ & 19 & 24 & 0.80 \\
-    0.15 & 2.6 & $1.2 \times 10^{-6}$ & $2.2 \times 10^{6}$ & 19 & 15 & 1.3 \\
-    0.25 & 1.0 & $5.4 \times 10^{-6}$ & $1.0 \times 10^{6}$ & 10 & 9.4 & 1.1 \\
-    \bottomrule
-    \end{tabular}
-    \caption{Diffusive ToF velocity $v_\text{ToF,Z}=\frac{L_Z}{\tau_Z}$ [m/s] comparison between multiscale modeled BCP and MADN molecular system with PBE0 functional. }
-    \label{tab:compare_Lz}
-\end{table}
-
-\begin{table}[htbp]
-\centering
-\begin{tabular}{c c c c c c c}
-    \toprule
-        &
-        \multicolumn{3}{c}{ with energy $E$} &
-        \multicolumn{3}{c}{all $E=0$}  \\
-    HFX & MADN & BCP & ratio & MADN & BCP & ratio  \\
-    \cmidrule(r){1-7}
-    0.05 & 0.10 & $1.5 \times 10^{-7}$ & $6.7 \times 10^{5}$ & 3.8 & 2.4 & 1.6 \\
-    0.15 & 0.031 & $1.5 \times 10^{-8}$ & $2.1 \times 10^{6}$ & 13 & 0.58 & 22 \\
-    0.25 & 0.0043 & $3.6 \times 10^{-7}$ & $1.2 \times 10^{4}$ & 4.0 & 1.07 & 3.7 \\
-    \bottomrule
-    \end{tabular}
-    \caption{Steady state diffusive velocity $v_\text{SS}$ [m/s] comparison between multiscale modeled BCP and MADN molecular system with PBE0 functional. }
-    \label{tab:compare_SS}
-\end{table}
-
+    \includegraphics[width=0.8\textwidth]{figs/fig_PF_plot_ave.pdf}
+    \caption{Electric-field dependence of the mobility $\mu$ in the multiscale modeled MADN system.
+The dash lines are Poole–Frenkel plots obtained with specific HFX value, and the green shadow indicates the 99\% confidence interval estimated from the MC sampling with a sample size of $N_\text{MC}=10000$.}
+    \label{fig:PF_plot_ave}
+\end{figure}
+%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\begin{comment}
-\textbf{Point 1:} To investigate the effect of different functionals $f^\text{DFT}$ on electronic structures, we compare the energies $E_i$ and couplings $J_{ij}$ for all molecule indices $i,j$.
-Scatter plots in Figures \ref{fig:scatterE} and \ref{fig:scatterJ} illustrate these comparisons.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.95\textwidth]{figs/scatterE_all.pdf}
-    \caption{Energy heat maps: $X$-axis shows energies of BCP molecules obtained using PBE0, while the $Y$-axis shows energies from a different functional $f'$.}
-    \label{fig:scatterE}
-\end{figure}
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.95\textwidth]{figs/scatterJ_all.pdf}
-    \caption{Scatter heat maps of $\log_{10}(J^2)$: $X$-axis shows $\log_{10}(J^2)$ of BCP molecules obtained using PBE0, while the $Y$-axis shows $\log_{10}(J^2)$ from a different functional $f'$.}
-    \label{fig:scatterJ}
-\end{figure}
-
-\textbf{Point 2:} Both $E_i$ and $J_{ij}$ are distributions.
-To quantify the impact of these distributions on $\Delta$ToF, we plot the Wasserstein distance versus $\Delta$ToF.
-Figure \ref{fig:distance_ToF} shows that different functionals generate similar energy sets, but $\Delta$ToF is not correlated with energy distribution distance.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.9\textwidth]{figs/DeltaToF_W_KL_E.pdf}
-    \caption{Left: scatter plot of $W_1(P_f,P_{f'})$ vs. $\Delta$ToF. Right: scatter plot of $KL(P_f(E),P_{f'}(E))$ vs. $\Delta$ToF.}
-    \label{fig:distance_ToF}
-\end{figure}
-
-\textbf{Point 3:} We then examine other rate-related parameter distributions, calculating the Wasserstein distance and plotting against $\Delta$ToF.
-Figure \ref{fig:d_WD_tof} reveals that only the rate $P_f(\omega)$ has a large Wasserstein distance when varying $f^\text{DFT}$; other parameters show similar distributions.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.7\textwidth]{figs/DeltaToF_W_all.pdf}
-    \caption{Scatter plots of (a): $W_1(P_f(\Delta E),P_{f'}(\Delta E))$, (b): $W_1(P_f(\exp(\Delta E)),P_{f'}(\exp(\Delta E)))$, (c): $W_1(P_f(\exp \frac{-(\Delta E - \lambda)^2}{4 k_B T \lambda}),P_{f'}(\exp \frac{-(\Delta E - \lambda)^2}{4 k_B T \lambda}))$, and (d): $W_1 (P_f(\omega), P_{f'}(\omega) )$ vs.
-$\Delta$ToF.}
-    \label{fig:d_WD_tof}
-\end{figure}
-
-\textbf{Point4:} Although $f^\text{DFT}$ affects $P_f(\omega)$, but we further notice that $\Delta$ToF is not correlated to its Wasserstein distance. 
-So we hypothesize that the connectivity of the graph changed due to different $f^\text{DFT}$.
-The connectivity of the graph is quantified by the second eigenvector of the graph Laplacian, so we make the figure to investigate the correlation between the $\Delta$ToF and the graph connectivity.
-Figure .\ref{fig:d_eig_tof} shows the ratio of $f^\text{DFT}$ and the second eigenvalue ratio between the graph Laplacian.
-These two quantities look correlated, and we calculate the Spearman rank coefficient, which is shown in Table.\ref{tab:spearman}.
-
-\begin{table}[h]
-    \centering
-    \begin{tabular}{c c c}
-    \hline
-        Data Set & Spearman Rank Coefficient & $p$-value \\ 
-        \hline
-        $\frac{\lambda_{2,L_W}(f)}{\lambda_{2,L_W}(f')}$ vs $\frac{\text{ToF}(f)}{\text{ToF}(f')}$ & -0.57 & 4.6e-5 \\
-        $\frac{\lambda_{2,L_\text{rw}}(f)}{\lambda_{2,L_\text{rw}}(f')}$ vs $\frac{\text{ToF}(f)}{\text{ToF}(f')}$ & -0.38 & 9.4e-3 \\ 
-    \hline
-    \end{tabular}
-    \caption{Spearman rank coefficients for the relationship between $\frac{\lambda_2(f)}{\lambda_2(f')}$ and $\frac{\text{ToF}(f)}{\text{ToF}(f')}$}
-    \label{tab:spearman}
-\end{table}
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.6\textwidth]{figs/ratio_tof_2ndEigval.pdf}
-    \caption{Scatter plot of $\frac{\lambda_{2}(f)}{\lambda_{2}(f')}$ vs. $\frac{\text{ToF}(f)}{\text{ToF}(f')}$}
-    \label{fig:d_eig_tof}
-\end{figure}
-
-\textbf{Point5:} The eigenvalue comes in pair with the eigenvector, so we further investigated the corresponding second eigenvector element distributions, as shown in Fig.\ref{fig:2ndVecLW}. 
-To our surprise, node 66 has very different second eigenvector entries, so we performed K-means partitioning on those second eigenvector elements.
-
-\textbf{Point6:} After partitioning, we notice that the partition cost function is correlated to $\Delta$ToF.
-This correlation shows that the $\Delta$ToF correlated to the connectivity of the graph, althouth the electronic structures and rate-related parameters are similar.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\textwidth]{figs/fig_2ndVecLw.png}
-    \caption{Scatter plot of the eigen vector entries $\Vec{v}_i$ of $L_W$ for various $f$ indicated by the legend and point color. 
-    The numbers are node index. The dash rectangular indicates the 3-means clusters that are detected as clusters by the Kmeans Lloyd's algorithm. }
-    \label{fig:2ndVecLW}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\textwidth]{figs/fig_2ndVecRW.png}
-    \caption{Scatter plot of the eigen vector entries $\Vec{v}_i$ of $L_{rw}$ for various $f$ indicated by the legend and point color. 
-    The numbers are node index. The dash rectangular indicates the 3-means clusters that are detected as clusters by the Kmeans Lloyd's algorithm.  }
-    \label{fig:2ndVecRW}
-\end{figure}
-
-Figure \ref{fig:fig_Z_ToF} shows scatter plots of K-means clustering partition cost $Z_{2c}, Z_{3c}$ versus ToF.
-For the normal Laplacian $L_w$, $Z_{2c}$ is not correlated with the ToF, but $Z_{3c}$ is.
-For the Random-walk Laplacian, both $Z_{2c}$ and $Z_{3c}$ show a strong correlation with ToF.
-Thus, the clustering cost function indicates the speed of charge dynamics as measured by ToF.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.9\textwidth]{figs/fig_Z_ToF.pdf}
-    \caption{Scatter plot of $Z$ vs $\text{ToF}$.
-(a): K-means partition of the second eigenvector of $L_W$ for $K=2$ and $K=3$ (b) K-means partition of the second eigenvector of $L_{RW}$ for $K=2$ and $K=3$}
-    \label{fig:fig_Z_ToF}
-\end{figure}
-
-\textbf{Point7:} Now that the ToF has a large range, we want to know which ToF to trust.
-And for application purposes, a very important message is to know what the range of ToF will give a 90\% confidence level.
-
-Since we do not really know the exchange-correlation potential, we assume that for each molecule, the uncertainty in its energy $E_i$ is represented by a normal distribution $E_i \in N(\bar{E_i},\sigma(E_i))$.
-Normal distribution is used because the normal distribution encodes the maximum amount of uncertainty over the real numbers out of all possible probability distributions with the same variance.
-So the normal distribution inserts the least amount of prior knowledge into our model. 
-So we experiment:
-
-\textbf{Point8:} For each molecule energy $E_i$, we use maximum likelihood estimation to obtain the $N(\bar{E_i},\sigma(E_i))$.
-Then use sample a set of $E_i$ and calculate the ToF, with $\lambda,J_{ij}$ fixed at the average values.
-Repeat the $E_i$ sampling and ToF calculation for 100000 times, and plot ToF distribution. This process is called the Monte Carlo sampling.
-
-Similarly, for $\lambda,J_{ij}$, we perform the Monte Carlo sampling as been done for $E_i$. The resulting ToF is shown in Fig.\ref{fig:ToFs}.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.9\textwidth]{figs/fig_mle.png}
-    \caption{(a)The ToF distribution for 100000 samples where each $E_i$ is drawn from $N(\bar{E}_i,\sigma(E_i))$.
-The red curve is fitted to a gamma distribution.
-(b)The ToF distribution for 100000 samples where each $\lambda$ is drawn from $N(\bar{\lambda},\sigma(\lambda))$.(c)The ToF distribution for 100000 samples when each $J_{ij}$ is drawn from $N(\bar{J_{ij}},\sigma(J_{ij}))$.}
-    \label{fig:ToFs}
-\end{figure}
-
-This figure shows that ToF is more sensitive to change in $E_i$ and least sensitive to $J_{ij}$, even though from the scatter plots Fig.\ref{fig:scatterJ} the $J_{ij}$ has a very large magnitude deviation.
-
-The dataset of $\log_{10}(\text{ToF})$ can be well-fitted to a Gamma distribution. 
-The statistical calculation has results:
-\begin{itemize}
-    \item When $E_i \in N(\bar{E_i},\sigma(E_i))$, the $\log_{10}(\text{ToF})$ has mean -1.73 and a standard deviation of 0.73.
-    \item When $\lambda \in N(\bar{\lambda},\sigma(\lambda))$, the $\log_{10}(\text{ToF})$ has mean -1.91 and a standard deviation of 0.34.
-    \item When $J_{ij} \in N(\bar{J_{ij}},\sigma(J_{ij}))$, the $\log_{10}(\text{ToF})$ has mean -2.92 and a standard deviation of 0.08.
-\end{itemize}
-
-When we use $E_i \in N(\bar{E_i},\sigma(E_i))$, $\lambda \in N(\bar{\lambda},\sigma(\lambda))$, $J_{ij} \in N(\bar{J_{ij}},\sigma(J_{ij}))$ at the same to perform the Monte Carlo sampling of ToF calculation, the ToF is shown in Fig.\ref{fig:ToFs2}.
-the $\log_{10}(\text{ToF})$ has mean -2.72 and a standard deviation of 0.80.
-To obtain a 90\% confidence level, then $-3.93 < \log_{10}(\text{ToF}) < -1.30$.
-\begin{figure}
-    \centering
-    \includegraphics[width=0.6\textwidth]{figs/fig_mle2.png}
-    \caption{The ToF distribution for 100000 samples where each $E_i$ is drawn from $N(\bar{E}_i,\sigma(E_i))$, $\lambda$ is drawn from $N(\bar{\lambda},\sigma(\lambda))$, and each $J_{ij}$ is drawn from $N(\bar{J_{ij}},\sigma(J_{ij}))$.
-The red curve is fitted to a gamma distribution.}
-    \label{fig:ToFs2}
-\end{figure}
-
-\section{Uncertainty in ToF}
-Now we need to answer which ToF is accurate. 
-Using the multiscale model to determine the ToF is a function $f: \mathbb{R}^d \rightarrow \mathbb{R}^+$, which maps the parameter vector $$\vec{x} = [ E_1,E_2,\cdots,E_N, R_1,R_2,\cdots,R_N,J_1,J_2,\cdots,J_{N_\text{pair}} ]$$ to a real value $\tau \in \mathbb{R}^+$.
-
-Due to noise and approximation in the multiscale model, each element in $\vec{x}$ can be considered as an exact value plus an error term, for example $$E_1 = \hat{E}_1 + \epsilon_{E_1} $$
-There is no prior knowledge about this error terms. 
-Since the normal distribution inserts the least amount of prior knowledge into a model and encodes the maximum amount of uncertainty, we want to quantify the uncertainty when those error terms are normally distributed.
-\end{comment}
-
 \end{document}

### 2024-11-09 paper.tex
update introduction and some results

@@
 
-Theoretical model and computer simulation for understanding a physical system must contain some uncertainties in predicting the system features. 
-For example, the theoretical model does not encompass all relevant physical factors, the theoretical model incorporates empirical parameters that include noise, the numerical scheme contains approximation, etc.
+Theoretical model and computer simulation for understanding a physical system usually contain some uncertainties in predicting the system features. 
+For example, the theoretical model does not encompass all relevant physical factors, the theoretical model incorporates empirical parameters that include noise, the numerical scheme contains approximation, the simulation use noisy quantities, etc.
 Nevertheless, those uncertainties should not affect the validity of the model or the accuracy for the predicting system in terms of some quantities of interest (QoI). 
 Here the terminology "uncertainties" refers to the impossibility of getting a deterministic QoI, and excludes theoretical or numerical errors. 
+The amount of uncertainty in the QoI plays an important role in determining the usefulness of the model. 
+So quantifying the uncertainty is a key factor for telling if the model is quanlitatively or quantitatively accurate.
 
-In this work, an investigated model containing uncertainties is the first-principle multiscale model for charge dynamics in organic semiconductors (OSCs).
-From a broad perspective, this model contains uncertainties due to the limitation of the model, the randomness nature of the QoI, and the limitation of the numerical simulations.
+In this work, an investigated model containing uncertainties is the multiscale model of charge dynamics in organic semiconductors (OSCs), which are materials that consist of organic molecules with disordered and amorphous structure.
+Besides its semiconducting properties, tthey are mechanically flexible and comes with controllable charge transport properties.
+This flexible functionality is achieved by tuning molecular properties to achieve an ideal operating properties at the device-level, so a fundamental understanding of OSC from molecule scale  plays an important role in OSC optimization.
+Conducting these optimization processes through experimental methods is financially demanding.
+In contrast, computational approaches such as the multiscale model provides insightful guidance for such investigation.
+So robustness of the computational model is paramount to promote OSC optimization.
 
+Like every other models, the multiscale model contains uncertainties due to certain approximation in modeling perspective, the randomness nature of the physical quantities, and the limitation of the numerical simulations, only to name a few.
 To explain in detail those uncertainties, the first-principle multiscale model is briefly reviewed.
+
 Fundamentally, quantum-mechanical description is needed to model charge dynamics due to the motion of electrons.
-However, the resulting full many-electron schr\"{o}dinger equation is too complex to solve due to complexity, so Density Functional Theory (DFT) appears as a manageable way to model electrons.
+However, the resulting full many-electron schr\"{o}dinger equation is impossible to solve due to its complexity, so Density Functional Theory (DFT) appears as a manageable way to model electrons.
 DFT has its own challenges in achieving multiscale modeling.
-
 The first challenge relates to the Born-Oppenheimer approximation in quantum
@@
 The next challenge is the infeasibility of solving the DFT equations for the entire system even at a fixed time. 
-To address this challenge, state localization is used and the electron's wavefunction becomes localized in space around the nuclei.
-As a result, the charge dynamic is modeled as a continuous time random walk (CTRW) process, with transition rates between the molecules determined by their electronic structures, namely, the molecule energy, reorganization energy and coupling elements which will be explained in the methodology section.
+But due to fact that OSCs have disordered and amorphous structure and the quantum states of each molecule is confined to a limited region, the charge dynamic can be well-approxmiated as a jumping process between molecules, which is a continuous time random walk (CTRW) process.
+The transition rates between the molecules can be calculated from quantum chemical calculations and related to the electronic structures parameters including the molecule energy, reorganization energy and coupling elements which will be explained in the methodology section.
 
-In brief summary, the multiscale model can be summarized in Fig. \ref{fig:MSM} using MADN, a type of OSC as an example.
+Until this point, the molecular system is modeled as graph $\mathbf{G}(\mathbf{V}, \mathbf{W})$ where $\mathbf{V}$ is the set of nodes and $\mathbf{W}: \omega_{ij}$ is the adjacency matrix.
+Each node represents one molecule, the weighted and directed edge $\omega_{ij}$ represents the transition rates from node $i$ to node $j$ calculated from quantum chemical methods.
+As will be shown in the method section, $\omega_{ij}$ determines the QoIs whose quantities we want to quantify.
+
+Figure \ref{fig:MSM} summarized the multiscale model as mentioned above using MADN, a type of OSC as an example. 
 The process includes: Firstly, classical Molecular Dynamics is used to generate the atomistic coordinates of all molecules.
-Then DFT is used to attain electronic structures.
+Then DFT is used to obtain electronic structures.
 Finally the charge dynamic is model as a CTRW among the molecules.
@@
 
-In overcoming the challenges and achieving the multiscale model, uncertainties are introduced. 
-While Born-Oppenheimer approximation allows for the use of force field to approximate the potential energy surfaces (need citation) and model the atomic coordinates using Newton’s equations, the atomic coordinates are not exactly the same as that modeled by the many-electron schr\"{o}dinger equation.
+In achieving the multiscale model, uncertainties are introduced. 
+While Born-Oppenheimer approximation allows for the use of force field to approximate the potential energy surfaces (need citation) and model the atomic coordinates using Newton’s equations, the force field is not exactly the same as the potential for DFT.
 So the atomic coordinates, that is the molecule structures contain uncertainty which ultimately affects the charge dynamics. 
-This is one source of uncertainty that have not been investigated.
-But in our investigation, a fixed molecule structure is used and we do not consider this source of uncertainty. 
-Secondly, state localization is not exactly a time dependent DFT process. 
-But for amorphous OSCs used in this work, model noise from state localization is negligible and we do not consider the uncertainty brought by state localization.
-Lastly, the exact functional for the exchange-correlation energy is unknown so approximations like the Local Density Approximation (LDA) or the Generalized Gradient Approximation (GGA) are used, resulting in exchange-correlation functional in practice.
-The accuracy of DFT depends heavily on the choice of the exchange-correlation functional whose accuracy is usually unknown for new synthesized molecules. 
+This is one source of uncertainty that have not been investigated. But in our investigation, a fixed molecule structure is used and we do not consider this source of uncertainty. 
+Secondly, charge jumping between the state localization is not exactly a time dependent DFT process. 
+However, the amorphous OSCs used in this work has strong disorder, so the model noise from state localization is negligible and we do not consider the uncertainty originated from this perspective.
+Lastly, the source of uncertain that this work focus on comes from the approximation for the exchange-correlation energy in DFT. 
+There is no exact formula for the exchange-correlation functional, so in practical approximations are developed and tested to guarantee the robustness of DFT method. 
+The accuracy of DFT depends heavily on the choice of the exchange-correlation functional whose suitability is usually unknown for new synthesized molecules. 
 As an advancement to improve accuracy, Hybrid-DFT incorporates a portion $\alpha$ of exact HF exchange functional (HFX) from Hartree-Fock (HF) theory into the exchange-correlation functional, particularly for systems where DFT falls short.
-For example, the PBE0 functional has a portion of 0.25 HF exchange functional.
+For example, the PBE0 functional has a portion of 0.25 HFX.
 
-The charge dynamics is determined by CTRW transition rates, which depend on the electronic structures.
-Since DFT is used to calculate the molecular electronic structures, the unknown exchange-correlation functional will bring uncertainties to the multiscale model. 
-In particular, different hybrid-DFT functionals contain varying levels of HFX to represent the exchange-correlation potential. 
-The effect of the uncertainty from the electronic structure level on the multiscale model is not yet explored in literatures. 
+Looking back into the CTRW of the charge transport, the transition rates depend on the electronic structures parameters which rely on the validity of the exchange-correlation functional from the modeling perspectives.
+So the approximations in exchange-correlation functional will bring uncertainties to the multiscale model. 
+In particular, different hybrid-DFT functionals containing varying HFX levels will generate different output from the multiscale model mentioned aboved. 
+The effect of such uncertainty from the electronic structure level on the multiscale model is not yet explored in literatures. 
 The goal of this work is to quantify the uncertainty effect of the exchange-correlation functional on the charge dynamics in OSCs and to study the robustness of the multiscale model, with a particular focus on the uncertainty represented by different portional of HFX.
 
-To perform this goal of uncertainty quantification, a first step is to choose a QoI.
-A quantity commonly seen in OSC investigation is the charge mobility, which is the distance traveled by the charge carrier divided by the time period.
-The charge mobility is calculated in a \textit{time-of-flight} (ToF) setting. 
+A QoI need be chosen to perform this goal of uncertainty quantification. 
+The figure of merit in OSC investigation is the charge mobility, which quantitatively describe how fast charges move in an OSC. 
+The charge mobility is commonly measured in a \textit{time-of-flight} (ToF) setting. 
 As shown in Fig.\ref{fig:MSM}(d), charge carriers are injected into one electrode called \textit{Source} and they are collected by another electrode at the opposite end called \textit{Sink}. 
 Knowing the length of the sample $L$ and the time-of-flight $\tau$, the diffusive velocity is calculated as $v_\text{ToF}=\frac{L}{\tau}$.
-When electric field $\vec{F}$ is used to drift the charge transport, the charge mobility is calculated as $\mu_\text{ToF}=\frac{\vec{v}_\text{ToF} \vec{F}}{|\vec{F}|^2}$.
+When electric field $\vec{F}$ is used and the charge dynamics undergo a field-drifted transport, the charge mobility is calculated as $\mu_\text{ToF}=\frac{\vec{v}_\text{ToF} \vec{F}}{|\vec{F}|^2}$.
 
-Some literatures also report the charge mobility in a steady state setting, where no electrodes are used and the molecular system is infinitely repeated in all three dimensions by periodic boundary conditions.
-Over a long time period, the charge occupation on each molecule $\pi_i$ reach equilibrium.
-The steady state charge mobility $\mu_\text{SS}$ is calculated as the charge velocity along the direction of the electric field normalized by the steady state charge occupation $\vec{\pi}:\pi_i$. 
+Some literatures also report a steady state setting for investigation of charge mobility.
+In such condition, there is no \textit{Source}-\textit{Sink} boundary condition.
+Instead, the molecular system is infinitely repeated in all three dimensions by periodic boundary conditions.
+Over a long time period, the charge occupation on each molecule $\pi_i$ reach an equilibrium, allowing a steady state distribution to be obtained.
+The steady state charge velocity $v_\text{SS}$ is calculated as the charge velocity along the direction of the electric field normalized by the steady state charge occupation $\vec{\pi}:\pi_i$. 
 The calculation for $v_\text{ToF}$ and $\mu_\text{SS}$ will be detailed in the method section.
 
-To quantify the uncertainty for QoI, the focus of our work will be placed on the following questions: 
+To quantify the uncertainty for QoI, the focus of our work will be placed on answering the following questions: 
 \begin{enumerate}
@@
 
+The rest of the paper is organized as follows.
+Section 2 will outline the multiscale model in OSCs.
+This includes the electronic structure calculation centering on Kohn-Sham equation, the calucation of molecule energy, reorganization energy and coupling elements.
+The details of the molecule dynamics to obtain the MADN system will be listed.
+Then section 3 present the multiscale modeling results with the chose HFX values.
+In section 4, the Monte Carlo sampling method is utilized to estimate the ToF distribution and $v_\text{SS}$ distribution, followed by the sensitivity analysis on the parameters.
+Section 5 shows calculated Poole-Frankel behavior of the MADN with varying HFX values. The confidence interval of the Poole-Frankel plot is estimated. Section 6 concludes the paper. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Multiscale Model}
-The multiscale model results in the charge dynamics being modeled by CTRW.
+As mentioned in the introduction, the multiscale model maps a structural morphology into graph $\mathbf{G}(\mathbf{V}, \mathbf{W})$.
+In our context, the graph properties, that is the entries in $\mathbf{W}$, depends on the HFX values.
+
+{\Huge Here}
+
 When there is one charge carrier, each state in CTRW corresponds to the charge occupation in each molecule.
@@
 \subsection{Electronic Structure Calculations} 
-A first essential step in first-principle multiscale model is to determine the single-electronic wave function and the associated energy $\epsilon_l$, which are used to obtain atomic charges, reorganization energy, molecule energy, and coupling elements.
+Starting from an atomic morphology, a first step in first-principle multiscale model is to determine the single-electronic wave function and the associated energy $\epsilon_l$, which are used to obtain atomic charges, reorganization energy, molecule energy, and coupling elements.
 
@@
 A physical property related to the overall atomic charges is dipole moment at charge neutral state.
+
+%
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.75\textwidth]{figs/fig_autogen.pdf}
+    \caption{(a) The dipole moment of neutral state MAND molecule $\mu$, (b) isotropic polarizability $P_\text{iso}$, (c) reorganization energies $\lambda$ and (d) energy disorder $\sigma(E)$ as a function of the HFX parameters (denoted by $\alpha$).}
+    \label{fig:autogen_MADN}
+\end{figure}
+%
+
 To demonstration the effect of HFX on the atomic charges and molecule polarizability $P_\text{iso}$,
@@
 The reorganization energy $\lambda$ and energy disorder $\sigma(E)$ as a function of HFX parameter are also shown in Fig .\ref{fig:autogen_MADN}(c)(d).
-
-%
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.80\textwidth]{figs/fig_autogen.pdf}
-    \caption{(a) The dipole moment of neutral state MAND molecule $\mu$, (b) isotropic polarizability $P_\text{iso}$, (c) reorganization energies $\lambda$ and (d) energy disorder $\sigma(E)$ as a function of the HFX parameters (denoted by $\alpha$).}
-    \label{fig:autogen_MADN}
-\end{figure}
-%
 
@@
 
-The distribution of $\log_{10} J^2$ has a range of -14 to -2, and for all HFX values, the distribution has a peak at around -5. 
+The distribution of the majority $\log_{10} J^2$ has a range of -14 to -2 while only a few $\log_{10} J^2$ has low value below -15. For all HFX values, the distribution has a peak at around -5. 
 For large values $\log_{10} J^2 < -5$ the coupling element calculated from $\alpha'=0, 0.05, 0.10, 0.15, 0.2$ remains consistently close to that calculated by $\alpha=0.25$.

### 2024-11-09 paper.tex
update some methods

@@
 The details of the molecule dynamics to obtain the MADN system will be listed.
-Then section 3 present the multiscale modeling results with the chose HFX values.
+Then section 3 present the multiscale modeling results with the chosen HFX values.
 In section 4, the Monte Carlo sampling method is utilized to estimate the ToF distribution and $v_\text{SS}$ distribution, followed by the sensitivity analysis on the parameters.
@@
 \section{Multiscale Model}
-As mentioned in the introduction, the multiscale model maps a structural morphology into graph $\mathbf{G}(\mathbf{V}, \mathbf{W})$.
-In our context, the graph properties, that is the entries in $\mathbf{W}$, depends on the HFX values.
+As mentioned in the introduction, the multiscale model maps a structural morphology into a graph $\mathbf{G}(\mathbf{V}, \mathbf{W})$.
+In our context, the graph properties, that is the entries $\omega_{ij}$ in the adjacency matrix $\mathbf{W}$, only depends on the HFX values since other modeling parameters are kept consistent.
 
-{\Huge Here}
-
-When there is one charge carrier, each state in CTRW corresponds to the charge occupation in each molecule.
-The transition rates between the state, that is the rate for charge transfer rates between two molecules $i$ and $j$ is calculated as the Marcus rate:
+Those transition rates charge transfer rates from molecules $i$ to $j$ is calculated as the bi-molecular transition rates:
 %
@@
 The temperature $T$ (in \unit[]{K}), the charge of the carrier $q$ (in \unit[]{e}) and the external electric field $\vec{F}$ (in V/m) can be considered the external, environmental parameters of the simulation.
-The vector $\vec{r}_{ij} = (r^x_{ij},r^y_{ij},r^z_{ij})^\text{T}$ connects the center-of-masses (COMs) of molecules $i$ and $j$, which is calculated cyclic boundary conditions depending on the boundary condition.
+The vector $\vec{r}_{ij} = (r^x_{ij},r^y_{ij},r^z_{ij})^\text{T}$ connects the center-of-masses (COMs) of molecules $i$ and $j$, which is calculated using cyclic boundary conditions.
 The remaining physical, material-specific (or rather transfer-pair-specific) quantities are the reorganization energy $\lambda_{ij}$, the electronic coupling $J_{ij}$, and the energy difference $E_{ij} = E_i - E_j$ (all in \unit[]{eV}).
-With the information about the molecular COMs and the rates, one can construct the graph $\mathbf{G}=(\mathbf{V}, \mathbf{W})$ on which the CTRW takes place.
-$\mathbf{V}$ is a set of nodes (molecules) and $\mathbf{W}: \omega_{ij}$ is the adjacency matrix.
-A rate is only considered between molecules $i$ and $j$ if their closest-contact distance is smaller than $r_\text{cutoff}=\unit[0.5]{nm}$.
+In our model, two nodes $i,j$ form a connection of the corresponding molecules $i,j$ have their closest-contact distance smaller than $r_\text{cutoff}=\unit[0.5]{nm}$.
 
-In the section, the components of the multiscale model will be introduced: molecule dynamics, calculation of reorganization energy, molecule energy, coupling element, $v_\text{SS}$ and $v_\text{ToF}$.
+The rest of this section will introduce the following: the molecular dynamics used to obtain the coordinates $r^x_{i},r^y_{i},r^z_{i}$, the calculation of node-specific quantities $\lambda$, $E_i$ and $J_{ij}$, as well as the calculation of ToF $\tau$ and steady state velocity $v_\text{SS}$.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Molecule Dynamics Simulation}
+\subsection{Molecular Dynamics}
+The OSC morphology, that is the spacial coordinate of all the atoms, are generated by molecule dynamics.
+The GROMACS software package~\cite{berendsen_gromacs_1995} is utilized to implement atomistic molecular dynamics simulations of bulk amorphous MADN with the empirical force field obtained via Automated Topology Builder~\cite{stroet_automated_2018}.
+
+The MADN system starts with 1000 MADN molecules randomly placed in a cubic cell with a large enougth side length to allow a low density.
+Periodic boundary conditions are applied throughout in all three spatial directions.
+After energy minimization, the system is simulated for \unit[1]{ns} (?) in a $NpT$ ensemble, keeping a constant temperature of \unit[300]{K} and constant pressure of \unit[1]{bar} using the V-rescale thermostat~\cite{bussi_canonical_2007} with the coupling time constant \unit[0.1]{ps} and the Parrinello-Rahman barostat~\cite{parrinello_polymorphic_1981} with a time constant for pressure coupling \unit[2]{ps}.
+The equation of motion for updating the atomic coordinates is implemented by leap-frog algorithm~\cite{van_gunsteren_leap-frog_1988} with a time step of \unit[1]{fs}.
+
+Following this, simulated annealing is applied to relax the MADN.  
+The temperature is increased to \unit[800]{K}, well above the glass transition temperature during a period of \unit[0.5]{ns}. 
+This temperature is maintained for \unit[1]{ns} before cooling back down to \unit[300]{K} during a period of \unit[0.5]{ns}.
+Such heating-cooling cycle is repeated three times.
+After this simulated annealing, a production run is conducted for \unit[2]{ns} using the $NpT$ ensemble.
+The final configuration of MADN is chosen for the further steps in the multiscale model, whose configuration is a cubic box with a length of \unit[9.0]{nm} and a density of $\unit[1.08]{g/cm^3}$.
+
 \begin{comment}
@@
 \subsection{Electronic Structure Calculations} 
+\label{sec:es}
 Starting from an atomic morphology, a first step in first-principle multiscale model is to determine the single-electronic wave function and the associated energy $\epsilon_l$, which are used to obtain atomic charges, reorganization energy, molecule energy, and coupling elements.
@@
 where $T_s[\rho]$ is the kinetic energy, $E_\text{H}[\rho]$ and $E_\text{XC}[\rho]$ the Hartree and exchange-correlation energies, respectively.
-Equations \ref{eq:KS2} and \ref{eq:KS_model} can be solved for different total charge states $x=\text{n,c}$ and corresponding  equilibrium geometries $X=\text{N,C}$, where $\text{n}$ and $\text{N}$ stand for ''neutral'' and $\text{c}$ and $\text{C}$ for ''charged''.
-The respective total energies will be denoted in the following as $U^\text{xX}$.
 
@@
 \subsection{Transition Rate Calculation}
+Electronic structure calculation via Equation \ref{eq:KS2} and \ref{eq:KS_model} are performed for different combinations of molecular charge states $x=$ n,c and the corresponding equilibrium geometries $X=$ N,C.
+The notion n and N stand for "neutral", and the notion c and C stand for "charged".
+Following this, the total energy will be denoted as $U^\text{xX}$, dropping of the explicit functional dependency on the density $\rho$. 
+The reorganization energy $\lambda$ accounts for the energy change caused by the geometry variation during the charge transport, and is linked to the total energy via:
+%
+\begin{equation}
+    \lambda_{ij} = U_i^\text{nC} - U_i^\text{nN} + U_j^\text{cN} - U_j^\text{cC}
+    \label{eq:lambda}
+\end{equation}
+%
+In this work, the OSC only has one type of molecule, and $\lambda_{ij}$ of all molecular pairs are equal. So the subscript is left out and denoted as $\lambda$.
+
+The molecule energy $E_i = E_i^\text{c} - E_i^\text{n}$ is the difference between the total energies of the system in which molecule $i$ is carrying a charge or not, corresponding to the ionization potential in case of hole transport and the negative of the electron affinity in case of electron transport.
+
+These total energies in turn consist of different contributions associated with different physical mechanism, i.e.,
+%
+\begin{equation}
+E_i^x = U_i^{xX} + E_i^{x,\text{el}} + E_i^{x,\text{polar}},
+\label{eq:Es}
+\end{equation}
+%
+where $U_i^{xX}$ is the internal energy from single molecules as above.
+Both $E_i^{x,\text{el}}$ and $E_i^{x,\text{polar}}$ are contributions arising from intermolecular interactions: $E_i^{x,\text{el}}$ is the electrostatic energy due to the surrounding molecules and $E_i^{x,\text{polar}}$ is the polarization energy.
+These contributions are calculated with a microelectrostatic model using parametrized point charge representations\cite{https://doi.org/10.1002/jcc.540110311}
+
+In the multiscale model, $E_i^{x,\text{el}}$ is evaluated with a \unit[4]{nm} cutoff distance:
+\begin{equation}
+    E_i^{x,\text{el}} = \frac{1}{4 \pi \epsilon_0} \sum\limits_{a_i} \sum\limits_{b_k,k \neq i} \frac{(q^c_{a_i} - q^n_{b_i})q^n_{b_k}}{ r_{a_i b_k}} 
+\end{equation}
+where $\epsilon_0$ is the vacuum permittivity, $a_i, b_k$ denotes the atoms in molecule $i,k$, $q^{n(c)}_{a_i}$ are the partial charge of atom $a$ when molecule $i$ is in state x.
+And $r_{a_i b_k} = |r_{a_i} - r_{b_k}|$ is the distance between atoms $a_i$ and $b_k$, which should be within \unit[4]{nm} due to the cutoff setting.
+For the purpose of quantifying uncertainty in HFX, the long-range electrostatic interactions are not considered.
+
+The polarization effects are determined self-consistently to consider the response of the molecules to the associated fields~\cite{thole_molecular_1981}.
+Polarization effects are considered in a region of \unit[4.0]{nm} around each individual molecule.
+Practical calculations of the site energies are performed using the VOTCA software~\cite{Baumeier2011,doi:10.1021/acs.jctc.8b00617,10.1063/1.5144277,Baumeier2024}.
+
+The coupling element $J_{ij}$ between molecule $i$ and $j$ describe the coupling strength between two localized states.
+In the case of hole transport, the relevant orbitals are highest-occupied molecular orbital (HOMO) of the isolated molecules (monomers) $\phi^\text{HOMO}_i(\vec{r})$ and $\phi^\text{HOMO}_j(\vec{r})$,
+leading to the calculation of $J_{ij}$ is implemented using the Dimer-Projection Method~\cite{baumeier_density_2010}. Specifically, the coupling element is determined as:
+Specifically, the coupling element is determined as: 
+%
+\begin{equation}
+    J_{ij} = \frac{ J^0_{ij}- \frac{1}{2}(e_i+e_j) S_{ij} }{ 1- S_{ij}^2 }
+    \label{equ:JAB}
+\end{equation}
+%
+where $J^0_{ij} = \langle \phi^\text{HOMO}_i | \hat{H}^\text{KS}_\text{D} | \phi^\text{HOMO}_j \rangle $, $e_i = \langle \phi^\text{HOMO}_i | \hat{H}^\text{KS}_\text{D} | \phi^\text{HOMO}_i \rangle $, $e_j = \langle \phi^\text{HOMO}_j | \hat{H}^\text{KS}_\text{D} | \phi^\text{HOMO}_j \rangle $, and $S_{ij}=\langle \phi^\text{HOMO}_i | \phi^\text{HOMO}_j \rangle $ with bra-ket notation.
+and $H^\text{KS}_\text{D}$ is the Hamiltonian of the dimer (see Eq.~\ref{eq:KS2}). 
+As the Hamiltonian of the dimer is diagonal in its eigenbasis $\left\{ \phi_\text{D}(\vec{r})\right\}$ with eigenvalues $\left\{ \epsilon_D\right\}$, so $H^\text{KS}_\text{D} = \text{diag}(\epsilon_D)$, $J^0_{ij}$ can be calculated as $J^0_{ij} = \mathbf{p}_i^\text{T} \text{diag}(\epsilon_\text{D}) \mathbf{p}_j$,  where the vector $\mathbf{p}_i = \langle \phi_i^\text{HOMO} | \phi^\text{HOMO}_\text{D} \rangle$ and $\mathbf{p}_j = \langle \phi_j^\text{HOMO} | \phi_\text{D}^\text{HOMO} \rangle$ are the projections of the monomer orbitals $\phi_i^\text{HOMO}, \phi_j^\text{HOMO}$ onto the dimer orbitals $\phi^\text{HOMO}_\text{D}$.
+Similarly, $e_{i(j)} = \mathbf{p}_{i(j)}^\text{T} \mathbf{p}_{i(j)}$ and $S_{ij} =  \mathbf{p}_i^\text{T} \mathbf{p}_j$.
+All  of these operations are performed in the basis set representation of the Kohn--Sham wave functions (see Sec.~\ref{sec:es}) as implemented in VOTCA.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Time-of-flight and Steady State Velocity Calculation}
-The multiscale model defines a graph $\mathbf{G}$ with an adjacency matrix $\mathbf{W}$, where the nodes represent molecules and the edge weights $\omega_{ij}$ represent the Marcus rate from molecule $i$ to molecule $j$.
+Following the graph $\mathbf{G}$ from the multiscale model,
 The charge dynamics are modeled as a continuous-time random walk on this graph.
 In the time-of-flight (ToF) model, some vertices serve as \textit{Source} nodes, representing the electrode where charge carriers are injected, and some as \textit{Sink} nodes, where charge carriers are detected and the ToF is recorded.
-
 In CTRW the ToF is calculated as the expected hitting time of a continuous time Markov chain.
-
 For a system with $N$ molecules and one charge carriers, there are $N$ possible occupation states.
@@
 
-The transition rates between the states defines the adjacency matrix $\mathbf{W}:\omega_{ij}$.
+The transition rates between the states define the adjacency matrix $\mathbf{W}:\omega_{ij}$.
 According to such connectivity between the molecules, the transition rates $\mathbf{W}_{ij}$ from state $i$ to $j$ is:

### 2024-11-10 paper.tex
update results

@@
 
-Figure \ref{fig:E_qmmm_MADN} presents a scatter plot comparing the site energies of MADN molecules across different HFX values, using $\alpha$ = 0.25 (PBE0 functional) as a reference.
-The energies consistently fall within the range of -0.5 to -1.1 eV, with data points clustering near the diagonal line, indicating similar molecular energies regardless of HFX variation.
-To quantify the similarity between two empirical distribution, Wasserstein distance is used.
+Figure \ref{fig:E_qmmm_MADN} presents a scatter plot comparing the site energies of MADN molecules across different HFX values, using $\alpha$ = 0.25 (PBE0 functional) as a reference for which the calculated molecule energy has a range from -1.12 to -0.63 \unit[]{eV}.
+The range of molecule energy for the other five HFX are: from -1.17 to -0.60 \unit[]{eV} for $\alpha=0$, from -1.11 to -0.59 \unit[]{eV} for $\alpha=0.05$, from -1.07 to -0.63 \unit[]{eV} for $\alpha=0.10$, from -1.13 to -0.61 \unit[]{eV} for $\alpha=0.15$, and from -1.16 to -0.60 \unit[]{eV} for $\alpha=0.20$.
+
+The bright-yellow color in all plots of Fig.
+\ref{fig:E_qmmm_MADN} indicates that most data points are clustering near the diagonal line, so the molecular energies calculated by different HFX are very close.
+To quantify the similarity between two empirical distribution, Wasserstein distance~\cite{villani_optimal_2009} is used.
 Denote the empirical distribution of molecular energy $E$ at $\alpha=0$ to be $P_{E(\alpha=0)}$. 
@@
 \begin{equation}
-    W_1 (P_{E(\alpha=0)}, P_{E(\alpha=0.25)}) = (\frac{1}{N} \sum\limits_{i=1}^N | E_{i,\text{order}}(\alpha=0) - E_{i,\text{order}}(\alpha=0.25) |)
+    W_1 (P_{E(\alpha=0)}, P_{E(\alpha=0.25)}) = (\frac{1}{N} \sum\limits_{i=1}^N | E_{(i)}(\alpha=0) - E_{(i)}(\alpha=0.25) |)
 \end{equation}
-where $E_{i,\text{order}}(\alpha=0)$ is the order statistics of $E_i(\alpha=0)$.
+where $E_{(i)}(\alpha=0)$ is the order statistics of $E_i(\alpha=0)$.
 The 1-Wasserstein distance between two empirical distributions for each plot in Fig.
 \ref{fig:E_qmmm_MADN} is shown in Table \ref{tab:W2_E}.
-$W_1 (P_{E(\alpha=0)}, P_{E(\alpha=0.25)})$ has range between 0.0045 to 0.0091, indicating that such molecule energy on average has difference less than 2\% since the energy has range from -0.5 to -1.1 eV.
+$W_1 (P_{E(\alpha=0)}, P_{E(\alpha=0.25)})$ has range between 0.0045 to 0.0091, indicating that the molecular energy distributions are very similar.
 
@@
 
-Figures \ref{fig:Estat_qmmm_MADN} and \ref{fig:Edip_qmmm_MADN} show that both electrostatic and polarization energies remain consistent close across HFX values from 0 to 0.25, since all the points comparing $E_i(\alpha')$ and $E_i(\alpha=0.25)$ in the scatter plot are close to the diagonal line.
-The 1-Wasserstein distance between the distribution of $E^\text{el}$ calculated by $\alpha'$ and that calculated by $\alpha=0.25$, $W_1(P_{E^\text{el}(\alpha')}, P_{E^\text{el}(\alpha=0.25)})$, is shown at Table \ref{tab:W2_E}.
-It shows that $W_1(P_{E^\text{el}(\alpha')}, P_{E^\text{el}(\alpha=0.25)})$ is at maximum 0.012.
-The 1-Wasserstein distance between the $E^\text{polar}$ distribution calculated by $\alpha'$ and that calculated by $\alpha=0.25$ is also shown in Table .\ref{tab:W2_E}, with a maximum of 0.006.
-So the small Wasserstein distances suggest that the using different $\alpha'$ other than $\alpha=0.25$, the data of $E, E^\text{el}, E^\text{polar}$ have not changed significantly.
+To further estimate the energy variation due to HFX, one can look at the molecule that has maximum $|E_i(\alpha=0.25) - E_i(\alpha')|$ for all molecule index $i=1,2,\cdots,N$. 
+This quantity provides information of the amount of the largest variation one can expect in $E_i(\alpha)$. Index the molecule that has maximum $|E_i(\alpha=0.25) - E_i(\alpha')|$ to be $i'$. 
+If molecule $i'$ energy is the lowest one among the $N$ molecules, then a further lowering in the energy of molecule $i'$ may lead to large change in ToF, since low energy potentially lead to a trap in the charge transport dynamics.
+%
+\begin{table}[H]
+    \centering
+    \begin{tabular}{c c c c}
+    \hline
+ $\alpha'$ & $\max(|E_i(\alpha=0.25) - E_i(\alpha')|)$  & $E_{i'}(\alpha=0.25)$ & $E_{i'}(\alpha')$ \\
+    \hline
+ 0 & 0.13 &  -1.07 & -0.94 \\
+ 0.05 & 0.12 & -0.82 & -0.94 \\
+ 0.10 & 0.13 & -1.07 & -0.94 \\
+ 0.15 & 0.15 & -0.84 & -0.69 \\
+ 0.20 & 0.12 & -1.70 & -0.82 \\
+    \hline
+    \end{tabular}
+    \caption{ In the tested $\alpha'$ values, the second column shows the maximum of $E_i(\alpha=0.25) - E_i(\alpha')$ for all molecules.
+Denoting the index of the molecule which has maximum $E_i(\alpha=0.25) - E_i(\alpha')$ for the chosen $\alpha'$ case, the third column shows the energy of molecule $i'$ calculated by $\alpha=0.25$.
+The fourth column shows the molecule energy $E_{i'}(\alpha')$ calculated by $\alpha'$.
+All the energies are in unit \unit[]{eV}.}
+    \label{tab:maxEi}
+\end{table}
+%
+Table \ref{tab:maxEi} shows that depending on $\alpha'$, the maximum $|E_i(\alpha=0.25) - E_i(\alpha')|$ is 0.12 to 0.15, which is considerable small compared to the range of molecular energy. 
+The energy of molecule $i'$ shown in Table \ref{tab:maxEi} indicates that the $i'$ molecule energy is not the lowest one in the system.
+So the maximum energy variation quantified by $\max(|E_i(\alpha=0.25) - E_i(\alpha')|)$ is not likely to results in large change in ToF due to trapping effects.
 
@@
 \end{figure}
+
+Figures \ref{fig:Estat_qmmm_MADN} and \ref{fig:Edip_qmmm_MADN} show that both electrostatic and polarization energies remain consistent close across HFX values from 0 to 0.25, since all the points comparing $E_i(\alpha')$ and $E_i(\alpha=0.25)$ in the scatter plot are close to the diagonal line.
+The 1-Wasserstein distance between the distribution of $E^\text{el}$ calculated by $\alpha'$ and that calculated by $\alpha=0.25$, $W_1(P_{E^\text{el}(\alpha')}, P_{E^\text{el}(\alpha=0.25)})$, is shown at Table \ref{tab:W2_E}.
+It shows that $W_1(P_{E^\text{el}(\alpha')}, P_{E^\text{el}(\alpha=0.25)})$ is at maximum 0.012.
+The 1-Wasserstein distance between the $E^\text{polar}$ distribution calculated by $\alpha'$ and that calculated by $\alpha=0.25$ is also shown in Table .\ref{tab:W2_E}, with a maximum of 0.006.
+So the small Wasserstein distances suggest that the using different $\alpha'$ other than $\alpha=0.25$, the data of $E, E^\text{el}, E^\text{polar}$ have not changed significantly.
 
@@
 
-Since the exchange-correlation functional is not known and each molecule has a slightly different structure compared to the optimized structure, each parameter has uncertain. 
-To estimate the uncertainty, we consider the maximum amount of uncertainties according to the obtained $(\lambda, \{E_i|i=1,2,\cdots,N \}, \{J_{ij}|i,j=1,2,\cdots,N \})$ with the six different HFX.
+Each parameter has uncertainty caused by the exchange-correlation functional in the multiscale model.
+To estimate the uncertainty which is unknown, we consider the maximum amount of uncertainties according to the obtained $(\lambda, \{E_i|i=1,2,\cdots,N \}, \{J_{ij}|i,j=1,2,\cdots,N \})$ with the six different HFX.
 To achieve this, each parameter can be modeled as a normal distribution with the mean and standard deviation obtained by the maximum likelihood estimation.
-For a normal distribution, they are respectively the sample mean and standard deviation obtained by six varying HFXs.
+For a normal distribution, they are respectively the sample mean and standard deviation obtained by six different HFXs.
 
@@
 %
+
+\section{Conclusion}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2024-11-13 apssamp.tex
update

--- 2024-11-10 paper.tex
@@
-\documentclass[letterpaper,12pt]{article}
-\usepackage{tabularx} % extra features for tabular environment
+% ****** Start of file apssamp.tex ******
+%
+%   This file is part of the APS files in the REVTeX 4.2 distribution.
+%   Version 4.2a of REVTeX, December 2014
+%
+%   Copyright (c) 2014 The American Physical Society.
+%
+%   See the REVTeX 4 README file for restrictions and more information.
+%
+% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
+% as well as the rest of the prerequisites for REVTeX 4.2
+%
+% See the REVTeX 4 README file
+% It also requires running BibTeX. The commands are as follows:
+%
+%  1)  latex apssamp.tex
+%  2)  bibtex apssamp
+%  3)  latex apssamp.tex
+%  4)  latex apssamp.tex
+%
+\documentclass[%
+ reprint,
+%superscriptaddress,
+%groupedaddress,
+%unsortedaddress,
+%runinaddress,
+%frontmatterverbose, 
+%preprint,
+%preprintnumbers,
+%nofootinbib,
+%nobibnotes,
+%bibnotes,
+ amsmath,amssymb,
+ aps,
+%pra,
+%prb,
+%rmp,
+%prstab,
+%prstper,
+%floatfix,
+]{revtex4-2}
+
+\usepackage{graphicx}% Include figure files
+\usepackage{dcolumn}% Align table columns on decimal point
+\usepackage{bm}% bold math
+%%%%%%%%%%%%%%%%%%%%%%%%%package by Zhong
+\usepackage{units}
+\usepackage{lineno}
+\usepackage{float}
 \usepackage{amsmath}  % improve math presentation
@@
 \usepackage{verbatim}
-\usepackage{graphicx} % takes care of graphic including machinery
-\usepackage[margin=1in,letterpaper]{geometry} % decreases margins
-\usepackage{cite} % takes care of citations
-\usepackage[final]{hyperref} % adds hyper links inside the generated pdf file
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\usepackage{hyperref}% add hypertext capabilities
+%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
+%\linenumbers\relax % Commence numbering lines
 
-\usepackage{booktabs}
-
-\hypersetup{
-	colorlinks=true,       % false: boxed links; true: colored links
-	linkcolor=blue,        % color of internal links
-	citecolor=blue,        % color of links to bibliography
-	filecolor=magenta,     % color of file links
-	urlcolor=blue         
-}
-\usepackage{blindtext}
-
-\usepackage{units}
-\usepackage{lineno}
-\usepackage{comment}
-\usepackage{float}
-%++++++++++++++++++++++++++++++++++++++++
+%\usepackage[showframe,%Uncomment any one of the following lines to test 
+%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
+%%text={7in,10in},centering,
+%%margin=1.5in,
+%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
+%%height=10in,a5paper,hmargin={3cm,0.8in},
+%]{geometry}
 
 \begin{document}
-\linenumbers
-\title{Uncertainty Quantification in Multiscale Model }
-\author{authors}
-\date{\today}
-\maketitle
+
+\preprint{APS/123-QED}
+
+\title{Uncertainty Quantification in Multiscale Model}% Force line breaks with \\
+% \thanks{A footnote to the article title}%
+
+\author{Zhongquan Chen, Baumeier Bj\"orn, Pim van der Hoorn}
+ \altaffiliation{Department of Mathematics and Computer Science \& Institute for Complex Molecular Systems, Eindhoven University of Technology},
+%Lines break automatically or can be forced with \\
+
+% \collaboration{MUSO Collaboration}%\noaffiliation
+
+%\collaboration{CLEO Collaboration}%\noaffiliation
+
+\date{\today}% It is always \today, today,
+             %  but any date may be explicitly specified
+
 \begin{abstract}
   This work quantifies uncertainties in a multiscale model for charge dynamics in organic semiconductors (OSCs).
-A first-principle multiscale model integrates classical molecular dynamics (MD), density functional theory (DFT), and continuous-time random walk (CTRW) processes to allow the simulation of charge transport in OSCs.
+A first-principle multiscale model integrates classical molecular dynamics (MD), density functional theory (DFT), quantum mechanical calculation and continuous-time random walk (CTRW) processes to allow the simulation of charge transport in OSCs.
 The model brings inherent uncertainties arising from the empirical approximations and numerical simulations.
@@
 As shown by Sobol indices, the QoI is most sensitive to molecule energy, then reorganization energy and least sensitive to coupling elements.
+\begin{description}
+\item[Usage]
+Secondary publications and information retrieval purposes.
+\item[Structure]
+You may use the \texttt{description} environment to structure your abstract;
+use the optional argument of the \verb+\item+ command to give the category of each item. 
+\end{description}
 \end{abstract}
+
+%\keywords{Suggested keywords}%Use showkeys class option if keyword
+                              %display desired
+\maketitle
+
+%\tableofcontents
 
@@
 Theoretical model and computer simulation for understanding a physical system usually contain some uncertainties in predicting the system features. 
-For example, the theoretical model does not encompass all relevant physical factors, the theoretical model incorporates empirical parameters that include noise, the numerical scheme contains approximation, the simulation use noisy quantities, etc.
+For example, the theoretical model does not encompass all relevant physical factors, the theoretical model incorporates empirical parameters that include noise, the numerical scheme contains approximation, the simulation use noisy quantities, etc~\cite{sarkar_uncertainty_2017,oconnor_quantifying_2024, chernatynskiy_uncertainty_2013, suleimenova_tutorial_2021,coveney_reliability_2021, coveney_when_2021}.
 Nevertheless, those uncertainties should not affect the validity of the model or the accuracy for the predicting system in terms of some quantities of interest (QoI). 
@@
 
-In this work, an investigated model containing uncertainties is the multiscale model of charge dynamics in organic semiconductors (OSCs), which are materials that consist of organic molecules with disordered and amorphous structure.
-Besides its semiconducting properties, tthey are mechanically flexible and comes with controllable charge transport properties.
+In this work, an investigated model containing uncertainties is the multiscale model of charge dynamics~\cite{Baumeier2011, edeling_global_2024,coropceanu_charge_2007} in organic semiconductors (OSCs), which are materials that consist of organic molecules with disordered and amorphous structure.
+Besides its semiconducting properties, they are mechanically flexible and comes with controllable charge transport properties.
 This flexible functionality is achieved by tuning molecular properties to achieve an ideal operating properties at the device-level, so a fundamental understanding of OSC from molecule scale  plays an important role in OSC optimization.
@@
 To explain in detail those uncertainties, the first-principle multiscale model is briefly reviewed.
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.9\textwidth]{figs/MSM.pdf}
+  \caption{The multiscale model workflow for OSC.
+Step 1: MD simulation to generate atom coordinates.
+Step 2: Molecule energy $E_i$ calculation.
+Step 3: Calculation of Reorganization energy $\lambda_{ij}$ and coupling element $J_{ij}$ for pairs of molecule $i,j$ whose COM distance is less than $r_\text{cutoff}$.
+Step 4: Modelling dynamics on device level, such as ToF calculation.}
+  \label{fig:MSM}
+\end{figure*}
 
@@
 Finally the charge dynamic is model as a CTRW among the molecules.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.99\textwidth]{figs/MSM.pdf}
-    \caption{The multiscale model workflow for OSC.
-Step 1: MD simulation to generate atom coordinates.
-Step 2: Molecule energy $E_i$ calculation.
-Step 3: Calculation of Reorganization energy $\lambda_{ij}$ and coupling element $J_{ij}$ for pairs of molecule $i,j$ whose COM distance is less than $r_\text{cutoff}$.
-Step 4: Modelling dynamics on device level, such as ToF calculation.}
-    \label{fig:MSM}
-\end{figure}
 
@@
 In our model, two nodes $i,j$ form a connection of the corresponding molecules $i,j$ have their closest-contact distance smaller than $r_\text{cutoff}=\unit[0.5]{nm}$.
-
 The rest of this section will introduce the following: the molecular dynamics used to obtain the coordinates $r^x_{i},r^y_{i},r^z_{i}$, the calculation of node-specific quantities $\lambda$, $E_i$ and $J_{ij}$, as well as the calculation of ToF $\tau$ and steady state velocity $v_\text{SS}$.
@@
 After energy minimization, the system is simulated for \unit[1]{ns} (?) in a $NpT$ ensemble, keeping a constant temperature of \unit[300]{K} and constant pressure of \unit[1]{bar} using the V-rescale thermostat~\cite{bussi_canonical_2007} with the coupling time constant \unit[0.1]{ps} and the Parrinello-Rahman barostat~\cite{parrinello_polymorphic_1981} with a time constant for pressure coupling \unit[2]{ps}.
-The equation of motion for updating the atomic coordinates is implemented by leap-frog algorithm~\cite{van_gunsteren_leap-frog_1988} with a time step of \unit[1]{fs}.
+The equation of motion for updating the atomic coordinates is implemented by leap-frog algorithm~\cite{van_gunsteren_leap} with a time step of \unit[1]{fs}.
 
@@
 The final configuration of MADN is chosen for the further steps in the multiscale model, whose configuration is a cubic box with a length of \unit[9.0]{nm} and a density of $\unit[1.08]{g/cm^3}$.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\begin{comment}
-    The MD in the multiscale model is to use Newton's second law to update the atomic coordinate. Written in Hamilton equation, the equation of motion reads:
-\begin{equation}
-    \begin{cases}
-        \frac{d \vec{r}_i}{dt} = \frac{\partial H^\text{MD} }{\partial \vec{p}_i} \\
-        \frac{d \vec{p}_i}{dt} = -\frac{\partial H^\text{MD} }{\partial \vec{r}_i}
-    \end{cases}
-    \label{eq:Hamilton}
-\end{equation}
-for $i=1,\cdots,N_a$. Where $N_a$, $m_i$, $\vec{r}_i$, $\vec{p}_i$ are the atom number, atomic mass,  position vector and momentum, respectively. 
-And the Hamiltonian $H$ reads:
-$H^\text{MD}=\sum\limits_{i} \frac{|\vec{p}_i|^2}{2 m_i} + U(\vec{r}_1,\cdots,\vec{r}_{N_a})$.
-
-In principle the potential energy function $U(\vec{r}_1,\cdots,\vec{r}_{N_a})$ of the system can be obtained from electronic structure models.
-As mentioned in the introduction, it is a very computationally expensive procedure, and without too much loss in precision, MD use empirical potentials that are designed for specific purposes.
-The MD simulation performed using the GROMACS software package~\cite{berendsen_gromacs_1995}, employing a gromos54a7 type force field obtained via the tool Automated Topology Builder~\cite{stroet_automated_2018}.
-The procedure of the MD simulation in this work is as followed:...
-\end{comment}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Electronic Structure Calculations} 
@@
 %
-\begin{equation}
-    \left(-\frac{1}{2}\nabla^2_{\vec{r}} + v_\text{ext}(\vec{r}) + v_\text{H}[\rho](\vec{r}) + v_\text{XC}[\rho](\vec{r})\right) \phi_l(\vec{r}) = H^\text{KS} \phi_l(\vec{r}) = \epsilon_l \phi_l (\vec{r}) ,
+\begin{eqnarray}
+    && \left(-\frac{1}{2}\nabla^2_{\vec{r}} + v_\text{ext}(\vec{r}) + v_\text{H}[\rho](\vec{r}) + v_\text{XC}[\rho](\vec{r})\right) \phi_l(\vec{r}) \nonumber \\
+    && = H^\text{KS} \phi_l(\vec{r}) = \epsilon_l \phi_l (\vec{r}) ,
     \label{eq:KS2}
-\end{equation}
+\end{eqnarray}
 %
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \subsection{Time-of-flight and Steady State Velocity Calculation}
@@
 To account for all possible starting nodes of the carriers, all Source states must be considered.
-The random walk process can be modeled as a parallel electric network of capacitors \cite{doyle_random_2000}.
+The random walk process can be modeled as a parallel electric network of capacitors \cite{doyle_random_1984}.
 Accordingly, the ToF is evaluated using the harmonic mean:
@@
 %
-\begin{figure}[H]
+\begin{figure}
     \centering
-    \includegraphics[width=0.75\textwidth]{figs/fig_autogen.pdf}
+    \includegraphics[width=0.45\textwidth]{figs/fig_autogen.pdf}
     \caption{(a) The dipole moment of neutral state MAND molecule $\mu$, (b) isotropic polarizability $P_\text{iso}$, (c) reorganization energies $\lambda$ and (d) energy disorder $\sigma(E)$ as a function of the HFX parameters (denoted by $\alpha$).}
@@
 
-\begin{table}[H]
-    \centering
+\begin{table}[tbp]%The best place to locate the table environment is directly after its first reference in text
+\caption{\label{tab:ToF_MADN_HFX}%
+The ToF and diffusive velocity calculated by ToF along a distance $L_x = 8$ [nm] with and without energy disorder of the MADN system as a function of the HFX.
+The ToF is in unit \unit[]{s} and $v_\text{ToF}$ in unit \unit[]{m/s}.
+}
+\begin{ruledtabular}
   \begin{tabular}{c c c c c}
-    \hline
-        $\alpha$ & ToF [s] & $v_\text{ToF}$ [m/s] & ToF(no $E$) [s] & $v_\text{ToF}$ (no $E$) [m/s] \\
+        $\alpha$ & ToF& $v_\text{ToF}$ & ToF(no $E$)& $v_\text{ToF}$(no $E$) \\
     \hline
@@
         0.25 & $ 9.5 \times 10^{-8}$ & 0.083 & $7.2 \times 10^{-10}$ & 11 \\
-    \hline
     \end{tabular}
-    \caption{The ToF and diffusive velocity calculated by ToF along a distance $L_x = 8$ [nm] with and without energy disorder of the MADN system as a function of the HFX. }
-    \label{tab:ToF_MADN_HFX}
+\end{ruledtabular}
 \end{table}
 
-Figure \ref{fig:E_qmmm_MADN} presents a scatter plot comparing the site energies of MADN molecules across different HFX values, using $\alpha$ = 0.25 (PBE0 functional) as a reference for which the calculated molecule energy has a range from -1.12 to -0.63 \unit[]{eV}.
-The range of molecule energy for the other five HFX are: from -1.17 to -0.60 \unit[]{eV} for $\alpha=0$, from -1.11 to -0.59 \unit[]{eV} for $\alpha=0.05$, from -1.07 to -0.63 \unit[]{eV} for $\alpha=0.10$, from -1.13 to -0.61 \unit[]{eV} for $\alpha=0.15$, and from -1.16 to -0.60 \unit[]{eV} for $\alpha=0.20$.
-
-The bright-yellow color in all plots of Fig.
-\ref{fig:E_qmmm_MADN} indicates that most data points are clustering near the diagonal line, so the molecular energies calculated by different HFX are very close.
-To quantify the similarity between two empirical distribution, Wasserstein distance~\cite{villani_optimal_2009} is used.
-Denote the empirical distribution of molecular energy $E$ at $\alpha=0$ to be $P_{E(\alpha=0)}$. 
-The 1-Wasserstein distance between $P_{E(\alpha=0)}$ and $P_{E(\alpha=0.25)}$ is calculated as:
-\begin{equation}
-    W_1 (P_{E(\alpha=0)}, P_{E(\alpha=0.25)}) = (\frac{1}{N} \sum\limits_{i=1}^N | E_{(i)}(\alpha=0) - E_{(i)}(\alpha=0.25) |)
-\end{equation}
-where $E_{(i)}(\alpha=0)$ is the order statistics of $E_i(\alpha=0)$.
-The 1-Wasserstein distance between two empirical distributions for each plot in Fig.
-\ref{fig:E_qmmm_MADN} is shown in Table \ref{tab:W2_E}.
-$W_1 (P_{E(\alpha=0)}, P_{E(\alpha=0.25)})$ has range between 0.0045 to 0.0091, indicating that the molecular energy distributions are very similar.
-
-\begin{table}[H]
-    \centering
+%
+\begin{table*}[tbp]%The best place to locate the table environment is directly after its first reference in text
+\caption{\label{tab:W2_E}%
+The 1-Wasserstein distance between the distributions pair of molecule energy $P_{E(\alpha)}$, electrostatic energy $P_{E^\text{el}(\alpha)}$, polar energy $P_{E^\text{polar}(\alpha)}$ and $P_{\log_{10}(J_{ij}^2)(\alpha)}$.
+}
+\begin{ruledtabular}
   \begin{tabular}{c c c c c c}
-    \hline
   $\alpha'$ & 0 & 0.05 & 0.10 & 0.15 & 0.20 \\
@@
   $W_1 (P_{\log_{10}(J_{ij}^2)(\alpha')}, P_{\log_{10}(J_{ij}^2)(\alpha=0.25)})$ &  0.0054 & 0.0091 & 0.0067 & 0.0053 & 0.0045 \\
-    \hline
     \end{tabular}
-    \caption{The 1-Wasserstein distance between the distributions pair of molecule energy $P_{E(\alpha)}$, electrostatic energy $P_{E^\text{el}(\alpha)}$, polar energy $P_{E^\text{polar}(\alpha)}$ and $P_{\log_{10}(J_{ij}^2)(\alpha)}$.
-}
-    \label{tab:W2_E}
-\end{table}
+\end{ruledtabular}
+\end{table*}
+%
 
-\begin{figure}[H]
+\begin{figure*}
   \centering
-    \includegraphics[width=0.99\textwidth]{figs/scatterE_qmmm.pdf}
+  \includegraphics[width=0.80\textwidth]{figs/scatterE_qmmm.pdf}
   \caption{Scatter plot of site energy of MADN molecules calculated from different HFX, compared to the site energy calculated from HFX=0.25 (The PBE0 functional).
@@
   \label{fig:E_qmmm_MADN}
-\end{figure}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.80\textwidth]{figs/scatterEstat_qmmm.pdf}
+  \caption{Scatter plot of MADN electrostatic energy calculated from different HFX, compared to the electrostatic energy calculated from HFX=0.25 (The PBE0 functional).
+The brighter color near the diagonal lines indicates denser population of the molecules.
+The top and right histogram show the energy distributions.}
+  \label{fig:Estat_qmmm_MADN}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.80\textwidth]{figs/scatterEdip_qmmm.pdf}
+  \caption{Scatter plot of MADN polarization energy calculated from different HFX, compared to the polarization energy calculated from HFX=0.25 (The PBE0 functional).
+The brighter color near the diagonal lines indicates denser population of the molecules.
+The top and right histogram show the energy distributions.}
+  \label{fig:Edip_qmmm_MADN}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.80\textwidth]{figs/scatterJ_all.pdf}
+  \caption{Scatter plot of MADN coupling element $\log_{10} J^2$ calculated from different HFX, compared to the polarization energy calculated from HFX=0.25 (The PBE0 functional).
+The brighter color near the diagonal lines indicates denser population of the molecules.
+The top and right histogram show the energy distributions.}
+  \label{fig:J_MADN}
+\end{figure*}
+
+Figure \ref{fig:E_qmmm_MADN} presents a scatter plot comparing the site energies of MADN molecules across different HFX values, using $\alpha$ = 0.25 (PBE0 functional) as a reference for which the calculated molecule energy has a range from -1.17 to -0.60 \unit[]{eV}y.
+The range of molecule energy for the other five HFX are: 
+from -1.11 to -0.59 \unit[]{eV} for $\alpha=0$, 
+from -1.07 to -0.63 \unit[]{eV} for $\alpha=0.05$, 
+from -1.13 to -0.61 \unit[]{eV} for $\alpha=0.10$
+from -1.16 to -0.60 \unit[]{eV} for $\alpha=0.15$, 
+and from -1.12 to -0.63 \unit[]{eV} for $\alpha=0.20$.
+The bright-yellow color in all plots of Fig.
+\ref{fig:E_qmmm_MADN} indicates that most data points are clustering near the diagonal line, so the molecular energies calculated by different HFX are very close.
+
+To quantify the similarity between two empirical distribution, Wasserstein distance~\cite{villani_optimal_2009} is used.
+Denote the empirical distribution of molecular energy $E$ at $\alpha=0$ to be $P_{E(\alpha=0)}$. 
+The 1-Wasserstein distance between $P_{E(\alpha=0)}$ and $P_{E(\alpha=0.25)}$ is calculated as:
+\begin{eqnarray}
+    && W_1 (P_{E(\alpha=0)}, P_{E(\alpha=0.25)}) = \nonumber \\
+    && (\frac{1}{N} \sum\limits_{i=1}^N | E_{(i)}(\alpha=0) - E_{(i)}(\alpha=0.25) |)
+\end{eqnarray}
+where $E_{(i)}(\alpha=0)$ is the order statistics of $E_i(\alpha=0)$.
+The 1-Wasserstein distance between two empirical distributions for each plot in Fig.
+\ref{fig:E_qmmm_MADN} is shown in Table \ref{tab:W2_E}.
+$W_1 (P_{E(\alpha=0)}, P_{E(\alpha=0.25)})$ has range between 0.0045 to 0.0091, indicating that the molecular energy distributions are very similar.
 
@@
 If molecule $i'$ energy is the lowest one among the $N$ molecules, then a further lowering in the energy of molecule $i'$ may lead to large change in ToF, since low energy potentially lead to a trap in the charge transport dynamics.
+
+Table \ref{tab:maxEi} shows that depending on $\alpha'$, the maximum $|E_i(\alpha=0.25) - E_i(\alpha')|$ is 0.12 to 0.15, which is considerable small compared to the range of molecular energy and the magnitude of the energy disorder, which is around 0.08 as shown in Table \ref{tab:ToF_MADN_HFX}.
+The energy of molecule $i'$ shown in Table \ref{tab:maxEi} indicates that the $i'$ molecule energy is not the lowest one in the system.
+So the maximum energy variation quantified by $\max(|E_i(\alpha=0.25) - E_i(\alpha')|)$ is not likely to results in large change in ToF due to trapping effects.
 %
-\begin{table}[H]
-    \centering
+\begin{table}[tbp]%The best place to locate the table environment is directly after its first reference in text
+\caption{\label{tab:maxEi}%
+In the tested $\alpha'$ values, the second column shows the maximum of $E_i(\alpha=0.25) - E_i(\alpha')$ for all molecules.
+Denoting the index of the molecule which has maximum $E_i(\alpha=0.25) - E_i(\alpha')$ for the chosen $\alpha'$ case, the third column shows the energy of molecule $i'$ calculated by $\alpha=0.25$.
+The fourth column shows the molecule energy $E_{i'}(\alpha')$ calculated by $\alpha'$.
+All the energies are in unit \unit[]{eV}.
+}
+\begin{ruledtabular}
   \begin{tabular}{c c c c}
-    \hline
   $\alpha'$ & $\max(|E_i(\alpha=0.25) - E_i(\alpha')|)$  & $E_{i'}(\alpha=0.25)$ & $E_{i'}(\alpha')$ \\
@@
   0.15 & 0.15 & -0.84 & -0.69 \\
- 0.20 & 0.12 & -1.70 & -0.82 \\
-    \hline
+  0.20 & 0.12 & -0.70 & -0.82 \\
     \end{tabular}
-    \caption{ In the tested $\alpha'$ values, the second column shows the maximum of $E_i(\alpha=0.25) - E_i(\alpha')$ for all molecules.
-Denoting the index of the molecule which has maximum $E_i(\alpha=0.25) - E_i(\alpha')$ for the chosen $\alpha'$ case, the third column shows the energy of molecule $i'$ calculated by $\alpha=0.25$.
-The fourth column shows the molecule energy $E_{i'}(\alpha')$ calculated by $\alpha'$.
-All the energies are in unit \unit[]{eV}.}
-    \label{tab:maxEi}
+\end{ruledtabular}
 \end{table}
-%
-Table \ref{tab:maxEi} shows that depending on $\alpha'$, the maximum $|E_i(\alpha=0.25) - E_i(\alpha')|$ is 0.12 to 0.15, which is considerable small compared to the range of molecular energy. 
-The energy of molecule $i'$ shown in Table \ref{tab:maxEi} indicates that the $i'$ molecule energy is not the lowest one in the system.
-So the maximum energy variation quantified by $\max(|E_i(\alpha=0.25) - E_i(\alpha')|)$ is not likely to results in large change in ToF due to trapping effects.
 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.99\textwidth]{figs/scatterEstat_qmmm.pdf}
-    \caption{Scatter plot of MADN electrostatic energy calculated from different HFX, compared to the electrostatic energy calculated from HFX=0.25 (The PBE0 functional).
-The brighter color near the diagonal lines indicates denser population of the molecules.
-The top and right histogram show the energy distributions.}
-    \label{fig:Estat_qmmm_MADN}
-\end{figure}
+Figures \ref{fig:Estat_qmmm_MADN} and \ref{fig:Edip_qmmm_MADN} show that both electrostatic and polarization energies remain consistently close to the ones calculated from $\alpha=0.25$, since all the points comparing $E^\text{el}_i(\alpha')$ and $E^\text{el}_i(\alpha=0.25)$ in the scatter plot are close to the diagonal line.
+The range of $E^\text{el}$ calculated by different $\alpha$ is as follows:
+from  -0.55 to 0.078 eV for $\alpha=0$, 
+from  -0.52 to 0.047 eV for $\alpha=0.05$, 
+from  -0.57 to 0.086 eV for $\alpha=0.10$, 
+from  -0.59 to 0.14 eV for $\alpha=0.15$, 
+from  -0.57 to 0.10 eV for $\alpha=0.20$, 
+and from -0.63 to 0.10 eV for $\alpha=0.25$.
 
-Figures \ref{fig:Estat_qmmm_MADN} and \ref{fig:Edip_qmmm_MADN} show that both electrostatic and polarization energies remain consistent close across HFX values from 0 to 0.25, since all the points comparing $E_i(\alpha')$ and $E_i(\alpha=0.25)$ in the scatter plot are close to the diagonal line.
-The 1-Wasserstein distance between the distribution of $E^\text{el}$ calculated by $\alpha'$ and that calculated by $\alpha=0.25$, $W_1(P_{E^\text{el}(\alpha')}, P_{E^\text{el}(\alpha=0.25)})$, is shown at Table \ref{tab:W2_E}.
-It shows that $W_1(P_{E^\text{el}(\alpha')}, P_{E^\text{el}(\alpha=0.25)})$ is at maximum 0.012.
-The 1-Wasserstein distance between the $E^\text{polar}$ distribution calculated by $\alpha'$ and that calculated by $\alpha=0.25$ is also shown in Table .\ref{tab:W2_E}, with a maximum of 0.006.
+The 1-Wasserstein distance between the distribution of $E^\text{el}$ calculated by $\alpha'$ and that calculated by $\alpha=0.25$, $W_1(P_{E^\text{el}(\alpha')}, P_{E^\text{el}(\alpha=0.25)})$, is shown at the third row at Table \ref{tab:W2_E}.
+The maximum of $W_1(P_{E^\text{el}(\alpha')}, P_{E^\text{el}(\alpha=0.25)})$ 0.012.
+The 1-Wasserstein distance between the $E^\text{polar}$ distribution calculated by $\alpha'$ and that calculated by $\alpha=0.25$ is also shown in Table \ref{tab:W2_E}, with a maximum of 0.006.
 So the small Wasserstein distances suggest that the using different $\alpha'$ other than $\alpha=0.25$, the data of $E, E^\text{el}, E^\text{polar}$ have not changed significantly.
 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.99\textwidth]{figs/scatterEdip_qmmm.pdf}
-    \caption{Scatter plot of MADN polarization energy calculated from different HFX, compared to the polarization energy calculated from HFX=0.25 (The PBE0 functional).
-The brighter color near the diagonal lines indicates denser population of the molecules.
-The top and right histogram show the energy distributions.}
-    \label{fig:Edip_qmmm_MADN}
-\end{figure}
-
-The electrostatic energy ranges from 0.1 to -0.6 eV, while polarization energy spans -0.5 to -0.8 eV.  Similar to the molecule energy, the data points are clustered near the diagonal line. 
 The standard deviations of the electrostatic energy are 0.099, 0.094, 0.099, 0.11, 0.10, \unit[0.10]{eV}, and the standard deviations of the polarization energies are 0.044, 0.043, 0.043, 0.047, 0.045, \unit[0.045]{eV}.
-So the disorder in electrostatic energies is consistently larger than than in molecule energies, and the palorization effect reduces the electrostatic energy disorder.
+So the disorder in electrostatic energies is consistently larger than that in molecule energies, and the palorization effect reduces the electrostatic energy disorder.
 Each individual molecule has similar polarization energies under different HFX calculation, in spite of $P_\text{iso}$ is linearly dependent on HFX.
@@
 The coupling element obtained with different HFX for each molecular pair compared to that obtained with HFX=0.25 is shown in the scatter plot Fig. \ref{fig:J_MADN}.
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.95\textwidth]{figs/scatterJ_all.pdf}
-    \caption{Scatter plot of MADN coupling element $\log_{10} J^2$ calculated from different HFX, compared to the polarization energy calculated from HFX=0.25 (The PBE0 functional).
-The brighter color near the diagonal lines indicates denser population of the molecules.
-The top and right histogram show the energy distributions.}
-    \label{fig:J_MADN}
-\end{figure}
 
-The distribution of the majority $\log_{10} J^2$ has a range of -14 to -2 while only a few $\log_{10} J^2$ has low value below -15. For all HFX values, the distribution has a peak at around -5. 
-For large values $\log_{10} J^2 < -5$ the coupling element calculated from $\alpha'=0, 0.05, 0.10, 0.15, 0.2$ remains consistently close to that calculated by $\alpha=0.25$.
-While for small values $\log_{10} J^2 > -5$, the $\alpha'$ calculated coupling elements for a specific molecular pair can have large variation compared to $\log_{10} J^2$ calculated using $\alpha=0.25$.
+The distribution of the majority $\log_{10} J_{ij}^2$ has a range of -14 to -2 while only a few $\log_{10} J_{ij}^2$ has low value below -15.
+For all HFX values, the distribution has a peak at around -5.
+For large values $\log_{10} J_{ij}^2 < -5$ the coupling element calculated from $\alpha'=0, 0.05, 0.10, 0.15, 0.2$ remains consistently close to that calculated by $\alpha=0.25$.
+While for small values $\log_{10} J_{ij}^2 > -5$, the $\alpha'$ calculated coupling elements for a specific molecular pair can have large variation compared to $\log_{10} J_{ij}^2$ calculated using $\alpha=0.25$.
+The 1-Wasserstein distance between the $J$ distributions obtained by different $\alpha$ is always smaller than 0.01,  
+indicating similar $J$ distributions even though a few $J_{ij}$ shows large difference when $\alpha$ varies.
 
-In charge transport network, $J^2$ is undirectional for a molecular pair, and decays exponentially as the mutual center-of-mass distance increases.
-The large $\log_{10} J^2$ are usually observed for molecular pairs with small center-of-mass distance.
-When the center-of-mass distance is very large, the $\log_{10} J^2$ is small and some of those small $\log_{10} J^2$ are sensitive to $\alpha$.
+In charge transport network, $J_{ij}^2$ is undirectional for a molecular pair, and decays exponentially as the mutual center-of-mass distance increases.
+The large $\log_{10} J_{ij}^2$ are usually observed when molecular $i$ and $j$ are close.
+When the center-of-mass distance is very large, the $\log_{10} J_{ij}^2$ is small and some of those small $\log_{10} J_{ij}^2$ are sensitive to $\alpha$.
 
-However, the charge dynamics is dominated by large $\log_{10} J^2$ which are found between molecule pair having small center-of-mass.
+However, the charge dynamics is dominated by large $\log_{10} J_{ij}^2$ which are found between molecule pair having small center-of-mass.
 As the center-of-mass distance increases, $\log_{10} J^2$ becomes small and negligible for the charge dynamics.
+So the small $J_{ij}$ may not have noticeable effect on the ToF although their calculated values from different HFX are very different.
 
@@
     \item A critical value $J_c$ is chosen,
-    \item In graph $\mathbf{G}$ remove all the edges with $J^2 < J_c^2$
+    \item In graph $\mathbf{G}$ remove all the edges with $J_{ij}^2 < J_c^2$
     \item Calculate the maximum size $\max({N_\text{sub}})$ of the connected subgraphs
@@
 
-\begin{figure}[H]
+\begin{figure}[btp]
   \centering
-    \includegraphics[width=0.75\textwidth]{figs/fig_network_all.pdf}
+  \includegraphics[width=0.45\textwidth]{figs/fig_network_all.pdf}
   \caption{The maximum size of the subgraphs obtained in the percolation algorithm as a function of critical value $J_c$.
@@
 \end{figure}
+
+\begin{table}[H]
+  \caption{\label{tab:ToF_J} The ToF along a distance $L_x = 8$ [nm] of the MADN system as a function of the HFX. The molecular connections with coupling element $\log_{10} J^2_{ij} < 5$ are deleted.}
+  \centering
+  \begin{tabular}{c c }
+  \hline
+  \hline
+      $\alpha$ & ToF [s]  \\
+  \hline
+      0.00 &  $7.5 \times 10^{-9}$ \\
+      0.05 & $ 8.1 \times 10^{-9}$ \\
+      0.10 & $ 1.6 \times 10^{-8}$ \\
+      0.15 & $ 3.1 \times 10^{-8}$ \\
+      0.20 & $ 2.5 \times 10^{-8}$ \\
+      0.25 & $ 9.7 \times 10^{-8}$ \\
+  \hline
+  \hline
+  \end{tabular}
+\end{table}
+
 After performing percolation algorithm, Figure \ref{fig:J_percolate} shows the dependence of $\max({N_\text{sub}})$ on the critical value $J_c$.
-When $\log_{10} J_c^2 < -4.5$, $\max({N_\text{sub}})$ is 1000, meaning that removing all the edges with $J^2 < 3.1 \times 10^{-5}$ the 1000 vertexes still form a connected graph.
-But when removing the edges with $J^2 < 3.1 \times 10^{-4}$ ( corresponding to $J_c > -3.5$), the maximum size subgraph is 600, and it quickly decreases as $J_c$ increases, showing a phase transition.
-So the dominated coupling elements are those with $\log_{10} J_c^2 > -4.5$. 
-And the variation in small $J$ due to HFX has less impact on the charge dynamics.
+When $\log_{10} J_c^2 < 5$, $\max({N_\text{sub}})$ is 1000, meaning that removing all the edges with $J_{ij}^2 < 1 \times 10^{-5}$ the 1000 vertexes still form a connected graph.
+But when removing the edges with $J_{ij}^2 < 3.1 \times 10^{-4}$ ( corresponding to $J_c > -3.5$), the maximum size subgraph is 600, and it quickly decreases as $J_c$ increases, showing a phase transition.
+So the dominated coupling elements are those with $\log_{10} J_c^2 > -5$. 
+And the variation in small $J_{ij}$ due to HFX has less impact on the charge dynamics.
+Table \ref{tab:ToF_J} shows the ToF for the MADN system after deleting the molecular connections with  $\log_{10} J_c^2 < -5$.
+The resulting ToF is close to the values obtained without deleting any connections (shown in Table \ref{tab:ToF_MADN_HFX}).
+The increase of ToF after deleting the connections with  $\log_{10} J_c^2 < -5$ is always less than 30\%, confirming that the molecular connections with the small $J_{ij}$ has small effect in ToF.
 
-In this section we answer the question of how does HF level change the electronic structures and 
-how does HF level change the charge mobility. 
-In the next section, uncertainty quantification via Monte Carlo method and sensitivity analysis is perform to answer which electronic structure (among energy, coupling element and reorganization energy) uncertainty has the most impact on the charge mobility distribution.
+In this section we answer the question of how does HF level change the electronic structures ($\lambda, E_i, J_{ij}$) and 
+how does HF level change the ToF. 
+In the next section, uncertainty quantification via Monte Carlo method and sensitivity analysis is performed to answer which electronic structure (among energy, coupling element and reorganization energy) uncertainty has the most impact on the ToF distribution.
 And further we estimate the range of the quantity of interest, given a confidence level.
@@
 
-%From equation \ref{eq:hitting_time}, the ToF can be considered as the some combination of occupation time in the molecules, which is $log_{10}(\omega_{i}^{-1})$. 
-%When the parameters $E, J_{ij}, \lambda_{ij}$ are normally distributed random variables, the calculated ToF shows that variables $E,\lambda_{ij}$ has a larger influence than $J_{ij}$. 
-%The Marcus rate uses $E,\lambda_{ij}$ in the exponential form. If $\Delta E$ is normally distributed, then $log_{10}(\omega_{i}^{-1})$ is Gamma distributed. 
-%Since $E$ has greater influence to ToF than $\lambda_{ij}, J_{ij}$ and to be consistent, Gamma distribution is used to fit the Monte Carlo sampled ToF in all the investigated cases.
-
-\begin{comment}
-    Sampling the molecule energy as a normal distribution $E_i \sim \mathcal{N}(\bar{E}_i, \sigma_{E_i})$ will potentially destroy the energy correlation, especially for correlated systems, resulting a shift in the ToF calculation.
-But we will show that making the molecule energy uncorrelated in the MADN system will not cause such a shift in ToF. 
-To do so, let $\{E_1, E_2, \cdots, E_N\}^{\alpha}$ be an ordered set with elements being the energy calculated using a specific $\alpha$ value. 
-Then the order of the energies are randomly shuffled so that they are no longer correlated, and denote it as $\{E_1, E_2, \cdots, E_N\}^{\alpha}_{\text{shuffle}}$.
-The ToF calculated using the shuffled energy is $ \tau_{\text{sh}} = \tau(\{E_1, E_2, \cdots, E_N\}^{\alpha}_{\text{shuffle}}) $.
-%
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\textwidth]{figs/ToFx_shuffle.pdf}
-    \caption{Distribution of $\tau_{\text{sh}}$ calculated using shuffle energies.
-Each distribution are a sample of 10000 $\tau_{\text{shuffle}}$.
-The position of the solid circle indicates the ToF calculated from the specific $\alpha$ value, and the position of the solid square indicates the average $\tau_{\text{shuffle}}$ over the 10000 samples.}
-    \label{fig:ToF_shuffle_MADN}
-\end{figure}
-%
-After such shuffling energy and ToF calculation for 10000 times, the distribution of $\tau_{\text{sh}}$ are shown in Fig.\ref{fig:ToF_shuffle_MADN}. 
-For the chosen $\alpha=0.05, 0.15, 0.25$, the $\tau_{\text{sh}}$ does not overall shift to smaller or large values, and the averaged $\tau_{\text{sh}}$ is close to the ToF obtained without energy shuffle.
-So making the energy uncorrelated will not shift the ToF to smaller or larger values.
-This enables representing the parameter uncertainties in $\lambda, \{E_i\}, \{ J_{ij}\}$ by the normal distribution without shift the ToF.
-\end{comment}
-
 To understand how the uncertainty pass from $E, \lambda, J_{ij}$ to ToF, the parameter control is used.
@@
 which uncertainty among $E, \lambda, J_{ij}$ has a greater impact on the ToF,
+
+%
+\begin{figure}
+  \centering
+  \includegraphics[width=0.45\textwidth]{figs/fig_mle_MADN_withE.pdf}
+  \caption{Distribution of ToFs in the multiscale modeled MADN system.
+  Monte Carlo sampling with a sample size $N_\text{MC}=50000$ is used to obtain the sampled distribution.
+The red vertical lines indicate the lower bound and upper bound of the 99\% confidence interval around the median.
+  The black circles indicate the ToF obtained using varying HFX values.
+  (a) $P(\log_{10}(\tau)|E_i \text{ uncertain})$, 
+  (b) $P(\log_{10}(\tau)|\lambda \text{ uncertain})$, 
+  (c) $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$, 
+  (d) $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$. }
+  \label{fig:mle_MADN_withE}
+\end{figure}
+%
 
@@
 Finally obtain and plot the histogram  $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$.
-    \item Both $E_i$, $\lambda$ and $J_{ij}$ are sampled from their normal distribution:$\lambda_i \in \mathcal{N}(\mathbb{E}(\lambda), \mathbb{V}(\lambda))$, $E_i \in \mathcal{N}(\mathbb{E}(E), \mathbb{V}(E))$, $\log_{10}J_{ij}^2 \in \mathcal{N}(\mathbb{E}(\log_{10}J_{ij}^2), \mathbb{V}(\log_{10}J_{ij}^2))$.
+    \item Both $E_i$, $\lambda$ and $J_{ij}$ are sampled from their normal distribution:
+
+    $\lambda_i \in \mathcal{N}(\mathbb{E}(\lambda), \mathbb{V}(\lambda))$,
+
+    $E_i \in \mathcal{N}(\mathbb{E}(E), \mathbb{V}(E))$,
+
+    $\log_{10}J_{ij}^2 \in \mathcal{N}(\mathbb{E}(\log_{10}J_{ij}^2), \mathbb{V}(\log_{10}J_{ij}^2))$.
     Then obtain and plot the histogram $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as the following distribution: 
@@
 Figure .\ref{fig:mle_MADN_withE}(b) shows that $\log_{10}(\tau)$ has a confidence interval of -8.0 to -7.4 when $\lambda$ is varied. 
-Figure \ref{fig:mle_MADN_withE}(c) show that when $J_{ij}$ is uncertain $\log_{10}(\tau)$ has a sharp confidence interval of -7.9 to -7.7, suggesting that the variation in $J_{ij}$ leads to relatively small change in $\log_{10}(\tau)$ compared to $E_i$ and $\lambda$.
-%
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.70\textwidth]{figs/fig_mle_MADN_withE.pdf}
-    \caption{Distribution of ToFs in the multiscale modeled MADN system.
-    Monte Carlo sampling with a sample size $N_\text{MC}=50000$ is used to obtain the sampled distribution.
-The red vertical lines indicate the lower bound and upper bound of the 99\% confidence interval around the median.
-    The black circles indicate the ToF obtained using varying HFX values.
-    (a) $P(\log_{10}(\tau)|E_i \text{ uncertain})$, 
-    (b) $P(\log_{10}(\tau)|\lambda \text{ uncertain})$, 
-    (c) $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$, 
-    (d) $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$. }
-    \label{fig:mle_MADN_withE}
-\end{figure}
-%
-
-% The 90\% confidence interval of each distribution and the fitted Gamma distribution is summarized in table 
-When the energy disorder in MADN system is not considered, that is, all the MADN molecule energy are set to be equal giving $\Delta E=0$, the distribution of ToF is shown in Fig.\ref{fig:mle_MADN_noE}
-
-Measuring the sensitivity of each electronic parameter to ToF is to measure each electronic parameter's contribution to the variance of ToF. 
-That is, if ToF is most sensitive to one parameter, the variance in this particular parameter will contribute most to the ToF variance.
+Figure \ref{fig:mle_MADN_withE}(c) show that when $J_{ij}$ is uncertain $\log_{10}(\tau)$ has a narrow confidence interval of -7.9 to -7.7, suggesting that the variation in $J_{ij}$ leads to relatively small change in $\log_{10}(\tau)$ compared to $E_i$ and $\lambda$.
 
@@
   \centering
-    \includegraphics[width=0.99\textwidth]{figs/fig_mle_MADN_noE.pdf}
+  \includegraphics[width=0.45\textwidth]{figs/fig_mle_MADN_noE.pdf}
   \caption{Distribution of ToFs in the multiscale modeled MADN system.
@@
 %
+
+When the energy disorder in MADN system is not considered, that is, all the MADN molecule energy are set to be equal giving $\Delta E=0$, the distribution of ToF is shown in Fig.\ref{fig:mle_MADN_noE}.
+The distribution $P(\log_{10}(\tau)|\lambda \text{ uncertain})$ has a range of confidence interval -9.6 to -9.0 resembles that of $P(\log_{10}(\tau)|\lambda, J_{ij} \text{ uncertain})$, which has a range of confidence interval -9.7 to -9.1.
+
+Measuring the sensitivity of each electronic parameter to ToF is to measure each electronic parameter's contribution to the variance of ToF. 
+That is, if ToF is most sensitive to one parameter, the variance in this particular parameter will contribute most to the ToF variance.
 
@@
 
-Then the $\lambda$ contribution to the total variance is $S_{T,i=1}$.
-The energy contribution to the total variance is $S_{T,E} = \sum\limits_{i=1}^{N+1} S_{T,i}$ where $N=1000$ is the number of energy parameter, and the coupling element contribution due to variation in $\log_{10}(J_{ij}^2)$ to the total variance is $S_{T,J}=\sum\limits_{i=N+2}^{N_d} S_{T,i}$.
-Using the quasi Monte Carlo method\cite{sobol_global_2001} with a sample size $N_\text{QMC}=1000$ to calculate $S_{T,i}$, the results are shown in the table \ref{tab:Sobol}.
 %
-%\begin{table}[H]
-%    \centering
-%    \begin{tabular}{c c c c }
-%        \toprule
-%        parameter & $\lambda$ & $E$ & $\log_{10} J^2$   \\
-%        \midrule
-%        $S_T$ & 0.097 & 0.95 & 0.018\\
-%        \bottomrule
-%    \end{tabular}
-%        \caption{Sobol indices of $\lambda$, $E$ and $\log_{10} J^2$.}
-%        \label{tab:Sobol}
-%\end{table}
-%
-
-\begin{table}[H]
-    \caption{Sobol indices of $\lambda$, $E$ and $\log_{10} J^2$ when ToF is calculated with energy disorder, and Sobol indices of $\lambda$ and $\log_{10} J^2$ when ToF is calculated without energy disorder.}\label{tab:Sobol}
+\begin{table}[tbp]%The best place to locate the table environment is directly after its first reference in text
+\caption{\label{tab:Sobol}%
+Sobol indices of $\lambda$, $E$ and $\log_{10} J^2$ when ToF is calculated with energy disorder, and Sobol indices of $\lambda$ and $\log_{10} J^2$ when ToF is calculated without energy disorder.
+}
+\begin{ruledtabular}
   \begin{center}
-      \begin{tabular}{c c c c c c c} \hline
+    \begin{tabular}{c c c c c c c} %\hline
       &  \multicolumn{3}{c}{\bf Energy Disorder} & &\multicolumn{2}{c}{\bf no Disorder}\\\cline{2-4}  \cline{6-7}
@@
    $S_T$  & 0.097 & 0.95 & 0.018 && 0.96 & 0.11 \\
-    \hline
     \end{tabular}
   \end{center}
+\end{ruledtabular}
 \end{table}
+%
+Then the $\lambda$ contribution to the total variance is $S_{T,i=1}$.
+The energy contribution to the total variance is $S_{T,E} = \sum\limits_{i=1}^{N+1} S_{T,i}$ where $N=1000$ is the number of energy parameter, and the coupling element contribution due to variation in $\log_{10}(J_{ij}^2)$ to the total variance is $S_{T,J}=\sum\limits_{i=N+2}^{N_d} S_{T,i}$.
+Using the quasi Monte Carlo method\cite{sobol_global_2001} with a sample size $N_\text{QMC}=1000$ to calculate $S_{T,i}$, the results are shown in the table \ref{tab:Sobol}.
 
@@
 
-\section{Distribution of Steady State Velocity}
-The distribution of steady state velocity of MADN is shown as Fig.\ref{fig:mle_MADN_withE_SS} and \ref{fig:mle_MADN_noE_SS}. 
-Those distribution shows that the variation in $v_\text{SS}$ distribution is greater than ToF distribution.
-
-\begin{figure}[H]
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+\begin{figure}
   \centering
-    \includegraphics[width=0.7\textwidth]{figs/fig_mle_MADN_withE_SS.pdf}
+  \includegraphics[width=0.45\textwidth]{figs/fig_mle_MADN_withE_SS.pdf}
   \caption{Distribution of steady state velocity $v_\text{SS}$ in the multiscale modeled MADN.
@@
 \end{figure}
-
-\begin{figure}[H]
+%
+%
+\begin{figure}
   \centering
-    \includegraphics[width=0.90\textwidth]{figs/fig_mle_MADN_noE_SS.pdf}
+  \includegraphics[width=0.45\textwidth]{figs/fig_mle_MADN_noE_SS.pdf}
   \caption{Distribution of steady state velocity $v_\text{SS}$ in the multiscale modeled MADN. All molecule energies are set to be zero.  
@@
 \end{figure}
+%
+\section{Distribution of Steady State Velocity}
+
+The distribution of steady state velocity of MADN is shown as Fig.\ref{fig:mle_MADN_withE_SS} and \ref{fig:mle_MADN_noE_SS}. 
+From the confidence interval, $P(\log_{10}(v_\text{SS})|E_i \text{ uncertain})$ has a range of -2.6 to -0.9, and the confidence interval $P(\log_{10}(v_\text{SS})|\lambda \text{ uncertain})$ has a range from -1.7 to -1.1.
+The width of those confidence intervals is very close to the confidence interval of distributions $P(\log_{10}(\tau)|E_i \text{ uncertain})$ and $P(\log_{10}(\tau)|\lambda \text{ uncertain})$, respectively.
+However, $P(\log_{10}(v_\text{SS})|J_{ij} \text{ uncertain})$ has a range from -1.6 to 1.3, spanning 3 orders of magnitude.
+This is  much larger than $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$ as shown in Fig .\ref{fig:mle_MADN_withE}.
+The large confidence interval in $P(\log_{10}(v_\text{SS})|J_{ij} \text{ uncertain})$ shows that $v_{ss}$ is very sensitive to the change in $J_{ij}$.
+Combining all the uncertainty effects in $E_i, \lambda, J_{ij}$, the confidence interval of $P(\log_{10}(v_\text{SS})|E_i, \lambda, J_{ij} \text{ uncertain})$ is from -2.5 to 1.3, covering 4 orders of magnitude.
+
+When energy disorder is not considered, the $v_\text{SS}$ distribution $P(\log_{10}(v_\text{SS})|\lambda, J_{ij} \text{ uncertain})$ has a confidence interval from 0.3 to 3.5, spanning 3 orders of magnitude.
+This interval is close to the range of $P(\log_{10}(v_\text{SS})|J_{ij} \text{ uncertain})$ when only $J_{ij}$ is uncertain.
+In contrast, the interval of $P(\log_{10}(v_\text{SS})|\lambda \text{ uncertain})$ is from 0.6 to 1.2, whose width is much smaller than that of $P(\log_{10}(v_\text{SS})|J_{ij} \text{ uncertain})$.
+
+These result suggests that compared to the ToF $\tau$, the quantity $v_\text{SS}$ is significantly affected by uncertainties in $J_{ij}$, so $v_\text{SS}$ is less robust when the parameters $E_i, \lambda, J_{ij}$ contains uncertainty at the same time.
+In the next section, the Poole–Frenkel behavior, that is the dependence of charge mobility on the electric field will be study using the ToF setting. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \section{Charge mobility and PF Behavior}
+
 In this section, we want to study the dependence of drift mobility on the HFX. The charge mobility is calculated as:
@@
 %
-\begin{figure}[H]
+\begin{figure}
     \centering
-    \includegraphics[width=1.05\textwidth]{figs/fig_mle_withE_mu2_ave.pdf}
+    \includegraphics[width=0.45\textwidth]{figs/fig_mle_withE_mu2_ave.pdf}
     \caption{Distribution of $\mu_\text{PF}$ in the multiscale modeled MADN system.
@@
 which is shown in Fig. \ref{fig:PF_plot_ave} for specifie HFX values. The 99\% confidence interval obtained via MC sampled in shown in the green shadow. 
+This interval suggests that if the uncertainties from the parameters are represented by the maximum likelihood distribution, the Poole–Frenkel plot from $\alpha=0$ has less 1\% chance to happen and thus is very likely.
 %
-\begin{figure}[H]
+\begin{figure}[tbp]
     \centering
-    \includegraphics[width=0.8\textwidth]{figs/fig_PF_plot_ave.pdf}
+    \includegraphics[width=0.45\textwidth]{figs/fig_PF_plot_ave.pdf}
     \caption{Electric-field dependence of the mobility $\mu$ in the multiscale modeled MADN system.
@@
 \end{figure}
-%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusion}
+The uncertainty effect from the exchange-correlation functional of the DFT on the multiscale model of OSC is studied.
+By choosing different HFX, the calculated values of some electronic structures remain very similar,
+such as the reorganization energy $\lambda$, molecular energy $E_i$ and the majority of the coupling elements  $J_{ij}$.
+While a few small-value coupling elements $J_{ij}$ show large different in calculated values when different HFX is used.
+Those uncertainties propagate to the output of the multiscale model, resulting in a range of QoI which has a maximum about 15 times of its minimum.
+These findings high-
+light the importance of selecting appropriate functionals to ensure model robustness.
+Also indicated is that for multiscale model charge mobility, when the values have difference is approximately 10\%, we should interpret the results with caution and refrain from concluding that they represent fundamentally different phenomena.
 
-\section{Conclusion}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Assuming the maximum amount of uncertainty from the calculated electronic structure parameters using the six HFX, the 99\% confidence level of the ToFs around the median are estimated.
+The Sobol indexes show that the molecular energy has the most contribution to the total variance, followed by the reorganization energy and coupling elements.
+Our results also shows that due to the uncertainties, the steady state velocity distribution spans 4 orders of magnitude.
+So it is less robust when
+the electronic structure parameters are uncertain, and a useful range of velocity is hard to obtain.
+Future research should explore the impact of other sources of uncertainty and extend this framework to different types of semiconducting materials, thus enhancing the predictive power and applicability of multiscale models in the field.
+% The \nocite command causes all entries in a bibliography to be printed out
+% whether or not they are actually referenced in the text. This is appropriate
+% for the sample file to show the different styles of references, but authors
+% most likely will not want to use it.
+\nocite{*}
 
-\bibliographystyle{unsrt}
-\bibliography{references}
+\bibliography{apssamp}% Produces the bibliography via BibTeX.
 
 \end{document}
+%
+% ****** End of file apssamp.tex ******

### 2024-11-14 apssamp.tex
update figure

@@
   \centering
-  \begin{tabular}{c c }
+  \begin{tabular}{c c c c }
   \hline
   \hline
-      $\alpha$ & ToF [s]  \\
+      $\alpha$ & & & ToF [s]  \\
   \hline
-      0.00 &  $7.5 \times 10^{-9}$ \\
-      0.05 & $ 8.1 \times 10^{-9}$ \\
-      0.10 & $ 1.6 \times 10^{-8}$ \\
-      0.15 & $ 3.1 \times 10^{-8}$ \\
-      0.20 & $ 2.5 \times 10^{-8}$ \\
-      0.25 & $ 9.7 \times 10^{-8}$ \\
+      0.00 & & &  $7.5 \times 10^{-9}$ \\
+      0.05 & & & $ 8.1 \times 10^{-9}$ \\
+      0.10 & & & $ 1.6 \times 10^{-8}$ \\
+      0.15 & & & $ 3.1 \times 10^{-8}$ \\
+      0.20 & & & $ 2.5 \times 10^{-8}$ \\
+      0.25 & & & $ 9.7 \times 10^{-8}$ \\
   \hline
@@
     Monte Carlo sampling with a sample size $N_\text{MC}=10000$ is used to obtain the sampled distribution.
-The red vertical lines indicate the lower bound and upper bound of the 99\% confidence interval around the median.}
+The red vertical lines indicate the lower bound and upper bound of the 99\% confidence interval around the median.
+(a) $|\vec{F}|=4 \times 10^7 \unit{V/m}$, (b) $|\vec{F}|=5 \times 10^7 \unit{V/m}$, (c) $|\vec{F}|=6 \times 10^7 \unit{V/m}$, (d) $|\vec{F}|=7 \times 10^7 \unit{V/m}$, (e) $|\vec{F}|=8 \times 10^7 \unit{V/m}$, (f) $|\vec{F}|=9 \times 10^7 \unit{V/m}$.}
     \label{fig:fig_mle_withE_mu2_ave}
@@
 %
+
+When the $\lambda, E_i, J_{ij}$ are uncertain and sampled from the normal distribution, the distributions of charge mobility obtained from MC sample under specific electric field are shown in Fig.
+\ref{fig:fig_mle_withE_mu2_ave}.
+The ToF depends on the electric field through the Marcus rate.
+As the electric increase from $|\vec{F}|=4 \times 10^7 \unit{V/m}$
+$|\vec{F}|=9 \times 10^7 \unit{V/m}$, the
+range of the 90\% confidence interval where $\log_{10} \mu_\text{PF}$ lies
+estimated from the MC sample decrease from -1.1 to 0.69.
+So the electric field results in a narrower range
+of $\mu_\text{PF}$ distribution, making the results more trustable.
 

### 2024-11-18 apssamp.tex
update reference

@@
 In this work, an investigated model containing uncertainties is the multiscale model of charge dynamics~\cite{Baumeier2011, edeling_global_2024,coropceanu_charge_2007} in organic semiconductors (OSCs), which are materials that consist of organic molecules with disordered and amorphous structure.
-Besides its semiconducting properties, they are mechanically flexible and comes with controllable charge transport properties.
-This flexible functionality is achieved by tuning molecular properties to achieve an ideal operating properties at the device-level, so a fundamental understanding of OSC from molecule scale  plays an important role in OSC optimization.
+Besides its semiconducting properties, they are mechanically flexible and comes with controllable charge transport properties~\cite{hamers_flexible_2001,liu_high_2015,chow_organic_2020}.
+This flexible functionality is achieved by tuning molecular properties to achieve an ideal operating properties at the device-level\cite{bronstein_role_2020, bredas_organic_2002}, so a fundamental understanding of OSC from molecule scale  plays an important role in OSC optimization.
 Conducting these optimization processes through experimental methods is financially demanding.
@@
 Fundamentally, quantum-mechanical description is needed to model charge dynamics due to the motion of electrons.
-However, the resulting full many-electron schr\"{o}dinger equation is impossible to solve due to its complexity, so Density Functional Theory (DFT) appears as a manageable way to model electrons.
+However, the resulting full many-electron schr\"{o}dinger equation is impossible to solve due to its complexity, so Density Functional Theory (DFT) \cite{kohn_selfconsistent_1965,jones_density_2015, hammesschiffer_conundrum_2017} appears as a manageable way to model electrons.
 DFT has its own challenges in achieving multiscale modeling.
-The first challenge relates to the Born-Oppenheimer approximation in quantum
+The first challenge relates to the Born-Oppenheimer approximation \cite{born_zur_1927} in quantum
 mechanics, which simplifies the problem by separating the electronic and nuclear
 coordinates.
-As a result, the time evolution of the atomic coordinates can be modeled in molecular dynamics (MD) by solving the Newton's equation using empirical force field to approximate the potential energy surfaces (need citation).
+As a result, the time evolution of the atomic coordinates can be modeled in molecular dynamics (MD) by solving the Newton's equation using empirical force field to approximate the potential energy surfaces~\cite{rapaport_art_2004}.
 
-The next challenge is the infeasibility of solving the DFT equations for the entire system even at a fixed time. 
+The next challenge is the infeasibility of solving the DFT equations for the entire system even at a fixed time~\cite{hammesschiffer_conundrum_2017}. 
 But due to fact that OSCs have disordered and amorphous structure and the quantum states of each molecule is confined to a limited region, the charge dynamic can be well-approxmiated as a jumping process between molecules, which is a continuous time random walk (CTRW) process.
@@
 In achieving the multiscale model, uncertainties are introduced. 
-While Born-Oppenheimer approximation allows for the use of force field to approximate the potential energy surfaces (need citation) and model the atomic coordinates using Newton’s equations, the force field is not exactly the same as the potential for DFT.
+While Born-Oppenheimer approximation allows for the use of force field to approximate the potential energy surfaces and model the atomic coordinates using Newton’s equations, the force field is not exactly the same as the potential for DFT~\cite{izvekov_effective_2004}.
 So the atomic coordinates, that is the molecule structures contain uncertainty which ultimately affects the charge dynamics. 
@@
 Lastly, the source of uncertain that this work focus on comes from the approximation for the exchange-correlation energy in DFT. 
-There is no exact formula for the exchange-correlation functional, so in practical approximations are developed and tested to guarantee the robustness of DFT method. 
+There is no exact formula for the exchange-correlation functional, so in practical approximations are developed and tested to guarantee the robustness of DFT method~\cite{gunnarsson_exchange_1976, bilc_hybrid_2008, lee_development_1988}.
 The accuracy of DFT depends heavily on the choice of the exchange-correlation functional whose suitability is usually unknown for new synthesized molecules. 
-As an advancement to improve accuracy, Hybrid-DFT incorporates a portion $\alpha$ of exact HF exchange functional (HFX) from Hartree-Fock (HF) theory into the exchange-correlation functional, particularly for systems where DFT falls short.
-For example, the PBE0 functional has a portion of 0.25 HFX.
+As an advancement to improve accuracy, Hybrid-DFT \cite{marques_densitybased_2011,perdew_rationale_1996} incorporates a portion $\alpha$ of exact HF exchange functional (HFX) from Hartree-Fock (HF) theory into the exchange-correlation functional, particularly for systems where DFT falls short.
+For example, the PBE0 functional has a portion of 0.25 HFX~\cite{adamo_toward_1999}.
 
 Looking back into the CTRW of the charge transport, the transition rates depend on the electronic structures parameters which rely on the validity of the exchange-correlation functional from the modeling perspectives.
-So the approximations in exchange-correlation functional will bring uncertainties to the multiscale model. 
+So the approximations in exchange-correlation functional will bring uncertainties to the multiscale model~\cite{medvedev_density_2017}. 
 In particular, different hybrid-DFT functionals containing varying HFX levels will generate different output from the multiscale model mentioned aboved. 

### 2024-11-18 apssamp.tex
clean up template

@@
  reprint,
-%superscriptaddress,
+superscriptaddress,
 %groupedaddress,
@@
 %pra,
-%prb,
+prb,
 %rmp,
@@
 %prstper,
-%floatfix,
+floatfix
 ]{revtex4-2}
@@
 \usepackage{units}
-\usepackage{lineno}
-\usepackage{float}
-\usepackage{amsmath}  % improve math presentation
-\usepackage{amsfonts}
-\usepackage{verbatim}
+%\usepackage{lineno}
+%\usepackage{float}
+%\usepackage{amsmath}  % improve math presentation
+%\usepackage{amsfonts}
+%\usepackage{verbatim}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\usepackage{hyperref}% add hypertext capabilities
+\usepackage{hyperref}% add hypertext capabilities
 %\usepackage[mathlines]{lineno}% Enable numbering of text and display math
@@
 
-\preprint{APS/123-QED}
+\title{Uncertainty Quantification in Multiscale Model}
 
-\title{Uncertainty Quantification in Multiscale Model}% Force line breaks with \\
-% \thanks{A footnote to the article title}%
-
-\author{Zhongquan Chen, Baumeier Bj\"orn, Pim van der Hoorn}
- \altaffiliation{Department of Mathematics and Computer Science \& Institute for Complex Molecular Systems, Eindhoven University of Technology},
+\author{Zhongquan Chen}
+\author{Pim van der Hoorn}
+\author{Bj\"orn Baumeier}
+\affiliation{Department of Mathematics and Computer Science \& Institute for Complex Molecular Systems, Eindhoven University of Technology}
 %Lines break automatically or can be forced with \\
@@
 As shown by Sobol indices, the QoI is most sensitive to molecule energy, then reorganization energy and least sensitive to coupling elements.
-\begin{description}
-\item[Usage]
-Secondary publications and information retrieval purposes.
-\item[Structure]
-You may use the \texttt{description} environment to structure your abstract;
-use the optional argument of the \verb+\item+ command to give the category of each item. 
-\end{description}
 \end{abstract}
@@
 
-\section{Background}
+\section{Introduction}
 
@@
 
-\begin{table}[H]
+\begin{table}[t]
   \caption{\label{tab:ToF_J} The ToF along a distance $L_x = 8$ [nm] of the MADN system as a function of the HFX. The molecular connections with coupling element $\log_{10} J^2_{ij} < 5$ are deleted.}
@@
 %
-\begin{figure}[H]
+\begin{figure}[t]
   \centering
@@
 % most likely will not want to use it.
-\nocite{*}
+%\nocite{*}
 

### 2024-11-18 apssamp.tex
add extracted Poole-Frenkel parameter table VI

@@
 The ToF depends on the electric field through the Marcus rate. 
-Poole and Frenkel predicted the electric-field dependence of charge mobility as $\mu_\text{PF}(F)=\mu_0 \exp (\beta \sqrt{|\vec{F}|})$.
+Poole and Frenkel \cite{frenkel_prebreakdown_1938} predicted the electric-field dependence of charge mobility as $\mu_\text{PF}(F)=\mu_0 \exp (\beta \sqrt{|\vec{F}|})$.
 So it is common to plot the mobility $\mu_\text{PF}$ against $\sqrt{|\vec{F}|}$ in a so-called Poole–Frenkel plot.
@@
 \end{figure}
+
+%
+\begin{table}[tbp]%The best place to locate the table environment is directly after its first reference in text
+  \caption{\label{tab:PF_parameter}%
+  Poole-Frenkel parameters $\mu_0$ (in $\unit[]{cm^2/(Vs)}$) and $\beta$ (in $\unit[]{\sqrt{cm/V}}$) of the multiscale modeled MADN, calculated by the six different HFX values. 
+  }
+  \begin{ruledtabular}
+    \begin{tabular}{c c c c c}
+    $\alpha$ & & $\mu_0$  & & $\beta$ \\
+      \hline
+    0 & & $4.0 \times 10^{-3}$ & & $1.0 \times 10^{-3}$ \\
+    0.05 & & $2.1 \times 10^{-3}$ & & $9.3 \times 10^{-4}$ \\
+    0.10 & & $1.0 \times 10^{-3}$ & & $1.5 \times 10^{-3}$ \\
+    0.15 & & $8.0 \times 10^{-4}$ & & $1.6 \times 10^{-3}$ \\
+    0.20 & & $9.3 \times 10^{-4}$ & & $1.3 \times 10^{-3}$ \\
+    0.20 & & $2.6 \times 10^{-4}$ & & $1.8 \times 10^{-3}$ \\
+      \end{tabular}
+  \end{ruledtabular}
+  \end{table}
+%  
+The extracted Poole–Frenkel paratermeter calculated from the six $\alpha$ values are summarized in Table \ref{tab:PF_parameter}. 
+Excluding the data of $\alpha=0$, the extracted zero-field mobility $\mu_0$ has a range from $2.6 \times 10^{-4}$ to $2.1 \times 10^{-3}$, and the field effect constant $\beta$ range from $9.3 \times 10^{-4}$ to $1.8 \times 10^{-3}$.
+So $\beta$ is less sensitive to the multiscale model parameter $\alpha$ compared the zero-field mobility.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2024-11-19 apssamp.tex
change comparison sentence in page 6

@@
 \caption{\label{tab:ToF_MADN_HFX}%
-The ToF and diffusive velocity calculated by ToF along a distance $L_x = 8$ [nm] with and without energy disorder of the MADN system as a function of the HFX.
-The ToF is in unit \unit[]{s} and $v_\text{ToF}$ in unit \unit[]{m/s}.
+The ToF and diffusive velocity calculated by ToF along a distance $L_x = \unit[9.0]{nm}$ with and without energy disorder of the MADN system as a function of the HFX.
+The ToF is in unit $\unit[]{s}$ and $v_\text{ToF}$ in unit $\unit[]{m/s}$.
 }
@@
     && W_1 (P_{E(\alpha=0)}, P_{E(\alpha=0.25)}) = \nonumber \\
-    && (\frac{1}{N} \sum\limits_{i=1}^N | E_{(i)}(\alpha=0) - E_{(i)}(\alpha=0.25) |)
+    && \frac{1}{N} \sum\limits_{i=1}^N | E_{(i)}(\alpha=0) - E_{(i)}(\alpha=0.25) |
 \end{eqnarray}
@@
 This quantity provides information of the amount of the largest variation one can expect in $E_i(\alpha)$. Index the molecule that has maximum $|E_i(\alpha=0.25) - E_i(\alpha')|$ to be $i'$. 
-If molecule $i'$ energy is the lowest one among the $N$ molecules, then a further lowering in the energy of molecule $i'$ may lead to large change in ToF, since low energy potentially lead to a trap in the charge transport dynamics.
+If molecule $i'$ energy is the lowest one among the $N$ molecules, then a further change (such as lowering) in the energy of molecule $i'$ may lead to large change in ToF, since low energy potentially lead to a trap in the charge transport dynamics and significantly affects the mobility.
 
-Table \ref{tab:maxEi} shows that depending on $\alpha'$, the maximum $|E_i(\alpha=0.25) - E_i(\alpha')|$ is 0.12 to 0.15, which is considerable small compared to the range of molecular energy and the magnitude of the energy disorder, which is around 0.08 as shown in Table \ref{tab:ToF_MADN_HFX}.
+Table \ref{tab:maxEi} shows that depending on $\alpha'$, the maximum $|E_i(\alpha=0.25) - E_i(\alpha')|$ is 0.12 to 0.15, which is considerable small compared to the range of molecular energy and the magnitude of the energy disorder, which is around 0.08 as shown in Fig.
+\ref{fig:autogen_MADN}.
 The energy of molecule $i'$ shown in Table \ref{tab:maxEi} indicates that the $i'$ molecule energy is not the lowest one in the system.
@@
 In the tested $\alpha'$ values, the second column shows the maximum of $E_i(\alpha=0.25) - E_i(\alpha')$ for all molecules.
-Denoting the index of the molecule which has maximum $E_i(\alpha=0.25) - E_i(\alpha')$ for the chosen $\alpha'$ case, the third column shows the energy of molecule $i'$ calculated by $\alpha=0.25$.
+Denoting $i'$ as the index of the molecule which has maximum $E_i(\alpha=0.25) - E_i(\alpha')$ for the chosen $\alpha'$, the third column shows the energy of molecule $i'$ calculated by $\alpha=0.25$.
 The fourth column shows the molecule energy $E_{i'}(\alpha')$ calculated by $\alpha'$.
-All the energies are in unit \unit[]{eV}.
+All the energies are in unit $\unit[]{eV}$.
 }
@@
 \begin{table}[t]
-  \caption{\label{tab:ToF_J} The ToF along a distance $L_x = 8$ [nm] of the MADN system as a function of the HFX. The molecular connections with coupling element $\log_{10} J^2_{ij} < 5$ are deleted.}
+  \caption{\label{tab:ToF_J} The ToF along a distance $L_x = 9 \unit[]{nm}$  of the MADN system as a function of the HFX.
+The molecular connections with coupling element $\log_{10} J^2_{ij} < 5$ are deleted.}
   \centering

### 2024-11-20 apssamp.tex
add reason why mobility of alpha=0 is outside the interval

@@
 range of the 90\% confidence interval where $\log_{10} \mu_\text{PF}$ lies
-estimated from the MC sample decrease from -1.1 to 0.69.
-So the electric field results in a narrower range
-of $\mu_\text{PF}$ distribution, making the results more trustable.
+estimated from the MC sample decrease from 0.90 to 0.69.
+So the electric field results in a narrower range of $\mu_\text{PF}$ distribution.
+Due to this reason, the $\mu_\text{PF}$ calculated from $\alpha=0$ is not in the 99\% confidence interval around the median of the MC sampled data, although the zero-field ToF of $\alpha=0$ is contained in the according 99\% confidence interval, as shown in Fig.
+\ref{fig:mle_MADN_withE}(d).
 

### 2024-11-26 paper.tex
renamed files

@@
-\documentclass[letterpaper,12pt]{article}
-\usepackage{tabularx} % extra features for tabular environment
-\usepackage{amsmath}  % improve math presentation
-\usepackage{amsfonts}
-\usepackage{verbatim}
-\usepackage{graphicx} % takes care of graphic including machinery
-\usepackage[margin=1in,letterpaper]{geometry} % decreases margins
-\usepackage{cite} % takes care of citations
-\usepackage[final]{hyperref} % adds hyper links inside the generated pdf file
+% ****** Start of file apssamp.tex ******
+%
+%   This file is part of the APS files in the REVTeX 4.2 distribution.
+%   Version 4.2a of REVTeX, December 2014
+%
+%   Copyright (c) 2014 The American Physical Society.
+%
+%   See the REVTeX 4 README file for restrictions and more information.
+%
+% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
+% as well as the rest of the prerequisites for REVTeX 4.2
+%
+% See the REVTeX 4 README file
+% It also requires running BibTeX. The commands are as follows:
+%
+%  1)  latex apssamp.tex
+%  2)  bibtex apssamp
+%  3)  latex apssamp.tex
+%  4)  latex apssamp.tex
+%
+\documentclass[%
+ reprint,
+superscriptaddress,
+%groupedaddress,
+%unsortedaddress,
+%runinaddress,
+%frontmatterverbose, 
+%preprint,
+%preprintnumbers,
+%nofootinbib,
+%nobibnotes,
+%bibnotes,
+ amsmath,amssymb,
+ aps,
+%pra,
+prb,
+%rmp,
+%prstab,
+%prstper,
+floatfix
+]{revtex4-2}
 
-\usepackage{booktabs}
+\usepackage{graphicx}% Include figure files
+\usepackage{dcolumn}% Align table columns on decimal point
+\usepackage{bm}% bold math
+%%%%%%%%%%%%%%%%%%%%%%%%%package by Zhong
+\usepackage{units}
+%\usepackage{lineno}
+%\usepackage{float}
+%\usepackage{amsmath}  % improve math presentation
+%\usepackage{amsfonts}
+%\usepackage{verbatim}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\usepackage{hyperref}% add hypertext capabilities
+%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
+%\linenumbers\relax % Commence numbering lines
 
-\hypersetup{
-	colorlinks=true,       % false: boxed links; true: colored links
-	linkcolor=blue,        % color of internal links
-	citecolor=blue,        % color of links to bibliography
-	filecolor=magenta,     % color of file links
-	urlcolor=blue         
-}
-\usepackage{blindtext}
-
-\usepackage{units}
-\usepackage{lineno}
-\usepackage{comment}
-\usepackage{float}
-%++++++++++++++++++++++++++++++++++++++++
+%\usepackage[showframe,%Uncomment any one of the following lines to test 
+%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
+%%text={7in,10in},centering,
+%%margin=1.5in,
+%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
+%%height=10in,a5paper,hmargin={3cm,0.8in},
+%]{geometry}
 
 \begin{document}
-\linenumbers
-\title{Uncertainty Quantification in Multiscale Model }
-\author{authors}
-\date{\today}
-\maketitle
+
+\title{Uncertainty Quantification in Multiscale Model}
+
+\author{Zhongquan Chen}
+\author{Pim van der Hoorn}
+\author{Bj\"orn Baumeier}
+\affiliation{Department of Mathematics and Computer Science \& Institute for Complex Molecular Systems, Eindhoven University of Technology}
+%Lines break automatically or can be forced with \\
+
+% \collaboration{MUSO Collaboration}%\noaffiliation
+
+%\collaboration{CLEO Collaboration}%\noaffiliation
+
+\date{\today}% It is always \today, today,
+             %  but any date may be explicitly specified
+
 \begin{abstract}
   This work quantifies uncertainties in a multiscale model for charge dynamics in organic semiconductors (OSCs).
-A first-principle multiscale model integrates classical molecular dynamics (MD), density functional theory (DFT), and continuous-time random walk (CTRW) processes to allow the simulation of charge transport in OSCs.
+A first-principle multiscale model integrates classical molecular dynamics (MD), density functional theory (DFT), quantum mechanical calculation and continuous-time random walk (CTRW) processes to allow the simulation of charge transport in OSCs.
 The model brings inherent uncertainties arising from the empirical approximations and numerical simulations.
@@
 
-\section{Background}
+%\keywords{Suggested keywords}%Use showkeys class option if keyword
+                              %display desired
+\maketitle
+
+%\tableofcontents
+
+\section{Introduction}
 
 Theoretical model and computer simulation for understanding a physical system usually contain some uncertainties in predicting the system features. 
-For example, the theoretical model does not encompass all relevant physical factors, the theoretical model incorporates empirical parameters that include noise, the numerical scheme contains approximation, the simulation use noisy quantities, etc.
+For example, the theoretical model does not encompass all relevant physical factors, the theoretical model incorporates empirical parameters that include noise, the numerical scheme contains approximation, the simulation use noisy quantities, etc~\cite{sarkar_uncertainty_2017,oconnor_quantifying_2024, chernatynskiy_uncertainty_2013, suleimenova_tutorial_2021,coveney_reliability_2021, coveney_when_2021}.
 Nevertheless, those uncertainties should not affect the validity of the model or the accuracy for the predicting system in terms of some quantities of interest (QoI). 
@@
 
-In this work, an investigated model containing uncertainties is the multiscale model of charge dynamics in organic semiconductors (OSCs), which are materials that consist of organic molecules with disordered and amorphous structure.
-Besides its semiconducting properties, tthey are mechanically flexible and comes with controllable charge transport properties.
-This flexible functionality is achieved by tuning molecular properties to achieve an ideal operating properties at the device-level, so a fundamental understanding of OSC from molecule scale  plays an important role in OSC optimization.
+In this work, an investigated model containing uncertainties is the multiscale model of charge dynamics~\cite{Baumeier2011, edeling_global_2024,coropceanu_charge_2007} in organic semiconductors (OSCs), which are materials that consist of organic molecules with disordered and amorphous structure.
+Besides its semiconducting properties, they are mechanically flexible and comes with controllable charge transport properties~\cite{hamers_flexible_2001,liu_high_2015,chow_organic_2020}.
+This flexible functionality is achieved by tuning molecular properties to achieve an ideal operating properties at the device-level\cite{bronstein_role_2020, bredas_organic_2002}, so a fundamental understanding of OSC from molecule scale  plays an important role in OSC optimization.
 Conducting these optimization processes through experimental methods is financially demanding.
@@
 
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.9\textwidth]{figs/MSM.pdf}
+  \caption{The multiscale model workflow for OSC.
+Step 1: MD simulation to generate atom coordinates.
+Step 2: Molecule energy $E_i$ calculation.
+Step 3: Calculation of Reorganization energy $\lambda_{ij}$ and coupling element $J_{ij}$ for pairs of molecule $i,j$ whose COM distance is less than $r_\text{cutoff}$.
+Step 4: Modelling dynamics on device level, such as ToF calculation.}
+  \label{fig:MSM}
+\end{figure*}
+
 Fundamentally, quantum-mechanical description is needed to model charge dynamics due to the motion of electrons.
-However, the resulting full many-electron schr\"{o}dinger equation is impossible to solve due to its complexity, so Density Functional Theory (DFT) appears as a manageable way to model electrons.
+However, the resulting full many-electron schr\"{o}dinger equation is impossible to solve due to its complexity, so Density Functional Theory (DFT) \cite{kohn_selfconsistent_1965,jones_density_2015, hammesschiffer_conundrum_2017} appears as a manageable way to model electrons.
 DFT has its own challenges in achieving multiscale modeling.
-The first challenge relates to the Born-Oppenheimer approximation in quantum
+The first challenge relates to the Born-Oppenheimer approximation \cite{born_zur_1927} in quantum
 mechanics, which simplifies the problem by separating the electronic and nuclear
 coordinates.
-As a result, the time evolution of the atomic coordinates can be modeled in molecular dynamics (MD) by solving the Newton's equation using empirical force field to approximate the potential energy surfaces (need citation).
+As a result, the time evolution of the atomic coordinates can be modeled in molecular dynamics (MD) by solving the Newton's equation using empirical force field to approximate the potential energy surfaces~\cite{rapaport_art_2004}.
 
-The next challenge is the infeasibility of solving the DFT equations for the entire system even at a fixed time. 
+The next challenge is the infeasibility of solving the DFT equations for the entire system even at a fixed time~\cite{hammesschiffer_conundrum_2017}. 
 But due to fact that OSCs have disordered and amorphous structure and the quantum states of each molecule is confined to a limited region, the charge dynamic can be well-approxmiated as a jumping process between molecules, which is a continuous time random walk (CTRW) process.
@@
 
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.99\textwidth]{figs/MSM.pdf}
-    \caption{The multiscale model workflow for OSC.
-Step 1: MD simulation to generate atom coordinates.
-Step 2: Molecule energy $E_i$ calculation.
-Step 3: Calculation of Reorganization energy $\lambda_{ij}$ and coupling element $J_{ij}$ for pairs of molecule $i,j$ whose COM distance is less than $r_\text{cutoff}$.
-Step 4: Modelling dynamics on device level, such as ToF calculation.}
-    \label{fig:MSM}
-\end{figure}
-
 In achieving the multiscale model, uncertainties are introduced. 
-While Born-Oppenheimer approximation allows for the use of force field to approximate the potential energy surfaces (need citation) and model the atomic coordinates using Newton’s equations, the force field is not exactly the same as the potential for DFT.
+While Born-Oppenheimer approximation allows for the use of force field to approximate the potential energy surfaces and model the atomic coordinates using Newton’s equations, the force field is not exactly the same as the potential for DFT~\cite{izvekov_effective_2004}.
 So the atomic coordinates, that is the molecule structures contain uncertainty which ultimately affects the charge dynamics. 
@@
 
-\begin{table}[H]
-    \centering
+\begin{table}[tbp]%The best place to locate the table environment is directly after its first reference in text
+\caption{\label{tab:ToF_MADN_HFX}%
+The ToF and diffusive velocity calculated by ToF along a distance $L_x = \unit[9.0]{nm}$ with and without energy disorder of the MADN system as a function of the HFX.
+The ToF is in unit $\unit[]{s}$ and $v_\text{ToF}$ in unit $\unit[]{m/s}$.
+}
+\begin{ruledtabular}
   \begin{tabular}{c c c c c}
-    \hline
-        $\alpha$ & ToF [s] & $v_\text{ToF}$ [m/s] & ToF(no $E$) [s] & $v_\text{ToF}$ (no $E$) [m/s] \\
+        $\alpha$ & ToF& $v_\text{ToF}$ & ToF(no $E$)& $v_\text{ToF}$(no $E$) \\
     \hline
@@
   \label{fig:E_qmmm_MADN}
-\end{figure}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.80\textwidth]{figs/scatterEstat_qmmm.pdf}
+  \caption{Scatter plot of MADN electrostatic energy calculated from different HFX, compared to the electrostatic energy calculated from HFX=0.25 (The PBE0 functional).
+The brighter color near the diagonal lines indicates denser population of the molecules.
+The top and right histogram show the energy distributions.}
+  \label{fig:Estat_qmmm_MADN}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.80\textwidth]{figs/scatterEdip_qmmm.pdf}
+  \caption{Scatter plot of MADN polarization energy calculated from different HFX, compared to the polarization energy calculated from HFX=0.25 (The PBE0 functional).
+The brighter color near the diagonal lines indicates denser population of the molecules.
+The top and right histogram show the energy distributions.}
+  \label{fig:Edip_qmmm_MADN}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.80\textwidth]{figs/scatterJ_all.pdf}
+  \caption{Scatter plot of MADN coupling element $\log_{10} J^2$ calculated from different HFX, compared to the polarization energy calculated from HFX=0.25 (The PBE0 functional).
+The brighter color near the diagonal lines indicates denser population of the molecules.
+The top and right histogram show the energy distributions.}
+  \label{fig:J_MADN}
+\end{figure*}
+
+Figure \ref{fig:E_qmmm_MADN} presents a scatter plot comparing the site energies of MADN molecules across different HFX values, using $\alpha$ = 0.25 (PBE0 functional) as a reference for which the calculated molecule energy has a range from -1.17 to -0.60 \unit[]{eV}y.
+The range of molecule energy for the other five HFX are: 
+from -1.11 to -0.59 \unit[]{eV} for $\alpha=0$, 
+from -1.07 to -0.63 \unit[]{eV} for $\alpha=0.05$, 
+from -1.13 to -0.61 \unit[]{eV} for $\alpha=0.10$
+from -1.16 to -0.60 \unit[]{eV} for $\alpha=0.15$, 
+and from -1.12 to -0.63 \unit[]{eV} for $\alpha=0.20$.
+The bright-yellow color in all plots of Fig.
+\ref{fig:E_qmmm_MADN} indicates that most data points are clustering near the diagonal line, so the molecular energies calculated by different HFX are very close.
+
+To quantify the similarity between two empirical distribution, Wasserstein distance~\cite{villani_optimal_2009} is used.
+Denote the empirical distribution of molecular energy $E$ at $\alpha=0$ to be $P_{E(\alpha=0)}$. 
+The 1-Wasserstein distance between $P_{E(\alpha=0)}$ and $P_{E(\alpha=0.25)}$ is calculated as:
+\begin{eqnarray}
+    && W_1 (P_{E(\alpha=0)}, P_{E(\alpha=0.25)}) = \nonumber \\
+    && \frac{1}{N} \sum\limits_{i=1}^N | E_{(i)}(\alpha=0) - E_{(i)}(\alpha=0.25) |
+\end{eqnarray}
+where $E_{(i)}(\alpha=0)$ is the order statistics of $E_i(\alpha=0)$.
+The 1-Wasserstein distance between two empirical distributions for each plot in Fig.
+\ref{fig:E_qmmm_MADN} is shown in Table \ref{tab:W2_E}.
+$W_1 (P_{E(\alpha=0)}, P_{E(\alpha=0.25)})$ has range between 0.0045 to 0.0091, indicating that the molecular energy distributions are very similar.
 
@@
 This quantity provides information of the amount of the largest variation one can expect in $E_i(\alpha)$. Index the molecule that has maximum $|E_i(\alpha=0.25) - E_i(\alpha')|$ to be $i'$. 
-If molecule $i'$ energy is the lowest one among the $N$ molecules, then a further lowering in the energy of molecule $i'$ may lead to large change in ToF, since low energy potentially lead to a trap in the charge transport dynamics.
+If molecule $i'$ energy is the lowest one among the $N$ molecules, then a further change (such as lowering) in the energy of molecule $i'$ may lead to large change in ToF, since low energy potentially lead to a trap in the charge transport dynamics and significantly affects the mobility.
+
+Table \ref{tab:maxEi} shows that depending on $\alpha'$, the maximum $|E_i(\alpha=0.25) - E_i(\alpha')|$ is 0.12 to 0.15, which is considerable small compared to the range of molecular energy and the magnitude of the energy disorder, which is around 0.08 as shown in Fig.
+\ref{fig:autogen_MADN}.
+The energy of molecule $i'$ shown in Table \ref{tab:maxEi} indicates that the $i'$ molecule energy is not the lowest one in the system.
+So the maximum energy variation quantified by $\max(|E_i(\alpha=0.25) - E_i(\alpha')|)$ is not likely to results in large change in ToF due to trapping effects.
 %
-\begin{table}[H]
-    \centering
+\begin{table}[tbp]%The best place to locate the table environment is directly after its first reference in text
+\caption{\label{tab:maxEi}%
+In the tested $\alpha'$ values, the second column shows the maximum of $E_i(\alpha=0.25) - E_i(\alpha')$ for all molecules.
+Denoting $i'$ as the index of the molecule which has maximum $E_i(\alpha=0.25) - E_i(\alpha')$ for the chosen $\alpha'$, the third column shows the energy of molecule $i'$ calculated by $\alpha=0.25$.
+The fourth column shows the molecule energy $E_{i'}(\alpha')$ calculated by $\alpha'$.
+All the energies are in unit $\unit[]{eV}$.
+}
+\begin{ruledtabular}
   \begin{tabular}{c c c c}
-    \hline
   $\alpha'$ & $\max(|E_i(\alpha=0.25) - E_i(\alpha')|)$  & $E_{i'}(\alpha=0.25)$ & $E_{i'}(\alpha')$ \\
@@
 \end{figure}
+
+\begin{table}[t]
+  \caption{\label{tab:ToF_J} The ToF along a distance $L_x = 9 \unit[]{nm}$  of the MADN system as a function of the HFX.
+The molecular connections with coupling element $\log_{10} J^2_{ij} < 5$ are deleted.}
+  \centering
+  \begin{tabular}{c c c c }
+  \hline
+  \hline
+      $\alpha$ & & & ToF [s]  \\
+  \hline
+      0.00 & & &  $7.5 \times 10^{-9}$ \\
+      0.05 & & & $ 8.1 \times 10^{-9}$ \\
+      0.10 & & & $ 1.6 \times 10^{-8}$ \\
+      0.15 & & & $ 3.1 \times 10^{-8}$ \\
+      0.20 & & & $ 2.5 \times 10^{-8}$ \\
+      0.25 & & & $ 9.7 \times 10^{-8}$ \\
+  \hline
+  \hline
+  \end{tabular}
+\end{table}
+
 After performing percolation algorithm, Figure \ref{fig:J_percolate} shows the dependence of $\max({N_\text{sub}})$ on the critical value $J_c$.
-When $\log_{10} J_c^2 < -4.5$, $\max({N_\text{sub}})$ is 1000, meaning that removing all the edges with $J^2 < 3.1 \times 10^{-5}$ the 1000 vertexes still form a connected graph.
-But when removing the edges with $J^2 < 3.1 \times 10^{-4}$ ( corresponding to $J_c > -3.5$), the maximum size subgraph is 600, and it quickly decreases as $J_c$ increases, showing a phase transition.
-So the dominated coupling elements are those with $\log_{10} J_c^2 > -4.5$. 
-And the variation in small $J$ due to HFX has less impact on the charge dynamics.
+When $\log_{10} J_c^2 < 5$, $\max({N_\text{sub}})$ is 1000, meaning that removing all the edges with $J_{ij}^2 < 1 \times 10^{-5}$ the 1000 vertexes still form a connected graph.
+But when removing the edges with $J_{ij}^2 < 3.1 \times 10^{-4}$ ( corresponding to $J_c > -3.5$), the maximum size subgraph is 600, and it quickly decreases as $J_c$ increases, showing a phase transition.
+So the dominated coupling elements are those with $\log_{10} J_c^2 > -5$. 
+And the variation in small $J_{ij}$ due to HFX has less impact on the charge dynamics.
+Table \ref{tab:ToF_J} shows the ToF for the MADN system after deleting the molecular connections with  $\log_{10} J_c^2 < -5$.
+The resulting ToF is close to the values obtained without deleting any connections (shown in Table \ref{tab:ToF_MADN_HFX}).
+The increase of ToF after deleting the connections with  $\log_{10} J_c^2 < -5$ is always less than 30\%, confirming that the molecular connections with the small $J_{ij}$ has small effect in ToF.
 
-In this section we answer the question of how does HF level change the electronic structures and 
-how does HF level change the charge mobility. 
-In the next section, uncertainty quantification via Monte Carlo method and sensitivity analysis is perform to answer which electronic structure (among energy, coupling element and reorganization energy) uncertainty has the most impact on the charge mobility distribution.
+In this section we answer the question of how does HF level change the electronic structures ($\lambda, E_i, J_{ij}$) and 
+how does HF level change the ToF. 
+In the next section, uncertainty quantification via Monte Carlo method and sensitivity analysis is performed to answer which electronic structure (among energy, coupling element and reorganization energy) uncertainty has the most impact on the ToF distribution.
 And further we estimate the range of the quantity of interest, given a confidence level.
@@
 Figure .\ref{fig:mle_MADN_withE}(b) shows that $\log_{10}(\tau)$ has a confidence interval of -8.0 to -7.4 when $\lambda$ is varied. 
-Figure \ref{fig:mle_MADN_withE}(c) show that when $J_{ij}$ is uncertain $\log_{10}(\tau)$ has a sharp confidence interval of -7.9 to -7.7, suggesting that the variation in $J_{ij}$ leads to relatively small change in $\log_{10}(\tau)$ compared to $E_i$ and $\lambda$.
-%
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.70\textwidth]{figs/fig_mle_MADN_withE.pdf}
-    \caption{Distribution of ToFs in the multiscale modeled MADN system.
-    Monte Carlo sampling with a sample size $N_\text{MC}=50000$ is used to obtain the sampled distribution.
-The red vertical lines indicate the lower bound and upper bound of the 99\% confidence interval around the median.
-    The black circles indicate the ToF obtained using varying HFX values.
-    (a) $P(\log_{10}(\tau)|E_i \text{ uncertain})$, 
-    (b) $P(\log_{10}(\tau)|\lambda \text{ uncertain})$, 
-    (c) $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$, 
-    (d) $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$. }
-    \label{fig:mle_MADN_withE}
-\end{figure}
-%
-
-% The 90\% confidence interval of each distribution and the fitted Gamma distribution is summarized in table 
-When the energy disorder in MADN system is not considered, that is, all the MADN molecule energy are set to be equal giving $\Delta E=0$, the distribution of ToF is shown in Fig.\ref{fig:mle_MADN_noE}
-
-Measuring the sensitivity of each electronic parameter to ToF is to measure each electronic parameter's contribution to the variance of ToF. 
-That is, if ToF is most sensitive to one parameter, the variance in this particular parameter will contribute most to the ToF variance.
+Figure \ref{fig:mle_MADN_withE}(c) show that when $J_{ij}$ is uncertain $\log_{10}(\tau)$ has a narrow confidence interval of -7.9 to -7.7, suggesting that the variation in $J_{ij}$ leads to relatively small change in $\log_{10}(\tau)$ compared to $E_i$ and $\lambda$.
 
 %
-\begin{figure}[H]
+\begin{figure}[t]
   \centering
-    \includegraphics[width=0.99\textwidth]{figs/fig_mle_MADN_noE.pdf}
+  \includegraphics[width=0.45\textwidth]{figs/fig_mle_MADN_noE.pdf}
   \caption{Distribution of ToFs in the multiscale modeled MADN system.
@@
 %
-\begin{figure}[H]
+\begin{figure}
     \centering
-    \includegraphics[width=1.05\textwidth]{figs/fig_mle_withE_mu2_ave.pdf}
+    \includegraphics[width=0.45\textwidth]{figs/fig_mle_withE_mu2_ave.pdf}
     \caption{Distribution of $\mu_\text{PF}$ in the multiscale modeled MADN system.
     Monte Carlo sampling with a sample size $N_\text{MC}=10000$ is used to obtain the sampled distribution.
-The red vertical lines indicate the lower bound and upper bound of the 99\% confidence interval around the median.}
+The red vertical lines indicate the lower bound and upper bound of the 99\% confidence interval around the median.
+(a) $|\vec{F}|=4 \times 10^7 \unit{V/m}$, (b) $|\vec{F}|=5 \times 10^7 \unit{V/m}$, (c) $|\vec{F}|=6 \times 10^7 \unit{V/m}$, (d) $|\vec{F}|=7 \times 10^7 \unit{V/m}$, (e) $|\vec{F}|=8 \times 10^7 \unit{V/m}$, (f) $|\vec{F}|=9 \times 10^7 \unit{V/m}$.}
     \label{fig:fig_mle_withE_mu2_ave}
@@
 
+When the $\lambda, E_i, J_{ij}$ are uncertain and sampled from the normal distribution, the distributions of charge mobility obtained from MC sample under specific electric field are shown in Fig.
+\ref{fig:fig_mle_withE_mu2_ave}.
 The ToF depends on the electric field through the Marcus rate.
-Poole and Frenkel predicted the electric-field dependence of charge mobility as $\mu_\text{PF}(F)=\mu_0 \exp (\beta \sqrt{|\vec{F}|})$.
+As the electric increase from $|\vec{F}|=4 \times 10^7 \unit{V/m}$
+$|\vec{F}|=9 \times 10^7 \unit{V/m}$, the
+range of the 90\% confidence interval where $\log_{10} \mu_\text{PF}$ lies
+estimated from the MC sample decrease from 0.90 to 0.69.
+So the electric field results in a narrower range of $\mu_\text{PF}$ distribution.
+Due to this reason, the $\mu_\text{PF}$ calculated from $\alpha=0$ is not in the 99\% confidence interval around the median of the MC sampled data, although the zero-field ToF of $\alpha=0$ is contained in the according 99\% confidence interval, as shown in Fig.
+\ref{fig:mle_MADN_withE}(d).
+
+The ToF depends on the electric field through the Marcus rate. 
+Poole and Frenkel \cite{frenkel_prebreakdown_1938} predicted the electric-field dependence of charge mobility as $\mu_\text{PF}(F)=\mu_0 \exp (\beta \sqrt{|\vec{F}|})$.
 So it is common to plot the mobility $\mu_\text{PF}$ against $\sqrt{|\vec{F}|}$ in a so-called Poole–Frenkel plot.
 which is shown in Fig. \ref{fig:PF_plot_ave} for specifie HFX values. The 99\% confidence interval obtained via MC sampled in shown in the green shadow. 
+This interval suggests that if the uncertainties from the parameters are represented by the maximum likelihood distribution, the Poole–Frenkel plot from $\alpha=0$ has less 1\% chance to happen and thus is very likely.
 %
-\begin{figure}[H]
+\begin{figure}[tbp]
     \centering
-    \includegraphics[width=0.8\textwidth]{figs/fig_PF_plot_ave.pdf}
+    \includegraphics[width=0.45\textwidth]{figs/fig_PF_plot_ave.pdf}
     \caption{Electric-field dependence of the mobility $\mu$ in the multiscale modeled MADN system.
@@
 \end{figure}
+
 %
+\begin{table}[tbp]%The best place to locate the table environment is directly after its first reference in text
+  \caption{\label{tab:PF_parameter}%
+  Poole-Frenkel parameters $\mu_0$ (in $\unit[]{cm^2/(Vs)}$) and $\beta$ (in $\unit[]{\sqrt{cm/V}}$) of the multiscale modeled MADN, calculated by the six different HFX values. 
+  }
+  \begin{ruledtabular}
+    \begin{tabular}{c c c c c}
+    $\alpha$ & & $\mu_0$  & & $\beta$ \\
+      \hline
+    0 & & $4.0 \times 10^{-3}$ & & $1.0 \times 10^{-3}$ \\
+    0.05 & & $2.1 \times 10^{-3}$ & & $9.3 \times 10^{-4}$ \\
+    0.10 & & $1.0 \times 10^{-3}$ & & $1.5 \times 10^{-3}$ \\
+    0.15 & & $8.0 \times 10^{-4}$ & & $1.6 \times 10^{-3}$ \\
+    0.20 & & $9.3 \times 10^{-4}$ & & $1.3 \times 10^{-3}$ \\
+    0.20 & & $2.6 \times 10^{-4}$ & & $1.8 \times 10^{-3}$ \\
+      \end{tabular}
+  \end{ruledtabular}
+  \end{table}
+%  
+The extracted Poole–Frenkel paratermeter calculated from the six $\alpha$ values are summarized in Table \ref{tab:PF_parameter}. 
+Excluding the data of $\alpha=0$, the extracted zero-field mobility $\mu_0$ has a range from $2.6 \times 10^{-4}$ to $2.1 \times 10^{-3}$, and the field effect constant $\beta$ range from $9.3 \times 10^{-4}$ to $1.8 \times 10^{-3}$.
+So $\beta$ is less sensitive to the multiscale model parameter $\alpha$ compared the zero-field mobility.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusion}
+The uncertainty effect from the exchange-correlation functional of the DFT on the multiscale model of OSC is studied.
+By choosing different HFX, the calculated values of some electronic structures remain very similar,
+such as the reorganization energy $\lambda$, molecular energy $E_i$ and the majority of the coupling elements  $J_{ij}$.
+While a few small-value coupling elements $J_{ij}$ show large different in calculated values when different HFX is used.
+Those uncertainties propagate to the output of the multiscale model, resulting in a range of QoI which has a maximum about 15 times of its minimum.
+These findings high-
+light the importance of selecting appropriate functionals to ensure model robustness.
+Also indicated is that for multiscale model charge mobility, when the values have difference is approximately 10\%, we should interpret the results with caution and refrain from concluding that they represent fundamentally different phenomena.
 
-\section{Conclusion}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Assuming the maximum amount of uncertainty from the calculated electronic structure parameters using the six HFX, the 99\% confidence level of the ToFs around the median are estimated.
+The Sobol indexes show that the molecular energy has the most contribution to the total variance, followed by the reorganization energy and coupling elements.
+Our results also shows that due to the uncertainties, the steady state velocity distribution spans 4 orders of magnitude.
+So it is less robust when
+the electronic structure parameters are uncertain, and a useful range of velocity is hard to obtain.
+Future research should explore the impact of other sources of uncertainty and extend this framework to different types of semiconducting materials, thus enhancing the predictive power and applicability of multiscale models in the field.
+% The \nocite command causes all entries in a bibliography to be printed out
+% whether or not they are actually referenced in the text. This is appropriate
+% for the sample file to show the different styles of references, but authors
+% most likely will not want to use it.
+%\nocite{*}
 
-\bibliographystyle{unsrt}
-\bibliography{references}
+\bibliography{references}% Produces the bibliography via BibTeX.
 
 \end{document}
+%
+% ****** End of file apssamp.tex ******

### 2024-11-27 paper.tex
comments with figure changes required

@@
-% ****** Start of file apssamp.tex ******
-%
-%   This file is part of the APS files in the REVTeX 4.2 distribution.
-%   Version 4.2a of REVTeX, December 2014
-%
-%   Copyright (c) 2014 The American Physical Society.
-%
-%   See the REVTeX 4 README file for restrictions and more information.
-%
-% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
-% as well as the rest of the prerequisites for REVTeX 4.2
-%
-% See the REVTeX 4 README file
-% It also requires running BibTeX. The commands are as follows:
-%
-%  1)  latex apssamp.tex
-%  2)  bibtex apssamp
-%  3)  latex apssamp.tex
-%  4)  latex apssamp.tex
-%
 \documentclass[%
@@
 \usepackage{hyperref}% add hypertext capabilities
-%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
-%\linenumbers\relax % Commence numbering lines
+\usepackage{xcolor}
 
-%\usepackage[showframe,%Uncomment any one of the following lines to test 
-%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
-%%text={7in,10in},centering,
-%%margin=1.5in,
-%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
-%%height=10in,a5paper,hmargin={3cm,0.8in},
-%]{geometry}
+\newcommand{\bjoern}[2]{{\color{blue}{{\bf #1} #2}}}
 
@@
 
-\title{Uncertainty Quantification in Multiscale Model}
+\title{Uncertainty Quantification in Multiscale Model\bjoern{Needs}{new title}}
 
@@
 \affiliation{Department of Mathematics and Computer Science \& Institute for Complex Molecular Systems, Eindhoven University of Technology}
-%Lines break automatically or can be forced with \\
 
-% \collaboration{MUSO Collaboration}%\noaffiliation
-
-%\collaboration{CLEO Collaboration}%\noaffiliation
-
-\date{\today}% It is always \today, today,
-             %  but any date may be explicitly specified
+\date{\today}
 
@@
 \section{Introduction}
-
+\bjoern{UQ in general}{}
 Theoretical model and computer simulation for understanding a physical system usually contain some uncertainties in predicting the system features. 
@@
 
-In this work, an investigated model containing uncertainties is the multiscale model of charge dynamics~\cite{Baumeier2011, edeling_global_2024,coropceanu_charge_2007} in organic semiconductors (OSCs), which are materials that consist of organic molecules with disordered and amorphous structure.
+\bjoern{Intro OSCs}{}In this work, an investigated model containing uncertainties is the multiscale model of charge dynamics~\cite{Baumeier2011, edeling_global_2024,coropceanu_charge_2007} in organic semiconductors (OSCs), which are materials that consist of organic molecules with disordered and amorphous structure.
 Besides its semiconducting properties, they are mechanically flexible and comes with controllable charge transport properties~\cite{hamers_flexible_2001,liu_high_2015,chow_organic_2020}.
@@
 
-Like every other models, the multiscale model contains uncertainties due to certain approximation in modeling perspective, the randomness nature of the physical quantities, and the limitation of the numerical simulations, only to name a few.
+\bjoern{Idea of the Multiscale Model}{}Like every other models, the multiscale model contains uncertainties due to certain approximation in modeling perspective, the randomness nature of the physical quantities, and the limitation of the numerical simulations, only to name a few.
 To explain in detail those uncertainties, the first-principle multiscale model is briefly reviewed.
 
-\begin{figure*}
+\begin{figure*}[tbp]
   \centering
-  \includegraphics[width=0.9\textwidth]{figs/MSM.pdf}
-  \caption{The multiscale model workflow for OSC.
+  \includegraphics[width=\linewidth]{figs/MSM2.pdf}
+  \caption{\bjoern{TODO Bjoern}{Rewrite caption}The multiscale model workflow for OSC.
 Step 1: MD simulation to generate atom coordinates.
@@
 
+\bjoern{Uncertainties in the MSM}{way too verbose}
 In achieving the multiscale model, uncertainties are introduced. 
@@
 However, the amorphous OSCs used in this work has strong disorder, so the model noise from state localization is negligible and we do not consider the uncertainty originated from this perspective.
-Lastly, the source of uncertain that this work focus on comes from the approximation for the exchange-correlation energy in DFT. 
+
+\bjoern{Focus on functional dependence}{should talk about the sensitivity of the functional first, then say that looking at HFX is a 'single-parameter' study.} Lastly, the source of uncertain that this work focus on comes from the approximation for the exchange-correlation energy in DFT.
 There is no exact formula for the exchange-correlation functional, so in practical approximations are developed and tested to guarantee the robustness of DFT method~\cite{gunnarsson_exchange_1976, bilc_hybrid_2008, lee_development_1988}.
@@
 
-A QoI need be chosen to perform this goal of uncertainty quantification. 
+\bjoern{Definition of a QoI}{is ToF (mobility)} A QoI need be chosen to perform this goal of uncertainty quantification. 
 The figure of merit in OSC investigation is the charge mobility, which quantitatively describe how fast charges move in an OSC. 
@@
 
-Some literatures also report a steady state setting for investigation of charge mobility.
+%Some literatures also report a steady state setting for investigation of charge mobility.
 In such condition, there is no \textit{Source}-\textit{Sink} boundary condition.
 Instead, the molecular system is infinitely repeated in all three dimensions by periodic boundary conditions.
-Over a long time period, the charge occupation on each molecule $\pi_i$ reach an equilibrium, allowing a steady state distribution to be obtained.
-The steady state charge velocity $v_\text{SS}$ is calculated as the charge velocity along the direction of the electric field normalized by the steady state charge occupation $\vec{\pi}:\pi_i$. 
-The calculation for $v_\text{ToF}$ and $\mu_\text{SS}$ will be detailed in the method section.
+%Over a long time period, the charge occupation on each molecule $\pi_i$ reach an equilibrium, allowing a steady state distribution to be obtained.
+%The steady state charge velocity $v_\text{SS}$ is calculated as the charge velocity along the direction of the electric field normalized by the steady state charge occupation $\vec{\pi}:\pi_i$. 
+%The calculation for $v_\text{ToF}$ and $\mu_\text{SS}$ will be detailed in the method section.
 
-To quantify the uncertainty for QoI, the focus of our work will be placed on answering the following questions: 
+\bjoern{Rephrase}{!}To quantify the uncertainty for QoI, the focus of our work will be placed on answering the following questions: 
 \begin{enumerate}
@@
 
-The rest of the paper is organized as follows.
+\bjoern{Update}{later} The rest of the paper is organized as follows.
 Section 2 will outline the multiscale model in OSCs.
@@
 Section 5 shows calculated Poole-Frankel behavior of the MADN with varying HFX values. The confidence interval of the Poole-Frankel plot is estimated. Section 6 concludes the paper.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Multiscale Model}
@@
 In the multiscale model, $E_i^{x,\text{el}}$ is evaluated with a \unit[4]{nm} cutoff distance:
+%
 \begin{equation}
@@
 \end{equation}
+%
 where $\epsilon_0$ is the vacuum permittivity, $a_i, b_k$ denotes the atoms in molecule $i,k$, $q^{n(c)}_{a_i}$ are the partial charge of atom $a$ when molecule $i$ is in state x.
@@
 All  of these operations are performed in the basis set representation of the Kohn--Sham wave functions (see Sec.~\ref{sec:es}) as implemented in VOTCA.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Time-of-flight and Steady State Velocity Calculation}
@@
 According to such connectivity between the molecules, the transition rates $\mathbf{W}_{ij}$ from state $i$ to $j$ is:
-\begin{equation}\label{eq:transition_rates}
+%
+\begin{equation}
+  \label{eq:transition_rates}
 	\mathbf{W}_{ij} =
@@
 And the expected time from state $i$ to reach the Sink state $\tau_i$ is calculated via: 
-\begin{equation}\label{eq:hitting_time}
+%
+\begin{equation}
+  \label{eq:hitting_time}
 	\tau_i = \begin{cases}
@@
 To account for all possible starting nodes of the carriers, all Source states must be considered.
-The random walk process can be modeled as a parallel electric network of capacitors \cite{doyle_random_1984}.
+The random walk process can be modeled as a parallel electric network of capacitors~\cite{doyle_random_1984}.
 Accordingly, the ToF is evaluated using the harmonic mean:
+%
 \begin{equation} 
@@
 \end{equation}
+%
 where $N_\text{source}$ is the number of Source states.
 
-To calculate $v_\text{SS}$ the steady state distribution $\pi_i$ is required.
+%To calculate $v_\text{SS}$ the steady state distribution $\pi_i$ is required.
 In continuous time Markov chain, the steady state distribution vector $\vec{\pi}: \pi_i$ is the null-space of $\mathbf{W}-\mathbf{D}$:
-\begin{equation}
-    (\mathbf{W}-\mathbf{D} )\vec{\pi} = \mathbf{0}
-\end{equation}
-where $\mathbf{D} = \text{diag}(D_i)$ is the out-degree matrix of $\mathbf{W}$.
+%\begin{equation}
+%    (\mathbf{W}-\mathbf{D} )\vec{\pi} = \mathbf{0}
+%\end{equation}
+%where $\mathbf{D} = \text{diag}(D_i)$ is the out-degree matrix of $\mathbf{W}$.
 
-\begin{equation}
-    v_\text{SS} = \sum_i \pi_i \sum_j \omega_{ij} || \vec{r}_{ij}||_2
-\end{equation} 
-where $\omega_{ij}$ is the charge transition rate from molecule $i$ to molecule $j$, and $\vec{r}_{ij}=\vec{r}_j - \vec{r}_i$ is the center-of-mass (COM) distance vector. 
+%\begin{equation}
+%    v_\text{SS} = \sum_i \pi_i \sum_j \omega_{ij} || \vec{r}_{ij}||_2
+%\end{equation} 
+%where $\omega_{ij}$ is the charge transition rate from molecule $i$ to molecule $j$, and $\vec{r}_{ij}=\vec{r}_j - \vec{r}_i$ is the center-of-mass (COM) distance vector. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%
-\begin{figure}
+\begin{figure}[tbp]
     \centering
-    \includegraphics[width=0.45\textwidth]{figs/fig_autogen.pdf}
-    \caption{(a) The dipole moment of neutral state MAND molecule $\mu$, (b) isotropic polarizability $P_\text{iso}$, (c) reorganization energies $\lambda$ and (d) energy disorder $\sigma(E)$ as a function of the HFX parameters (denoted by $\alpha$).}
+    \includegraphics[width=\linewidth]{figs/fig_autogen.pdf}
+    \caption{\bjoern{TODO Zhong:}{The labels (a), (b), (c),(d) should be bigger and places at slightly to the left from the individual panels, which includes the y axis labels; panel (b): these atomic units can be abbreviated a.u.
+and you should also use [a.u.] and not round brackets; pane (d) is missing a ); I would also like to use $\alpha_{HF}$ throughout the paper; change $\mu$ to $d$.}(a) The dipole moment of neutral state MAND molecule $\mu$, (b) isotropic polarizability $P_\text{iso}$, (c) reorganization energies $\lambda$ and (d) energy disorder $\sigma(E)$ as a function of the HFX parameters (denoted by $\alpha$).}
     \label{fig:autogen_MADN}
 \end{figure}
-%
 
@@
 Figure \ref{fig:autogen_MADN}(c)(d) show 
-The reorganization energy $\lambda$ and energy disorder $\sigma(E)$ as a function of HFX parameter are also shown in Fig .\ref{fig:autogen_MADN}(c)(d).
+The reorganization energy $\lambda$ and energy disorder $\sigma(E)$ as a function of HFX parameter are also shown in Fig.~\ref{fig:autogen_MADN}(c)(d).
 
-From Fig.
-\ref{fig:autogen_MADN}(a) one can notice a mild decrease in the dipole moment with increasing HFX and in Fig.
-\ref{fig:autogen_MADN}(b) a linear decrease in isotropic polarizability for both neutral and charged MADN states as HFX increases from 0 to 0.25, indicating reduced molecular polarizability.
-Figure \ref{fig:autogen_MADN}(c) indicates an increase in reorganization energy $\lambda$ with higher HFX, reflecting greater energy requirements for electronic adjustments during charge transfer.
+From Fig.~\ref{fig:autogen_MADN}(a) one can notice a mild decrease in the dipole moment with increasing HFX and in Fig.~\ref{fig:autogen_MADN}(b) a linear decrease in isotropic polarizability for both neutral and charged MADN states as HFX increases from 0 to 0.25, indicating reduced molecular polarizability.
+Figure~\ref{fig:autogen_MADN}(c) indicates an increase in reorganization energy $\lambda$ with higher HFX, reflecting greater energy requirements for electronic adjustments during charge transfer.
 This increase is nonlinear compared to the linear decrease in $P_\text{iso}$.
-Figure \ref{fig:autogen_MADN}(d) shows that the energy disorder $\sigma(E)$ for MADN are similar and close to \unit[0.08]{eV} under different HFX values.
+Figure~\ref{fig:autogen_MADN}(d) shows that the energy disorder $\sigma(E)$ for MADN are similar and close to \unit[0.08]{eV} under different HFX values.
 
@@
   \includegraphics[width=0.80\textwidth]{figs/scatterE_qmmm.pdf}
-  \caption{Scatter plot of site energy of MADN molecules calculated from different HFX, compared to the site energy calculated from HFX=0.25 (The PBE0 functional).
+  \caption{\bjoern{TODO Zhong:}{add labels (a)...; replace $\alpha$ with $\alpha_\text{HF}$.}Scatter plot of site energy of MADN molecules calculated from different HFX, compared to the site energy calculated from HFX=0.25 (The PBE0 functional).
 The brighter color near the diagonal lines indicates denser population of the molecules.
@@
   \includegraphics[width=0.80\textwidth]{figs/scatterEstat_qmmm.pdf}
-  \caption{Scatter plot of MADN electrostatic energy calculated from different HFX, compared to the electrostatic energy calculated from HFX=0.25 (The PBE0 functional).
+  \caption{\bjoern{TODO Zhong:}{add labels (a)...; replace $\alpha$ with $\alpha_\text{HF}$.}Scatter plot of MADN electrostatic energy calculated from different HFX, compared to the electrostatic energy calculated from HFX=0.25 (The PBE0 functional).
 The brighter color near the diagonal lines indicates denser population of the molecules.
@@
   \includegraphics[width=0.80\textwidth]{figs/scatterEdip_qmmm.pdf}
-  \caption{Scatter plot of MADN polarization energy calculated from different HFX, compared to the polarization energy calculated from HFX=0.25 (The PBE0 functional).
+  \caption{\bjoern{TODO Zhong:}{add labels (a)...; replace $\alpha$ with $\alpha_\text{HF}$.}Scatter plot of MADN polarization energy calculated from different HFX, compared to the polarization energy calculated from HFX=0.25 (The PBE0 functional).
 The brighter color near the diagonal lines indicates denser population of the molecules.
@@
   \includegraphics[width=0.80\textwidth]{figs/scatterJ_all.pdf}
-  \caption{Scatter plot of MADN coupling element $\log_{10} J^2$ calculated from different HFX, compared to the polarization energy calculated from HFX=0.25 (The PBE0 functional).
+  \caption{\bjoern{TODO Zhong:}{add labels (a)...; replace $\alpha$ with $\alpha_\text{HF}$; it should be $\log_{10}(J^2/(\unit[]{eV})^2)$; make sure the 10 of $\log_{10}$ is not touching $J$.} Scatter plot of MADN coupling element $\log_{10} J^2$ calculated from different HFX, compared to the polarization energy calculated from HFX=0.25 (The PBE0 functional).
 The brighter color near the diagonal lines indicates denser population of the molecules.
@@
   \includegraphics[width=0.45\textwidth]{figs/fig_network_all.pdf}
-  \caption{The maximum size of the subgraphs obtained in the percolation algorithm as a function of critical value $J_c$.
+  \caption{\bjoern{TODO Zhong:}{same comments regarding the $\log_{10}$ as above; replace $\alpha$ with $\alpha_\text{HF}$.}The maximum size of the subgraphs obtained in the percolation algorithm as a function of critical value $J_c$.
 The molecular systems obtained by different HFX are colored according to the legend.}
@@
   \includegraphics[width=0.45\textwidth]{figs/fig_mle_MADN_withE.pdf}
-  \caption{Distribution of ToFs in the multiscale modeled MADN system.
+  \caption{\bjoern{TODO Zhong:}{these should also strictly be $\log_{10}(\tau/\unit[]{s})$.}Distribution of ToFs in the multiscale modeled MADN system.
   Monte Carlo sampling with a sample size $N_\text{MC}=50000$ is used to obtain the sampled distribution.
@@
   \includegraphics[width=0.45\textwidth]{figs/fig_mle_MADN_noE.pdf}
-  \caption{Distribution of ToFs in the multiscale modeled MADN system.
+  \caption{\bjoern{TODO Zhong:}{these should also strictly be $\log_{10}(\tau/\unit[]{s})$.}Distribution of ToFs in the multiscale modeled MADN system.
   Monte Carlo sampling with a sample size $N_\text{MC}=50000$ is used to obtain the sampled distribution.
@@
 %
-\begin{figure}
-  \centering
-  \includegraphics[width=0.45\textwidth]{figs/fig_mle_MADN_withE_SS.pdf}
-  \caption{Distribution of steady state velocity $v_\text{SS}$ in the multiscale modeled MADN.
-  Monte Carlo sampling with a sample size $N_\text{MC}=50000$ is used to obtain the sampled distribution.
-  The red vertical lines indicate the lower bound and upper bound of the 99\% confidence interval around the median.
-  The black circles indicate the $v_\text{SS}$ obtained using varying HFX values.
-  (a) $P(\log_{10}(v_\text{SS})|E_i \text{ uncertain})$, 
-  (b) $P(\log_{10}(v_\text{SS})|\lambda \text{ uncertain})$, 
-  (c) $P(\log_{10}(v_\text{SS})|J_{ij} \text{ uncertain})$, 
-  (d) $P(\log_{10}(v_\text{SS})|E_i, \lambda, J_{ij} \text{ uncertain})$. }
-  \label{fig:mle_MADN_withE_SS}
-\end{figure}
+%\begin{figure}
+%  \centering
+%  \includegraphics[width=0.45\textwidth]{figs/fig_mle_MADN_withE_SS.pdf}
+%  \caption{Distribution of steady state velocity $v_\text{SS}$ in the multiscale modeled MADN.
+%  Monte Carlo sampling with a sample size $N_\text{MC}=50000$ is used to obtain the sampled distribution.
+%  The red vertical lines indicate the lower bound and upper bound of the 99\% confidence interval around the median.
+%  The black circles indicate the $v_\text{SS}$ obtained using varying HFX values.
+%  (a) $P(\log_{10}(v_\text{SS})|E_i \text{ uncertain})$, 
+%  (b) $P(\log_{10}(v_\text{SS})|\lambda \text{ uncertain})$, 
+%  (c) $P(\log_{10}(v_\text{SS})|J_{ij} \text{ uncertain})$, 
+%  (d) $P(\log_{10}(v_\text{SS})|E_i, \lambda, J_{ij} \text{ uncertain})$. }
+%  \label{fig:mle_MADN_withE_SS}
+%\end{figure}
 %
 %
-\begin{figure}
-  \centering
-  \includegraphics[width=0.45\textwidth]{figs/fig_mle_MADN_noE_SS.pdf}
-  \caption{Distribution of steady state velocity $v_\text{SS}$ in the multiscale modeled MADN. All molecule energies are set to be zero.  
-  Monte Carlo sampling with a sample size $N_\text{MC}=50000$ is used to obtain the sampled distribution.
-  The red vertical lines indicate the lower bound and upper bound of the 99\% confidence interval around the median.
-  The black circles indicate the $v_\text{SS}$ obtained using varying HFX values.
-  (a) $P(\log_{10}(v_\text{SS})|\lambda \text{ uncertain})$, 
-  (b) $P(\log_{10}(v_\text{SS})|J_{ij} \text{ uncertain})$, 
-  (c) $P(\log_{10}(v_\text{SS})|\lambda, J_{ij} \text{ uncertain})$.  }
-  \label{fig:mle_MADN_noE_SS}
-\end{figure}
-%
-\section{Distribution of Steady State Velocity}
+%\begin{figure}
+%  \centering
+%  \includegraphics[width=0.45\textwidth]{figs/fig_mle_MADN_noE_SS.pdf}
+%  \caption{Distribution of steady state velocity $v_\text{SS}$ in the multiscale modeled MADN. All molecule energies are set to be zero.  
+%  Monte Carlo sampling with a sample size $N_\text{MC}=50000$ is used to obtain the sampled distribution.
+%  The red vertical lines indicate the lower bound and upper bound of the 99\% confidence interval around the median.
+%  The black circles indicate the $v_\text{SS}$ obtained using varying HFX values.
+%  (a) $P(\log_{10}(v_\text{SS})|\lambda \text{ uncertain})$, 
+%  (b) $P(\log_{10}(v_\text{SS})|J_{ij} \text{ uncertain})$, 
+%  (c) $P(\log_{10}(v_\text{SS})|\lambda, J_{ij} \text{ uncertain})$.  }
+%  \label{fig:mle_MADN_noE_SS}
+%\end{figure}
 
-The distribution of steady state velocity of MADN is shown as Fig.\ref{fig:mle_MADN_withE_SS} and \ref{fig:mle_MADN_noE_SS}. 
-From the confidence interval, $P(\log_{10}(v_\text{SS})|E_i \text{ uncertain})$ has a range of -2.6 to -0.9, and the confidence interval $P(\log_{10}(v_\text{SS})|\lambda \text{ uncertain})$ has a range from -1.7 to -1.1.
+%\section{Distribution of Steady State Velocity}
+
+%The distribution of steady state velocity of MADN is shown as Fig.\ref{fig:mle_MADN_withE_SS} and \ref{fig:mle_MADN_noE_SS}. 
+%From the confidence interval, $P(\log_{10}(v_\text{SS})|E_i \text{ uncertain})$ has a range of -2.6 to -0.9, and the confidence interval $P(\log_{10}(v_\text{SS})|\lambda \text{ uncertain})$ has a range from -1.7 to -1.1.
 The width of those confidence intervals is very close to the confidence interval of distributions $P(\log_{10}(\tau)|E_i \text{ uncertain})$ and $P(\log_{10}(\tau)|\lambda \text{ uncertain})$, respectively.
-However, $P(\log_{10}(v_\text{SS})|J_{ij} \text{ uncertain})$ has a range from -1.6 to 1.3, spanning 3 orders of magnitude.
+%However, $P(\log_{10}(v_\text{SS})|J_{ij} \text{ uncertain})$ has a range from -1.6 to 1.3, spanning 3 orders of magnitude.
 This is  much larger than $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$ as shown in Fig .\ref{fig:mle_MADN_withE}.
-The large confidence interval in $P(\log_{10}(v_\text{SS})|J_{ij} \text{ uncertain})$ shows that $v_{ss}$ is very sensitive to the change in $J_{ij}$.
+%The large confidence interval in $P(\log_{10}(v_\text{SS})|J_{ij} \text{ uncertain})$ shows that $v_{ss}$ is very sensitive to the change in $J_{ij}$.
 Combining all the uncertainty effects in $E_i, \lambda, J_{ij}$, the confidence interval of $P(\log_{10}(v_\text{SS})|E_i, \lambda, J_{ij} \text{ uncertain})$ is from -2.5 to 1.3, covering 4 orders of magnitude.
 
-When energy disorder is not considered, the $v_\text{SS}$ distribution $P(\log_{10}(v_\text{SS})|\lambda, J_{ij} \text{ uncertain})$ has a confidence interval from 0.3 to 3.5, spanning 3 orders of magnitude.
+%When energy disorder is not considered, the $v_\text{SS}$ distribution $P(\log_{10}(v_\text{SS})|\lambda, J_{ij} \text{ uncertain})$ has a confidence interval from 0.3 to 3.5, spanning 3 orders of magnitude.
 This interval is close to the range of $P(\log_{10}(v_\text{SS})|J_{ij} \text{ uncertain})$ when only $J_{ij}$ is uncertain.
-In contrast, the interval of $P(\log_{10}(v_\text{SS})|\lambda \text{ uncertain})$ is from 0.6 to 1.2, whose width is much smaller than that of $P(\log_{10}(v_\text{SS})|J_{ij} \text{ uncertain})$.
+%In contrast, the interval of $P(\log_{10}(v_\text{SS})|\lambda \text{ uncertain})$ is from 0.6 to 1.2, whose width is much smaller than that of $P(\log_{10}(v_\text{SS})|J_{ij} \text{ uncertain})$.
 
-These result suggests that compared to the ToF $\tau$, the quantity $v_\text{SS}$ is significantly affected by uncertainties in $J_{ij}$, so $v_\text{SS}$ is less robust when the parameters $E_i, \lambda, J_{ij}$ contains uncertainty at the same time.
-In the next section, the Poole–Frenkel behavior, that is the dependence of charge mobility on the electric field will be study using the ToF setting. 
+%These result suggests that compared to the ToF $\tau$, the quantity $v_\text{SS}$ is significantly affected by uncertainties in $J_{ij}$, so $v_\text{SS}$ is less robust when the parameters $E_i, \lambda, J_{ij}$ contains uncertainty at the same time.
+%In the next section, the Poole–Frenkel behavior, that is the dependence of charge mobility on the electric field will be study using the ToF setting. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     \includegraphics[width=0.45\textwidth]{figs/fig_mle_withE_mu2_ave.pdf}
-    \caption{Distribution of $\mu_\text{PF}$ in the multiscale modeled MADN system.
+    \caption{\bjoern{TODO Zhong:}{these should also strictly be $\log_{10}(\mu/(\unit[]{cm^2(Vs)^{-1}}))$; there should be no PF label at $\mu$.} Distribution of $\mu_\text{PF}$ in the multiscale modeled MADN system.
     Monte Carlo sampling with a sample size $N_\text{MC}=10000$ is used to obtain the sampled distribution.
@@
     \includegraphics[width=0.45\textwidth]{figs/fig_PF_plot_ave.pdf}
-    \caption{Electric-field dependence of the mobility $\mu$ in the multiscale modeled MADN system.
+    \caption{\bjoern{TODO Zhong:}{remove PF label; avoid the large white space at the right; make data plot symbols a little bigger and lines a little thicker.}Electric-field dependence of the mobility $\mu$ in the multiscale modeled MADN system.
 The dash lines are Poole–Frenkel plots obtained with specific HFX value, and the green shadow indicates the 99\% confidence interval estimated from the MC sampling with a sample size of $N_\text{MC}=10000$.}

### 2024-11-28 paper.tex
small typos
moved some blocks around

@@
 
-\title{Uncertainty Quantification in Multiscale Model\bjoern{Needs}{new title}}
+\title{Uncertainty Quantification in Multiscale Models of Charge Transport in Organic Semiconductors: Influence of the Exhange-Correlation Functional}
 
@@
 
-%\keywords{Suggested keywords}%Use showkeys class option if keyword
-                              %display desired
+%\keywords{Suggested keywords}
+
 \maketitle
 
-%\tableofcontents
-
 \section{Introduction}
-\bjoern{UQ in general}{}
-Theoretical model and computer simulation for understanding a physical system usually contain some uncertainties in predicting the system features. 
-For example, the theoretical model does not encompass all relevant physical factors, the theoretical model incorporates empirical parameters that include noise, the numerical scheme contains approximation, the simulation use noisy quantities, etc~\cite{sarkar_uncertainty_2017,oconnor_quantifying_2024, chernatynskiy_uncertainty_2013, suleimenova_tutorial_2021,coveney_reliability_2021, coveney_when_2021}.
-Nevertheless, those uncertainties should not affect the validity of the model or the accuracy for the predicting system in terms of some quantities of interest (QoI). 
-Here the terminology "uncertainties" refers to the impossibility of getting a deterministic QoI, and excludes theoretical or numerical errors. 
-The amount of uncertainty in the QoI plays an important role in determining the usefulness of the model. 
-So quantifying the uncertainty is a key factor for telling if the model is quanlitatively or quantitatively accurate.
 
@@
 To explain in detail those uncertainties, the first-principle multiscale model is briefly reviewed.
-
-\begin{figure*}[tbp]
-  \centering
-  \includegraphics[width=\linewidth]{figs/MSM2.pdf}
-  \caption{\bjoern{TODO Bjoern}{Rewrite caption}The multiscale model workflow for OSC.
-Step 1: MD simulation to generate atom coordinates.
-Step 2: Molecule energy $E_i$ calculation.
-Step 3: Calculation of Reorganization energy $\lambda_{ij}$ and coupling element $J_{ij}$ for pairs of molecule $i,j$ whose COM distance is less than $r_\text{cutoff}$.
-Step 4: Modelling dynamics on device level, such as ToF calculation.}
-  \label{fig:MSM}
-\end{figure*}
 
@@
 Finally the charge dynamic is model as a CTRW among the molecules.
+
+\bjoern{UQ in general}{}
+Theoretical model and computer simulation for understanding a physical system usually contain some uncertainties in predicting the system features. 
+For example, the theoretical model does not encompass all relevant physical factors, the theoretical model incorporates empirical parameters that include noise, the numerical scheme contains approximation, the simulation use noisy quantities, etc~\cite{sarkar_uncertainty_2017,oconnor_quantifying_2024, chernatynskiy_uncertainty_2013, suleimenova_tutorial_2021,coveney_reliability_2021, coveney_when_2021}.
+Nevertheless, those uncertainties should not affect the validity of the model or the accuracy for the predicting system in terms of some quantities of interest (QoI). 
+Here the terminology "uncertainties" refers to the impossibility of getting a deterministic QoI, and excludes theoretical or numerical errors. 
+The amount of uncertainty in the QoI plays an important role in determining the usefulness of the model. 
+So quantifying the uncertainty is a key factor for telling if the model is quanlitatively or quantitatively accurate.
+
+\begin{figure*}[tbp]
+  \centering
+  \includegraphics[width=\linewidth]{figs/MSM2.pdf}
+  \caption{\bjoern{TODO Bjoern}{Rewrite caption}The multiscale model workflow for OSC.
+Step 1: MD simulation to generate atom coordinates.
+Step 2: Molecule energy $E_i$ calculation.
+Step 3: Calculation of Reorganization energy $\lambda_{ij}$ and coupling element $J_{ij}$ for pairs of molecule $i,j$ whose COM distance is less than $r_\text{cutoff}$.
+Step 4: Modelling dynamics on device level, such as ToF calculation.}
+  \label{fig:MSM}
+\end{figure*}
 
@@
 Poole and Frenkel \cite{frenkel_prebreakdown_1938} predicted the electric-field dependence of charge mobility as $\mu_\text{PF}(F)=\mu_0 \exp (\beta \sqrt{|\vec{F}|})$.
-So it is common to plot the mobility $\mu_\text{PF}$ against $\sqrt{|\vec{F}|}$ in a so-called Poole–Frenkel plot.
+So it is common to plot the mobility $\mu_\text{PF}$ against $\sqrt{|\vec{F}|}$ in a so-called Poole-Frenkel plot.
 which is shown in Fig. \ref{fig:PF_plot_ave} for specifie HFX values. The 99\% confidence interval obtained via MC sampled in shown in the green shadow. 

### 2024-11-28 paper.tex
cosmetics

@@
 
-\bjoern{Intro OSCs}{}In this work, an investigated model containing uncertainties is the multiscale model of charge dynamics~\cite{Baumeier2011, edeling_global_2024,coropceanu_charge_2007} in organic semiconductors (OSCs), which are materials that consist of organic molecules with disordered and amorphous structure.
+\bjoern{Intro OSCs}{to adjust}In this work, an investigated model containing uncertainties is the multiscale model of charge dynamics~\cite{Baumeier2011, edeling_global_2024,coropceanu_charge_2007} in organic semiconductors (OSCs), which are materials that consist of organic molecules with disordered and amorphous structure.
 Besides its semiconducting properties, they are mechanically flexible and comes with controllable charge transport properties~\cite{hamers_flexible_2001,liu_high_2015,chow_organic_2020}.
@@
 \begin{equation}
-    \omega_{ij} = \frac{2\pi}{\hbar} \frac{|J_{ij}|^2}{\sqrt{4\pi \lambda_{ij} k_\text{B}T}} \exp\left(-\frac{(E_{ij} + q \vec{F} \cdot \vec{r}_{ij} - \lambda_{ij})^2}{4\lambda_{ij} k_\text{B}T}\right) ,
+    \omega_{ij} = \frac{2\pi}{\hbar} \frac{|J_{ij}|^2}{\sqrt{4\pi \lambda_{ij} k_\text{B}T}} \exp\left(-\frac{(\Delta E_{ij} + q \vec{F} \cdot \vec{r}_{ij} - \lambda_{ij})^2}{4\lambda_{ij} k_\text{B}T}\right) ,
     \label{equ:Marcus}
@@
 
-\subsection{Time-of-flight and Steady State Velocity Calculation}
+\subsection{Time-of-flight Calculation}
 Following the graph $\mathbf{G}$ from the multiscale model,
@@
 
+\subsection{Molecular Parameters}
 Atomic charges and molecule polarizability $P_\text{iso}$ are crucial for evaluating molecular energy contributions from electrostatic and polarization effects.
@@
 
-To demonstration the effect of HFX on the atomic charges and molecule polarizability $P_\text{iso}$,
-Figure \ref{fig:autogen_MADN}(a)(b) illustrates the dependence of the dipole moment $\mu$ and isotropic polarizability $P_\text{iso}$ on HFX.
+To demonstration the effect of HFX on the atomic charges and molecule polarizability $P_\text{iso}$,Figure \ref{fig:autogen_MADN}(a)(b) illustrates the dependence of the dipole moment $\mu$ and isotropic polarizability $P_\text{iso}$ on HFX.
 Figure \ref{fig:autogen_MADN}(c)(d) show 

### 2024-11-29 paper.tex
first pass at the intro

@@
 \begin{abstract}
-  This work quantifies uncertainties in a multiscale model for charge dynamics in organic semiconductors (OSCs).
+  \bjoern{TODO}{rewrite}This work quantifies uncertainties in a multiscale model for charge dynamics in organic semiconductors (OSCs).
 A first-principle multiscale model integrates classical molecular dynamics (MD), density functional theory (DFT), quantum mechanical calculation and continuous-time random walk (CTRW) processes to allow the simulation of charge transport in OSCs.
@@
 \section{Introduction}
-
-\bjoern{Intro OSCs}{to adjust}In this work, an investigated model containing uncertainties is the multiscale model of charge dynamics~\cite{Baumeier2011, edeling_global_2024,coropceanu_charge_2007} in organic semiconductors (OSCs), which are materials that consist of organic molecules with disordered and amorphous structure.
-Besides its semiconducting properties, they are mechanically flexible and comes with controllable charge transport properties~\cite{hamers_flexible_2001,liu_high_2015,chow_organic_2020}.
-This flexible functionality is achieved by tuning molecular properties to achieve an ideal operating properties at the device-level\cite{bronstein_role_2020, bredas_organic_2002}, so a fundamental understanding of OSC from molecule scale  plays an important role in OSC optimization.
-Conducting these optimization processes through experimental methods is financially demanding.
-In contrast, computational approaches such as the multiscale model provides insightful guidance for such investigation.
-So robustness of the computational model is paramount to promote OSC optimization.
-
-\bjoern{Idea of the Multiscale Model}{}Like every other models, the multiscale model contains uncertainties due to certain approximation in modeling perspective, the randomness nature of the physical quantities, and the limitation of the numerical simulations, only to name a few.
-To explain in detail those uncertainties, the first-principle multiscale model is briefly reviewed.
-
-Fundamentally, quantum-mechanical description is needed to model charge dynamics due to the motion of electrons.
-However, the resulting full many-electron schr\"{o}dinger equation is impossible to solve due to its complexity, so Density Functional Theory (DFT) \cite{kohn_selfconsistent_1965,jones_density_2015, hammesschiffer_conundrum_2017} appears as a manageable way to model electrons.
-DFT has its own challenges in achieving multiscale modeling.
-The first challenge relates to the Born-Oppenheimer approximation \cite{born_zur_1927} in quantum
-mechanics, which simplifies the problem by separating the electronic and nuclear
-coordinates.
-As a result, the time evolution of the atomic coordinates can be modeled in molecular dynamics (MD) by solving the Newton's equation using empirical force field to approximate the potential energy surfaces~\cite{rapaport_art_2004}.
-
-The next challenge is the infeasibility of solving the DFT equations for the entire system even at a fixed time~\cite{hammesschiffer_conundrum_2017}. 
-But due to fact that OSCs have disordered and amorphous structure and the quantum states of each molecule is confined to a limited region, the charge dynamic can be well-approxmiated as a jumping process between molecules, which is a continuous time random walk (CTRW) process.
-The transition rates between the molecules can be calculated from quantum chemical calculations and related to the electronic structures parameters including the molecule energy, reorganization energy and coupling elements which will be explained in the methodology section.
-
-Until this point, the molecular system is modeled as graph $\mathbf{G}(\mathbf{V}, \mathbf{W})$ where $\mathbf{V}$ is the set of nodes and $\mathbf{W}: \omega_{ij}$ is the adjacency matrix.
-Each node represents one molecule, the weighted and directed edge $\omega_{ij}$ represents the transition rates from node $i$ to node $j$ calculated from quantum chemical methods.
-As will be shown in the method section, $\omega_{ij}$ determines the QoIs whose quantities we want to quantify.
-
-Figure \ref{fig:MSM} summarized the multiscale model as mentioned above using MADN, a type of OSC as an example. 
-The process includes: Firstly, classical Molecular Dynamics is used to generate the atomistic coordinates of all molecules.
-Then DFT is used to obtain electronic structures.
-Finally the charge dynamic is model as a CTRW among the molecules.
-
-\bjoern{UQ in general}{}
-Theoretical model and computer simulation for understanding a physical system usually contain some uncertainties in predicting the system features. 
-For example, the theoretical model does not encompass all relevant physical factors, the theoretical model incorporates empirical parameters that include noise, the numerical scheme contains approximation, the simulation use noisy quantities, etc~\cite{sarkar_uncertainty_2017,oconnor_quantifying_2024, chernatynskiy_uncertainty_2013, suleimenova_tutorial_2021,coveney_reliability_2021, coveney_when_2021}.
-Nevertheless, those uncertainties should not affect the validity of the model or the accuracy for the predicting system in terms of some quantities of interest (QoI). 
-Here the terminology "uncertainties" refers to the impossibility of getting a deterministic QoI, and excludes theoretical or numerical errors. 
-The amount of uncertainty in the QoI plays an important role in determining the usefulness of the model. 
-So quantifying the uncertainty is a key factor for telling if the model is quanlitatively or quantitatively accurate.
+Organic semiconductors (OSCs) are materials that consist of organic molecules, often in disordered structures formed during spin-coating or deposition processing.
+Besides their semiconducting properties, they are mechanically flexible and come with the potential to control charge transport properties~\cite{hamers_flexible_2001,liu_high_2015,chow_organic_2020}.
+This flexible functionality is achieved by tuning molecular properties to achieve an ideal operation at the device level~\cite{bronstein_role_2020, bredas_organic_2002}.
+Computational approaches that aim at predicting the charge transport properties of disordered molecular materials resolving the interplay between single-molecule properties (such as their electronic structure or response properties) and mesoscale material morphology can play an important role in supporting or even guiding experimental optimization processes.\bjoern{add citations}{}
 
@@
 
-\bjoern{Uncertainties in the MSM}{way too verbose}
-In achieving the multiscale model, uncertainties are introduced. 
-While Born-Oppenheimer approximation allows for the use of force field to approximate the potential energy surfaces and model the atomic coordinates using Newton’s equations, the force field is not exactly the same as the potential for DFT~\cite{izvekov_effective_2004}.
-So the atomic coordinates, that is the molecule structures contain uncertainty which ultimately affects the charge dynamics. 
-This is one source of uncertainty that have not been investigated. But in our investigation, a fixed molecule structure is used and we do not consider this source of uncertainty. 
-Secondly, charge jumping between the state localization is not exactly a time dependent DFT process. 
-However, the amorphous OSCs used in this work has strong disorder, so the model noise from state localization is negligible and we do not consider the uncertainty originated from this perspective.
+First-principles based multiscale models are such types of computational approaches.
+Due to the infeasibility of explicitly simulating the coupled non-adiabatic electron-nuclear dynamics for the time- and length scales of realistic materials, these models typically exploit the localization of electronic states in disordered molecular materials and consider a rate-based description of hopping-type transport.
+A popular choice for the electron transfer rate $\omega_{ij}$ between two localization sites $i$ and $j$ is Marcus theory~\bjoern{add}{citation}, in which
+%
+\begin{equation}
+    \omega_{ij} = \frac{2\pi}{\hbar} \frac{|J_{ij}|^2}{\sqrt{4\pi \lambda_{ij} k_\text{B}T}} \exp\left(-\frac{(\Delta E_{ij} - \lambda)^2}{4\lambda k_\text{B}T}\right) ,
+    \label{equ:Marcus}
+\end{equation}
+%
+where $\hbar$ is the reduced Planck constant,  $k_\text{B}$ the Boltzmann constant, and $T$ the temperature.
+As depicted in Fig.~\ref{fig:MSM}, given a larger scale morphology and with the definition of localization sites (Fig.~\ref{fig:MSM}(a)), multiscale models employ first-principles based methods (Fig.~\ref{fig:MSM}(b)) to explicitly calculate the remaining physical, material-specific (or rather transfer-pair-specific) quantities in Eq.~\ref{equ:Marcus}: the reorganization energy $\lambda$ (here a single value as we assume a single-component material), the electronic coupling $J_{ij}$, and the site energy difference $\Delta E_{ij} = E_i - E_j$.
+With all that information, charge transport is modeled as a continuous time random walk (CTRW) process on a graph $\mathbf{G}$, constructed from the localization sites and the calculated rates between them (Fig.~\ref{fig:MSM}(c)).
+Panel (b) of Fig.~\ref{fig:MSM} mentions some specific methods for the calculation of the quantities entering Eq.~\ref{equ:Marcus}, such as mixed quantum-classical methods for obtaining the site energies with the help of microelectrostatic methods \bjoern{add}{citations} or the dimer projection method for determining coupling elements~\cite{baumeier_density_2010}, as they are the ones adopted in this work.
+What is essential about these and alternative ones is that they typically rely on density-functional theory (DFT) calculations, either directly or as a mean to parametrize classical models.
+The dependence of DFT calculations on the choice of an exchange-correlation functional raises the question of how sensitive the simulated charge transport is to this choice and how certain predictions of material properties are.
 
-\bjoern{Focus on functional dependence}{should talk about the sensitivity of the functional first, then say that looking at HFX is a 'single-parameter' study.} Lastly, the source of uncertain that this work focus on comes from the approximation for the exchange-correlation energy in DFT.
-There is no exact formula for the exchange-correlation functional, so in practical approximations are developed and tested to guarantee the robustness of DFT method~\cite{gunnarsson_exchange_1976, bilc_hybrid_2008, lee_development_1988}.
-The accuracy of DFT depends heavily on the choice of the exchange-correlation functional whose suitability is usually unknown for new synthesized molecules. 
-As an advancement to improve accuracy, Hybrid-DFT \cite{marques_densitybased_2011,perdew_rationale_1996} incorporates a portion $\alpha$ of exact HF exchange functional (HFX) from Hartree-Fock (HF) theory into the exchange-correlation functional, particularly for systems where DFT falls short.
-For example, the PBE0 functional has a portion of 0.25 HFX~\cite{adamo_toward_1999}.
+Uncertainty quantification (UQ) is concept from computational science which allows for an estimation of confidence intervals for a quantity of interest (QoI) and an analysis of its sensitivity in models of a physical system that contain uncertain, maybe empirical, or noisy, parameters~\cite{sarkar_uncertainty_2017,oconnor_quantifying_2024, chernatynskiy_uncertainty_2013, suleimenova_tutorial_2021,coveney_reliability_2021, coveney_when_2021}.
+Many common UQ studies focus on models with (partial) differential equations, e.g., drift-diffusion equations in which the diffusivity as parameter, and assume a certain distribution for the values of the parameter(s).
+For the multiscale model of charge transport, it is not straightforward to cast the large variety of available exchange-correlation functionals into the role of a model parameter with some distribution.
+To keep the problem tractable, we focus here instead specifically on the exchange part in hybrid functionals~\cite{perdew_rationale_1996,marques_densitybased_2011}, in which a DFT model for the exchange is mixed using a weighting factor $\alpha_\text{HFX}$ with a Hartree--Fock type exchange, i.e.,
+%
+\begin{equation}
+  E_\text{x} = \alpha_\text{HFX} E_\text{x}^\text{HF} + (1-\alpha_\text{HFX})E_\text{x}^\text{DFT}.
+  \label{equ:hybrid}
+\end{equation}
+%
+More specifically, we take as the basis the PBE0 functional~\cite{adamo_toward_1999} and scrutinize (i) how the predictions of the multiscale model of charge transport are affected by variation of $\alpha_\text{HFX}$ as a proxy for uncertainties in the choice of DFT functionals, (ii) what the level of confidence is in quantitative predictions, and (iii) what are the most sensitive quantities in the model.
+In this sense, Eq.~\ref{equ:hybrid} is deceptively simple.
+For each value of $\alpha_\text{HFX}$, the graph $G$ is constructed using the respective value of the reorganization energy, the $N_\text{mol}$ site energies, and the $N_\text{pair}$ coupling elements, and the dimensionality of the problem from the perspective of UQ is $N_\text{UQ}=1+N_\text{mol}+N_\text{pair}$, which can easily be on the order of $10^{4}-10^{5}$.
+We consider the simulated time-of-flight (ToF) and the associated mobility the QoI in the following (see Fig.~\ref{fig:MSM}(c)) which then are subject to uncertainties in these $N_\text{UQ}$ parameters, {\em stemming} from the variation in $\alpha_\text{HFX}$.
+As a prototypical system, we will study hole transport in an amorphous morphology of 2-methyl-9, 10-bis(naphthalen-2-yl)anthracene (MADN), a wide-gap semiconductor that is used extensively as an ambipolar host material in organic light-emitting diodes~\bjoern{add}{citation}.
 
-Looking back into the CTRW of the charge transport, the transition rates depend on the electronic structures parameters which rely on the validity of the exchange-correlation functional from the modeling perspectives.
-So the approximations in exchange-correlation functional will bring uncertainties to the multiscale model~\cite{medvedev_density_2017}. 
-In particular, different hybrid-DFT functionals containing varying HFX levels will generate different output from the multiscale model mentioned aboved. 
-The effect of such uncertainty from the electronic structure level on the multiscale model is not yet explored in literatures. 
-The goal of this work is to quantify the uncertainty effect of the exchange-correlation functional on the charge dynamics in OSCs and to study the robustness of the multiscale model, with a particular focus on the uncertainty represented by different portional of HFX.
-
-\bjoern{Definition of a QoI}{is ToF (mobility)} A QoI need be chosen to perform this goal of uncertainty quantification. 
-The figure of merit in OSC investigation is the charge mobility, which quantitatively describe how fast charges move in an OSC. 
-The charge mobility is commonly measured in a \textit{time-of-flight} (ToF) setting. 
-As shown in Fig.\ref{fig:MSM}(d), charge carriers are injected into one electrode called \textit{Source} and they are collected by another electrode at the opposite end called \textit{Sink}. 
-Knowing the length of the sample $L$ and the time-of-flight $\tau$, the diffusive velocity is calculated as $v_\text{ToF}=\frac{L}{\tau}$.
-When electric field $\vec{F}$ is used and the charge dynamics undergo a field-drifted transport, the charge mobility is calculated as $\mu_\text{ToF}=\frac{\vec{v}_\text{ToF} \vec{F}}{|\vec{F}|^2}$.
-
-%Some literatures also report a steady state setting for investigation of charge mobility.
-In such condition, there is no \textit{Source}-\textit{Sink} boundary condition.
-Instead, the molecular system is infinitely repeated in all three dimensions by periodic boundary conditions.
-%Over a long time period, the charge occupation on each molecule $\pi_i$ reach an equilibrium, allowing a steady state distribution to be obtained.
-%The steady state charge velocity $v_\text{SS}$ is calculated as the charge velocity along the direction of the electric field normalized by the steady state charge occupation $\vec{\pi}:\pi_i$. 
-%The calculation for $v_\text{ToF}$ and $\mu_\text{SS}$ will be detailed in the method section.
-
-\bjoern{Rephrase}{!}To quantify the uncertainty for QoI, the focus of our work will be placed on answering the following questions: 
-\begin{enumerate}
-    \item How does HFX level change the electronic structures: reorganization energy, distribution of molecule energies and coupling elements? 
-    \item How does HFX level change the charge mobility?
-    \item Which electronic structure (among energy, coupling element and reorganization energy) uncertainty has the most impact on the QoI distribution?
-    \item Can we estimate the range of the QoI, given a confidence level?
-\end{enumerate}
-
-\bjoern{Update}{later} The rest of the paper is organized as follows.
-Section 2 will outline the multiscale model in OSCs.
-This includes the electronic structure calculation centering on Kohn-Sham equation, the calucation of molecule energy, reorganization energy and coupling elements.
-The details of the molecule dynamics to obtain the MADN system will be listed.
-Then section 3 present the multiscale modeling results with the chosen HFX values.
-In section 4, the Monte Carlo sampling method is utilized to estimate the ToF distribution and $v_\text{SS}$ distribution, followed by the sensitivity analysis on the parameters.
-Section 5 shows calculated Poole-Frankel behavior of the MADN with varying HFX values. The confidence interval of the Poole-Frankel plot is estimated. Section 6 concludes the paper.
+This paper is organized as follows.
+Section~\ref{sec:model} outlines the theoretical and computational details of the multiscale model, including the morphology simulation with classical molecular dynamics, the determination of all quantities in the transition rates, and the calculation of the charge transport properties from the constructed graph model.
+In Section~\ref{sec:MSMresults}, we discuss the explicit results from the model using different values of $\alpha_\text{HFX}$, before we show the results of uncertainty quantification and sensitivity analysis via Monte Carlo sampling.
+A brief summary concludes the paper.
 
 \section{Multiscale Model}
+\label{sec:model}
 As mentioned in the introduction, the multiscale model maps a structural morphology into a graph $\mathbf{G}(\mathbf{V}, \mathbf{W})$.
@@
     \omega_{ij} = \frac{2\pi}{\hbar} \frac{|J_{ij}|^2}{\sqrt{4\pi \lambda_{ij} k_\text{B}T}} \exp\left(-\frac{(\Delta E_{ij} + q \vec{F} \cdot \vec{r}_{ij} - \lambda_{ij})^2}{4\lambda_{ij} k_\text{B}T}\right) ,
-    \label{equ:Marcus}
+    \label{equ:Marcus2}
 \end{equation}
@@
 \section{Results on MADN}
-
+\label{sec:MSMresults}
 In this study, we investigate the hole-transporting organic semiconductor MADN (2-Methyl-9,10-di(naphth-2-yl)anthracene) and study its charge mobility's dependence on HFX.
@@
 A physical property related to the overall atomic charges is dipole moment at charge neutral state.
+
+To calculate the ToF from the electronic structures, the \textit{Source} region contains molecules with X-coordinate $0 < r^x_i < 0.5$ nm, and the \textit{Sink} region contains molecules with X-coordinate $8.5 < r^x_i < 9$ nm.
 
@@
 
-To demonstration the effect of HFX on the atomic charges and molecule polarizability $P_\text{iso}$,Figure \ref{fig:autogen_MADN}(a)(b) illustrates the dependence of the dipole moment $\mu$ and isotropic polarizability $P_\text{iso}$ on HFX.
-Figure \ref{fig:autogen_MADN}(c)(d) show 
-The reorganization energy $\lambda$ and energy disorder $\sigma(E)$ as a function of HFX parameter are also shown in Fig.~\ref{fig:autogen_MADN}(c)(d).
+To demonstration the effect of HFX on the atomic charges and molecule polarizability $P_\text{iso}$, Fig.~\ref{fig:autogen_MADN}(a)(b) illustrates the dependence of the dipole moment $\mu$ and isotropic polarizability $P_\text{iso}$ on HFX.
+Figure~\ref{fig:autogen_MADN}(c)(d) show the reorganization energy $\lambda$ and energy disorder $\sigma(E)$ as a function of HFX parameter are also shown in Fig.~\ref{fig:autogen_MADN}(c)(d).
 
@@
 
-To calculate the ToF from the electronic structures, the \textit{Source} region contains molecules with X-coordinate $0 < r^x_i < 0.5$ nm, and the \textit{Sink} region contains molecules with X-coordinate $8.5 < r^x_i < 9$ nm.
-
 The ToF is also calculated without energy disorder, meaning $\Delta E_{ij}=0$ for all $i,j$.
-Table \ref{tab:ToF_MADN_HFX} shows the ToF and corresponding diffusive velocity $v_\text{ToF}$.
+Table~\ref{tab:ToF_MADN_HFX} shows the ToF and corresponding diffusive velocity $v_\text{ToF}$.
 With energy disorder, the ToF increases by a factor of approximately 15 as $\alpha$ increases from 0 to 0.25.  
@@
 
-\begin{table}[tbp]%The best place to locate the table environment is directly after its first reference in text
-\caption{\label{tab:ToF_MADN_HFX}%
-The ToF and diffusive velocity calculated by ToF along a distance $L_x = \unit[9.0]{nm}$ with and without energy disorder of the MADN system as a function of the HFX.
-The ToF is in unit $\unit[]{s}$ and $v_\text{ToF}$ in unit $\unit[]{m/s}$.
-}
+\begin{table}[tbp]
+\caption{The ToF and diffusive velocity calculated by ToF along a distance $L_x = \unit[9.0]{nm}$ with and without energy disorder of the MADN system as a function of the HFX.
+The ToF is in unit $\unit[]{s}$ and $v_\text{ToF}$ in unit $\unit[]{m/s}$.}
 \begin{ruledtabular}
@@
 \end{ruledtabular}
+\label{tab:ToF_MADN_HFX}
 \end{table}
 
-%
 \begin{table*}[tbp]%The best place to locate the table environment is directly after its first reference in text
@@
 \section{ToF Distribution and Sensitivity Analysis}
+\label{sec:UQ}
 The previous section shows that different HFX affect the calculated ToF.

### 2024-11-29 paper.tex
small edit

@@
 \label{sec:model}
-As mentioned in the introduction, the multiscale model maps a structural morphology into a graph $\mathbf{G}(\mathbf{V}, \mathbf{W})$.
-In our context, the graph properties, that is the entries $\omega_{ij}$ in the adjacency matrix $\mathbf{W}$, only depends on the HFX values since other modeling parameters are kept consistent.
+The multiscale model maps a large scale molecular morphology with atomistic detail into a graph $\mathbf{G}(\mathbf{V}, \mathbf{W})$, where the set of nodes $\mathbf{V}$ is determined from the center-of-masses of the individual molecules and $\mathbf{W}$ is the adjacency matrix formed by the Marcus rates $\omega_{ij}$.
+Two nodes $i,j$ are connected if the corresponding molecules have their closest-contact distance smaller than $r_\text{cutoff}=\unit[0.5]{nm}$.
 
-Those transition rates charge transfer rates from molecules $i$ to $j$ is calculated as the bi-molecular transition rates:
+%Those transition rates charge transfer rates from molecules $i$ to $j$ is calculated as the bi-molecular transition rates:
 %
-\begin{equation}
-    \omega_{ij} = \frac{2\pi}{\hbar} \frac{|J_{ij}|^2}{\sqrt{4\pi \lambda_{ij} k_\text{B}T}} \exp\left(-\frac{(\Delta E_{ij} + q \vec{F} \cdot \vec{r}_{ij} - \lambda_{ij})^2}{4\lambda_{ij} k_\text{B}T}\right) ,
-    \label{equ:Marcus2}
-\end{equation}
+%\begin{equation}
+%    \omega_{ij} = \frac{2\pi}{\hbar} \frac{|J_{ij}|^2}{\sqrt{4\pi \lambda_{ij} k_\text{B}T}} \exp\left(-\frac{(\Delta E_{ij} + q \vec{F} \cdot \vec{r}_{ij} - \lambda_{ij})^2}{4\lambda_{ij} k_\text{B}T}\right) ,
+%    \label{equ:Marcus2}
+%\end{equation}
 %
-where $\hbar$ is the reduced Planck constant and $k_\text{B}$ the Boltzmann constant.
+%where $\hbar$ is the reduced Planck constant and $k_\text{B}$ the Boltzmann constant.
 The temperature $T$ (in \unit[]{K}), the charge of the carrier $q$ (in \unit[]{e}) and the external electric field $\vec{F}$ (in V/m) can be considered the external, environmental parameters of the simulation.
 The vector $\vec{r}_{ij} = (r^x_{ij},r^y_{ij},r^z_{ij})^\text{T}$ connects the center-of-masses (COMs) of molecules $i$ and $j$, which is calculated using cyclic boundary conditions.
-The remaining physical, material-specific (or rather transfer-pair-specific) quantities are the reorganization energy $\lambda_{ij}$, the electronic coupling $J_{ij}$, and the energy difference $E_{ij} = E_i - E_j$ (all in \unit[]{eV}).
-In our model, two nodes $i,j$ form a connection of the corresponding molecules $i,j$ have their closest-contact distance smaller than $r_\text{cutoff}=\unit[0.5]{nm}$.
-The rest of this section will introduce the following: the molecular dynamics used to obtain the coordinates $r^x_{i},r^y_{i},r^z_{i}$, the calculation of node-specific quantities $\lambda$, $E_i$ and $J_{ij}$, as well as the calculation of ToF $\tau$ and steady state velocity $v_\text{SS}$.
+%The remaining physical, material-specific (or rather transfer-pair-specific) quantities are the reorganization energy $\lambda_{ij}$, the electronic coupling $J_{ij}$, and the energy difference $E_{ij} = E_i - E_j$ (all in \unit[]{eV}).
+
+%The rest of this section will introduce the following: the molecular dynamics used to obtain the coordinates $r^x_{i},r^y_{i},r^z_{i}$, the calculation of node-specific quantities $\lambda$, $E_i$ and $J_{ij}$, as well as the calculation of ToF $\tau$ and steady state velocity $v_\text{SS}$.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\bjoern{STOP}{HERE}
+
 \subsection{Molecular Dynamics}

### 2024-12-03 paper.tex
pass through methods section

@@
 
-\bjoern{STOP}{HERE}
-
 \subsection{Molecular Dynamics}
-The OSC morphology, that is the spacial coordinate of all the atoms, are generated by molecule dynamics.
-The GROMACS software package~\cite{berendsen_gromacs_1995} is utilized to implement atomistic molecular dynamics simulations of bulk amorphous MADN with the empirical force field obtained via Automated Topology Builder~\cite{stroet_automated_2018}.
-
-The MADN system starts with 1000 MADN molecules randomly placed in a cubic cell with a large enougth side length to allow a low density.
+Classical molecular dynamics (MD) is used to create an amorphous morphology of MADN.
+An empirical force-field for these simulations has been obtained via the Automated Topology Builder~\cite{stroet_automated_2018}, and an initial structure containing 1000 molecules in a cubic cell is created.
 Periodic boundary conditions are applied throughout in all three spatial directions.
-After energy minimization, the system is simulated for \unit[1]{ns} (?) in a $NpT$ ensemble, keeping a constant temperature of \unit[300]{K} and constant pressure of \unit[1]{bar} using the V-rescale thermostat~\cite{bussi_canonical_2007} with the coupling time constant \unit[0.1]{ps} and the Parrinello-Rahman barostat~\cite{parrinello_polymorphic_1981} with a time constant for pressure coupling \unit[2]{ps}.
-The equation of motion for updating the atomic coordinates is implemented by leap-frog algorithm~\cite{van_gunsteren_leap} with a time step of \unit[1]{fs}.
-
-Following this, simulated annealing is applied to relax the MADN.  
-The temperature is increased to \unit[800]{K}, well above the glass transition temperature during a period of \unit[0.5]{ns}. 
+After energy minimization, the system is simulated for \unit[1]{ns} in the $NpT$ ensemble, keeping a constant temperature of \unit[300]{K} and constant pressure of \unit[1]{bar} using the velocity-rescale thermostat~\cite{bussi_canonical_2007} with the coupling time constant \unit[0.1]{ps} and the Parrinello-Rahman barostat~\cite{parrinello_polymorphic_1981} with a time constant for pressure coupling \unit[2]{ps}.
+The equation of motion for updating the atomic coordinates is implemented by leap-frog \bjoern{CHECK}{really?
+not velocity-verlet?} algorithm~\cite{van_gunsteren_leap} with a time step of \unit[1]{fs}.
+Following this, the temperature is increased to \unit[800]{K}, well above the glass transition temperature, during a period of \unit[0.5]{ns}.
 This temperature is maintained for \unit[1]{ns} before cooling back down to \unit[300]{K} during a period of \unit[0.5]{ns}.
-Such heating-cooling cycle is repeated three times.
+Such a heating-cooling cycle is repeated three times.
 After this simulated annealing, a production run is conducted for \unit[2]{ns} using the $NpT$ ensemble.
 The final configuration of MADN is chosen for the further steps in the multiscale model, whose configuration is a cubic box with a length of \unit[9.0]{nm} and a density of $\unit[1.08]{g/cm^3}$.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+All calculations have been performed with the GROMACS software package~\cite{berendsen_gromacs_1995}.
 
@@
 \label{sec:es}
-Starting from an atomic morphology, a first step in first-principle multiscale model is to determine the single-electronic wave function and the associated energy $\epsilon_l$, which are used to obtain atomic charges, reorganization energy, molecule energy, and coupling elements.
-
-Each electron $l$ in a system with $N_\text{el}$ electrons has a single-electronic wave function $\phi_l (\vec{r})$ and associated energies $\epsilon_l$ determined as solutions to the Kohn--Sham equations~\cite{kohn_self_1965}
+Molecular orbitals $\phi_l (\mathbf{r})$ with energies $\epsilon_l$ of the individual molecules in the morphology are obtained within DFT as the solutions to the  Kohn--Sham equations~\cite{kohn_self_1965}
 %
 \begin{eqnarray}
-    && \left(-\frac{1}{2}\nabla^2_{\vec{r}} + v_\text{ext}(\vec{r}) + v_\text{H}[\rho](\vec{r}) + v_\text{XC}[\rho](\vec{r})\right) \phi_l(\vec{r}) \nonumber \\
-    && = H^\text{KS} \phi_l(\vec{r}) = \epsilon_l \phi_l (\vec{r}) ,
+    && \left(-\frac{1}{2}\nabla^2_{\mathbf{r}} + v_\text{ext}(\mathbf{r}) + v_\text{H}[\rho](\mathbf{r}) + v_\text{XC}[\rho](\mathbf{r})\right) \phi_l(\mathbf{r}) \nonumber \\
+    && = H^\text{KS} \phi_l(\mathbf{r}) = \epsilon_l \phi_l (\mathbf{r}) ,
     \label{eq:KS2}
@@
 %
-where $v_\text{ext}$ in an external potential (typically from the nuclei), $v_\text{H}[\rho]$ the electrostatic Hartree potential of a classical charge density $\rho(\vec{r})$, and $v_\text{XC}[\rho]$ the exchange-correlation functional containing explicit quantum-mechanical electron-electron interactions.
-The charge density is determined from the single-particle wave functions as $\rho(\vec{r})=\sum\limits_{l=1}^{N_\text{el}} \left\vert\phi_l(\vec{r})\right\vert^2$.
-As the Hartree and exchange-correlation potential depend on the thus defined density, solutions to Eq.~\ref{eq:KS2} have to be found self-consistently.
-This corresponds to finding the ground-state density $\rho_0$ that minimized the total energy of the system
+where $v_\text{ext}$ in an external potential (typically from the nuclei), $v_\text{H}[\rho]$ the electrostatic Hartree potential of a classical charge density $\rho(\mathbf{r})$, and $v_\text{XC}[\rho]$ the exchange-correlation potential containing explicit quantum-mechanical electron-electron interactions.
+The charge density is determined from the single-particle wave functions as $\rho(\mathbf{r})=\sum\limits_{l=1}^{N_\text{el}} \left\vert\phi_l(\mathbf{r})\right\vert^2$.
+As the Hartree and exchange-correlation potential depend on this density, solutions to Eq.~\ref{eq:KS2} have to be found self-consistently.
+This corresponds to finding the ground-state density $\rho_0$ that minimizes the total energy of the system expressed as
 %
 \begin{equation}
-    U[\rho] = T_s[\rho] + \int v_\text{ext}(\vec{r}) \rho(\vec{r}) d \vec{r} + E_\text{H}[\rho] + E_\text{XC}[\rho]
+    U=U[\rho] = T_s[\rho] + \int v_\text{ext}(\mathbf{r}) \rho(\mathbf{r}) d \vec{r} + E_\text{H}[\rho] + E_\text{XC}[\rho]
     \label{eq:KS_model}
@@
 
-The practical calculations in this work have been performed with the ORCA software~\cite{Neese2012a} using the def2-tzvp~\cite{weigend_accurate_2006} basis set to represent the Kohn--Sham wave functions $\phi_l(\vec{r})$.
-The correlation potential is represented by PBE0 functional, and the exchange potential is represented by a portion $\alpha$ of (HFX) potential and another portion $(1-\alpha)$ from PBE0 functional.
+The practical calculations in this work have been performed with the ORCA software~\cite{Neese2012a} using the def2-tzvp~\cite{weigend_accurate_2006} basis set to represent the Kohn--Sham wave functions.
+As mentioned in the Introduction, the correlation part of the exchange-correlation functional is taken from the PBE0 functional, while the weighting factor of the Hartree--Fock type exchange in the exchange part is varied.
 In common practice, $\alpha$ is small and below 0.25.
-For our uncertain quantification study, $\alpha=0,0.05,0.10,0.15,0.20,0.25$ is chosen for the multiscale model.
+For our uncertain quantification study, $\alpha=0,0.05,0.10,0.15,0.20,0.25$ are chosen for the multiscale model.
 
-\subsection{Transition Rate Calculation}
-Electronic structure calculation via Equation \ref{eq:KS2} and \ref{eq:KS_model} are performed for different combinations of molecular charge states $x=$ n,c and the corresponding equilibrium geometries $X=$ N,C.
-The notion n and N stand for "neutral", and the notion c and C stand for "charged".
-Following this, the total energy will be denoted as $U^\text{xX}$, dropping of the explicit functional dependency on the density $\rho$. 
-The reorganization energy $\lambda$ accounts for the energy change caused by the geometry variation during the charge transport, and is linked to the total energy via:
+\subsection{Reorganiztion Energy}
+ The reorganization energy $\lambda$ accounts for the energy change caused by the geometry variation during the charge transport, and is linked to four points on the potential energy surfaces of neutral (n) and charged (c) molecules at neutral (N) or charged (C) equilibrium geometries via:
 %
 \begin{equation}
-    \lambda_{ij} = U_i^\text{nC} - U_i^\text{nN} + U_j^\text{cN} - U_j^\text{cC}
+    \lambda_{ij} = U_i^\text{nC} - U_i^\text{nN} + U_j^\text{cN} - U_j^\text{cC},
     \label{eq:lambda}
@@
 %
-In this work, the OSC only has one type of molecule, and $\lambda_{ij}$ of all molecular pairs are equal. So the subscript is left out and denoted as $\lambda$.
+where $U^\text{xX}$ is the total DFT energy of $\text{x}=\text{n},\text{c}$ state in the $\text{X}=\text{N},\text{C}$ geometry.
+While in principle transfer pair specific, we use a single value of all molecular pairs.
 
-The molecule energy $E_i = E_i^\text{c} - E_i^\text{n}$ is the difference between the total energies of the system in which molecule $i$ is carrying a charge or not, corresponding to the ionization potential in case of hole transport and the negative of the electron affinity in case of electron transport.
-
-These total energies in turn consist of different contributions associated with different physical mechanism, i.e.,
+\subsection{Site Energy}
+The site energy $E_i = E_i^\text{c} - E_i^\text{n}$ is the difference between the total energies of the system in which molecule $i$ is carrying a charge or not, corresponding to the ionization potential in case of hole transport and the negative of the electron affinity in case of electron transport.
+The individual total energies in turn consist of different contributions associated with different physical mechanism, i.e.,
 %
 \begin{equation}
-E_i^x = U_i^{xX} + E_i^{x,\text{el}} + E_i^{x,\text{polar}},
+E_i^x = U_i^\text{xX} + E_i^{\text{x},\text{el}} + E_i^{\text{x},\text{polar}},
 \label{eq:Es}
@@
 %
-where $U_i^{xX}$ is the internal energy from single molecules as above.
-Both $E_i^{x,\text{el}}$ and $E_i^{x,\text{polar}}$ are contributions arising from intermolecular interactions: $E_i^{x,\text{el}}$ is the electrostatic energy due to the surrounding molecules and $E_i^{x,\text{polar}}$ is the polarization energy.
-These contributions are calculated with a microelectrostatic model using parametrized point charge representations\cite{https://doi.org/10.1002/jcc.540110311}
-
-In the multiscale model, $E_i^{x,\text{el}}$ is evaluated with a \unit[4]{nm} cutoff distance:
+where $U_i^\text{xX}$ is the internal energy contributions and both $E_i^{\text{x},\text{el}}$ and $E_i^{\text{x},\text{polar}}$ are contributions arising from purely static and polarizable intermolecular interactions, respectively.
+As those interactions are typically long-ranged, the intermolecular contributions to the site energy can typically not be calculated with a fully quantum-mechanical method and classical models are adopted, instead, which we refer to as a microelectrostatic model using moment representations parametrized based on single molecule DFT reference data.
+Specifically, in the multiscale model here, we employ a point charge respresentation~\cite{jcc540110311} for the electrostatic potential of charged and neutral molecules, so that the electrostatic energy contribution is
 %
 \begin{equation}
-    E_i^{x,\text{el}} = \frac{1}{4 \pi \epsilon_0} \sum\limits_{a_i} \sum\limits_{b_k,k \neq i} \frac{(q^c_{a_i} - q^n_{b_i})q^n_{b_k}}{ r_{a_i b_k}} 
+    E_i^{\text{x},\text{el}} = \frac{1}{4 \pi \epsilon_0} \sum\limits_{a_i} \sum\limits_{b_k,k \neq i} \frac{q^\text{x}_{a_i}q^n_{b_k}}{ |\mathbf{R}_{a_i} - \mathbf{R}_{b_k}|} 
 \end{equation}
 %
-where $\epsilon_0$ is the vacuum permittivity, $a_i, b_k$ denotes the atoms in molecule $i,k$, $q^{n(c)}_{a_i}$ are the partial charge of atom $a$ when molecule $i$ is in state x.
-And $r_{a_i b_k} = |r_{a_i} - r_{b_k}|$ is the distance between atoms $a_i$ and $b_k$, which should be within \unit[4]{nm} due to the cutoff setting.
-For the purpose of quantifying uncertainty in HFX, the long-range electrostatic interactions are not considered.
-
-The polarization effects are determined self-consistently to consider the response of the molecules to the associated fields~\cite{thole_molecular_1981}.
-Polarization effects are considered in a region of \unit[4.0]{nm} around each individual molecule.
+where $\epsilon_0$ is the vacuum permittivity, $a_i, b_k$ denotes the atoms in molecule $i,k$, $q^{\text{x}}_{a_i}$ are the partial charge of atom $a$ when molecule $i$ is in state $\text{x}$.
+To account for effects of polarization, and to evaluate $ E_i^{\text{x},\text{polar}}$, we use the model of distributed atomic dipole polarizabilities (Thole model)~\cite{thole_molecular_1981}, in which the parameters are also determined such that the classical volume of the molecular polarizability tensor matches the DFT reference.
+Intermoelcular effects are considered in a region of \unit[4.0]{nm} around each individual molecule.
 Practical calculations of the site energies are performed using the VOTCA software~\cite{Baumeier2011,doi:10.1021/acs.jctc.8b00617,10.1063/1.5144277,Baumeier2024}.
 
-The coupling element $J_{ij}$ between molecule $i$ and $j$ describe the coupling strength between two localized states.
-In the case of hole transport, the relevant orbitals are highest-occupied molecular orbital (HOMO) of the isolated molecules (monomers) $\phi^\text{HOMO}_i(\vec{r})$ and $\phi^\text{HOMO}_j(\vec{r})$,
-leading to the calculation of $J_{ij}$ is implemented using the Dimer-Projection Method~\cite{baumeier_density_2010}. Specifically, the coupling element is determined as:
-Specifically, the coupling element is determined as: 
+\subsection{Electronic Coupling Elements}
+The coupling element $J_{ij}$ between molecule $i$ and $j$ describe the coupling strength between two localized states, here approximated by monomer single-particle wavefunctions $\vert \phi_i\rangle$ and $\vert\phi_j\rangle$, respectively.
+For hole transport, the relevant orbitals are highest-occupied molecular orbital (HOMO).
+Using the Dimer-Projection Method~\cite{baumeier_density_2010} the coupling element is determined as:
 %
@@
 %
-where $J^0_{ij} = \langle \phi^\text{HOMO}_i | \hat{H}^\text{KS}_\text{D} | \phi^\text{HOMO}_j \rangle $, $e_i = \langle \phi^\text{HOMO}_i | \hat{H}^\text{KS}_\text{D} | \phi^\text{HOMO}_i \rangle $, $e_j = \langle \phi^\text{HOMO}_j | \hat{H}^\text{KS}_\text{D} | \phi^\text{HOMO}_j \rangle $, and $S_{ij}=\langle \phi^\text{HOMO}_i | \phi^\text{HOMO}_j \rangle $ with bra-ket notation.
-and $H^\text{KS}_\text{D}$ is the Hamiltonian of the dimer (see Eq.~\ref{eq:KS2}). 
-As the Hamiltonian of the dimer is diagonal in its eigenbasis $\left\{ \phi_\text{D}(\vec{r})\right\}$ with eigenvalues $\left\{ \epsilon_D\right\}$, so $H^\text{KS}_\text{D} = \text{diag}(\epsilon_D)$, $J^0_{ij}$ can be calculated as $J^0_{ij} = \mathbf{p}_i^\text{T} \text{diag}(\epsilon_\text{D}) \mathbf{p}_j$,  where the vector $\mathbf{p}_i = \langle \phi_i^\text{HOMO} | \phi^\text{HOMO}_\text{D} \rangle$ and $\mathbf{p}_j = \langle \phi_j^\text{HOMO} | \phi_\text{D}^\text{HOMO} \rangle$ are the projections of the monomer orbitals $\phi_i^\text{HOMO}, \phi_j^\text{HOMO}$ onto the dimer orbitals $\phi^\text{HOMO}_\text{D}$.
+where $J^0_{ij} = \langle \phi_i | \hat{H}^\text{KS}_\text{D} | \phi_j \rangle $, $e_i = \langle \phi_i | \hat{H}^\text{KS}_\text{D} | \phi_i \rangle $, $e_j = \langle \phi_j | \hat{H}^\text{KS}_\text{D} | \phi_j \rangle $, and $S_{ij}=\langle \phi_i | \phi_j \rangle $ with bra-ket notation.
+The Hamiltonian of the dimer,  $H^\text{KS}_\text{D}$ (see Eq.~\ref{eq:KS2}), is diagonal in its eigenbasis $\left\{\vert \phi^\text{D}_k\rangle\right\}$ with eigenvalues $\left\{ \epsilon^\text{D}_k\right\}$, so $H^\text{KS}_\text{D} = \text{diag}(\epsilon^\text{D})$.
+With the projections of the monomer functions on the dimer eigenbasis, i.e., $p_{ik} = \langle \phi_i | \phi^\text{D}_k \rangle$ and  $p_{jk} = \langle \phi_j | \phi^\text{D}_k \rangle$, $J^0_{ij}$ can be calculated as $J^0_{ij} = \mathbf{p}_i^\text{T} \text{diag}(\epsilon^\text{D}) \mathbf{p}_j$.
 Similarly, $e_{i(j)} = \mathbf{p}_{i(j)}^\text{T} \mathbf{p}_{i(j)}$ and $S_{ij} =  \mathbf{p}_i^\text{T} \mathbf{p}_j$.
@@
 \subsection{Time-of-flight Calculation}
-Following the graph $\mathbf{G}$ from the multiscale model,
-The charge dynamics are modeled as a continuous-time random walk on this graph.
-In the time-of-flight (ToF) model, some vertices serve as \textit{Source} nodes, representing the electrode where charge carriers are injected, and some as \textit{Sink} nodes, where charge carriers are detected and the ToF is recorded.
+After constructing the  graph $\mathbf{G}$ from the multiscale model, charge dynamics are modeled as a continuous-time random walk on this graph.
+In the time-of-flight (ToF) model, some vertices serve as source nodes, representing the electrode where charge carriers are injected, and some as sink nodes, where charge carriers are detected and the ToF is recorded.
 In CTRW the ToF is calculated as the expected hitting time of a continuous time Markov chain.
-For a system with $N$ molecules and one charge carriers, there are $N$ possible occupation states.
-A state is called the Source state if one of the Source molecule is occupied, and a Sink state is the one when one of the Sink molecule is occupied.
-
-The transition rates between the states define the adjacency matrix $\mathbf{W}:\omega_{ij}$.
-According to such connectivity between the molecules, the transition rates $\mathbf{W}_{ij}$ from state $i$ to $j$ is:
+For a system with $N$ molecules and one charge carrier, the transition rates between the molecules define the adjacency matrix $\mathbf{W}$:
 %
@@
 Then the transition probability from state $i$ to $j$ is $p_{ij} = \mathbf{W}_{ij}/D_i$ where $D_i := \sum_{j} \mathbf{W}_{ij}$.
-And the expected time from state $i$ to reach the Sink state $\tau_i$ is calculated via: 
+And the expected time from node $i$ to reach the sink $\tau_i$ is calculated via: 
 %
@@
 	\tau_i = \begin{cases}
-		\frac{1}{D_i} + \sum_{j \ne i} p_{ij} \tau_{j} &\text{if $i$ is not a sink state},\\
+		\frac{1}{D_i} + \sum_{j \ne i} p_{ij} \tau_{j} &\text{if $i$ is not a sink node},\\
 		0 &\text{else.} 
@@
 
-To account for all possible starting nodes of the carriers, all Source states must be considered.
+To account for all possible starting nodes of the carrier, all source nodes must be considered.
 The random walk process can be modeled as a parallel electric network of capacitors~\cite{doyle_random_1984}.
@@
 %
-where $N_\text{source}$ is the number of Source states.
+where $N_\text{source}$ is the number of source nodes.
 
-%To calculate $v_\text{SS}$ the steady state distribution $\pi_i$ is required.
-In continuous time Markov chain, the steady state distribution vector $\vec{\pi}: \pi_i$ is the null-space of $\mathbf{W}-\mathbf{D}$:
-%\begin{equation}
-%    (\mathbf{W}-\mathbf{D} )\vec{\pi} = \mathbf{0}
-%\end{equation}
-%where $\mathbf{D} = \text{diag}(D_i)$ is the out-degree matrix of $\mathbf{W}$.
+To determine the ToF in the simulated MADN system along the positive $x$-direction, we remove the PBC in this direction and define the nodes with coordinates $\unit[0]{nm} < x < \unit[0.5]{nm}$ as source nodes, and those with coordinates $\unit[8.5]{nm} < x < \unit[9]{nm}$ as sink nodes.
+These definitions are changed accordingly for simulating transport in negative $x$-direction, and $y$- or $z$-directions.
 
-%\begin{equation}
-%    v_\text{SS} = \sum_i \pi_i \sum_j \omega_{ij} || \vec{r}_{ij}||_2
-%\end{equation} 
-%where $\omega_{ij}$ is the charge transition rate from molecule $i$ to molecule $j$, and $\vec{r}_{ij}=\vec{r}_j - \vec{r}_i$ is the center-of-mass (COM) distance vector. 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\bjoern{STOP}{HERE}
 
@@
 
-To calculate the ToF from the electronic structures, the \textit{Source} region contains molecules with X-coordinate $0 < r^x_i < 0.5$ nm, and the \textit{Sink} region contains molecules with X-coordinate $8.5 < r^x_i < 9$ nm.
+To calculate the ToF from the electronic structures, the \textit{Source} region contains molecules with X-coordinate
 

### 2024-12-06 paper.tex
some rearrangements and removal of too extensive Wasserstein distance discussion

@@
 \usepackage{xcolor}
+\usepackage{xspace}
 
 \newcommand{\bjoern}[2]{{\color{blue}{{\bf #1} #2}}}
+\newcommand{\ahfx}{\ensuremath{\alpha_\text{HFX}}\xspace}
 
@@
 
-%Those transition rates charge transfer rates from molecules $i$ to $j$ is calculated as the bi-molecular transition rates:
-%
-%\begin{equation}
-%    \omega_{ij} = \frac{2\pi}{\hbar} \frac{|J_{ij}|^2}{\sqrt{4\pi \lambda_{ij} k_\text{B}T}} \exp\left(-\frac{(\Delta E_{ij} + q \vec{F} \cdot \vec{r}_{ij} - \lambda_{ij})^2}{4\lambda_{ij} k_\text{B}T}\right) ,
-%    \label{equ:Marcus2}
-%\end{equation}
-%
-%where $\hbar$ is the reduced Planck constant and $k_\text{B}$ the Boltzmann constant.
-The temperature $T$ (in \unit[]{K}), the charge of the carrier $q$ (in \unit[]{e}) and the external electric field $\vec{F}$ (in V/m) can be considered the external, environmental parameters of the simulation.
-The vector $\vec{r}_{ij} = (r^x_{ij},r^y_{ij},r^z_{ij})^\text{T}$ connects the center-of-masses (COMs) of molecules $i$ and $j$, which is calculated using cyclic boundary conditions.
-%The remaining physical, material-specific (or rather transfer-pair-specific) quantities are the reorganization energy $\lambda_{ij}$, the electronic coupling $J_{ij}$, and the energy difference $E_{ij} = E_i - E_j$ (all in \unit[]{eV}).
-
-%The rest of this section will introduce the following: the molecular dynamics used to obtain the coordinates $r^x_{i},r^y_{i},r^z_{i}$, the calculation of node-specific quantities $\lambda$, $E_i$ and $J_{ij}$, as well as the calculation of ToF $\tau$ and steady state velocity $v_\text{SS}$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \subsection{Molecular Dynamics}
@@
 After energy minimization, the system is simulated for \unit[1]{ns} in the $NpT$ ensemble, keeping a constant temperature of \unit[300]{K} and constant pressure of \unit[1]{bar} using the velocity-rescale thermostat~\cite{bussi_canonical_2007} with the coupling time constant \unit[0.1]{ps} and the Parrinello-Rahman barostat~\cite{parrinello_polymorphic_1981} with a time constant for pressure coupling \unit[2]{ps}.
-The equation of motion for updating the atomic coordinates is implemented by leap-frog \bjoern{CHECK}{really?
-not velocity-verlet?} algorithm~\cite{van_gunsteren_leap} with a time step of \unit[1]{fs}.
+The equation of motion for updating the atomic coordinates is implemented by leap-frog algorithm~\cite{van_gunsteren_leap} with a time step of \unit[1]{fs}.
 Following this, the temperature is increased to \unit[800]{K}, well above the glass transition temperature, during a period of \unit[0.5]{ns}.
@@
 
-\bjoern{STOP}{HERE}
-
-\section{Results on MADN}
+\section{Explicit Results from the Multiscale Model}
 \label{sec:MSMresults}
-In this study, we investigate the hole-transporting organic semiconductor MADN (2-Methyl-9,10-di(naphth-2-yl)anthracene) and study its charge mobility's dependence on HFX.
+In this section, we present and analyze the explicit results of the multiscale model of charge transport in amorphous MADN as obtained for different values of $\alpha_\text{HFX}$.
 
 \subsection{Molecular Parameters}
-Atomic charges and molecule polarizability $P_\text{iso}$ are crucial for evaluating molecular energy contributions from electrostatic and polarization effects.
-A physical property related to the overall atomic charges is dipole moment at charge neutral state.
-
-To calculate the ToF from the electronic structures, the \textit{Source} region contains molecules with X-coordinate
 
@@
     \includegraphics[width=\linewidth]{figs/fig_autogen.pdf}
-    \caption{\bjoern{TODO Zhong:}{The labels (a), (b), (c),(d) should be bigger and places at slightly to the left from the individual panels, which includes the y axis labels; panel (b): these atomic units can be abbreviated a.u.
-and you should also use [a.u.] and not round brackets; pane (d) is missing a ); I would also like to use $\alpha_{HF}$ throughout the paper; change $\mu$ to $d$.}(a) The dipole moment of neutral state MAND molecule $\mu$, (b) isotropic polarizability $P_\text{iso}$, (c) reorganization energies $\lambda$ and (d) energy disorder $\sigma(E)$ as a function of the HFX parameters (denoted by $\alpha$).}
+    \caption{Dependence of molecular parameters as used directly in the multiscale model or in its paramaterization phase on the amount of Hartree--Fock type exchange in the PBE0-based hybrid functional $\alpha_\text{HFX}$.
+(a) The adiabatic ionization potential, (b) reorganization energy, (c) dipole moment of the neutral molecule, and (d) isotropic molecular polarizability in neutral and charged states, respectively.}
     \label{fig:autogen_MADN}
@@
 
-To demonstration the effect of HFX on the atomic charges and molecule polarizability $P_\text{iso}$, Fig.~\ref{fig:autogen_MADN}(a)(b) illustrates the dependence of the dipole moment $\mu$ and isotropic polarizability $P_\text{iso}$ on HFX.
-Figure~\ref{fig:autogen_MADN}(c)(d) show the reorganization energy $\lambda$ and energy disorder $\sigma(E)$ as a function of HFX parameter are also shown in Fig.~\ref{fig:autogen_MADN}(c)(d).
+We begin with a brief discussion of the molecular parameters as they are used in different ways in the multiscale model.
+Figure~\ref{fig:autogen_MADN} shows the adiabatic ionization potential, reorganization energy, neutral state dipole moment, and isotropic polarizability in neutral and cationic (hole) states, respectively.
+The adiabatic ionization potential in Fig.~\ref{fig:autogen_MADN}(a) in principle contributes to the site energy but as it is determined per molecule-type in the system, it has no effect on the site-energy difference $\Delta E_{ij}$ in Eq.~\ref{equ:Marcus}.
+It is nevertheless interesting to see that it increases almost linearly over the shown range of \ahfx.
+In contrast, the reorganization energy as shown in Fig.~\ref{fig:autogen_MADN}(b) appears to saturate for \ahfx after an initially close to linear increase.
+In total, $\lambda$ is found to be in an interval between \unit[0.25]{eV} and \unit[0.31]{eV} \bjoern{need}{correct numbers here}.
+Panels (c) and (d) of Fig.~\ref{fig:autogen_MADN} show the dipole moment of the neutral MADN molecule and the isotropic polarizability of the neutral and cationic (hole) states, respectively, both as electrostatic properties that enter indirectly the parameterization of the microelectrostatic model.
+As is visible, the dipole moment is rather independent on \ahfx (note that the jump of the last shown data point appears more pronounced because of the vert small scale on the $y$-axis).
+The isotropic polarizabilities in panel (d) exhibit a linear decrease with increasing value of \ahfx which can be attributed to an increasingly attractive effective potential from stronger the Hartree--Fock-like exchange term and consequently more strongly bound electrons as one can also see from the increaseing ionization potential in panel (a).
 
-From Fig.~\ref{fig:autogen_MADN}(a) one can notice a mild decrease in the dipole moment with increasing HFX and in Fig.~\ref{fig:autogen_MADN}(b) a linear decrease in isotropic polarizability for both neutral and charged MADN states as HFX increases from 0 to 0.25, indicating reduced molecular polarizability.
-Figure~\ref{fig:autogen_MADN}(c) indicates an increase in reorganization energy $\lambda$ with higher HFX, reflecting greater energy requirements for electronic adjustments during charge transfer.
-This increase is nonlinear compared to the linear decrease in $P_\text{iso}$.
-Figure~\ref{fig:autogen_MADN}(d) shows that the energy disorder $\sigma(E)$ for MADN are similar and close to \unit[0.08]{eV} under different HFX values.
+\subsection{Distributions of site energies}
 
-The ToF is also calculated without energy disorder, meaning $\Delta E_{ij}=0$ for all $i,j$.
-Table~\ref{tab:ToF_MADN_HFX} shows the ToF and corresponding diffusive velocity $v_\text{ToF}$.
-With energy disorder, the ToF increases by a factor of approximately 15 as $\alpha$ increases from 0 to 0.25.  
-While without energy disorder, the increase factor is about 4. This increase in ToF is attributed to the rise in $\lambda$, changes in molecular energies, and variations in coupling elements.
+\bjoern{STOP}{HERE}
 
-\begin{table}[tbp]
-\caption{The ToF and diffusive velocity calculated by ToF along a distance $L_x = \unit[9.0]{nm}$ with and without energy disorder of the MADN system as a function of the HFX.
-The ToF is in unit $\unit[]{s}$ and $v_\text{ToF}$ in unit $\unit[]{m/s}$.}
-\begin{ruledtabular}
-  \begin{tabular}{c c c c c}
-        $\alpha$ & ToF& $v_\text{ToF}$ & ToF(no $E$)& $v_\text{ToF}$(no $E$) \\
-    \hline
-        0.00 &  $6.4 \times 10^{-9}$ & 1.2 & $1.9 \times 10^{-10}$ & 42 \\
-        0.05 & $ 7.9 \times 10^{-9}$ & 1.0 & $4.1 \times 10^{-10}$ & 20 \\
-        0.10 & $ 1.6 \times 10^{-8}$ & 0.51 & $4.0 \times 10^{-10} $ & 20 \\
-        0.15 & $ 3.0 \times 10^{-8}$ & 0.31 & $4.0 \times 10^{-10} $ & 25 \\
-        0.20 & $ 2.1 \times 10^{-8}$ & 0.39 & $4.5 \times 10^{-10}$ & 18 \\
-        0.25 & $ 9.5 \times 10^{-8}$ & 0.083 & $7.2 \times 10^{-10}$ & 11 \\
-    \end{tabular}
-\end{ruledtabular}
-\label{tab:ToF_MADN_HFX}
-\end{table}
-
-\begin{table*}[tbp]%The best place to locate the table environment is directly after its first reference in text
-\caption{\label{tab:W2_E}%
-The 1-Wasserstein distance between the distributions pair of molecule energy $P_{E(\alpha)}$, electrostatic energy $P_{E^\text{el}(\alpha)}$, polar energy $P_{E^\text{polar}(\alpha)}$ and $P_{\log_{10}(J_{ij}^2)(\alpha)}$.
-}
-\begin{ruledtabular}
-  \begin{tabular}{c c c c c c}
-  $\alpha'$ & 0 & 0.05 & 0.10 & 0.15 & 0.20 \\
-    \hline
-  $W_1 (P_{E(\alpha')}, P_{E(\alpha=0.25)})$ &  0.0054 & 0.0091 & 0.0067 & 0.0053 & 0.0045 \\
-  $W_1 (P_{E^\text{el}(\alpha')}, P_{E^\text{el}(\alpha=0.25)})$ &  0.010 & 0.012 & 0.0089 & 0.0070 & 0.0032 \\
-  $W_1 (P_{E^\text{polar}(\alpha')}, P_{E^\text{polar}(\alpha=0.25)})$ &  0.0065 & 0.0043 & 0.0027 & 0.0023 & 0.0031 \\
-  $W_1 (P_{\log_{10}(J_{ij}^2)(\alpha')}, P_{\log_{10}(J_{ij}^2)(\alpha=0.25)})$ &  0.0054 & 0.0091 & 0.0067 & 0.0053 & 0.0045 \\
-    \end{tabular}
-\end{ruledtabular}
-\end{table*}
+%\begin{table*}[tbp]%The best place to locate the table environment is directly after its first reference in text
+%\caption{\label{tab:W2_E}%
+%The 1-Wasserstein distance between the distributions pair of molecule energy $P_{E(\alpha)}$, electrostatic energy $P_{E^\text{el}(\alpha)}$, polar energy $P_{E^\text{polar}(\alpha)}$ and $P_{\log_{10}(J_{ij}^2)(\alpha)}$.
+%}
+%\begin{ruledtabular}
+%  \begin{tabular}{c c c c c c}
+%  $\alpha'$ & 0 & 0.05 & 0.10 & 0.15 & 0.20 \\
+%    \hline
+%  $W_1 (P_{E(\alpha')}, P_{E(\alpha=0.25)})$ &  0.0054 & 0.0091 & 0.0067 & 0.0053 & 0.0045 \\
+%  $W_1 (P_{E^\text{el}(\alpha')}, P_{E^\text{el}(\alpha=0.25)})$ &  0.010 & 0.012 & 0.0089 & 0.0070 & 0.0032 \\
+%  $W_1 (P_{E^\text{polar}(\alpha')}, P_{E^\text{polar}(\alpha=0.25)})$ &  0.0065 & 0.0043 & 0.0027 & 0.0023 & 0.0031 \\
+%  $W_1 (P_{\log_{10}(J_{ij}^2)(\alpha')}, P_{\log_{10}(J_{ij}^2)(\alpha=0.25)})$ &  0.0054 & 0.0091 & 0.0067 & 0.0053 & 0.0045 \\
+%    \end{tabular}
+%\end{ruledtabular}
+%\end{table*}
 %
@@
   \label{fig:E_qmmm_MADN}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.80\textwidth]{figs/scatterEstat_qmmm.pdf}
-  \caption{\bjoern{TODO Zhong:}{add labels (a)...; replace $\alpha$ with $\alpha_\text{HF}$.}Scatter plot of MADN electrostatic energy calculated from different HFX, compared to the electrostatic energy calculated from HFX=0.25 (The PBE0 functional).
-The brighter color near the diagonal lines indicates denser population of the molecules.
-The top and right histogram show the energy distributions.}
-  \label{fig:Estat_qmmm_MADN}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.80\textwidth]{figs/scatterEdip_qmmm.pdf}
-  \caption{\bjoern{TODO Zhong:}{add labels (a)...; replace $\alpha$ with $\alpha_\text{HF}$.}Scatter plot of MADN polarization energy calculated from different HFX, compared to the polarization energy calculated from HFX=0.25 (The PBE0 functional).
-The brighter color near the diagonal lines indicates denser population of the molecules.
-The top and right histogram show the energy distributions.}
-  \label{fig:Edip_qmmm_MADN}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.80\textwidth]{figs/scatterJ_all.pdf}
-  \caption{\bjoern{TODO Zhong:}{add labels (a)...; replace $\alpha$ with $\alpha_\text{HF}$; it should be $\log_{10}(J^2/(\unit[]{eV})^2)$; make sure the 10 of $\log_{10}$ is not touching $J$.} Scatter plot of MADN coupling element $\log_{10} J^2$ calculated from different HFX, compared to the polarization energy calculated from HFX=0.25 (The PBE0 functional).
-The brighter color near the diagonal lines indicates denser population of the molecules.
-The top and right histogram show the energy distributions.}
-  \label{fig:J_MADN}
 \end{figure*}
@@
 
-To quantify the similarity between two empirical distribution, Wasserstein distance~\cite{villani_optimal_2009} is used.
-Denote the empirical distribution of molecular energy $E$ at $\alpha=0$ to be $P_{E(\alpha=0)}$. 
-The 1-Wasserstein distance between $P_{E(\alpha=0)}$ and $P_{E(\alpha=0.25)}$ is calculated as:
-\begin{eqnarray}
-    && W_1 (P_{E(\alpha=0)}, P_{E(\alpha=0.25)}) = \nonumber \\
-    && \frac{1}{N} \sum\limits_{i=1}^N | E_{(i)}(\alpha=0) - E_{(i)}(\alpha=0.25) |
-\end{eqnarray}
-where $E_{(i)}(\alpha=0)$ is the order statistics of $E_i(\alpha=0)$.
+%To quantify the similarity between two empirical distribution, Wasserstein distance~\cite{villani_optimal_2009} is used.
+%Denote the empirical distribution of molecular energy $E$ at $\alpha=0$ to be $P_{E(\alpha=0)}$. 
+%The 1-Wasserstein distance between $P_{E(\alpha=0)}$ and $P_{E(\alpha=0.25)}$ is calculated as:
+%\begin{eqnarray}
+%    && W_1 (P_{E(\alpha=0)}, P_{E(\alpha=0.25)}) = \nonumber \\
+%    && \frac{1}{N} \sum\limits_{i=1}^N | E_{(i)}(\alpha=0) - E_{(i)}(\alpha=0.25) |
+%\end{eqnarray}
+%where $E_{(i)}(\alpha=0)$ is the order statistics of $E_i(\alpha=0)$.
 The 1-Wasserstein distance between two empirical distributions for each plot in Fig.
@@
 So the maximum energy variation quantified by $\max(|E_i(\alpha=0.25) - E_i(\alpha')|)$ is not likely to results in large change in ToF due to trapping effects.
-%
-\begin{table}[tbp]%The best place to locate the table environment is directly after its first reference in text
+
+\begin{table}[tbp]
 \caption{\label{tab:maxEi}%
@@
 Each individual molecule has similar polarization energies under different HFX calculation, in spite of $P_\text{iso}$ is linearly dependent on HFX.
+
+\subsection{Distributions of electronic couplings}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.80\textwidth]{figs/scatterJ_all.pdf}
+  \caption{\bjoern{TODO Zhong:}{add labels (a)...; replace $\alpha$ with $\alpha_\text{HF}$; it should be $\log_{10}(J^2/(\unit[]{eV})^2)$; make sure the 10 of $\log_{10}$ is not touching $J$.} Scatter plot of MADN coupling element $\log_{10} J^2$ calculated from different HFX, compared to the polarization energy calculated from HFX=0.25 (The PBE0 functional).
+The brighter color near the diagonal lines indicates denser population of the molecules.
+The top and right histogram show the energy distributions.}
+  \label{fig:J_MADN}
+\end{figure*}
 
@@
 And further we estimate the range of the quantity of interest, given a confidence level.
+
+The ToF is also calculated without energy disorder, meaning $\Delta E_{ij}=0$ for all $i,j$.
+Table~\ref{tab:ToF_MADN_HFX} shows the ToF and corresponding diffusive velocity $v_\text{ToF}$.
+With energy disorder, the ToF increases by a factor of approximately 15 as $\alpha$ increases from 0 to 0.25.  
+While without energy disorder, the increase factor is about 4. This increase in ToF is attributed to the rise in $\lambda$, changes in molecular energies, and variations in coupling elements.
+
+\begin{table}[tbp]
+\caption{The ToF and diffusive velocity calculated by ToF along a distance $L_x = \unit[9.0]{nm}$ with and without energy disorder of the MADN system as a function of the HFX.
+The ToF is in unit $\unit[]{s}$ and $v_\text{ToF}$ in unit $\unit[]{m/s}$.}
+\begin{ruledtabular}
+  \begin{tabular}{c c c c c}
+        $\alpha$ & ToF& $v_\text{ToF}$ & ToF(no $E$)& $v_\text{ToF}$(no $E$) \\
+    \hline
+        0.00 &  $6.4 \times 10^{-9}$ & 1.2 & $1.9 \times 10^{-10}$ & 42 \\
+        0.05 & $ 7.9 \times 10^{-9}$ & 1.0 & $4.1 \times 10^{-10}$ & 20 \\
+        0.10 & $ 1.6 \times 10^{-8}$ & 0.51 & $4.0 \times 10^{-10} $ & 20 \\
+        0.15 & $ 3.0 \times 10^{-8}$ & 0.31 & $4.0 \times 10^{-10} $ & 25 \\
+        0.20 & $ 2.1 \times 10^{-8}$ & 0.39 & $4.5 \times 10^{-10}$ & 18 \\
+        0.25 & $ 9.5 \times 10^{-8}$ & 0.083 & $7.2 \times 10^{-10}$ & 11 \\
+    \end{tabular}
+\end{ruledtabular}
+\label{tab:ToF_MADN_HFX}
+\end{table}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\section{ToF Distribution and Sensitivity Analysis}
+\section{Uncertainty Quantification and Sensitivity Analysis}
 \label{sec:UQ}
@@
 Future research should explore the impact of other sources of uncertainty and extend this framework to different types of semiconducting materials, thus enhancing the predictive power and applicability of multiscale models in the field.
-% The \nocite command causes all entries in a bibliography to be printed out
-% whether or not they are actually referenced in the text. This is appropriate
-% for the sample file to show the different styles of references, but authors
-% most likely will not want to use it.
-%\nocite{*}
 
-\bibliography{references}% Produces the bibliography via BibTeX.
+\bibliography{references}
+
+\appendix*
+\section{Electrostatic and polarized energy contributions}
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.80\textwidth]{figs/scatterEstat_qmmm.pdf}
+  \caption{\bjoern{TODO Zhong:}{add labels (a)...; replace $\alpha$ with $\alpha_\text{HF}$.}Scatter plot of MADN electrostatic energy calculated from different HFX, compared to the electrostatic energy calculated from HFX=0.25 (The PBE0 functional).
+The brighter color near the diagonal lines indicates denser population of the molecules.
+The top and right histogram show the energy distributions.}
+  \label{fig:Estat_qmmm_MADN}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.80\textwidth]{figs/scatterEdip_qmmm.pdf}
+  \caption{\bjoern{TODO Zhong:}{add labels (a)...; replace $\alpha$ with $\alpha_\text{HF}$.}Scatter plot of MADN polarization energy calculated from different HFX, compared to the polarization energy calculated from HFX=0.25 (The PBE0 functional).
+The brighter color near the diagonal lines indicates denser population of the molecules.
+The top and right histogram show the energy distributions.}
+  \label{fig:Edip_qmmm_MADN}
+\end{figure*}
 
 \end{document}
-%
-% ****** End of file apssamp.tex ******

### 2024-12-09 figs/energy_data/plot_scatterE_qmmm.py
add energy data

@@ -1,0 +1,158 @@
+from scipy.stats import wasserstein_distance
+from scipy.stats import entropy
+import scipy.stats as stats
+
+import numpy as np
+import scipy as sp
+import matplotlib.pyplot as plt
+import math
+import matplotlib.gridspec as gridspec
+import matplotlib as mpl
+import matplotlib.ticker as mticker
+
+k_B = 8.617333 * 10**(-5) # ev/K
+pi = math.pi
+hbar = 6.582119569 * 1e-16 # eV*s
+T = 300
+
+def Marcus(E,J,re):
+    temp = 2*pi/hbar * J**2/math.sqrt(4*pi*(re*k_B*300))*math.exp(-(E-re)**2/(4*re*k_B*300) )
+    return temp
+
+tick_font_size = 13
+
+def scatter_hist(x, y, ax, ax_histx, ax_histy):
+    # no labels
+    ax.set_facecolor('white')
+    ax_histx.set_facecolor('white')
+    ax_histy.set_facecolor('white')
+
+    ax_histx.tick_params(axis="x", labelbottom=False,labelsize=tick_font_size)
+    ax_histx.tick_params(axis="y", labelleft=False,labelsize=tick_font_size)
+
+    ax_histy.tick_params(axis="y", labelleft=False,labelsize = tick_font_size)
+    ax_histy.tick_params(axis="x", labelbottom=False,labelsize = tick_font_size)
+    # plt.style.use('_mpl-gallery-nogrid')
+    # ax.hist2d(x, y,bins=50,norm=mpl.colors.LogNorm())
+    # fig.colorbar(ax.hist2d(x, y,bins=50,norm=mpl.colors.LogNorm())[3],location='left')
+    nbins = 30
+    # now determine nice limits by hand:
+    xmin = -1.4
+    xmax = -0.4
+    ax_histx.hist(x,bins=nbins, range=(xmin,xmax),color = "blue")
+    
+    ymin = -1.4
+    ymax = -0.4
+    width = 0.05
+    ax_histy.hist(y,bins=nbins, range=(ymin,ymax), orientation='horizontal',color = "blue")
+
+    plt.style.use('ggplot')
+    #plt.grid(False)
[…]

### 2024-12-09 figs/energy_data/plot_scatterEdip_qmmm.py

@@ -1,0 +1,156 @@
+from scipy.stats import wasserstein_distance
+from scipy.stats import entropy
+import scipy.stats as stats
+
+import numpy as np
+import scipy as sp
+import matplotlib.pyplot as plt
+import math
+import matplotlib.gridspec as gridspec
+import matplotlib as mpl
+import matplotlib.ticker as mticker
+
+k_B = 8.617333 * 10**(-5) # ev/K
+pi = math.pi
+hbar = 6.582119569 * 1e-16 # eV*s
+T = 300
+
+def Marcus(E,J,re):
+    temp = 2*pi/hbar * J**2/math.sqrt(4*pi*(re*k_B*300))*math.exp(-(E-re)**2/(4*re*k_B*300) )
+    return temp
+
+tick_font_size = 13
+
+def scatter_hist(x, y, ax, ax_histx, ax_histy):
+    # no labels
+    ax.set_facecolor('white')
+    ax_histx.set_facecolor('white')
+    ax_histy.set_facecolor('white')
+
+    ax_histx.tick_params(axis="x", labelbottom=False,labelsize=tick_font_size)
+    ax_histx.tick_params(axis="y", labelleft=False,labelsize=tick_font_size)
+
+    ax_histy.tick_params(axis="y", labelleft=False,labelsize = tick_font_size)
+    ax_histy.tick_params(axis="x", labelbottom=False,labelsize = tick_font_size)
+    # plt.style.use('_mpl-gallery-nogrid')
+    # ax.hist2d(x, y,bins=50,norm=mpl.colors.LogNorm())
+    # fig.colorbar(ax.hist2d(x, y,bins=50,norm=mpl.colors.LogNorm())[3],location='left')
+    nbins = 30
+    # now determine nice limits by hand:
+    xmin = -0.9
+    xmax = -0.4
+    ax_histx.hist(x,bins=nbins, range=(xmin,xmax),color = "blue")
+    
+    ymin = -0.9
+    ymax = -0.4
+    width = 0.02
+    ax_histy.hist(y,bins=nbins, range=(ymin,ymax), orientation='horizontal',color = "blue")
+
+    plt.style.use('ggplot')
+    #plt.grid(False)
[…]

### 2024-12-09 figs/energy_data/plot_scatterEstat_qmmm.py

@@ -1,0 +1,155 @@
+from scipy.stats import wasserstein_distance
+from scipy.stats import entropy
+import scipy.stats as stats
+
+import numpy as np
+import scipy as sp
+import matplotlib.pyplot as plt
+import math
+import matplotlib.gridspec as gridspec
+import matplotlib as mpl
+import matplotlib.ticker as mticker
+
+k_B = 8.617333 * 10**(-5) # ev/K
+pi = math.pi
+hbar = 6.582119569 * 1e-16 # eV*s
+T = 300
+
+def Marcus(E,J,re):
+    temp = 2*pi/hbar * J**2/math.sqrt(4*pi*(re*k_B*300))*math.exp(-(E-re)**2/(4*re*k_B*300) )
+    return temp
+
+tick_font_size = 13
+
+def scatter_hist(x, y, ax, ax_histx, ax_histy):
+    # no labels
+    ax.set_facecolor('white')
+    ax_histx.set_facecolor('white')
+    ax_histy.set_facecolor('white')
+
+    ax_histx.tick_params(axis="x", labelbottom=False,labelsize=tick_font_size)
+    ax_histx.tick_params(axis="y", labelleft=False,labelsize=tick_font_size)
+
+    ax_histy.tick_params(axis="y", labelleft=False,labelsize = tick_font_size)
+    ax_histy.tick_params(axis="x", labelbottom=False,labelsize = tick_font_size)
+    # plt.style.use('_mpl-gallery-nogrid')
+    # ax.hist2d(x, y,bins=50,norm=mpl.colors.LogNorm())
+    # fig.colorbar(ax.hist2d(x, y,bins=50,norm=mpl.colors.LogNorm())[3],location='left')
+    nbins = 30
+    # now determine nice limits by hand:
+    xmin = -0.7
+    xmax = 0.2
+    ax_histx.hist(x,bins=nbins, range=(xmin,xmax),color = "blue")
+    
+    ymin = -0.7
+    ymax = 0.2
+    width = 0.02
+    ax_histy.hist(y,bins=nbins, range=(ymin,ymax), orientation='horizontal',color = "blue")
+
+    plt.style.use('ggplot')
+    #plt.grid(False)
+    ax.hist2d(x, y,bins=nbins,range=[[xmin,xmax],[ymin,ymax]],norm=mpl.colors.LogNorm())
[…]

### 2025-01-02 paper.tex
add citations, reorganization energy data

@@
 This flexible functionality is achieved by tuning molecular properties to achieve an ideal operation at the device level~\cite{bronstein_role_2020, bredas_organic_2002}.
-Computational approaches that aim at predicting the charge transport properties of disordered molecular materials resolving the interplay between single-molecule properties (such as their electronic structure or response properties) and mesoscale material morphology can play an important role in supporting or even guiding experimental optimization processes.\bjoern{add citations}{}
+Computational approaches that aim at predicting the charge transport properties of disordered molecular materials resolving the interplay between single-molecule properties (such as their electronic structure or response properties) and mesoscale material morphology can play an important role in supporting or even guiding experimental optimization processes~\cite{bronstein_role_2020, sokolov_computational_2011, grynova_read_2018}.\bjoern{add citations}{}
 
@@
 Due to the infeasibility of explicitly simulating the coupled non-adiabatic electron-nuclear dynamics for the time- and length scales of realistic materials, these models typically exploit the localization of electronic states in disordered molecular materials and consider a rate-based description of hopping-type transport.
-A popular choice for the electron transfer rate $\omega_{ij}$ between two localization sites $i$ and $j$ is Marcus theory~\bjoern{add}{citation}, in which
+A popular choice for the electron transfer rate $\omega_{ij}$ between two localization sites $i$ and $j$ is Marcus theory~\cite{marcus_theory_1956, marcus_electron_1993}  ~\bjoern{add}{citation}, in which
 %
@@
 With all that information, charge transport is modeled as a continuous time random walk (CTRW) process on a graph $\mathbf{G}$, constructed from the localization sites and the calculated rates between them (Fig.~\ref{fig:MSM}(c)).
-Panel (b) of Fig.~\ref{fig:MSM} mentions some specific methods for the calculation of the quantities entering Eq.~\ref{equ:Marcus}, such as mixed quantum-classical methods for obtaining the site energies with the help of microelectrostatic methods \bjoern{add}{citations} or the dimer projection method for determining coupling elements~\cite{baumeier_density_2010}, as they are the ones adopted in this work.
+Panel (b) of Fig.~\ref{fig:MSM} mentions some specific methods for the calculation of the quantities entering Eq.~\ref{equ:Marcus}, such as mixed quantum-classical methods for obtaining the site energies with the help of microelectrostatic methods~\cite{poelking_impact_2015, poelking_long-range_2016} \bjoern{add}{citations} or the dimer projection method for determining coupling elements~\cite{baumeier_density_2010}, as they are the ones adopted in this work.
 What is essential about these and alternative ones is that they typically rely on density-functional theory (DFT) calculations, either directly or as a mean to parametrize classical models.
@@
 We consider the simulated time-of-flight (ToF) and the associated mobility the QoI in the following (see Fig.~\ref{fig:MSM}(c)) which then are subject to uncertainties in these $N_\text{UQ}$ parameters, {\em stemming} from the variation in $\alpha_\text{HFX}$.
-As a prototypical system, we will study hole transport in an amorphous morphology of 2-methyl-9, 10-bis(naphthalen-2-yl)anthracene (MADN), a wide-gap semiconductor that is used extensively as an ambipolar host material in organic light-emitting diodes~\bjoern{add}{citation}.
+As a prototypical system, we will study hole transport in an amorphous morphology of 2-methyl-9, 10-bis(naphthalen-2-yl)anthracene (MADN), a wide-gap semiconductor that is used extensively as an ambipolar host material in organic light-emitting diodes~\cite{ko_accurate_2019, chang_great_2017} ~\bjoern{add}{citation}.
 
@@
 In contrast, the reorganization energy as shown in Fig.~\ref{fig:autogen_MADN}(b) appears to saturate for \ahfx after an initially close to linear increase.
-In total, $\lambda$ is found to be in an interval between \unit[0.25]{eV} and \unit[0.31]{eV} \bjoern{need}{correct numbers here}.
+In total, $\lambda$ is found to be in an interval between \unit[0.246]{eV} and \unit[0.316]{eV} \bjoern{need}{correct numbers here}.
 Panels (c) and (d) of Fig.~\ref{fig:autogen_MADN} show the dipole moment of the neutral MADN molecule and the isotropic polarizability of the neutral and cationic (hole) states, respectively, both as electrostatic properties that enter indirectly the parameterization of the microelectrostatic model.

### 2025-01-03 paper.tex
probably just a space

--- 2024-12-06 paper.tex
@@
 As is visible, the dipole moment is rather independent on \ahfx (note that the jump of the last shown data point appears more pronounced because of the vert small scale on the $y$-axis).
-The isotropic polarizabilities in panel (d) exhibit a linear decrease with increasing value of \ahfx which can be attributed to an increasingly attractive effective potential from stronger the Hartree--Fock-like exchange term and consequently more strongly bound electrons as one can also see from the increaseing ionization potential in panel (a).
+The isotropic polarizabilities in panel (d) exhibit a linear decrease with increasing value of \ahfx which can be attributed to an increasingly attractive effective potential from stronger the Hartree--Fock-like exchange term and consequently more strongly bound electrons as one can also see from the increasing ionization potential in panel (a).
 

### 2025-01-03 paper.tex
done site energies

--- 2025-01-02 paper.tex
@@
 
-\subsection{Distributions of site energies}
+\subsection{Site energies}
 
-\bjoern{STOP}{HERE}
-
-%\begin{table*}[tbp]%The best place to locate the table environment is directly after its first reference in text
-%\caption{\label{tab:W2_E}%
-%The 1-Wasserstein distance between the distributions pair of molecule energy $P_{E(\alpha)}$, electrostatic energy $P_{E^\text{el}(\alpha)}$, polar energy $P_{E^\text{polar}(\alpha)}$ and $P_{\log_{10}(J_{ij}^2)(\alpha)}$.
-%}
-%\begin{ruledtabular}
-%  \begin{tabular}{c c c c c c}
-%  $\alpha'$ & 0 & 0.05 & 0.10 & 0.15 & 0.20 \\
-%    \hline
-%  $W_1 (P_{E(\alpha')}, P_{E(\alpha=0.25)})$ &  0.0054 & 0.0091 & 0.0067 & 0.0053 & 0.0045 \\
-%  $W_1 (P_{E^\text{el}(\alpha')}, P_{E^\text{el}(\alpha=0.25)})$ &  0.010 & 0.012 & 0.0089 & 0.0070 & 0.0032 \\
-%  $W_1 (P_{E^\text{polar}(\alpha')}, P_{E^\text{polar}(\alpha=0.25)})$ &  0.0065 & 0.0043 & 0.0027 & 0.0023 & 0.0031 \\
-%  $W_1 (P_{\log_{10}(J_{ij}^2)(\alpha')}, P_{\log_{10}(J_{ij}^2)(\alpha=0.25)})$ &  0.0054 & 0.0091 & 0.0067 & 0.0053 & 0.0045 \\
-%    \end{tabular}
-%\end{ruledtabular}
-%\end{table*}
-%
-
-\begin{figure*}
+\begin{figure*}[t]
   \centering
-  \includegraphics[width=0.80\textwidth]{figs/scatterE_qmmm.pdf}
-  \caption{\bjoern{TODO Zhong:}{add labels (a)...; replace $\alpha$ with $\alpha_\text{HF}$.}Scatter plot of site energy of MADN molecules calculated from different HFX, compared to the site energy calculated from HFX=0.25 (The PBE0 functional).
+  \includegraphics[width=\linewidth]{figs/scatterE_qmmm.pdf}
+  \caption{\bjoern{TODO: }{rewrite caption}Scatter plot of site energy of MADN molecules calculated from different HFX, compared to the site energy calculated from HFX=0.25 (The PBE0 functional).
 The brighter color near the diagonal lines indicates denser population of the molecules.
@@
 
-Figure \ref{fig:E_qmmm_MADN} presents a scatter plot comparing the site energies of MADN molecules across different HFX values, using $\alpha$ = 0.25 (PBE0 functional) as a reference for which the calculated molecule energy has a range from -1.17 to -0.60 \unit[]{eV}y.
-The range of molecule energy for the other five HFX are: 
-from -1.11 to -0.59 \unit[]{eV} for $\alpha=0$, 
-from -1.07 to -0.63 \unit[]{eV} for $\alpha=0.05$, 
-from -1.13 to -0.61 \unit[]{eV} for $\alpha=0.10$
-from -1.16 to -0.60 \unit[]{eV} for $\alpha=0.15$, 
-and from -1.12 to -0.63 \unit[]{eV} for $\alpha=0.20$.
-The bright-yellow color in all plots of Fig.
-\ref{fig:E_qmmm_MADN} indicates that most data points are clustering near the diagonal line, so the molecular energies calculated by different HFX are very close.
-
-%To quantify the similarity between two empirical distribution, Wasserstein distance~\cite{villani_optimal_2009} is used.
-%Denote the empirical distribution of molecular energy $E$ at $\alpha=0$ to be $P_{E(\alpha=0)}$. 
-%The 1-Wasserstein distance between $P_{E(\alpha=0)}$ and $P_{E(\alpha=0.25)}$ is calculated as:
-%\begin{eqnarray}
-%    && W_1 (P_{E(\alpha=0)}, P_{E(\alpha=0.25)}) = \nonumber \\
-%    && \frac{1}{N} \sum\limits_{i=1}^N | E_{(i)}(\alpha=0) - E_{(i)}(\alpha=0.25) |
-%\end{eqnarray}
-%where $E_{(i)}(\alpha=0)$ is the order statistics of $E_i(\alpha=0)$.
-The 1-Wasserstein distance between two empirical distributions for each plot in Fig.
-\ref{fig:E_qmmm_MADN} is shown in Table \ref{tab:W2_E}.
-$W_1 (P_{E(\alpha=0)}, P_{E(\alpha=0.25)})$ has range between 0.0045 to 0.0091, indicating that the molecular energy distributions are very similar.
-
-To further estimate the energy variation due to HFX, one can look at the molecule that has maximum $|E_i(\alpha=0.25) - E_i(\alpha')|$ for all molecule index $i=1,2,\cdots,N$. 
-This quantity provides information of the amount of the largest variation one can expect in $E_i(\alpha)$. Index the molecule that has maximum $|E_i(\alpha=0.25) - E_i(\alpha')|$ to be $i'$. 
-If molecule $i'$ energy is the lowest one among the $N$ molecules, then a further change (such as lowering) in the energy of molecule $i'$ may lead to large change in ToF, since low energy potentially lead to a trap in the charge transport dynamics and significantly affects the mobility.
-
-Table \ref{tab:maxEi} shows that depending on $\alpha'$, the maximum $|E_i(\alpha=0.25) - E_i(\alpha')|$ is 0.12 to 0.15, which is considerable small compared to the range of molecular energy and the magnitude of the energy disorder, which is around 0.08 as shown in Fig.
-\ref{fig:autogen_MADN}.
-The energy of molecule $i'$ shown in Table \ref{tab:maxEi} indicates that the $i'$ molecule energy is not the lowest one in the system.
-So the maximum energy variation quantified by $\max(|E_i(\alpha=0.25) - E_i(\alpha')|)$ is not likely to results in large change in ToF due to trapping effects.
-
 \begin{table}[tbp]
-\caption{\label{tab:maxEi}%
-In the tested $\alpha'$ values, the second column shows the maximum of $E_i(\alpha=0.25) - E_i(\alpha')$ for all molecules.
+  \caption{\bjoern{TODO: }{rewrite caption}In the tested $\alpha'$ values, the second column shows the maximum of $E_i(\alpha=0.25) - E_i(\alpha')$ for all molecules.
 Denoting $i'$ as the index of the molecule which has maximum $E_i(\alpha=0.25) - E_i(\alpha')$ for the chosen $\alpha'$, the third column shows the energy of molecule $i'$ calculated by $\alpha=0.25$.
 The fourth column shows the molecule energy $E_{i'}(\alpha')$ calculated by $\alpha'$.
-All the energies are in unit $\unit[]{eV}$.
-}
+All the energies are in unit $\unit[]{eV}$.}
   \begin{ruledtabular}
-  \begin{tabular}{c c c c}
-  $\alpha'$ & $\max(|E_i(\alpha=0.25) - E_i(\alpha')|)$  & $E_{i'}(\alpha=0.25)$ & $E_{i'}(\alpha')$ \\
+    \begin{tabular}{c c c c c c c}
+    $\ahfx$ & $E_\text{min}$ & $E_\text{max}$ & $\sigma$ & $\sigma_\text{el}$ & $\sigma_\text{polar}$ &  $D_{\ahfx}$ \\%  & $E_{i_\text{max}}$ \\
     \hline
-  0 & 0.13 &  -1.07 & -0.94 \\
-  0.05 & 0.12 & -0.82 & -0.94 \\
-  0.10 & 0.13 & -1.07 & -0.94 \\
-  0.15 & 0.15 & -0.84 & -0.69 \\
-  0.20 & 0.12 & -0.70 & -0.82 \\
+    0    & -1.11 & -0.59 & 0.08 & 0.10 & 0.04 & 0.13 \\ %&  -0.94 \\
+    0.05 & -1.07 & -0.63 & 0.07 & 0.09 & 0.04 & 0.12 \\ %&  -0.94 \\
+    0.10 & -1.13 & -0.61 & 0.08 & 0.10 & 0.04 & 0.13 \\ %&  -0.94 \\
+    0.15 & -1.16 & -0.59 & 0.09 & 0.11 & 0.05 & 0.15 \\ %&  -0.69 \\
+    0.20 & -1.12 & -0.63 & 0.08 & 0.10 & 0.05 & 0.12 \\ %&  -0.82 \\
+    0.25 & -1.17 & -0.60 & 0.08 & 0.11 & 0.04 & ---  \\ %&   ---\\
     \end{tabular}
   \end{ruledtabular}
+  \label{tab:maxEi}
 \end{table}
 
-Figures \ref{fig:Estat_qmmm_MADN} and \ref{fig:Edip_qmmm_MADN} show that both electrostatic and polarization energies remain consistently close to the ones calculated from $\alpha=0.25$, since all the points comparing $E^\text{el}_i(\alpha')$ and $E^\text{el}_i(\alpha=0.25)$ in the scatter plot are close to the diagonal line.
-The range of $E^\text{el}$ calculated by different $\alpha$ is as follows:
-from  -0.55 to 0.078 eV for $\alpha=0$, 
-from  -0.52 to 0.047 eV for $\alpha=0.05$, 
-from  -0.57 to 0.086 eV for $\alpha=0.10$, 
-from  -0.59 to 0.14 eV for $\alpha=0.15$, 
-from  -0.57 to 0.10 eV for $\alpha=0.20$, 
-and from -0.63 to 0.10 eV for $\alpha=0.25$.
+Figure~\ref{fig:E_qmmm_MADN}(a)-(e) presents scatter plots comparing the distributions of the calculated site energies of MADN molecules for different \ahfx values, using $\ahfx = \unit[0.25]{}$ (PBE0 functional) as a reference in all cases.
+Visually, the distributions look very similar as most data points cluster near the diagonal line.
+In Table~\ref{tab:maxEi}, we report the minimum ($E_\text{min}$) and maximum ($E_\text{max}$) values of the energies and the standard deviation $\sigma$ of the individual distributions, which are also shown in Fig.~\ref{fig:E_qmmm_MADN}(f).
+All noted variations in these quantities appear small.
+The data in Figures~\ref{fig:Estat_qmmm_MADN} and \ref{fig:Edip_qmmm_MADN} in the Appendix show that the observations on the total site energies also hold for the individual contributions of electrostatic and polarization energies.
+This is also reflected by the small variations in the respective standard deviations $\sigma_\text{el}$ and $\sigma_\text{polar}$ listed in Tab.~\ref{tab:maxEi}.
 
-The 1-Wasserstein distance between the distribution of $E^\text{el}$ calculated by $\alpha'$ and that calculated by $\alpha=0.25$, $W_1(P_{E^\text{el}(\alpha')}, P_{E^\text{el}(\alpha=0.25)})$, is shown at the third row at Table \ref{tab:W2_E}.
-The maximum of $W_1(P_{E^\text{el}(\alpha')}, P_{E^\text{el}(\alpha=0.25)})$ 0.012.
-The 1-Wasserstein distance between the $E^\text{polar}$ distribution calculated by $\alpha'$ and that calculated by $\alpha=0.25$ is also shown in Table \ref{tab:W2_E}, with a maximum of 0.006.
-So the small Wasserstein distances suggest that the using different $\alpha'$ other than $\alpha=0.25$, the data of $E, E^\text{el}, E^\text{polar}$ have not changed significantly.
+Interestingly, we find the biggest variation of \unit[0.1]{eV} in the values for $E_\text{min}$.
+This minimal energy (or rather all the energies in the low-energy region of the distributions) can have a very significant influence on the charge transport properties, depending on how much the site energy differences are influenced in the charge transport network.
+To further characterize the effect of different \ahfx values, we consider the largest absolute variation in the site energies depending on \ahfx by calculating the Chebyshev distance $D_{\ahfx} = \max\limits_{i}(|E_i(\ahfx=0.25) - E_i(\ahfx)|)$.
+From the results listed in Tab.~\ref{tab:maxEi}, one can see that on individual level the site energies can vary substantially, with more than \unit[0.1]{eV}.
+This variation is larger than the recorded values of $\sigma$ and with all \ahfx yielding the same mean site energy of \unit[-0.86]{eV} this could indicate non-neglibible effects on charge transport.
 
-The standard deviations of the electrostatic energy are 0.099, 0.094, 0.099, 0.11, 0.10, \unit[0.10]{eV}, and the standard deviations of the polarization energies are 0.044, 0.043, 0.043, 0.047, 0.045, \unit[0.045]{eV}.
-So the disorder in electrostatic energies is consistently larger than that in molecule energies, and the palorization effect reduces the electrostatic energy disorder.
-Each individual molecule has similar polarization energies under different HFX calculation, in spite of $P_\text{iso}$ is linearly dependent on HFX.
+\bjoern{STOP}{HERE}
 
-\subsection{Distributions of electronic couplings}
+\subsection{Electronic couplings}
 

### 2025-01-03 paper.tex
coupling part

@@
 \usepackage{xspace}
+\usepackage{mathbbol}
 
@@
 
-\begin{figure*}[t]
+\begin{figure*}[tbp]
   \centering
@@
 
-\begin{figure*}
+\begin{figure*}[tbp]
   \centering
-  \includegraphics[width=0.80\textwidth]{figs/scatterJ_all.pdf}
-  \caption{\bjoern{TODO Zhong:}{add labels (a)...; replace $\alpha$ with $\alpha_\text{HF}$; it should be $\log_{10}(J^2/(\unit[]{eV})^2)$; make sure the 10 of $\log_{10}$ is not touching $J$.} Scatter plot of MADN coupling element $\log_{10} J^2$ calculated from different HFX, compared to the polarization energy calculated from HFX=0.25 (The PBE0 functional).
+  \includegraphics[width=\linewidth]{figs/scatterJ_all.pdf}
+  \caption{\bjoern{TODO:}{rewrite caption} Scatter plot of MADN coupling element $\log_{10} J^2$ calculated from different HFX, compared to the polarization energy calculated from HFX=0.25 (The PBE0 functional).
 The brighter color near the diagonal lines indicates denser population of the molecules.
@@
 
-The coupling element obtained with different HFX for each molecular pair compared to that obtained with HFX=0.25 is shown in the scatter plot Fig. \ref{fig:J_MADN}.
+Distributions and correlations compared with the PBE0 reference for the electronic coupling elements calculated with different values for \ahfx are shown in Figure~\ref{fig:J_MADN}.
+The individual distributions appear very similar, with a peak of $\log_{10}[(J_{ij}/\unit[]{eV})^2]$ between \unit[-5]{} to \unit[-6]{}, and a long tail of the distribution towards more negative values.
+The comparison with the PBE0 reference shows that while there is a clear correlation between the results for different values of \ahfx, the spread in the order of magntitudes of $J_{ij}^2$ can be very large especially for the lower coupling regions.
+Overall, the squared electronic coupling elements are found in a very wide range from $\unit[10^{-2}]{}$ to $\unit[10^{-15}]{(eV)^2}$ due to its exponential distance dependence and sensitivity to mutual orientation of the two involved molecules.
+Whereas the site energy distributions discussed in the preceding section are well-defined in the sense that each energy is unambiguously associated to a physical entity -- a molecule in the morphology --, the coupling elements are evaluated for a neighborlist based on a chosen cutoff as explained in Section~\ref{sec:model}.\bjoern{TODO:}{add!} Clearly, if this cutoff is chosen to be large, a lot of hopping pairs with very small coupling elements will be considered that may not be relevant at all (or even unphysical) for charge transport.
+Therefore, the increasing deviations for the most negative values in Figure~\ref{fig:J_MADN} may not be relavent either.
 
-The distribution of the majority $\log_{10} J_{ij}^2$ has a range of -14 to -2 while only a few $\log_{10} J_{ij}^2$ has low value below -15.
-For all HFX values, the distribution has a peak at around -5.
-For large values $\log_{10} J_{ij}^2 < -5$ the coupling element calculated from $\alpha'=0, 0.05, 0.10, 0.15, 0.2$ remains consistently close to that calculated by $\alpha=0.25$.
-While for small values $\log_{10} J_{ij}^2 > -5$, the $\alpha'$ calculated coupling elements for a specific molecular pair can have large variation compared to $\log_{10} J_{ij}^2$ calculated using $\alpha=0.25$.
-The 1-Wasserstein distance between the $J$ distributions obtained by different $\alpha$ is always smaller than 0.01,  
-indicating similar $J$ distributions even though a few $J_{ij}$ shows large difference when $\alpha$ varies.
-
-In charge transport network, $J_{ij}^2$ is undirectional for a molecular pair, and decays exponentially as the mutual center-of-mass distance increases.
-The large $\log_{10} J_{ij}^2$ are usually observed when molecular $i$ and $j$ are close.
-When the center-of-mass distance is very large, the $\log_{10} J_{ij}^2$ is small and some of those small $\log_{10} J_{ij}^2$ are sensitive to $\alpha$.
-
-However, the charge dynamics is dominated by large $\log_{10} J_{ij}^2$ which are found between molecule pair having small center-of-mass.
-As the center-of-mass distance increases, $\log_{10} J^2$ becomes small and negligible for the charge dynamics.
-So the small $J_{ij}$ may not have noticeable effect on the ToF although their calculated values from different HFX are very different.
-
-To determine the range of $\log_{10} J^2$ that are significant for the charge dynamics, a percolation algorithm is performed.
-This algorithm aims to find the largest size of subgraphs after removing the edges whose coupling elements are below a critical value.
-The procedure is as follows:
-\begin{enumerate}
-    \item A critical value $J_c$ is chosen,
-    \item In graph $\mathbf{G}$ remove all the edges with $J_{ij}^2 < J_c^2$
-    \item Calculate the maximum size $\max({N_\text{sub}})$ of the connected subgraphs
-\end{enumerate}
-
-\begin{figure}[btp]
+\begin{figure}[tbp]
   \centering
-  \includegraphics[width=0.45\textwidth]{figs/fig_network_all.pdf}
+  \includegraphics[width=\linewidth]{figs/fig_network_all.pdf}
   \caption{\bjoern{TODO Zhong:}{same comments regarding the $\log_{10}$ as above; replace $\alpha$ with $\alpha_\text{HF}$.}The maximum size of the subgraphs obtained in the percolation algorithm as a function of critical value $J_c$.
@@
 
-\begin{table}[t]
-  \caption{\label{tab:ToF_J} The ToF along a distance $L_x = 9 \unit[]{nm}$  of the MADN system as a function of the HFX.
-The molecular connections with coupling element $\log_{10} J^2_{ij} < 5$ are deleted.}
-  \centering
-  \begin{tabular}{c c c c }
-  \hline
-  \hline
-      $\alpha$ & & & ToF [s]  \\
-  \hline
-      0.00 & & &  $7.5 \times 10^{-9}$ \\
-      0.05 & & & $ 8.1 \times 10^{-9}$ \\
-      0.10 & & & $ 1.6 \times 10^{-8}$ \\
-      0.15 & & & $ 3.1 \times 10^{-8}$ \\
-      0.20 & & & $ 2.5 \times 10^{-8}$ \\
-      0.25 & & & $ 9.7 \times 10^{-8}$ \\
-  \hline
-  \hline
-  \end{tabular}
-\end{table}
+To determine the range of $\log_{10}[(J_{ij}/\unit[]{eV})^2]$ that are significant for the charge dynamics, a percolation analysis is performed to find a critical threshold value for the squared electronic coupling below which the largest connected subgraph is identical to the full graph.
+This is achieved by removing for a given value for $J_\text{c}$ from the full graph the edges with $J_{ij}^2 < J^2_\text{c}$ followed by the determination of the number of vertices in the larges connected subgraph $\max(N_\text{sub})$.
+Figure~\ref{fig:J_percolate} shows the resulting dependence of $\max({N_\text{sub}})$ on the critical value $J_c$.
+It is apparent that for $\log_{10} J_c^2 = -5$, all vertices are in the largest connected subgraph.
+The overall connectivity of the charge transport network is therefore mostly affected by the coupling elements larger than this threshold, and the charge transport properties are expected to be more sensitive to deviations for the associated edges.
+We also note that overall, the results in Fig.~\ref{fig:J_percolate} again seem to be very similar for all \ahfx studied in the work.
 
-After performing percolation algorithm, Figure \ref{fig:J_percolate} shows the dependence of $\max({N_\text{sub}})$ on the critical value $J_c$.
-When $\log_{10} J_c^2 < 5$, $\max({N_\text{sub}})$ is 1000, meaning that removing all the edges with $J_{ij}^2 < 1 \times 10^{-5}$ the 1000 vertexes still form a connected graph.
-But when removing the edges with $J_{ij}^2 < 3.1 \times 10^{-4}$ ( corresponding to $J_c > -3.5$), the maximum size subgraph is 600, and it quickly decreases as $J_c$ increases, showing a phase transition.
-So the dominated coupling elements are those with $\log_{10} J_c^2 > -5$. 
+\subsection{Time-of-flight calculations}
 And the variation in small $J_{ij}$ due to HFX has less impact on the charge dynamics.
@@
 \begin{ruledtabular}
-  \begin{tabular}{c c c c c}
-        $\alpha$ & ToF& $v_\text{ToF}$ & ToF(no $E$)& $v_\text{ToF}$(no $E$) \\
+  \begin{tabular}{c c c c }
+        \ahfx & full & $J_{ij} \mathbb{1}(\log_{10} J^2_{ij} > 5)$ & $\Delta E_{ij} =0$ \\% & $v_\text{ToF}$(no $E$) \\
     \hline
-        0.00 &  $6.4 \times 10^{-9}$ & 1.2 & $1.9 \times 10^{-10}$ & 42 \\
-        0.05 & $ 7.9 \times 10^{-9}$ & 1.0 & $4.1 \times 10^{-10}$ & 20 \\
-        0.10 & $ 1.6 \times 10^{-8}$ & 0.51 & $4.0 \times 10^{-10} $ & 20 \\
-        0.15 & $ 3.0 \times 10^{-8}$ & 0.31 & $4.0 \times 10^{-10} $ & 25 \\
-        0.20 & $ 2.1 \times 10^{-8}$ & 0.39 & $4.5 \times 10^{-10}$ & 18 \\
-        0.25 & $ 9.5 \times 10^{-8}$ & 0.083 & $7.2 \times 10^{-10}$ & 11 \\
+        0.00 &  $6.4 \cdot 10^{-9}$ & $7.5 \cdot 10^{-9}$ & $1.9 \cdot 10^{-10}$ \\%& 42 \\
+        0.05 & $ 7.9 \cdot 10^{-9}$ & $8.1 \cdot 10^{-9}$ & $4.1 \cdot 10^{-10}$ \\%& 20 \\
+        0.10 & $ 1.6 \cdot 10^{-8}$ & $1.6 \cdot 10^{-8}$ & $4.0 \cdot 10^{-10} $ \\%& 20 \\
+        0.15 & $ 3.0 \cdot 10^{-8}$ & $3.1 \cdot 10^{-8}$ & $4.0 \cdot 10^{-10} $ \\%& 25 \\
+        0.20 & $ 2.1 \cdot 10^{-8}$ & $2.5 \cdot 10^{-8}$ & $4.5 \cdot 10^{-10}$ \\%& 18 \\
+        0.25 & $ 9.5 \cdot 10^{-8}$ & $9.7 \cdot 10^{-8}$ & $7.2 \cdot 10^{-10}$ \\%& 11 \\
     \end{tabular}
@@
 The red vertical lines indicate the lower bound and upper bound of the 99\% confidence interval around the median.
-(a) $|\vec{F}|=4 \times 10^7 \unit{V/m}$, (b) $|\vec{F}|=5 \times 10^7 \unit{V/m}$, (c) $|\vec{F}|=6 \times 10^7 \unit{V/m}$, (d) $|\vec{F}|=7 \times 10^7 \unit{V/m}$, (e) $|\vec{F}|=8 \times 10^7 \unit{V/m}$, (f) $|\vec{F}|=9 \times 10^7 \unit{V/m}$.}
+(a) $|\vec{F}|=4 \cdot 10^7 \unit{V/m}$, (b) $|\vec{F}|=5 \cdot 10^7 \unit{V/m}$, (c) $|\vec{F}|=6 \cdot 10^7 \unit{V/m}$, (d) $|\vec{F}|=7 \cdot 10^7 \unit{V/m}$, (e) $|\vec{F}|=8 \cdot 10^7 \unit{V/m}$, (f) $|\vec{F}|=9 \cdot 10^7 \unit{V/m}$.}
     \label{fig:fig_mle_withE_mu2_ave}
@@
 The ToF depends on the electric field through the Marcus rate.
-As the electric increase from $|\vec{F}|=4 \times 10^7 \unit{V/m}$
-$|\vec{F}|=9 \times 10^7 \unit{V/m}$, the
+As the electric increase from $|\vec{F}|=4 \cdot 10^7 \unit{V/m}$
+$|\vec{F}|=9 \cdot 10^7 \unit{V/m}$, the
 range of the 90\% confidence interval where $\log_{10} \mu_\text{PF}$ lies
@@
       \hline
-    0 & & $4.0 \times 10^{-3}$ & & $1.0 \times 10^{-3}$ \\
-    0.05 & & $2.1 \times 10^{-3}$ & & $9.3 \times 10^{-4}$ \\
-    0.10 & & $1.0 \times 10^{-3}$ & & $1.5 \times 10^{-3}$ \\
-    0.15 & & $8.0 \times 10^{-4}$ & & $1.6 \times 10^{-3}$ \\
-    0.20 & & $9.3 \times 10^{-4}$ & & $1.3 \times 10^{-3}$ \\
-    0.20 & & $2.6 \times 10^{-4}$ & & $1.8 \times 10^{-3}$ \\
+    0 & & $4.0 \cdot 10^{-3}$ & & $1.0 \cdot 10^{-3}$ \\
+    0.05 & & $2.1 \cdot 10^{-3}$ & & $9.3 \cdot 10^{-4}$ \\
+    0.10 & & $1.0 \cdot 10^{-3}$ & & $1.5 \cdot 10^{-3}$ \\
+    0.15 & & $8.0 \cdot 10^{-4}$ & & $1.6 \cdot 10^{-3}$ \\
+    0.20 & & $9.3 \cdot 10^{-4}$ & & $1.3 \cdot 10^{-3}$ \\
+    0.20 & & $2.6 \cdot 10^{-4}$ & & $1.8 \cdot 10^{-3}$ \\
       \end{tabular}
@@
 The extracted Poole–Frenkel paratermeter calculated from the six $\alpha$ values are summarized in Table \ref{tab:PF_parameter}. 
-Excluding the data of $\alpha=0$, the extracted zero-field mobility $\mu_0$ has a range from $2.6 \times 10^{-4}$ to $2.1 \times 10^{-3}$, and the field effect constant $\beta$ range from $9.3 \times 10^{-4}$ to $1.8 \times 10^{-3}$.
+Excluding the data of $\alpha=0$, the extracted zero-field mobility $\mu_0$ has a range from $2.6 \cdot 10^{-4}$ to $2.1 \cdot 10^{-3}$, and the field effect constant $\beta$ range from $9.3 \cdot 10^{-4}$ to $1.8 \cdot 10^{-3}$.
 So $\beta$ is less sensitive to the multiscale model parameter $\alpha$ compared the zero-field mobility.

### 2025-01-03 paper.tex
typo

@@
 
-\bjoern{STOP}{HERE}
-
 \subsection{Electronic couplings}
@@
 \subsection{Time-of-flight calculations}
-And the variation in small $J_{ij}$ due to HFX has less impact on the charge dynamics.
-Table \ref{tab:ToF_J} shows the ToF for the MADN system after deleting the molecular connections with  $\log_{10} J_c^2 < -5$.
-The resulting ToF is close to the values obtained without deleting any connections (shown in Table \ref{tab:ToF_MADN_HFX}).
-The increase of ToF after deleting the connections with  $\log_{10} J_c^2 < -5$ is always less than 30\%, confirming that the molecular connections with the small $J_{ij}$ has small effect in ToF.
-
-In this section we answer the question of how does HF level change the electronic structures ($\lambda, E_i, J_{ij}$) and 
-how does HF level change the ToF. 
-In the next section, uncertainty quantification via Monte Carlo method and sensitivity analysis is performed to answer which electronic structure (among energy, coupling element and reorganization energy) uncertainty has the most impact on the ToF distribution.
-And further we estimate the range of the quantity of interest, given a confidence level.
-
-The ToF is also calculated without energy disorder, meaning $\Delta E_{ij}=0$ for all $i,j$.
-Table~\ref{tab:ToF_MADN_HFX} shows the ToF and corresponding diffusive velocity $v_\text{ToF}$.
-With energy disorder, the ToF increases by a factor of approximately 15 as $\alpha$ increases from 0 to 0.25.  
-While without energy disorder, the increase factor is about 4. This increase in ToF is attributed to the rise in $\lambda$, changes in molecular energies, and variations in coupling elements.
 
 \begin{table}[tbp]
-\caption{The ToF and diffusive velocity calculated by ToF along a distance $L_x = \unit[9.0]{nm}$ with and without energy disorder of the MADN system as a function of the HFX.
+\caption{\bjoern{TODO:}{rewrite}The ToF and diffusive velocity calculated by ToF along a distance $L_x = \unit[9.0]{nm}$ with and without energy disorder of the MADN system as a function of the HFX.
 The ToF is in unit $\unit[]{s}$ and $v_\text{ToF}$ in unit $\unit[]{m/s}$.}
@@
   \begin{tabular}{c c c c }
-        \ahfx & full & $J_{ij} \mathbb{1}(\log_{10} J^2_{ij} > 5)$ & $\Delta E_{ij} =0$ \\% & $v_\text{ToF}$(no $E$) \\
+        \ahfx & full & $J_{ij} \mathbb{1}(\log_{10} J^2_{ij} > -5)$ & $\Delta E_{ij} =0$ \\% & $v_\text{ToF}$(no $E$) \\
     \hline
@@
 \end{table}
+
+From the analysis of reorganization energies, site energies, and electronic coupling elements for different values of \ahfx, it is not clear how the mostly on distribution-level observed variations impact the overall charge transport properties.
+To scrutinize the dependence of such a material property, we now calculate the time-of-flight $\tau$ and report the respective values in Table~\ref{tab:ToF_MADN_HFX}.
+Here, we refer with ''full'' to time-of-flight obtained for the the as-calculated charge transport network.
+One can see that $\tau$ varies by roughly one order of magnitude between $\ahfx=0$ ($\unit[6.3\cdot 10^{-9}]{s}$) and $\ahfx=0.25$ ($\unit[9.5\cdot 10^{-8}]{s}$), with an almost monotonous increase.
+When the squared coupling elements with values below $\unit[10^{-5}]{(eV)^2}$ are set to zero ($J_{ij} \mathbb{1}(\log_{10} J^2_{ij} > -5)$), one obtains only minimally, but consistently, larger $\tau$, corroborating the notion that the very small coupling elements are of little relevance for charge transport.
+Finally, we also consider the case in which the energetic disorder is ignored ($\Delta E_{ij}=0$).
+Here, one also can see (next to the generally shorter time-of-flight) a consistent increase in $\tau$, however only by a factor of about \unit[3.8]{}, a combined effect of the increased reorganization energy and variations in coupling elements.
+
+\bjoern{STOP}{HERE}
 

### 2025-01-06 paper.tex
getting started on sampling

@@
 
-\bjoern{STOP}{HERE}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\subsection{ToF Distribution}
-The ToF is calculated from electronic structure ($E$, $\lambda$ and $\log_{10}(J^2)$) data, that is, ToF is a function with the input of all electronic structure parameters:
-\begin{equation}
-    %\tau = g(\lambda, \{E_i|i=1,2,\cdots,N \}, \{J_{ij}|i,j=1,2,\cdots,N \}) \;
-    \tau = g(x_1, x_2, \cdots, x_{N_d})
-    \label{eq:tau1}
-\end{equation}
-The input $(x_1, x_2, \cdots, x_{N_d})$ represents the collection of the parameters $$(\lambda, \{E_i|i=1,2,\cdots,N \}, \{J_{ij}|i,j=1,2,\cdots,N \})$$  where $N_d$ is the parameter dimension, that is the number of input parameters.
-And $\{E_i|i=1,2,\cdots,N \}$ is the ordered set whose elements are the molecule energy,
-$\{J_{ij}|i,j=1,2,\cdots,N \}$ is the ordered set whose elements are the coupling elements.
+\subsection{Monte-Carlo Sampling of ToF}
+As discussed the ToF is calculated from the graph with weighted edges defined by the electronic structure data $(\lambda, E_1,\ldots,E_N, J_1^2,\ldots,J_{N_\text{p}}^2)$, where $N$ is the number of molecules (vertices) and $N_\text{p}$ the number of molecule pairs (edges) in the neighbor list.
+We can therefore consider that $\tau = \tau(\mathbf{x})$ with $\mathbf{x}=(\lambda, E_1,\ldots,E_N, \log_{10}(J_1^2),\ldots,\log_{10}(J_{N_\text{p}}^2))$ as dependent on $M = 1+N+N_\text{p}$ parameters with uncertainty, in this case stemming from the possible choices of \ahfx in the exchange-correlation functional of the multiscale model.
+Note that due to the data range for the electronic coupling element as discussed in the previous section, we consider $\log_{10}(J^2)$ instead of $J^2$.
+For MADN, we have that $M=XXX$ \bjoern{ADD:}{how many pairs?}
 
-Each parameter has uncertainty caused by the exchange-correlation functional in the multiscale model.
-To estimate the uncertainty which is unknown, we consider the maximum amount of uncertainties according to the obtained $(\lambda, \{E_i|i=1,2,\cdots,N \}, \{J_{ij}|i,j=1,2,\cdots,N \})$ with the six different HFX.
-To achieve this, each parameter can be modeled as a normal distribution with the mean and standard deviation obtained by the maximum likelihood estimation.
-For a normal distribution, they are respectively the sample mean and standard deviation obtained by six different HFXs.
+Because the precise distribution of the uncertainties of the $M$ parameters is not known, we consider the maximum amount of uncertainties from a maximum likelihood estimation based on the data obtained from the explicit results for the different values of \ahfx and the assumption of normal distributions.
+In other words, each of the parameters $x_i$ for $i=1,\ldots,M$ is assigned a normal distribution with $\mathcal{N}(\mathbb{E}(x_i),\mathbb{V}(x_i))$, with $\mathbb{E}(x_i)$ ($\mathbb{V}(x_i)$) the mean (variance) of the respective data.
+Then, Monte-Carlo sampling is used to obtain $N_\text{MC}=50000$ different realizations of $\mathbf{x}$, the respective time-of-flight is calculated from these samples, and the resulting distribution $P(\log_{10}(\tau))$ is statistically analyzed.
+Specifically, we consider four different settings: in three settings, only one of the parameters blocks $(\lambda,\left\{E\right\},\left\{\log_{10}(J^2)\right\})$ is sampled while the values of the other blocks are set to their respective mean values and we denote the resulting distributions as $P_\lambda(\log_{10}(\tau))$, $P_E(\log_{10}(\tau))$, and $P_J(\log_{10}(\tau))$, respectively.
+In the fourth setting, all parameters are sampled at the same time, yielding $P_\mathbf{x}(\log_{10}(\tau))$.
 
-Then Monte Carlo scheme is used to estimate the distribution of the ToF. The Monte Carlo scheme has the procedure:
-\begin{enumerate}
-\item For all $i,j=1,2,\cdots, N_d$, obtain a realization $(x_1, x_2, \cdots, x_{N_d})$ where each parameter has the normal distribution, meaning the corresponding electronic parameters are sampled from the distribution $\lambda_i \in \mathcal{N}(\mathbb{E}(\lambda), \mathbb{V}(\lambda))$, $E_i \in \mathcal{N}(\mathbb{E}(E_i), \mathbb{V}(E_i))$, $\log_{10}(J_{ij}^2) \in \mathcal{N}(\mathbb{E}(\log_{10}(J_{ij}^2)), \mathbb{V}(\log_{10}(J_{ij}^2)))$.
-\item Calculate ToF using the sampled data set $(x_1, x_2, \cdots, x_{Nd})$. 
-\item Repeat step 1 and 2 for $N_\text{MC} = 50000$ times to obtain ToFs. Plot the distribution of the ToFs.
-\item Estimate the 99\% confidence interval around the median.
-\end{enumerate}
+%Then Monte Carlo scheme is used to estimate the distribution of the ToF. The Monte Carlo scheme has the procedure:
+%\begin{enumerate}
+%\item For all $i,j=1,2,\cdots, N_d$, obtain a realization $(x_1, x_2, \cdots, x_{N_d})$ where each parameter has the normal distribution, meaning the corresponding electronic parameters are sampled from the distribution $\lambda_i \in \mathcal{N}(\mathbb{E}(\lambda), \mathbb{V}(\lambda))$, $E_i \in \mathcal{N}(\mathbb{E}(E_i), \mathbb{V}(E_i))$, $\log_{10}(J_{ij}^2) \in \mathcal{N}(\mathbb{E}(\log_{10}(J_{ij}^2)), \mathbb{V}(\log_{10}(J_{ij}^2)))$.
+%\item Calculate ToF using the sampled data set $(x_1, x_2, \cdots, x_{Nd})$. 
+%\item Repeat step 1 and 2 for $N_\text{MC} = 50000$ times to obtain ToFs. Plot the distribution of the ToFs.
+%\item Estimate the 99\% confidence interval around the median.
+%\end{enumerate}
 
-To understand how the uncertainty pass from $E, \lambda, J_{ij}$ to ToF, the parameter control is used.
+%To understand how the uncertainty pass from $E, \lambda, J_{ij}$ to ToF, the parameter control is used.
 That is, a set of parameter, such as $E_i$ for all $i=1,2,\cdots,N$ is choose while keeping other parameter fixed, then performed Monte Carlo sampling to obtain ToF distribution and estimate upper and lower confidence bound.
-Then we use Sobol total indices to analyze and quantify 
-which uncertainty among $E, \lambda, J_{ij}$ has a greater impact on the ToF,
+%Then we use Sobol total indices to analyze and quantify 
+%which uncertainty among $E, \lambda, J_{ij}$ has a greater impact on the ToF,
 
-%
 \begin{figure}
@@
   \includegraphics[width=0.45\textwidth]{figs/fig_mle_MADN_withE.pdf}
-  \caption{\bjoern{TODO Zhong:}{these should also strictly be $\log_{10}(\tau/\unit[]{s})$.}Distribution of ToFs in the multiscale modeled MADN system.
+  \caption{\bjoern{TODO Zhong:}{swap panels a and b}Distribution of ToFs in the multiscale modeled MADN system.
   Monte Carlo sampling with a sample size $N_\text{MC}=50000$ is used to obtain the sampled distribution.
@@
 \end{figure}
-%
 
-The distribution that we want to obtained during the parameter control are as followed:
-\begin{enumerate}
-    \item Fixed the $\lambda$ to be $\mathbb{E}(\lambda)$, and $\log_{10}(J_{ij}^2)$ to be $\mathbb{E}(\log_{10}(J_{ij}^2))$.
+%The distribution that we want to obtained during the parameter control are as followed:
+%\begin{enumerate}
+%    \item Fixed the $\lambda$ to be $\mathbb{E}(\lambda)$, and $\log_{10}(J_{ij}^2)$ to be $\mathbb{E}(\log_{10}(J_{ij}^2))$.
 Then each molecule energy $E_i$ is sampled from the normal distribution $\mathcal{N}(\mathbb{E}(E_i), \mathbb{V}(E_i))$.
 Finally obtain and plot the histogram $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|E_i \text{ uncertain})$.
-    \item Fixed all $E_i$ to be $\mathbb{E}(E_i)$ and all $\log_{10}(J_{ij}^2)$ to be $\mathbb{E}(\log_{10}(J_{ij}^2))$.
+%    \item Fixed all $E_i$ to be $\mathbb{E}(E_i)$ and all $\log_{10}(J_{ij}^2)$ to be $\mathbb{E}(\log_{10}(J_{ij}^2))$.
 Then $\lambda$ is sampled from the normal distribution $\mathcal{N}(\mathbb{E}(\lambda), \mathbb{V}(\lambda))$.
 Finally obtain and plot the histogram  $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|\lambda \text{ uncertain})$.
-    \item Fixed the $\lambda$ to be $\mathbb{E}(\lambda)$ and all $E_i$ to be $\mathbb{E}(E_i)$.
+%    \item Fixed the $\lambda$ to be $\mathbb{E}(\lambda)$ and all $E_i$ to be $\mathbb{E}(E_i)$.
 Then $J_{ij}$ is sampled from the normal distribution $\log_{10}(J_{ij}^2) \in \mathcal{N}(\mathbb{E}(\log_{10}(J_{ij}^2)), \mathbb{V}(\log_{10}(J_{ij}^2)))$.
 Finally obtain and plot the histogram  $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$.
-    \item Both $E_i$, $\lambda$ and $J_{ij}$ are sampled from their normal distribution:
+%    \item Both $E_i$, $\lambda$ and $J_{ij}$ are sampled from their normal distribution:
 
-    $\lambda_i \in \mathcal{N}(\mathbb{E}(\lambda), \mathbb{V}(\lambda))$,
+%    $\lambda_i \in \mathcal{N}(\mathbb{E}(\lambda), \mathbb{V}(\lambda))$,
 
-    $E_i \in \mathcal{N}(\mathbb{E}(E), \mathbb{V}(E))$,
+%    $E_i \in \mathcal{N}(\mathbb{E}(E), \mathbb{V}(E))$,
 
-    $\log_{10}J_{ij}^2 \in \mathcal{N}(\mathbb{E}(\log_{10}J_{ij}^2), \mathbb{V}(\log_{10}J_{ij}^2))$.
-    Then obtain and plot the histogram $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as the following distribution: 
-    $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$.
-\end{enumerate}
+%    $\log_{10}J_{ij}^2 \in \mathcal{N}(\mathbb{E}(\log_{10}J_{ij}^2), \mathbb{V}(\log_{10}J_{ij}^2))$.
+%    Then obtain and plot the histogram $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as the following distribution: 
+%    $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$.
+%\end{enumerate}
+
+\bjoern{STOP}{HERE}
 
@@
 
+\subsection{Sobol indices}
 Measuring the sensitivity of each electronic parameter to ToF is to measure each electronic parameter's contribution to the variance of ToF. 

### 2025-01-06 paper.tex
change figure6 and text

@@
 \bjoern{STOP}{HERE}
+The analytical forms of the distribution $P_\lambda(\log_{10}(\tau))$, $P_E(\log_{10}(\tau))$, $P_J(\log_{10}(\tau))$ and $P_\mathbf{x}(\log_{10}(\tau))$ are usually unknown. 
+To quantify the uncertainty and variability in the sample data, we calculate a $99\%$ confidence interval around the median. 
+This statistical quantity is typically nonparametric, and relies on percentiles of the data, making it robust to different types of probability mass function.
+
+Using the equal-tailed percentile method, its calculation involves sorting the data and determining percentiles that correspond to the desired confidence level.
+Given a dataset $\{ \tau_1, \tau_2, \dots, \tau_n \}$, the procedure can be described as follows:
+\begin{enumerate}
+  \item Sort the data in ascending order. For a confidence level $CL$, the corresponding complement 
+  $1-CL$ determines the tails of the interval. 
+  \item Find the lower bound $\tau_{\eta}$ corresponds to the $\eta$-th percentile of the dataset where $\eta = (1-CL)/2$. For a $99\%$ confidence interval, $\eta=0.05$.
+  \item Find the upper bound $\tau_{(1-\eta)}$ corresponds to the $(1-\eta)$-th percentile of the dataset.
+  \item The confidence interval around the median is $[\tau_{\eta}, \tau_{(1-\eta)}]$.
+\end{enumerate}
 

### 2025-01-06 paper.tex
few sentences only

--- 2025-01-06 paper.tex
@@
 In the fourth setting, all parameters are sampled at the same time, yielding $P_\mathbf{x}(\log_{10}(\tau))$.
+As these distributions do not necessarily follow any specific analytic form, we estimate a $99\%$ confidence interval around the median using the equal-tailed percentile method.
 
@@
 
+%The analytical forms of the distribution $P_\lambda(\log_{10}(\tau))$, $P_E(\log_{10}(\tau))$, $P_J(\log_{10}(\tau))$ and $P_\mathbf{x}(\log_{10}(\tau))$ are usually unknown. 
+%To quantify the uncertainty and variability in the sample data, we calculate a $99\%$ confidence interval around the median. 
+%This statistical quantity is typically nonparametric, and relies on percentiles of the data, making it robust to different types of probability mass function.
+
+%Using the equal-tailed percentile method, its calculation involves sorting the data and determining percentiles that correspond to the desired confidence level.
+%Given a dataset $\{ \tau_1, \tau_2, \dots, \tau_n \}$, the procedure can be described as follows:
+%\begin{enumerate}
+%  \item Sort the data in ascending order. For a confidence level $CL$, the corresponding complement 
+%  $1-CL$ determines the tails of the interval. 
+%  \item Find the lower bound $\tau_{\eta}$ corresponds to the $\eta$-th percentile of the dataset where $\eta = (1-CL)/2$. For a $99\%$ confidence interval, $\eta=0.05$.
+%  \item Find the upper bound $\tau_{(1-\eta)}$ corresponds to the $(1-\eta)$-th percentile of the dataset.
+%  \item The confidence interval around the median is $[\tau_{\eta}, \tau_{(1-\eta)}]$.
+%\end{enumerate}
+
+The four respective distributions of $\tau$ in the MADN system are shown in Fig.~\ref{fig:mle_MADN_withE} together with the indicated confidence intervals.
+Considering first the three distributions with single property sampling in panels (a)-(c), we find the confidence intervals for $\log_{10}(\tau)$ of $[-8.0,-7.4]$ for uncertain $\lambda$, $[-8.0,-6.5]$ for uncertain $E$, and $[-7.9,-7.7]$ for uncertain $J$, respectively.
+Interestingly, all three share very similar lower limits of the confidence interval, while the upper limits and the shape of the distributions differ significantly.
 \bjoern{STOP}{HERE}
 
-The ToF distribution for the MADN systems with energy disorder is shown in Fig.\ref{fig:mle_MADN_withE}.
 The lower and upper bounds in Fig.

### 2025-01-07 paper.tex
ending ToF

@@
 As these distributions do not necessarily follow any specific analytic form, we estimate a $99\%$ confidence interval around the median using the equal-tailed percentile method.
+\bjoern{Maybe discuss somewhere:}{correlations between parameters are gone, especially in site energies, but they are (practically) uncorrelated in MADN.}
 
@@
 
-\begin{figure}
+\begin{figure}[tbp]
   \centering
@@
 
-The four respective distributions of $\tau$ in the MADN system are shown in Fig.~\ref{fig:mle_MADN_withE} together with the indicated confidence intervals.
+The four respective distributions of $\tau$ in the MADN system are shown in Fig.~\ref{fig:mle_MADN_withE} together with the indicated confidence intervals obtained from Monte-Carlo sampling.
+Black dots at the $x$-axes are the data from the explicit calculations for the six \ahfx values discussed before.
 Considering first the three distributions with single property sampling in panels (a)-(c), we find the confidence intervals for $\log_{10}(\tau)$ of $[-8.0,-7.4]$ for uncertain $\lambda$, $[-8.0,-6.5]$ for uncertain $E$, and $[-7.9,-7.7]$ for uncertain $J$, respectively.
 Interestingly, all three share very similar lower limits of the confidence interval, while the upper limits and the shape of the distributions differ significantly.
-\bjoern{STOP}{HERE}
+While $P_\lambda(\log_{10}(\tau))$ and $P_J(\log_{10}(\tau))$ appear relatively symmetric, indictaing possible a log-normal distribution of $\tau$, $P_E(\log_{10}(\tau))$ is distinctly asymmetric which might point to a normal distribution of $\tau$ for uncertain energies.
+From the three distributions and the confidence intervals one can see that the effect of the uncertainty in the coupling elements on the time-of-flight is small (factor of 2 on $\tau$).
+The effect of uncertainty in the reorganization energy is only slightly higher (factor of four).
+Uncertainty in the site energies, in contrast, has a much bigger impact on the estimates of $\tau$.
+From the distribution of $P_\mathbf{x}(\log_{10}(\tau))$ in Fig.~\ref{fig:mle_MADN_withE}(d), one can see than when all parameters are sampled, the result is dominated by the effects from the uncertainty in the site energies, with an overall similar shape and a confidence interval of $[-8.3,-6.6]$, corresponding to a range from about \unit[5]{ns} to about \unit[250]{ns} in $\tau$.
 
-The lower and upper bounds in Fig.
-\ref{fig:mle_MADN_withE} shows that when only the energies $E_i$ are uncertain, the $\log_{10}(\tau)$ has lower -8.0 and upper bound -6.5.
-This lower and upper bound is close to that of $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$, meaning that varying the energy alone generates a $\tau$ distribution close to that when $E_i, \lambda, J_{ij}$ are uncertain.
-
-Figure .\ref{fig:mle_MADN_withE}(b) shows that $\log_{10}(\tau)$ has a confidence interval of -8.0 to -7.4 when $\lambda$ is varied. 
-Figure \ref{fig:mle_MADN_withE}(c) show that when $J_{ij}$ is uncertain $\log_{10}(\tau)$ has a narrow confidence interval of -7.9 to -7.7, suggesting that the variation in $J_{ij}$ leads to relatively small change in $\log_{10}(\tau)$ compared to $E_i$ and $\lambda$.
+%Figure .\ref{fig:mle_MADN_withE}(b) shows that $\log_{10}(\tau)$ has a confidence interval of -8.0 to -7.4 when $\lambda$ is varied. 
+%Figure \ref{fig:mle_MADN_withE}(c) show that when $J_{ij}$ is uncertain $\log_{10}(\tau)$ has a narrow confidence interval of -7.9 to -7.7, suggesting that the variation in $J_{ij}$ leads to relatively small change in $\log_{10}(\tau)$ compared to $E_i$ and $\lambda$.
 
 %
-\begin{figure}[t]
-  \centering
-  \includegraphics[width=0.45\textwidth]{figs/fig_mle_MADN_noE.pdf}
-  \caption{\bjoern{TODO Zhong:}{these should also strictly be $\log_{10}(\tau/\unit[]{s})$.}Distribution of ToFs in the multiscale modeled MADN system.
-  Monte Carlo sampling with a sample size $N_\text{MC}=50000$ is used to obtain the sampled distribution.
+%\begin{figure}[t]
+%  \centering
+%  \includegraphics[width=0.45\textwidth]{figs/fig_mle_MADN_noE.pdf}
+%  \caption{\bjoern{TODO Zhong:}{these should also strictly be $\log_{10}(\tau/\unit[]{s})$.}Distribution of ToFs in the multiscale modeled MADN system.
+%  Monte Carlo sampling with a sample size $N_\text{MC}=50000$ is used to obtain the sampled distribution.
 The red vertical lines indicate the lower bound and upper bound of the 99\% confidence interval around the median.
-  Energy disorder is not consider. 
-  The black circles indicate the ToF obtained using varying HFX values.
-  (a) $P(\log_{10}(\tau)|\lambda \text{ uncertain})$, 
-  (b) $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$, 
-  (c) $P(\log_{10}(\tau)|\lambda, J_{ij} \text{ uncertain})$. }
-  \label{fig:mle_MADN_noE}
-\end{figure}
+%  Energy disorder is not consider. 
+%  The black circles indicate the ToF obtained using varying HFX values.
+%  (a) $P(\log_{10}(\tau)|\lambda \text{ uncertain})$, 
+%  (b) $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$, 
+%  (c) $P(\log_{10}(\tau)|\lambda, J_{ij} \text{ uncertain})$. }
+%  \label{fig:mle_MADN_noE}
+%\end{figure}
 %
 
-When the energy disorder in MADN system is not considered, that is, all the MADN molecule energy are set to be equal giving $\Delta E=0$, the distribution of ToF is shown in Fig.\ref{fig:mle_MADN_noE}.
-The distribution $P(\log_{10}(\tau)|\lambda \text{ uncertain})$ has a range of confidence interval -9.6 to -9.0 resembles that of $P(\log_{10}(\tau)|\lambda, J_{ij} \text{ uncertain})$, which has a range of confidence interval -9.7 to -9.1.
+%When the energy disorder in MADN system is not considered, that is, all the MADN molecule energy are set to be equal giving $\Delta E=0$, the distribution of ToF is shown in Fig.\ref{fig:mle_MADN_noE}.
+%The distribution $P(\log_{10}(\tau)|\lambda \text{ uncertain})$ has a range of confidence interval -9.6 to -9.0 resembles that of $P(\log_{10}(\tau)|\lambda, J_{ij} \text{ uncertain})$, which has a range of confidence interval -9.7 to -9.1.
 
 \subsection{Sobol indices}
-Measuring the sensitivity of each electronic parameter to ToF is to measure each electronic parameter's contribution to the variance of ToF. 
-That is, if ToF is most sensitive to one parameter, the variance in this particular parameter will contribute most to the ToF variance.
+Besides the inspection on the distributions for various uncertain parameter (sets) as above, one can also quantify the sensitivity of the time-of-fight to the respective parameters by evaluating their contributions to the overall observed variance in $\tau$.
+One way of decomposing the variance of the model output into fractions attributed to input parameters is the variance-based sensitivity analysis using Sobol indices~\cite{saltelli_variance_2010}.
 
-One way of decomposing the variance of the model output into fractions attributed to input parameters is the variance-based sensitivity analysis.
-The local sensitive analysis is to use the partial derivative $\frac{\partial \tau}{\partial x_i}$.
-While the global sensitivity analysis can use Sobol's indices.
-Given a model of Equation \ref{eq:tau1}, to measure the parameter $x_i$'s contribution to $\tau$ including all variance caused by its interaction with other parameters $\{x_k, k \neq i \}$, the total effect Sobol's index is calculated as \cite{saltelli_variance_2010}:
+To measure the parameter $x_i$'s contribution to $\tau=\tau(\mathbf{x})$ including all variance caused by its interaction with other parameters $\{x_k, k \neq i \}$, the total Sobol index $S_{T,i}$ is calculated as
+%
 \begin{equation}
-    S_{T,i} = \frac{ \mathbb{E}_{\mathbf{x}_{\sim i}}[ \mathbb{V}_{x_i}(\tau|\mathbf{x}_{\sim i}) ] }{ \mathbb{V}(\tau) }
+    S_{T,i} = \frac{ \mathbb{E}_{\mathbf{x}_{\sim i}}[ \mathbb{V}_{x_i}(\tau|\mathbf{x}_{\sim i}) ] }{ \mathbb{V}(\tau) } .
     \label{eq:STi}
 \end{equation}
-The details of the notation is as followed: the vector $\mathbf{x}=(x_1, x_2, \cdots, x_{N_d})$, and $\mathbf{x}_{\sim i}$ denotes the vector of all entries but $x_i$. 
-$\mathbb{V}_{x_i}(\tau|\mathbf{x}_{\sim i})$ means the variance of $\tau$ given a set of $\mathbf{x}_{\sim i}$ taken over $x_i$.
-And $ \mathbb{E}_{\mathbf{x}_{\sim i}}[\cdot]$ denotes the mean of argument $(\cdot)$ taken over all factors but $x_i$.
+%
+Here, $\mathbf{x}_{\sim i}$ denotes the vector of all entries of $\mathbf{x}$ but $x_i$.
+The variance of $\tau$ given a set of $\mathbf{x}_{\sim i}$ taken over $x_i$ is $\mathbb{V}_{x_i}(\tau|\mathbf{x}_{\sim i})$ and $ \mathbb{E}_{\mathbf{x}_{\sim i}}[\cdot]$ denotes the mean of argument $(\cdot)$ taken over all factors but $x_i$.
+We then consider based on the structure of the vector $\mathbf{x}$ the Sobol index for the reorganization energy as $S_{T,\lambda} = S_{T,1}$, for the site energies as $S_{T,E} = \sum\limits_{i=2}^{N+1} S_{T,i}$, and for the coupling elements as $S_{T,E} = \sum\limits_{i=N+2}^{N+1+N_\text{p}} S_{T,i}$.
+Using the quasi Monte Carlo method\cite{sobol_global_2001} with a sample size $N_\text{QMC}=1000$ to calculate $S_{T,i}$, we find that $S_{T,\lambda}=0.097$, $S_{T,E} =0.950$ and $S_{T,J}=0.018$.
+The Sobol indices corroborate the observation from the confidence intervals that the uncertainty in the site energies gives the dominant contribution to the variance of the simulated time-of-flight.
+Contributions from the reorganization energy and the coupling elements are both small in relation, with the one of $\lambda$ slightly larger than the one of $J$.
+This is also in line with the general observations on the distributions in Fig.~\ref{fig:mle_MADN_withE}.
 
+%\begin{table}[tbp]%The best place to locate the table environment is directly after its first reference in text
+%\caption{\label{tab:Sobol}%
+%Sobol indices of $\lambda$, $E$ and $\log_{10} J^2$ when ToF is calculated with energy disorder, and Sobol indices of $\lambda$ and $\log_{10} J^2$ when ToF is calculated without energy disorder.
+%}
+%\begin{ruledtabular}
+%  \begin{center}
+%    \begin{tabular}{c c c c c c c} %\hline
+%      &  \multicolumn{3}{c}{\bf Energy Disorder} & &\multicolumn{2}{c}{\bf no Disorder}\\\cline{2-4}  \cline{6-7}
+%      parameter  & $\lambda$ & $ E_i$ & $ \log_{10}(J_{ij}^2)$ && $\lambda$ & $ \log_{10}(J_{ij}^2)$ \\ \hline
+      %\multicolumn{6}{c}{\bf GRW for $\mathbf{N_c=1}$}\\
+%   $S_T$  & 0.097 & 0.95 & 0.018 && 0.96 & 0.11 \\
+%    \end{tabular}
+%  \end{center}
+%\end{ruledtabular}
+%\end{table}
 %
-\begin{table}[tbp]%The best place to locate the table environment is directly after its first reference in text
-\caption{\label{tab:Sobol}%
-Sobol indices of $\lambda$, $E$ and $\log_{10} J^2$ when ToF is calculated with energy disorder, and Sobol indices of $\lambda$ and $\log_{10} J^2$ when ToF is calculated without energy disorder.
-}
-\begin{ruledtabular}
-  \begin{center}
-    \begin{tabular}{c c c c c c c} %\hline
-      &  \multicolumn{3}{c}{\bf Energy Disorder} & &\multicolumn{2}{c}{\bf no Disorder}\\\cline{2-4}  \cline{6-7}
-      parameter  & $\lambda$ & $ E_i$ & $ \log_{10}(J_{ij}^2)$ && $\lambda$ & $ \log_{10}(J_{ij}^2)$ \\ \hline
-      %\multicolumn{6}{c}{\bf GRW for $\mathbf{N_c=1}$}\\
-   $S_T$  & 0.097 & 0.95 & 0.018 && 0.96 & 0.11 \\
-    \end{tabular}
-  \end{center}
-\end{ruledtabular}
-\end{table}
-%
-Then the $\lambda$ contribution to the total variance is $S_{T,i=1}$.
-The energy contribution to the total variance is $S_{T,E} = \sum\limits_{i=1}^{N+1} S_{T,i}$ where $N=1000$ is the number of energy parameter, and the coupling element contribution due to variation in $\log_{10}(J_{ij}^2)$ to the total variance is $S_{T,J}=\sum\limits_{i=N+2}^{N_d} S_{T,i}$.
-Using the quasi Monte Carlo method\cite{sobol_global_2001} with a sample size $N_\text{QMC}=1000$ to calculate $S_{T,i}$, the results are shown in the table \ref{tab:Sobol}.
 
-From table \ref{tab:Sobol} one can see that most of the total variance can be attributed to the energy $E$.
+%From table \ref{tab:Sobol} one can see that most of the total variance can be attributed to the energy $E$.
 In contrast to $E$, the uncertainty in $\lambda$ and $\log_{10} J^2$ contributes much less compared to $E$, this is consistent to the Fig.\ref{fig:mle_MADN_withE}, where the distribution in Fig.\ref{fig:mle_MADN_withE}(d) resembles the distribution in Fig.\ref{fig:mle_MADN_withE}(a).
-And Fig.\ref{fig:mle_MADN_withE}(c) shows that the uncertainty in $\log_{10}(J^2)$ only leads to small variances.
-When there is no energy disorder, the variance in $\lambda$ has the most contribution to the total variance as shown in Table \ref{tab:Sobol}.
+%And Fig.\ref{fig:mle_MADN_withE}(c) shows that the uncertainty in $\log_{10}(J^2)$ only leads to small variances.
+%When there is no energy disorder, the variance in $\lambda$ has the most contribution to the total variance as shown in Table \ref{tab:Sobol}.
+
+\bjoern{STOP}{HERE}
 

### 2025-01-07 paper.tex
more in mobility

@@
 
-\subsection{Monte-Carlo Sampling of ToF}
+\subsection{Time-of-flight of diffusion}
 As discussed the ToF is calculated from the graph with weighted edges defined by the electronic structure data $(\lambda, E_1,\ldots,E_N, J_1^2,\ldots,J_{N_\text{p}}^2)$, where $N$ is the number of molecules (vertices) and $N_\text{p}$ the number of molecule pairs (edges) in the neighbor list.
@@
 
-\subsection{Sobol indices}
+%\subsection{Sobol indices}
 Besides the inspection on the distributions for various uncertain parameter (sets) as above, one can also quantify the sensitivity of the time-of-fight to the respective parameters by evaluating their contributions to the overall observed variance in $\tau$.
@@
 %When there is no energy disorder, the variance in $\lambda$ has the most contribution to the total variance as shown in Table \ref{tab:Sobol}.
-
-\bjoern{STOP}{HERE}
 
@@
 
-\section{Charge mobility and PF Behavior}
-
-In this section, we want to study the dependence of drift mobility on the HFX. The charge mobility is calculated as:
+\subsection{Drift-diffusion Charge mobility}
+When an external electric field, $\mathbf{F}$, is applied to the system, the transport is not just diffusive but a drift-diffusion process. The material property of interest is then the drift mobility
+%
 \begin{equation}
-    \mu = \frac{\vec{v} \vec{F} }{ |\vec{F}|^2}
+    \mu = \frac{\mathbf{v} \mathbf{F} }{ |\mathbf{F}|^2},
     \label{eq:mu}
 \end{equation}
-To consider the charge dynamics along X, Y and Z axis in the ToF setting, the ToF is calculated with different settings of \textit{Source}-\textit{Sink} and $\vec{F}$ combinations.
+%
+where $\mathbf{v} = \mathbf{s}/{\tau}$ is the effective velocity of the charge carrier and $\mathbf{s}$ is the vector connecting the inital and final positions of the charge carrier.
+Here, we perform calculations for six different field directions (positive and negative Cartesian directions) with the source and sink conditions set accordingly.
+Finally, we define for a certain field strength $F=\vert\mathbf{F}\vert$  the ToF drift mobility $\mu(F)$ is as the average over the six directions.
 
-\begin{itemize}
-    \item Setting the molecules with $r^x < \min(r^x)+0.5$ as \textit{Source}, and the molecules with $r^x > \max(r^x)-0.5$ as \textit{Sink}, and $\vec{F}^T = (F,0,0)$, denote the calculated the ToF as $\tau_\text{Xmin}$, and the mobility is as $\mu_\text{Xmin} = \frac{L_x }{\tau_\text{Xmin} |\vec{F}|}$.
-    \item Setting the molecules with $r^x > \max(r^x)-0.5$ as \textit{Source}, and the molecules with $r^x < \min(r^x)+0.5$ as \textit{Sink}, and $\vec{F}^T = (-F,0,0)$, denote the calculated the ToF as $\tau_\text{Xmax}$, and the mobility is as $\mu_\text{Xmax} = \frac{L_x }{\tau_\text{Xmax} |\vec{F}|}$.
-    \item Setting the molecules with $r^y < \min(r^y)+0.5$ as \textit{Source}, and the molecules with $r^y > \max(r^y)-0.5$ as \textit{Sink}, and $\vec{F}^T = (0,F,0)$, denote the calculated the ToF as $\tau_\text{Ymin}$, and the mobility is as $\mu_\text{Ymin} = \frac{L_y }{\tau_\text{Ymin} |\vec{F}|}$.
-    \item Setting the molecules with $r^y > \max(r^y)-0.5$ as \textit{Source}, and the molecules with $r^y > \max(r^y)-0.5$ as \textit{Sink}, and $\vec{F}^T = (0,-F,0)$, denote the calculated the ToF as $\tau_\text{Ymax}$, and the mobility is as $\mu_\text{Ymax} = \frac{L_y }{\tau_\text{Ymax} |\vec{F}|}$.
-    \item Setting the molecules with $r^z < \min(r^z)+0.5$ as \textit{Source}, and the molecules with $r^z > \max(r^z)-0.5$ as \textit{Sink}, and $\vec{F}^T = (0,0,F)$, denote the calculated the ToF as $\tau_\text{Zmin}$, and the mobility is as $\mu_\text{Zmin} = \frac{L_z }{\tau_\text{Zmin} |\vec{F}|}$.
-    \item Setting the molecules with $r^z > \max(r^z)-0.5$ as \textit{Source}, and the molecules with $r^z > \min(r^z)+0.5$ as \textit{Sink}, and $\vec{F}^T = (0,0,-F)$, denote the calculated the ToF as $\tau_\text{Zmax}$, and the mobility is as $\mu_\text{Zmax} = \frac{L_z }{\tau_\text{Zmax} |\vec{F}|}$.
-\end{itemize}
-Finally the ToF drift mobility is calculated as:
-\begin{equation}
-    \mu_\text{PF} = \frac{1}{6} (\mu_\text{Xmin}+\mu_\text{Xmax}+\mu_\text{Ymin}+\mu_\text{Ymax}+\mu_\text{Zmin}+\mu_\text{Zmax})
-\end{equation}
-
-When the $\lambda, E_i, J_{ij}$ are uncertain and sampled from the normal distribution, the distributions of charge mobility obtained from MC sample under specific electric field are shown in Fig.\ref{fig:fig_mle_withE_mu2_ave}.
-%
-\begin{figure}
+\begin{figure}[tbp]
     \centering
-    \includegraphics[width=0.45\textwidth]{figs/fig_mle_withE_mu2_ave.pdf}
-    \caption{\bjoern{TODO Zhong:}{these should also strictly be $\log_{10}(\mu/(\unit[]{cm^2(Vs)^{-1}}))$; there should be no PF label at $\mu$.} Distribution of $\mu_\text{PF}$ in the multiscale modeled MADN system.
+    \includegraphics[width=\linewidth]{figs/fig_mle_withE_mu2_ave.pdf}
+    \caption{\bjoern{TODO Zhong:}{all panels should have the same x-axis range for better comparison} Distribution of $\mu_\text{PF}$ in the multiscale modeled MADN system.
     Monte Carlo sampling with a sample size $N_\text{MC}=10000$ is used to obtain the sampled distribution.
@@
 \end{figure}
-%
 
-When the $\lambda, E_i, J_{ij}$ are uncertain and sampled from the normal distribution, the distributions of charge mobility obtained from MC sample under specific electric field are shown in Fig.
-\ref{fig:fig_mle_withE_mu2_ave}.
-The ToF depends on the electric field through the Marcus rate.
-As the electric increase from $|\vec{F}|=4 \cdot 10^7 \unit{V/m}$
-$|\vec{F}|=9 \cdot 10^7 \unit{V/m}$, the
-range of the 90\% confidence interval where $\log_{10} \mu_\text{PF}$ lies
-estimated from the MC sample decrease from 0.90 to 0.69.
-So the electric field results in a narrower range of $\mu_\text{PF}$ distribution.
+We perform such mobility calculations for the six explicit \ahfx models as well as the Monte-Carlo sampled uncertainty for six different values of $F$.
+The results are shown in Fig.~\ref{fig:fig_mle_withE_mu2_ave}.
+While the distributions shift depending on the strength of the applied field, the overall shape and the width of the confidence intervals is very similar.
+The width of the confidence intervals in $\log_{10}(\mu)$ decreases from \unit[0.9] at low fields ($\unit[4 \cdot 10^7]{V/m}$) to \unit[0.9] at a field of $\unit[9 \cdot 10^7]{V/m}$, corresponding broadly to a width of close to one order of magnitude in $\mu$.
+A stronger drift component due to a larger external electric field seems to make the mobility slightly less sensitive to uncertainties \bjoern{CHECK}{not sure about this interpretation}.
+
+\bjoern{STOP}{HERE}
+
+%As the electric increase from $|\vec{F}|=4 \cdot 10^7 \unit{V/m}$
+%$|\vec{F}|=9 \cdot 10^7 \unit{V/m}$, the
+%range of the 90\% confidence interval \bjoern{TO CHECK}{above and below it is 99\%!!} where $\log_{10} \mu_\text{PF}$ lies
+%estimated from the MC sample decrease from 0.90 to 0.69.
+%So the electric field results in a narrower range of $\mu_\text{PF}$ distribution.
+
 Due to this reason, the $\mu_\text{PF}$ calculated from $\alpha=0$ is not in the 99\% confidence interval around the median of the MC sampled data, although the zero-field ToF of $\alpha=0$ is contained in the according 99\% confidence interval, as shown in Fig.

### 2025-01-07 paper.tex
change figure7

@@
 Panels (c) and (d) of Fig.~\ref{fig:autogen_MADN} show the dipole moment of the neutral MADN molecule and the isotropic polarizability of the neutral and cationic (hole) states, respectively, both as electrostatic properties that enter indirectly the parameterization of the microelectrostatic model.
-As is visible, the dipole moment is rather independent on \ahfx (note that the jump of the last shown data point appears more pronounced because of the vert small scale on the $y$-axis).
+As is visible, the dipole moment is rather independent on \ahfx (note that the jump of the last shown data point appears more pronounced because of the very small scale on the $y$-axis).
 The isotropic polarizabilities in panel (d) exhibit a linear decrease with increasing value of \ahfx which can be attributed to an increasingly attractive effective potential from stronger the Hartree--Fock-like exchange term and consequently more strongly bound electrons as one can also see from the increaseing ionization potential in panel (a).
@@
 Note that due to the data range for the electronic coupling element as discussed in the previous section, we consider $\log_{10}(J^2)$ instead of $J^2$.
-For MADN, we have that $M=XXX$ \bjoern{ADD:}{how many pairs?}
+For MADN, we have that $M=9765$.
+\bjoern{ADD:}{how many pairs?
+$N_\text{p}=8764$}
 
@@
 light the importance of selecting appropriate functionals to ensure model robustness.
-Also indicated is that for multiscale model charge mobility, when the values have difference is approximately 10\%, we should interpret the results with caution and refrain from concluding that they represent fundamentally different phenomena.
+Also indicated is that for multiscale model charge mobility, when the values have difference in approximately 10\%, we should interpret the results with caution and refrain from concluding that they represent fundamentally different phenomena.
 

### 2025-01-08 paper.tex
not sure what

--- 2025-01-07 paper.tex
@@
 %
-where $\mathbf{v} = \mathbf{s}/{\tau}$ is the effective velocity of the charge carrier and $\mathbf{s}$ is the vector connecting the inital and final positions of the charge carrier.
+where $\mathbf{v} = \mathbf{s}/{\tau}$ is the effective velocity of the charge carrier and $\mathbf{s}$ is the vector connecting the initial and final positions of the charge carrier.
 Here, we perform calculations for six different field directions (positive and negative Cartesian directions) with the source and sink conditions set accordingly.
+The electric field is taken account in the Marcus rate in Eq.~\ref{equ:Marcus} via an additional term in $\Delta E_{ij}$ given by $e\mathbf{F} \cdot \mathbf{r}_{ij}$, where $\mathbf{r}_{ij}$ connects the center-of-masses (COMs) of molecules $i$ and $j$.
 Finally, we define for a certain field strength $F=\vert\mathbf{F}\vert$ the ToF drift mobility $\mu(F)$ is as the average over the six directions.
@@
 While the distributions shift depending on the strength of the applied field, the overall shape and the width of the confidence intervals is very similar.
-The width of the confidence intervals in $\log_{10}(\mu)$ decreases from \unit[0.9] at low fields ($\unit[4 \cdot 10^7]{V/m}$) to \unit[0.9] at a field of $\unit[9 \cdot 10^7]{V/m}$, corresponding broadly to a width of close to one order of magnitude in $\mu$.
+The width of the confidence intervals in $\log_{10}(\mu)$ decreases from \unit[0.9]{} at low fields ($\unit[4 \cdot 10^7]{V/m}$) to \unit[0.7]{} at a field of $\unit[9 \cdot 10^7]{V/m}$, corresponding broadly to a width of close to one order of magnitude in $\mu$.
 A stronger drift component due to a larger external electric field seems to make the mobility slightly less sensitive to uncertainties \bjoern{CHECK}{not sure about this interpretation}.
+
+\begin{figure}[tbp]
+    \centering
+    \includegraphics[width=0.45\textwidth]{figs/fig_PF_plot_ave.pdf}
+    \caption{\bjoern{TODO Zhong:}{remove PF label; avoid the large white space at the right; make data plot symbols a little bigger and lines a little thicker.}Electric-field dependence of the mobility $\mu$ in the multiscale modeled MADN system.
+The dash lines are Poole--Frenkel plots obtained with specific HFX value, and the green shadow indicates the 99\% confidence interval estimated from the MC sampling with a sample size of $N_\text{MC}=10000$.}
+    \label{fig:PF_plot_ave}
+\end{figure}
+
+Figure~\ref{fig:PF_plot_ave} shows the plot of the charge mobility one logarithmic $y$-axis as a function of $\sqrt{F}$ to reveal the electric field dependence of the type $\mu(F)=\mu_0 \exp (\beta \sqrt{F})$ as predicted by Poole and Frenkel~\cite{frenkel_prebreakdown_1938}.
+We show the explicit results for the six chosen \ahfx values together with the confidence interval estimate from the uncertainty quantification via Monte-Carlo sampling.
 
@@
 
-Due to this reason, the $\mu_\text{PF}$ calculated from $\alpha=0$ is not in the 99\% confidence interval around the median of the MC sampled data, although the zero-field ToF of $\alpha=0$ is contained in the according 99\% confidence interval, as shown in Fig.
-\ref{fig:mle_MADN_withE}(d).
+This interval suggests that if the uncertainties from the parameters are represented by the maximum likelihood distribution, the Poole–Frenkel plot from $\alpha=0$ has less 1\% chance to happen and thus is very likely.
 
-The ToF depends on the electric field through the Marcus rate. 
-Poole and Frenkel \cite{frenkel_prebreakdown_1938} predicted the electric-field dependence of charge mobility as $\mu_\text{PF}(F)=\mu_0 \exp (\beta \sqrt{|\vec{F}|})$.
-So it is common to plot the mobility $\mu_\text{PF}$ against $\sqrt{|\vec{F}|}$ in a so-called Poole-Frenkel plot.
-which is shown in Fig. \ref{fig:PF_plot_ave} for specifie HFX values. The 99\% confidence interval obtained via MC sampled in shown in the green shadow. 
-This interval suggests that if the uncertainties from the parameters are represented by the maximum likelihood distribution, the Poole–Frenkel plot from $\alpha=0$ has less 1\% chance to happen and thus is very likely.
-%
-\begin{figure}[tbp]
-    \centering
-    \includegraphics[width=0.45\textwidth]{figs/fig_PF_plot_ave.pdf}
-    \caption{\bjoern{TODO Zhong:}{remove PF label; avoid the large white space at the right; make data plot symbols a little bigger and lines a little thicker.}Electric-field dependence of the mobility $\mu$ in the multiscale modeled MADN system.
-The dash lines are Poole–Frenkel plots obtained with specific HFX value, and the green shadow indicates the 99\% confidence interval estimated from the MC sampling with a sample size of $N_\text{MC}=10000$.}
-    \label{fig:PF_plot_ave}
-\end{figure}
-
-%
 \begin{table}[tbp]%The best place to locate the table environment is directly after its first reference in text
@@
     0.20 & & $9.3 \cdot 10^{-4}$ & & $1.3 \cdot 10^{-3}$ \\
-    0.20 & & $2.6 \cdot 10^{-4}$ & & $1.8 \cdot 10^{-3}$ \\
+    0.25 & & $2.6 \cdot 10^{-4}$ & & $1.8 \cdot 10^{-3}$ \\
       \end{tabular}
@@
   \end{table}
-%  
+
 The extracted Poole–Frenkel paratermeter calculated from the six $\alpha$ values are summarized in Table \ref{tab:PF_parameter}. 
@@
 So $\beta$ is less sensitive to the multiscale model parameter $\alpha$ compared the zero-field mobility.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Conclusion}

### 2025-01-08 paper.tex
add sobol index data in fig/sobol_data

@@
 We then consider based on the structure of the vector $\mathbf{x}$ the Sobol index for the reorganization energy as $S_{T,\lambda} = S_{T,1}$, for the site energies as $S_{T,E} = \sum\limits_{i=2}^{N+1} S_{T,i}$, and for the coupling elements as $S_{T,E} = \sum\limits_{i=N+2}^{N+1+N_\text{p}} S_{T,i}$.
-Using the quasi Monte Carlo method\cite{sobol_global_2001} with a sample size $N_\text{QMC}=1000$ to calculate $S_{T,i}$, we find that $S_{T,\lambda}=0.097$, $S_{T,E} =0.950$ and $S_{T,J}=0.018$.
+Using the quasi Monte Carlo method\cite{sobol_global_2001} with a sample size $N_\text{QMC}=1000$ to calculate $S_{T,i}$, we find that $S_{T,\lambda}=0.097$, $S_{T,E} =0.950$ and $S_{T,J}=0.028$.
 The Sobol indices corroborate the observation from the confidence intervals that the uncertainty in the site energies gives the dominant contribution to the variance of the simulated time-of-flight.

### 2025-01-08 figs/sobol_data/plot_sobol_E_dist.py

@@ -1,0 +1,58 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import scipy as sp
+import matplotlib.pyplot as plt
+import xml.etree.ElementTree as ET
+
+data = np.loadtxt("Sobol_Sti_E.txt")
+Sti_max = np.max(data)
+print(Sti_max)
+print(np.argmax(np.max(data)))
+########## get energy and coordinates
+N=1000
+posX = np.zeros(N)
+print(max(posX))
+posY = np.zeros(N)
+posZ = np.zeros(N)
+eCation = np.zeros(N)
+index = np.zeros(N)
+
+tree = ET.parse('jobs.xml')
+root = tree.getroot()
+
+for i in range(int(len(root)/3)):
+    posX[i] = float(root[i*3][6][0][1].text.split()[0])
+    posY[i] = float(root[i*3][6][0][1].text.split()[1])
+    posZ[i] = float(root[i*3][6][0][1].text.split()[2])
+    eCation[i] = float(root[i*3+2][6][0][2].text) - float(root[i*3][6][0][2].text)
+    index[i] = i
+
+nbins = 50
+setupsize = 18
+
+fig = plt.figure(figsize=(14, 6))
+# First subplot with 3D projection
+ax1 = fig.add_subplot(1,2,1, projection='3d')
+ax1.view_init(elev=25, azim=70, roll=1)
+scatter = ax1.scatter(posX, posY,posZ, c=(np.log10(data)), cmap='viridis', s=40, alpha=0.7)  # Adjust 'cmap' as needed
+cbar = plt.colorbar(scatter, ax=ax1, label=r'log$_{10}S_{T,i}$')  # Add colorbar for reference
+cbar.ax.tick_params(labelsize=setupsize)
+cbar.set_label(r'log$_{10}S_{T,i}$', size=setupsize)
+ax1.set_xlabel(r'$X$ [nm]',fontsize=setupsize)
+ax1.set_ylabel(r'$Y$ [nm]',fontsize=setupsize)
+ax1.set_zlabel(r'$Z$ [nm]',fontsize=setupsize)
+ax1.tick_params(axis='both', labelsize=setupsize)
+ax1.annotate("(a)", xy=(-0.05,1.03), xycoords='axes fraction', size=setupsize)
+
+ax2 = fig.add_subplot(1,2,2)
[…]

### 2025-01-08 figs/sobol_data/plot_sobol_J_dist.py

@@ -1,0 +1,30 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import scipy as sp
+import matplotlib.pyplot as plt
+import xml.etree.ElementTree as ET
+
+data = np.loadtxt("Sobol_Sti_J_all.txt")
+data1 = []
+for i in range(len(data)):
+    if data[i] > 1e-35:
+        data1.append(data[i])
+
+########## get energy and coordinates
+
+
+nbins = 50
+setupsize = 18
+
+fig,ax2 = plt.subplots()
+ax2.hist(np.log10(data1), bins= nbins,histtype='step', linewidth=2, facecolor='c', 
+         hatch='|', edgecolor='k',fill=True)
+ax2.set_xlabel(r'log$_{10}S_{T,i}$', fontsize=setupsize)
+ax2.set_ylabel(r'counts', fontsize=setupsize)
+ax2.tick_params(axis="both",labelsize=setupsize)
+ax2.annotate("(b)", xy=(-0.15,1.03), xycoords='axes fraction', size=setupsize)
+
+# Show the plot
+plt.tight_layout()
+fig.savefig("fig_Sobol_J.pdf",dpi=300)
+fig.savefig("fig_Sobol_J.png",dpi=300)

### 2025-01-09 figs/sobol_data/sobol_E.py
some additional plots

@@ -1,0 +1,22 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy.stats import gaussian_kde
+
+data=np.loadtxt("Eid_ave_std_sobol.txt")
+
+id=data[:,0]
+E=data[:,1]
+std=data[:,2]
+sobol=data[:,3]
+nbins = 50
+values=np.vstack([E, sobol])
+k = gaussian_kde(values)
+xi, yi = np.mgrid[E.min():E.max():nbins*1j, sobol.min():sobol.max():nbins*1j]
+zi = k(np.vstack([xi.flatten(), yi.flatten()]))
+plt.pcolormesh(xi, yi, zi.reshape(xi.shape), shading='gouraud', cmap=plt.cm.BuGn_r)
+plt.contour(xi, yi, zi.reshape(xi.shape) )
+#plt.yscale("log")
+
+plt.scatter(E,std)
+plt.show()
+

### 2025-01-09 figs/sobol_data/sobol_J.py

@@ -1,0 +1,25 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy.stats import gaussian_kde
+
+data=np.loadtxt("J_id_seg1_seg2_ave_std_sobol.txt")
+
+id=data[:,0]
+J=data[:,3]
+std=data[:,4]
+sobol=data[:,5]
+nbins = 50
+values=np.vstack([J, std])
+k = gaussian_kde(values)
+xi, yi = np.mgrid[J.min():J.max():nbins*1j, std.min():std.max():nbins*1j]
+zi = k(np.vstack([xi.flatten(), yi.flatten()]))
+plt.pcolormesh(xi, yi, zi.reshape(xi.shape), shading='gouraud', cmap=plt.cm.BuGn_r)
+plt.contour(xi, yi, zi.reshape(xi.shape) )
+
+
+
+#plt.yscale("log")
+#plt.ylim([1e-20,1e-1])
+#plt.scatter(J,std)
+plt.show()
+

### 2025-01-09 paper.tex
little ending

@@
 
-Figure~\ref{fig:PF_plot_ave} shows the plot of the charge mobility one logarithmic $y$-axis as a function of $\sqrt{F}$ to reveal the electric field dependence of the type $\mu(F)=\mu_0 \exp (\beta \sqrt{F})$ as predicted by Poole and Frenkel~\cite{frenkel_prebreakdown_1938}.
-We show the explicit results for the six chosen \ahfx values together with the confidence interval estimate from the uncertainty quantification via Monte-Carlo sampling.
-
-\bjoern{STOP}{HERE}
-
-%As the electric increase from $|\vec{F}|=4 \cdot 10^7 \unit{V/m}$
-%$|\vec{F}|=9 \cdot 10^7 \unit{V/m}$, the
-%range of the 90\% confidence interval \bjoern{TO CHECK}{above and below it is 99\%!!} where $\log_{10} \mu_\text{PF}$ lies
-%estimated from the MC sample decrease from 0.90 to 0.69.
-%So the electric field results in a narrower range of $\mu_\text{PF}$ distribution.
-
-This interval suggests that if the uncertainties from the parameters are represented by the maximum likelihood distribution, the Poole–Frenkel plot from $\alpha=0$ has less 1\% chance to happen and thus is very likely.
-
 \begin{table}[tbp]%The best place to locate the table environment is directly after its first reference in text
@@
   \begin{ruledtabular}
-    \begin{tabular}{c c c c c}
-    $\alpha$ & & $\mu_0$  & & $\beta$ \\
+    \begin{tabular}{c c c}
+    $\ahfx$ & $\mu_0$  & $\beta$ \\
       \hline
-    0 & & $4.0 \cdot 10^{-3}$ & & $1.0 \cdot 10^{-3}$ \\
-    0.05 & & $2.1 \cdot 10^{-3}$ & & $9.3 \cdot 10^{-4}$ \\
-    0.10 & & $1.0 \cdot 10^{-3}$ & & $1.5 \cdot 10^{-3}$ \\
-    0.15 & & $8.0 \cdot 10^{-4}$ & & $1.6 \cdot 10^{-3}$ \\
-    0.20 & & $9.3 \cdot 10^{-4}$ & & $1.3 \cdot 10^{-3}$ \\
-    0.25 & & $2.6 \cdot 10^{-4}$ & & $1.8 \cdot 10^{-3}$ \\
+    0 & $4.0 \cdot 10^{-3}$ & $1.0 \cdot 10^{-3}$ \\
+    0.05 & $2.1 \cdot 10^{-3}$ & $9.3 \cdot 10^{-4}$ \\
+    0.10 & $1.0 \cdot 10^{-3}$ & $1.5 \cdot 10^{-3}$ \\
+    0.15 & $8.0 \cdot 10^{-4}$ & $1.6 \cdot 10^{-3}$ \\
+    0.20 & $9.3 \cdot 10^{-4}$ & $1.3 \cdot 10^{-3}$ \\
+    0.25 & $2.6 \cdot 10^{-4}$ & $1.8 \cdot 10^{-3}$ \\
       \end{tabular}
@@
 
-The extracted Poole–Frenkel paratermeter calculated from the six $\alpha$ values are summarized in Table \ref{tab:PF_parameter}. 
-Excluding the data of $\alpha=0$, the extracted zero-field mobility $\mu_0$ has a range from $2.6 \cdot 10^{-4}$ to $2.1 \cdot 10^{-3}$, and the field effect constant $\beta$ range from $9.3 \cdot 10^{-4}$ to $1.8 \cdot 10^{-3}$.
-So $\beta$ is less sensitive to the multiscale model parameter $\alpha$ compared the zero-field mobility.
+Figure~\ref{fig:PF_plot_ave} shows the plot of the charge mobility one logarithmic $y$-axis as a function of $\sqrt{F}$ to reveal the electric field dependence of the type $\mu(F)=\mu_0 \exp (\beta \sqrt{F})$ as predicted by Poole and Frenkel~\cite{frenkel_prebreakdown_1938}.
+We show the explicit results for the six chosen \ahfx values together with the confidence interval estimate from the uncertainty quantification via Monte-Carlo sampling.
+In Table~\ref{tab:PF_parameter} we also summarize the  parameters $\mu_0$ and $\beta$ extracted from fits of the explicit data to the Poole--Frenkel expression.
+The values for $\mu_0$ vary from $\unit[2.6\cdot 10^{-4}]{cm^2/(Vs)}$ to $\unit[4.0\cdot 10^{-3}]{cm^2/(Vs)}$, roughly one order or magnitude depending on the chosen \ahfx, in line with the uncertainty from the Monte-Carlo sampling.
+The Poole--Frenkel slope $\beta$ in contrast is found to be much less sensitive to uncertainties, with recorded values between $\unit[9.3\cdot 10^{-4}]{\sqrt{cm/V}}$ and $\unit[1.8\cdot 10^{-3}]{\sqrt{cm/V}}$.
+
+\bjoern{STOP}{HERE}
+\begin{itemize}
+\item \ahfx, while only a proxy for the use of different functionals in MMM, gives a good indication the challenges in obtaining quantutative predictions of charge mobilities
+\item uncertainty for a low/moderate disorder material covering a range of one order of magnitude 
+\item field-dependence much less affected
+\item uncertainty mostly stems from site energy uncertainties, in a broader sense this highlights the importance for accurate methods to determine these energies not just as a distribution
+\end{itemize}
 

### 2025-01-09 figs/sobol_data/sobol_J.py

@@ -13,10 +13,10 @@ values=np.vstack([J, std])
 k = gaussian_kde(values)
 xi, yi = np.mgrid[J.min():J.max():nbins*1j, std.min():std.max():nbins*1j]
 zi = k(np.vstack([xi.flatten(), yi.flatten()]))
-plt.pcolormesh(xi, yi, zi.reshape(xi.shape), shading='gouraud', cmap=plt.cm.BuGn_r)
-plt.contour(xi, yi, zi.reshape(xi.shape) )
+plt.pcolormesh(xi, yi, zi.reshape(xi.shape), shading='gouraud', cmap=plt.cm.RdYlBu_r)
+plt.contour(xi, yi, zi.reshape(xi.shape),levels=10, colors='white', linewidths=1.0)
 
-
+plt.xlabel("$\mathbb{E}\log_{10}$")
 
 #plt.yscale("log")
 #plt.ylim([1e-20,1e-1])

### 2025-01-20 paper.tex
base draft of discussion

@@
 \begin{abstract}
-  \bjoern{TODO}{rewrite}This work quantifies uncertainties in a multiscale model for charge dynamics in organic semiconductors (OSCs).
+This study investigates the impact of exchange-correlation functional choices on the predictive accuracy of multiscale models for charge transport in organic semiconductors (OSCs).
+A hybrid functional approach is applied to analyze uncertainties in key parameters influencing charge mobility, focusing on the Hartree--Fock exchange fraction .
+Using 2-methyl-9,10-bis(naphthalen-2-yl)anthracene (MADN) as a test system, molecular dynamics and density functional theory are combined to compute reorganization energies, site energies, and electronic coupling elements.
+Monte Carlo sampling quantifies the uncertainty propagation, revealing that site energy variations dominate transport property uncertainties, while coupling elements contribute minimally.
+The findings underscore the need for accurate parameter determination and functional selection, with implications for enhancing the reliability of first-principles-based multiscale modeling frameworks in OSC design.
+  %\bjoern{TODO}{rewrite}This work quantifies uncertainties in a multiscale model for charge dynamics in organic semiconductors (OSCs).
 A first-principle multiscale model integrates classical molecular dynamics (MD), density functional theory (DFT), quantum mechanical calculation and continuous-time random walk (CTRW) processes to allow the simulation of charge transport in OSCs.
@@
 
-  By investigating the effects of varying Hartree-Fock (HF) levels within DFT functionals, we analyze the impact on electronic structures such as reorganization energy, molecule energy distribution, and coupling elements.
+%  By investigating the effects of varying Hartree-Fock (HF) levels within DFT functionals, we analyze the impact on electronic structures such as reorganization energy, molecule energy distribution, and coupling elements.
 The primary goal is to assess the robustness of predicting the quantity of interest (QoI), that is time-of-flight and charge mobility, under these uncertainties.
 
-  Monte Carlo simulations and sensitivity analysis are employed to estimate the range and confidence levels of the predicted charge mobility.
+%  Monte Carlo simulations and sensitivity analysis are employed to estimate the range and confidence levels of the predicted charge mobility.
 As shown by Sobol indices, the QoI is most sensitive to molecule energy, then reorganization energy and least sensitive to coupling elements.
@@
 \bjoern{STOP}{HERE}
+\section{Discussion}
+The findings presented in this study provide valuable insights into the sensitivity and uncertainty of multiscale models for charge transport in organic semiconductors (OSCs) due to the choice of exchange-correlation functionals in density functional theory (DFT).
+By systematically varying the Hartree--Fock exchange fraction  in hybrid functionals, the study uncovers critical dependencies and sources of uncertainty in the computational prediction of charge mobility.
+
+One key observation is the dominance of site energy uncertainties in influencing the variability of the time-of-flight (ToF) and mobility predictions.
+This reflects the substantial impact of electrostatic and polarization interactions, which are integral to site energy determination, on charge transport dynamics.
+In contrast, the uncertainties in reorganization energies and electronic coupling elements are shown to have a relatively minor effect.
+This suggests that further efforts to enhance the accuracy of site energy calculations—potentially through improved parameterization or advanced quantum mechanical methods—could significantly improve the reliability of multiscale modeling predictions.
+
+Interestingly, the results also demonstrate that the uncertainties in electronic coupling elements, particularly those with very small magnitudes, are less relevant for overall charge transport.
+This aligns with the percolation analysis, which indicates that coupling elements below a critical threshold contribute minimally to the connectivity of the charge transport network.
+Thus, simplifying approximations in handling these low-value couplings could be justified in specific scenarios to reduce computational complexity without compromising accuracy.
+
+Another notable finding is the robustness of field-dependent mobility predictions.
+Despite uncertainties in the underlying molecular parameters, the electric field dependence of mobility exhibits relatively consistent Poole--Frenkel behavior across the tested range of \ahfx values.
+This robustness suggests that multiscale models retain predictive value for field-dependent trends, even when parameter uncertainties are present.
+
+However, the study also highlights the challenge of achieving quantitative accuracy in charge mobility predictions, given that the uncertainty range spans an order of magnitude.
+This raises important considerations for interpreting simulation results in the context of experimental data.
+For instance, small differences in predicted mobility between two materials or designs may not be statistically significant given the intrinsic uncertainties.
+
+The use of Monte Carlo sampling and Sobol sensitivity analysis in this study provides a powerful framework for systematically quantifying the contributions of different sources of uncertainty to model predictions.
+The results clearly demonstrate that site energies are the dominant source of variability, with a Sobol index of 0.95.
+This indicates that future developments in multiscale modeling should prioritize reducing uncertainties in site energy calculations to enhance the reliability of predicted charge transport properties.
+
+Despite the progress made, there are limitations to this study that warrant further investigation.
+First, the analysis is restricted to variations in \ahfx as a proxy for different exchange-correlation functionals.
+While this approach captures a significant portion of the uncertainty, other factors such as basis set selection, dispersion corrections, and model approximations may also contribute to variability in the results.
+Expanding the uncertainty quantification framework to include these factors would provide a more comprehensive understanding of the robustness of multiscale models.
+
+Furthermore, the study focuses on a single material system, MADN, which exhibits moderate disorder.
+Extending the analysis to other OSCs with varying degrees of disorder, charge-carrier types, or different molecular morphologies would enhance the generality of the conclusions.
+
+\section{Conclusion and Future Directions}
+
+In conclusion, this study underscores the importance of uncertainty quantification in multiscale modeling of OSCs.
+The dominant role of site energy uncertainties highlights the need for accurate quantum mechanical methods and parameterization techniques in this area.
+Additionally, the robustness of field-dependent mobility trends suggests that multiscale models remain valuable tools for guiding material design, even in the presence of parameter uncertainties.
+
+Future research should aim to expand the scope of uncertainty quantification to include additional sources of variability, such as alternative functionals and morphological complexities.
+Integrating machine learning approaches to refine parameter estimates and leveraging high-throughput simulations could further enhance the predictive power of multiscale models in the design of next-generation OSCs.
+
+The results for the quantification of the uncertainty from functional choices in charge transport properties obtained from first-principles based multiscale modeling for the disordered system of MADN have revealed
+
 \begin{itemize}

### 2025-01-24 paper.tex
caption cleanup, discussion still TODO

@@
 This study investigates the impact of exchange-correlation functional choices on the predictive accuracy of multiscale models for charge transport in organic semiconductors (OSCs).
-A hybrid functional approach is applied to analyze uncertainties in key parameters influencing charge mobility, focusing on the Hartree--Fock exchange fraction .
+A hybrid functional approach is applied to analyze uncertainties in key parameters influencing charge mobility, focusing on the Hartree--Fock exchange fraction.
 Using 2-methyl-9,10-bis(naphthalen-2-yl)anthracene (MADN) as a test system, molecular dynamics and density functional theory are combined to compute reorganization energies, site energies, and electronic coupling elements.
@@
 The findings underscore the need for accurate parameter determination and functional selection, with implications for enhancing the reliability of first-principles-based multiscale modeling frameworks in OSC design.
-  %\bjoern{TODO}{rewrite}This work quantifies uncertainties in a multiscale model for charge dynamics in organic semiconductors (OSCs).
-A first-principle multiscale model integrates classical molecular dynamics (MD), density functional theory (DFT), quantum mechanical calculation and continuous-time random walk (CTRW) processes to allow the simulation of charge transport in OSCs.
-The model brings inherent uncertainties arising from the empirical approximations and numerical simulations.
-Our work particularly focusing on quantifying the uncertainty in DFT exchange-correlation functional.
-
-%  By investigating the effects of varying Hartree-Fock (HF) levels within DFT functionals, we analyze the impact on electronic structures such as reorganization energy, molecule energy distribution, and coupling elements.
-The primary goal is to assess the robustness of predicting the quantity of interest (QoI), that is time-of-flight and charge mobility, under these uncertainties.
-
-%  Monte Carlo simulations and sensitivity analysis are employed to estimate the range and confidence levels of the predicted charge mobility.
-As shown by Sobol indices, the QoI is most sensitive to molecule energy, then reorganization energy and least sensitive to coupling elements.
 \end{abstract}
@@
 This flexible functionality is achieved by tuning molecular properties to achieve an ideal operation at the device level~\cite{bronstein_role_2020, bredas_organic_2002}.
-Computational approaches that aim at predicting the charge transport properties of disordered molecular materials resolving the interplay between single-molecule properties (such as their electronic structure or response properties) and mesoscale material morphology can play an important role in supporting or even guiding experimental optimization processes~\cite{bronstein_role_2020, sokolov_computational_2011, grynova_read_2018}.\bjoern{add citations}{}
+Computational approaches that aim at predicting the charge transport properties of disordered molecular materials resolving the interplay between single-molecule properties (such as their electronic structure or response properties) and mesoscale material morphology can play an important role in supporting or even guiding experimental optimization processes~\cite{bronstein_role_2020, sokolov_computational_2011, grynova_read_2018}.
 
@@
   \includegraphics[width=\linewidth]{figs/MSM2.pdf}
-  \caption{\bjoern{TODO Bjoern}{Rewrite caption}The multiscale model workflow for OSC.
-Step 1: MD simulation to generate atom coordinates.
-Step 2: Molecule energy $E_i$ calculation.
-Step 3: Calculation of Reorganization energy $\lambda_{ij}$ and coupling element $J_{ij}$ for pairs of molecule $i,j$ whose COM distance is less than $r_\text{cutoff}$.
-Step 4: Modelling dynamics on device level, such as ToF calculation.}
+  \caption{Schematic representation of the multiscale framework for simulation of charge transport: (a) a representative large-scale morphology is obtained from Molecular Dynamics.
+(b) Information about the molecular building blocks and the morphology are used to determine the molecular transport graph $\mathbf{G}$ for a given choice of the \ahfx via calculation of reorganization energy, site energies, and electronic couplings.
+(c) The time-of-flight charge mobility is simulated based on the graph.}
   \label{fig:MSM}
@@
 Due to the infeasibility of explicitly simulating the coupled non-adiabatic electron-nuclear dynamics for the time- and length scales of realistic materials, these models typically exploit the localization of electronic states in disordered molecular materials and consider a rate-based description of hopping-type transport.
-A popular choice for the electron transfer rate $\omega_{ij}$ between two localization sites $i$ and $j$ is Marcus theory~\cite{marcus_theory_1956, marcus_electron_1993}  ~\bjoern{add}{citation}, in which
+A popular choice for the electron transfer rate $\omega_{ij}$ between two localization sites $i$ and $j$ is Marcus theory~\cite{marcus_theory_1956, marcus_electron_1993}, in which
 %
@@
 With all that information, charge transport is modeled as a continuous time random walk (CTRW) process on a graph $\mathbf{G}$, constructed from the localization sites and the calculated rates between them (Fig.~\ref{fig:MSM}(c)).
-Panel (b) of Fig.~\ref{fig:MSM} mentions some specific methods for the calculation of the quantities entering Eq.~\ref{equ:Marcus}, such as mixed quantum-classical methods for obtaining the site energies with the help of microelectrostatic methods~\cite{poelking_impact_2015, poelking_long-range_2016} \bjoern{add}{citations} or the dimer projection method for determining coupling elements~\cite{baumeier_density_2010}, as they are the ones adopted in this work.
+Panel (b) of Fig.~\ref{fig:MSM} mentions some specific methods for the calculation of the quantities entering Eq.~\ref{equ:Marcus}, such as mixed quantum-classical methods for obtaining the site energies with the help of microelectrostatic methods~\cite{poelking_impact_2015, poelking_long-range_2016} or the dimer projection method for determining coupling elements~\cite{baumeier_density_2010}, as they are the ones adopted in this work.
 What is essential about these and alternative ones is that they typically rely on density-functional theory (DFT) calculations, either directly or as a mean to parametrize classical models.
@@
 We consider the simulated time-of-flight (ToF) and the associated mobility the QoI in the following (see Fig.~\ref{fig:MSM}(c)) which then are subject to uncertainties in these $N_\text{UQ}$ parameters, {\em stemming} from the variation in $\alpha_\text{HFX}$.
-As a prototypical system, we will study hole transport in an amorphous morphology of 2-methyl-9, 10-bis(naphthalen-2-yl)anthracene (MADN), a wide-gap semiconductor that is used extensively as an ambipolar host material in organic light-emitting diodes~\cite{ko_accurate_2019, chang_great_2017} ~\bjoern{add}{citation}.
+As a prototypical system, we will study hole transport in an amorphous morphology of 2-methyl-9, 10-bis(naphthalen-2-yl)anthracene (MADN), a wide-gap semiconductor that is used extensively as an ambipolar host material in organic light-emitting diodes~\cite{ko_accurate_2019, chang_great_2017}.
 
@@
 In contrast, the reorganization energy as shown in Fig.~\ref{fig:autogen_MADN}(b) appears to saturate for \ahfx after an initially close to linear increase.
-In total, $\lambda$ is found to be in an interval between \unit[0.246]{eV} and \unit[0.316]{eV} \bjoern{need}{correct numbers here}.
+In total, $\lambda$ is found to be in an interval between \unit[0.25]{eV} and \unit[0.33]{eV}.
 Panels (c) and (d) of Fig.~\ref{fig:autogen_MADN} show the dipole moment of the neutral MADN molecule and the isotropic polarizability of the neutral and cationic (hole) states, respectively, both as electrostatic properties that enter indirectly the parameterization of the microelectrostatic model.
 As is visible, the dipole moment is rather independent on \ahfx (note that the jump of the last shown data point appears more pronounced because of the very small scale on the $y$-axis).
-The isotropic polarizabilities in panel (d) exhibit a linear decrease with increasing value of \ahfx which can be attributed to an increasingly attractive effective potential from stronger the Hartree--Fock-like exchange term and consequently more strongly bound electrons as one can also see from the increaseing ionization potential in panel (a).
+The isotropic polarizabilities in panel (d) exhibit a linear decrease with increasing value of \ahfx which can be attributed to an increasingly attractive effective potential from stronger the Hartree--Fock-like exchange term and consequently more strongly bound electrons as one can also see from the increasing ionization potential in panel (a).
 
@@
   \includegraphics[width=\linewidth]{figs/scatterE_qmmm.pdf}
-  \caption{\bjoern{TODO: }{rewrite caption}Scatter plot of site energy of MADN molecules calculated from different HFX, compared to the site energy calculated from HFX=0.25 (The PBE0 functional).
-The brighter color near the diagonal lines indicates denser population of the molecules.
-The top and right histogram show the energy distributions.}
+  \caption{Panels (a)-(e): Scatter plot of site energies of the MADN system for different values of \ahfx vs the PBE0 ($\ahfx=0.25$) reference.
+(f) Site energy disorder $\sigma$ in \unit[]{eV} for all values of \ahfx.}
   \label{fig:E_qmmm_MADN}
@@
 \begin{table}[tbp]
-  \caption{\bjoern{TODO: }{rewrite caption}In the tested $\alpha'$ values, the second column shows the maximum of $E_i(\alpha=0.25) - E_i(\alpha')$ for all molecules.
-Denoting $i'$ as the index of the molecule which has maximum $E_i(\alpha=0.25) - E_i(\alpha')$ for the chosen $\alpha'$, the third column shows the energy of molecule $i'$ calculated by $\alpha=0.25$.
-The fourth column shows the molecule energy $E_{i'}(\alpha')$ calculated by $\alpha'$.
-All the energies are in unit $\unit[]{eV}$.}
+  \caption{Characteristics of site energies $E$ (all in \unit[]{eV}) obtained for the different values of \ahfx : minimum ($E_\text{min}$) and maximum ($E_\text{max}$), the overall standard deviation and the contributions for static and polar calculations, as well as the largest absolute variation $D_{\ahfx}$ with respect to the PBE0 data ($\ahfx=0.25$).}
   \begin{ruledtabular}
@@
   \includegraphics[width=\linewidth]{figs/scatterJ_all.pdf}
-  \caption{\bjoern{TODO:}{rewrite caption} Scatter plot of MADN coupling element $\log_{10} J^2$ calculated from different HFX, compared to the polarization energy calculated from HFX=0.25 (The PBE0 functional).
-The brighter color near the diagonal lines indicates denser population of the molecules.
-The top and right histogram show the energy distributions.}
+  \caption{Scatter plot of electronic coupling elements of the MADN system for different values of \ahfx vs the PBE0 ($\ahfx=0.25$) reference.}
   \label{fig:J_MADN}
@@
   \includegraphics[width=\linewidth]{figs/fig_network_all.pdf}
-  \caption{\bjoern{TODO Zhong:}{same comments regarding the $\log_{10}$ as above; replace $\alpha$ with $\alpha_\text{HF}$.}The maximum size of the subgraphs obtained in the percolation algorithm as a function of critical value $J_c$.
-The molecular systems obtained by different HFX are colored according to the legend.}
+  \caption{The maximum size of the subgraphs obtained in the percolation algorithm as a function of critical value $J_c$.}
   \label{fig:J_percolate}
@@
 \begin{table}[tbp]
-\caption{\bjoern{TODO:}{rewrite}The ToF and diffusive velocity calculated by ToF along a distance $L_x = \unit[9.0]{nm}$ with and without energy disorder of the MADN system as a function of the HFX.
-The ToF is in unit $\unit[]{s}$ and $v_\text{ToF}$ in unit $\unit[]{m/s}$.}
+\caption{Simulated ToF (in \unit[]{s}) for different values of \ahfx in the full graph, with an additional cutoff on $J^2$, and for the case with no energetic disorder, respectively.}
 \begin{ruledtabular}
@@
 Note that due to the data range for the electronic coupling element as discussed in the previous section, we consider $\log_{10}(J^2)$ instead of $J^2$.
-For MADN, we have that $M=9765$.
-\bjoern{ADD:}{how many pairs?
-$N_\text{p}=8764$}
+For MADN, we have $N=1000$ and $N_\text{p}=8764$ so that $M=9765$.
 
@@
 Then, Monte-Carlo sampling is used to obtain $N_\text{MC}=50000$ different realizations of $\mathbf{x}$, the respective time-of-flight is calculated from these samples, and the resulting distribution $P(\log_{10}(\tau))$ is statistically analyzed.
-Specifically, we consider four different settings: in three settings, only one of the parameters blocks $(\lambda,\left\{E\right\},\left\{\log_{10}(J^2)\right\})$ is sampled while the values of the other blocks are set to their respective mean values and we denote the resulting distributions as $P_\lambda(\log_{10}(\tau))$, $P_E(\log_{10}(\tau))$, and $P_J(\log_{10}(\tau))$, respectively.
+Specifically, we consider four different settings: in three settings, only one of the parameters blocks $(\lambda,\left\{E\right\},\left\{\log_{10}(J^2)\right\})$ is sampled while the values of the other blocks are set to their respective mean values, and we denote the resulting distributions as $P_\lambda(\log_{10}(\tau))$, $P_E(\log_{10}(\tau))$, and $P_J(\log_{10}(\tau))$, respectively.
 In the fourth setting, all parameters are sampled at the same time, yielding $P_\mathbf{x}(\log_{10}(\tau))$.
@@
   \includegraphics[width=0.45\textwidth]{figs/fig_mle_MADN_withE.pdf}
-  \caption{\bjoern{TODO Zhong:}{swap panels a and b}Distribution of ToFs in the multiscale modeled MADN system.
-  Monte Carlo sampling with a sample size $N_\text{MC}=50000$ is used to obtain the sampled distribution.
+  \caption{Distribution of ToFs in the MADN system from  Monte Carlo sampling with a sample size $N_\text{MC}=50000$.
 The red vertical lines indicate the lower bound and upper bound of the 99\% confidence interval around the median.
-  The black circles indicate the ToF obtained using varying HFX values.
-  (a) $P(\log_{10}(\tau)|E_i \text{ uncertain})$, 
-  (b) $P(\log_{10}(\tau)|\lambda \text{ uncertain})$, 
-  (c) $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$, 
-  (d) $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$. }
+The black circles indicate the ToF obtained using explicit \ahfx values.
+Uncertainties considered are (a) in the eorganziation energy, (b) in the site energy, (c) in the coupling elements, and (d) in all simultaneously.}
   \label{fig:mle_MADN_withE}
@@
     \includegraphics[width=\linewidth]{figs/fig_mle_withE_mu2_ave.pdf}
-    \caption{\bjoern{TODO Zhong:}{all panels should have the same x-axis range for better comparison} Distribution of $\mu_\text{PF}$ in the multiscale modeled MADN system.
-    Monte Carlo sampling with a sample size $N_\text{MC}=10000$ is used to obtain the sampled distribution.
+    \caption{Distribution of the mobility $\mu$ for different values of the externally applied electric field $F$ as obtained from uncertainty quantification using 
+    Monte Carlo sampling with a sample size $N_\text{MC}=10000$.
 The red vertical lines indicate the lower bound and upper bound of the 99\% confidence interval around the median.
@@
     \includegraphics[width=0.45\textwidth]{figs/fig_PF_plot_ave.pdf}
-    \caption{\bjoern{TODO Zhong:}{remove PF label; avoid the large white space at the right; make data plot symbols a little bigger and lines a little thicker.}Electric-field dependence of the mobility $\mu$ in the multiscale modeled MADN system.
-The dash lines are Poole--Frenkel plots obtained with specific HFX value, and the green shadow indicates the 99\% confidence interval estimated from the MC sampling with a sample size of $N_\text{MC}=10000$.}
+    \caption{Electric-field dependence of the mobility $\mu$ in the multiscale modeled MADN system.
+The dash lines are Poole--Frenkel plots obtained with specific \ahfx values, and the green shaded area indicates the 99\% confidence interval estimated from the MC sampling with a sample size of $N_\text{MC}=10000$.}
     \label{fig:PF_plot_ave}
@@
   \caption{\label{tab:PF_parameter}%
-  Poole-Frenkel parameters $\mu_0$ (in $\unit[]{cm^2/(Vs)}$) and $\beta$ (in $\unit[]{\sqrt{cm/V}}$) of the multiscale modeled MADN, calculated by the six different HFX values. 
+  Poole-Frenkel parameters $\mu_0$ (in $\unit[]{cm^2/(Vs)}$) and $\beta$ (in $\unit[]{\sqrt{cm/V}}$) of the multiscale modeled MADN, calculated by the six different \ahfx values. 
   }
@@
   \includegraphics[width=0.80\textwidth]{figs/scatterEstat_qmmm.pdf}
-  \caption{\bjoern{TODO Zhong:}{add labels (a)...; replace $\alpha$ with $\alpha_\text{HF}$.}Scatter plot of MADN electrostatic energy calculated from different HFX, compared to the electrostatic energy calculated from HFX=0.25 (The PBE0 functional).
-The brighter color near the diagonal lines indicates denser population of the molecules.
-The top and right histogram show the energy distributions.}
+  \caption{Panels (a)-(e): Scatter plot of the electrostatic contribution to site energies of the MADN system for different values of \ahfx vs the PBE0 ($\ahfx=0.25$) reference.
+(f) Site energy disorder $\sigma$ in \unit[]{eV} for all values of \ahfx.}
   \label{fig:Estat_qmmm_MADN}
@@
   \includegraphics[width=0.80\textwidth]{figs/scatterEdip_qmmm.pdf}
-  \caption{\bjoern{TODO Zhong:}{add labels (a)...; replace $\alpha$ with $\alpha_\text{HF}$.}Scatter plot of MADN polarization energy calculated from different HFX, compared to the polarization energy calculated from HFX=0.25 (The PBE0 functional).
-The brighter color near the diagonal lines indicates denser population of the molecules.
-The top and right histogram show the energy distributions.}
+  \caption{Panels (a)-(e): Scatter plot of polarization contribution to site energies of the MADN system for different values of \ahfx vs the PBE0 ($\ahfx=0.25$) reference.
+(f) Site energy disorder $\sigma$ in \unit[]{eV} for all values of \ahfx.}
   \label{fig:Edip_qmmm_MADN}

### 2025-01-27 paper.tex
cleaned up conclusion

@@
 Overall, the squared electronic coupling elements are found in a very wide range from $\unit[10^{-2}]{}$ to $\unit[10^{-15}]{(eV)^2}$ due to its exponential distance dependence and sensitivity to mutual orientation of the two involved molecules.
-Whereas the site energy distributions discussed in the preceding section are well-defined in the sense that each energy is unambiguously associated to a physical entity -- a molecule in the morphology --, the coupling elements are evaluated for a neighborlist based on a chosen cutoff as explained in Section~\ref{sec:model}.\bjoern{TODO:}{add!} Clearly, if this cutoff is chosen to be large, a lot of hopping pairs with very small coupling elements will be considered that may not be relevant at all (or even unphysical) for charge transport.
+Whereas the site energy distributions discussed in the preceding section are well-defined in the sense that each energy is unambiguously associated to a physical entity -- a molecule in the morphology --, the coupling elements are evaluated for a neighborlist based on a chosen cutoff as explained in Section~\ref{sec:model}.
+Clearly, if this cutoff is chosen to be large, a lot of hopping pairs with very small coupling elements will be considered that may not be relevant at all (or even unphysical) for charge transport.
 Therefore, the increasing deviations for the most negative values in Figure~\ref{fig:J_MADN} may not be relavent either.
@@
 
-\bjoern{STOP}{HERE}
-\section{Discussion}
-The findings presented in this study provide valuable insights into the sensitivity and uncertainty of multiscale models for charge transport in organic semiconductors (OSCs) due to the choice of exchange-correlation functionals in density functional theory (DFT).
-By systematically varying the Hartree--Fock exchange fraction  in hybrid functionals, the study uncovers critical dependencies and sources of uncertainty in the computational prediction of charge mobility.
-
-One key observation is the dominance of site energy uncertainties in influencing the variability of the time-of-flight (ToF) and mobility predictions.
-This reflects the substantial impact of electrostatic and polarization interactions, which are integral to site energy determination, on charge transport dynamics.
+\section{Discussion \& Conclusion}
+One key observation of this study of Uncertainty Quantification in multiscale models for charge transport in organic semiconductors due to the choice of exchange-correlation functionals in density functional theory by systematically varying the Hartree--Fock exchange fraction in hybrid functionals is the dominance of site energy uncertainties in influencing the variability of the time-of-flight (ToF) and mobility predictions.
 In contrast, the uncertainties in reorganization energies and electronic coupling elements are shown to have a relatively minor effect.
-This suggests that further efforts to enhance the accuracy of site energy calculations—potentially through improved parameterization or advanced quantum mechanical methods—could significantly improve the reliability of multiscale modeling predictions.
-
+This suggests that further efforts to enhance the accuracy of site energy calculations -- potentially through improved parameterization or advanced quantum mechanical methods -- could significantly improve the reliability of multiscale modeling predictions.
 Interestingly, the results also demonstrate that the uncertainties in electronic coupling elements, particularly those with very small magnitudes, are less relevant for overall charge transport.
@@
 This robustness suggests that multiscale models retain predictive value for field-dependent trends, even when parameter uncertainties are present.
-
-However, the study also highlights the challenge of achieving quantitative accuracy in charge mobility predictions, given that the uncertainty range spans an order of magnitude.
+However, the results also highlight the challenge of achieving quantitative accuracy in charge mobility predictions, given that the uncertainty range spans an order of magnitude.
 This raises important considerations for interpreting simulation results in the context of experimental data.
 For instance, small differences in predicted mobility between two materials or designs may not be statistically significant given the intrinsic uncertainties.
-
-The use of Monte Carlo sampling and Sobol sensitivity analysis in this study provides a powerful framework for systematically quantifying the contributions of different sources of uncertainty to model predictions.
-The results clearly demonstrate that site energies are the dominant source of variability, with a Sobol index of 0.95.
-This indicates that future developments in multiscale modeling should prioritize reducing uncertainties in site energy calculations to enhance the reliability of predicted charge transport properties.
 
@@
 Extending the analysis to other OSCs with varying degrees of disorder, charge-carrier types, or different molecular morphologies would enhance the generality of the conclusions.
-
-\section{Conclusion and Future Directions}
-
-In conclusion, this study underscores the importance of uncertainty quantification in multiscale modeling of OSCs.
-The dominant role of site energy uncertainties highlights the need for accurate quantum mechanical methods and parameterization techniques in this area.
-Additionally, the robustness of field-dependent mobility trends suggests that multiscale models remain valuable tools for guiding material design, even in the presence of parameter uncertainties.
-
-Future research should aim to expand the scope of uncertainty quantification to include additional sources of variability, such as alternative functionals and morphological complexities.
-Integrating machine learning approaches to refine parameter estimates and leveraging high-throughput simulations could further enhance the predictive power of multiscale models in the design of next-generation OSCs.
-
-The results for the quantification of the uncertainty from functional choices in charge transport properties obtained from first-principles based multiscale modeling for the disordered system of MADN have revealed
-
-\begin{itemize}
-\item \ahfx, while only a proxy for the use of different functionals in MMM, gives a good indication the challenges in obtaining quantutative predictions of charge mobilities
-\item uncertainty for a low/moderate disorder material covering a range of one order of magnitude 
-\item field-dependence much less affected
-\item uncertainty mostly stems from site energy uncertainties, in a broader sense this highlights the importance for accurate methods to determine these energies not just as a distribution
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Conclusion}
-The uncertainty effect from the exchange-correlation functional of the DFT on the multiscale model of OSC is studied.
-By choosing different HFX, the calculated values of some electronic structures remain very similar,
-such as the reorganization energy $\lambda$, molecular energy $E_i$ and the majority of the coupling elements  $J_{ij}$.
-While a few small-value coupling elements $J_{ij}$ show large different in calculated values when different HFX is used.
-Those uncertainties propagate to the output of the multiscale model, resulting in a range of QoI which has a maximum about 15 times of its minimum.
-These findings high-
-light the importance of selecting appropriate functionals to ensure model robustness.
-Also indicated is that for multiscale model charge mobility, when the values have difference in approximately 10\%, we should interpret the results with caution and refrain from concluding that they represent fundamentally different phenomena.
-
-Assuming the maximum amount of uncertainty from the calculated electronic structure parameters using the six HFX, the 99\% confidence level of the ToFs around the median are estimated.
-The Sobol indexes show that the molecular energy has the most contribution to the total variance, followed by the reorganization energy and coupling elements.
-Our results also shows that due to the uncertainties, the steady state velocity distribution spans 4 orders of magnitude.
-So it is less robust when
-the electronic structure parameters are uncertain, and a useful range of velocity is hard to obtain.
-Future research should explore the impact of other sources of uncertainty and extend this framework to different types of semiconducting materials, thus enhancing the predictive power and applicability of multiscale models in the field.
 

### 2025-01-27 paper.tex
cleaned up

@@
 Section~\ref{sec:model} outlines the theoretical and computational details of the multiscale model, including the morphology simulation with classical molecular dynamics, the determination of all quantities in the transition rates, and the calculation of the charge transport properties from the constructed graph model.
-In Section~\ref{sec:MSMresults}, we discuss the explicit results from the model using different values of $\alpha_\text{HFX}$, before we show the results of uncertainty quantification and sensitivity analysis via Monte Carlo sampling.
+In Section~\ref{sec:MSMresults}, we discuss the explicit results from the model using different values of $\alpha_\text{HFX}$, before we show the results of uncertainty quantification and sensitivity analysis via Monte Carlo sampling in Section~\ref{sec:UQ}.
 A brief summary concludes the paper.

### 2025-02-03 paper.tex
some discussion added

@@
 \newcommand{\bjoern}[2]{{\color{blue}{{\bf #1} #2}}}
+\newcommand{\Zhong}[2]{{\color{purple}{{\bf #1} #2}}}
 \newcommand{\ahfx}{\ensuremath{\alpha_\text{HFX}}\xspace}
@@
 
+\Zhong{}{It is worth noting that in multiscale modeling there is usually correlations between the site energies $E_i$. 
+Those correlations are due to electrostatic interactions, while the distribution $P(\log_{10}(\tau))$ evaluated from the Monte Carlo sampling does not take the energy correlations into account.
+However, in the case of MADN, these correlations are notably absent.
+This can be attributed to the specific molecular arrangement and electronic structure of MADN, which effectively decouples the site energies from one another.
+As a result, the site energies in MADN are practically uncorrelated, simplifying the analysis of their contributions to the time-of-flight distribution.
+}
+
 %Figure .\ref{fig:mle_MADN_withE}(b) shows that $\log_{10}(\tau)$ has a confidence interval of -8.0 to -7.4 when $\lambda$ is varied. 
@@
 
+\Zhong{}{The decrease in the confidence intervals of $\log_{10}(\mu)$ indicates a reduction in the relative uncertainty in charge mobility, so a higher fields lead to a more deterministic mobility values.
+There some possible physical reasons for such reduction in uncertainty.
+At low electric fields, the charge carriers spend a significant amount of time in some low-energy sites which are generated in the Monte Carlo sampling.
+As the field strength increases, the drift term becomes more dominant, reducing the impact of these stochastic factors.
+
+Furthermore, a stronger electric field help the carrier to escape from the low energy sites more efficiently.
+This effect would reduce variability in observed mobilities, contributing to a narrowing confidence interval.
+So a stronger applied field, which is deterministic, results in a more predictable mobility response, therefore reducing the spread in $\log_{10}(\mu)$ distribution.
+}
+
 \begin{figure}[tbp]

### 2025-03-27 paper.tex
change two typo

@@
 %
-where $v_\text{ext}$ in an external potential (typically from the nuclei), $v_\text{H}[\rho]$ the electrostatic Hartree potential of a classical charge density $\rho(\mathbf{r})$, and $v_\text{XC}[\rho]$ the exchange-correlation potential containing explicit quantum-mechanical electron-electron interactions.
+where $v_\text{ext}$ is an external potential (typically from the nuclei), $v_\text{H}[\rho]$ the electrostatic Hartree potential of a classical charge density $\rho(\mathbf{r})$, and $v_\text{XC}[\rho]$ the exchange-correlation potential containing explicit quantum-mechanical electron-electron interactions.
 The charge density is determined from the single-particle wave functions as $\rho(\mathbf{r})=\sum\limits_{l=1}^{N_\text{el}} \left\vert\phi_l(\mathbf{r})\right\vert^2$.
@@
 Clearly, if this cutoff is chosen to be large, a lot of hopping pairs with very small coupling elements will be considered that may not be relevant at all (or even unphysical) for charge transport.
-Therefore, the increasing deviations for the most negative values in Figure~\ref{fig:J_MADN} may not be relavent either.
+Therefore, the increasing deviations for the most negative values in Figure~\ref{fig:J_MADN} may not be relevent either.
 
@@
 To determine the range of $\log_{10}[(J_{ij}/\unit[]{eV})^2]$ that are significant for the charge dynamics, a percolation analysis is performed to find a critical threshold value for the squared electronic coupling below which the largest connected subgraph is identical to the full graph.
-This is achieved by removing for a given value for $J_\text{c}$ from the full graph the edges with $J_{ij}^2 < J^2_\text{c}$ followed by the determination of the number of vertices in the larges connected subgraph $\max(N_\text{sub})$.
+This is achieved by removing for a given value for $J_\text{c}$ from the full graph the edges with $J_{ij}^2 < J^2_\text{c}$ followed by the determination of the number of vertices in the largest connected subgraph $\max(N_\text{sub})$.
 Figure~\ref{fig:J_percolate} shows the resulting dependence of $\max({N_\text{sub}})$ on the critical value $J_c$.
@@
 To scrutinize the dependence of such a material property, we now calculate the time-of-flight $\tau$ and report the respective values in Table~\ref{tab:ToF_MADN_HFX}.
-Here, we refer with ''full'' to time-of-flight obtained for the the as-calculated charge transport network.
+Here, we refer with ''full'' to time-of-flight obtained for the as-calculated charge transport network.
 One can see that $\tau$ varies by roughly one order of magnitude between $\ahfx=0$ ($\unit[6.3\cdot 10^{-9}]{s}$) and $\ahfx=0.25$ ($\unit[9.5\cdot 10^{-8}]{s}$), with an almost monotonous increase.
@@
 \Zhong{}{The decrease in the confidence intervals of $\log_{10}(\mu)$ indicates a reduction in the relative uncertainty in charge mobility, so a higher fields lead to a more deterministic mobility values.
-There some possible physical reasons for such reduction in uncertainty.
+There are some possible physical reasons for such reduction in uncertainty.
 At low electric fields, the charge carriers spend a significant amount of time in some low-energy sites which are generated in the Monte Carlo sampling.
@@
 
-Furthermore, a stronger electric field help the carrier to escape from the low energy sites more efficiently.
+Furthermore, a stronger electric field helps the carrier to escape from the low energy sites more efficiently.
 This effect would reduce variability in observed mobilities, contributing to a narrowing confidence interval.

### 2025-03-28 paper.tex
cleanup

--- 2025-01-27 paper.tex
@@
 \end{abstract}
-
-%\keywords{Suggested keywords}
 
@@
     \begin{tabular}{c c c c c c c}
-    $\ahfx$ & $E_\text{min}$ & $E_\text{max}$ & $\sigma$ & $\sigma_\text{el}$ & $\sigma_\text{polar}$ &  $D_{\ahfx}$ \\%  & $E_{i_\text{max}}$ \\
+    $\ahfx$ & $E_\text{min}$ & $E_\text{max}$ & $\sigma$ & $\sigma_\text{el}$ & $\sigma_\text{polar}$ &  $D_{\ahfx}$ \\
     \hline
-    0    & -1.11 & -0.59 & 0.08 & 0.10 & 0.04 & 0.13 \\ %&  -0.94 \\
-    0.05 & -1.07 & -0.63 & 0.07 & 0.09 & 0.04 & 0.12 \\ %&  -0.94 \\
-    0.10 & -1.13 & -0.61 & 0.08 & 0.10 & 0.04 & 0.13 \\ %&  -0.94 \\
-    0.15 & -1.16 & -0.59 & 0.09 & 0.11 & 0.05 & 0.15 \\ %&  -0.69 \\
-    0.20 & -1.12 & -0.63 & 0.08 & 0.10 & 0.05 & 0.12 \\ %&  -0.82 \\
-    0.25 & -1.17 & -0.60 & 0.08 & 0.11 & 0.04 & ---  \\ %&   ---\\
+    0    & -1.11 & -0.59 & 0.08 & 0.10 & 0.04 & 0.13 \\ 
+    0.05 & -1.07 & -0.63 & 0.07 & 0.09 & 0.04 & 0.12 \\ 
+    0.10 & -1.13 & -0.61 & 0.08 & 0.10 & 0.04 & 0.13 \\ 
+    0.15 & -1.16 & -0.59 & 0.09 & 0.11 & 0.05 & 0.15 \\ 
+    0.20 & -1.12 & -0.63 & 0.08 & 0.10 & 0.05 & 0.12 \\ 
+    0.25 & -1.17 & -0.60 & 0.08 & 0.11 & 0.04 & ---  \\ 
     \end{tabular}
@@
   \begin{tabular}{c c c c }
-        \ahfx & full & $J_{ij} \mathbb{1}(\log_{10} J^2_{ij} > -5)$ & $\Delta E_{ij} =0$ \\% & $v_\text{ToF}$(no $E$) \\
+        \ahfx & full & $J_{ij} \mathbb{1}(\log_{10} J^2_{ij} > -5)$ & $\Delta E_{ij} =0$ \\
     \hline
-        0.00 &  $6.4 \cdot 10^{-9}$ & $7.5 \cdot 10^{-9}$ & $1.9 \cdot 10^{-10}$ \\%& 42 \\
-        0.05 & $ 7.9 \cdot 10^{-9}$ & $8.1 \cdot 10^{-9}$ & $4.1 \cdot 10^{-10}$ \\%& 20 \\
-        0.10 & $ 1.6 \cdot 10^{-8}$ & $1.6 \cdot 10^{-8}$ & $4.0 \cdot 10^{-10} $ \\%& 20 \\
-        0.15 & $ 3.0 \cdot 10^{-8}$ & $3.1 \cdot 10^{-8}$ & $4.0 \cdot 10^{-10} $ \\%& 25 \\
-        0.20 & $ 2.1 \cdot 10^{-8}$ & $2.5 \cdot 10^{-8}$ & $4.5 \cdot 10^{-10}$ \\%& 18 \\
-        0.25 & $ 9.5 \cdot 10^{-8}$ & $9.7 \cdot 10^{-8}$ & $7.2 \cdot 10^{-10}$ \\%& 11 \\
+        0.00 &  $6.4 \cdot 10^{-9}$ & $7.5 \cdot 10^{-9}$ & $1.9 \cdot 10^{-10}$ \\
+        0.05 & $ 7.9 \cdot 10^{-9}$ & $8.1 \cdot 10^{-9}$ & $4.1 \cdot 10^{-10}$ \\
+        0.10 & $ 1.6 \cdot 10^{-8}$ & $1.6 \cdot 10^{-8}$ & $4.0 \cdot 10^{-10} $ \\
+        0.15 & $ 3.0 \cdot 10^{-8}$ & $3.1 \cdot 10^{-8}$ & $4.0 \cdot 10^{-10} $ \\
+        0.20 & $ 2.1 \cdot 10^{-8}$ & $2.5 \cdot 10^{-8}$ & $4.5 \cdot 10^{-10}$ \\
+        0.25 & $ 9.5 \cdot 10^{-8}$ & $9.7 \cdot 10^{-8}$ & $7.2 \cdot 10^{-10}$ \\
     \end{tabular}
@@
 Here, one also can see (next to the generally shorter time-of-flight) a consistent increase in $\tau$, however only by a factor of about \unit[3.8]{}, a combined effect of the increased reorganization energy and variations in coupling elements.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 As these distributions do not necessarily follow any specific analytic form, we estimate a $99\%$ confidence interval around the median using the equal-tailed percentile method.
-\bjoern{Maybe discuss somewhere:}{correlations between parameters are gone, especially in site energies, but they are (practically) uncorrelated in MADN.}
-
-%Then Monte Carlo scheme is used to estimate the distribution of the ToF. The Monte Carlo scheme has the procedure:
-%\begin{enumerate}
-%\item For all $i,j=1,2,\cdots, N_d$, obtain a realization $(x_1, x_2, \cdots, x_{N_d})$ where each parameter has the normal distribution, meaning the corresponding electronic parameters are sampled from the distribution $\lambda_i \in \mathcal{N}(\mathbb{E}(\lambda), \mathbb{V}(\lambda))$, $E_i \in \mathcal{N}(\mathbb{E}(E_i), \mathbb{V}(E_i))$, $\log_{10}(J_{ij}^2) \in \mathcal{N}(\mathbb{E}(\log_{10}(J_{ij}^2)), \mathbb{V}(\log_{10}(J_{ij}^2)))$.
-%\item Calculate ToF using the sampled data set $(x_1, x_2, \cdots, x_{Nd})$. 
-%\item Repeat step 1 and 2 for $N_\text{MC} = 50000$ times to obtain ToFs. Plot the distribution of the ToFs.
-%\item Estimate the 99\% confidence interval around the median.
-%\end{enumerate}
-
-%To understand how the uncertainty pass from $E, \lambda, J_{ij}$ to ToF, the parameter control is used.
-That is, a set of parameter, such as $E_i$ for all $i=1,2,\cdots,N$ is choose while keeping other parameter fixed, then performed Monte Carlo sampling to obtain ToF distribution and estimate upper and lower confidence bound.
-%Then we use Sobol total indices to analyze and quantify 
-%which uncertainty among $E, \lambda, J_{ij}$ has a greater impact on the ToF,
 
@@
 
-%The distribution that we want to obtained during the parameter control are as followed:
-%\begin{enumerate}
-%    \item Fixed the $\lambda$ to be $\mathbb{E}(\lambda)$, and $\log_{10}(J_{ij}^2)$ to be $\mathbb{E}(\log_{10}(J_{ij}^2))$.
-Then each molecule energy $E_i$ is sampled from the normal distribution $\mathcal{N}(\mathbb{E}(E_i), \mathbb{V}(E_i))$.
-Finally obtain and plot the histogram $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|E_i \text{ uncertain})$.
-%    \item Fixed all $E_i$ to be $\mathbb{E}(E_i)$ and all $\log_{10}(J_{ij}^2)$ to be $\mathbb{E}(\log_{10}(J_{ij}^2))$.
-Then $\lambda$ is sampled from the normal distribution $\mathcal{N}(\mathbb{E}(\lambda), \mathbb{V}(\lambda))$.
-Finally obtain and plot the histogram  $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|\lambda \text{ uncertain})$.
-%    \item Fixed the $\lambda$ to be $\mathbb{E}(\lambda)$ and all $E_i$ to be $\mathbb{E}(E_i)$.
-Then $J_{ij}$ is sampled from the normal distribution $\log_{10}(J_{ij}^2) \in \mathcal{N}(\mathbb{E}(\log_{10}(J_{ij}^2)), \mathbb{V}(\log_{10}(J_{ij}^2)))$.
-Finally obtain and plot the histogram  $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$.
-%    \item Both $E_i$, $\lambda$ and $J_{ij}$ are sampled from their normal distribution:
-
-%    $\lambda_i \in \mathcal{N}(\mathbb{E}(\lambda), \mathbb{V}(\lambda))$,
-
-%    $E_i \in \mathcal{N}(\mathbb{E}(E), \mathbb{V}(E))$,
-
-%    $\log_{10}J_{ij}^2 \in \mathcal{N}(\mathbb{E}(\log_{10}J_{ij}^2), \mathbb{V}(\log_{10}J_{ij}^2))$.
-%    Then obtain and plot the histogram $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as the following distribution: 
-%    $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$.
-%\end{enumerate}
-
-%The analytical forms of the distribution $P_\lambda(\log_{10}(\tau))$, $P_E(\log_{10}(\tau))$, $P_J(\log_{10}(\tau))$ and $P_\mathbf{x}(\log_{10}(\tau))$ are usually unknown. 
-%To quantify the uncertainty and variability in the sample data, we calculate a $99\%$ confidence interval around the median. 
-%This statistical quantity is typically nonparametric, and relies on percentiles of the data, making it robust to different types of probability mass function.
-
-%Using the equal-tailed percentile method, its calculation involves sorting the data and determining percentiles that correspond to the desired confidence level.
-%Given a dataset $\{ \tau_1, \tau_2, \dots, \tau_n \}$, the procedure can be described as follows:
-%\begin{enumerate}
-%  \item Sort the data in ascending order. For a confidence level $CL$, the corresponding complement 
-%  $1-CL$ determines the tails of the interval. 
-%  \item Find the lower bound $\tau_{\eta}$ corresponds to the $\eta$-th percentile of the dataset where $\eta = (1-CL)/2$. For a $99\%$ confidence interval, $\eta=0.05$.
-%  \item Find the upper bound $\tau_{(1-\eta)}$ corresponds to the $(1-\eta)$-th percentile of the dataset.
-%  \item The confidence interval around the median is $[\tau_{\eta}, \tau_{(1-\eta)}]$.
-%\end{enumerate}
-
 The four respective distributions of $\tau$ in the MADN system are shown in Fig.~\ref{fig:mle_MADN_withE} together with the indicated confidence intervals obtained from Monte-Carlo sampling.
@@
 
-%Figure .\ref{fig:mle_MADN_withE}(b) shows that $\log_{10}(\tau)$ has a confidence interval of -8.0 to -7.4 when $\lambda$ is varied. 
-%Figure \ref{fig:mle_MADN_withE}(c) show that when $J_{ij}$ is uncertain $\log_{10}(\tau)$ has a narrow confidence interval of -7.9 to -7.7, suggesting that the variation in $J_{ij}$ leads to relatively small change in $\log_{10}(\tau)$ compared to $E_i$ and $\lambda$.
+We note that the above analysis from sampling via independent distributions of the uncertain parameters assumes that the parameters themselves are independent or uncorrelated.
+Correlations in organic semiconductors are typically found among the site energies when the molecules are polar~\cite{Baumeier2011,10.1063/5.0049513}.
+MADN has a very low dipole moment, and we find practically no spatial correlations between the site energies, making the sampling approach suitable for this material system.
 
-%
-%\begin{figure}[t]
-%  \centering
-%  \includegraphics[width=0.45\textwidth]{figs/fig_mle_MADN_noE.pdf}
-%  \caption{\bjoern{TODO Zhong:}{these should also strictly be $\log_{10}(\tau/\unit[]{s})$.}Distribution of ToFs in the multiscale modeled MADN system.
-%  Monte Carlo sampling with a sample size $N_\text{MC}=50000$ is used to obtain the sampled distribution.
-The red vertical lines indicate the lower bound and upper bound of the 99\% confidence interval around the median.
-%  Energy disorder is not consider. 
-%  The black circles indicate the ToF obtained using varying HFX values.
-%  (a) $P(\log_{10}(\tau)|\lambda \text{ uncertain})$, 
-%  (b) $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$, 
-%  (c) $P(\log_{10}(\tau)|\lambda, J_{ij} \text{ uncertain})$. }
-%  \label{fig:mle_MADN_noE}
-%\end{figure}
-%
-
-%When the energy disorder in MADN system is not considered, that is, all the MADN molecule energy are set to be equal giving $\Delta E=0$, the distribution of ToF is shown in Fig.\ref{fig:mle_MADN_noE}.
-%The distribution $P(\log_{10}(\tau)|\lambda \text{ uncertain})$ has a range of confidence interval -9.6 to -9.0 resembles that of $P(\log_{10}(\tau)|\lambda, J_{ij} \text{ uncertain})$, which has a range of confidence interval -9.7 to -9.1.
-
-%\subsection{Sobol indices}
 Besides the inspection on the distributions for various uncertain parameter (sets) as above, one can also quantify the sensitivity of the time-of-fight to the respective parameters by evaluating their contributions to the overall observed variance in $\tau$.
@@
 
-%\begin{table}[tbp]%The best place to locate the table environment is directly after its first reference in text
-%\caption{\label{tab:Sobol}%
-%Sobol indices of $\lambda$, $E$ and $\log_{10} J^2$ when ToF is calculated with energy disorder, and Sobol indices of $\lambda$ and $\log_{10} J^2$ when ToF is calculated without energy disorder.
-%}
-%\begin{ruledtabular}
-%  \begin{center}
-%    \begin{tabular}{c c c c c c c} %\hline
-%      &  \multicolumn{3}{c}{\bf Energy Disorder} & &\multicolumn{2}{c}{\bf no Disorder}\\\cline{2-4}  \cline{6-7}
-%      parameter  & $\lambda$ & $ E_i$ & $ \log_{10}(J_{ij}^2)$ && $\lambda$ & $ \log_{10}(J_{ij}^2)$ \\ \hline
-      %\multicolumn{6}{c}{\bf GRW for $\mathbf{N_c=1}$}\\
-%   $S_T$  & 0.097 & 0.95 & 0.018 && 0.96 & 0.11 \\
-%    \end{tabular}
-%  \end{center}
-%\end{ruledtabular}
-%\end{table}
-%
-
-%From table \ref{tab:Sobol} one can see that most of the total variance can be attributed to the energy $E$.
-In contrast to $E$, the uncertainty in $\lambda$ and $\log_{10} J^2$ contributes much less compared to $E$, this is consistent to the Fig.\ref{fig:mle_MADN_withE}, where the distribution in Fig.\ref{fig:mle_MADN_withE}(d) resembles the distribution in Fig.\ref{fig:mle_MADN_withE}(a).
-%And Fig.\ref{fig:mle_MADN_withE}(c) shows that the uncertainty in $\log_{10}(J^2)$ only leads to small variances.
-%When there is no energy disorder, the variance in $\lambda$ has the most contribution to the total variance as shown in Table \ref{tab:Sobol}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%\begin{figure}
-%  \centering
-%  \includegraphics[width=0.45\textwidth]{figs/fig_mle_MADN_withE_SS.pdf}
-%  \caption{Distribution of steady state velocity $v_\text{SS}$ in the multiscale modeled MADN.
-%  Monte Carlo sampling with a sample size $N_\text{MC}=50000$ is used to obtain the sampled distribution.
-%  The red vertical lines indicate the lower bound and upper bound of the 99\% confidence interval around the median.
-%  The black circles indicate the $v_\text{SS}$ obtained using varying HFX values.
-%  (a) $P(\log_{10}(v_\text{SS})|E_i \text{ uncertain})$, 
-%  (b) $P(\log_{10}(v_\text{SS})|\lambda \text{ uncertain})$, 
-%  (c) $P(\log_{10}(v_\text{SS})|J_{ij} \text{ uncertain})$, 
-%  (d) $P(\log_{10}(v_\text{SS})|E_i, \lambda, J_{ij} \text{ uncertain})$. }
-%  \label{fig:mle_MADN_withE_SS}
-%\end{figure}
-%
-%
-%\begin{figure}
-%  \centering
-%  \includegraphics[width=0.45\textwidth]{figs/fig_mle_MADN_noE_SS.pdf}
-%  \caption{Distribution of steady state velocity $v_\text{SS}$ in the multiscale modeled MADN. All molecule energies are set to be zero.  
-%  Monte Carlo sampling with a sample size $N_\text{MC}=50000$ is used to obtain the sampled distribution.
-%  The red vertical lines indicate the lower bound and upper bound of the 99\% confidence interval around the median.
-%  The black circles indicate the $v_\text{SS}$ obtained using varying HFX values.
-%  (a) $P(\log_{10}(v_\text{SS})|\lambda \text{ uncertain})$, 
-%  (b) $P(\log_{10}(v_\text{SS})|J_{ij} \text{ uncertain})$, 
-%  (c) $P(\log_{10}(v_\text{SS})|\lambda, J_{ij} \text{ uncertain})$.  }
-%  \label{fig:mle_MADN_noE_SS}
-%\end{figure}
-
-%\section{Distribution of Steady State Velocity}
-
-%The distribution of steady state velocity of MADN is shown as Fig.\ref{fig:mle_MADN_withE_SS} and \ref{fig:mle_MADN_noE_SS}. 
-%From the confidence interval, $P(\log_{10}(v_\text{SS})|E_i \text{ uncertain})$ has a range of -2.6 to -0.9, and the confidence interval $P(\log_{10}(v_\text{SS})|\lambda \text{ uncertain})$ has a range from -1.7 to -1.1.
-The width of those confidence intervals is very close to the confidence interval of distributions $P(\log_{10}(\tau)|E_i \text{ uncertain})$ and $P(\log_{10}(\tau)|\lambda \text{ uncertain})$, respectively.
-%However, $P(\log_{10}(v_\text{SS})|J_{ij} \text{ uncertain})$ has a range from -1.6 to 1.3, spanning 3 orders of magnitude.
-This is  much larger than $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$ as shown in Fig .\ref{fig:mle_MADN_withE}.
-%The large confidence interval in $P(\log_{10}(v_\text{SS})|J_{ij} \text{ uncertain})$ shows that $v_{ss}$ is very sensitive to the change in $J_{ij}$.
-Combining all the uncertainty effects in $E_i, \lambda, J_{ij}$, the confidence interval of $P(\log_{10}(v_\text{SS})|E_i, \lambda, J_{ij} \text{ uncertain})$ is from -2.5 to 1.3, covering 4 orders of magnitude.
-
-%When energy disorder is not considered, the $v_\text{SS}$ distribution $P(\log_{10}(v_\text{SS})|\lambda, J_{ij} \text{ uncertain})$ has a confidence interval from 0.3 to 3.5, spanning 3 orders of magnitude.
-This interval is close to the range of $P(\log_{10}(v_\text{SS})|J_{ij} \text{ uncertain})$ when only $J_{ij}$ is uncertain.
-%In contrast, the interval of $P(\log_{10}(v_\text{SS})|\lambda \text{ uncertain})$ is from 0.6 to 1.2, whose width is much smaller than that of $P(\log_{10}(v_\text{SS})|J_{ij} \text{ uncertain})$.
-
-%These result suggests that compared to the ToF $\tau$, the quantity $v_\text{SS}$ is significantly affected by uncertainties in $J_{ij}$, so $v_\text{SS}$ is less robust when the parameters $E_i, \lambda, J_{ij}$ contains uncertainty at the same time.
-%In the next section, the Poole–Frenkel behavior, that is the dependence of charge mobility on the electric field will be study using the ToF setting. 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \subsection{Drift-diffusion Charge mobility}
@@
 Here, we perform calculations for six different field directions (positive and negative Cartesian directions) with the source and sink conditions set accordingly.
-The electric field is taken account in the Marcus rate in Eq.~\ref{equ:Marcus} via an additional term in $\Delta E_{ij}$ given by $e\mathbf{F} \cdot \mathbf{r}_{ij}$, where $\mathbf{r}_{ij}$ connects the center-of-masses (COMs) of molecules $i$ and $j$.
+The electric field is taken account in the Marcus rate in Eq.~\ref{equ:Marcus} via an additional term in $\Delta E_{ij}$ given by $e\mathbf{F} \cdot \mathbf{r}_{ij}$, where $\mathbf{r}_{ij}$ connects the center-of-masses of molecules $i$ and $j$.
 Finally, we define for a certain field strength $F=\vert\mathbf{F}\vert$ the ToF drift mobility $\mu(F)$ is as the average over the six directions.
@@
 The width of the confidence intervals in $\log_{10}(\mu)$ decreases from \unit[0.9]{} at low fields ($\unit[4 \cdot 10^7]{V/m}$) to \unit[0.7]{} at a field of $\unit[9 \cdot 10^7]{V/m}$, corresponding broadly to a width of close to one order of magnitude in $\mu$.
-A stronger drift component due to a larger external electric field seems to make the mobility slightly less sensitive to uncertainties \bjoern{CHECK}{not sure about this interpretation}.
+A stronger drift component due to a larger external electric field seems to make the mobility slightly less sensitive to uncertainties.
 
@@
 
-\begin{table}[tbp]%The best place to locate the table environment is directly after its first reference in text
+\begin{table}[tbp]
   \caption{\label{tab:PF_parameter}%
@@
 \section{Discussion \& Conclusion}
-One key observation of this study of Uncertainty Quantification in multiscale models for charge transport in organic semiconductors due to the choice of exchange-correlation functionals in density functional theory by systematically varying the Hartree--Fock exchange fraction in hybrid functionals is the dominance of site energy uncertainties in influencing the variability of the time-of-flight (ToF) and mobility predictions.
+One key observation of this study of Uncertainty Quantification in multiscale models for charge transport in organic semiconductors due to the choice of exchange-correlation functionals in density functional theory by systematically varying the Hartree--Fock exchange fraction in hybrid functionals is the dominance of site energy uncertainties in influencing the variability of the time-of-flightand mobility predictions.
 In contrast, the uncertainties in reorganization energies and electronic coupling elements are shown to have a relatively minor effect.

### 2025-05-15 submit/paper.tex
started on a revision

--- 2025-03-28 paper.tex
@@
   \centering
-  \includegraphics[width=\linewidth]{figs/MSM2.pdf}
+  \includegraphics[width=\linewidth]{fig1.pdf}
   \caption{Schematic representation of the multiscale framework for simulation of charge transport: (a) a representative large-scale morphology is obtained from Molecular Dynamics.
@@
     \centering
-    \includegraphics[width=\linewidth]{figs/fig_autogen.pdf}
+    \includegraphics[width=\linewidth]{fig2.pdf}
     \caption{Dependence of molecular parameters as used directly in the multiscale model or in its paramaterization phase on the amount of Hartree--Fock type exchange in the PBE0-based hybrid functional $\alpha_\text{HFX}$.
@@
   \centering
-  \includegraphics[width=\linewidth]{figs/scatterE_qmmm.pdf}
+  \includegraphics[width=\linewidth]{fig3.pdf}
   \caption{Panels (a)-(e): Scatter plot of site energies of the MADN system for different values of \ahfx vs the PBE0 ($\ahfx=0.25$) reference.
@@
   \centering
-  \includegraphics[width=\linewidth]{figs/scatterJ_all.pdf}
+  \includegraphics[width=\linewidth]{fig4.pdf}
   \caption{Scatter plot of electronic coupling elements of the MADN system for different values of \ahfx vs the PBE0 ($\ahfx=0.25$) reference.}
@@
   \centering
-  \includegraphics[width=\linewidth]{figs/fig_network_all.pdf}
+  \includegraphics[width=\linewidth]{fig5.pdf}
   \caption{The maximum size of the subgraphs obtained in the percolation algorithm as a function of critical value $J_c$.}
@@
   \centering
-  \includegraphics[width=0.45\textwidth]{figs/fig_mle_MADN_withE.pdf}
+  \includegraphics[width=0.45\textwidth]{fig6.pdf}
   \caption{Distribution of ToFs in the MADN system from  Monte Carlo sampling with a sample size $N_\text{MC}=50000$.
@@
     \centering
-    \includegraphics[width=\linewidth]{figs/fig_mle_withE_mu2_ave.pdf}
+    \includegraphics[width=\linewidth]{fig7.pdf}
     \caption{Distribution of the mobility $\mu$ for different values of the externally applied electric field $F$ as obtained from uncertainty quantification using 
@@
     \centering
-    \includegraphics[width=0.45\textwidth]{figs/fig_PF_plot_ave.pdf}
+    \includegraphics[width=0.45\textwidth]{fig8.pdf}
     \caption{Electric-field dependence of the mobility $\mu$ in the multiscale modeled MADN system.
@@
 \section{Discussion \& Conclusion}
-One key observation of this study of Uncertainty Quantification in multiscale models for charge transport in organic semiconductors due to the choice of exchange-correlation functionals in density functional theory by systematically varying the Hartree--Fock exchange fraction in hybrid functionals is the dominance of site energy uncertainties in influencing the variability of the time-of-flightand mobility predictions.
+One key observation of this study of Uncertainty Quantification in multiscale models for charge transport in organic semiconductors due to the choice of exchange-correlation functionals in density functional theory by systematically varying the Hartree--Fock exchange fraction in hybrid functionals is the dominance of site energy uncertainties in influencing the variability of the time-of-flight and mobility predictions.
 In contrast, the uncertainties in reorganization energies and electronic coupling elements are shown to have a relatively minor effect.
@@
 
-\bibliography{references}
+\bibliography{../references.bib}
 
@@
   \centering
-  \includegraphics[width=0.80\textwidth]{figs/scatterEstat_qmmm.pdf}
+  \includegraphics[width=0.80\textwidth]{fig9.pdf}
   \caption{Panels (a)-(e): Scatter plot of the electrostatic contribution to site energies of the MADN system for different values of \ahfx vs the PBE0 ($\ahfx=0.25$) reference.
@@
   \centering
-  \includegraphics[width=0.80\textwidth]{figs/scatterEdip_qmmm.pdf}
+  \includegraphics[width=0.80\textwidth]{fig10.pdf}
   \caption{Panels (a)-(e): Scatter plot of polarization contribution to site energies of the MADN system for different values of \ahfx vs the PBE0 ($\ahfx=0.25$) reference.

### 2025-05-20 submit/paper.tex
revision and reply draft

@@
 \newcommand{\ahfx}{\ensuremath{\alpha_\text{HFX}}\xspace}
+\newcommand{\change}[1]{{\color{blue}{#1}}}
 
@@
 
-\title{Uncertainty Quantification in Multiscale Models of Charge Transport in Organic Semiconductors: Influence of the Exhange-Correlation Functional}
+\title{Uncertainty Quantification in Multiscale Models of Charge Transport in Organic Semiconductors: Influence of the Exchange-Correlation Functional}
 
@@
 %
-More specifically, we take as the basis the PBE0 functional~\cite{adamo_toward_1999} and scrutinize (i) how the predictions of the multiscale model of charge transport are affected by variation of $\alpha_\text{HFX}$ as a proxy for uncertainties in the choice of DFT functionals, (ii) what the level of confidence is in quantitative predictions, and (iii) what are the most sensitive quantities in the model.
+\change{This choice is motivated by the observation that the simulated charge-carrier time-of-flight (ToF) for a set of commonly used functionals --- PBE~\cite{PhysRevLett.77.3865}, B3LYP~\cite{10.1063/1.464913}, PBE0~\cite{adamo_toward_1999}, BHLYP~\cite{10.1063/1.464913,lee_development_1988}, M06L~\cite{10.1063/1.2370993}, TPSS~\cite{PhysRevLett.91.146401} --- (see Tab.~\ref{tab:actual_functionals} in the Appendix) is more sensitive to the amount of included Hartree--Fock exchange than to variations in the generalized-gradient approximation (GGA) parametrization.
+While these functionals vary in more details, the data shows that for functionals with varying \ahfx, the simulated ToF spans two orders of magnitude, whereas among non-hybrid (meta-)GGA functionals the ToF results on the same order of magnitude.} More specifically, we take as the basis the PBE0 functional and scrutinize (i) how the predictions of the multiscale model of charge transport are affected by variation of $\alpha_\text{HFX}$ as a proxy for uncertainties in the choice of DFT functionals, (ii) what the level of confidence is in quantitative predictions, and (iii) what are the most sensitive quantities in the model.
 In this sense, Eq.~\ref{equ:hybrid} is deceptively simple.
@@
 Two nodes $i,j$ are connected if the corresponding molecules have their closest-contact distance smaller than $r_\text{cutoff}=\unit[0.5]{nm}$.
+\change{To determine the quantities that define the Marcus rates from the material morphology, we follow the workflow of \cite{Baumeier2011} and employ DFT calculations (for reorganization energies and coupling elements) with classical microelectrostatic models (for site energies).
+In this, first special care is taken to avoid discrepancies between the molecular structures obtained via classical MD and the DFT calculations.
+Following the practice of~\cite{Baumeier2011}, bond length fluctuations introduced by molecular dynamics simulations are removed as they are already integrated out in the derivation of the rate expression, by replacing molecular fragments (rigid, planar $\pi$ systems) in place with their DFT-optimized versions.
+Below we give concise summaries of the individual methods and refer the reader to \cite{Baumeier2011,doi:10.1021/acs.jctc.8b00617,10.1063/1.5144277,Baumeier2024} for more detailed discussions.}
 
@@
 For our uncertain quantification study, $\alpha=0,0.05,0.10,0.15,0.20,0.25$ are chosen for the multiscale model.
+\change{DFT calculations are performed in vacuum for the parametrization of microelectrostatic models and the calculations of reorganization energies and coupling elements below.}
 
-\subsection{Reorganiztion Energy}
+\subsection{Reorganization Energy}
  The reorganization energy $\lambda$ accounts for the energy change caused by the geometry variation during the charge transport, and is linked to four points on the potential energy surfaces of neutral (n) and charged (c) molecules at neutral (N) or charged (C) equilibrium geometries via:
@@
 %
-where $U^\text{xX}$ is the total DFT energy of $\text{x}=\text{n},\text{c}$ state in the $\text{X}=\text{N},\text{C}$ geometry.
-While in principle transfer pair specific, we use a single value of all molecular pairs.
+where $U^\text{xX}$ is the total DFT energy of $\text{x}=\text{n},\text{c}$ state in the \change{optimized} $\text{X}=\text{N},\text{C}$ geometry.
+\change{As the optimizations are performed in vacuum, a single value of $\lambda$ is used for all molecular pairs.
+In general, molecular conformations could be constrained by the environment in the material, affecting mostly soft degrees of freedom, such as dihedrals connecting rigid $\pi$-conjugated fragments with another.
+The effects on reorganization energy have shown to be small~\cite{Baumeier2011,10.1063/5.0049513} and are not considered in this work.}
 
@@
 The Hamiltonian of the dimer,  $H^\text{KS}_\text{D}$ (see Eq.~\ref{eq:KS2}), is diagonal in its eigenbasis $\left\{\vert \phi^\text{D}_k\rangle\right\}$ with eigenvalues $\left\{ \epsilon^\text{D}_k\right\}$, so $H^\text{KS}_\text{D} = \text{diag}(\epsilon^\text{D})$.
-With the projections of the monomer functions on the dimer eigenbasis, i.e., $p_{ik} = \langle \phi_i | \phi^\text{D}_k \rangle$ and  $p_{jk} = \langle \phi_j | \phi^\text{D}_k \rangle$, $J^0_{ij}$ can be calculated as $J^0_{ij} = \mathbf{p}_i^\text{T} \text{diag}(\epsilon^\text{D}) \mathbf{p}_j$.
-Similarly, $e_{i(j)} = \mathbf{p}_{i(j)}^\text{T} \mathbf{p}_{i(j)}$ and $S_{ij} =  \mathbf{p}_i^\text{T} \mathbf{p}_j$.
-All  of these operations are performed in the basis set representation of the Kohn--Sham wave functions (see Sec.~\ref{sec:es}) as implemented in VOTCA.
+With the projections of the monomer functions on the dimer eigenbasis, i.e., $m_{ik} = \langle \phi_i | \phi^\text{D}_k \rangle$ and  $m_{jk} = \langle \phi_j | \phi^\text{D}_k \rangle$, $J^0_{ij}$ can be calculated as $J^0_{ij} = \mathbf{m}_i^\text{T} \text{diag}(\epsilon^\text{D}) \mathbf{m}_j$.
+Similarly, $e_{i(j)} = \mathbf{m}_{i(j)}^\text{T} \mathbf{m}_{i(j)}$ and $S_{ij} =  \mathbf{m}_i^\text{T} \mathbf{m}_j$.
+All of these operations are performed in the \change{Gaussian-type orbital atomic} basis set representation of the Kohn--Sham wave functions (see Sec.~\ref{sec:es}) as implemented in VOTCA \change{and outlined in detail in \cite{baumeier_density_2010}.
+The underlying DFT calculations on monomers and dimers are done in vacuum, respectively.}
 
@@
 As is visible, the dipole moment is rather independent on \ahfx (note that the jump of the last shown data point appears more pronounced because of the very small scale on the $y$-axis).
-The isotropic polarizabilities in panel (d) exhibit a linear decrease with increasing value of \ahfx which can be attributed to an increasingly attractive effective potential from stronger the Hartree--Fock-like exchange term and consequently more strongly bound electrons as one can also see from the increasing ionization potential in panel (a).
+The isotropic polarizabilities in panel (d) exhibit a linear decrease with increasing value of \ahfx which can be attributed to an increasingly attractive effective potential from the stronger Hartree--Fock-like exchange term and consequently more strongly bound electrons as one can also see from the increasing ionization potential in panel (a).
 
@@
 This minimal energy (or rather all the energies in the low-energy region of the distributions) can have a very significant influence on the charge transport properties, depending on how much the site energy differences are influenced in the charge transport network.
-To further characterize the effect of different \ahfx values, we consider the largest absolute variation in the site energies depending on \ahfx by calculating the Chebyshev distance $D_{\ahfx} = \max\limits_{i}(|E_i(\ahfx=0.25) - E_i(\ahfx)|)$.
-From the results listed in Tab.~\ref{tab:maxEi}, one can see that on individual level the site energies can vary substantially, with more than \unit[0.1]{eV}.
+\change{We emphasize that the molecule(s) with the $E_\text{min}$ (and $E_\text{max}$) values also differ for the different cases.} To further characterize the effect of different \ahfx values, we consider the largest absolute variation in the site energies depending on \ahfx by calculating the Chebyshev distance $D_{\ahfx} = \max\limits_{i}(|E_i(\ahfx=0.25) - E_i(\ahfx)|)$.
+From the results listed in Tab.~\ref{tab:maxEi}, one can see that on individual level the site energies can vary substantially, with \change{at least one (but not the same) molecule whose energy has changed} more than \unit[0.1]{eV}.
 This variation is larger than the recorded values of $\sigma$ and with all \ahfx yielding the same mean site energy of \unit[-0.86]{eV} this could indicate non-neglibible effects on charge transport.
@@
 The individual distributions appear very similar, with a peak of $\log_{10}[(J_{ij}/\unit[]{eV})^2]$ between \unit[-5]{} to \unit[-6]{}, and a long tail of the distribution towards more negative values.
-The comparison with the PBE0 reference shows that while there is a clear correlation between the results for different values of \ahfx, the spread in the order of magntitudes of $J_{ij}^2$ can be very large especially for the lower coupling regions.
+The comparison with the PBE0 reference shows that while there is a clear correlation between the results for different values of \ahfx, the spread in the order of magnitudes of $J_{ij}^2$ can be very large especially for the lower coupling regions.
 Overall, the squared electronic coupling elements are found in a very wide range from $\unit[10^{-2}]{}$ to $\unit[10^{-15}]{(eV)^2}$ due to its exponential distance dependence and sensitivity to mutual orientation of the two involved molecules.
@@
 
-From the analysis of reorganization energies, site energies, and electronic coupling elements for different values of \ahfx, it is not clear how the mostly on distribution-level observed variations impact the overall charge transport properties.
+From the analysis of reorganization energies, \change{the distributions of } site energies and electronic coupling elements for different values of \ahfx, \change{it is not straighforward to assess how the} observed variations impact the overall charge transport properties.
 To scrutinize the dependence of such a material property, we now calculate the time-of-flight $\tau$ and report the respective values in Table~\ref{tab:ToF_MADN_HFX}.
 Here, we refer with ''full'' to time-of-flight obtained for the as-calculated charge transport network.
+
 One can see that $\tau$ varies by roughly one order of magnitude between $\ahfx=0$ ($\unit[6.3\cdot 10^{-9}]{s}$) and $\ahfx=0.25$ ($\unit[9.5\cdot 10^{-8}]{s}$), with an almost monotonous increase.
-When the squared coupling elements with values below $\unit[10^{-5}]{(eV)^2}$ are set to zero ($J_{ij} \mathbb{1}(\log_{10} J^2_{ij} > -5)$), one obtains only minimally, but consistently, larger $\tau$, corroborating the notion that the very small coupling elements are of little relevance for charge transport.
+\change{The range of ToF obtained by the variation of \ahfx in the PBE0 baseline agrees well with the range covered by the results from the popular hybrid functionals in Tab.~\ref{tab:actual_functionals} in the Appendix.} When the squared coupling elements with values below $\unit[10^{-5}]{(eV)^2}$ are set to zero ($J_{ij} \mathbb{1}(\log_{10} J^2_{ij} > -5)$), one obtains only minimally, but consistently, larger $\tau$, corroborating the notion that the very small coupling elements are of little relevance for charge transport.
 Finally, we also consider the case in which the energetic disorder is ignored ($\Delta E_{ij}=0$).
@@
 The black circles indicate the ToF obtained using explicit \ahfx values.
-Uncertainties considered are (a) in the eorganziation energy, (b) in the site energy, (c) in the coupling elements, and (d) in all simultaneously.}
+Uncertainties considered are (a) in the reorganziation energy, (b) in the site energy, (c) in the coupling elements, and (d) in all simultaneously.}
   \label{fig:mle_MADN_withE}
@@
 Here, we perform calculations for six different field directions (positive and negative Cartesian directions) with the source and sink conditions set accordingly.
-The electric field is taken account in the Marcus rate in Eq.~\ref{equ:Marcus} via an additional term in $\Delta E_{ij}$ given by $e\mathbf{F} \cdot \mathbf{r}_{ij}$, where $\mathbf{r}_{ij}$ connects the center-of-masses of molecules $i$ and $j$.
+The electric field is taken into account in the Marcus rate in Eq.~\ref{equ:Marcus} via an additional term in $\Delta E_{ij}$ given by $e\mathbf{F} \cdot \mathbf{r}_{ij}$, where $\mathbf{r}_{ij}$ connects the center-of-masses of molecules $i$ and $j$.
 Finally, we define for a certain field strength $F=\vert\mathbf{F}\vert$ the ToF drift mobility $\mu(F)$ is as the average over the six directions.
@@
 
-Figure~\ref{fig:PF_plot_ave} shows the plot of the charge mobility one logarithmic $y$-axis as a function of $\sqrt{F}$ to reveal the electric field dependence of the type $\mu(F)=\mu_0 \exp (\beta \sqrt{F})$ as predicted by Poole and Frenkel~\cite{frenkel_prebreakdown_1938}.
+Figure~\ref{fig:PF_plot_ave} shows the plot of the charge mobility on logarithmic $y$-axis as a function of $\sqrt{F}$ to reveal the electric field dependence of the type $\mu(F)=\mu_0 \exp (\beta \sqrt{F})$ as predicted by Poole and Frenkel~\cite{frenkel_prebreakdown_1938}.
 We show the explicit results for the six chosen \ahfx values together with the confidence interval estimate from the uncertainty quantification via Monte-Carlo sampling.
@@
 First, the analysis is restricted to variations in \ahfx as a proxy for different exchange-correlation functionals.
-While this approach captures a significant portion of the uncertainty, other factors such as basis set selection, dispersion corrections, and model approximations may also contribute to variability in the results.
+While this approach captures a significant portion of the uncertainty, \change{other parameters in the definition of exchange-correlation functionals} and other factors such as basis set selection, dispersion corrections, and model approximations may also contribute to variability in the results.
 Expanding the uncertainty quantification framework to include these factors would provide a more comprehensive understanding of the robustness of multiscale models.
@@
 
+\section*{Data Availability Statement}
+The data that support the findings of this article are openly available~\cite{Baumeier2025}.
+
 \bibliography{../references.bib}
@@
 \appendix*
+\section{Explicit ToF Results for hybrid and meta-GGA functionals}
+\begin{table}[h]
+\caption{Simulated ToF (in \unit[]{s}) for different hybrid GGA and non-hybrid (meta-)GGA functionals.}
+\begin{ruledtabular}
+  \begin{tabular}{c c c}
+        functional & \ahfx & $\tau$ \\
+    \hline
+    \multicolumn{3}{c}{\bf Hybrid GGA functionals}\\
+        PBE & 0.00 &  $6.4 \cdot 10^{-9}$ \\
+        B3LYP & 0.20 & $ 2.1 \cdot 10^{-8}$  \\
+        PBE0  & 0.25 & $ 9.5 \cdot 10^{-8}$  \\
+        BHLYP & 0.50 & $ 1.4 \cdot 10^{-7}$ \\
+    \multicolumn{3}{c}{\bf Non-hybrid (Meta-)GGA functionals}\\
+        PBE  & 0.00 &  $6.4 \cdot 10^{-9}$ \\
+        M06L & 0.00 & $ 8.9 \cdot 10^{-9}$  \\
+        TPSS & 0.00 & $ 6.9 \cdot 10^{-9}$ \\
+    \end{tabular}
+\end{ruledtabular}
+  \label{tab:actual_functionals}
+\end{table}
+
 \section{Electrostatic and polarized energy contributions}

### 2025-05-21 submit/paper.tex
Checked reply and manuscript. Few suggestions in red and a first attempt at reply to point 12.

@@
 Uncertainty quantification (UQ) is concept from computational science which allows for an estimation of confidence intervals for a quantity of interest (QoI) and an analysis of its sensitivity in models of a physical system that contain uncertain, maybe empirical, or noisy, parameters~\cite{sarkar_uncertainty_2017,oconnor_quantifying_2024, chernatynskiy_uncertainty_2013, suleimenova_tutorial_2021,coveney_reliability_2021, coveney_when_2021}.
-Many common UQ studies focus on models with (partial) differential equations, e.g., drift-diffusion equations in which the diffusivity as parameter, and assume a certain distribution for the values of the parameter(s).
+Many common UQ studies focus on models with (partial) differential equations, e.g., drift-diffusion equations in which the diffusivity as {\color{red}[Should this be: servers as the]} parameter, and assume a certain distribution for the values of the parameter(s).
 For the multiscale model of charge transport, it is not straightforward to cast the large variety of available exchange-correlation functionals into the role of a model parameter with some distribution.
@@
 \change{This choice is motivated by the observation that the simulated charge-carrier time-of-flight (ToF) for a set of commonly used functionals --- PBE~\cite{PhysRevLett.77.3865}, B3LYP~\cite{10.1063/1.464913}, PBE0~\cite{adamo_toward_1999}, BHLYP~\cite{10.1063/1.464913,lee_development_1988}, M06L~\cite{10.1063/1.2370993}, TPSS~\cite{PhysRevLett.91.146401} --- (see Tab.~\ref{tab:actual_functionals} in the Appendix) is more sensitive to the amount of included Hartree--Fock exchange than to variations in the generalized-gradient approximation (GGA) parametrization.
-While these functionals vary in more details, the data shows that for functionals with varying \ahfx, the simulated ToF spans two orders of magnitude, whereas among non-hybrid (meta-)GGA functionals the ToF results on the same order of magnitude.} More specifically, we take as the basis the PBE0 functional and scrutinize (i) how the predictions of the multiscale model of charge transport are affected by variation of $\alpha_\text{HFX}$ as a proxy for uncertainties in the choice of DFT functionals, (ii) what the level of confidence is in quantitative predictions, and (iii) what are the most sensitive quantities in the model.
+While these functionals vary in more details, the data shows that for functionals with varying \ahfx, the simulated ToF spans two orders of magnitude, whereas among non-hybrid (meta-)GGA functionals the ToF results {\color{red} are} on the same order of magnitude.} More specifically, we take as the basis the PBE0 functional and scrutinize (i) how the predictions of the multiscale model of charge transport are affected by variation of $\alpha_\text{HFX}$ as a proxy for uncertainties in the choice of DFT functionals, (ii) what the level of confidence is in quantitative predictions, and (iii) what are the most sensitive quantities in the model.
 In this sense, Eq.~\ref{equ:hybrid} is deceptively simple.
@@
 Uncertainty in the site energies, in contrast, has a much bigger impact on the estimates of $\tau$.
-From the distribution of $P_\mathbf{x}(\log_{10}(\tau))$ in Fig.~\ref{fig:mle_MADN_withE}(d), one can see than when all parameters are sampled, the result is dominated by the effects from the uncertainty in the site energies, with an overall similar shape and a confidence interval of $[-8.3,-6.6]$, corresponding to a range from about \unit[5]{ns} to about \unit[250]{ns} in $\tau$.
+From the distribution of $P_\mathbf{x}(\log_{10}(\tau))$ in Fig.~\ref{fig:mle_MADN_withE}(d), one can see that when all parameters are sampled, the result is dominated by the effects from the uncertainty in the site energies, with an overall similar shape and a confidence interval of $[-8.3,-6.6]$, corresponding to a range from about \unit[5]{ns} to about \unit[250]{ns} in $\tau$.
 

### 2025-05-21 submit/paper.tex
integrated Pim's comments and expanded p12r1

@@
 Uncertainty quantification (UQ) is concept from computational science which allows for an estimation of confidence intervals for a quantity of interest (QoI) and an analysis of its sensitivity in models of a physical system that contain uncertain, maybe empirical, or noisy, parameters~\cite{sarkar_uncertainty_2017,oconnor_quantifying_2024, chernatynskiy_uncertainty_2013, suleimenova_tutorial_2021,coveney_reliability_2021, coveney_when_2021}.
-Many common UQ studies focus on models with (partial) differential equations, e.g., drift-diffusion equations in which the diffusivity as {\color{red}[Should this be: servers as the]} parameter, and assume a certain distribution for the values of the parameter(s).
+Many common UQ studies focus on models with (partial) differential equations, e.g., drift-diffusion equations in which the diffusivity serves as the parameter, and assume a certain distribution for the values of the parameter(s).
 For the multiscale model of charge transport, it is not straightforward to cast the large variety of available exchange-correlation functionals into the role of a model parameter with some distribution.
@@
 \change{This choice is motivated by the observation that the simulated charge-carrier time-of-flight (ToF) for a set of commonly used functionals --- PBE~\cite{PhysRevLett.77.3865}, B3LYP~\cite{10.1063/1.464913}, PBE0~\cite{adamo_toward_1999}, BHLYP~\cite{10.1063/1.464913,lee_development_1988}, M06L~\cite{10.1063/1.2370993}, TPSS~\cite{PhysRevLett.91.146401} --- (see Tab.~\ref{tab:actual_functionals} in the Appendix) is more sensitive to the amount of included Hartree--Fock exchange than to variations in the generalized-gradient approximation (GGA) parametrization.
-While these functionals vary in more details, the data shows that for functionals with varying \ahfx, the simulated ToF spans two orders of magnitude, whereas among non-hybrid (meta-)GGA functionals the ToF results {\color{red} are} on the same order of magnitude.} More specifically, we take as the basis the PBE0 functional and scrutinize (i) how the predictions of the multiscale model of charge transport are affected by variation of $\alpha_\text{HFX}$ as a proxy for uncertainties in the choice of DFT functionals, (ii) what the level of confidence is in quantitative predictions, and (iii) what are the most sensitive quantities in the model.
+While these functionals vary in more details, the data shows that for functionals with varying \ahfx, the simulated ToF spans two orders of magnitude, whereas among non-hybrid (meta-)GGA functionals the ToF results are on the same order of magnitude.} More specifically, we take as the basis the PBE0 functional and scrutinize (i) how the predictions of the multiscale model of charge transport are affected by variation of $\alpha_\text{HFX}$ as a proxy for uncertainties in the choice of DFT functionals, (ii) what the level of confidence is in quantitative predictions, and (iii) what are the most sensitive quantities in the model.
 In this sense, Eq.~\ref{equ:hybrid} is deceptively simple.
